### 2017-06-06 Docs/Thesis/00_Acronyms.tex
New testes scripts in Python and Bash to calc the costFunction of the prototype. Also, at the folder Docs, the thesis text was added, i'm editing it using texstudio.

% For loading this file the following package and lines are 
% required in main latex file:
%
%   \usepackage[acronym]{glossaries}
%   \loadglsentries{acronyms}
%   \makeglossaries
%
% The entries follows are according to the line:
% \newacronym{<label>}{<abbrv>}{<full description>}
%[A]
%\newglossaryentry{IDS}{name=IDS, description={Coordinated Universal Time}}
%\newglossaryentry{adt}{name=ADT, description={Atlantic Daylight Time}}
%\newglossaryentry{est}{name=EST, description={Eastern Standard Time}}
%\printglossaries
%\newglossaryentry{CLI}
%{
%    name=CLI,
%    description={Command Line Interface}
%}
%\newglossaryentry{XSS}
%{
%    name=XSS,
%    description={Type of computer security vulnerability typically found in Web applications}
%}
\newglossaryentry{botnet}
{
    name=botnet,
    description={inter-connected computers and controlled by a malicious user in order to launch repetitive tasks against certain target}
}
\newglossaryentry{container}
{
	name=container,
	description={Lightweight virtualization method for running multiple isolated instances of an single Linux operating system}
}
\newglossaryentry{testbed}
{
    name=TESTBED,
    description={Platform for testing of containers, applications and servers}
}
\newglossaryentry{intelligence}
{
    name=intelligence,
    description={Information previously processed by intelligence analysts and that are relevant, actionable and valuable for the organization}
}
\newglossaryentry{INTRIG}
{
    name=INTRIG,
    description={Information \& Networking Technologies Research \& Innovation Group}
}
\newglossaryentry{TEST}
{
    name=TEST,
    description={testing}
}
\newglossaryentry{malware}
{
	name=malware,
	description={This description will be write later}
}
\newglossaryentry{actionable}
{
	name=actionable,
	description={Data that must be specific enough to prompt some response, or change}
}
\newglossaryentry{REN-ISAC}
{
	name=REN-ISAC,
	description={Research and Education Networking Information Sharing and Analysis Center}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%[A]
\newacronym{AaaS}{AaaS}{ALTO-as-a-Service}
\newacronym{CDF}{CDF}{Cumulative Distribution Function}
\newacronym{ALTO}{ALTO}{Application-Layer Traffic Optimization}
\newacronym{API}{API}{Application Programming Interface}
\newacronym[\glsshortpluralkey=ASes]{AS}{AS}{Autonomous System}
\newacronym{ASN}{ASN}{Autonomous System Number}
%[B]
\newacronym{BGP}{BGP}{Border Gateway Protocol}
%[C]
\newacronym{CDN}{CDN}{Content Delivery Network}
\newacronym{CL}{CL}{Confidence Level}
\newacronym{CI}{CI}{Confidence Interval}
\newacronym{CC}{CC}{Correlation Coefficient}
%[D]
%[E]
\newacronym{EPS}{EPS}{Endpoint Property Service}
\newacronym{ECS}{ECS}{Endpoint Cost Service}
%[F]
\newacronym{FCC}{FCC}{Federal Communications Commission}
%[G]
\newacronym{GDB}{GDB}{Graph Database}
\newacronym{GTC}{GTC}{General Terms and Conditions}
%[H]
%[I]
\newacronym{IETF}{IETF}{Internet Engineering Task Force}
\newacronym{IXP}{IXP}{Internet eXchange Point}
\newacronym{ISP}{ISP}{Internet Service Provider}
\newacronym{IX.br}{IX.br}{Internet Steering Committee project in Brazil}
%[J]
%[K]
\newacronym{KP}{KP}{Knowledge Plane}
%[L]
\newacronym{LG}{LG}{Looking Glass}
%[M]
\newacronym{MBA}{MBA}{Measuring Broadband America}
%[N]
\newacronym{NAP}{NAP}{Network Access Point}
\newacronym{NOS}{NOS}{Network Operating System}
\newacronym{NSP}{NSP}{Network Service Provider}
\newacronym{NOC}{NOC}{Network Operation Center}
\newacronym{NSF}{NSF}{National Science Foundation}
%[O]
\newacronym{OS}{OS}{Operating System}
\newacronym{ODL}{ODL}{OpenDaylight}
%[P]
\newacronym{P2P}{P2P}{Peer-to-peer}
\newacronym{P4P}{P4P}{Provider Portal for Applications}
\newacronym{PID}{PID}{Provider-Defined Identifier}
%[Q]
\newacronym{QoE}{QoE}{Quality of Experience}
%[R]
\newacronym{RS}{RS}{Route Server}
\newacronym{RA}{RA}{Routing Arbiter}
%[S]
\newacronym{SDN}{SDN}{Software-Defined Networking}
\newacronym{SP}{SP}{Service Provider}
%[T]
%[U]
%[W]
\newacronym{WAN}{WAN}{Wide Area Network}
%[V]
\newacronym{VM}{VM}{Virtual Machine}
%[X]
%[Y]
%[Z]

### 2017-06-06 Docs/Thesis/docs/appendix/appendixA.tex
New testes scripts in Python and Bash to calc the costFunction of the prototype. Also, at the folder Docs, the thesis text was added, i'm editing it using texstudio.

%\newpage
%\renewcommand{\appendixname}{Appendix}

%\appendix

\chapter{Revision of Probability}
\label{ap:revision-probability}

\section{Stochastic Process}

\section{Random variable}

\section{Probability Distribution Function (PDF)}

\section{Cumulative Distribution Function (CDF)}

\section{Expected value, Variance, Mean and Standard Deviation}

\section{Self-similarity}

\section{Heavy-tailed distributions}

\section{Hurst Exponent}

\section{Maximum likelihood function}

\section{Akaike information criterion}

\section{Bayesian information criterion}

\section{Estimation of parameters of stochastic distributions}

\subsection{Linear Regression and Gradient Descendant Algorithm}

\subsection{Maximum likelihood estimation}

\subsection{Others methods}

### 2017-06-06 Docs/Thesis/docs/chapter1.tex
New testes scripts in Python and Bash to calc the costFunction of the prototype. Also, at the folder Docs, the thesis text was added, i'm editing it using texstudio.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}\label{ch:introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{State of Affairs and Motivation}\label{sec:state-of-the-art}

%2nd-review
Emerging technologies such as SDN and NFV are great promises. If succeeding at large-scale, they would change drastically the development and operation of computer networks. But, especially on NFV, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since it has a much more predictable behavior. Once it is expected virtualization to impact negatively, these VNFs have to keep performance degradation and as small as possible, along with a high stability. Thus, guarantee the Service Layer Agreements on emerging scenarios is now a harder question. There is a demand for more reliable methods to ensure the SLAs, over different types of loads.

%2nd-review
It is already a well-known fact that the type of traffic used on performing tests matters. Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption. It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of a new technology. There are many reasons for this behavior, which includes burstiness and packet sizes.

%2nd-review
A burstier traffic can cause packet drops buffer overflows on network\cite{burstiness-queue-lenght}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}, what degrades the network performance. So, characteristics on packet-trains and inter-packet times, that cause traffic burstiness. Also, a burstier and realistic traffic will not just impact on performance, but on measurement as well. Realistic and burstiness traffic impacts on bandwidth measurement accuracy\cite{legotg-paper}\cite{background-traffic-matter}. Another key question is how applications will deal with packets. It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. A realistic traffic will have not a single packet-size as used by constant rate traffic generator tools, but a distribution\cite{packet-distribution-model}.

%2nd-review
Also, we have that realistic workload generators are essential security research\cite{ditg-paper}.  Generation of realistic workloads is important on evaluation firewall middleboxes. It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.   Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible, we can expect that its impact over virtualized middle-boxes should be even larger. That's because we will have an extra overhead introduced by the virtualization layer. Also, on SDN networks, each new flow arriving o a switch introduces an extra communication load between it and the controller, which can generate a performance degradation. 
We also have a flow-oriented operation on SDN switches. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual ISP scenario.

%2nd-review
Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a relevant subject. Also, how its underlying hardware will behave with this type of a load is an important case of study\cite{instrumentation-framework-nfv}.

%2nd-review
\section{Open-source Solutions}

%2nd-review
The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation.

%2nd-review
Some traffic generator tools offer support emulation of single application workloads. But this does not correspond to real complex scenarios, with a large number of distributed hosts in an Internet Service Provider (ISP) or even a Local Area Network (LAN).

%2nd-review
Other tools work as packet replay engines, such as TCPreplay and TCPivo. Although in that way is possible to produce a realistic workload at high rates, it comes with some issues. First, the storage space required becomes huge for long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources.

%2nd-review
Many tools support a larger set of protocols and high-performance such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen. They can give a good control of the traffic and high rates. The most relevant examples of features are:

\begin{itemize}

%2nd-review
\item Throughput, the number of bytes, number of packets.

%2nd-review
\item Protocol: most of the tools give support to network and transport protocols. Many also offer support to Link and Application protocols;

%2nd-review
\item Header and payload configuration: support to header customization includes source and destination port/addresses, QoS parameters, flags, etc. Some traffic generators also allow customizing payload bytes.

%2nd-review
\item Inter-packet time: custom inter-packet times. Some tools offer a set of stochastic distributions to control inter-packet times. The user can use these stochastic functions to emulate realistic inter-arrival times.

%2nd-review
\item On/off periods: support of packet trains periods. Many offer stochastic models to control these bursts.

%2nd-review
\item Sending time and start-time: the user can use these features to control flows timings.

%2nd-review
\item Packet-size: support for different packet sizes. Some tools offer constant values or stochastic distributions to control packet sizes.

%2nd-review
\item Many configurable flows.

%2nd-review
\item Emulation of specific applications: common examples are Web server/client communication, VoIP, HTTP, FTP, p2p applications, and so on.

\end{itemize}

%2nd-review
But, in this case, selecting a good configuration is by itself a research project. How to use each parameter to simulate a specific scenario is a hard question \cite{legotg-paper}\cite{selfsimilar-ethernet}. It is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic patterns and experimental evaluation.

%2nd-review
Some tools like Swing and Harpoon, try to use the best of both worlds. Both use capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels which are able to provide a high degree of realism\cite{swing-paper}. But they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem on setup and configuration. Swing\cite{swing-paper} aims to generate realistic background traffic, but do not reach high throughputs \cite{swing-paper} \cite{legotg-paper}. As is possible to see, this a result of the fact that its traffic generation engine is coupled to its modeling framework. You can't opt to use a newer/faster packet generator. The only way of replacing the traffic engine is changing and recompiling the original code. And this is a hard task.

%2nd-review
Since synthetic traffic traces generation is mature in academia, the creation of custom network workloads through the configuration of high-throughput open-source is an affordable task. But it is not often available in an automatic way, and most of the times is a challenging question\cite{legotg-paper}, and still, requires expert knowledge. It requires time, study, and is vulnerable to human mistakes and lack of validation. Such work may require weeks to complete a realistic reproduction of a single scenario, so most of the time it is just not done. We argue that widely (i.e. affordable) existing approaches can be regarded as simplistic often point solutions to more general cases.

%2nd-review
Also, by itself, choosing which workload generator tool may fit better for the user needs is not a simple question. Tools like D-ITG\footnote{\href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}} provide support to many different stochastic functions, Ostinato\footnote{\href{http://ostinato.org/}{http://ostinato.org/}} provide a larger support for protocols, and a higher throughput for each thread\cite{comparative-trafficgen-tools}, and other like Seagull\footnote{\href{http://gull.sourceforge.net/doc/WP_Seagull_Open_Source_tool_for_IMS_testing.pdf}{http://gull.sourceforge.net/doc/WP\_Seagull\_Open\_Source\_tool\_for\_IMS\_testing.pdf}} are responsive.

\section{\textit{SIMITAR}: SnIffing, ModellIng and TrAffic geneRation}

\begin{figure*}[ht!]
        \centering
        \includegraphics[height=2.4in]{figures/ch1/layer-diagram}
        \caption{ Conceptual idea: a <configuration><modelling><intelligence><emulation><acceleration><visualization><distributed><open-source>}
    \label{fig:layer-diagram}
\end{figure*}

%2nd-review
Now, we are going to formalize these exposed concepts in a proposal of research and development. Or main targets here are:

\begin{itemize}

%2nd-review
\item Survey the available open-source Ethernet workload tools available, addressing different features available;

%2nd-review
\item Define what is a realistic Ethernet traffic, and the man approaches found in literature;

%2nd-review
\item Create a general method for modeling and parameterization of Ethernet traffic, aiming to mimic any traffic provided as input;

%2nd-review
\item Create a software \textit{tool} able of \textit{learning} patterns and characteristics of real network traffic traces, and based on the acquired knowledge, allowing to reproduce network traffic with similar (but not equal) characteristics, \textit{avoiding} the storage of \textit{pcap} files. It must have a flow-oriented operation, and be able to choose the best features to represent each flow traffic. It will generate realistic Ethernet traffic based on these features learned, using available open source tools and APIs;

\end{itemize}

%2nd-review
We call our  tool \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}.  These targets summarize a target of research, based on what we have exposed until now. We also will define some extra features, we want to have on our tool:

\begin{itemize}

%2nd-review
\item Traffic Flow Programmability: the tool records this parameterization on a light-weight and human-readable version of a \textit{pcap} file. So the user can create his own models of traffic based on flows, in a platform-independent manner. He will not have to learn how to configure and script each tool.

%2nd-review
\item Easy expansion: The sniffing, modeling, and traffic generation processes must work separately, so updates will be easy to manage. Also, the traffic generation is flow-oriented (it generates each flow individually). Thus the scheduling of each flow is platform-independent. In this way, is much easier to expand the support for new traffic generation engines.

\end{itemize}

%2nd-review
Our main goal is to offer an easier configuration, realism than the available platforms today, at a reasonable speed. We are introducing programmability and abstraction to the traffic generation, since the user may create a custom traffic in a platform agnostic way. The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.

%2nd-review
Instead of storing a file huge \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace. This tool will store the generalized set of parameters in a human and machine readable XML file we call \textit{Compact Trace Descriptor} (\textit{CTD}). Then, we use this data as input for a traffic generator engine. We do so using APIs or creating new processes in a controlled manner. So will be possible to control packet parameters and flow's behavior in a automatized and self-configuring way.

%2nd-review
Using a component methodology, we decouple the traffic generation, from the data collection and parameterization process. Building it in this non-monolithic way,  enable a simple port for different traffic generators engines, what make our tools easy for updating with newer technologies. A project guideline is to reuse as much code and components as possible from the open-source community.

%2nd-review
Now, we are going to formalize these exposed concepts in a proposal of research and development. Or main targets here are:

\begin{itemize}

%2nd-review
\item Survey the available open-source Ethernet workload tools available, addressing different features available;

%2nd-review
\item Define what is a realistic Ethernet traffic, and the man approaches found in literature;

%2nd-review
\item Create a general method for modeling and parameterization of Ethernet traffic, aiming to mimic any traffic provided as input;

%2nd-review
\item Create a software \textit{tool} able of \textit{learning} patterns and characteristics of real network traffic traces, and auto-configure the network traffic workloads, allowing to reproduce network traffic with similar (but not equal) characteristics, avoiding storage of \textit{pcap} files.

%2nd-review
\item It must have a flow-oriented operation, and be able to choose the best features to represent each flow traffic. It will generate realistic Ethernet traffic based on these features learned, using available open source tools and APIs;

\end{itemize}

%2nd-review
We call our  tool \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}.  These targets summarize a target of research, based on what we have exposed. Now, we will define some extra features, we want our tool to have:

\begin{itemize}

%2nd-review
\item Traffic Flow Programmability: the tool records this parameterization on a light-weight and human-readable version of a \textit{pcap} file. So the user can create his own models of traffic flow based traffic, in a platform-independent manner. He will not have to learn how to configure and script each tool.

%2nd-review
\item Easy expansion: The sniffing, modeling, and traffic generation processes must work separately, so updates will be easy to manage. Also, the traffic generation is flow-oriented (it generates each flow individually). Thus the scheduling of each flow is platform-independent. In this way, is much easier to expand the support for new traffic generation engines.

\end{itemize}

%2nd-review
Our main goal is to offer an easier configuration, realism than the available platforms today, at a reasonable speed. We are introducing programmability and abstraction to the traffic generation, since the user may create a custom traffic in a platform agnostic way. The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.

%2nd-review
Instead of storing a file huge \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace. This tool will store the generalized set of parameters in a human and machine readable XML file we call \textit{Compact Trace Descriptor} (\textit{CTD}). Then, we use this data as input for a traffic generator engine. We do so using APIs or creating new processes in a controlled manner. So will be possible to control packet parameters and flow's behavior in a automatized and self-configuring way.

%2nd-review
Using a component methodology, we decouple the traffic generation, from the data collection and parameterization process. Building it in this non-monolithic way,  enable a simple port for different traffic generators engines, what make our tools easy for updating with newer technologies. A project guideline is to reuse as much code and components as possible from the open-source community.

%We also aim some advantages from the addition features: data visualization, packet acceleration, and distributed operation. Providing data visualization, it will not just work as a workload generator, but as a benchmark tool, providing statistics and performance analysis. Using packet acceleration, we will be able to produce a high throughput at the wire, and at the same time generate a trace as realistic as possible. Through a distributed operation of multiple instances, it will be easier to control its operation in a virtualized environment.  Finally, a project guideline is to reuse as much code and components as possible from the open-source community.

\section{Document Overview}

%2nd-review
In this introductory chapter, we presented an abstract of the state of the art, a problem statement, and proposed an approach for research and requirements for development.

%2nd-review
In the chapter section~\ref{ch:literature-review}, we go deeper on some subjects mentioned here. First, we present an extensive survey on open-source traffic generator tools. We summarize the benefits, and features supported by each one. After, we present a brief survey of important topics on realistic traffic generation. There, we are defining some important concepts we are going to use in this work, such as self-similarity, and heavy-tailed functions. Then, we discuss some techniques of validation of traffic generator tools and some practical examples. We will define our tests using this set. Finally, we will discuss some main topics on emerging network scenarios: SDN and NFV.

%2nd-review
Chapter ~\ref{ch:architecture} introduces the methodology used in our project. We describe \textit{SIMITAR} low-level requirements and define an architecture and algorithms.  We also present its classes design and explain how \textit{SIMITAR} we can expand to any traffic generator engine with an API, CLI or script interface. We use the D-ITG API as an example. We explain its operation and suggest some use cases.

%2nd-review
The following chapter~\ref{ch:modeling-evaluation} is a direct sequence of the last. We present how the modeling process actually works, using a defined data set (which we are going to use in the rest of the work). We also present some evaluation methods to check the modeling quality. We also describe our used and developed algorithms. Finally, we give some implementation.

%2nd-review
In the chapter Proof of concepts and Validation~\ref{ch:validation}, we define a set of metrics based on previous tests on validation of traffic generators found in the literature. Here, we focus on packet, flow, and scaling metrics. we test \textit{SIMITAR} in an emulated SDN testbed with Mininet, using OpenDayLight as controller\cite{web-opendaylight}.

%On chapter Use Cases~\ref{ch:use-cases}, we present two use cases of our tool. One using an NFV testbed, and other using an SDN p4 switch. Here we focus on QoS metrics, such as mean RTT. %use tools such as tcptrace and NFPA  on the use cases

%2nd-review
Finally, on chapter Conclusion and Future Work~\ref{ch:conclusion}, we summarized our work and highlights future works to improve \textit{SIMITAR} on realism and performance.

### 2017-06-06 Docs/Thesis/docs/chapter2.tex
New testes scripts in Python and Bash to calc the costFunction of the prototype. Also, at the folder Docs, the thesis text was added, i'm editing it using texstudio.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Literature Review}\label{ch:literature-review}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%2nd-review
In this chapter, we will review some topics from the literature that serve as a base for this whole work. First of all, we will define what is a traffic generator tool, and introduce a taxonomy that distinguishes them. After this, we will present a survey of many available open-source and free traffic generators. We introduce each tool and present a feature comparison between each of them. As far as we know, this is the extensible features comparison of traffic generators available so far in the literature. The first two sections are devoted for this topic.

%2nd-review
We also will overview network traffic modeling and realistic traffic generation. We will discuss stochastic models that used to describe the Internet traffic. Based on that we will discuss what features a realistic traffic should have and highlight important features needed to control to achieve it.  We can count self-similarity and burstiness,  header fields, packet size and flow features.

%2nd-review
In the following section, we will make a brief discussion on validation of traffic generator tools. First, presenting the main approaches of validation made on literature. Then, we will discuss some validation study cases of related works, always introducing new concepts when needed.

%Finally, we will present a short overview of new arriving network technologies: SDN and NFV. We will use them as use cases at the chapter ~\ref{ch:use-cases}. Also, we will present our motivations for this choice.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Traffic generator tools}

%2nd-review
A traffic generator tool is a system capable of creating and injecting packets into a computer network in a controlled way to generate a synthetic traffic \cite{validate-trafficgen}.  there is a huge variety of traffic generation tools described on the literature \cite{validate-trafficgen} \cite{ditg-paper} and available i the open-source community\footnote{\href{http://www.icir.org/models/trafficgenerators.html}{http://www.icir.org/models/trafficgenerators.html}}. In fact, as exposed in the chapter~\ref{ch:introduction} it is a hard task to find what is the best tool for your needs. This is a cause of many  different approaches and methodologies available to network traffic generator's developers \cite{validate-trafficgen}.

%2nd-review
%Also, previous research such as Oliver et al. \cite{flow-level-ip} have demonstrated that one unique statistical law cannot express all complexity of an original Internet trace (an Internet trace is an Internet traffic capture made over a network interface). So, just selecting a stochastic process for a traffic generator, do not guarantee realism.

%2nd-review
New network generators development is directly related with to the current needs of network environment, applications sets, and purpose of use \cite{validate-trafficgen}. According to the context, you may want to send as many packets as possible through an interface to  equipment stress . So, in this case, a maximum throughput traffic generator is more interesting. In others situations, you may want a stochastically realist profile. Or even a traffic generator that reflect a special scenario such as a specific application; for example a client and server exchanging data\cite{surge-paper}. In this case, the target would be to stress a server, not an equipment. Another possibility a huge variety of protocols available, or even support of new protocols.

%2nd-review
Alongside with the traffic generators, there are many APIs available. There are low-level APIs which enables direct packet injection and capture, such as \textit{libpcap}\cite{web-tcpdump}, \textit{libtins}\cite{web-libtins}, DPDK\cite{web-dpdk} and the GNU C socket library\cite{web-socket}. And there are high-level APIs, provided by traffic generator tools, such as D-ITG\cite{ditg-paper}, Ostinato\cite{web-ostinato} and MoonGen\cite{moongen-paper}. In this case they enable an easy custom traffic generation and statistics. Also, there are implementations of hardware-based traffic generators using NetFPGAs\footnote{\href{http://netfpga.org/site/\#/}{http://netfpga.org/site/\#/}}.

%2nd-review
In the literature there are many classifications of traffic generators\cite{sourcesonoff-paper}\cite{hybrid-traffic-gen}\cite{validate-trafficgen}\cite{do-you-trust}. Some tools may have some features compatible with one or more classes. But classify them it is an efficient way to distinguish the difference between these tools. We will give two different taxonomies:

%2nd-review
\begin{itemize}
\item According to its abstraction level \cite{do-you-trust};
%\item According to its purpose (engine replay, throughput, realism) \cite{validate-trafficgen}
\item According to its implementation.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classes of traffic generator tools}

The most common traffic generator taxonomy found is  according to its abstraction level\cite{do-you-trust}. They are: Application-level/Special-scenarios, flow-level, packet-level and Closed-loop and multi-level traffic generators. We present a diagram  ilustrating its concept at figure ~\ref{fig:layers-workload-tools}.

\subsubsection{According to its abstraction level}

\textbf{Application-level/Special-scenarios traffic generators}: they try to emulate the behavior of network applications, simulating real workloads stochastically, responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool. That means, the behavior of the output may change according to what packets have arrived in the network interface} or both. As examples we have Surge\cite{surge-paper} able to emulate the behavior of web clients and services. The behavior of such applications is, in general, based on request-response exchanges models.

\textbf{Flow-level traffic generators}: they are able to configure and reproduce precisely features at the flow level\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}. Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from live routers.

\textbf{Packet-level traffic generators}: most traffic generators available fall in this class. They are able to craft packets and inject them into the network based on Inter departure times (IDT) and packet size(PS). \cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model based generators. Traffic Replay engines, such TCPreplay\cite{web-tcpreplay}, are  able to read packet capture files (\textit{pcap} files), and inject copies on a network interface. Model-based generators, such D-ITG \cite{ditg-paper}, TG\cite{web-tg}, may have PS and IDT configured by the user. They can configure IDT  either by constant values (defining the packet rate or bandwidth) or by stochastic models. Maximum throughput engines like Ostinato and Seagull are tools that the main goal is to perform end-to-end stress testing. Are included in this category generators that are able to craft packets from the link layer, like Brute\cite{web-brute}, KUTE\cite{web-brute}, and pktgen\cite{web-pktgen}.

\textbf{Closed-loop and multi-level traffic generators}: this is a more recent class of network traffic generator, and its proposal is to take into account existing interaction among each layer of the network stack, to create background network traffic as close as possible from reality. One of the most relevant tools we can found is Swing \cite{swing-paper}. Swing take into account many points of each layer, using an approach based on randomness and responsiveness \cite{swing-paper}. That means, it uses PS and IDT stochastic models, but also take into account flow and application layer behavior. Swing is able to model things like\cite{swing-paper}: 
\begin{itemize}

\item User behavior: Number of request and responses, time between requests and responses;

\item Request and Responses: number of connections, time between start of connections;

\item Connection: Number of request and responses per connection, applications modeling (HTTP, P2P, SMTP), transport protocols TCP/UDP based on the application, response sizes, request sizes, user think between exchanges on a connection;

\item Packet: packet size (Maximum transmission unit), IP addresses, (MTU), bit rate and packet arrival distribution,

\item Link: link Latency Delay, loss rates.

\end{itemize}

Swing take as input collected \textit{pcap} files. Botta at al. \cite{do-you-trust} argues that due its complexity, they are rarely used to conduct experimental researchers. Also, we can  justify due its overheads, since the performance of such complex traffic generator is limited\cite{legotg-paper}. The authors Vishwanat et al. \cite{swing-paper} cite that they have generated traces of about of 200 Mbps, about the same result found by \cite{legotg-paper}. In the other hand, D-ITG reached 9808 Mbps\cite{comparative-trafficgen-tools} in a link of 10 Gbps, but operating as a maximum throughput generator.g1

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.4]{figures/ch2/types-workload-tools}
	\caption{Diagram representing different traffic generators, according to its abstraction layer.}
	\label{fig:layers-workload-tools}
\end{figure}

\subsubsection{According to its implementation}

\textbf{Software-only traffic generators}: Implementations of traffic generators completely independent of its running hardware platform. This comprehends most of traffic generator tolls.

\textbf{Software and hardware-dependent traffic generators}: Traffic generators implemented in software, but dependent of underlying hardware. The most preeminent examples of this class are implemented over DPDK\cite{web-dpdk}. DPDK works directly on the NIC interface, avoiding overheads of the Operational System. As cited on its official website, this approach permits huge precision and speed in the timing of packets, since it is able to send and receive packets within less than 80 clock cycles.

\textbf{Hardware traffic generators}: This open-source traffic generators implementations are implemented in hardware description language (VHDL/Verilog), and work on NetFPGAs. Some examples of implementations are: PacketGenerator \cite{web-netfpgapacketgenerator}, Caliper \cite{web-caliper}, and OSNT Packet Generator \cite{web-osnt}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open-source and free traffic generator tools}

In this section we will presented a short review of many open-source tools available for synthetic traffic generation and benchmark. The goal in this section is to present both the most mentioned tools in the literature, and the most recent and advanced ones. On table~\ref{tab:trafficgen-list1} is presented a short review of some of the main features of such tools, such as support for Operational systems, protocols, stochastic functions available for traffic generation, available interfaces, and traffic generator class. Some free, but not open-source traffic generators are listed as well.

Before present our survey, we will refer to some tools mentioned in literature, but we couldn't found source code and manual. \textbf{BRUNO}\cite{bruno-paper} is traffic generator implemented aiming performance and accuracy on timings. It has many configurable parameters that allow emulation of many web server scenarios. \textbf{Divide and conquer}\cite{validate-trafficgen}: Divide and conquer is replay engine that works in a distributed manner. It is able to split traces among multiple commodity PCs, and reply packets, to produce realistic traffic. Some others mentioned tools\cite{web-ditg} we weren't able to find any reference of available features are: \textbf{UDPgen}, \textbf{Network Traffic Generator}, \textbf{Packet Shell}, \textbf{Real-Time Voice Traffic Generator}, \textbf{PIM-SM Protocol Independent Multicast Packet Generator}, \textbf{TTCP}, \textbf{SPAK, Packet Generator}, \textbf{TfGen}, \textbf{TrafGen} and \textbf{Mtools}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Packet-crafting libraries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Packet-level traffic generators}

\textbf{D-ITG}\cite{ditg-paper}\cite{web-ditg}: D-ITG(Distributed Internet Traffic Generator) is a platform capable to produce IPv4 and IPv6 traffic defined by IDT and PS probabilistic distributions such as constant, uniform, Pareto, Cauch, Normal, Poisson, Gamma, Weibull, and On/Off; both configurable and pre-defined for many applications, from Telnet, through online games. It provide many flow-level options of customization, like duration, start delay and number of packets, support to many link-layer and transport-layer protocols, options, sources and destinations addresses/ports. If has support for NAT traversal, so it is possible to make experiments between two different networks separated by the cloud. D-ITG can be also used to measure packet loss, jitter, and throughput. D-ITG may be used through a CLI, scripts, or a C API, that can be use to create applications and remotely control another hosts through a daemon. The code may be downloaded on its official website.

\textbf{Ostinato}\cite{web-ostinato}: Ostinato is a packet crafter, network traffic generator and analyzer with a friendly GUI(“wireshark in reverse” as the documentation says) and a Python API. This tool permits craft and send packets of different protocols  at different rates. Support Server/Client communication, and a huge variety of protocols, from the link layer(such as 802.3 and VLAN) to the application layer (such HTTP and SIP). It is also possible to add any unimplemented protocols, through scripts defined by the user. The code may be downloaded on its official website (http://ostinato.org/downloads).

\textbf{Seagull}\cite{wp-seagull}\cite{web-seagull}: Seagull is a traffic generator and test open-source tool, released by HP. It has support of many protocols, from link layer to application layer, and it support is easily extended, via XML dictionaries. As the documentation argues, the protocol extension flexibility is one of the main features. It support high speeds, and is reliable, being tested through hundreds of hours. It can also generate traffic using three statistical models: uniform(constant), best-effort and Poisson.The code may be downloaded on its official website.

\textbf{BRUTE}\cite{web-brute}: Is a traffic generator that operates on the top of  Linux 2.4-6 and 2.6.x, not currently being supported on newer versions. It also support some stochastic functions(constant, poisson, trimodal) for departure time brust, and is able to simulate VoIP traffic. The source code(old release) may me fond on official website and on google code repository (\href{https://code.google.com/archive/p/brute/}{https://code.google.com/archive/p/brute/}).

\textbf{PackETH} \cite{web-packeth}: PackETH is GUI and CLI stateless packet generator tool for ethernet.It support many adjustments of parameters, and many protocols as well, ans can set MAC addresses. The download link may be found on it official website.

\textbf{Iperf}\cite{web-iperf}: Ipef is network traffic generator tools, designed for the measure of the maximum achievable bandwidth on IP networks, for both TCP and UDP traffic, bu can evaluate delay, windows size, and packet loss.  Although it is, originally, a command line tool, some developers have created a GUI interface, called Jperf\cite{web-jperf}. There is also a Java API, for automating tests\cite{jperf-git}. Support IPv4 and IPv6. The source code can be found on their offical website.

\textbf{NetPerf}\cite{web-netperf}: Netperf is a benchmark tools that can be used to measure performance of many types of networks, providing tests for both unidirectional throughput, and end-to-end latency. It uses a command line interface, and has support to TCP, UDP and SCTP, both over IPv4 and IPv6. The source code can be downloaded at website homepage.

\textbf{sourcesOnOff}\cite{sourcesonoff-paper} \cite{web-sourcesonoff}: sourcesOnOff is a recent traffic generator released on 2014, that aims to generate realistic synthetic traffic using probabilistic models to controll on and off time of traffic flows. As shown on the paper, it is able to guarantee self-similatiry, an has support to many probabilistic distributions for the on/off times: Weibull, Pareto, Exponential  and Gaussian. Supports TCP and UDP over IPv4. The source code can be found on the author personal page.

\textbf{TG}\cite{web-tg}: TG is a traffic generator that is able to generate and receive one-way packet streams transmitted from the UNIX user level process between source and traffic sink nodes. It is controlled by a simple specification language, that enables the craft of different lengths and interarrival times distributions, such as Constant, uniform, exponential and on/off(markov2).

\footnote{not open-source}\textbf{MGEN}\cite{web-mgen}: MGEN (Multi-Generator) is a traffic generator developed by the Naval Research Laboratory (NRL) PROTocol Engineering Advanced Networking (PROTEAN) Research Group. It uses as input can be used to emulate the traffic patterns of unicast and/or multicast UDP and TCP IP applications. It support many different types of stochastic functions, nominated periodic, Poisson, burst jitter and clone which are able to control inter departure times and packet size.

\textbf{KUTE}\cite{web-kute}: KUTE is a kernel level packet generator, designed to have a maximum performance traffic generator, and receiver mainly for use with Gigabit Ethernet. It works in the kernel level, sending packets as fast as possible, direct to the hardware driver, bypassing the stack. But KUTE works only on Linux 2.6, and has only be tested on Ethernet Hardware. Also, it only supports constant UDP traffic. The source code of the tools is available on its homepage.

\textbf{RUDE \& CRUDE}\cite{web-rude-crude}: RUDE(Real-time UDP Data Emitter) and CRUDE(Collector for RUDE), are small and flexible programs which runs on user-level. It has a GUI called GRUDE. It works in a similar way MGEN does, but has a higher time resolution. But it works only with UDP. The source code can be found on its homepage.

\footnote{not open-source}\textbf{NetSpec}\cite{web-netspec}: NetSpec is tool designed to do network tests, as opposed to doing point to point testing. NetSpec provides a framework that allows a user to control multiple processes across multiple hosts from a central point of control, using daemons that implement traffic sources and sinks, along with measurement tools. Also, it is able to model many different traffic patterns and applications, such as host maximum rate; Constant Bit Rate (CBR) at user level; WWW, World Wide Web; FTP, File Transfer Protocol; telnet; MPEG video; voice and video teleconference. This source and application wasn't available anymore on its webpage.

\textbf{Nping}\cite{web-nping}: active hosts, as a traffic generator for network stack stress testing, ARP poisoning, Denial of Service attacks, route tracing, etc. Nping CLI permits the users control over protocols headers. To source code can be downloaded on its website.

\textbf{TCPreplay}\cite{web-tcpreplay}: TCPreplay is a user-level replay engine, that can use pcap files as input, and then forward, packets in a network interface. It can modify some header parameters as well. The source code of TCPreplay can be found on github \href{https://github.com/synfinatic/tcpreplay}{https://github.com/synfinatic/tcpreplay}.

\textbf{TCPivo}\cite{tcpivo-paper}\cite{web-tcpivo}: TCPivo is a high-speed traffic replay engine that is able to read traffic traces, and replay packets in a network interface, working at kernel level. Until the present data, it is not currently supported kernel versions greater than 2.6. The source code can be fond on its official website.

\textbf{NetFPGA PacketGenerator}\cite{web-netfpgapacketgenerator}: NetFPGA PacketGenerator is a hardware-based traffic generator and capture tool, build over the NetFPGA 1G, and open FPGA platform with 4 ethernet interfaces of 1 Gigabit of bandwidth each. It is a replay engine tool which uses as input \textit{pcap} files. It is able to accurately control the delay between the frames, with the default delay being the same in the pcap file. It is also able to capture packets, and report statistics of the traffic. The code can be downloaded on github.

\textbf{NetFPGA Caliper}\cite{web-caliper}:  is a hardware-based traffic generator, build on NetFPGA 1G, built over NetThreads platform, a FPGA microprocessor which support threads programing. Different form NetFPGA PacketGenerator, Caliper is able to produce live packets. It is written in C.  The code can be downloaded on github.

\textbf{NetFPGA OSNT}\cite{web-osnt}: OSNT(Open Source Network Tester) is hardware based network traffic generator built over the NetFPGA 10G. As NetFPGA 1G, NetFPGA 10G is a FPGA platform with 4 ethernet interfaces, but with 10 Gigabits of bandwidth.  OSNT is a replay engine, and is loaded with pcap traces. OSNT Source Network Test code can be found on github.

\textbf{Dpdk Pktgen}\cite{web-dpdk-pktgen}: Pktgen is a traffic generator measurer built over DPDK. DPDK is a development kit, a set of libraries and drivers for fast packet processing. DPDK was designed to run on any processor, but has some limitation on terms of supported NICs, that can be found on its website.

\textbf{MoonGen}\cite{moongen-paper}\cite{web-moongen} : MoonGen is a scriptable high-speed packet generator built over DPDK and LuaJIT. It is able to send packets at 10 Gbit/s, even with 64 bytes packets on a single CPU core. MoonGen can achieve this rate even if each packet is modified by a Lua script. Also, it provides accurate timestamping and rate control. It is able to generate traffic using several protocols ( IPv4, IPv6, IPsec, ARP, ICMP, UDP, and  TCP), and can generate different inter-departure times, like a Poisson process and burst traffic. This project can be found on github.

\textbf{gen\_send/gen\_recv}\cite{web-gensend-genrecv}: gen\_send and gen\_recv are simple UDP traffic generator applications. It uses UDP sockets, and  gen\_send is able to control features like desired data rate, packet size and inter packet time. You can find their source at \href{http://www.citi.umich.edu/projects/qbone/generator.html}{http://www.citi.umich.edu/projects/qbone/generator.html}.

\textbf{mxtraf}\cite{web-mxtraf}: mxtraf enables that a small number of hosts to saturate a network, with a tunable mixture of TCP and UDP traffic. You can found the source code at \href{http://mxtraf.sourceforge.net/}{http://mxtraf.sourceforge.net/}.

\textbf{Jigs Traffic Generator (JTG)}\cite{web-jtg}: is a simple, accurate traffic generator. JTG process only sends one stream of traffic, and steam characteristics are defined only by command line arguments. It also supports IPv6. You can find the code at \href{http://www.netlab.tkk.fi/~jmanner/jtg/}{http://www.netlab.tkk.fi/~jmanner/jtg/}.

\textbf{*Poisson Traffic Generator}:

%Tabela: revisao dos principais geradores de trafego
\renewcommand{\tabularxcolumn}[1]{>{\small}m{#1}}

\begin{table}[t!]
\caption{Review of features of some open-source traffic generators}
\begin{center}
\begin{footnotesize}
\begin{tabularx}{\linewidth}{
|>{\hsize=0.9\hsize\raggedright\arraybackslash}X	% 10% of 4\hsize 
|>{\hsize=1.16\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=1.37\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=1.16\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=0.7\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=0.7\hsize\centering\arraybackslash}X|					% 30% of 4\hsize
% sum=4.0\hsize for 4 columns
}
	\hline
	\textbf{Traffic Generator} & 
    \textbf{Operating System} & 
    \textbf{Protocols supported} & 
    \textbf{Stochastic distribution} & 
    \textbf{Interface} & 
    \textbf{Operation Level} \\

    \hline
    GenSyn	&
    Java virtual machine &
    TCP, UDP, IPv4 &
    (\textit{user model}, \textit{responsible}) &
    GUI &
    application-level \\

    \hline
    Harpoon &
    FreeBSD 5.1-5.4, Linux 2.2-2.6, MacOS X 10.2-10.4, and Solaris 8-10 &
    TCP, UDP, IPv4, IPv6 &
    (\textit{flow-level model, based on a input trace})&
    CLI &
    flow-level\\

    \hline
    D-ITG &
    Linux, Windows, Linux Familiar, Montavista, Snapgear &
    IPv4, IPv6, ICMP, TCP, UDP, DCCP, SCTP &
    Constant, uniform, exponential, pareto, cauchy, normal, poisson, gamma, on/off, \textit{pcap}&
    CLI, Script, API &
    packet-level \\

    \hline
    Ostinato &
    Linux, Windows, FreeBDS &
    Ethernet/802.3/LLC SNAP; VLAN (with QinQ); ARP, IPv4, IPv6, IP Tunnelling (6over4, 4over6, 4over4, 6over6);TCP, UDP, ICMPv4, ICMPv6, IGMP, MLD; HTTP, SIP, RTSP, NNTP etc... \textit{extensible}&
    constant &
    GUI, CLI, Script, API &
    packet-level\\

    \hline
    Seagull&
    Linux, Windows &
    IPv4, IPv6, UDP, TCP, SCTP, SSL/TLS and SS7/TCAP. \textit{extensible}&
    constant, poisson, \textit{responsible} &
    CLI, API &
    packet-level\\

    \hline
    PackETH &
    Linux, MacOS, Windows &
    ethernet II, ethernet 802.3, 802.1q, QinQ, ARP, IPv4, IPv6, UDP, TCP, ICMP, ICMPv6, IGMP &
    constant &
    CLI, GUI &
    packet-level \\

    \hline
    Iperf &
    Windows, Linux, Android, MacOS X, FreeBSD, OpenBSD, NetBSD, VxWorks, Solaris &
    IPv4, IPv4, UDP, TCP, SCTP &
    constant &
    CLI &
    packet-level \\

    \hline
\end{tabularx} 
\label{tab:trafficgen-list1}
\end{footnotesize}
\end{center}
\end{table}

\begin{table}[t!]
\caption{Review of features of some open-source traffic generators}
\begin{center}
\begin{footnotesize}
\begin{tabularx}{\linewidth}{
|>{\hsize=0.9\hsize\raggedright\arraybackslash}X	% 10% of 4\hsize 
|>{\hsize=1.16\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=1.37\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=1.16\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=0.7\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=0.7\hsize\centering\arraybackslash}X|					% 30% of 4\hsize
% sum=4.0\hsize for 4 columns
}
	\hline
	\textbf{Traffic Generator} & 
    \textbf{Operating System} & 
    \textbf{Protocols supported} & 
    \textbf{Stochastic distribution} & 
    \textbf{Interface} & 
    \textbf{Operation Level} \\

    \hline
    Swing &
    Linux &
    IPv4, TCP, UDP, HTTP, NAPSTER, NNTP and SMTP &
    \textit{capture trace}  &
    CLI &
    closed-loop and multilevel \\

    \hline
    BRUTE &
    Linux &
    IPv4, IPv6 &
    constant, poisson, trimoda &
    CLI &
    packet-level \\

    \hline
    SourcesOnOff &
    Linux &
    IPv4, TCP, UDP &
    on/off (Weibull, Pareto, Exponential and Gaussian) &
    CLI &
    packet-level \\

     \hline
    TG &
    Linux, FreeBSD, Solaris SunOS &
    IPv4, TCP, UDP &
    Constant, uniform, exponential, on/off &
    CLI &
    packet-level \\

    \hline
    Mgen &
    Linux(Unix), Windows &
    IPv4, IPv6, UDP, TCP, SINK &
    Constant, exponential, on/off &
    CLI, Script &
    packet-level \\

     \hline
    KUTE &
    Linux 2.6 &
    UDP &
    constant &
    kernel module &
    packet-level \\

     \hline
    RUDE \& CRUDE &
    Linux, Solaris SunOS, and FreeBSD &
    IPv4, UDP &
    constant &
    CLI &
    packet-level\\

     \hline
    NetSpec &
    Linux &
    IPv4,UDP, TCP &
    uniform, Normal, log-normal, exponential, Poisson, geometric, Pareto, gamma &
    Script &
    packet-level \\

     \hline
    Nping &
    Windows, Linux, Mac OS X &
    TCP, UDP, ICMP, IPv4, IPv6, ARP &
    constant &
    CLI &
    packet-level \\

     \hline
    TCPreplay &
    Linux &
    \textit{pcap} &
    constant, \textit{pcap} &
    CLI &
    packet-level (\textit{replay engine}) \\

     \hline
    TCPivo &
    Linux &
    \textit{pcap} &
    constant, \textit{pcap} &
    CLI &
    packet-level (\textit{replay engine}) \\

     \hline
     NetFPGA PacketGenerator &
     Linux &
     \textit{pcap} &
     constant &
     CLI &
     packet-level (\textit{hardware-based}) \\

    \hline
\end{tabularx} 
\label{tab:trafficgen-list2}
\end{footnotesize}
\end{center}
\end{table}

\begin{table}[t!]
\caption{Review of features of some open-source traffic generators}
\begin{center}
\begin{footnotesize}
\begin{tabularx}{\linewidth}{
|>{\hsize=0.9\hsize\raggedright\arraybackslash}X	% 10% of 4\hsize 
|>{\hsize=1.16\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=1.37\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=1.16\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=0.7\hsize\centering\arraybackslash}X					% 30% of 4\hsize
>{\hsize=0.7\hsize\centering\arraybackslash}X|					% 30% of 4\hsize
% sum=4.0\hsize for 4 columns
}
	\hline
	\textbf{Traffic Generator} & 
    \textbf{Operating System} & 
    \textbf{Protocols supported} & 
    \textbf{Stochastic distribution} & 
    \textbf{Interface} & 
    \textbf{Operation Level} \\

    \hline
    NetFPGA Caliper &
    Linux &
    \textit{pcap} &
    constant &
    CLI &
    packet-level (\textit{hardware-based}) \\

    \hline
    NetFPGA OSNT &
    Linux &
    \textit{pcap} &
    constant &
    CLI &
    packet-level (\textit{hardware-based}) \\

     \hline
     MoonGen &
     Linux &
     IPv4, IPv6, IPsec, ICMP, UDP, TCP &
     constant, poisson &
     Script API (Lua) &
     packet-level (\textit{hardware-dependent}) \\

    \hline
    Dpdk Pktgen &
    Linux &
    IPv4, IPv6, ARP, ICMP, TCP, UDP, \textit{pcap} &
    constant, \textit{pcap} &
    CLI, Script API (Lua) &
    packet-level (\textit{hardware-dependent})\\

     \hline
     Dpdk NFPA &
     Linux &
     \textit{pcap} &
     constant, \textit{pcap} &
     CLI, Web &
     packet-level (\textit{hardware-dependent}) \\

     \hline
     LegoTG &
     Linux &
     \footnote{Depend on underlying tools used} &
     \footnote{Depend on underlying tools used}  &
     CLI, Script &
     packet-level \\

     \hline
     LiTGen &
     \textit{missingInfo} &
     \textit{missingInfo} &
     \textit{wifi model} &
     \textit{missingInfo} &
     closed-loop and multilevel\\

     \hline 
     gen\_send/ gen\_recv &
     Solaris, FreeBSD, AIX4.1, Linux &
     UDP &
     constant &
     CLI &
     packet-level \\

     \hline 
     mxtraf &
     Linux &
     TCP, UDP, IPv4 &
     constant &
     GUI, script &
     packet-level \\

     \hline 
     Jigs Traffic Generator (JTG) &
     Linux &
     TCP, UDP, IPv4, IPv6 &
     constant &
     CLI &
     packet-level \\

     \hline 
     SURGE &
     Linux &
     TCP, IPv4 &
     \textit{application model} &
     CLI &
     application-level\\

     \hline 
     Httperf  &
     Linux &
     TCP, IPv4 &
     \textit{application model} &
     CLI &
     aplication-level \\

     \hline 
     VoIP Traffic Generator &
     Linux &
     UDP, IPv4 &
     \textit{application model} &
     CLI &
     application-level \\

    \hline
\end{tabularx} 
\label{tab:trafficgen-list3}
\end{footnotesize}
\end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Application-level/Special-scenarios traffic generators}

\footnote{not open-source}\textbf{ParaSynTG}\cite{parasyntg-paper}: application-level traffic generator configurable by input parameters, which considers most of the observes www traffic workload properties.

\footnote{not open-source}\textbf{EAR}\cite{validate-trafficgen}: traffic generator that uses a technique called “Event Reproduction Ratio”  to mimic wireless IEEE 802.11 protocol behavior.

\footnote{not open-source}\textbf{GenSyn}\cite{web-gensyn}: network traffic generator implemented in Java, that mimic TCP and UDP connections, based on user behavior.

\textbf{Surge}\cite{surge-paper}: Surge is an application level workload generator which emulates a set of real users accessing a web server. It matches many empirical measurements of real traffic, like server file distribution, request size distribution, relative file popularity, idle periods of users and other characteristics. Its source code can be  found at \href{http://cs-www.bu.edu/faculty/crovella/surge_1.00a.tar.gz}{http://cs-www.bu.edu/faculty/crovella/surge\_1.00a.tar.gz}.

\textbf{Httperf}\cite{web-httperf}: Is an application lever traffic generator to measure web server performance. It uses the protocol HTTP (HTTP/1.0 and HTTP/1.1), and offer many types of workloads while keeping track of statistics related to the generated traffic. Its most basic operation is to generate a set of HTTP GET requests and measure the number of replies and response rate.  You can found its source code on GitHub \href{https://github.com/httperf/httperf}{https://github.com/httperf/httperf}.

\textbf{VoIP Traffic Generator}: it is a traffic generator written in Perl, and creates multiple streams of traffic,  aiming to simulate VoIP traffic. You can found its code at \href{
https://sourceforge.net/projects/voiptg/}{
https://sourceforge.net/projects/voiptg/}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Flow-level and Closed-loop and multi-level traffic generators}

\textbf{Harpoon}\cite{harpoon-paper}: Harpoon is a flow based traffic generator, that is able to 
automatically extract form Netflow traces parameters, in order to generate flows that exhibit the same statistical characteristics measured before, including temporal and spatial characteristics. The source code of Harpoon can be found on github (\href{https://github.com/jsommers/harpoon}{https://github.com/jsommers/harpoon}).

\textbf{Swing}\cite{swing-paper} \cite{web-swing}: Swing is a closed-loop multi-layer, and network responsive generator. It is able to read capture traces, and captures the packet interactions of many applications, being able to models distributions for user, application, and network behavior, stochastic and responsively. As mentioned in the previous section, Swing is able to model user behavior, REEs, connection, packets, and network. The code may be downloaded on its official website.

\footnote{not open-source}\textbf{LiTGen}(Lightweight Traffic Generator)\cite{litgen-paper} is a open-loop, multilevel traffic generator. It is able to model wireless network traffic in a peer user and application basis. This tool models the traffic in three different levels: packet level, object level (smaller parts of an application session), and session level.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Others traffic generation tools}

\textbf{NFPA}\cite{nfpa-paper}: NFPA is a benchmark tools based on DPDK Pkgen, specialized on executing and automatize performance measurements over network functions. It works being directly connected to an specific device under tests. It uses built-in and user defined traffic traces, and Lua scripts control and collect information of DPDK Pktgen. It has an command line and Web interface, and automatically plot the results.

\textbf{LegoTG}\cite{legotg-paper}: LegoTG is a modular framework for composing custom traffic generation. It aims to simplify the combination on the use of different traffic generators and modulators on different testbeds, automatizing the process of installation, execution, resource allocation and synchronization via a centralized orchestrator, which uses a software repository. It already has support to many tools, and to add support to new tools is necessary to add and edit two files, called TGblock, and ExFile.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview of Network Traffic Modeling and Realistic Traffic Generation}

Along with the huge diversity of traffic generator tools, there are many traffic generation approaches, depending on the main purpose of the traffic generator. Maximum throughput traffic generators have in mind the idea of sending as much traffic through an interface as it can. But the generation of a realistic workload is a need for validation of many aspects of a new infrastructure. First, to generate a realist traffic, we need to define the complexity that our synthetic traffic must have, compared to real ones. Depending on our purpose, we may focus on one or more aspects of the traffic. For example, protocols, header customization, packet-level features (inter-departure, packet-size) and flow level features (number of flows and flow modeling).

As presented, there is a huge amount of open-source traffic generators available. Each of them with many different sets of features available. But, on the generation of realistic workload, the set of possibilities become much more restrict. On the other hand, there are many works on characterization, modeling, and simulation of different types of network workload \cite{ditg-paper}.

As stated by Botta et al.\cite{ditg-paper},  a synthetic network workload generation over real networks should be able to: (1) Capture real traces complexity over different scenarios; (2) Be able to custom change some specific properties generated traffic ; (3) Return measure indicators of performance experienced by the workload.

To generate realistic traffic workloads, two main approaches exist in the literature \cite{ditg-paper}. First, we have the trace-based generation, where replay engines generate the traffic. As examples, we have TCPreplay, TCPivo, and others. The other approach is an analytical model-based generation. In this case, the packet generation process depends on analytical and stochastic models. As examples of tools, we have Swing, D-ITG, TG, MGEN RUDE/CRUDE, Seagull, and many others.  These tools control traffic features using stochastic and analytical models and/or enable header customization.

The advantage of the replay engine is its simplicity. There is no need for stochastic modeling of features. It just needs to know how to read the packet from a file, called \textit{pcap}, and replicate it on the internet interface. Most of the traffic features such as packet sizes, inter-departure, and packet headers will be realistic. But, its major issue is the storage space required to generate traffic without replication. In fact, depending on the throughput required, just some seconds of traffic replication will cost GB's of hard disk space. If it is necessary to generate traffic for a longer time, or good \textit{pcaps} traces are not available, analytical are necessary.

Classical models for network traffic generation were the same used in telephone traffic, such as pure Poisson or Poisson-related, like Markov and Poisson-batch\cite{selfsimilar-ethernet}. They are able to describe the randomness of an Ethernet link but cannot capture the presence of "burstiness" in a long-term time scale, such as traffic "spikes" on long-range "ripples" \cite{selfsimilar-ethernet}. In fact, as we can see at \cite{selfsimilar-ethernet} the nature of the Ethernet traffic is self-similar. It has a fractal-like shape since characteristics seen in a small time scale should appear on a long-scale as well. This is most of the time referred as long-range dependence or degree of long-range dependence (LRD). One way to identify if a process is self-similar is checking its Hurst parameter, or Hurst exponent H, as a measure of the "burstiness" and LRD. In fact, a random process is self-similar and LRD  if 0.5 < H < 1 \cite{stochartic-selfsimilar}. Furthermore, some later studies advocate the use of more advanced multiscaling models (multifractal), addressed by investigations that state multifractal characteristics.

Another desired characteristic is a high variability, in mathematical terms, an infinite variance. Process with such characteristic is said to be heavy-tailed \cite{sourcesonoff-paper}. In practical terms, that means a sudden discontinuous change can always occur. Heavy tail means that a stochastic distribution is not exponentially bounded\cite{sourcesonoff-paper}. This means that a value far from the mean does not have a negligible probability of occurrence. We can express self-similar and heavy-tailed processes using heavy-tailed stochastic distributions, such as Pareto and Weibull. As a reference for these stochastic distributions, a list in the table ~\ref{tab:distributions-equations}. In the last column, we indicate if the distribution is or not heavy-tailed.

\begin{table}[t!]
\centering
\caption{Probability density function (PDF) and Cumulative distribution function (CDF) of some random variables, and if this stochastic distribution has or not self-similarity property. Some functions used to express these distributions are defined at the table ~\ref{tab:distributions-definitions} }
\label{tab:distributions-equations}
\scalebox{0.82}{ 
\begin{tabular}{lcccr}
Distribution & PDF Equation & CDF Equation & Parameters & Heavy-tailed\\ \hline
\\
\multirow{2}{*}{Poisson} & \multirow{2}{*}{$f[k] = \frac{e^{-\lambda}\lambda^k}{k!}$} & \multirow{2}{*}{$F[k] = \frac{\Gamma(\lfloor k + 1 \rfloor, \lambda)}{ \lfloor k \rfloor!}$} &  $\lambda > 0$  (mean, \\
 &  &  & variance) & no \\ 
\\ 
\multirow{2}{*}{Binomial} & \multirow{2}{*}{$f[k] = \binom{n}{k}p^{k}(1 - p)^{n - k} $} & \multirow{2}{*}{$F[k] = I_{1 - p}(n - k, 1 + k)$} &  $n > 0$ (trials)\\  &  &  &$p > 0$ (success)  & no \\ 
\\
\multirow{2}{*}{Normal} & \multirow{2}{*}{$f(t) =  \frac{1}{\sqrt[]{2\sigma^2}\pi}e^{\frac{(t - \mu)^2}{2\sigma^2}}$ } & \multirow{2}{*}{ $F(t) = \frac{1}{2}[ 1 + \text{erf}(\frac{t - \mu}{\sigma\sqrt[]{2}})]$ } &  $\mu$ (mean) \\ &  &  & $\sigma > 0$ (std.dev) & no \\ 
\\ 
\multirow{2}{*}{Exponential} & \multirow{2}{*}{ $f(t) = \begin{cases} \lambda e^{-\lambda t} ;& t \geq 0 \\ 0;& t < 0 \end{cases} $  }   & \multirow{2}{*}{ $F(t) = 1 - e^{-\lambda t} $ } & \\ &  &  & $\lambda > 0$ (rate)  & no \\ 
\\
\multirow{2}{*}{Pareto} & \multirow{2}{*}{$f(t) = \begin{cases} \frac{\alpha t_{m}^\alpha}{t^{\alpha + 1}} ;& t \geq t_{m} \\ 0;& t < t_{m} \end{cases} $ } & \multirow{2}{*}{$F(t) = \begin{cases} 1 - (\frac{t_{m}}{t})^\alpha ;& t \geq t_{m} \\ 0;& t < t_{m}\end{cases} $} &  $\alpha > 0$ (shape)  \\ & &  &  $t_{m} > 0$ (scale)   & yes \\ 
\\ 
\multirow{2}{*}{Cauchy} & \multirow{2}{*}{ $f(t) = \frac{1}{\pi \gamma}[\frac{\gamma^2}{(t - t_{0})^{2} + \gamma^{2}}]$ } & \multirow{2}{*}{ $F(t) = \frac{1}{\pi}\arctan( \frac{t - t_{0}}{\gamma} ) + \frac{1}{2}  $ } &  $\gamma > 0$ (scale) \\ &  &   & $t_{0} > 0$ (location) & yes \\  
\\
\multirow{2}{*}{Weibull} & \multirow{2}{*}{ $f(t) = \begin{cases} \frac{\alpha}{\beta^\alpha}t^{\alpha - 1}e^{(t/\beta)^{\alpha}}; & t \geq 0 \\ 0; & t < 0 \end{cases}$  } & \multirow{2}{*}{ $F(t) = \begin{cases} 1 - e^{-(t/\beta)^{\alpha}}; & t \geq 0 \\ 0 ; & t < 0  \end{cases}$ } & $\alpha  > 0 $ (shape) \\ &  &  & $\beta > 0$ (scale)  & yes \\
\\
\multirow{2}{*}{Gamma} & \multirow{2}{*}{ $ f(t) = \frac{\beta^{\alpha}}{\Gamma(\alpha)}t^{\alpha - 1}e^{-\beta t}  $ } & \multirow{2}{*}{$ F(t) = 1 - \frac{1}{\Gamma(\alpha)}\Gamma(\alpha, \beta x) $} & $\alpha > 0$ (shape) \\ &  &  & $\beta > 0$ (rate) & no \\
\\ 
%\multirow{2}{*}{Student's t} & \multirow{2}{*}{} & \multirow{2}{*}{} &  \\ &  &  & & \\ 
%\\
\multirow{2}{*}{Beta} & \multirow{2}{*}{ $ f(t) = \frac{x^{\alpha - 1}(1 - x)^{\beta - 1}}{B(\alpha, \beta)} $ } & \multirow{2}{*}{ $ F(t) = I_{x}(\alpha, \beta) $ } &  $\alpha > 0$ (shape) \\ &  &  & $\beta > 0$ (shape) & no \\ 
\\ 
\multirow{2}{*}{Log-normal} & \multirow{2}{*}{ $ f(t) = \frac{1}{t \sigma \sqrt[]{2 \pi}}e^{- \frac{(\ln(x) - \mu)^{2}}{2 \sigma^{2}}} $ } & \multirow{2}{*}{ $ F(t) = \frac{1}{2} + \frac{1}{2}\text{erf}[\frac{\ln(x) - \mu}{\sqrt[]{2} \sigma}] $ } & $\mu$ (location)\\
 &  &  & $ \sigma > 0 $ (shape) & yes \\ 
\\
\multirow{2}{*}{Chi-squared} & \multirow{2}{*}{ $ f(t) = \frac{1}{2^{\frac{k}{2}}\Gamma(\frac{k}{2}) }t^{\frac{k}{2} - 1}e^{-\frac{t}{2}} $ } & \multirow{2}{*}{ $ F(t) = \frac{1}{\Gamma(\frac{k}{2})}\gamma(\frac{k}{2}, \frac{x}{2}) $ } &  \\
 &  &  & $ k \in \mathbb{N}_{>0} $ &  no\\ 
\\

\hline
\end{tabular} 
} %scalebox
\end{table}

\begin{table}[t!]
\centering
\caption{Definitions of some functions used by PDFs and CDFs}
\label{tab:distributions-definitions}
\begin{tabular}{ll}
\hline
Function                             & Definition \\ 
\hline
\\
Regularized Incomplete beta function & $ I_{x}(a, b) = \frac{B(x; a, b)}{B(a, b)} $           \\
\\
Incomplete beta function             & $ B(x; a, b) = \int_{0}^{x} t^{a - 1} (1 - t)^{(b - 1)} \text{d}t $           \\
\\
Beta function                        & $ B(x; a, b) = \int_{0}^{1} t^{a - 1} (1 - t)^{(b - 1)} \text{d}t $           \\
\\
Error function                       & $ \text{erf}(x) = \frac{1}{\sqrt[]{\pi}}\int_{x}^{-x} e^{-t^{2}} \text{d}t $           \\ 
\\
Lower incomplete Gamma function      & $ \gamma(s, x) = x^{s}\Gamma(s)e^{-x}\sum_{k = 0}^{\infty}\frac{x^{k}}{\Gamma(s+k+1)} $  \\
\\
\hline
\end{tabular}
\end{table}

We call these concepts of High variability and Self-similarity Noah and Joseph Effects \cite{selfsimilar-highvariability}. We can see at\cite{selfsimilar-highvariability} that a superposition of many ON/OFF sources (or packet trains) using ON and OFF that obey the Noah Effect (heavy-tailed probabilistic functions), also obey the Joseph effect. That means, it is self-similar and we can use to describe an Ethernet traffic. As we can see, some works on the literature on synthetic traffic uses this principle, like sourcesOnOff\cite{sourcesonoff-paper}, or have to support models like D-ITG\cite{ditg-paper}.

An accurate replication of a workload should be able to control packet headers such as QoS fields, protocols, ports, addresses, and so on. Traffic generators provide support for these features, more frequently in a limitted way. Most offer support just common protocols, such as TCP, UDP, and IPv4. On the other hands, there are some which provide a huge variety of support and control over packet headers like PackETH\cite{web-packeth} and D-ITG. Other tools are even able to enable you to extend this feature and develop support to new protocols. For example, Ostinato and Seagull permit you to define your own customized protocol.

%revisão da sessão 0.1 até aqui

An important desirable feature that should be controlled is the packet size distribution since each flow may have its own packet distribution. As we can see in many works, the packet size of a trace may result in a huge impact in a trace throughput \cite{stochartic-selfsimilar}\cite{performance-trafficgen}; small packets cause a huge overhead in the packet throughput. In the table ~\ref{tab:packet-size-impact} there are a survey of results found by two different works \cite{comparative-trafficgen-tools} \cite{performance-trafficgen} about the impact of different packet sizes in the throughput rate.Therefore, it is an important factor we must taken into account in the evaluation of new proposals, and in the implementation of network workloads generators. On packet size distribution characterization, we can find many works in the literature. For example, \cite{packet-distribution-model} analyses many packet sizes distributions of many packet traces, in many environments. Some general results are that 90\% of UDP packets are smaller than 500 bytes, and most packets transmitted using TCP have 40 bytes (acknowledgment) and 1500 bytes (Maximum Transmission Unit, MTU) \cite{packet-distribution-model}. For UDP traffic, we have similar results, since mostly they are bimodal as well \cite{udp-flows-model}. Ostrowsky et al.\cite{udp-flows-model} found that, on UDP traces the modes of two regions are 120 and 1350 bytes, with a cut-off value of 750 bytes. They also find that roughly UDP packets constitute 20\% of the total number of packets on captures.

\begin{table}[t!]
\centering
\caption{Two different studies evaluating the impact of packet size on the throughput. Both compare many available open-source tools on different testbeds. In all cases, small packet sizes penalize the throughput. Bigger packet sizes achieve a higher throughput.}
\label{tab:packet-size-impact}
\scalebox{0.9}{
\begin{tabular}{|l|c|c|c|}
\hline
 & \multicolumn{3}{c|}{Traffic Generators} \\ \cline{2-4} 
\multicolumn{1}{|c|}{Article and setup} &  & \multicolumn{1}{c|}{Maximum bit-rate} & \multicolumn{1}{c|}{Maximum bit-rate} \\
 & \multicolumn{1}{c|}{Toll} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}at small packet \\ sizes\end{tabular}} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}at big packet \\ sizes\end{tabular}} \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Comparative study of various \\ Traffic Generator Tools \cite{comparative-trafficgen-tools} ;\end{tabular}} & PackETH & 150 @(64 bytes) & 1745 @(1408 bytes) \\ \cline{2-4} 
\begin{tabular}[c]{@{}l@{}}setup: Linux (Centos 6.2, \\ Kernel version 2.6.32),\end{tabular} & Ostinato & 135 @(64 bytes) & 2850 @(1408 bytes) \\ \cline{2-4} 
\begin{tabular}[c]{@{}l@{}}Inter(R) Xeon(R) CPU with 2.96GHz,\\  RAM of 64GB , NIC Mellanox\end{tabular} & D-ITG & 62 @(64 bytes) & 1950 @(1408 bytes), \\
\begin{tabular}[c]{@{}l@{}}Technologies MT25418 {[}ConnectXVPI \\ PCIe 2.0 2.5GT/s - IB DDR{]}\end{tabular} &  &  & \begin{tabular}[c]{@{}l@{}}9808 @(1460 bytes, \\ 12 threads)\end{tabular} \\ \cline{2-4} 
10 Bbps. Protocol: TCP & Iperf & * & \begin{tabular}[c]{@{}l@{}}8450 @(1460 bytes, \\ 12 threads)\end{tabular} \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Performance Monitoring of Various \\ Network Traffic Generators \cite{performance-trafficgen};\end{tabular}} & Iperf & 46.0 @(128 bytes) & 93.1 @(1408 bytes) \\ \cline{2-4} 
\begin{tabular}[c]{@{}l@{}}Inter(R) Pentium 4(R), CPU \\ with 3.0GHz, RAM 1GB,\end{tabular} & Netperf & 46.0 @(128 bytes) & 89.9 @(1408 bytes) \\ \cline{2-4} 
\begin{tabular}[c]{@{}l@{}}NIC Intel Pro/100 Adapter \\ (100Mbps),\end{tabular} & D-ITG & 38.1 @(128 bytes) & 83.1 @(1408 bytes) \\ \cline{2-4} 
\begin{tabular}[c]{@{}l@{}}Hard Drivers Seagate Barracuda \\ 7200 series with 20BG. \\ Protocol:TCP\end{tabular} & IP Traffic & 61.0 @(128 bytes) & 76.7 @(1408 bytes) \\ \hline
\end{tabular}
}
\end{table}

As could be expected, router capture traces, are mostly bimodal, since most of the traffic in backbones is TCP. But, the size of the each mode may change depending on the application. For example, a www usage tends to have a mode close to the MTU higher if compared to an FTP capture. So, for packet workload generation, these results suggest the importance of controlling the packet size behavior for each flow\cite{packet-distribution-model}.

On flow level traffic generation, some packet-level traffic generators permit the control of flow generation, mostly by manually controlling headers parameters through an API or via scripting. In terms of automatic flow configuration, an example is Harpoon\cite{harpoon-paper} which can to automatic configure its flows, using as input NetFlow Cisco traffic traces to automatically setting parameters. Harpoon deals with flow modeling in three different levels: file level, session level, and user level, not dealing with packet level at all.  In the file level, Harpoon model two parameters:  the size of files being transferred, and the time interval between consecutive file requests, called inter-file request time. The middle level is the session level, that consist of sequences files transfer between two distinct IP addresses. The session level has three components: the IP spatial distribution, the second is the inter-session start times and the third is the session duration. The last level is the user level. In Harpoon, "users" are divided on "TCP" and "UDP" users. Which conduct consecutive session using these protocols. This level has two components: the user ON time, and the number of active users. By modeling the number of users, harpoon can reproduce temporal(diurnal) traffic volumes, which is an interesting feature, once it is common on Internet traffic.

A feature that may be highly desirable for realistic traffic generation is  operating in closed-loop like Swing\cite{swing-paper}. This means when the changes its behavior at run time according to the observation made in real-time, with involves modification of the traffic to be generated \cite{ditg-paper}. These modifications involve changes on parameters of statistical distributions of inter-departure time (IDT) and packet size (PS).

Closed-loop multi-layer and application layer traffic generators also models application and user behavior, like the number of request/response exchanges per connection, response sizes, request sizes, user think time between connections, the number of RREs, RREs think time, etc \cite{swing-paper}.

Finally, on newly arrived internet scenarios, due its increasing complexity of networks and the rise of many new technologies, such as SDN\cite{sdn-survey} and NFV\cite{nfv-challenges}; which include the replacement of old and reliable technologies by new and not as strongly validated ones. In this sense that a point to point validation is not enough anymore, an arriving requirement is the distributed workload generator, which includes a logically centralized module such as a controller\cite{ditg-paper}, or an orchestrator\cite{legotg-paper}, able to control and synchronize and deploy workloads of many different hots. As examples, D-ITG API gives this possibility via daemons, and LegoTG\cite{legotg-paper} Framework implements a complete and easily extensible orchestrator. Due new scenarios where virtualization network functions and hardware is overcoming hardware, a logically centralized control and orchestration of synthetic workloads is a feature that easy the work\cite{legotg-paper}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Validation of Traffic Generator Tools}

There are many possible validation technics for traffic generator tools found in the literature. Any of them have their own importance and application. Magyesi and Szabó\cite{validate-trafficgen} presents an abstract of the main metrics validation metrics. The authors classify them in four categories: packet based metrics, flow based metrics, scaling characteristics and QoS/QoE related metrics. As suggested by other works\cite{swing-paper}, we state here that an synthetic traffic can be considered realistic, metrics of these four classes are close to measured on a real scenario.

Here we present a short review of each of these validation techniques. After that, we will present seven different study cases on validation of related traffic generators. They are Swing\cite{swing-paper}, Harpoon\cite{harpoon-paper}, D-ITG\cite{ditg-paper}, sourcesOnOff\cite{sourcesonoff-paper}, MoonGen\cite{moongen-paper}, LegoTG\cite{legotg-paper} and NFPA\cite{nfpa-paper}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Packet Based Metrics}

Packet based are the most simple and more used metrics in the validation of traffic generators \cite{validate-trafficgen}. The most relevant packet based metrics are throughput\cite{do-you-trust}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}\cite{moongen-paper} (bytes and packets), packet size distribution\cite{packet-distribution-model} and inter packet time distribution (inter-arrival and inter-departure) \cite{sourcesonoff-paper} \cite{ditg-paper}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Flow Based Metrics}

Flow based metrics are becoming more important since newer network elements, like SDN devices, are able of execute flow-based operations\cite{validate-trafficgen}\cite{sdn-survey}. Magyesi and Szabó\cite{validate-trafficgen} consider the most important flow metrics the flow size distribution and the flow volume. The flow volume are proportional to the number of flow instances and flow-based device should run simultaneously. And the flow sizes defines how much time each instance will run.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scaling Characteristics}

Second order characteristics such as burstiness and long-range dependence are responsible for the complex nature of the internet traffic\cite{validate-trafficgen}. Due its non-stationary nature, traditional methods fail on extract useful information\cite{validate-trafficgen}. The first analysis made in that way were focus on the estimation of the Hurst exponent\cite{selfsimilar-ethernet}. They demonstrated the self-similar nature of the ethernet traffic. As explained before, a self-similar traffic should an Hust exponent $H$, such as $ 0.5 < H < 1$. Over the years, wavalet based analysis have become an efficient way of reveal correlations, bursts and scaling  nature of the ethernet traffic\cite{validate-trafficgen}. Many works found on the literature have used wavelet based analysis \cite{swing-paper}\cite{non-intrusive-wavelet}\cite{wavelet-analysis-long-range}.

Huang et al. \cite{non-intrusive-wavelet} and Abry and Veitch \cite{wavelet-analysis-long-range} offers an extensible explanation of  wavelet-based scaling analysis (WSA) or wavelet multi-resolution energy analysis (WMA). Here, is presented a brief summary of the main information presented by these two works, which you should refer to, for further details.

First, consider a time series $X_{0,k}$ for $k = 0, 1, ... 2^n$:

\begin{equation}
\{X_{0,k}\} = \{ X_{0,0}, X_{0,1}, ... ,X_{0,2^{n}} \}
\end{equation}

Supose then that we coaser $X_{0}$ in another time-serie $X_{1}$ with half of the original resolution, but using  $ \sqrt[]{2} $  as normalization factor:

\begin{equation}
X_{1,k} = \frac{1}{\sqrt{2}}(X_{0,2k} + X_{0,2k+1})
\end{equation}

If we take the differences, instead of the avarages, evaluate the so called \textit{details}.

\begin{equation}
d_{1,k} = \frac{1}{\sqrt{2}}(X_{0,2k} - X_{0,2k+1})
\end{equation}

We can continue repeating this process, writing more coarse time series $X_{2}$ from $X_{1}$, until we reach $X_{n}$. Therefore, we will get a collection of \textit{details}:

\begin{equation}
\{d_{j,k}\} = \{ d_{1,0}, d_{1,1}, ..., d_{1,2^{n/2}}, ..., d_{n, 0} \}
\end{equation}

This collection of details ${d_{j,k}}$ are called Discrete Haar Wavelet Transform. Using the \textit{details} we can calculate the energy function $E_{j}$, for each scale $j$, using:

\begin{equation}
E_{j} = \frac{1}{N_{j}} \sum_{k = 0}^{N_{j} - 1} |d_{j,k}|^{2}; \qquad j = 1, 2, ..., n
\end{equation} 
\\ 
were $N_{j}$ is the number of coefficients at scale $j$. If we plot $\log(E_{j})$ as a function o the scale $j$, we will obtain an wavelet multiresolution energy plot.

On energy wavelet multiresolution energy plots, we can capture three main different behavior, according to the scale.  On \textbf{periodic time series}, the Energy values will be small. In fact, on perfectly periodic scales $j$, the values of the energy function $E_{j}$ will be zero. So periodicity will be sensed if the value of the energy function decrease. Perfect \textbf{white noise time series} will maintain the same value of the energy function. So an approximately constant values for the energy function $E_{j}$ indicates white noise behavior (wich can be represented by a Poisson process\cite{poisson-white-noise}). On \textbf{self-similar time series}, the energy function plot $\log(E_{j})$ will grow approximately linearly with the scale $j$.

Some recent works suggest the use of multi-fractal models, instead of the self-similar models (also called monofractal)\cite{validate-trafficgen}\cite{udp-flows-model}. Since there is a lack  on multiscaling analysis on the literature on validation of traffic generators, this approach will not be used in this work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{QoS/QoE Related Metrics}

For the point of view of a traffic generation, is interesting that the QoS and QoE metrics present similar values to the ones found on real scenarios. As stated by Magyesi and Szabó\cite{validate-trafficgen}, important QoS/QoE metrics on validation of workload tools are: Round trip Time values (RTT), avarage queue whaiting time and queue size. Still on queue size, self-similar traffic consumes router buffers faster than Poisson traffic\cite{multi-player-online-game-self-similarity}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Study cases}

\subsubsection{Swing}
Swing\cite{swing-paper} is at the present time, one of the main references of realistic traffic generation.  The authors extracted bidirectional metrics from a network link of synthetic traces. Their goals were to get  realism, responsiveness, and randomness.  They define realism as a trace that reflects the following characteristics of the original:

\begin{itemize}
\item Packet inter-arrival rate and burstiness across many time scales;
\item Packet size distributions;
\item Flow characteristics as arrival rate and length distributions;
\item Destination IPs and port distributions.
\end{itemize}

The traffic generator uses a structural model the account interactions between many layers of the network stack. Each layer has many control variables, which is randomly generated by a stochastic process.  They begin the parameterization, classifying tcpdump\cite{web-libpcap} \textit{pcap}  files with the data, they are able to estimate parameters.

They validate the results using public available traffic traces, from Mawi\cite{web-mawi} and CAIDA\cite{web-caida}. On the paper, the author focuses on these validation metrics:

\begin{itemize}
\item Comparison of estimated parameters of the original and swing  generated traces;
\item Comparison of aggregate and per-application bandwidth and packets per seconds ;
\item QoS metrics such as two-way delay and loss rates;
\item Scaling analysis, via Energy multiresolution energy analysis.
\end{itemize}

To the vast majority of the results, both original and swing traces results were close from each other. Thus,  Swing was able to match aggregate and burstiness metrics, per byte and per packet, across many time scales.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Harpoon}

Harpoon\cite{harpoon-validation}\cite{harpoon-paper} is a traffic generator able to generate representative traffic at IP \textit{flow level}. It is able to generate TCP and IP with the same byte, packet, temporal and spatial characteristics measured at routers. Also, Harpoon is a self-configurable tool, since it automatically extracts parameters from network traces. It estimates some parameters from original traffic trace: file sizes, inter-connection times, source and destination IP addresses, and the number of active sessions.

As proof of concept \cite{ harpoon-validation}, the authors compared statistics from original and harpoon's generated traces. The two main types of comparisons: diurnal throughput, and for stochastic variable CDF and frequency distributions. Diurnal throughput refers to the mean bandwidth variation within a day period.  In a usual network, during the day the bandwidth consumption is larger, and at night smaller. Also, they compared:

\begin{itemize}
\item CDF of bytes transferred per 10 minutes
\item CDF of packets transferred per 10 minutes
\item CDF of inter-connection time
\item CDF of file size
\item CDF of flow arrivals per 1 hour
\item Destination IP address frequency
\end{itemize}

At the end, they showed the differences on throughput evaluation of a Cisco 6509 switch/router using Harpoon and a constant rate traffic generator.  
Harpoon was proven able to give close CDFs, frequency and diurnal throughput plots compared to the original traces. Also, the results demonstrated that Harpoon provide a more variable load on routers, compared to a constant rate traffic. It indicates the importance of using realistic traffic traces on the evaluation of equipment and technologies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{D-ITG}

D-ITG\cite{ditg-paper} is a network traffic generator, with many configurable features. The tool provides a platform that meets many emerging requirements for a realistic traffic generation. For example, multi-platform, support of many protocols, distributed operation, sending/receiving flow scalability, generation models, and analytical model based generation high bit/packet rate. You can see different analytical and models and protocols supported by D-ITG at table ~\ref{tab:trafficgen-list1}.

We will focus on the evaluation of realism on analytical model parameterization.  It is a synthetic replication of a LAN party of eight players of Age of Mythology \footnote{\href{https://www.ageofempires.com/games/aom/}{https://www.ageofempires.com/games/aom/}}. They have captured traffic flows during the party. Then, they modeled its packet size and inter-packet time distributions. They show that the synthetic traffic and the analytical model have similar curves of packet size and inter-packet time, thus it can approximate the empirical data. Also, the mean and the standard deviation of the bit rate of the empirical and synthetic data are similar.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{sourcesOnOff}

Varet et al. \cite{sourcesonoff-paper} creates an application implemented in C, called SourcesOnOff. It models the activity interval of packet trains using probabilistic distributions. To choose the best stochastic models, the authors have captured traffic traces using TCPdump. Then the developed tool is able to figure out what distribution(Weibull, Pareto, Exponential, Gaussian, etc) fits better the original traffic traces. It uses the Bayesian Information Criterion (BIC) for distance assessment. It tests the smaller BIC for each distribution, and selects it as the best choice. It ensures good correlation between the original and generated traces and self-similarity.

The validation methods used on sourcesOnOff are: 
\begin{itemize}
\item Visual comparison between On time and Off time of the original trace and the stochastic fitting;
\item QQplots\footnote{
QQplot is a visual method to compare sample data with a specific stochastic distribution. It orders the sample data values from the smallest to largest, then plots it against the expected value given by the probability distribution function. The data sample values appear along the y-axis and the expected values along the x-axis. The more linear, the more the data is likely to be expressed by this specific stochastic distribution.
}, which aim to evaluate the correlation between inter-trains duration of real and generated traffic;
\item Measurement of Autocorrelation\footnote{
The autocorrelation functions measures the correlation between data samples $y_{t}$ and $y_{t + k}$, where $k =0, ..., K$, and the data sample $\{y\}$  is generated by an stochastic process.

According to \cite{book-time-series-analysis}, the autocorrelation for a lag $k$ is:

\begin{equation}
r_{k} = \frac{c_{k}}{c_{0}}
\end{equation}

where

\begin{equation}
c_{k} = \frac{1}{T - 1}\sum_{t = 1}^{T - k} (y_{t} - \bar{y})(y_{t+k} - \bar{y})
\end{equation}

and $c_{0}$ is the sample variance of the time series. 
} of the measured throughput of the real and synthetic traffic;
\item Hurst exponent computation of the real and the synthetic trace;
\end{itemize}

The results pointed to a good stochastic fitting, but better for On time values. On the other hand, the correlation value of the QQplot was bigger on the Off time values (99.8\% versus 97.9\%). In the real and synthetic traces, the autocorrelation of the throughput remained between an upper limit of 5\%. Finally, the ratio between the evaluated Hurst exponent always remained smaller than 12\%.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{MoonGen}

MoonGen\cite{moongen-paper} is a high-speed scriptable paper capable of sature  10 GnE link with 64 bytes packets, using a single CPU core. The authors have built it over DPDK and LuaJit, enabling the user to have high flexibility on the crafting of each packet, through Lua scripts. It has multi-core support and runs on commodity server hardware. It is able to test latency with sub-microsecond precision and accuracy, using hardware timestamping of modern NICs cards. The Lua scripting API enable the implementation and high customization along with high-speed. This includes the controlling of packet sizes and control of inter-departure times.

The authors evaluated this traffic generator focused on throughput metrics, rather than others. Also, they have small packet sizes (64 bytes to 256), since the per-packet costs dominate. In their work, they were able to surpass 15 Gbit/s with an XL710 40 GbE NIC. Also, they achieve throughput values close to the line rate with packets of 128 bytes, and 2 CPU cores.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LegoTG}

Bartlett et al.\cite{legotg-paper} implements a modular framework for composing custom traffic generation, called LegoTG. As argued by the authors (and by this present work), automation of many aspects of traffic generation is a desirable feature. The process of how to generate a proper background traffic may become a research by itself. Traffic generators available today offer a single model and a restricted set of features into a single code base, makes customization difficult.

The main purpose of their experiment is to show how LegoTG is able to generate background traffic, in a simple way. Also, it shows how a realistic background traffic can influence on research conclusions. The experiment chosen is one of the use cases proposed for Swing\cite{background-traffic-matter}, and its evaluate the error on bandwidth estimation of different measurement tools. It shows that LegoTG is able eble to provide easy and custrom traffic generation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{An short overview of some Network emerging scenarios}

%\textcolor{red}{TODO}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{SDN: Software Defined Networks}

%\textcolor{red}{TODO}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{NFV: Network Function Virtualization}

%\textcolor{red}{TODO}

%For NFV instrumentation and benchmark, there are still few works aiming this gap. \cite{instrumentation-framework-nfv} create a web-based framework for NFV instrumentation in bare-metal and embedded level, but the source code is not provided. \cite{nfv-benchmarking-fault} implement some usage cases of NFVIs (Network Function Virtualization Infrastructures) based on fault injection. \cite{nfpa-paper} implement an open-source tool, called NFPA, focusing on benchmarking of Network Functions.

### 2017-06-06 Docs/Thesis/docs/chapter3.tex
New testes scripts in Python and Bash to calc the costFunction of the prototype. Also, at the folder Docs, the thesis text was added, i'm editing it using texstudio.

\chapter{System architecture and Methods}\label{ch:architecture}

%2nd-review
In this chapter, we will present developed tool, called SIMITAR: SnIffing, ModellIng and TrAffic geneRation, and how it works. First, we will discuss its architecture and components. Then we will present a brief tutorial of how to expand its support for a traffic generator engine.

%2nd-review
We abstract its whole operation cycle in the figure ~\ref{fig:cycle-of-operation}. Our tool, from live captures or \textit{pcap} file collects raw data from Ethernet traffic. It then breaks these data into different flows. It uses this data to generate a set of parameters for our traffic models, using a set of algorithms. Finally, it provides these parameters to a traffic generator engine and controls its packets injection.

% cycle of operation
%2nd-review
\begin{figure*}[ht!]
        \centering
        \includegraphics[height=3.0in]{figures/ch3/digram-project-cycle}
        \caption{This figure represents an operation cycle of SIMITAR, emphasizing each main step: sniffing, flow classification, data storing, data processing and fitting, model parameterization,  and synthetic traffic generation.}
    \label{fig:cycle-of-operation}
\end{figure*}

\section{SIMITAR Architecture}

%2nd-review
To meet the requirements presented in the section ~\ref{ch:introduction}, we will present a solution, and define how each part works, as in a low-level requirement list\cite{sommerville}.

%2nd-review
SIMITAR architecture is presented in the figure~\ref{fig:architecture}, and it is composed of five components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator} and the \textit{Network Traffic Generator}, as subsystem. We describe each part below.

% component diagram and module design
\begin{figure*}[ht!]
        \centering
        \includegraphics[height=2.7in]{figures/ch3/architecture-diagram}
        \caption{Architecture of SIMITAR}
    \label{fig:architecture}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sniffer}

%2nd-review
This component collects network traffic data and classifies it into flows, storing stores in an SQLite database. It defines each flow by the same criteria used by SDN switches\cite{sdn-survey}, through header fields matches (Link Protocol, Network Protocol, Network Source Address, Network Destination Address, Transport Protocol, Transport Source Port, Transport Destination Port). It can work over a \textit{pcap} file or over an Ethernet interface.

\begin{figure*}[ht!]
        \centering
        \includegraphics[height=2.5in]{figures/ch3/sniffer-classifier}
        \caption{SIMITAR's sniffer hash-based flow classification}
    \label{fig:sniffer}
\end{figure*}

%2nd-review
The first version of this component was implemented in Shell Script (Bash).  Tsahrk\footnote{\href{https://www.wireshark.org/docs/man-pages/tshark.html}{https://www.wireshark.org/docs/man-pages/tshark.html}} was used to extract header fields, and Awk to match the flows, and Sed/Awk to create the Sqlite queries. This version was too slow to operate in real time on Ethernet interfaces. On the other hand, was fast to implement, and enable the implementation of the other components, before this final version was released.

%2nd-review
The second version was implemented using Python. This version used Pyshark\footnote{\href{https://pypi.python.org/pypi/pyshark}{https://pypi.python.org/pypi/pyshark}} as sniffer library. The flow classification is made by a class called FlowId. It contains class we developed called OrderedSet. A set is a list of elements with no repetition, but do not keep track of the insertion order. But our OrderedSet does. Also, it make use of a  32 bits hash function of the family FNV. The listed header fields are inputs for a hash function, its value is set on the ordered set, and its order is returned. This value is set as a packet flowID.

%c++ http://ideone.com/F0V42m
%2nd-review
As future improvements for this component, we propose a more efficient implementation in C++ and data visualization for the collected data. We discuss this in deeper details in the chapter~\ref{ch:conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SQLite database}

\begin{figure*}[ht!]
        \centering
        \includegraphics[height=2.5in]{figures/ch3/database-relational-model}
        \caption{SIMITAR's SQLite database relational model}
    \label{fig:simitar-database}
\end{figure*}

%2nd-review
The database will store the collected raw data for further analysis. It is responsible for storing data from different traces in different tables.  The \textit{Sniffer} and the \textit{TraceAnalyzer}  can access the database.

%2nd-review
We choose an SQLite database, because according to the SQLite specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it is the best option for our database. It is simple and well-suitable for an amount of data smaller than terabytes.

%2nd-review
In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from the packets, along with the FlowID calculated by the sniffer component.

\subsection{Trace Analyzer}

%2nd-review
This module is the core of our project. It creates a compact trace descriptor via the analysis of the collected data. We define here a Compact Trace Descriptor (CTD) as a human and machine readable file, which describes an original traffic trace trough a set of flows, each of them described by a set of parameters, like header information and analytical models.

%2nd-review
Therefore, the Trace Analyze learns the features from raw data of traces (stored in the SQLite database) and write them in an XML file.  In the figure~\ref{fig:CTD-diagram} we show a directory diagram of a CDT file. It has many of many flow fields, and each one contains each parameter estimated.

%\begin{figure*}[!ht]
%    \centering
%    \begin{subfigure}[t]{0.45\textwidth}
%        \centering
%        \includegraphics[height=2.5in]{figures/03_compact_trace_descriptor_tree_structure}
%        \caption{caption}
%    \end{subfigure}%
%    ~ 
%    \begin{subfigure}[t]{0.45\textwidth}
%        \centering
%        \includegraphics[height=2.5in]{figures/03_compact_trace_descriptor_tree_structure_2}
%        \caption{caption}
%    \end{subfigure}
%    \caption{caption}
%    \label{fig:CTD-diagram}
%\end{figure*}
%height=2.5in
%

%2nd-review
\begin{figure}
\centering
\subfloat[first]{
  \includegraphics[height=4.in]{figures/ch3/cdt1}
}
\subfloat[second]{
  \includegraphics[height=4.in]{figures/ch3/cdt2}
}
\caption{Directory diagram of the schema of a Compact Trace Descriptor (CDT) file. On the left, we present a dissected flow, and on the right a set of flows.}
\label{fig:CTD-diagram}
\end{figure}

\subsubsection{Flow features}

%2nd-review
Some features are unique per flow and can be directly measured from the data. They are:

%2nd-review
\begin{itemize}
\item Flow-level properties like duration of flow, start delay, number of packets per flow, number of KBytes per flow;
\item Packet-level QoS metrics like bit rate and packet rate; 
\item Header fields, like protocols (IPv4, IPv6, TCP, UDP, ICMP, DCCP, SCTP, etc), QoS fields, ports, and addresses.
\end{itemize}

%2nd-review
Each one of these parameters is unique per flow. Other features like PSD (packet size distribution) e IPT (Inter-packet time), have a more complex behavior.  To represent these characteristics, we will use sets of stochastic-based models.

\subsubsection{Inter Packet Times}

\begin{figure*}[ht!]
    \centering
    \includegraphics[height=2.0in]{figures/ch3/modified-harpoon-model}
    \caption{The schema of the modified version of the Harpoon algorithm we adopt on SCIMITAR.}
    \label{fig:modified-harpoon-model}
\end{figure*}

%2nd-review
To represent IPT, we adopt a simplified version of the Harpoon traffic model. A deep explanation of the original model can be found at \cite{harpoon-paper} and \cite{harpoon-validation}. Here, we will explain our simplified version, which is illustrated at figure~\ref{fig:modified-harpoon-model}.

%2nd-review
Harpoon uses a more conventional definition of each level, based on the measurement of SYN and ACK TCP flags. Harpoons use TCP flags (SYN) to classify packets in different levels (named there: file, session and user level). Since we are just modeling inter-packet times, we choose to estimate these values, based on inter-packet times. Since we want to generalize this approach for any protocol, the distinction will be made based on the time delay between packets.

%2nd-review
In our version of the algorithm, we define (as Harpoon does) three different layers of data transference to model and control: file, session, and flow.

%2nd-review
For SIMITAR, a file is just a sequence of consecutive packets transmitted continuously, without large interruption of traffic. It can be, for example, packets transmitted downloading a file, of UDP packets of a connection or a single ICMP echo packet. The session-layer refers to a sequence of multiple files transmitted between a source and a destination, belonging to the same flow.  And the flow level refers to the conjunct of flow classified by the Sniffer.

%2nd-review
\textbf{Flow-layer}: The Trace Analyzer loads the flow arrival times from the database, and calculates the inter-packet times within the flow context.

%2nd-review
\textbf{Session-layer}: At the session layer, we use a deterministic approach for evaluating times between transferred files (OFF times) and the actual file transference (ON times). It is basically a deterministic ON/OFF model. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.  \textcolor{red}{<<<<pode mudar, calibrar>>>>} We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the on times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. We did this, first because ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators. Second, because in the case of just one packet, the ON time would be zero. OFF times, on the other hand, are defined by the constant \texttt{m\_session\_cut\_time}. If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds).
The control of ON/OFF periods is made by the \texttt{NetworkFlow} class.

%2nd-review
\textbf{File-layer}: Here we model the inter-packet times at the file level. To estimate inter-packet times within files, we select all inter-packet times smaller than \texttt{m\_session\_cut\_time}. All files within the same flow are considered to follow the same model. We delegate the control of the inter-packet times to the underlying workload engine tool. We ordered them, from the best to the worst. Currently, we are using eight different stochastic functions parameterizations. They are Weibull(linear regression), Normal(mean/standard deviation calculation), Exponential(mean and linear regression estimation), Pareto(linear regression and maximum likelihood), Cauchy(linear regression) and Constant(mean calculation). From those, Weibull, Pareto, and Cauchy are heavy-tailed functions, and therefore self-similar processes. \textcolor{red}{<<<<pode mudar, calibrar>>>>} But if the flow has less than 30 packets, just the constant model is evaluated. It is because numerical methods gave poor results if the data sample used is small. We sort these models according to the Akaike Information Criterion (AIC)\cite{sourcesonoff-paper}\cite{bic-aic-comparision}. We will enter in deeper details on this methodology on the chapter ~\ref{ch:modeling-evaluation}. The methodology of selection is presented in the figure~\ref{fig:model-parameterization}

%2nd-review
\begin{figure*}[ht!]
    \centering
    \includegraphics[height=1.6in]{figures/ch3/ipt-modeling}
    \caption{Diagram of parameterization and model selection for inter-packet times and inter-file times.}
    \label{fig:model-parameterization}
\end{figure*}

%\begin{figure*}[ht!]
%    \centering
%    \includegraphics[height=4.0in]{figures/ch3/alg-paremeterization}
%    \caption{caption.}
%    \label{fig:harpoon-alg-times-estimator}
%\end{figure*}

\subsubsection{Packet Sizes}

%2nd-review
Our approach for the packet size is much simpler. Since the majority of packet size distribution found on real measurements are bi-modal \cite{packet-distribution-model}\cite{sourcesonoff-paper}\cite{udp-flows-model}, we first sort all packet sizes of flow in two modes. We define a packet size mode cut value of 750 bytes, same value adopted by \cite{udp-flows-model}.

%2nd-review
We first know how much packets each mode has, and then we fit a model for it. We use three stochastic models: constant, exponential and normal. Since self-similarity is not a requirement, we prefer to use just simple models. But, when there is no packet we set a flag NO\_MODEL, and when there is just a single packet we just use the constant model.  We then calculate the BIC and AIC for each of them and sort according to the AIC value by default, but we decide to set the constant model as the first.

%2nd-review
As is possible to see on many studies \cite{packet-distribution-model}\cite{udp-flows-model}, since the standard deviation of each mode is small, constant fittings use to give good approximations. Also, it is computationally cheaper than the others models, since no calculation is a need for each packet sent. Since both AIC and BIC criteria always will select the constant model as the worst, we decide to ignore this indicator for the constant model.

\subsubsection{Compact Trace Descriptor}

%2nd-review
An example of the final result of all the methods is presented in the XML code down below. It illustrates a flow of a \textit{Compact Trace Descriptor}(CDT) file.

\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{xml}
<flow start_delay="31.621941" duration="91.584654" ds_byte="0" n_kbytes="1" n_packets="13">
	<link_layer mac_src="no-mac-src" mac_dst="no-mac-dst">ETHERNET</link_layer>
	<network_layer src_ip="10.1.1.48" dst_ip="216.58.199.35" ttl="64">IPV4</network_layer>
	<transport_layer dst_port="34683" src_port="443">TCP</transport_layer>
	<application_layer>HTTPS</application_layer>
	<inter_packet_times>
		<stochastic_model name="pareto-ml" aic="-24.738412" bic="-23.768599" param1="0.152500524612205" param2="0.000024050000003"/>
		<stochastic_model name="weibull" aic="-16.155977" bic="-15.186164" param1="0.130469107098031" param2="0.063433369086366"/>
		<stochastic_model name="pareto-lr" aic="49.322192" bic="50.292005" param1="0.892551148108768" param2="0.000024050000003"/>
		<stochastic_model name="exponential-me" aic="76.776570" bic="77.746383" param1="0.131026317153354" param2="0.000000000000000"/>
        <stochastic_model name="normal" aic="105.882623" bic="106.852436" param1="7.632054549999999" param2="17.598918053235813"/>
        <stochastic_model name="exponential-lr" aic="116.913056" bic="117.882870" param1="0.009752000000000" param2="0.000000000000000"/>
        <stochastic_model name="cauchy" aic="128.406532" bic="129.376345" param1="1.935832000000000" param2="-7.245692000000000"/>
        <stochastic_model name="constant" aic="inf" bic="inf" param1="7.632054549999999" param2="0.000000000000000"/>
    </inter_packet_times>
	<session_times on_times="0.96856400,0.10000000,0.10000000" off_times="45.30807900,45.30801100" n_packets="11,1,1" n_bytes="1650,66,66"/>
	<packet_sizes n_packets="13" n_kbytes="1">
		<ps_mode1 n_packets="12" n_kbytes="1">
			<stochastic_model name="constant" aic="inf" bic="inf" param1="99.916667" param2="0.000000"/>
			<stochastic_model name="normal" aic="137.020397" bic="137.990210" param1="99.916667" param2="64.408439"/>
			<stochastic_model name="exponential-me" aic="138.504076" bic="139.473889" param1="0.010008" param2="0.000000"/>
		</ps_mode1>
		<ps_mode2 n_packets="1" n_kbytes="0">
		<stochastic_model name="constant" aic="inf" bic="inf" param1="583.000000" param2="0.000000"/>
		</ps_mode2>
	</packet_sizes>
</flow>
\end{minted}

%2nd-review
The current version of our tool, do not intrinsically supports responsiveness. The underlying traffic generator API can support it (such as Seagull\cite{web-seagull}), but we do not generate any mathematical model for this purpose, and this may also stand as a future work we discuss on chapter ~\ref{ch:conclusion}.

\subsection{Flow Generator}

\begin{figure*}[ht!]
    \centering
    \includegraphics[height=4.0in]{figures/ch3/alg-simplified-harpoon}
    \caption{Simplified-harpoon emission algorithm}
    \label{fig:alg-simplified-harpoon}
\end{figure*}

%2nd-review
The Flow Generator handles the data on the CTD file, and use it as parameters for the traffic generation. It crafts and controls each flow in a separated thread.

%2nd-review
We first implemented it using the D-ITG API. But our Flow Generator can use any traffic generator with API, CLI or script interface as well. To easily expand this component, we use the design pattern factory. If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow} and add the support on the method \texttt{make\_flow()} of the class \texttt{NetworkFlow}. We will discuss this deeper in the next section.

%2nd-review
This component works in two different layers according to the traffic generators classification introduced in the chapter ~\ref{ch:literature-review}: at the Flow level, and packet level, as presented in the figure ~\ref{fig:layers-workload-tools}.

\begin{figure*}[ht!]
    \centering
    \includegraphics[height=4.0in]{figures/ch3/alg-traffic-engine-config}
    \caption{Traffic engine configuration model}
    \label{fig:alg-traffic-engine-config}
\end{figure*}

\subsubsection{Flow-level Traffic Generation Operation}

%2nd-review
At the flow level, it controls each flow using the algorithm at figure~\ref{alg-simplified-harpoon}. This algorithm basically handles the our model defined at the figure~\ref{fig:modified-harpoon-model}.

%2nd-review
It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps its \texttt{start\_delay}. It is the time when the first flow packet was captured in the original capture. it then calls the underlying traffic generation method, passing to it the file ON time, number of packets and number of bytes to be sent (file size). Then it sleeps the next Session-OFF time from the stack until it ends. When the list of ON/OFF times is over, the thread ends. The thread scheduling/joining is implemented by the class \texttt{NetworkTrace} and its sleep/wake process by the class \texttt{DummyFlow}.

\subsubsection{Packet-level Traffic Generation Operation}

%2nd-review
At the packet level, it must use the expanded class of the \texttt{DummyFlow}. In this level, the job of our tool is to configure the underlying engine, to send a file. Therefore it uses the \textit{getters} available, and the passed parameters, defined by the operation described in the previous session. The implementation of this level should follow the flowchart presented in the figure ~\ref{fig:alg-traffic-engine-config}.
Down below we present a simplistic code of how the D-ITG API can be used to generate packet-level traffic using our framework. A more complex configuration is possible, but it serves to illustrate the procedure. Its API documentation is available at on D-ITG web-site \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}. 
\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{c++}
void flowGenerate(const counter& flowId, const time_sec& onTime, const uint& npackets, const uint& nbytes,  const string& netInterface)
{
	char localhost[CHAR_BUFFER];
	string strCommand;
	char command[CHAR_BUFFER];
	uint i = 0;
	int rc = 0;
	getLocalIp("eth0", localhost);
	strCommand += " -t " + std::to_string(onTime); 
	strCommand += " -k " + std::to_string(nbytes / 1024);
	strCommand += " -a " + getHostIP();
	if (this->getTransportProtocol() == PROTOCOL__TCP)
		strCommand += " -T TCP -D ";
	else if (this->getTransportProtocol() == PROTOCOL__UDP)
		strCommand += " -T UDP ";
	else if (this->getTransportProtocol() == PROTOCOL__ICMP)
		strCommand += " -T ICMP ";
	for(;;i++)
	{	
		StochasticModelFit idtModel = this->getInterDepertureTimeModel(i);
		if(idtModel.modelName() == WEIBULL)
		{
			strCommand += " -W " + std::to_string(idtModel.param1()) + " " + std::to_string(idtModel.param2());
			break;
		}
		else if ( idtModel.modelName() == CONSTANT)
		{
			strCommand += " -C " + std::to_string(nbytes/(1024*onTime));
			break;
		}
	}
	strcpy(command, strCommand.c_str());
	rc = DITGsend(localhost, command); // it is not blocking
    usleep(onTime*10e6);
	if (rc != 0)
	{
		printf("\nDITGsend() return value was %d\n", rc);
		exit(EXIT_FAILURE);
	}
}
\end{minted}

\subsection{Network Traffic Generator}

A network traffic generator software that should provide its API or script interface for the \textit{FlowGenerator} component.

Since \texttt{DITGsend()} is thread safe, no mutex is need. It would be needed if a lower level API, such Libtins or Libpcap was used. In that case, these APIs would permit control precisely each packet sent through the interface, but a mutex would be necessary. An scriptable application, such as Iperf can be used as well, using \texttt{fork()} or \texttt{popen()}.

As we claimed before, this tools is simple of being expanded for almost any traffic generation API, since its modeling framework is not coupled to the traffic generation.
The figure \ref{fig:network-trace-flow-class-diagram} illustrates it well. It presents three possibilities of different traffic generation engines, all being configured and scheduled in a platform-agnostic way.

\begin{figure*}[ht!]
    \centering
    \includegraphics[height=3.0in]{figures/ch3/trace-flow}
    \caption{Class hierarchy of NetworkTrace and NetworkFlow, which enables the abstraction of the traffic generation model of the traffic generation engine.}
    \label{fig:network-trace-flow-class-diagram}
\end{figure*}

\section{Usage and Use Cases}

SIMITAR works in four different states: as a sniffer, packet injector, client or server. 
When it working as a sniffer, is produces as output a Compact Trace Descriptor file. It may operate over a \textit{pcap} file or an Ethernet interface.

When it operates as a client or as packet injector, it is operating as a traffic generator. The difference is that as a client, the used traffic generator is connection-oriented. It needs to establish a connection with the destination host (the server), before start sending packets. It takes as an input a single destination in the command line, or list of many, in a text file passes as a parameter. Also, it uses the machine IP address as packet's source IP.

Operating as a client, it must take as an input a list of IP or MAC destination addresses, since they will not match with the ones in the original trace. As a packet injector can generate packets on the output interface, without establishing a connection. It uses the original IP and MAC destination and source addresses. As a client, the reproduction of the trace is expected to be poor in the flow level metrics exposed in the chapter ~\ref{ch:literature-review}, since it will use new addresses values.

The operation of packet injector is still under implementation, and we are using Libtins library. Currently, SIMITAR supports client mode with D-ITG, implemented using its C++ API. We intend to provide support for many others traffic generators, such Iperf and Ostinato.

When operating as a server, it just start-up the traffic generator server, and waits for server connections. Down bellow, we present simple examples of commands used to activate each operation mode.

\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{bash}
# Operation as a sniffer over a Ethernet interface named <ether-interface> 
./simitar --sniffer -if <ether-interface> --out/-o <cdt-name>
# Operation as a client using the traffic generator D-ITG, using a list of destination hosts of a text file
./simitar --client ditg --in <cdt-xml-name> --dst-list-ip <ip-list-file> 
# Operation as a packet injector with uses the Libtins library to craft packets
./simitar --pkt-injection libtins --in <cdt-xml-name> 
# Operation as a server. just runs D-ITG in the server mode.
./simitar --server/-sv ditg

\end{minted}

As use cases, we can cite:

\begin{itemize}

\item Generate Background traffic with D-ITG: SIMITAR can work to generate background traffic over a network when it receives many addresses as input. If each destination is reachable, D-ITG will establish a connection with each destination, and recreate flows as described in the CDT file.

\item Stress a Device Under Test (DUT): It can be used to stress a single device with a more self-similar realistic traffic. The CDT file can be manually modified to change some aspects of the traffic, such as the number os packets or throughput applied by the traffic generator of each flow. Some undesirable features such as Stochastic models or lesser flow may be taken out, SIMITAR does not have constraints on a number of flows and Stochastic models adopted (but must have at least one).

\item Generate synthetic \textit{pcap} files: Using virtual interfaces, we can reproduce a traffic, and capture it with a sniffer tool, such as Tcpdump, Wireshark or Tshark. We plan to automatize this process as a future work, with an operation mode of \textit{pcap} generator. To do this we are going to use Mininet to create the virtual interfaces and Libtins to inject packets.

\end{itemize}

### 2017-06-06 Docs/Thesis/docs/chapter4.tex
New testes scripts in Python and Bash to calc the costFunction of the prototype. Also, at the folder Docs, the thesis text was added, i'm editing it using texstudio.

\chapter{Modeling and Algorithms}\label{ch:modeling-evaluation}

\section{Introduction}

As discussed before, there is many works devoted on studding the nature of the Ethernet traffic \cite{selfsimilar-ethernet}. Classic Ethernet models used Poisson related process to express generation of traffic. In a first look it makes sense,  sense, since a Poisson process represents the probability of events occur with a known average rate, and independently of the time since the last event\cite{selfsimilar-ethernet} \cite{book-poisson}. But studies made by Leland et al.\cite{selfsimilar-ethernet} showed that the Ethernet traffic has a self-similar and fractal nature. Even if they are able to represent the randomness of an Ethernet traffic, simple Poisson processes can't express the presence of "burstiness" in a long-term time scale, such as traffic "spikes" on long-range "ripples".  This is an indicative of the fractal and self-similar nature of the traffic.

Stochastic process that respects this characteristic have infinite variance, said to be heavy-tailed. Heavy-tail means that a stochastic distribution is not exponentially bounded\cite{sourcesonoff-paper}. Examples of heavy-tailed functions are Weibull, Pareto, Cauchy. But not many works on the literature deal with a process for parameterization of different stochastic models for Ethernet traffic. Also, a heavy-tailed function may guarantee self-similarity, but not necessarily they would guarantee other features like good correlation and same mean packet rate and dispersion.

In this chapter we proposed an unified and simple method for modeling inter packet times, and choose the best fit automatically, without having to generate random data. We estimate many stochastic functions through many methodologies, and select the best model through the AIC computation. Since generating random can be computationally cost an have a bias, depending of the seed generator, an analytical method for selecting the best fitting eliminate these problems.

We made a brief bibliographic review on some works related works. Then, we will present the traffic traces we are going to use in this chapter, and in the rest of the work. After we present or selected methodology for parameterization selection of the best fitting. To evaluate the quality of this selection criteria, we define a methodology for evaluate if our model selection is good or not.

\section{Related Works}

There are plenty of works on the literature which proposes new processes and methodologies foe generation on inter-packet times.

Fiorini \cite{modeling-concurrent-heavy-tailed} presents a heavy-tailed ON/OFF model, which tries to represent a traffic generated by many sources. The model emulates a multiple source power-tail Markov-Modulated (PT-MMPP) ON/OFF process, where the ON times are power-tail distributed. They achieve analytical performance measurements using Linear Algebra Queueing Theory.

Kreban and Clearwater\cite{hierarchical-dynamics-interarrival-times} presents a model for times between job submissions of multiple users on a super computer. They show in their job that the Weibull probability functions is able to express well small and high values of inter-job submission times. They also tested exponential, lognormal and Pareto(called there power law) distributions. Exponential distribution couldn't  represent long-range values because it fell off too fast and Pareto was too slow. Lognormal fit well small values, but was poor on larger ones.

Kronewitter\cite{optimal-scheduling-of-heavy-tailed-traffic} presents a models of scheduler of heavy-tailed traffic of multiple sources. On his work, he uses multiple Pareto sources to represent the traffic. To estimate the shape parameter $\alpha$ they use linear regression.

\section{Methodology}

We will start defining the datasets we are going to use in this evaluation, and in the rest of this work as well. We define our criteria of parameterization and model selection, and a methodology for measure the quality of our choices.

%In this chapter we will evaluate our proposed method for data modeling of inter-packet times.  We will present curves obtained by our prototype (implemented in Gnu Octave\footnote{\href{https://www.gnu.org/software/octave/}{https://www.gnu.org/software/octave/}}) that shows in detail how each step works. After explaining this process, we will present an evaluation method of our results, analyzing to analyze its quality. After this, we give some details of how we convert code from Octave to C++ and its benefits on time execution. All code used in this section is available on our GitHub page.%, on the directory \texttt{Prototypes}.

\subsection{Datasets}

We start defining also define the \textit{pcaps} datasets we are going to use in the rest of this text. We will use for datasets, and for reproduction purposes, three are public available. 
The first is a light weight Skype capture, found at Wireshark wiki\footnote{https://wiki.wireshark.org/}, and can be found at \href{https://wiki.wireshark.org/SampleCaptures}{https://wiki.wireshark.org/SampleCaptures}. The file name is \texttt{SkypeIRC.cap}.

The second is a CAIDA\footnote{http://www.caida.org/home/}{http://www.caida.org/home/} capture, and can be found at  \href{https://data.caida.org/datasets/passive-2016/equinix-chicago/20160121-130000.UTC}{https://data.caida.org/datasets/passive-2016/equinix-chicago/20160121-130000.UTC}. Access to this file need login, so you will have to create an account and wait for approval first. The pcap's file name is \texttt{equinix-chicago.dirB.20160121-135641.UTC.anon.pcap.gz}.

The third we capture in our laboratory LAN, through a period of 24 hours. It was captured in the firewall gateway between our local and external network. Along with other tests, We intend to verify diurnal behavior on it. That means, a high demand of packets during the day, an a small in the night. The fourth is a capture of a busy private network's access point to the Internet, available on-line on TCPreplay\cite{web-tcpreplay} website \footnote{ http://tcpreplay.appneta.com/wiki/captures.html}, and is called \texttt{bigFlows.pcap}. We will refer to these \textit{pcaps} as \textit{skype-pcap}, \textit{wan-pcap}, \textit{lan-diurnal-pcap}, and \textit{bigflows-pcap} respectivaly. Along with these datasets, we will use two subpcaps from the originals. The first, \textit{skype-flowburst-pcap}, is a burst of a single HTTP flow from \textit{skype-pcap}. It can be obtained from Wireshark using the filter \texttt{(ip.src\_host==172.16.133.25) \&\& (ip.dst\_host==74.125.170.42) \&\& (tcp.dstport==80) \&\& (tcp.srcport==63378) \&\& (frame.time\_relative>30.0) \&\&( frame.time\_relative<50.0)}. The second, \textit{caida1s-pcap} is a trace with the first second from \texttt{wan-pcap}.

\subsection{Modelling Inter-Packet times and Packet Sizes: Proposed Process}

We summarize our process of modeling inter packet times at the figure~\ref{fig:model-parameterization}. We collect a set of inter-packet times from a actual traffic capture. Then, we estimate a set of parameters for stochastic functions, using different methodologies. Then, from these parametrized models, we estimate which best represent our data set, using the measure of quality AIC (Akaike information criterion). We also calculate another measure of quality called BIC(Bayesian information criterion), for comparison of results. In this chapter, we present our results obtained on our prototype implemented  in Octave.

Currently we are modeling:

\begin{itemize}
\item Weibull distribution, using linear regression, through the Gradient descendant algorithm;
\item Normal distribution, using direct estimation the mean and the standard deviation of the dataset;
\item Exponential distribution, using linear regression, through the Gradient descendant algorithm. We refer to this distribution as Exponential(LR);
\item Exponential distribution, using direct estimation of the dataset mean. We refer to this distribution as Exponential(Me);
\item Pareto distribution, using linear regression, through the Gradient descendant algorithm. We refer to this distribution as Pareto(LR);
\item Pareto distribution, using the maximum likelihood method. We refer to this distribution as Pareto(MLH);
\item Cauchy distribution, using linear regression, through the Gradient descendant algorithm;
\end{itemize}

%\textcolor{red}{TODO: Explciar quais dados são armazenados na base de dados e por que. Explicar como os dados são classificados, e modelados, e os parametros gerados. Citar métodos utilizado para parametrização, como calculo da média, maximmum likelihood e regressão linear. Apredentar o diagrama da ultima apresentação. Apresentar as equações utilizadas. Com esses dados bem como os plots dos dados linearizados, da corvergencia do custo e o fitting da CDF. Apresentar uma tabela com o valor do BIC e AIC para cada fitting. (Vai ficar muito grande a sessão)}

% In probability theory and statistics, the exponential distribution (a.k.a. negative exponential distribution) is the probability distribution that describes the time between events in a Poisson process, i.e. a process in which events occur continuously and independently at a constant average rate. It is a particular case of the gamma distribution. It is the continuous analogue of the geometric distribution, and it has the key property of being memoryless. In addition to being used for the analysis of Poisson processes, it is found in various other contexts.

Now we will give a brief explanation our three procedures: Linear Regression (with the  Gradient descendant algorithm), direct estimation, and maximum likelihood. We go deep in details on the explanation of the methods on the appendix ~\ref{ap:revision-probability}, and present the mathematical demonstrations on appendix~\ref{ap:mathematical-modeling}.

Some observations must be made. Since the resolution of the time samples used were of $10^{-6}$s, all values equals to zero were set to  $5\cdot10^{-8}$s, to avoid division by zero. To avoid divergence on tangent operation on the linearization the Cauchy function, the inter packets CDF function values were floor-limited and upper-limited to  $10^{-6}$ and $0.999999$ respectively.

We implemented this prototype using Octave. Its code is located on GitHub, for reproduction purposes\footnote{github-link-aqui}

\subsubsection{Linear regression (Gradient descendant)}

Linear regression is a method for estimating the best linear curve

\begin{equation}
y = ax + b
\end{equation}

to fit a given data set. We can use linear regression to estimate parameters of a non-linear curve expressing it on a linear format. For example, the Weibull CDF for $t > 0$ is:

\begin{equation}
F(t; \alpha, \beta) = F(t) = 1 - e^{-(t/\beta)^{\alpha}}
\end{equation}

manipuling it, we can found:
\begin{equation}
\alpha\ln{(t)} - \alpha\ln{(\beta)} = \ln{-\ln{1 - F(t)}}
\end{equation}

%corrigir erro
If we call $x = \ln{(t)}$ and $y = \ln{(-\ln{(1 - F(t))})}$, we found a linear equation, where $a = \alpha$ and $b = -\alpha\ln{(\beta)}$. Having in hands a estimation of the empirical CDF of our data samples, we apply the $x$ and $y$ definitions to linearize the data. Using the gradient descendant, we are able to find a estimation of the linear coefficients $\hat{a}$ and $\hat{b}$. Using the inverse function of the definition of linear coefficients, we are able to find the estimated parameters $\hat{\alpha}$ and $\hat{\beta}$.

\begin{equation}
\alpha = a
\end{equation}

\begin{equation}
\beta = e^{-(b/a)}
\end{equation}

We present examples of linearized data, and the linear approximation achieved, as well the cost convergence of the gradient descendant algorithm in the appendix ~\ref{ap:mathematical-modeling}.

Applying the inverse equations of the linear coefficients ($\hat{\alpha} = \hat{a}$ and $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$) (the symbol stands for the estimated parameters). So we are able to estimate the Weibull distribution parameters.

We can summarize this procedure, in these steps:
\begin{enumerate}
\item Linearize the stochastic CDF function F(t).
\item Apply the linearized $y = y(F(t))$ and  $x = x(t)$ on the empirical CDF and times datasets, respectively. 
\item Use Gradient Descendant algorithm to find linear coefficients $a$ and $b$.
\item Apply the inverse equation of the linear coefficients, to determine the stochastic function parameters.
\end{enumerate}

In the parameters estimation, there is an exception, since the Pareto scale ($t_{m}$) is defined by the minimum time.

In the table~\ref{tab:linearization-sumary} we present a summary of the used equations in the procedure. In this notation, the subscript $i$ means that it must be applied on every empirical value measured. The hat( $\widehat{}$ ) indicates an estimated value for a parameter.

In the figure~\ref{fig:linearization} we presente the linearized

\begin{table}[h!]
\centering
\caption{My caption}
\label{tab:linearization-sumary}
\begin{tabular}{llllll}
\hline
Function    & Linearized $x$     & Linearized $y$                    & \multicolumn{2}{l}{Parameters}                                                        &  \\
\hline
Cauchy      & $x_i = t_i$        & $y_i = \tan{(\pi(F(t_i) - 1/2))}$ & $\hat{\gamma} = \frac{1}{a}$ & $\hat{\hat{t_0}} = - \frac{b}{a}$                      &  \\
Exponential & $x_i = t_i$        & $y_i = \ln{(1 - F(t_i))})$        & \multicolumn{2}{l}{$\hat{\lambda} = -a$}                                              &  \\
Pareto      & $x_i = \ln{(t_i)}$ & $y_i = \ln{(1 = F(t_i))}$         & $\alpha = -a $         & $\hat{x_{m}} = \min_{i = 0, ..., m}\{x_{i}\}$ &  \\
Weibull     & $x = \ln{(t)}$     & $y = \ln{(-\ln{(1 - F(t))})}$     & $\alpha = a$                 & $\beta = e^{-(b/a)}$                                   & \\
\hline
\end{tabular}
\end{table}

\begin{figure}[ht!]
\centering
\subfloat[c]{
  \includegraphics[height=50mm]{figures/ch4/Skype_Weibull_-_Linearized_data_and_linear_fitting}
  \label{fig:linearization}
}
%\hspace{0mm}
\subfloat[c]{
  \includegraphics[height=50mm]{figures/ch4/Skype_Weibull_-_Cost_J_iterations__convergence}
  \label{fig:cost}
}
\label{fig:linearization-cost}
\end{figure}

\subsubsection{Direct Estimation}

%corrigir error
The expected value $E(X)$ and and variance $Var(X)$ of a random variable $X$ of some distributions are close related with its parameters. Since the mean $\bar{\mu}$ and the standard deviation $\bar{\sigma}$ are in general good approximations for the expected value and variance, we may estimate we may use them to estimate parameters.
%corrigir error
Following the notation presented at table~\ref{tab:distributions-equations}, we have for the normal distribution:
\begin{equation}
(\hat{\mu}, \hat{\sigma} = (\bar{\mu}, \bar{\sigma})
\end{equation}

For the exponential distribution $E(X) = \frac{1}{\lambda}$, therefore:
\begin{equation}
\hat{\lambda} = \frac{1}{\hat{\mu}}
\end{equation}

\subsubsection{Maximum Likelihood}

The maximum likelihood estimation, is a method for estimation of parameters, winch maximizes the likelihood function. We explain in details this subject in the Appendix A. Using this method for the Pareto distribution, it is possible to derive the following equations the its parameters:
\begin{equation}
\hat{x_{m}} = \min_{i = 0, ..., m}\{x_{i}\}
\end{equation}

\begin{equation}
\hat{\alpha} = \frac{n}{ \sum_{i = 0}^{m}(\ln{(x_{i}) - \ln(\hat{x_{m}})})  }
\end{equation}

where $m$ is the sample size.

\subsubsection{AIC and BIC}

Suppose that we have an statistical model $M$ of soma dataset ${\boldsymbol{x} = (x_1, ..., x_n)}$, with $n$ independent and identically distributed observations of a random variable $X$. This model can be expressed by a PDF $f(x, \boldsymbol{\theta})$, where $\boldsymbol{\theta}$ a vector of parameter of the PDF, $\boldsymbol{\theta} \in \mathbb{R}^{k}$ ($k$ is the number of parameters). The  likelihood function  of this model $M$ is given by:

\begin{equation}
L(\boldsymbol{\theta}|\boldsymbol{x} ) =  f(x_1|\boldsymbol{\theta})...f(x_n|\boldsymbol{\theta}) = \prod_{i = 1}^{n}f(x_i|\boldsymbol{\theta})
\end{equation}

Now, suppose we are trying to estimate the best statistical model, from a set ${M_1, ..., M_n}$, each one whit an estimated vector of parameters  ${\boldsymbol{\hat{\theta_1}}}, ..., {\boldsymbol{\hat{\theta_n}}}$. $AIC$ and $BIC$ are defined by:

\begin{equation}
AIC = 2k - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
\end{equation}

\begin{equation}
BIC = k\ln(n) - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
\end{equation}

In both cases, the preferred model $M_i$, is the one with the smaller value of $AIC_i$ or $BIC_i$.

\subsubsection{Validation}

To see if our criterion of parameter selection is actually is able to find which is the best model, we define a validation methodology. 
We generate a vector with the same size form the original, with random generated data through our model estimation. Then we compare it with the original sample, trough four different metrics, all with a confidence interval of 95\%:

\begin{itemize}
\item Correlation between the sample data and the estimated model;
\item Hurst exponent;
\item Mean inter packet time;
\item Standard deviation of inter packet times.
\end{itemize}

The Pearson's product-moment coefficient, or simply correlation coefficient,  is an expression of the dependence or association between two datasets. Its value goes from -1 to +1. +1 means a perfect direct linear correlation. -1 indicates perfect inverse linear correlation. 0 means no linear correlation. So, as close the result reach 1, more similar are the inter packet times to the original values. To estimate it, we use the Octave's function \texttt{corr()}.

As explained before in the chapter~\ref{ch:literature-review}, the Hurst exponent is a measurer of self-similarity, and indicates the fractal level of the inter packet times. As close the result is from the original, more similar is the fractal level of the estimated samples from the original.To estimate this value we use the function \texttt{hurst()} from Octave, which uses rescaled range method.

Finally we measure the mean and the standard deviation (as a measure of the dispersion), using the Octave's functions \texttt{mean()} and \texttt{std()}. We also present some \textit{QQplots}, to visually compare the random-generated data and the actual dataset.

As close the correlation, Hurst exponent, mean and the standard deviation is from the original dataset, the better is model fitting. Also, analyzing the mean, we can see if a certain modeling procedure tend to be more penalized for the values close, or far from zero. That means, if the mean inter-packet time tends to be smaller or higher compared to the original. With these results in hands, we can see if AIC and BIC are actually good criterion on model selection for inter-packet times.

\section{Results}

%%%%%%%%%%%%%%%%%%%%%%%
% Prototype results
\begin{table}[h!]
\centering
\caption{Results of the octave prototype, include BIC and AIC values, para estimated parameters for two of our pcap traces: \textit{skype-pcap }and \textit{bigflows-pcap}. \textit{bigflows-pcap} is much larger, and has a much much smaller mean inter-packet time}
\label{tab:prototype-results1}
\scalebox{0.70}{ 
\begin{tabular}{lllllllll}
\hline
                & \multicolumn{8}{c}{Trace} \\ \cline{2-9} 
Function		& AIC        & BIC        & \multicolumn{2}{c}{Parameters}              & AIC        & BIC        & \multicolumn{2}{c}{Parameters}                \\ \cline{2-9}
        & \multicolumn{4}{c}{skype-pcap}                                        & \multicolumn{4}{c}{bigflows-pcap}                                       \\ \hline 
Cauchy          & $ 21.8\cdot10^3 $  & $21.9\cdot10^3$  & $\gamma:0.000259 $ & $x_0:0.104891 $    & $ 7.2\cdot10^6 $   & $7.2\cdot10^6$   & $ \gamma:1.935833 $ & $x_0:-7.245697 $    \\
Exponential(LR) & $-4.3\cdot10^3$  & $ -4.3\cdot10^3 $  & \multicolumn{2}{l}{$\lambda:1.861121 $}   & $7.3\cdot10^6$   & $7.3\cdot10^6$   & \multicolumn{2}{l}{$ \lambda:0.009752 $}    \\
Exponential(Me) & $-1.6\cdot10^3$  & $-1.6\cdot10^3$  & \multicolumn{2}{l}{$\lambda:7.011624 $}   & $-10.9\cdot10^6$ & $-10.9\cdot10^6$ & \multicolumn{2}{l}{$ \lambda:2638.706529 $} \\
Normal          & $3.3\cdot10^3$   & $3.3\cdot10^3$   & $\mu:0.142620 $    & $\sigma:0.500698 $ & $-9.4\cdot10^6$  & $-9.4\cdot10^6$  & $ \mu:0.000379$     & $ \sigma:0.000660 $ \\
Pareto(LR)      & $-8.3\cdot10^3$  & $-8.3\cdot10^3$  & $\alpha:0.252367 $ & $x_m:0.000000 $    & $-10.3\cdot10^6$  & $-10.3\cdot10^6$  & $ \alpha:0.148862 $ & $ x_m:0.000000 $    \\
Pareto(MLH)     & $-11.6\cdot10^3$ & $-11.6\cdot10^3$ & $\alpha:0.092060 $ & $x_m:0.000000 $    & $-10.3\cdot10^6$  & $-10.3\cdot10^6$  & $ \alpha:0.136193 $ & $ x_m:0.000000 $    \\
Weibull         & $-14.6\cdot10^3$ & $-14.6\cdot10^3$ & $\alpha:0.319808 $ & $\beta:0.015244 $  & $-11.0\cdot10^6$ & $-11.0\cdot10^6$ & $ \alpha:0.281189 $ & $ \beta:0.000554 $  \\ \hline

				& \multicolumn{4}{c}{skype-pcap}                                        & \multicolumn{4}{l}{bigflows-pcap}                                       \\ \hline
Cauchy          & $ 21.8\cdot10^3 $  & $21.9\cdot10^3$  & $\gamma:0.000259 $ & $x_0:0.104891 $    & $ 7.2\cdot10^6 $   & $7.2\cdot10^6$   & $ \gamma:1.935833 $ & $x_0:-7.245697 $    \\
Exponential(LR) & $-4.3\cdot10^3$  & $ -4.3\cdot10^3 $  & \multicolumn{2}{l}{$\lambda:1.861121 $}   & $7.3\cdot10^6$   & $7.3\cdot10^6$   & \multicolumn{2}{l}{$ \lambda:0.009752 $}    \\
Exponential(Me) & $-1.6\cdot10^3$  & $-1.6\cdot10^3$  & \multicolumn{2}{l}{$\lambda:7.011624 $}   & $-10.9\cdot10^6$ & $-10.9\cdot10^6$ & \multicolumn{2}{l}{$ \lambda:2638.706529 $} \\
Normal          & $3.3\cdot10^3$   & $3.3\cdot10^3$   & $\mu:0.142620 $    & $\sigma:0.500698 $ & $-9.4\cdot10^6$  & $-9.4\cdot10^6$  & $ \mu:0.000379$     & $ \sigma:0.000660 $ \\
Pareto(LR)      & $-8.3\cdot10^3$  & $-8.3\cdot10^3$  & $\alpha:0.252367 $ & $x_m:0.000000 $    & $-10.3\cdot10^6$  & $-10.3\cdot10^6$  & $ \alpha:0.148862 $ & $ x_m:0.000000 $    \\
Pareto(MLH)     & $-11.6\cdot10^3$ & $-11.6\cdot10^3$ & $\alpha:0.092060 $ & $x_m:0.000000 $    & $-10.3\cdot10^6$  & $-10.3\cdot10^6$  & $ \alpha:0.136193 $ & $ x_m:0.000000 $    \\
Weibull         & $-14.6\cdot10^3$ & $-14.6\cdot10^3$ & $\alpha:0.319808 $ & $\beta:0.015244 $  & $-11.0\cdot10^6$ & $-11.0\cdot10^6$ & $ \alpha:0.281189 $ & $ \beta:0.000554 $  \\ \hline

\end{tabular}
}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%
% Logscale Skype

\begin{figure}[ht!]
\centering
\label{fig:aproximation-original-cdf}
\subfloat[Chauchy]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Cauchy_aproximation_vs_Original_set}
}
\subfloat[Exponential(LR)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Exponential_aproximation__linear_regression__vs_Original_set}
}
\hspace{0mm}
\subfloat[Exponential(Me)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Exponential_aproximation__mean__vs_Original_set}
}
\subfloat[Normal]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Normal_aproximation_vs_Original_set}
}
\hspace{0mm}
\subfloat[Pareto(LR)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Pareto_aproximation__linear_regression__vs_Original_set}
}
\subfloat[Pareto(MLH)]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Pareto_aproximation__maximum_likehood__vs_Original_set}
}
\hspace{0mm}
\subfloat[Weibull]{
  \includegraphics[width=78mm]{figures/ch4/Skype_Logscale_-_Weibull_aproximation_vs_Original_set}
}
\caption{CDF functions for the approximations of \textit{skype-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

%%%%%%%%%%%%%%
% Skype correlation
\begin{figure}[h!]
\centering
\label{fig:correlation-hurst-skype-pcap}
\subfloat[Correlation]{
  \includegraphics[width=75mm]{figures/ch4/Skype_Correlation}
  \label{correlation-skype-pcap}
}
\hspace{0mm}
\subfloat[Hust Exponent]{
  \includegraphics[width=75mm]{figures/ch4/Skype_Hurst_Exponent}
}
\hspace{0mm}
\subfloat[Mean]{
  \includegraphics[width=75mm]{figures/ch4/Skype_Mean}
}
\hspace{0mm}
\subfloat[Standard Deviation]{
  \includegraphics[width=75mm]{figures/ch4/Skype_Standard_Deviation}
  \label{hurst-skype-pcap}
}
\caption{Statistical parameters of \textit{skype-pcap} and its approximations}
\end{figure}

%%%%%%%%%%%%%%
% BigFlows correlation
\begin{figure}[ht!]
\centering
\label{fig:correlation-hurst-big-flows-pcap}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/bigFlows_Correlation}
  \label{correlation-skype-pcap}
}
\hspace{0mm}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/bigFlows_Hurst_Exponent}
}
\hspace{0mm}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/bigFlows_Mean}
}
\hspace{0mm}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/bigFlows_Standard_Deviation}
  \label{hurst-skype-pcap}
}
\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
\end{figure}

% BigFlows correlation
\begin{figure}[ht!]
\centering
\label{fig:correlation-hurst-big-flows-pcap}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/Skype_QQplot_-_Weibull_dat}
  \label{correlation-skype-pcap}
}
\hspace{0mm}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/Skype_QQplot_-_Cauchy}
}
\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
\end{figure}

The results for the parameters estimation and AIC and BIC for \textit{skype-pcap} and \textit{bigflows-pcap} are at the table~\ref{tab:prototype-results1}.  The results for \textit{wan-pcap} and \textit{lan-diurnal-pcap} are on the table ~\ref{tab:prototype-results2}. The difference between the values of BIC and AIC in all simulations were very small. Much smaller then the difference between the values found for each distribution. This is an indication that for our type of dataset, using AIC or BIC should will not influence significantly the results.

On our previsions, Weibull followed Pareto are the functions more indicated as good options. This was expected, since both are heavy-tailed functions. But, Cauchy, on most of the tests, seems to no present a good fitting. This is effect of the fast divergence of tangent function, when we linearize our data. Not letting the CDF values be so close to zero or avoided divergence, but still through linear regression the penalty was heavy.

In the figure ~\ref{fig:aproximation-original-cdf} we present all estimated CDF functions along with the empirical CDF, for the trace \textit{skype-pcap}. In the case of the normal function, all values smaller than zero, were set to zero on the plot. Is possible to see different accuracies on each plot, and types of fittings. Visually, the best fit seems to be the Weibull trough linear regression. In the figure ~\ref{fig:aproximation-originalbigflows-cdf} we present the fittings with higher BIC and AIC values for the \textit{bigflows-pcap}. On our previsions. Analyzing the plots, and what they would mean, our Cauchy fitting would impose an almost contant traffic , with the inter packet time close to the mean. On the trace \textit{skype-pcap} the exponential plots seems to not represent well the small values of inter packet times. On the other hand, on \textit{bigflows-pcap} they are expressed much well. This is due fact that an exponential process is good at representing values close to the mean. But, it fails to represent values too small and too higher. The \textit{bigflows-pcap}  has a much smaller dispersion. On the other hand, a self-similar process like Weibull and Pareto are better representing inter packet times with higher dispersion.

Analyzing the quality of AIC and BIC as criterion of choose on \textit{skype-pcap}, we see that in therms of Correlation and Self-similarity it picket the right model: Weibull. Also in therms of mean packet rate and dispersion, is still a good choice, since it is still one of the best choices. The third and the fourth choices (Pareto(LR)) and Exponential(LR) also are good options in most of these metrics. But, Pareto(MLH) is presented as the second best choice, and it had poor results in comparison to the others, especially on mean, correlation and dispersion. In this example, we illustrate it at the table ~\ref{tab:skype-evaluation}.

The trace \textit{bigflows-pcap} has a much higher inter packet rate, and a smaller dispersion. Weibull is the model chosen by AIC/BIC, and it is the second best on correlation and self-similarity (Exponential(Me) and Cauchy are the best respectively). Exponential(Me) chooses as the second preferable, has the closest to the original mean and standard deviation. Comparing the plots of the CDF function, the Weibull seams to express well both small and larger values of inter packet times, while Exponential(Me) is preciser on the mean values, as we can see at figure ~\ref{fig:aproximation-originalbigflows-cdf}.

%%%%%%%%%%%%%%%%%%%%%%%
% Logscale bigFlows
\begin{figure}[ht!]
\centering
\subfloat[]{
  \includegraphics[width=80mm]{figures/ch4/bigFlows_Logscale_-_Exponential_aproximation__mean__vs_Original_set}
  \label{correlation-skype-pcap}
}
%\hspace{0mm}
\subfloat[]{
  \includegraphics[width=80mm]{figures/ch4/bigFlows_Logscale_-_Weibull_aproximation_vs_Original_set}
}
\label{fig:aproximation-originalbigflows-cdf}
\end{figure}

On \textit{lan-firewall-pcap}

On \textit{wan-pcap}

%%%%%%%%%%%%%%%%%%%%%%%
% Prototype results
%%%%%%%%%%%%%%
% BigFlows correlation
\begin{figure}[ht!]
\centering
\label{fig:correlation-hurst-big-flows-pcap}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/Skype_costFunction}
  \label{correlation-skype-pcap}
}
\hspace{0mm}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/bigFlows_costFunction}
}
\hspace{0mm}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/Lan_costFunction}
}
\hspace{0mm}
\subfloat[]{
  \includegraphics[width=75mm]{figures/ch4/Wan_costFunction}
  \label{hurst-skype-pcap}
}
\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
\end{figure}

%%%%%%%%%%%

%\begin{figure}[ht!]
%\centering
%\subfloat[]{
%  \includegraphics[width=80mm]{figures4/Skype_QQplot_-_Cauchy}
%  \label{correlation-skype-pcap}
%}
%\hspace{0mm}
%\subfloat[]{
%  \includegraphics[width=80mm]{figures4/Skype_QQplot_-_Weibull_dat}
%}
%\label{correlation-hurst-skype-pcap}
%\end{figure}

\section{Others Algorithms}

\subsection{On/Off Times estimation}

\begin{algorithm}
\caption{calcOnOff}
\begin{algorithmic}[1]
	\Function{calcOnOff}{$arrivalTime, deltaTime, cutTime, minOnTime$}%\Comment{Where A - array, p - left, q - middle, r - right}
    \State $m = deltaTime.length() - 1$
    \State $j = 0$
    \State $lastOff = 0$
    \State $pktCounterSum = 0$
    \State $fileSizeSum = 0$
	\For{$i = 0:m$}
    	\State $pktCounterSum = pktCounterSum + 1$
		\State $fileSizeSum = fileSizeSum + psSizeList[i, 1]$
    	\If{$i == 1$} \Comment{if the first is session-off time}
        	\State $j++$
            \State $onTimes.push(minOnTime)$
            \State $offTimes.push(deltaTime[i])$
            	\State $pktCounter.push(pktCounterSum)$
				\State $fileSize.push(fileSizeSum)$
				\State $pktCounterSum = 0$
				\State $fileSizeSum = 0$
            \Else \Comment{base case} 
            	\State $pktCounter.push(pktCounterSum)$
				\State $fileSize.push(fileSizeSum)$
				\State $pktCounterSum = 0$
				\State $fileSizeSum = 0$
            	\If{$j == 0$}
                	\State $onTimes.push(arrivalTime[i - 1])$
					\State $offTimes.push(deltaTime[i])$
                \Else \Comment{others on times} 
					\State  $onTimes.push(max(deltaTime[i-1] - deltaTime[lastOff], minOnTime))$ 
					\State  $offTimes.push(deltaTime[i])$
                \EndIf
                \State $lastOff = i$
            \EndIf        
    \EndFor
    \State $pktCounterSum = pktCounterSum + 1$
	\State $fileSizeSum = fileSizeSum + psSizeList[m]$
    \If{$lastOff == m - 1$} \Comment{ if last is session-off }
		\State $onTimes.push(minOnTime)$ % on time
	\Else \Comment{ base last case}
		\If{$lastOff \neq 0$}
		\State $onTimes.push(arrivalTime[m] - arrivalTime[lastOff])$ 
		\Else 
		\State $onTimes.push(arrivalTime[m])$ \Comment{there was just on time}
		\EndIf
	\EndIf
    \State $pktCounter.push(pktCounterSum)$
	\State $fileSize.push(fileSizeSum)$
    \EndFunction
\end{algorithmic}
\end{algorithm}

\subsection{Application classification}

\begin{table}[]
\centering
\caption{Application classification table}
\label{my-label}
\begin{tabular}{lll}
\hline
Application Protocol & Transport Protocols & Transport Ports \\ \hline
HTTPS               & TCP                & 443             \\
FTP                 & TCP                & 20, 21          \\
HTTP                & TCP                & 80              \\
BGP                 & TCP                & 179             \\
DHCP                & UDP                & 67, 68          \\
SNMP                & UDP, TCP           & 161             \\
DNS                 & UDP, TCP           & 53              \\
SSH                 & UDP, TCP           & 22              \\
Telnet              & UDP, TCP           & 23              \\
TACACS              & UDP, TCP           & 49              \\ \hline
\end{tabular}
\end{table}

\section{Implementation Details}

\subsection{Modeling Process}

\subsection{Matlab prototyping and C++ Implementation}

\subsection{Software Engineering process and Lessons Leaned}

\section{Conclusion}

We can conclude by this evaluation, that our chosen methodology for selecting stochastic models for inter packet data is appropriated. The first thing to observe is that, for a high

First, we do not rely on only one type of parametrization. This turns our methodology more robust, since a linear regression may diverge. But aways there will be an packable model, since our estimations for Normal, Exponential(Me) and Pareto(MLH) cannot. Models wich the linear regression diverge, will not have god BIC/AIC estimations, and will not be picked.

% https://en.wikipedia.org/wiki/Gamma_process
%Intordução
%- Como previamente discutido, há uma farta bibliografia dedicada ao estudo da natureza do trafego de internet. Em especial, relacionada a modelos que possam expressar a natureza do tempos entre pacotes. 
%- Como discutido anteriormente, Sabemos pela literatura que o trafego de internet possui uma caracteristica fractal. Processos tipicos de Poisson (expresso em sua forma contínua por uma funções estocastica esponencial)  não são capazes de representar de maneira realistica o trafego. Para tal, podem ser utilizados processos estocasticos heavy-tailed.
%- Porém não são numerosos os trabalhos que tratam da parametrização desses processos. Qual o melhor tipo de parametirzação é uma questão difícil de ser respondida, por diversas. Primeiramente, utilizar funções heavy-tailed pode ser uma metodologia mais eficaz para se garantir a self-similarity do trafego. Porém não necessáriamente outras importantes características do trafego serão mantidas, como por exemplo: média de pacotes por segundo, disperssão e correlação entre o trafego real e o trafego sintético gerado por esse processo. Não há a prncípio uma carantia que a escolha baseada em self-similatrity também irá garantir que essas outras características se mantanham. O ideal é que  encontremos um método que possa garantir um bom resultado na maioria, se não em todas essas características.
%- Além disso, há diversos métodos disponíveis para se estimar parâmertos de uma função estocastica. Para citar alguns exemplos:
%* Em alguamas funções como a normal e a exponencial os parâmetros podem ser estimados diratemente através do calculo da média e da variância dos dados.
%* Em funções que é possivel realizar a linearização, os parametros podem ser estimados por meio de regressão linear
%* Outro método frequentemente usado é o do maximum likelihood
%Porém, prever comportamento que cada funções estocástica terá com cada um desses estimadores, não é trivial. Por exemplo.  Por exemplo:
%* Dependendo dos dados originais, a estimativa pode ser muito pobre, e posuir uma baixa correlação com os dados originais. 
%* Os estimadores possuirão algum "bias", desviando apresentando um desvio para cima ou para baixo no valor esperado. Ou isso pode não ocorrer.
%- O objetivo desse capítulo é somente avaliar a qualidade de nosso modelo para estimativa de parâmetros estocasticos para estimadores de inter packet times. iremos utilizar o nosso procedimento em diferentes datasets, e avaliar a qualidade dos resultados obtidos.

\begin{comment}

%%%%%%%%%%%%%%

%To evaluate the quality of the generated data, we use four criteria:

%As we can see in the figure~\ref{correlation-skype-pcap}, Weibull has a correlation close to one correlation (0.969). The follow values of next values of correlation are: Pareto(LR)(0.810), Normal (0.701), Exponential(LR) (0.697), Pareto(MLH) (0.556), Cauchy (0.470), and Exponential(Me) (0.294).

%The next criterion is The Hurst exponent. First, we can observe that all fittings have resulted in a  self-similar process since all values were between 0.5 and 1. Again, the AIC prediction was confirmed, since the Weibull fitting is the one with the closest fractal level from the original trace, around 0.80 and 0.85.

Revisão da literatura
* O trabalho do sourcesonoff realisa uma análise extensiva de uma modelagem apropriada entre bursts de trafego. No trabalho, algumas funções estocasticas são analizadas, e é recomendado o uso sa Weibull. Nesse trabalho é utilizado o calculo do prâmetro BIC como estimador da melhor função estocastica

Metodologia e validação
- por questões referentes a teoria da iinformação, optamos por utilizar o parametro AIC como nosso estimador oficial de melhor função estocastica. 
- Porém, também calculamos o BIC, e verificamos ue via de regra a diferença dos dois valores é bem baixa. Em geral, para datasets maiores, a diferença entre o BIC e AIC de uma mesma função tende a ser consideravelmente menor do que se comparado ao de outra funçao, como veremos a seguir
- A metodologia escolhida é a seguinte: realizamos a estimativa de parametors de diversas funções estocasticas para um mesmo dataset. Calcularemos o valor do AIC, e baseado nele, iremos estimar, em ordem crescente qual a melhor função estocástica. 
- fazer uma figura com cores, mostrando segundo o estimador a ordem das funções, e compara-las com  a ordem estimada por meio dos 4 outros parâmetros.
 - Utiizar correlação, media, variancia, e hurst.
- A vantagem do AIC é que tendo a disposição o datset original, ele é um metodo completamente analítico, não dependendo da geração de numeros aleatórios (como por exemplo no cauculo da correação). Nesse caso, evita que o gerador escolhido possua algum bias na geração dos dados, e comprometa o resultado do estimaor. Além disso, é um procedimento computacionalmente mais barato, pois é puramente analitico

Resultados
- Neste capítulo apresentaremos a análise de somente  2 datasets: da captura de skype e da captura big-flows. No apendice haverão outras análises, que incluem:
* uma análise de inter packets times de uma captura diurnal
* inter-packets times de um single flow do caida
* inter-burst timesconsiderando apenas inter-packet times maiores do que 1 segundo.
* inter pacekt time de 1 segundo do trace do caida.
- o porposito desse modelo é avaliar a qualidade do modelo de seleção, se ele é uma boa ou mpa escolha, já que não há muitso trabalhos relacionados na literatura.
- como o trafego de internet é fractal, caso essa metodologia represente uma boa escolha para os datsets analisados, ele também tende a ser uma boa escolha para datasets de diferentes intervalos de inter-packet times (maiores e menores). Uma análise mais precisa é feita no apendice a respeito dessa questão.

Conclusões

%In this chapter we will go deep into details on how our tool makes the data modeling, focusing on inter-packet times. We will present curves obtained by our Matlab prototype that shows in detail how each step works. After explaining this process, we will present an evaluation method of our results, using \textit{QQplots}. After this, we give some details of how we convert code from Matlab to C++ and its benefits on time execution. All code used in this section is available on our GitHub page, on the directory \texttt{Prototypes}.

%We also define here the datasets we are going to use in the rest of this text. We will use two datasets, and for reproduction purposes, one is public available. The first is a CAIDA\footnote{http://www.caida.org/home/}{http://www.caida.org/home/}, and can be found at  \href{https://data.caida.org/datasets/passive-2016/equinix-chicago/20160121-130000.UTC}{https://data.caida.org/datasets/passive-2016/equinix-chicago/20160121-130000.UTC}. Access to this file need login, so you will have to create an account and wait for approval first. The pcap's file name is \texttt{equinix-chicago.dirA.20160121-130500.UTC.anon.pcap.gz}. The second we capture in our laboratory LAN, through a period of 24 hours. Along with other tests, We intend to verify diurnal behavior on it.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%After we implement this models, we where able to get different approximations for the stochastic functions. To evaluate how well the method is able to fit inter packet times, we first test it against a whole set of inter packet times. Figures (...) represents the CDF fitting for the function for the \textit{skype-pcap}. In the apendix ~\ref{ap:mathematical-modeling}, we also present the fitting achieved for whole set of inter-packet times, and for a single selected flow of \textit{caida-pcap} and\textit{lan-diurnal-pcap} \textit{pcaps} . We are able to see that the Weibull approximation fits better then any exponential approximation. But, we define an automatic way to estimate the best fitting. We  use the AIC (Akaike information criterion), winch is gave by:

%\begin{equation}
%AIC = 2k - 2\ln{(L)} 
%\end{equation}

%where $k$ is the number os estimated parameters for the stochastic function, and $L$ is the value of the likelihood function. We explain it in details in the appendix A. The smaller is the AIC value, the best is the function fitting. An alternative for the AIC, is the BIC value, which follow the same rule. Big is defined by the equation:

%\begin{equation}
%BIC = k\ln{(n)} - 2\ln{(L)}
%\end{equation}

%where n is the number of elements of the sample dataset. We present at table ~\ref{tab:bic-aic} the values found by each estimator, for the \textit{skype-pcap}.

%As we can see, both BIC and AIC agree on each element, which one is the best and the worst. In this case, the best is the Weibull and the worst is the Cauchy. The exponential models, which are the continuous version of a classical Poisson process, is worse than Weibull and both Pareto estimation.

%But, to verify if our estimation is good, we need to see what sort of data these stochastic process are able to generate, and how close the stochastic properties of the synthetic dataset is from the original. In this way, we will be able to verify its actual quality in  unbiased way.

% The Pearson correlation is +1 in the case of a perfect direct (increasing) linear relationship (correlation), −1 in the case of a perfect decreasing (inverse) linear relationshi

%\textcolor{red}{TODO:Fazer uma breve avaliação das parametrizações obtidas com os dois traces utilizando QQplots, e comentar os resultados }

%\section{C codification}

%\textcolor{red}{TODO: Explicar detalhes da codificação em C, como bibliotecas utilizadas, a utilização de valores minimos para evitar o calculo de $\log{0}$, e a opção de executar testes de regressão, compilando com a opção regression-tests ou outra que eu criar na hora.}
\end{comment}

### 2017-06-06 Docs/Thesis/docs/chapter6.tex
New testes scripts in Python and Bash to calc the costFunction of the prototype. Also, at the folder Docs, the thesis text was added, i'm editing it using texstudio.

\chapter{Conclusion and Future Work}
\label{ch:conclusion}

\section{Future Work}

\subsection{Melhorando resultados}

\subsection{Calibração das ferramentas}

Para extensão do trafego gerado, é necessário um estudo da melhor calibração para cada ferramente, como o D-ITG, Iperf, Libtins, o que pode melhorar os resultados

\subsection{Melhorar Modelagem}
\subsubsection{Machine learning classification de aplicações}
\subsubsection{Modelagem de payload}
usando payloads pre-definidos em strings
\subsubsection{Modelagem de de windows size, e flags tcp}

\subsection{Improoving performance}

\subsubsection{Improving database storage}

basicamente eu vou aqui propor um novo modelo de database mais eficiente, no qual menos dados serão arnmazenados

\subsubsection{Improving DataProcessor Performance}

Melhorar os algoritimos adicionando técnicas adicionais de modelagem, como condição de parada para o algoritimo gradient descendent, stochastic gradient descendent, entre outros

\subsubsection{Sniffer baseado em SDN Switch}
Isso mudaria o tipo de dado adiquirido, porém os algorítimos implementados ainda poderiam ser utilizados, já que eles trabalham com qualquer tipo de dado. Haveriam mudanças em como eles seriam tratados pelo data processor

\subsubsection{Implementação}

- Sniffer em C++ para melhorar a performance
- Network Trace com uma API em Python

\subsubsection{Kernel bypass usando o DPDK}

Automatizar a criação de KKNI interfaces pelo FlowGenerator, o que possibilitaria kernel bypass na geração do trafego, melhorando a performance

\subsection{Novos trabalhos}

\subsubsection{PcapGen}

Mininet+TCPdump+LibtinsFlow=> possibilidade de captura de trafego gerado em uma interface virtual, gerando portante traces sintéticos.
Isso possibilitaria a criação de uma biblioteca de traces, para aplicações de banchmark como o NFPA.

\subsubsection{Extender para novas ferramentas e bibliotecas}

Ampliar para o moongen, ostinato, Seagull, NetFPGA, etc

\subsection{Benchmarking}

Oferecer a possibilidade de automatização de medições e testes extendendo a ferramenta

\section{Software Engineering process and Lessons Leaned}

\section{Conclusion}

### 2017-06-06 MesserTG/src/DataProcessor.h

@@ -202,7 +202,7 @@ private:
 	/**
 	 * Default value of cut time (SESSION_CUT_TIME) for sections
 	 */
-	double m_session_cut_time = 4;
+	double m_session_cut_time = 30;
 	//double m_session_cut_time = DEFAULT_SESSION_CUT_TIME;
 
 

### 2017-06-06 MesserTG/src/Main.cpp

@@ -55,7 +55,7 @@ int main()
 {
 	MESSER_LOG_INIT(DEBUG);
 	//bool regressionTests = false;
-	bool testDummy = false;
+	bool testDummy = true;
 	bool testDitg = true;
 
 #ifdef REGRESSION_TESTS
@@ -90,7 +90,7 @@ int main()
 		trace->writeToFile("kkk.xml");
 		trace->writeToFile("data/regression-tests/test-trace.xml");
 
-		trace->exec(true);
+		//trace->exec(true);
 		delete trace;
 	}
 	if (testDitg == true)
@@ -106,8 +106,8 @@ int main()
 		////dp.calculate(experimentName, &dbif, trace);
 		//trace->setTrafficGenEngine("D-ITG");
 		//trace->exec(true);
-		//NetworkTrace traceCdt =  NetworkTrace("changed-ips-macs-trace.xml", "D-ITG");
-		NetworkTrace traceCdt =  NetworkTrace("changed-ips-macs-trace.xml", "Dummy");
+		NetworkTrace traceCdt =  NetworkTrace("kkk.xml", "D-ITG");
+		//NetworkTrace traceCdt =  NetworkTrace("changed-ips-macs-trace.xml", "Dummy");
 		traceCdt.exec(true);
 
 	}

### 2017-06-06 Tests/scripts/mininet-validation/itgsend.sh

@@ -1,0 +1,2 @@
+#!/bin/bash
+ ITGSend -a 10.0.0.1 -c 1000 -V 0.092060 0.000050

### 2017-06-06 Tests/scripts/prototype-dataProcessor/dataProcessor.m

@@ -49,8 +49,15 @@ PLOT_DATA_EXT = ".dat";
 M = load(DATAFILE_NAME);
 %interArrival = sort(M(:,4)) + min_time;
 %interArrival = abs(sort(M)) + min_time;
+
+%%Change scale
+scale = 1000;
+
 interArrival = abs(sort(M));
 interArrival(interArrival == 0) =  min_time;
+
+interArrival = interArrival*scale
+
 max_time = max(interArrival);
 interArrivalCdf = empiricalCdf(interArrival);
 m = length(interArrival);

### 2017-06-06 Tests/scripts/prototype-dataProcessor/plotCostFunction.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+PLOT_DIR="../../plots";
+simName=$1;
+font_config="font='Helvetica,15'";
+
+if [[ ${simName} == "" ]];
+	then
+	simName=$RANDOM;
+fi
+SIM_DIR="/FINAL_prototype-"${simName}"/";
+
+./calcCostFunction.py ${PLOT_DIR}${SIM_DIR}
+gnuplot -e "datafile='${PLOT_DIR}${SIM_DIR}/costFunction.dat'" -e "filename='${PLOT_DIR}${SIM_DIR}/costFunction'" -e "ylabel='cost function'"   -e ${font_config} ../gnuplot/tickbar.gnu
+
+

### 2017-06-06 Tests/scripts/prototype-dataProcessor/remove-this.sh

@@ -1,0 +1,14 @@
+./plotCostFunction.sh "001_lan_diurnalFirewallCapture"
+./plotCostFunction.sh "001_wireshark-wiki_tftp_wrq"
+./plotCostFunction.sh "001_wireshark-wiki_eigrp-for-ipv6-auth"
+./plotCostFunction.sh "001_wireshark-wiki_dhcp-nanosecond"
+./plotCostFunction.sh "001_stp"
+./plotCostFunction.sh "001_RIPv2_subnet_down"
+./plotCostFunction.sh "001_ospf_over_gre_tunnel"
+./plotCostFunction.sh "001_bgp"
+./plotCostFunction.sh "001_equinix-1s"
+./plotCostFunction.sh "001_tcpreplay_bigFlows"
+./plotCostFunction.sh "001_tcpreplay_bigFlows"
+./plotCostFunction.sh "001_live_background-traffic-1"
+./plotCostFunction.sh "001_skype-flow"
+

### 2017-06-06 Tests/scripts/prototype-flowGenerator/calcOnOnffSimplified.m

@@ -1,0 +1,70 @@
+## Copyright (C) 2017 anderson
+## 
+## This program is free software; you can redistribute it and/or modify it
+## under the terms of the GNU General Public License as published by
+## the Free Software Foundation; either version 3 of the License, or
+## (at your option) any later version.
+## 
+## This program is distributed in the hope that it will be useful,
+## but WITHOUT ANY WARRANTY; without even the implied warranty of
+## MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+## GNU General Public License for more details.
+## 
+## You should have received a copy of the GNU General Public License
+## along with this program.  If not, see <http://www.gnu.org/licenses/>.
+
+## -*- texinfo -*- 
+## @deftypefn {Function File} {@var{retval} =} calcOnOnffSimplified (@var{input1}, @var{input2})
+##
+## @seealso{}
+## @end deftypefn
+
+## Author: anderson <anderson@duvel-ThinkCentre-M93p>
+## Created: 2017-05-31
+
+function [onOff onTimes offTimes] = calcOnOffTimes (arrival_time, delta_time, cut_time, min_on_time)
+	m = length(delta_time); % in: number of inter packet times
+	last_off = 0; i = 0; j = 0;
+	for i = 1:m % Calc list of OnOff times
+		if((delta_time(i) > cut_time))
+			if(i == 1) % if the first is session-off
+				j++;
+				onOff(j) = min_on_time; % on time
+				j++;
+				onOff(j) = delta_time(i);
+				last_off = i;
+			else 
+				if(j == 0) % base first case
+					j++;
+					onOff(j) = arrival_time(i - 1); % on time
+					j++;
+					onOff(j) = delta_time(i);
+					last_off = i;
+				else %base case
+					j++;
+					%onOff(j) = delta_time(i-1) - delta_time(last_off);
+					onOff(j) = arrival_time(i-1) - arrival_time(last_off); % on time				
+					if(onOff(j) < min_on_time)
+						onOff(j) = min_on_time; % on time
+					endif
+					j++;
+					onOff(j) = delta_time(i);
+					last_off = i;
+				endif		
+			endif
+		endif
+	endfor
+	i = m + 1; % calc the last On time
+	if(last_off == m ) % if last is session-off 
+		j++;
+		onOff(j) = min_on_time; % on time
+	else % base last case
+		j++;
+		if(last_off != 0)
[…]

### 2017-06-06 if-promisc.sh

@@ -1,4 +1,4 @@
 #/bin/bash
 interface=$1
-ifconfig $interface up
-ifconfig $interface promisc
+sudo ifconfig $interface up
+sudo ifconfig $interface promisc

### 2017-06-09 Docs/Thesis/docs/appendix/appendixB.tex
New testes scripts in Python and Bash to calc the costFunction of the prototype. Also, at the folder Docs, the thesis text was added, i'm editing it using texstudio.
new advancements on the thesis text

--- 2017-06-06 Docs/Thesis/docs/appendix/appendixA.tex
@@
-%\newpage
-%\renewcommand{\appendixname}{Appendix}
+\chapter{Chapter ~\ref{ch:modeling-evaluation} Aditional Plots}
+\label{ap:aditional-plots}
 
-%\appendix
+\section{CDFs distributions}
 
-\chapter{Revision of Probability}
-\label{ap:revision-probability}
+\begin{figure}[ht!]
+	\centering
+	\label{fig:aproximation-original-cdf-bigFlows}
+	\subfloat[Chauchy]{
+		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Cauchy_aproximation_vs_Original_set}
+	}
+	\subfloat[Exponential(LR)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Exponential_aproximation_(linear_regression)_vs_Original_set}
+	}
+	\hspace{0mm}
+	\subfloat[Exponential(Me)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Exponential_aproximation_(mean)_vs_Original_set}
+	}
+	\subfloat[Normal]{
+		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Normal_aproximation_vs_Original_set}
+	}
+	\hspace{0mm}
+	\subfloat[Pareto(LR)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Pareto_aproximation_(linear_regression)_vs_Original_set}
+	}
+	\subfloat[Pareto(MLH)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Pareto_aproximation_(maximum_likehood)_vs_Original_set}
+	}
+	\hspace{0mm}
+	\subfloat[Weibull]{
+		\includegraphics[width=78mm]{figures/apB/cdf/bigFlows_Logscale_-_Weibull_aproximation_vs_Original_set}
+	}
+	\caption{CDF functions for the approximations of \textit{bigFlows-pcap} inter  packet times, of many stochastic functions.}
+\end{figure}
 
-\section{Stochastic Process}
+\begin{figure}[ht!]
+	\centering
+	\label{fig:aproximation-original-cdf-wan}
+	\subfloat[Chauchy]{
+		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Cauchy_aproximation_vs_Original_set}
+	}
+	\subfloat[Exponential(LR)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Exponential_aproximation_(linear_regression)_vs_Original_set}
+	}
+	\hspace{0mm}
+	\subfloat[Exponential(Me)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Exponential_aproximation_(mean)_vs_Original_set}
+	}
+	\subfloat[Normal]{
+		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Normal_aproximation_vs_Original_set}
+	}
+	\hspace{0mm}
+	\subfloat[Pareto(LR)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Pareto_aproximation_(linear_regression)_vs_Original_set}
+	}
+	\subfloat[Pareto(MLH)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Pareto_aproximation_(maximum_likehood)_vs_Original_set}
+	}
+	\hspace{0mm}
+	\subfloat[Weibull]{
+		\includegraphics[width=78mm]{figures/apB/cdf/wan_Logscale_-_Weibull_aproximation_vs_Original_set}
+	}
+	\caption{CDF functions for the approximations of \textit{wan-pcap} inter  packet times, of many stochastic functions.}
+\end{figure}
 
-\section{Random variable}
+\begin{figure}[ht!]
+	\centering
+	\label{fig:aproximation-original-cdf-lan}
+	\subfloat[Chauchy]{
+		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Cauchy_aproximation_vs_Original_set}
+	}
+	\subfloat[Exponential(LR)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Exponential_aproximation_(linear_regression)_vs_Original_set}
+	}
+	\hspace{0mm}
+	\subfloat[Exponential(Me)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Exponential_aproximation_(mean)_vs_Original_set}
+	}
+	\subfloat[Normal]{
+		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Normal_aproximation_vs_Original_set}
+	}
+	\hspace{0mm}
+	\subfloat[Pareto(LR)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Pareto_aproximation_(linear_regression)_vs_Original_set}
+	}
+	\subfloat[Pareto(MLH)]{
+		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Pareto_aproximation_(maximum_likehood)_vs_Original_set}
+	}
+	\hspace{0mm}
+	\subfloat[Weibull]{
+		\includegraphics[width=78mm]{figures/apB/cdf/lan_Logscale_-_Weibull_aproximation_vs_Original_set}
+	}
+	\caption{CDF functions for the approximations of \textit{lan-diurnal-pcap} inter  packet times, of many stochastic functions.}
+\end{figure}
 
-\section{Probability Distribution Function (PDF)}
+\section{QQplots}
 
-\section{Cumulative Distribution Function (CDF)}
+%\begin{figure}[ht!]
+%	\centering
+%	\label{fig:aproximation-original-cdf-skype}
+%	\subfloat[Chauchy]{
+%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Cauchy}
+%	}
+%	\subfloat[Exponential(LR)]{
+%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Exponential(LR)}
+%	}
+%	\hspace{0mm}
+%	\subfloat[Exponential(Me)]{
+%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Exponential(Me)}
+%	}
+%	\subfloat[Normal]{
+%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Normal}
+%	}
+%	\hspace{0mm}
+%	\subfloat[Pareto(LR)]{
+%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Pareto(LR)}
+%	}
+%	\subfloat[Pareto(MLH)]{
+%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Pareto(MLH)}
+%	}
+%	\hspace{0mm}
+%	\subfloat[Weibull]{
+%		\includegraphics[width=78mm]{figures/apB/qq/skype_QQplot_-_Weibull}
+%	}
+%	\caption{CDF functions for the approximations of \textit{skype-pcap} inter  packet times, of many stochastic functions.}
+%\end{figure}
 
-\section{Expected value, Variance, Mean and Standard Deviation}
+\begin{figure}[ht!]
+	\centering
+	\label{fig:aproximation-original-cdf}
+	\subfloat[Chauchy]{
+		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Cauchy}
+	}
+	\subfloat[Exponential(LR)]{
+		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Exponential(LR)}
+	}
+	\hspace{0mm}
+	\subfloat[Exponential(Me)]{
+		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Exponential(Me)}
+	}
+	\subfloat[Normal]{
+		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Normal}
+	}
+	\hspace{0mm}
+	\subfloat[Pareto(LR)]{
+		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Pareto(LR)}
+	}
+	\subfloat[Pareto(MLH)]{
+		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Pareto(MLH)}
+	}
+	\hspace{0mm}
+	\subfloat[Weibull]{
+		\includegraphics[width=78mm]{figures/apB/qq/bigFlows_QQplot_-_Weibull}
+	}
+	\caption{CDF functions for the approximations of \textit{bigFlows-pcap} inter  packet times, of many stochastic functions.}
+\end{figure}
 
-\section{Self-similarity}
+\begin{figure}[ht!]
+	\centering
+	\label{fig:aproximation-original-cdf-lan}
+	\subfloat[Chauchy]{
+		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Cauchy}
+	}
+	\subfloat[Exponential(LR)]{
+		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Exponential(LR)}
+	}
+	\hspace{0mm}
+	\subfloat[Exponential(Me)]{
+		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Exponential(Me)}
+	}
+	\subfloat[Normal]{
+		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Normal}
+	}
+	\hspace{0mm}
+	\subfloat[Pareto(LR)]{
+		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Pareto(LR)}
+	}
+	\subfloat[Pareto(MLH)]{
+		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Pareto(MLH)}
+	}
+	\hspace{0mm}
+	\subfloat[Weibull]{
+		\includegraphics[width=78mm]{figures/apB/qq/lan_QQplot_-_Weibull}
+	}
+	\caption{CDF functions for the approximations of \textit{lan-diurnal-pcap} inter  packet times, of many stochastic functions.}
+\end{figure}
 
-\section{Heavy-tailed distributions}
+\begin{figure}[ht!]
+	\centering
+	\label{fig:aproximation-original-cdf-wan}
+	\subfloat[Chauchy]{
+		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Cauchy}
+	}
+	\subfloat[Exponential(LR)]{
+		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Exponential(LR)}
+	}
+	\hspace{0mm}
+	\subfloat[Exponential(Me)]{
+		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Exponential(Me)}
+	}
+	\subfloat[Normal]{
+		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Normal}
+	}
+	\hspace{0mm}
+	\subfloat[Pareto(LR)]{
+		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Pareto(LR)}
+	}
+	\subfloat[Pareto(MLH)]{
+		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Pareto(MLH)}
+	}
+	\hspace{0mm}
+	\subfloat[Weibull]{
+		\includegraphics[width=78mm]{figures/apB/qq/wan_QQplot_-_Weibull}
+	}
+	\caption{CDF functions for the approximations of \textit{wan-pcap} inter  packet times, of many stochastic functions.}
+\end{figure}
 
-\section{Hurst Exponent}
+\section{Validation}
 
-\section{Maximum likelihood function}
+\begin{figure}[ht!]
+	\centering
+	\label{fig:correlation-hurst-bigflows-pcap}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Correlation}
+		\label{correlation-skype-pcap}
+	}
+	\hspace{0mm}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Hurst_Exponent}
+	}
+	\hspace{0mm}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Mean}
+	}
+	\hspace{0mm}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/bigFlows_Standard_Deviation}
+		\label{hurst-skype-pcap}
+	}
+	\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
+\end{figure}
 
-\section{Akaike information criterion}
+\begin{figure}[ht!]
+	\centering
+	\label{fig:correlation-hurst-lan-pcap}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/lan_Correlation}
+		\label{correlation-skype-pcap}
+	}
+	\hspace{0mm}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/lan_Hurst_Exponent}
+	}
+	\hspace{0mm}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/lan_Mean}
+	}
+	\hspace{0mm}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/lan_Standard_Deviation}
+		\label{hurst-skype-pcap}
+	}
+	\caption{Statistical parameters of \textit{lan-diurnal-pcap} and its approximations}
+\end{figure}
 
-\section{Bayesian information criterion}
-
-\section{Estimation of parameters of stochastic distributions}
-
-\subsection{Linear Regression and Gradient Descendant Algorithm}
-
-\subsection{Maximum likelihood estimation}
-
-\subsection{Others methods}
+\begin{figure}[ht!]
+	\centering
+	\label{fig:correlation-hurst-wan-pcap}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/wan_Correlation}
+		\label{correlation-skype-pcap}
+	}
+	\hspace{0mm}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/wan_Hurst_Exponent}
+	}
+	\hspace{0mm}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/wan_Mean}
+	}
+	\hspace{0mm}
+	\subfloat[]{
+		\includegraphics[width=75mm]{figures/apB/val/wan_Standard_Deviation}
+		\label{hurst-skype-pcap}
+	}
+	\caption{Statistical parameters of \textit{wan-pcap} and its approximations}
+\end{figure}

### 2017-06-09 Docs/Thesis/docs/chapter3.tex
new advancements on the thesis text

@@
 We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.
-\textcolor{red}{<<<<pode mudar, calibrar>>>>} We develop an algorithm called \textit{calcOnOff} responsible for estimating these times.
+We develop an algorithm called \textit{calcOnOff} responsible for estimating these times.
 It also determines the number of packets and bytes transferred by each file.
@@
 If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time.
-In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds).
+In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds) \textcolor{red}{<<<<pode mudar, calibrar>>>>}.
 The control of ON/OFF periods is made by the \texttt{NetworkFlow} class.

### 2017-06-09 Docs/Thesis/docs/chapter4.tex
new advancements on the thesis text

@@
 
-As discussed before, there is many works devoted on studding the nature of the Ethernet traffic \cite{selfsimilar-ethernet}.
-Classic Ethernet models used Poisson related process to express generation of traffic.
-In a first look it makes sense,  sense, since a Poisson process represents the probability of events occur with a known average rate, and independently of the time since the last event\cite{selfsimilar-ethernet} \cite{book-poisson}.
+%2nd-review
+There are many works devoted to studying the nature of the Ethernet traffic\cite{selfsimilar-ethernet}.
+Classic Ethernet models used Poisson related processes to express generation of traffic.
+Initially, it makes sense since a Poisson process represents the probability of events occur with a known average rate, and independently of the last occurence\cite{selfsimilar-ethernet} \cite{book-poisson}.
 But studies made by Leland et al.\cite{selfsimilar-ethernet} showed that the Ethernet traffic has a self-similar and fractal nature.
-Even if they are able to represent the randomness of an Ethernet traffic, simple Poisson processes can't express the presence of "burstiness" in a long-term time scale, such as traffic "spikes" on long-range "ripples".
-This is an indicative of the fractal and self-similar nature of the traffic.
-
-Stochastic process that respects this characteristic have infinite variance, said to be heavy-tailed.
+Even if they are able to represent the randomness of an Ethernet traffic, simple Poisson processes can't express traffic "burstiness" in a long-term time scale, such as traffic "spikes" on long-range "ripples".
+This is an indicative of the fractal and self-similar nature of the traffic, that usually we express by distributions with infinite variance, called heavy-tailed.
 Heavy-tail means that a stochastic distribution is not exponentially bounded\cite{sourcesonoff-paper}.
 Examples of heavy-tailed functions are Weibull, Pareto, Cauchy.
-But not many works on the literature deal with a process for parameterization of different stochastic models for Ethernet traffic.
-Also, a heavy-tailed function may guarantee self-similarity, but not necessarily they would guarantee other features like good correlation and same mean packet rate and dispersion.
+But heavy-tailed function may guarantee self-similarity, but not necessarily they will ensure other features like good correlation and same mean packet rate.
 
-In this chapter we proposed an unified and simple method for modeling inter packet times, and choose the best fit automatically, without having to generate random data.
-We estimate many stochastic functions through many methodologies, and select the best model through the AIC computation.
-Since generating random can be computationally cost an have a bias, depending of the seed generator, an analytical method for selecting the best fitting eliminate these problems.
+%2nd-review
+There many consolidate works that investigate the nature of the internet traffic\cite{selfsimilar-ethernet}\cite{analysis-self-similar}\cite{stochartic-selfsimilar}\cite{selfsimilar-highvariability}\cite{multi-player-online-game-self-similarity}, and many others on the modelling of stochastic functions for specific scenarios\cite{estimation-renewal-function-ethernet-traffic}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}\cite{modeling-concurrent-heavy-tailed}\cite{optimal-scheduling-of-heavy-tailed-traffic}\cite{modelling-of-self-similar}.
+But not as many on model choice automatization\cite{sourcesonoff-paper}.
 
-We made a brief bibliographic review on some works related works.
-Then, we will present the traffic traces we are going to use in this chapter, and in the rest of the work.
-After we present or selected methodology for parameterization selection of the best fitting.
-To evaluate the quality of this selection criteria, we define a methodology for evaluate if our model selection is good or not.
+%2nd-review
+In this chapter, we propose a method that may be implemented by  software.
+We estimate many stochastic functions through many methodologies and select the best model through the AIC computation\cite{bic-aic-comparision}.
+Since generating random can be cost and have a bias, depending on the seed generator, we cut these problems since our method is analytical.
+
+%2nd-review
+We made a brief bibliographic review of some works related works on this topic.
+Then, we will present the traffic traces we are going to use in this chapter, and in the rest of our work.
+After we present or selected method for parameterization and fitting choice.
+To test our criteria quality, we define a validation method, based on cross-validations made by simulations.
 
@@
 
-There are plenty of works on the literature which proposes new processes and methodologies foe generation on inter-packet times.
+%2nd-review
+There are plenty of works on the literature which proposes new processes and methodologies for modeling times between packets and packet trains.
 
+%2nd-review
 Fiorini \cite{modeling-concurrent-heavy-tailed} presents a heavy-tailed ON/OFF model, which tries to represent a traffic generated by many sources.
@@
 
-Kreban and Clearwater\cite{hierarchical-dynamics-interarrival-times} presents a model for times between job submissions of multiple users on a super computer.
-They show in their job that the Weibull probability functions is able to express well small and high values of inter-job submission times.
-They also tested exponential, lognormal and Pareto(called there power law) distributions.
+%2nd-review
+Kreban and Clearwater\cite{hierarchical-dynamics-interarrival-times} presents a model for times between job submissions of multiple users over a super computer.
+They show that the Weibull probability functions are able to express well small and high values of inter-job submission times.
+They also tested exponential, lognormal and Pareto distributions.
 Exponential distribution couldn't  represent long-range values because it fell off too fast and Pareto was too slow.
@@
 
-Kronewitter\cite{optimal-scheduling-of-heavy-tailed-traffic} presents a models of scheduler of heavy-tailed traffic of multiple sources.
-On his work, he uses multiple Pareto sources to represent the traffic.
+%2nd-review
+Kronewitter\cite{optimal-scheduling-of-heavy-tailed-traffic} presents a model of scheduling traffic of many heavy-tail sources.
+On his work, he uses many Pareto sources to represent the traffic.
 To estimate the shape parameter $\alpha$ they use linear regression.
+
+% \cite{bivariate-gamma-distribution-arrival}
+% \cite{bic-aic-comparision}
+% \cite{sourcesonoff-paper}
+% \cite{modelling-of-self-similar}
+% \cite{realtime-detection-dos}
+% \cite{traffic-modelling-matlab}
+% \cite{trasmission-failure}
+% \cite{improvement-approaches-modeling}
 
@@
 
-We will start defining the datasets we are going to use in this evaluation, and in the rest of this work as well.
-We define our criteria of parameterization and model selection, and a methodology for measure the quality of our choices.
+%2nd-review
+We will start defining the datasets we are going to use in the rest of this work. Then, we define our criteria of parameterization and model choice and a methodology for measure the quality of method.
 
@@
 
+%2nd-review
 We start defining also define the \textit{pcaps} datasets we are going to use in the rest of this text. We will use for datasets, and for reproduction purposes, three are public available. 
-The first is a light weight Skype capture, found at Wireshark wiki\footnote{https://wiki.wireshark.org/}, and can be found at \href{https://wiki.wireshark.org/SampleCaptures}{https://wiki.wireshark.org/SampleCaptures}.
-The file name is \texttt{SkypeIRC.cap}.
+The first is a lightweight Skype capture, found in  Wireshark wiki\footnote{https://wiki.wireshark.org/}, and can be found at \href{https://wiki.wireshark.org/SampleCaptures}{https://wiki.wireshark.org/SampleCaptures}.
+The file name is \texttt{SkypeIRC.cap}, and we call it \textit{skype-pcap}.
 
+%2nd-review
 The second is a CAIDA\footnote{http://www.caida.org/home/}{http://www.caida.org/home/} capture, and can be found at  \href{https://data.caida.org/datasets/passive-2016/equinix-chicago/20160121-130000.UTC}{https://data.caida.org/datasets/passive-2016/equinix-chicago/20160121-130000.UTC}.
@@
 The pcap's file name is \texttt{equinix-chicago.dirB.20160121-135641.UTC.anon.pcap.gz}.
+We call it \textit{wan-pcap}.
 
+%2nd-review
 The third we capture in our laboratory LAN, through a period of 24 hours.
@@
 Along with other tests, We intend to verify diurnal behavior on it.
-That means, a high demand of packets during the day, an a small in the night.
-The fourth is a capture of a busy private network's access point to the Internet, available on-line on TCPreplay\cite{web-tcpreplay} website \footnote{ http://tcpreplay.appneta.com/wiki/captures.html}, and is called \texttt{bigFlows.pcap}.
-We will refer to these \textit{pcaps} as \textit{skype-pcap}, \textit{wan-pcap}, \textit{lan-diurnal-pcap}, and \textit{bigflows-pcap} respectivaly.
-Along with these datasets, we will use two subpcaps from the originals.
+That means a high demand of packets during the day and a small in the night.
+We call it \textit{lan-diurnal-pcap}.
+
+%2nd-review
+The fourth is a capture of a busy private network access point to the Internet, available on-line on TCPreplay\cite{web-tcpreplay} website \footnote{ http://tcpreplay.appneta.com/wiki/captures.html}, and is called \texttt{bigFlows.pcap}.
+We will refer to it \textit{bigflows-pcap}.
+
+%Along with these datasets, we will use two subpcaps from the originals.
 The first, \textit{skype-flowburst-pcap}, is a burst of a single HTTP flow from \textit{skype-pcap}.
@@
 
-\subsection{Modelling Inter-Packet times and Packet Sizes: Proposed Process}
+\subsection{Modelling Inter-Packet times and Packet Sizes}
 
-We summarize our process of modeling inter packet times at the figure~\ref{fig:model-parameterization}.
-We collect a set of inter-packet times from a actual traffic capture.
+%2nd-review
+We summarize our process of modeling inter-packet times at the figure~\ref{fig:model-parameterization}.
+We collect a set of inter-packet times from an actual traffic capture.
 Then, we estimate a set of parameters for stochastic functions, using different methodologies.
@@
 
-Currently we are modeling:
+%2nd-review
+Currently, we are modeling:
 
+%2nd-review
 \begin{itemize}
@@
 	\item Exponential distribution, using linear regression, through the Gradient descendant algorithm. We refer to this distribution as Exponential(LR);
-\item Exponential distribution, using direct estimation of the dataset mean. We refer to this distribution as Exponential(Me);
+	\item Exponential distribution, using a direct estimation of the dataset mean. We refer to this distribution as Exponential(Me);
 	\item Pareto distribution, using linear regression, through the Gradient descendant algorithm. We refer to this distribution as Pareto(LR);
@@
 
+%2nd-review
 Now we will give a brief explanation our three procedures: Linear Regression (with the  Gradient descendant algorithm), direct estimation, and maximum likelihood.
-We go deep in details on the explanation of the methods on the appendix ~\ref{ap:revision-probability}, and present the mathematical demonstrations on appendix~\ref{ap:mathematical-modeling}.
+We go deep into details explaining the methods on the appendix ~\ref{ap:revision-probability}, and present the mathematical demonstrations on appendix~\ref{ap:mathematical-modeling}.
 
+%2nd-review
 Some observations must be made.
-Since the resolution of the time samples used were of $10^{-6}$s, all values equals to zero were set to  $5\cdot10^{-8}$s, to avoid division by zero.
-To avoid divergence on tangent operation on the linearization the Cauchy function, the inter packets CDF function values were floor-limited and upper-limited to  $10^{-6}$ and $0.999999$ respectively.
+Since the time samples resolution used were of $10^{-6}$s, all values equal to zero were set to  $5\cdot10^{-8}$s, to avoid division by zero.
+To avoid divergence on tangent operation on the linearization the Cauchy function, the inter-packets CDF function values were floor-limited and upper-limited to  $10^{-6}$ and $0.999999$ respectively.
 
-We implemented this prototype using Octave. Its code is located on GitHub, for reproduction purposes\footnote{github-link-aqui}
+%2nd-review
+We implemented this prototype using Octave. We upload the code on GitHub, for reproduction purposes\footnote{github-link-aqui}
 
@@
 
-Linear regression is a method for estimating the best linear curve
+%2nd-review
+Linear regression is a method for estimating the best linear curve in the format:
 
@@
 
+%2nd-review
 to fit a given data set. We can use linear regression to estimate parameters of a non-linear curve expressing it on a linear format. For example, the Weibull CDF for $t > 0$ is:
@@
 \begin{equation}
-F(t; \alpha, \beta) = F(t) = 1 - e^{-(t/\beta)^{\alpha}}
+F(t|\alpha, \beta) = F(t) = 1 - e^{-(t/\beta)^{\alpha}}
 \end{equation}
 
-manipuling it, we can found:
+Manipuling the equation:
 \begin{equation}
@@
 
-%corrigir erro
+%%2nd-review
 If we call $x = \ln{(t)}$ and $y = \ln{(-\ln{(1 - F(t))})}$, we found a linear equation, where $a = \alpha$ and $b = -\alpha\ln{(\beta)}$.
@@
 
-We present examples of linearized data, and the linear approximation achieved, as well the cost convergence of the gradient descendant algorithm in the appendix ~\ref{ap:mathematical-modeling}.
+%2nd-review
+We present examples of linearized data, and the linear approximation achieved, as well the cost convergence of the gradient descendant algorithm in the appendix ~\ref{ap:revision-probability}.
 
+%2nd-review
 Applying the inverse equations of the linear coefficients ($\hat{\alpha} = \hat{a}$ and $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$) (the symbol stands for the estimated parameters).
@@
 
+%2nd-review
 We can summarize this procedure, in these steps:
@@
 
+%2nd-review
 In the parameters estimation, there is an exception, since the Pareto scale ($t_{m}$) is defined by the minimum time.
 
+%2nd-review
 In the table~\ref{tab:linearization-sumary} we present a summary of the used equations in the procedure.
@@
 
+%2nd-review
 In the figure~\ref{fig:linearization} we presente the linearized
 
+%2nd-review
 \begin{table}[h!]
 	\centering
-\caption{My caption}
+	\caption{Linearized functions, and parameters estimators, used by the linear regression}
 	\label{tab:linearization-sumary}
@@
 		\hline
-Function    & Linearized $x$     & Linearized $y$                    & \multicolumn{2}{l}{Parameters}                                                        &  \\
+		Function    & Linearized $x$     & Linearized $y$                    & \multicolumn{2}{l}{Parameters Estimator}      						 &  \\
 		\hline
-Cauchy      & $x_i = t_i$        & $y_i = \tan{(\pi(F(t_i) - 1/2))}$ & $\hat{\gamma} = \frac{1}{a}$ & $\hat{\hat{t_0}} = - \frac{b}{a}$                      &  \\
-Exponential & $x_i = t_i$        & $y_i = \ln{(1 - F(t_i))})$        & \multicolumn{2}{l}{$\hat{\lambda} = -a$}                                              &  \\
-Pareto      & $x_i = \ln{(t_i)}$ & $y_i = \ln{(1 = F(t_i))}$         & $\alpha = -a $         & $\hat{x_{m}} = \min_{i = 0, ..., m}\{x_{i}\}$ &  \\
-Weibull     & $x = \ln{(t)}$     & $y = \ln{(-\ln{(1 - F(t))})}$     & $\alpha = a$                 & $\beta = e^{-(b/a)}$                                   & \\
+		Cauchy      & $x_i = t_i$        & $y_i = \tan{(\pi(F(t_i) - 1/2))}$ & $\hat{\gamma} = \frac{1}{\hat{a}}$ & $\hat{t_0} = - \frac{\hat{b}}{\hat{a}}$                      &  \\
+		Exponential & $x_i = t_i$        & $y_i = \ln{(1 - F(t_i))})$        & \multicolumn{2}{l}{$\hat{\lambda} = -\hat{a}$}                                              &  \\
+		Pareto      & $x_i = \ln{(t_i)}$ & $y_i = \ln{(1 = F(t_i))}$         & $\hat{\alpha} = -\hat{a} $         & $\hat{x_{m}} = \min_{i = 0, ..., m}\{x_{i}\}$ &  \\
+		Weibull     & $x = \ln{(t)}$     & $y = \ln{(-\ln{(1 - F(t))})}$     & $\hat{\alpha} = \hat{a}$                 & $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$                                   & \\
 		\hline
@@
 
-%corrigir error
-The expected value $E(X)$ and and variance $Var(X)$ of a random variable $X$ of some distributions are close related with its parameters.
-Since the mean $\bar{\mu}$ and the standard deviation $\bar{\sigma}$ are in general good approximations for the expected value and variance, we may estimate we may use them to estimate parameters.
-%corrigir error
+%2nd-review
+The expected value $E(X)$ and variance $Var(X)$ of a random variable $X$ of some distributions are close related with its parameters.
+Since the mean $\bar{\mu}$ and its standard deviation $\bar{\sigma}$ are in general good approximations for the expected value and variance, we use them to estimate parameters.
+
+%2nd-review
 Following the notation presented at table~\ref{tab:distributions-equations}, we have for the normal distribution:
@@
 
+%2nd-review
 For the exponential distribution $E(X) = \frac{1}{\lambda}$, therefore:
@@
 
+%2nd-review
 The maximum likelihood estimation, is a method for estimation of parameters, winch maximizes the likelihood function.
@@
 Using this method for the Pareto distribution, it is possible to derive the following equations the its parameters:
+
 \begin{equation}
@@
 
+%2nd-review
  Suppose that we have an statistical model $M$ of soma dataset ${\boldsymbol{x} = (x_1, ..., x_n)}$, with $n$ independent and identically distributed observations of a random variable $X$.
@@
 
+%2nd-review
 To see if our criterion of parameter selection is actually is able to find which is the best model, we define a validation methodology. 
@@
 
+%2nd-review
 \begin{itemize}
@@
 
+%2nd-review
 The Pearson's product-moment coefficient, or simply correlation coefficient,  is an expression of the dependence or association between two datasets.
@@
 0 means no linear correlation.
-So, as close the result reach 1, more similar are the inter packet times to the original values.
+So, as close the result reach 1, more similar are the inter-packet times to the original values.
 To estimate it, we use the Octave's function \texttt{corr()}.
 
-As explained before in the chapter~\ref{ch:literature-review}, the Hurst exponent is a measurer of self-similarity, and indicates the fractal level of the inter packet times.
+%2nd-review
+As explained before in the chapter~\ref{ch:literature-review}, the Hurst exponent is meter self-similarity and indicates the fractal level of the inter-packet times.
 As close the result is from the original, more similar is the fractal level of the estimated samples from the original.To estimate this value we use the function \texttt{hurst()} from Octave, which uses rescaled range method.
+Finally we measure the mean and the standard deviation (as a measure of the dispersion), using the Octave's functions \texttt{mean()} and \texttt{std()}.
+We also present some \textit{QQplots}, to visually compare the random-generated data and the original dataset.
 
-Finally we measure the mean and the standard deviation (as a measure of the dispersion), using the Octave's functions \texttt{mean()} and \texttt{std()}.
-We also present some \textit{QQplots}, to visually compare the random-generated data and the actual dataset.
+%2nd-review
+As close the correlation, Hurst exponent, mean and the standard deviation is from the original dataset, the better is model fitting.
+Also, analyzing the mean, we can see if a certain modeling procedure tends to be more penalized for the values close, or far from zero.
+This means that if the mean inter-packet time tends to be smaller or higher compared to the original.
 
-As close the correlation, Hurst exponent, mean and the standard deviation is from the original dataset, the better is model fitting.
-Also, analyzing the mean, we can see if a certain modeling procedure tend to be more penalized for the values close, or far from zero.
-That means, if the mean inter-packet time tends to be smaller or higher compared to the original.
-With these results in hands, we can see if AIC and BIC are actually good criterion on model selection for inter-packet times.
+%2nd-review
+With these results in hands, we can see if AIC and BIC are good criteria for model selection for inter-packet times.
+To quantitatively check it, we define a cost function based on the correlation, Hurst exponent and mean.
+We exclude the standard deviation, because the Hurst exponent being a meter of the fractal level, also capture information about the desired dispersion of the data.
+So, for comparing all these results, we defined a cost function $J$, based on the randomly generated data values.
+
+%2nd-review
+Being $Cr$ the vector of correlations ordered from the greater to the smaller.
+Let $Me$ and $Hr$ defined by the absolute difference between mean and hurt exponent of the estimated values and the original dataset.
+Both are ordered from the smaller to the greatest values.
+Letting $\phi(V, M)$ be an operator wich gives the position of a model $M$ in a vector $V$, we define the cost function $J$ as:
+
+\begin{equation}
+J(M) = \phi(Cr, M) + \phi(Me, M) + \phi(Hr, M)
+\end{equation}
+
+%2nd-review
+The smaller is the cost $J$, the best is the model. Then we compare the results achieved by AIC and BIC, and $J$.
 
@@
 \label{tab:prototype-results1}
-\scalebox{0.70}{ 
-\begin{tabular}{lllllllll}
+\scalebox{0.75}{ 
+\begin{tabular}{lcccccccc}
 \hline
                 & \multicolumn{8}{c}{Trace} \\ \cline{2-9} 
-Function		& AIC        & BIC        & \multicolumn{2}{c}{Parameters}              & AIC        & BIC        & \multicolumn{2}{c}{Parameters}                \\ \cline{2-9}
-        & \multicolumn{4}{c}{skype-pcap}                                        & \multicolumn{4}{c}{bigflows-pcap}                                       \\ \hline 
-Cauchy          & $ 21.8\cdot10^3 $  & $21.9\cdot10^3$  & $\gamma:0.000259 $ & $x_0:0.104891 $    & $ 7.2\cdot10^6 $   & $7.2\cdot10^6$   & $ \gamma:1.935833 $ & $x_0:-7.245697 $    \\
-Exponential(LR) & $-4.3\cdot10^3$  & $ -4.3\cdot10^3 $  & \multicolumn{2}{l}{$\lambda:1.861121 $}   & $7.3\cdot10^6$   & $7.3\cdot10^6$   & \multicolumn{2}{l}{$ \lambda:0.009752 $}    \\
-Exponential(Me) & $-1.6\cdot10^3$  & $-1.6\cdot10^3$  & \multicolumn{2}{l}{$\lambda:7.011624 $}   & $-10.9\cdot10^6$ & $-10.9\cdot10^6$ & \multicolumn{2}{l}{$ \lambda:2638.706529 $} \\
-Normal          & $3.3\cdot10^3$   & $3.3\cdot10^3$   & $\mu:0.142620 $    & $\sigma:0.500698 $ & $-9.4\cdot10^6$  & $-9.4\cdot10^6$  & $ \mu:0.000379$     & $ \sigma:0.000660 $ \\
-Pareto(LR)      & $-8.3\cdot10^3$  & $-8.3\cdot10^3$  & $\alpha:0.252367 $ & $x_m:0.000000 $    & $-10.3\cdot10^6$  & $-10.3\cdot10^6$  & $ \alpha:0.148862 $ & $ x_m:0.000000 $    \\
-Pareto(MLH)     & $-11.6\cdot10^3$ & $-11.6\cdot10^3$ & $\alpha:0.092060 $ & $x_m:0.000000 $    & $-10.3\cdot10^6$  & $-10.3\cdot10^6$  & $ \alpha:0.136193 $ & $ x_m:0.000000 $    \\
-Weibull         & $-14.6\cdot10^3$ & $-14.6\cdot10^3$ & $\alpha:0.319808 $ & $\beta:0.015244 $  & $-11.0\cdot10^6$ & $-11.0\cdot10^6$ & $ \alpha:0.281189 $ & $ \beta:0.000554 $  \\ \hline
+Function		& AIC  & BIC  & \multicolumn{2}{c}{Parameters}  
+				& AIC & BIC  & \multicolumn{2}{c}{Parameters} \\ \hline
 
-				& \multicolumn{4}{c}{skype-pcap}                                        & \multicolumn{4}{l}{bigflows-pcap}                                       \\ \hline
-Cauchy          & $ 21.8\cdot10^3 $  & $21.9\cdot10^3$  & $\gamma:0.000259 $ & $x_0:0.104891 $    & $ 7.2\cdot10^6 $   & $7.2\cdot10^6$   & $ \gamma:1.935833 $ & $x_0:-7.245697 $    \\
-Exponential(LR) & $-4.3\cdot10^3$  & $ -4.3\cdot10^3 $  & \multicolumn{2}{l}{$\lambda:1.861121 $}   & $7.3\cdot10^6$   & $7.3\cdot10^6$   & \multicolumn{2}{l}{$ \lambda:0.009752 $}    \\
-Exponential(Me) & $-1.6\cdot10^3$  & $-1.6\cdot10^3$  & \multicolumn{2}{l}{$\lambda:7.011624 $}   & $-10.9\cdot10^6$ & $-10.9\cdot10^6$ & \multicolumn{2}{l}{$ \lambda:2638.706529 $} \\
-Normal          & $3.3\cdot10^3$   & $3.3\cdot10^3$   & $\mu:0.142620 $    & $\sigma:0.500698 $ & $-9.4\cdot10^6$  & $-9.4\cdot10^6$  & $ \mu:0.000379$     & $ \sigma:0.000660 $ \\
-Pareto(LR)      & $-8.3\cdot10^3$  & $-8.3\cdot10^3$  & $\alpha:0.252367 $ & $x_m:0.000000 $    & $-10.3\cdot10^6$  & $-10.3\cdot10^6$  & $ \alpha:0.148862 $ & $ x_m:0.000000 $    \\
-Pareto(MLH)     & $-11.6\cdot10^3$ & $-11.6\cdot10^3$ & $\alpha:0.092060 $ & $x_m:0.000000 $    & $-10.3\cdot10^6$  & $-10.3\cdot10^6$  & $ \alpha:0.136193 $ & $ x_m:0.000000 $    \\
-Weibull         & $-14.6\cdot10^3$ & $-14.6\cdot10^3$ & $\alpha:0.319808 $ & $\beta:0.015244 $  & $-11.0\cdot10^6$ & $-11.0\cdot10^6$ & $ \alpha:0.281189 $ & $ \beta:0.000554 $  \\ \hline
+				& \multicolumn{4}{c}{skype-pcap}  & \multicolumn{4}{c}{lan-diurnal-pcap}   \\ \hline 
+Cauchy          & $2.18e4$    & $2.19e4$    & $\gamma:2.59e-4$ & $x_0:1.05e-1$    
+				& $-2.85e7$   & $-2.85e7$   & $\gamma:9.63e-3$ & $x_0:-3.61e-3$    \\
+Exponential(LR) & $-1.61e3$   & $-1.60e3$   & \multicolumn{2}{c}{$\lambda:1.86$}   
+				& $1.79e6$    & $1.79e6$    & \multicolumn{2}{c}{$\lambda:8.51e-1$}    \\
+Exponential(Me) & $-4.29e3$   & $-4.28e3$   & \multicolumn{2}{c}{$\lambda:7.01$}   
+				& $-3.12e7$   & $-3.12e7$   & \multicolumn{2}{c}{$ \lambda:58.78$} \\
+Normal          & $3.29e3$    & $3.31e3$    & $\mu:1.43e-1 $    & $\sigma:5.01e-1$ 
+				& $Inf$       & $Inf$       & $\mu:1.70e-2$     & $\sigma:8.56e-2$ \\
+Pareto(LR)      & $-8.28e3$   & $-8.27e3$   & $\alpha:2.52e-1$ & $x_m:5e-8$    
+				& $-4.60e7$   & $-4.60e7$   & $\alpha:2.55e-1$ & $ x_m:5e-8$    \\
+Pareto(MLH)     & $-1.16e4$   & $-1.16e4$   & $\alpha:9.21e-2$ & $x_m:5e-8$    
+				& $-5.03e7$   & $-5.03e7$   & $\alpha:1.15e-1$ & $ x_m:5e-8$    \\
+Weibull         & $-1.46e4$   & $ -1.46e4$  & $\alpha:3.20e-1$ & $\beta:1.52e-2$  
+				& $-5.60e7$   & $-5.60e7$   & $\alpha:3.34e-1$ & $\beta:1.83e-3$  \\ \hline
+
+				& \multicolumn{4}{c}{bigFlows-pcap} & \multicolumn{4}{c}{wan-pcap}  \\ \hline
+Cauchy          & $7.14e6$    & $7.14e6$   & $\gamma:1.94e0$ &$x_0:-7.25$    
+				& $5.99e7$    & $5.99e7$   & $ \gamma:8.28e2$ &$x_0:-4.52e3$    \\
+Exponential(LR) & $7.33e6$    & $7.33e6$   & \multicolumn{2}{c}{$\lambda:1.489e-1$}   
+				& $5.68e7$    & $ 5.68e7$  & \multicolumn{2}{c}{$\lambda:2.2e-5$}   \\
+Exponential(Me) & $-1.09e7$   & $-1.09e7$  & \multicolumn{2}{c}{$\lambda:2.64e3$}   
+				& $-6.58e7$   & $-6.58e7$  & \multicolumn{2}{c}{$\lambda:6.58e5$} \\
+Normal          & $-9.35e6$   & $-9.35e6$  & $\mu:3.79e-4$   &$\sigma:6.60e-4$ 
+				& $-6.39e7$   & $-6.39e7$  & $\mu:2e-6$     & $\sigma:1e-6$ \\
+Pareto(LR)      & $-1.02e7$   & $-1.02e7$  & $\alpha:1.489e-1 $ & $x_m:5e-8 $    
+				& $-5.31e7$   & $-5.31e7$  & $\alpha:NaN$ & $x_m:5e-8 $    \\
+Pareto(MLH)     & $-1.03e7$   & $-1.03e7$  & $\alpha:1.362e-1$ & $x_m:5e-8 $    
+				& $-6.25e7$   & $-6.25e7$  & $\alpha:3.39e-1$ & $x_m:5e-8 $    \\
+Weibull         & $-1.10e7$   & $-1.10e7$  & $\alpha:2.81e-1$ & $\beta:5.54e-4$  
+				& $-5.46e7$   & $-5.46e7$  & $\alpha:7.64e-2$ & $\beta:1e-6$  \\ \hline
 
@@
 
+\begin{figure}[ht!]
+	\centering
+	\label{fig:aproximation-original-cdf-skype}
+	\subfloat[Chauchy]{
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Cauchy}
+	}
+	\subfloat[Exponential(LR)]{
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Exponential(LR)}
+	}
+	\hspace{0mm}
+	\subfloat[Exponential(Me)]{
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Exponential(Me)}
+	}
+	\subfloat[Normal]{
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Normal}
+	}
+	\hspace{0mm}
+	\subfloat[Pareto(LR)]{
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Pareto(LR)}
+	}
+	\subfloat[Pareto(MLH)]{
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Pareto(MLH)}
+	}
+	\hspace{0mm}
+	\subfloat[Weibull]{
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Weibull}
+	}
+	\caption{CDF functions for the approximations of \textit{skype-pcap} inter  packet times, of many stochastic functions.}
+\end{figure}
+
 %%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%
-% BigFlows correlation
+%validation Cost function
 \begin{figure}[ht!]
 	\centering
-\label{fig:correlation-hurst-big-flows-pcap}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/bigFlows_Correlation}
-  \label{correlation-skype-pcap}
+	\label{fig:cost-function}
+	\subfloat[\textit{skype-pcap}]{
+		\includegraphics[width=75mm]{figures/ch4/Skype_costFunction}
+		\label{cost-skype-pcap}
 	}
 	\hspace{0mm}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/bigFlows_Hurst_Exponent}
+	\subfloat[\textit{bigFlows-pcap}]{
+		\includegraphics[width=75mm]{figures/ch4/bigFlows_costFunction}
+		\label{cost-bigFlows-pcap}
 	}
 	\hspace{0mm}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/bigFlows_Mean}
+	\subfloat[\textit{lan-diurnal-pcap}]{
+		\includegraphics[width=75mm]{figures/ch4/Lan_costFunction}
+		\label{cost-lan-pcap}
 	}
 	\hspace{0mm}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/bigFlows_Standard_Deviation}
-  \label{hurst-skype-pcap}
+	\subfloat[\textit{wan-pcap}]{
+		\includegraphics[width=75mm]{figures/ch4/Wan_costFunction}
+		\label{cost-wan-pcap}
 	}
-\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
-\end{figure}
-
-% BigFlows correlation
-\begin{figure}[ht!]
-\centering
-\label{fig:correlation-hurst-big-flows-pcap}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/Skype_QQplot_-_Weibull_dat}
-  \label{correlation-skype-pcap}
-}
-\hspace{0mm}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/Skype_QQplot_-_Cauchy}
-}
-\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
+	\caption{Cost function for each one of the datasets used in this validation process}
 \end{figure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%
-% Logscale bigFlows
-\begin{figure}[ht!]
-\centering
-\subfloat[]{
-  \includegraphics[width=80mm]{figures/ch4/bigFlows_Logscale_-_Exponential_aproximation__mean__vs_Original_set}
-  \label{correlation-skype-pcap}
-}
-%\hspace{0mm}
-\subfloat[]{
-  \includegraphics[width=80mm]{figures/ch4/bigFlows_Logscale_-_Weibull_aproximation_vs_Original_set}
-}
-\label{fig:aproximation-originalbigflows-cdf}
-\end{figure}
-
-On \textit{lan-firewall-pcap}
-
-On \textit{wan-pcap}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-% Prototype results
-%%%%%%%%%%%%%%
-% BigFlows correlation
-\begin{figure}[ht!]
-\centering
-\label{fig:correlation-hurst-big-flows-pcap}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/Skype_costFunction}
-  \label{correlation-skype-pcap}
-}
-\hspace{0mm}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/bigFlows_costFunction}
-}
-\hspace{0mm}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/Lan_costFunction}
-}
-\hspace{0mm}
-\subfloat[]{
-  \includegraphics[width=75mm]{figures/ch4/Wan_costFunction}
-  \label{hurst-skype-pcap}
-}
-\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
-\end{figure}
-
 %%%%%%%%%%%
@@
 
-\begin{algorithm}
+\begin{algorithm}[ht!]
 \caption{calcOnOff}

### 2017-06-09 Docs/Thesis/docs/chapter5.tex
new advancements on the thesis text

\chapter{Proof of Concepts and Validation}

\section{Testbeds}

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.4]{figures/ch5/topo-tree}
	\caption{xxxx}
	\label{fig:topo-tree}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.4]{figures/ch5/topo-simple}
	\caption{xxxx}
	\label{fig:topo-simple}
\end{figure}

\section{Scalling Evaluation}

\section{Packet and Flow Metrics Evaluation}

### 2017-06-13 Docs/Thesis/docs/appendix/appendixB.tex
modification on the thesis text

@@
 \section{CDFs distributions}
+
+The trace \textit{bigflows-pcap} has a much higher inter packet rate, and a smaller dispersion.
+Weibull is the model chosen by AIC/BIC, and it is the second best on correlation and self-similarity (Exponential(Me) and Cauchy are the best respectively).
+Exponential(Me) chooses as the second preferable, has the closest to the original mean and standard deviation.
+Comparing the plots of the CDF function, the Weibull seams to express well both small and larger values of inter packet times, while Exponential(Me) is preciser on the mean values, as we can see at figure ~\ref{fig:aproximation-originalbigflows-cdf}.
 
@@
 	\centering
-	\label{fig:aproximation-original-cdf}
+	\label{fig:qq-bigFlows}
 	\subfloat[Chauchy]{
@@
 	\centering
-	\label{fig:aproximation-original-cdf-lan}
+	\label{fig:qq-lan}
 	\subfloat[Chauchy]{
@@
 	\centering
-	\label{fig:aproximation-original-cdf-wan}
+	\label{fig:qq-wan}
 	\subfloat[Chauchy]{
@@
 	\centering
-	\label{fig:correlation-hurst-bigflows-pcap}
+	\label{fig:correlation-hurst-bigflows}
 	\subfloat[]{
@@
 	\centering
-	\label{fig:correlation-hurst-lan-pcap}
+	\label{fig:correlation-hurst-lan}
 	\subfloat[]{
@@
 	\centering
-	\label{fig:correlation-hurst-wan-pcap}
+	\label{fig:correlation-hurst-wan}
 	\subfloat[]{

### 2017-06-13 Docs/Thesis/docs/chapter2.tex
modification on the thesis text

@@
 
+\begin{figure*}[ht!]
+	\centering
+	\includegraphics[width=0.6\textwidth]{figures/ch2/qqplot-tutorial}
+	\caption{ How information about may be extracted from QQplots.
+Source: "How to interpret a QQ plot" [Online].
+Available: \href{https://stats.stackexchange.com/questions/101274/how-to-interpret-a-qq-plot}{https://stats.stackexchange.com/questions/101274/how-to-interpret-a-qq-plot} [Accessed 09 June 2017]}
+	\label{fig:qqplot-tutorial}
+\end{figure*}
+
+Another way to analyze scalling characteristics is through QQplots.
+QQplot is a visual method to compare sample data with a specific stochastic distribution.
+It orders the sample data values from the smallest to largest, then plots it against the expected value given by the probability distribution function.
+The data sample values appear along the y-axis and the expected values along the x-axis.
+The more linear, the more the data is likely to be expressed by this specific stochastic distribution.
+
+Dependendin on the type of plot, some behavios of the empirical dataset, compared to the theoretical may be observed. In the figure ~\ref{fig:qqplot-tutorial} is presented a sumary.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \item Visual comparison between On time and Off time of the original trace and the stochastic fitting;
-\item QQplots\footnote{
-QQplot is a visual method to compare sample data with a specific stochastic distribution.
-It orders the sample data values from the smallest to largest, then plots it against the expected value given by the probability distribution function.
-The data sample values appear along the y-axis and the expected values along the x-axis.
-The more linear, the more the data is likely to be expressed by this specific stochastic distribution.
-}, which aim to evaluate the correlation between inter-trains duration of real and generated traffic;
+\item QQplots, which aim to evaluate the correlation between inter-trains duration of real and generated traffic;
 \item Measurement of Autocorrelation\footnote{

### 2017-06-13 Docs/Thesis/docs/chapter3.tex
modification on the thesis text

@@
 
-\subsubsection{Packet-level Traffic Generation Operation}
+\subsubsection{Flow Generation Programming}
 
@@
 The implementation of this level should follow the flowchart presented in the figure ~\ref{fig:alg-traffic-engine-config}.
-Down below we present a simplistic code of how the D-ITG API can be used to generate packet-level traffic using our framework.
-A more complex configuration is possible, but it serves to illustrate the procedure.
+Down below we present a simplistic code of how the D-ITG API can be used to generate packet-level traffic.
+We call this concept \textit{Flow Generation Programming} A more complex configuration is possible, but it serves to illustrate the procedure.
 Its API documentation is available at on D-ITG web-site \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}.
@@
 # Operation as a sniffer over a Ethernet interface named <ether-interface> 
-./simitar --sniffer -if <ether-interface> --out/-o <cdt-name>
+./simitar --sniffer --if <ether-interface> --out <cdt-name>
 # Operation as a client using the traffic generator D-ITG, using a list of destination hosts of a text file
@@
 # Operation as a server. just runs D-ITG in the server mode.
-./simitar --server/-sv ditg
+./simitar --server ditg
 

### 2017-06-13 Docs/Thesis/docs/chapter4.tex
modification on the thesis text

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Modeling and Algorithms}\label{ch:modeling-evaluation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Introduction}
+\section{Inter Packet Times Modelling}
+
+\subsection{Introduction}
 
@@
 
-\section{Related Works}
+\subsection{Related Works}
 
@@
 
-\section{Methodology}
+\subsection{Methodology}
 
@@
 
-\subsection{Modelling Inter-Packet times and Packet Sizes}
+\subsection{Methodology}
 
@@
 Now we will give a brief explanation our three procedures: Linear Regression (with the  Gradient descendant algorithm), direct estimation, and maximum likelihood.
-We go deep into details explaining the methods on the appendix ~\ref{ap:revision-probability}, and present the mathematical demonstrations on appendix~\ref{ap:mathematical-modeling}.
+We go deep into details explaining the methods on the appendix ~\ref{ap:revision-probability}, and present the mathematical demonstrations on appendix~\ref{ap:revision-probability}.
 
@@
 
-\section{Results}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-% Prototype results
-\begin{table}[h!]
-\centering
-\caption{Results of the octave prototype, include BIC and AIC values, para estimated parameters for two of our pcap traces: \textit{skype-pcap }and \textit{bigflows-pcap}.
-\textit{bigflows-pcap} is much larger, and has a much much smaller mean inter-packet time}
-\label{tab:prototype-results1}
-\scalebox{0.75}{ 
-\begin{tabular}{lcccccccc}
-\hline
-                & \multicolumn{8}{c}{Trace} \\ \cline{2-9} 
-Function		& AIC  & BIC  & \multicolumn{2}{c}{Parameters}  
-				& AIC & BIC  & \multicolumn{2}{c}{Parameters} \\ \hline
-
-				& \multicolumn{4}{c}{skype-pcap}  & \multicolumn{4}{c}{lan-diurnal-pcap}   \\ \hline 
-Cauchy          & $2.18e4$    & $2.19e4$    & $\gamma:2.59e-4$ & $x_0:1.05e-1$    
-				& $-2.85e7$   & $-2.85e7$   & $\gamma:9.63e-3$ & $x_0:-3.61e-3$    \\
-Exponential(LR) & $-1.61e3$   & $-1.60e3$   & \multicolumn{2}{c}{$\lambda:1.86$}   
-				& $1.79e6$    & $1.79e6$    & \multicolumn{2}{c}{$\lambda:8.51e-1$}    \\
-Exponential(Me) & $-4.29e3$   & $-4.28e3$   & \multicolumn{2}{c}{$\lambda:7.01$}   
-				& $-3.12e7$   & $-3.12e7$   & \multicolumn{2}{c}{$ \lambda:58.78$} \\
-Normal          & $3.29e3$    & $3.31e3$    & $\mu:1.43e-1 $    & $\sigma:5.01e-1$ 
-				& $Inf$       & $Inf$       & $\mu:1.70e-2$     & $\sigma:8.56e-2$ \\
-Pareto(LR)      & $-8.28e3$   & $-8.27e3$   & $\alpha:2.52e-1$ & $x_m:5e-8$    
-				& $-4.60e7$   & $-4.60e7$   & $\alpha:2.55e-1$ & $ x_m:5e-8$    \\
-Pareto(MLH)     & $-1.16e4$   & $-1.16e4$   & $\alpha:9.21e-2$ & $x_m:5e-8$    
-				& $-5.03e7$   & $-5.03e7$   & $\alpha:1.15e-1$ & $ x_m:5e-8$    \\
-Weibull         & $-1.46e4$   & $ -1.46e4$  & $\alpha:3.20e-1$ & $\beta:1.52e-2$  
-				& $-5.60e7$   & $-5.60e7$   & $\alpha:3.34e-1$ & $\beta:1.83e-3$  \\ \hline
-
-				& \multicolumn{4}{c}{bigFlows-pcap} & \multicolumn{4}{c}{wan-pcap}  \\ \hline
-Cauchy          & $7.14e6$    & $7.14e6$   & $\gamma:1.94e0$ &$x_0:-7.25$    
-				& $5.99e7$    & $5.99e7$   & $ \gamma:8.28e2$ &$x_0:-4.52e3$    \\
-Exponential(LR) & $7.33e6$    & $7.33e6$   & \multicolumn{2}{c}{$\lambda:1.489e-1$}   
-				& $5.68e7$    & $ 5.68e7$  & \multicolumn{2}{c}{$\lambda:2.2e-5$}   \\
-Exponential(Me) & $-1.09e7$   & $-1.09e7$  & \multicolumn{2}{c}{$\lambda:2.64e3$}   
-				& $-6.58e7$   & $-6.58e7$  & \multicolumn{2}{c}{$\lambda:6.58e5$} \\
-Normal          & $-9.35e6$   & $-9.35e6$  & $\mu:3.79e-4$   &$\sigma:6.60e-4$ 
-				& $-6.39e7$   & $-6.39e7$  & $\mu:2e-6$     & $\sigma:1e-6$ \\
-Pareto(LR)      & $-1.02e7$   & $-1.02e7$  & $\alpha:1.489e-1 $ & $x_m:5e-8 $    
-				& $-5.31e7$   & $-5.31e7$  & $\alpha:NaN$ & $x_m:5e-8 $    \\
-Pareto(MLH)     & $-1.03e7$   & $-1.03e7$  & $\alpha:1.362e-1$ & $x_m:5e-8 $    
-				& $-6.25e7$   & $-6.25e7$  & $\alpha:3.39e-1$ & $x_m:5e-8 $    \\
-Weibull         & $-1.10e7$   & $-1.10e7$  & $\alpha:2.81e-1$ & $\beta:5.54e-4$  
-				& $-5.46e7$   & $-5.46e7$  & $\alpha:7.64e-2$ & $\beta:1e-6$  \\ \hline
-
-\end{tabular}
-}
-\end{table}
+\subsection{Results}
 
@@
 % Logscale Skype
-
 \begin{figure}[ht!]
@@
 	\centering
-	\label{fig:aproximation-original-cdf-skype}
+	\label{fig:qq-skype}
 	\subfloat[Chauchy]{
@@
 	\subfloat[Exponential(LR)]{
-		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Exponential(LR)}
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Exponential_LR}
 	}
@@
 	\subfloat[Exponential(Me)]{
-		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Exponential(Me)}
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Exponential_Me}
 	}
@@
 	\subfloat[Pareto(LR)]{
-		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Pareto(LR)}
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Pareto_LR}
 	}
 	\subfloat[Pareto(MLH)]{
-		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Pareto(MLH)}
+		\includegraphics[width=78mm]{figures/ch4/skype_QQplot_-_Pareto_MLH}
 	}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%
+% Prototype results
+\begin{table}[h!]
+	\centering
+	\caption{Results of the octave prototype, include BIC and AIC values, para estimated parameters for two of our pcap traces: \textit{skype-pcap }and \textit{bigflows-pcap}.
+\textit{bigflows-pcap} is much larger, and has a much much smaller mean inter-packet time}
+	\label{tab:prototype-results}
+	\scalebox{0.75}{ 
+		\begin{tabular}{lcccccccc}
+			\hline
+			& \multicolumn{8}{c}{Trace} \\ \cline{2-9} 
+			Function		& AIC  & BIC  & \multicolumn{2}{c}{Parameters}  
+			& AIC & BIC  & \multicolumn{2}{c}{Parameters} \\ \hline
+
+			& \multicolumn{4}{c}{skype-pcap}  & \multicolumn{4}{c}{lan-diurnal-pcap}   \\ \hline 
+			Cauchy          & $2.18e4$    & $2.19e4$    & $\gamma:2.59e-4$ & $x_0:1.05e-1$    
+			& $-2.85e7$   & $-2.85e7$   & $\gamma:9.63e-3$ & $x_0:-3.61e-3$    \\
+			Exponential(LR) & $-1.61e3$   & $-1.60e3$   & \multicolumn{2}{c}{$\lambda:1.86$}   
+			& $1.79e6$    & $1.79e6$    & \multicolumn{2}{c}{$\lambda:8.51e-1$}    \\
+			Exponential(Me) & $-4.29e3$   & $-4.28e3$   & \multicolumn{2}{c}{$\lambda:7.01$}   
+			& $-3.12e7$   & $-3.12e7$   & \multicolumn{2}{c}{$ \lambda:58.78$} \\
+			Normal          & $3.29e3$    & $3.31e3$    & $\mu:1.43e-1 $    & $\sigma:5.01e-1$ 
+			& $Inf$       & $Inf$       & $\mu:1.70e-2$     & $\sigma:8.56e-2$ \\
+			Pareto(LR)      & $-8.28e3$   & $-8.27e3$   & $\alpha:2.52e-1$ & $x_m:5e-8$    
+			& $-4.60e7$   & $-4.60e7$   & $\alpha:2.55e-1$ & $ x_m:5e-8$    \\
+			Pareto(MLH)     & $-1.16e4$   & $-1.16e4$   & $\alpha:9.21e-2$ & $x_m:5e-8$    
+			& $-5.03e7$   & $-5.03e7$   & $\alpha:1.15e-1$ & $ x_m:5e-8$    \\
+			Weibull         & $-1.46e4$   & $ -1.46e4$  & $\alpha:3.20e-1$ & $\beta:1.52e-2$  
+			& $-5.60e7$   & $-5.60e7$   & $\alpha:3.34e-1$ & $\beta:1.83e-3$  \\ \hline	
+			& \multicolumn{4}{c}{bigFlows-pcap} & \multicolumn{4}{c}{wan-pcap}  \\ \hline
+			Cauchy          & $7.14e6$    & $7.14e6$   & $\gamma:1.94e0$ &$x_0:-7.25$    
+			& $5.99e7$    & $5.99e7$   & $ \gamma:8.28e2$ &$x_0:-4.52e3$    \\
+			Exponential(LR) & $7.33e6$    & $7.33e6$   & \multicolumn{2}{c}{$\lambda:1.489e-1$}   
+			& $5.68e7$    & $ 5.68e7$  & \multicolumn{2}{c}{$\lambda:2.2e-5$}   \\
+			Exponential(Me) & $-1.09e7$   & $-1.09e7$  & \multicolumn{2}{c}{$\lambda:2.64e3$}   
+			& $-6.58e7$   & $-6.58e7$  & \multicolumn{2}{c}{$\lambda:6.58e5$} \\
+			Normal          & $-9.35e6$   & $-9.35e6$  & $\mu:3.79e-4$   &$\sigma:6.60e-4$ 
+			& $-6.39e7$   & $-6.39e7$  & $\mu:2e-6$     & $\sigma:1e-6$ \\
+			Pareto(LR)      & $-1.02e7$   & $-1.02e7$  & $\alpha:1.489e-1 $ & $x_m:5e-8 $    
+			& $-5.31e7$   & $-5.31e7$  & $\alpha:NaN$ & $x_m:5e-8 $    \\
+			Pareto(MLH)     & $-1.03e7$   & $-1.03e7$  & $\alpha:1.362e-1$ & $x_m:5e-8 $    
+			& $-6.25e7$   & $-6.25e7$  & $\alpha:3.39e-1$ & $x_m:5e-8 $    \\
+			Weibull         & $-1.10e7$   & $-1.10e7$  & $\alpha:2.81e-1$ & $\beta:5.54e-4$  
+			& $-5.46e7$   & $-5.46e7$  & $\alpha:7.64e-2$ & $\beta:1e-6$  \\ \hline
+		\end{tabular}
+	}
+\end{table}
+
+Here in this chapter we only discuss the plots achived obtained by the pcap \textit{skype-pcap} for simplicity.
+The other plots are provided and commented on the appendix ~\ref{ap:aditional-plots}.
+In the figure ~\ref{fig:aproximation-original-cdf} we present all estimated CDF functions along with the empirical CDF, for the trace \textit{skype-pcap}.
+They are on logscale, wich provide a better visualization for small time scales.
+In the case of the normal function, all values smaller than zero, were set to zero on the plot.
+Is possible to see different accuracies and types of fittings on each plot.
+Visually, the best fit seems to be the Weibull trough linear regression.
+
+Analyzing the plots, and what they would mean, our Cauchy fitting would impose an almost contant traffic , with the inter packet time close to the mean.
+On the trace \textit{skype-pcap} the exponential plots seems to not represent well the small values of inter packet times.
+This is due fact that an exponential process is good at representing values close to the mean.
+But, it fails to represent values too small and higher.
+On the other hand, a self-similar process like Weibull and Pareto are better representing inter packet times with higher dispersion.
+Pareto(MLH) has a slow convergence, wich means this distribution may genarate values of inter-packet times too large.
+
+Analyzing the QQplots, we may observe that in most of the distribution, the samples (original data) has a much havier-tail effect than in the estimated data.
+This is verified by the almost blue horizontal lines formed by the "exes".
+But, the Weibull distribution follow much closer the original data.
+Also is possible to see that the sample has a right skew compared to the estimation on Exponential(LR), Exponential(Me), Normal, and Pareto(MLH).
+This means that this estimation would not represent so well small values of time in this case.
+On the other hand, Pareto(LR) and Weibull would not suffer from this problem.
+
+The results for the AIC, BIC and parameters of all four traces are at the table~\ref{tab:prototype-results1}.
+The results for \textit{wan-pcap} and \textit{lan-diurnal-pcap} are on the table ~\ref{tab:prototype-results}.
+The difference between BIC and AIC values in all simulations are very small.
+Much smaller then the difference between its values between the distributions.
+This is an indication that for inter packet times, using AIC or BIC should will not influence significantly the results.
+
+On our previsions, Weibull and Pareto(MLH and LR) are the best options.
+This was expected, since both are heavy-tailed functions.
+But, Cauchy, on most of the tests, even being a heavy-tailed distribution seems to no present a good fitting.
+This is effect of the fast divergence of tangent function, when we linearize our data.
+
+Analyzing the quality of AIC and BIC as criterion of choose on \textit{skype-pcap},based on the results form figure ~\ref{fig:correlation-hurst-skype-pcap} we see that in therms of Correlation and Self-similarity it picket the right model: Weibull.
+Also in therms of mean packet rate and dispersion it is still one of the best choises (along with Exponential(Me), Pareto(LR) and Cauchy).
+The third and the fourth choices (Pareto(LR)) and Exponential(LR) also are good options in most of these metrics.
+But, Pareto(MLH) is presented as the second best choice, and it had poor results in comparison to the others, especially on mean, correlation and dispersion.
+
+All these results are abstracted by the cost function $J$.
+As we can see, on all pcaps, the best function selected by BI and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.
+
+Another important observation is the fact that exponential function was able to provide the best fitting for the \textit{wan-pcap}.
+The reasons for this behavior are both result of a much intense traffic with no long-range gaps, and the precision of the measurement.
+
 %%%%%%%%%%%%%%
-% Skype correlation
+% Skype correlation, Hurst, Mean Standard Deviation
 \begin{figure}[h!]
 	\centering
-\label{fig:correlation-hurst-skype-pcap}
 	\subfloat[Correlation]{
 		\includegraphics[width=75mm]{figures/ch4/Skype_Correlation}
-  \label{correlation-skype-pcap}
+		\label{correlation-skype}
 	}
@@
 		\includegraphics[width=75mm]{figures/ch4/Skype_Hurst_Exponent}
+		\label{hurst-skype}
 	}
@@
 		\includegraphics[width=75mm]{figures/ch4/Skype_Mean}
+		\label{mean-skype}
 	}
@@
 		\includegraphics[width=75mm]{figures/ch4/Skype_Standard_Deviation}
-  \label{hurst-skype-pcap}
+		\label{std-skype}
 	}
 	\caption{Statistical parameters of \textit{skype-pcap} and its approximations}
+	\label{fig:correlation-hurst-skype-pcap}
 \end{figure}
@@
 	\centering
-	\label{fig:cost-function}
 	\subfloat[\textit{skype-pcap}]{
@@
 	\caption{Cost function for each one of the datasets used in this validation process}
+	\label{fig:cost-function}
 \end{figure}
 
-The results for the parameters estimation and AIC and BIC for \textit{skype-pcap} and \textit{bigflows-pcap} are at the table~\ref{tab:prototype-results1}.
-The results for \textit{wan-pcap} and \textit{lan-diurnal-pcap} are on the table ~\ref{tab:prototype-results2}.
-The difference between the values of BIC and AIC in all simulations were very small.
-Much smaller then the difference between the values found for each distribution.
-This is an indication that for our type of dataset, using AIC or BIC should will not influence significantly the results.
+\subsection{Conclusion}
 
-On our previsions, Weibull followed Pareto are the functions more indicated as good options.
-This was expected, since both are heavy-tailed functions.
-But, Cauchy, on most of the tests, seems to no present a good fitting.
-This is effect of the fast divergence of tangent function, when we linearize our data.
-Not letting the CDF values be so close to zero or avoided divergence, but still through linear regression the penalty was heavy.
+Also the order of the stochastic function tend to not differ much. We are able to conclude that using AIC or BIC as criteria for choosing models for inter-packet times is a good choise.
 
-In the figure ~\ref{fig:aproximation-original-cdf} we present all estimated CDF functions along with the empirical CDF, for the trace \textit{skype-pcap}.
-In the case of the normal function, all values smaller than zero, were set to zero on the plot.
-Is possible to see different accuracies on each plot, and types of fittings.
-Visually, the best fit seems to be the Weibull trough linear regression.
-In the figure ~\ref{fig:aproximation-originalbigflows-cdf} we present the fittings with higher BIC and AIC values for the \textit{bigflows-pcap}.
-On our previsions.
-Analyzing the plots, and what they would mean, our Cauchy fitting would impose an almost contant traffic , with the inter packet time close to the mean.
-On the trace \textit{skype-pcap} the exponential plots seems to not represent well the small values of inter packet times.
-On the other hand, on \textit{bigflows-pcap} they are expressed much well.
-This is due fact that an exponential process is good at representing values close to the mean.
-But, it fails to represent values too small and too higher.
-The \textit{bigflows-pcap}  has a much smaller dispersion.
-On the other hand, a self-similar process like Weibull and Pareto are better representing inter packet times with higher dispersion.
+Also, except by the Pareto function modeled using the Maximum likelyhood method, have comparative results between the simulations and the AIC/BIC gess.
+The best fittings according to the AIC/BIC usually  returned very acurate models, with close mean and fractal level, and correlation close to one.
+The models selected as the worsts usually returned poor results.
 
-Analyzing the quality of AIC and BIC as criterion of choose on \textit{skype-pcap}, we see that in therms of Correlation and Self-similarity it picket the right model: Weibull.
-Also in therms of mean packet rate and dispersion, is still a good choice, since it is still one of the best choices.
-The third and the fourth choices (Pareto(LR)) and Exponential(LR) also are good options in most of these metrics.
-But, Pareto(MLH) is presented as the second best choice, and it had poor results in comparison to the others, especially on mean, correlation and dispersion.
-In this example, we illustrate it at the table ~\ref{tab:skype-evaluation}.
+Also, it is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurante fitting, what justify the application of the criteria in all new experiment.
 
-The trace \textit{bigflows-pcap} has a much higher inter packet rate, and a smaller dispersion.
-Weibull is the model chosen by AIC/BIC, and it is the second best on correlation and self-similarity (Exponential(Me) and Cauchy are the best respectively).
-Exponential(Me) chooses as the second preferable, has the closest to the original mean and standard deviation.
-Comparing the plots of the CDF function, the Weibull seams to express well both small and larger values of inter packet times, while Exponential(Me) is preciser on the mean values, as we can see at figure ~\ref{fig:aproximation-originalbigflows-cdf}.
+We do not rely on only one type of parametrization.
+This turns our methodology more robust, since a linear regression may diverge.
+But aways there will be an packable model, since our estimations for Normal, Exponential(Me) and Pareto(MLH) cannot.
+Models wich the linear regression diverge, will not have god BIC/AIC estimations, and will not be pickedas primary options.
 
-%%%%%%%%%%%
+\section{Others Algorithms and Methods}
 
-%\begin{figure}[ht!]
-%\centering
-%\subfloat[]{
-%  \includegraphics[width=80mm]{figures4/Skype_QQplot_-_Cauchy}
-%  \label{correlation-skype-pcap}
-%}
-%\hspace{0mm}
-%\subfloat[]{
-%  \includegraphics[width=80mm]{figures4/Skype_QQplot_-_Weibull_dat}
-%}
-%\label{correlation-hurst-skype-pcap}
-%\end{figure}
-
-\section{Others Algorithms}
+In this section we breef present another methods used by the \textit{TraceAnalyzer} component.
+The first to calculate the session ON and OFF times.
+The second classify applications based on its tranport protocol and ports.
 
@@
 	\caption{calcOnOff}
+	\label{alg:calcOnOff}
 	\begin{algorithmic}[1]
+		\small
 		\Function{calcOnOff}{$arrivalTime, deltaTime, cutTime, minOnTime$}%\Comment{Where A - array, p - left, q - middle, r - right}
@@
 		\State $fileSizeSum = fileSizeSum + psSizeList[i, 1]$
+		\If{$deltaTime[i] > cutTime$} 
 		\If{$i == 1$} \Comment{if the first is session-off time}
@@
 		\EndIf 
+		\EndIf       
 		\EndFor
@@
 
+We developed an algorithms to calculate the times between the ON and OFF times of the \textit{files}, and the number of packets and bytes as well.
+It uses a list of packet arrival times(relative to the first), time between packets and packet sizes.
+It defines a minimum time of ON acceptable.
+This times is used for two reasons:
+
+\begin{itemize}
+\item In case of a \textit{file} of just one packet, it will not produce a On time of zero
+\item It avoid a \textit{file} On time too small, wich may be less than acceptable for packet generator tools.
+\end{itemize}
+
+As explained in the previous chapter, a \textit{file} is defined by a large OFF time, we call $cutTime$.
+If a inter packet $deltaTime$ time is larger than the $cutTime$ it defines an OFF time, and the ON time is calculated base on the last OFF time recorded.
+If the first $deltaTime$ defines an OFF time, or if it is the first ON time, its calculation is threated separetely.
+In the last ON time, it is not defined by an OFF time, so we deal with it after the loop.
+It keep counters to calc the number of bytes and packets within every defined ON time.
+It returns four vectors: $onTimes$, $offTimes$, $pktCounter$ and $fileSize$.
+Letting $n$ be the size of $onTimes$,  $offTimes$ has a size $n - 1$.
+The algorithm is presented in the Alforithm~\ref{alg:calcOnOff}.
+
 \subsection{Application classification}
 
-\begin{table}[]
+We also developed an simple test to guess the application protocol, based on the port numbers and the tranport protocol used by each flow.
+We currently are classifing the application protocols presented in the table ~\ref{tab:application-protocols}.
+If a flow matches the port number, and the transport protocol, it is classified as belongig to an application protocol.
+
+\begin{table}[h!]
 \centering
 \caption{Application classification table}
-\label{my-label}
+\label{tab:application-protocols}
 \begin{tabular}{lll}
@@
 
-\section{Implementation Details}
+%\section{Implementation Details}
 
-\subsection{Modeling Process}
+%\subsection{Modeling Process}
 
-\subsection{Matlab prototyping and C++ Implementation}
+%\subsection{Matlab prototyping and C++ Implementation}
 
-\subsection{Software Engineering process and Lessons Leaned}
+%\subsection{Software Engineering process and Lessons Leaned}
 
-\section{Conclusion}
+%\section{Conclusion}
 
-We can conclude by this evaluation, that our chosen methodology for selecting stochastic models for inter packet data is appropriated. The first thing to observe is that, for a high
+%We can conclude by this evaluation, that our chosen methodology for selecting stochastic models for inter packet data is appropriated. The first thing to observe is that, for a high
 
-First, we do not rely on only one type of parametrization.
+%First, we do not rely on only one type of parametrization.
 This turns our methodology more robust, since a linear regression may diverge.

### 2017-06-13 Docs/Thesis/docs/chapter5.tex
modification on the thesis text

@@
 
-\section{Testbeds}
+\section{Emulated Testbeds}
+
+As first proof of concepts for our tool, we are going to use Mininet's emulated testbeds.
+These tests are easily implemented and reproduced, and are able to test the performance of our tool, without kernel and hardware overheads.
+Tests in a physical testbeds, and real network functions stays for future work.
+
+This first testbed is a tree topology, and represents tests performed by Swing\cite{swing-paper} found on the literature \cite{background-traffic-matter}\cite{legotg-paper}.
+The second is much simples, and is just a one hop connection of two hosts.
+Both topologies are SDN neworks, and have OpenDayLight Beryllium as controller.
+
+All the traffic is generated by the host \textit{h1} with IPv4 address 10.0.0.1.
+The traffic will to be captured form the host interface with TCPdump in a pcap format, and just the outgoing traffic will be considered.
+Any response packet form the hosts will be ignorated, since we want to evaluate just the traffic generated by the host, as it were a replay engine, such as TCPreplay or TCPivo\cite{tcpivo-paper}
 
@@
 	\includegraphics[scale=0.4]{figures/ch5/topo-tree}
-	\caption{xxxx}
+	\caption{Tree SDN topology emulated by mininet, and controlled by OpenDayLight Beryllium}
 	\label{fig:topo-tree}
@@
 	\includegraphics[scale=0.4]{figures/ch5/topo-simple}
-	\caption{xxxx}
+	\caption{Single hop SDN topology emulated by mininet, and controlled by OpenDayLight Beryllium}
 	\label{fig:topo-simple}
@@
 
+All Python scripts used to create the scenarios, the Shell Scripts used to automate the tests and capture the traffic, and the Octave scripts to perform all the calculations are available on Github\footnote{\textcolor{red}{github-link}}.
+To start running the tests, following the tutorial on Github, you should not take more than 10 minutes.
+
+We will perform this testes using SIMITAR \textit{alpha} version, operation as a client on host \textit{h1}, and as a server on all other hosts.
+As traffic generator engine, we will use D-ITG and Iperf.
+The operation as a packet injector using Libtins is still unther implementation.
+
 \section{Scalling Evaluation}
 
+To evaluate the Scalling profile of the traccic generator, we are usig the same validation used for Swing\cite{swing-paper}: multiresolution energy analysis.
+
 \section{Packet and Flow Metrics Evaluation}

### 2017-06-13 Docs/Thesis/docs/chapter6.tex
new advancements on the thesis text
modification on the thesis text

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{Conclusion and Future Work}
 \label{ch:conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\subsection{Melhorando resultados}
+In this section we present some ideas for future works and implementation for SIMITAR.
+On the first section "Improoving results", we suggest approaches for improving the current results.
+They include calibration of some constants, finer controll of packet injection, and performance improovments.
 
-\subsection{Calibração das ferramentas}
+\subsection{Improoving results}
+
+\subsubsection{Tool calibration}
+
+To imprrove our results, one aproach can be a perform  a deeper study on how calibrate each tool, depending on themain porpose.
+It can be done first adjusting some parameters and constants of our algorithms and procedures, wich may affect the performance.
+Some parameters will change the performance  of the tools that support stochastic functions for inter pacekt times:
+
+\begin{itemize}
+
+	\item \texttt{DataProcessor::minimumAmountOfPackets}: we just estimate stochastic models for inter-packet times, if the number of flow packets is larger then it.
+If it is smaller, we just apply the constant model, because with a small sample, the acuracy of any model is poor.
+Today its value is set to 30.
+
+	\item \texttt{DataProcessor::min\_time}: minimum time considered on inter packet times.
+This is used to avoid inter packet times equals to zero, due the sniffer resolution.
+This may change the fitting acuracy, wich may change the performance of tools wich use inter-packet time models.
+Today, this value is $5e-8$.
+
+\end{itemize}
+
+Others parameters and change of approaches may change the performance for any type of underlying tools or API. They are:
+
+\begin{itemize}
+
+	\item \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have.
+This value we can change de precission of the generated traffic.
+Currently this value is $0.1$s.
+
+	\item \texttt{DataProcessor::m\_session\_cut\_time}:  this member is responsible for defining whaterver a file transfecence still active or has ended. It defines the minimum OFF timme acceptable.
+
+	\item \textit{Control a minimum number of pacekts required for a flow be created}: This would reduce the number of flows created.
+Since each flow is menaged by a different thread, it can imporrove the performance, reducing overheads.
+This action should not heavely impact negativally on the throughtput and scalling characteristics, but can increase the precision of the most significant flows.
+This apply for all underlying traffic-gen engines.
+
+\end{itemize}
 
@@
 
-\subsection{Melhorar Modelagem}
-\subsubsection{Machine learning classification de aplicações}
-\subsubsection{Modelagem de payload}
-usando payloads pre-definidos em strings
-\subsubsection{Modelagem de de windows size, e flags tcp}
+\subsubsection{SIMITAR as a Packet Injector}
 
-\subsection{Improoving performance}
+This proposed functionality is still unther implementation, and we are using Libtins API\footnote{\href{http://libtins.github.io/}{http://libtins.github.io/}}.
+It enable packet crafting and injection at a reasonable performance, adn provide support for many protocols.
+It is not thread safe, so will require some cares, such as use of mutexes.
+But will enable a finer controll of packet header contents, packet size, inter packet times and number of pacekts sent.
+In that way, we expect to achieve better results.
 
-\subsubsection{Improving database storage}
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[height=2.0in]{figures/ch6/libtins-flow}
+	\caption{Expansion of SIMITAR using Libtins for traffic generation}
+	\label{fig:libtins-flow}
+\end{figure}
 
-basicamente eu vou aqui propor um novo modelo de database mais eficiente, no qual menos dados serão arnmazenados
+\subsubsection{Traffic generation performance}
+
+\begin{figure}[h!]
+	\centering
+	\subfloat[DpdkFlow]{
+		\includegraphics[height=2.0in]{figures/ch6/dpdk-flow}
+		\label{fig:dpdk-flow}
+	}
+	\hspace{0mm}
+	\subfloat[DpdkInterface]{
+		\includegraphics[height=2.0in]{figures/ch6/dpdk-interface}
+		\label{fig:dpdk-if}
+	}
+	\caption{Class diagram for DPDK support expansions. On (a), we have a implementation of traffic generation based on DPDK. On (b) we are using DPDK KNI interfaces.}
+	\label{fig:DpdkFlow}
+\end{figure}
+
+Some aproaches may be taken to improove the traffic generation performance.
+One possibility is use DPDK KNI interfaces \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}.
+The The DPDK Kernel NIC Interface (KNI) allow applications from the users apace interact with DPDK ports.
+In this way we may achieve a faster packet processing.
+
+Another poossibility is use DPDK API craft packets.
+Using a low level library such for packet generation, we will be able to custom generate packetes, and bypass the Linux network stack (packet acceleration).
+We present in the figure ~\ref{fig:DpdkFlow} how we could expand our tool to implement an packet generator based on DPDK.
+
+\subsubsection{Thread Menager}
+
+Instead of each flow thread controll individually each sleep and waken times, a better approach would be a separed thread controll and manage all the other thereads life-cycle operation.
 
@@
 
-\subsubsection{Sniffer baseado em SDN Switch}
-Isso mudaria o tipo de dado adiquirido, porém os algorítimos implementados ainda poderiam ser utilizados, já que eles trabalham com qualquer tipo de dado.
-Haveriam mudanças em como eles seriam tratados pelo data processor
+\subsection{Further Implementations}
 
-\subsubsection{Implementação}
+\begin{itemize}
+	\item \textbf{C++ Sniffer}: Implementing the Sniffer and its SQL queries in C++ should increace its performance.
 
-- Sniffer em C++ para melhorar a performance
-- Network Trace com uma API em Python
+	\item \textbf{Use OpenDayLight REST API for data collection}: Another different approach for data collection ould be use the OpenDayLight REST API to collect data from a SDN OpenFlow switch, instead of a Sniffer.
+Using the REST API it is possible to stract many statistics from nodes, hosts and ports, such active flows, number of packets matched per flows, packet dopeds, and so on.
+But, in this case, different featutres would be measured, what would require a development of a new model for traffic generation.
+On the other hand, many precedures could be reused.
 
-\subsubsection{Kernel bypass usando o DPDK}
+	\item \textbf{SIMITAR Python API}: Currently, SIMITAR only enable the programming of flow traffic generation in C++.
+Adding Python support for reading NetwrokTrace and NetworkFlow objects would enalbe an easy expantion using Python traffic generation API, without the  need for creating "C++" wrappers.
 
-Automatizar a criação de KKNI interfaces pelo FlowGenerator, o que possibilitaria kernel bypass na geração do trafego, melhorando a performance
+	\item \textbf{Expand SIMITAR}: Expand the SIMITAR support for many other traffic generator tools and APIs, such as MoonGen LUA API, Ostinato Python API, Seagull traffic generator, and many others.
 
-\subsection{Novos trabalhos}
+		\begin{figure}[!ht]
+			\centering
+			\includegraphics[height=2.0in]{figures/ch6/pcap-gen}
+			\caption{Using SIMITAR for generation synthetic \textit{pcap} files, CTD files: a component schema}
+			\label{fig:pcap-gen}
+		\end{figure}
 
-\subsubsection{PcapGen}
+	\item \textbf{PcapGen: a compact \textit{pcap} lybrary}: This idea reffers to create a component capable of generate synthetic \textit{pcap} files, using Compact Trace Descriptors.
+This can be implemented using SIMITAR as a packet injector, but in an emulated host interface, using Mininet.
+Then, the traffic could be collected, using a tool such as TCPDump or Tshark.
+We present a diagram of this idea in the figure ~\ref{fig:pcap-gen}.
+This would enable SIMITAR works as trace lybrary for pcap-based benchmark tools.
 
-Mininet+TCPdump+LibtinsFlow=> possibilidade de captura de trafego gerado em uma interface virtual, gerando portante traces sintéticos.
-Isso possibilitaria a criação de uma biblioteca de traces, para aplicações de banchmark como o NFPA.
+	% Oferecer a possibilidade de automatização de medições e testes extendendo a ferramenta
 
-\subsubsection{Extender para novas ferramentas e bibliotecas}
+	% usar redes neurais para classificação de aplicações
 
-Ampliar para o moongen, ostinato, Seagull, NetFPGA, etc
-
-\subsection{Benchmarking}
-
-Oferecer a possibilidade de automatização de medições e testes extendendo a ferramenta
-
-\section{Software Engineering process and Lessons Leaned}
-
-\section{Conclusion}
+\end{itemize}

### 2017-06-13 Docs/Thesis/docs/chapter6.tex
d

@@
 
+%2nd review
 In this section we present some ideas for future works and implementation for SIMITAR.
-On the first section "Improoving results", we suggest approaches for improving the current results.
-They include calibration of some constants, finer controll of packet injection, and performance improovments.
+On the first section "improving results" we point some approaches for improving the current results.
+They include calibration of constants, finer control of packet injection, and performance improvement.
 
-\subsection{Improoving results}
+\subsection{Improving results}
 
@@
 
-	\item \texttt{DataProcessor::m\_session\_cut\_time}:  this member is responsible for defining whaterver a file transfecence still active or has ended. It defines the minimum OFF timme acceptable.
+	\item \texttt{DataProcessor::m\_session\_cut\_time}:  this member is responsible for defining whaterver a file transfecence still active or has ended. Baically it define the ON and OFF times.
 

### 2017-06-13 Docs/Thesis/docs/chapter6.tex
improving english, and corrections

--- 2017-06-06 Docs/Thesis/docs/chapter6.tex
@@
 
-\subsection{Melhorando resultados}
+In this section we present some ideas for future works and implementation for SIMITAR.
+On the first section "Improoving results", we suggest approaches for improving the current results.
+They include calibration of some constants, finer controll of packet injection, and performance improovments.
 
-\subsection{Calibração das ferramentas}
+\subsection{Improoving results}
 
-Para extensão do trafego gerado, é necessário um estudo da melhor calibração para cada ferramente, como o D-ITG, Iperf, Libtins, o que pode melhorar os resultados
+\subsubsection{Tool calibration}
 
-\subsection{Melhorar Modelagem}
-\subsubsection{Machine learning classification de aplicações}
-\subsubsection{Modelagem de payload}
-usando payloads pre-definidos em strings
-\subsubsection{Modelagem de de windows size, e flags tcp}
+To improve our results, the first approach is performing a deeper study on calibrating each tool, to achieve the best results possible.
+We can do this first adjusting some constants used by our algorithms.
+Some of these values will change the performance not for all but on tools that support stochastic functions for inter packet times.
+They are:
 
-\subsection{Improoving performance}
+\begin{itemize}
+	\item \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of flow packets is larger than this value.
+If it is smaller, we use only the constant model, for two reasons.
+First, because with a small sample, the accuracy estimate stochastic model is poor.
+Second, because we avoid the parameterization process, which can be costly in the case of linear regression.
+Its value today is set to 30.increasing this value, we may achieve a more reasonable performance for individual flows.
+	\item \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times.
+We use this value to avoid inter-packet times equals to zero due to the sniffer resolution.
+In that case, some of our procedures would diverge.
+It can change the fitting accuracy.
+Today, this value is $5e-8$.
+\end{itemize}
 
-\subsubsection{Improving database storage}
+The modification of others  constants or approaches may change the performance for any type of underlying tool or API. They are:
 
-basicamente eu vou aqui propor um novo modelo de database mais eficiente, no qual menos dados serão arnmazenados
+\begin{itemize}
 
-\subsubsection{Improving DataProcessor Performance}
+	\item \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have.
+This value  can change the precision of the generated traffic.
+Currently this value is $0.1$s.
 
-Melhorar os algoritimos adicionando técnicas adicionais de modelagem, como condição de parada para o algoritimo gradient descendent, stochastic gradient descendent, entre outros
+	\item \texttt{DataProcessor::m\_session\_cut\_time}: this member defines whatever a file transference still active or has ended.
+It defines the smallest OFF time acceptable.
+This value will change how many files SIMITAR will transfer per flow, and how many times it will call the underlying traffic generator.
+This constant may affect both computational performance and traffic realism.
 
-\subsubsection{Sniffer baseado em SDN Switch}
-Isso mudaria o tipo de dado adiquirido, porém os algorítimos implementados ainda poderiam ser utilizados, já que eles trabalham com qualquer tipo de dado.
-Haveriam mudanças em como eles seriam tratados pelo data processor
+	\item \textit{Control a minimum number of packets required for SIMITAR create a new flow}: This would reduce the number of flows created, improving its computational performance.
+Since SIMITAR manages each flow in a  different thread, it will create fewer threads, reducing overheads.
+This action should not impact  on throughput and scaling characteristics because few packets would be ignored.
+But it can increase the precision of the most significant flows since all the threads are competing each other on the Operational System.
+But, the number of flows created would be smaller.
 
-\subsubsection{Implementação}
+\end{itemize}
 
-- Sniffer em C++ para melhorar a performance
-- Network Trace com uma API em Python
+% Para extensão do trafego gerado, é necessário um estudo da melhor calibração para cada ferramente, como o D-ITG, Iperf, Libtins, o que pode melhorar os resultados
 
-\subsubsection{Kernel bypass usando o DPDK}
+\subsubsection{SIMITAR as a Packet Injector}
 
-Automatizar a criação de KKNI interfaces pelo FlowGenerator, o que possibilitaria kernel bypass na geração do trafego, melhorando a performance
+This proposed functionality is still under implementation, and we are using Libtins API \footnote{\href{http://libtins.github.io/}{http://libtins.github.io/}}.
+It enables packet crafting and injection at a reasonable performance, and provide support for many protocols.
+It is not threaded safe, so will require some cars, such as the use of mutexes.
+But will enable a finer control of packet header contents, packet sizes, inter-packet times and a number of packets sent.
+In that way, we expect to achieve better results in terms of realism.
 
-\subsection{Novos trabalhos}
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[height=2.0in]{figures/ch6/libtins-flow}
+	\caption{Expansion of SIMITAR using Libtins for traffic generation}
+	\label{fig:libtins-flow}
+\end{figure}
 
-\subsubsection{PcapGen}
+\subsubsection{Traffic generation performance}
 
-Mininet+TCPdump+LibtinsFlow=> possibilidade de captura de trafego gerado em uma interface virtual, gerando portante traces sintéticos.
-Isso possibilitaria a criação de uma biblioteca de traces, para aplicações de banchmark como o NFPA.
+\begin{figure}[h!]
+	\centering
+	\subfloat[DpdkFlow]{
+		\includegraphics[height=2.0in]{figures/ch6/dpdk-flow}
+		\label{fig:dpdk-flow}
+	}
+	\hspace{0mm}
+	\subfloat[DpdkInterface]{
+		\includegraphics[height=2.0in]{figures/ch6/dpdk-interface}
+		\label{fig:dpdk-if}
+	}
+	\caption{Class diagram for DPDK support expansions. On (a), we have a implementation of traffic generation based on DPDK. On (b) we are using DPDK KNI interfaces.}
+	\label{fig:DpdkFlow}
+\end{figure}
 
-\subsubsection{Extender para novas ferramentas e bibliotecas}
+Some approaches may be taken to improve the traffic generation performance.
+One possibility is to use DPDK KNI interfaces \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}.
+The The DPDK Kernel NIC Interface (KNI) allow applications from the user's space interact with DPDK ports.
+In this way, we may achieve a faster packet processing.
 
-Ampliar para o moongen, ostinato, Seagull, NetFPGA, etc
+Another possibility is to use DPDK API craft packets.
+Using a low-level library such for packet generation, we will be able to custom generate packets and bypass the Linux network stack (packet acceleration).
+We present in the figure ~\ref{fig:DpdkFlow} how we could expand our tool to implement a packet generator based on DPDK.
 
-\subsection{Benchmarking}
+\subsubsection{Thread Menager}
 
-Oferecer a possibilidade de automatização de medições e testes extendendo a ferramenta
+Instead of each flow's thread control individually sleep and wake times, a better approach would be a separated thread control and manage all the other threads' life-cycle operation.
+This approach can increase the timing accuracy for flows and \textit{files}.
 
-\section{Software Engineering process and Lessons Leaned}
+% \subsubsection{Improving DataProcessor Performance}
 
-\section{Conclusion}
+% Melhorar os algoritimos adicionando técnicas adicionais de modelagem, como condição de parada para o algoritimo gradient descendent, stochastic gradient descendent, entre outros
+
+\subsection{Further Implementations}
+
+\begin{itemize}
+
+	\item \textbf{C++ Sniffer}: Implementing the Sniffer and its SQL queries in C++ should increase its performance.
+
+	\item \textbf{Use OpenDayLight REST API for data collection}: Another different approach for data collection could be the use the OpenDayLight REST API to collect data from an SDN OpenFlow switches, instead of a using a Sniffer.
+Through REST API is possible to extract many statistics from nodes, hosts, and ports, such active flows, the number of packets matched per flows, packet drops, and so on.
+But, different features would be measured,  and a new model for traffic generation would be needed.
+On the other hand, we could reuse many procedures implemented.
+
+	\item \textbf{SIMITAR Python API}: Currently, SIMITAR only enables the programming of flow traffic generation in C++.
+Adding Python support for reading NetwrokTrace and NetworkFlow objects, we can enable expansion for Python traffic generation APIs, without creating C++ "wrappers".
+
+	\item \textbf{Expand SIMITAR}: Expand the SIMITAR support for more traffic generator tools and APIs, such as MoonGen LUA API, Ostinato Python API, Seagull traffic generator, and many others.
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[height=2.0in]{figures/ch6/pcap-gen}
+		\caption{Using SIMITAR for generation synthetic \textit{pcap} files, CTD files: a component schema}
+		\label{fig:pcap-gen}
+	\end{figure}
+
+	\item \textbf{PcapGen: a compact \textit{pcap} lybrary}: Create a component capable of generate synthetic \textit{pcap} files, using Compact Trace Descriptors(CTDs) files.
+We can implement this using SIMITAR as a packet injector, but in an emulated host interface, for example, using Mininet.
+Then, the traffic can be collected, using a tool such as TCPDump or Tshark.
+We present a diagram of this idea in the figure ~\ref{fig:pcap-gen}.
+This expansion would enable SIMITAR  to work as trace library for pcap-based benchmark tools.
+
+	% Oferecer a possibilidade de automatização de medições e testes extendendo a ferramenta
+
+	% usar redes neurais para classificação de aplicações
+
+\end{itemize}

### 2017-06-13 Docs/Thesis/docs/chapter4.tex
text

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this chapter we are going to go in deep details on some implementations and modelling approaches mentioned in the last chapter.
+
+In the frist section, we are going to discuss our methodology for modelling inter pacekt times, and validade it as a good choise. The problem we want to adress are these one:
+
+\begin{itemize}
+
+	\item We have a set of empirical inter-packet times, and some aproximate stochastic models that describe it. We want to know what is the best, in a analyctical way.
+
+	\item We whant to know whatever if our modelling aproaches are good ot not to describe inter pacekt times.
+
+\end{itemize}
+
+Many works have been made in second point on the literature, but not so many on the second. So we are proposing a model, and validating it.
+
+In the second section, we will describe breifely two others we used to calc flow's session ON and OFF times, and
 

### 2017-06-20 Docs/Thesis/docs/appendix/appendixB.tex
thesis makefile

--- 2017-06-06 Docs/Thesis/docs/appendix/appendixA.tex
@@
-%\newpage
-%\renewcommand{\appendixname}{Appendix}
+\chapter{Traffic Generators Survay}
+\label{ap:traffic-gen-survey}
 
-%\appendix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Open-source and free traffic generator tools}
 
-\chapter{Revision of Probability}
-\label{ap:revision-probability}
+In this section we will presented a short review of many open-source tools available for synthetic traffic generation and benchmark.
+The goal in this section is to present both the most mentioned tools in the literature, and the most recent and advanced ones.
+On table~\ref{tab:trafficgen-list1} is presented a short review of some of the main features of such tools, such as support for Operational systems, protocols, stochastic functions available for traffic generation, available interfaces, and traffic generator class.
+Some free, but not open-source traffic generators are listed as well.
 
-\section{Stochastic Process}
+Before present our survey, we will refer to some tools mentioned in literature, but we couldn't found source code and manual.
+\textbf{BRUNO}\cite{bruno-paper} is traffic generator implemented aiming performance and accuracy on timings.
+It has many configurable parameters that allow emulation of many web server scenarios.
+\textbf{Divide and conquer}\cite{validate-trafficgen}: Divide and conquer is replay engine that works in a distributed manner.
+It is able to split traces among multiple commodity PCs, and reply packets, to produce realistic traffic.
+Some others mentioned tools\cite{web-ditg} we weren't able to find any reference of available features are: \textbf{UDPgen}, \textbf{Network Traffic Generator}, \textbf{Packet Shell}, \textbf{Real-Time Voice Traffic Generator}, \textbf{PIM-SM Protocol Independent Multicast Packet Generator}, \textbf{TTCP}, \textbf{SPAK, Packet Generator}, \textbf{TfGen}, \textbf{TrafGen} and \textbf{Mtools}.
 
-\section{Random variable}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Packet-crafting libraries}
 
-\section{Probability Distribution Function (PDF)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Packet-level traffic generators}
 
-\section{Cumulative Distribution Function (CDF)}
+\textbf{D-ITG}\cite{ditg-paper}\cite{web-ditg}: D-ITG(Distributed Internet Traffic Generator) is a platform capable to produce IPv4 and IPv6 traffic defined by IDT and PS probabilistic distributions such as constant, uniform, Pareto, Cauch, Normal, Poisson, Gamma, Weibull, and On/Off; both configurable and pre-defined for many applications, from Telnet, through online games.
+It provide many flow-level options of customization, like duration, start delay and number of packets, support to many link-layer and transport-layer protocols, options, sources and destinations addresses/ports.
+If has support for NAT traversal, so it is possible to make experiments between two different networks separated by the cloud.
+D-ITG can be also used to measure packet loss, jitter, and throughput.
+D-ITG may be used through a CLI, scripts, or a C API, that can be use to create applications and remotely control another hosts through a daemon.
+The code may be downloaded on its official website.
 
-\section{Expected value, Variance, Mean and Standard Deviation}
+\textbf{Ostinato}\cite{web-ostinato}: Ostinato is a packet crafter, network traffic generator and analyzer with a friendly GUI(“wireshark in reverse” as the documentation says) and a Python API.
+This tool permits craft and send packets of different protocols  at different rates.
+Support Server/Client communication, and a huge variety of protocols, from the link layer(such as 802.3 and VLAN) to the application layer (such HTTP and SIP).
+It is also possible to add any unimplemented protocols, through scripts defined by the user.
+The code may be downloaded on its official website (http://ostinato.org/downloads).
 
-\section{Self-similarity}
+\textbf{Seagull}\cite{wp-seagull}\cite{web-seagull}: Seagull is a traffic generator and test open-source tool, released by HP.
+It has support of many protocols, from link layer to application layer, and it support is easily extended, via XML dictionaries.
+As the documentation argues, the protocol extension flexibility is one of the main features.
+It support high speeds, and is reliable, being tested through hundreds of hours.
+It can also generate traffic using three statistical models: uniform(constant), best-effort and Poisson.The code may be downloaded on its official website.
 
-\section{Heavy-tailed distributions}
+\textbf{BRUTE}\cite{web-brute}: Is a traffic generator that operates on the top of  Linux 2.4-6 and 2.6.x, not currently being supported on newer versions.
+It also support some stochastic functions(constant, poisson, trimodal) for departure time brust, and is able to simulate VoIP traffic.
+The source code(old release) may me fond on official website and on google code repository (\href{https://code.google.com/archive/p/brute/}{https://code.google.com/archive/p/brute/}).
 
-\section{Hurst Exponent}
+\textbf{PackETH} \cite{web-packeth}: PackETH is GUI and CLI stateless packet generator tool for ethernet.It support many adjustments of parameters, and many protocols as well, ans can set MAC addresses.
+The download link may be found on it official website.
 
-\section{Maximum likelihood function}
+\textbf{Iperf}\cite{web-iperf}: Ipef is network traffic generator tools, designed for the measure of the maximum achievable bandwidth on IP networks, for both TCP and UDP traffic, bu can evaluate delay, windows size, and packet loss.
+Although it is, originally, a command line tool, some developers have created a GUI interface, called Jperf\cite{web-jperf}.
+There is also a Java API, for automating tests\cite{jperf-git}.
+Support IPv4 and IPv6.
+The source code can be found on their offical website.
 
-\section{Akaike information criterion}
+\textbf{NetPerf}\cite{web-netperf}: Netperf is a benchmark tools that can be used to measure performance of many types of networks, providing tests for both unidirectional throughput, and end-to-end latency.
+It uses a command line interface, and has support to TCP, UDP and SCTP, both over IPv4 and IPv6.
+The source code can be downloaded at website homepage.
 
-\section{Bayesian information criterion}
+\textbf{sourcesOnOff}\cite{sourcesonoff-paper} \cite{web-sourcesonoff}: sourcesOnOff is a recent traffic generator released on 2014, that aims to generate realistic synthetic traffic using probabilistic models to controll on and off time of traffic flows.
+As shown on the paper, it is able to guarantee self-similatiry, an has support to many probabilistic distributions for the on/off times: Weibull, Pareto, Exponential  and Gaussian.
+Supports TCP and UDP over IPv4.
+The source code can be found on the author personal page.
 
-\section{Estimation of parameters of stochastic distributions}
+\textbf{TG}\cite{web-tg}: TG is a traffic generator that is able to generate and receive one-way packet streams transmitted from the UNIX user level process between source and traffic sink nodes.
+It is controlled by a simple specification language, that enables the craft of different lengths and interarrival times distributions, such as Constant, uniform, exponential and on/off(markov2).
 
-\subsection{Linear Regression and Gradient Descendant Algorithm}
+\footnote{not open-source}\textbf{MGEN}\cite{web-mgen}: MGEN (Multi-Generator) is a traffic generator developed by the Naval Research Laboratory (NRL) PROTocol Engineering Advanced Networking (PROTEAN) Research Group.
+It uses as input can be used to emulate the traffic patterns of unicast and/or multicast UDP and TCP IP applications.
+It support many different types of stochastic functions, nominated periodic, Poisson, burst jitter and clone which are able to control inter departure times and packet size.
 
-\subsection{Maximum likelihood estimation}
+\textbf{KUTE}\cite{web-kute}: KUTE is a kernel level packet generator, designed to have a maximum performance traffic generator, and receiver mainly for use with Gigabit Ethernet.
+It works in the kernel level, sending packets as fast as possible, direct to the hardware driver, bypassing the stack.
+But KUTE works only on Linux 2.6, and has only be tested on Ethernet Hardware.
+Also, it only supports constant UDP traffic.
+The source code of the tools is available on its homepage.
 
-\subsection{Others methods}
+\textbf{RUDE \& CRUDE}\cite{web-rude-crude}: RUDE(Real-time UDP Data Emitter) and CRUDE(Collector for RUDE), are small and flexible programs which runs on user-level.
+It has a GUI called GRUDE.
+It works in a similar way MGEN does, but has a higher time resolution.
+But it works only with UDP.
+The source code can be found on its homepage.
+
+\footnote{not open-source}\textbf{NetSpec}\cite{web-netspec}: NetSpec is tool designed to do network tests, as opposed to doing point to point testing.
+NetSpec provides a framework that allows a user to control multiple processes across multiple hosts from a central point of control, using daemons that implement traffic sources and sinks, along with measurement tools.
+Also, it is able to model many different traffic patterns and applications, such as host maximum rate; Constant Bit Rate (CBR) at user level; WWW, World Wide Web; FTP, File Transfer Protocol; telnet; MPEG video; voice and video teleconference.
+This source and application wasn't available anymore on its webpage.
+
+\textbf{Nping}\cite{web-nping}: active hosts, as a traffic generator for network stack stress testing, ARP poisoning, Denial of Service attacks, route tracing, etc.
+Nping CLI permits the users control over protocols headers.
+To source code can be downloaded on its website.
+
+\textbf{TCPreplay}\cite{web-tcpreplay}: TCPreplay is a user-level replay engine, that can use pcap files as input, and then forward, packets in a network interface.
+It can modify some header parameters as well.
+The source code of TCPreplay can be found on github \href{https://github.com/synfinatic/tcpreplay}{https://github.com/synfinatic/tcpreplay}.
+
+\textbf{TCPivo}\cite{tcpivo-paper}\cite{web-tcpivo}: TCPivo is a high-speed traffic replay engine that is able to read traffic traces, and replay packets in a network interface, working at kernel level.
+Until the present data, it is not currently supported kernel versions greater than 2.6.
+The source code can be fond on its official website.
+
+\textbf{NetFPGA PacketGenerator}\cite{web-netfpgapacketgenerator}: NetFPGA PacketGenerator is a hardware-based traffic generator and capture tool, build over the NetFPGA 1G, and open FPGA platform with 4 ethernet interfaces of 1 Gigabit of bandwidth each.
+It is a replay engine tool which uses as input \textit{pcap} files.
+It is able to accurately control the delay between the frames, with the default delay being the same in the pcap file.
+It is also able to capture packets, and report statistics of the traffic.
+The code can be downloaded on github.
+
+\textbf{NetFPGA Caliper}\cite{web-caliper}:  is a hardware-based traffic generator, build on NetFPGA 1G, built over NetThreads platform, a FPGA microprocessor which support threads programing.
+Different form NetFPGA PacketGenerator, Caliper is able to produce live packets.
+It is written in C.
+The code can be downloaded on github.
+
+\textbf{NetFPGA OSNT}\cite{web-osnt}: OSNT(Open Source Network Tester) is hardware based network traffic generator built over the NetFPGA 10G.
+As NetFPGA 1G, NetFPGA 10G is a FPGA platform with 4 ethernet interfaces, but with 10 Gigabits of bandwidth.
+OSNT is a replay engine, and is loaded with pcap traces.
+OSNT Source Network Test code can be found on github.
+
+\textbf{Dpdk Pktgen}\cite{web-dpdk-pktgen}: Pktgen is a traffic generator measurer built over DPDK.
+DPDK is a development kit, a set of libraries and drivers for fast packet processing.
+DPDK was designed to run on any processor, but has some limitation on terms of supported NICs, that can be found on its website.
+
+\textbf{MoonGen}\cite{moongen-paper}\cite{web-moongen} : MoonGen is a scriptable high-speed packet generator built over DPDK and LuaJIT.
+It is able to send packets at 10 Gbit/s, even with 64 bytes packets on a single CPU core.
+MoonGen can achieve this rate even if each packet is modified by a Lua script.
+Also, it provides accurate timestamping and rate control.
+It is able to generate traffic using several protocols ( IPv4, IPv6, IPsec, ARP, ICMP, UDP, and  TCP), and can generate different inter-departure times, like a Poisson process and burst traffic.
+This project can be found on github.
+
+\textbf{gen\_send/gen\_recv}\cite{web-gensend-genrecv}: gen\_send and gen\_recv are simple UDP traffic generator applications.
+It uses UDP sockets, and  gen\_send is able to control features like desired data rate, packet size and inter packet time.
+You can find their source at \href{http://www.citi.umich.edu/projects/qbone/generator.html}{http://www.citi.umich.edu/projects/qbone/generator.html}.
+
+\textbf{mxtraf}\cite{web-mxtraf}: mxtraf enables that a small number of hosts to saturate a network, with a tunable mixture of TCP and UDP traffic.
+You can found the source code at \href{http://mxtraf.sourceforge.net/}{http://mxtraf.sourceforge.net/}.
+
+\textbf{Jigs Traffic Generator (JTG)}\cite{web-jtg}: is a simple, accurate traffic generator.
+JTG process only sends one stream of traffic, and steam characteristics are defined only by command line arguments.
+It also supports IPv6.
+You can find the code at \href{http://www.netlab.tkk.fi/~jmanner/jtg/}{http://www.netlab.tkk.fi/~jmanner/jtg/}.
+
+\textbf{*Poisson Traffic Generator}:
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Application-level/Special-scenarios traffic generators}
+
+\footnote{not open-source}\textbf{ParaSynTG}\cite{parasyntg-paper}: application-level traffic generator configurable by input parameters, which considers most of the observes www traffic workload properties.
+
+\footnote{not open-source}\textbf{EAR}\cite{validate-trafficgen}: traffic generator that uses a technique called “Event Reproduction Ratio”  to mimic wireless IEEE 802.11 protocol behavior.
+
+\footnote{not open-source}\textbf{GenSyn}\cite{web-gensyn}: network traffic generator implemented in Java, that mimic TCP and UDP connections, based on user behavior.
+
+\textbf{Surge}\cite{surge-paper}: Surge is an application level workload generator which emulates a set of real users accessing a web server.
+It matches many empirical measurements of real traffic, like server file distribution, request size distribution, relative file popularity, idle periods of users and other characteristics.
+Its source code can be  found at \href{http://cs-www.bu.edu/faculty/crovella/surge_1.00a.tar.gz}{http://cs-www.bu.edu/faculty/crovella/surge\_1.00a.tar.gz}.
+
+\textbf{Httperf}\cite{web-httperf}: Is an application lever traffic generator to measure web server performance.
+It uses the protocol HTTP (HTTP/1.0 and HTTP/1.1), and offer many types of workloads while keeping track of statistics related to the generated traffic.
+Its most basic operation is to generate a set of HTTP GET requests and measure the number of replies and response rate.
+You can found its source code on GitHub \href{https://github.com/httperf/httperf}{https://github.com/httperf/httperf}.
+
+\textbf{VoIP Traffic Generator}: it is a traffic generator written in Perl, and creates multiple streams of traffic,  aiming to simulate VoIP traffic. You can found its code at \href{
+	https://sourceforge.net/projects/voiptg/}{
+	https://sourceforge.net/projects/voiptg/}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Flow-level and Closed-loop and multi-level traffic generators}
+
+\textbf{Harpoon}\cite{harpoon-paper}: Harpoon is a flow based traffic generator, that is able to 
+automatically extract form Netflow traces parameters, in order to generate flows that exhibit the same statistical characteristics measured before, including temporal and spatial characteristics.
+The source code of Harpoon can be found on github (\href{https://github.com/jsommers/harpoon}{https://github.com/jsommers/harpoon}).
+
+\textbf{Swing}\cite{swing-paper} \cite{web-swing}: Swing is a closed-loop multi-layer, and network responsive generator.
+It is able to read capture traces, and captures the packet interactions of many applications, being able to models distributions for user, application, and network behavior, stochastic and responsively.
+As mentioned in the previous section, Swing is able to model user behavior, REEs, connection, packets, and network.
+The code may be downloaded on its official website.
+
+\footnote{not open-source}\textbf{LiTGen}(Lightweight Traffic Generator)\cite{litgen-paper} is a open-loop, multilevel traffic generator.
+It is able to model wireless network traffic in a peer user and application basis.
+This tool models the traffic in three different levels: packet level, object level (smaller parts of an application session), and session level.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Others traffic generation tools}
+
+\textbf{NFPA}\cite{nfpa-paper}: NFPA is a benchmark tools based on DPDK Pkgen, specialized on executing and automatize performance measurements over network functions.
+It works being directly connected to an specific device under tests.
+It uses built-in and user defined traffic traces, and Lua scripts control and collect information of DPDK Pktgen.
+It has an command line and Web interface, and automatically plot the results.
+
+\textbf{LegoTG}\cite{legotg-paper}: LegoTG is a modular framework for composing custom traffic generation.
+It aims to simplify the combination on the use of different traffic generators and modulators on different testbeds, automatizing the process of installation, execution, resource allocation and synchronization via a centralized orchestrator, which uses a software repository.
+It already has support to many tools, and to add support to new tools is necessary to add and edit two files, called TGblock, and ExFile.

### 2017-06-20 Docs/Thesis/docs/appendix/todo.tex
thesis makefile

\chapter{TODO List}

\section{Chapter 1 - Introduction - Introduction}

\section{Chapter 2 - Bibliographic Revision }

Liks úteis:

>> http://www.backtrack-linux.org/forums/showthread.php?t=8740

>> https://sudks.wordpress.com/2016/04/27/tools-traffic-networking/

>> http://www.linuxlinks.com/article/2012042806090428/BenchmarkTools.html

>> http://uperf.org/

\begin{enumerate}

\item TODO \textbf{Geist}\cite{geist-paper} is an application level traffic generator for stress web servers. http://kkant.net/geist/ http://kkant.net/geist/doc/geist\_doc.pdf

\item TODO https://wiki.fd.io/view/Project\_Proposals/TRex https://github.com/cisco-system-traffic-generator/trex-core
\item TODO TFGEN/MCAST: http://www.pgcgi.com/hptools/
\item TODO Poisson traffic generator http://www.spin.rice.edu/Software/poisson\_gen/
\item TODO http://netsniff-ng.org/ (trafgen)
\item TODO Synthetic self-similar traffic generation http://glenkramer.com/trf\_research.shtml
\item  TODO https://github.com/steerapi/udpgen
\item TODO  http://nutsaboutnets.com/netstress/
\item TODO https://sourceforge.net/projects/ip-packet/
\item TODO PacGen http://sourceforge.net/projects/pacgen/ Packet Forger
\item TODO NTGen http://nssl.eew.technion.ac.il/files/Projects/NTGen\_v2.0/html/index.htm
\item TODO epb - Ethernet Package Bombardier  http://maz-programmersdiary.blogspot.com.br/2012/05/epb-ethernet-package-bombardier.html

\item (Programa não encontrado) FTP traffic generator: https://pdfs.semanticscholar.org/5756/cf54e46c38dd98c7ad0d5c50deb65a8b33a7.pdf
\item (Programa não encontrado) \textbf{NetSpec}: http://www.cs.columbia.edu/~hgs/internet/traffic-generator.html http://www.ittc.ku.edu/netspec/

\end{enumerate}

\section{Chapter 3 - Architecture}

\section{Chapter 4 - Modeling}

\section{Chapter 5 - Prof of concepts}

\section{Chapter 6 - Usage cases}

\section{Chapter 7 - Conclusion}

### 2017-06-20 Docs/Thesis/docs/chapter2.tex
thesis makefile

@@
 Some examples of implementations are: PacketGenerator \cite{web-netfpgapacketgenerator}, Caliper \cite{web-caliper}, and OSNT Packet Generator \cite{web-osnt}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Open-source and free traffic generator tools}
-
-In this section we will presented a short review of many open-source tools available for synthetic traffic generation and benchmark.
-The goal in this section is to present both the most mentioned tools in the literature, and the most recent and advanced ones.
-On table~\ref{tab:trafficgen-list1} is presented a short review of some of the main features of such tools, such as support for Operational systems, protocols, stochastic functions available for traffic generation, available interfaces, and traffic generator class.
-Some free, but not open-source traffic generators are listed as well.
-
-Before present our survey, we will refer to some tools mentioned in literature, but we couldn't found source code and manual.
-\textbf{BRUNO}\cite{bruno-paper} is traffic generator implemented aiming performance and accuracy on timings.
-It has many configurable parameters that allow emulation of many web server scenarios.
-\textbf{Divide and conquer}\cite{validate-trafficgen}: Divide and conquer is replay engine that works in a distributed manner.
-It is able to split traces among multiple commodity PCs, and reply packets, to produce realistic traffic.
-Some others mentioned tools\cite{web-ditg} we weren't able to find any reference of available features are: \textbf{UDPgen}, \textbf{Network Traffic Generator}, \textbf{Packet Shell}, \textbf{Real-Time Voice Traffic Generator}, \textbf{PIM-SM Protocol Independent Multicast Packet Generator}, \textbf{TTCP}, \textbf{SPAK, Packet Generator}, \textbf{TfGen}, \textbf{TrafGen} and \textbf{Mtools}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Packet-crafting libraries}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Packet-level traffic generators}
-
-\textbf{D-ITG}\cite{ditg-paper}\cite{web-ditg}: D-ITG(Distributed Internet Traffic Generator) is a platform capable to produce IPv4 and IPv6 traffic defined by IDT and PS probabilistic distributions such as constant, uniform, Pareto, Cauch, Normal, Poisson, Gamma, Weibull, and On/Off; both configurable and pre-defined for many applications, from Telnet, through online games.
-It provide many flow-level options of customization, like duration, start delay and number of packets, support to many link-layer and transport-layer protocols, options, sources and destinations addresses/ports.
-If has support for NAT traversal, so it is possible to make experiments between two different networks separated by the cloud.
-D-ITG can be also used to measure packet loss, jitter, and throughput.
-D-ITG may be used through a CLI, scripts, or a C API, that can be use to create applications and remotely control another hosts through a daemon.
-The code may be downloaded on its official website.
-
-\textbf{Ostinato}\cite{web-ostinato}: Ostinato is a packet crafter, network traffic generator and analyzer with a friendly GUI(“wireshark in reverse” as the documentation says) and a Python API.
-This tool permits craft and send packets of different protocols  at different rates.
-Support Server/Client communication, and a huge variety of protocols, from the link layer(such as 802.3 and VLAN) to the application layer (such HTTP and SIP).
-It is also possible to add any unimplemented protocols, through scripts defined by the user.
-The code may be downloaded on its official website (http://ostinato.org/downloads).
-
-\textbf{Seagull}\cite{wp-seagull}\cite{web-seagull}: Seagull is a traffic generator and test open-source tool, released by HP.
-It has support of many protocols, from link layer to application layer, and it support is easily extended, via XML dictionaries.
-As the documentation argues, the protocol extension flexibility is one of the main features.
-It support high speeds, and is reliable, being tested through hundreds of hours.
-It can also generate traffic using three statistical models: uniform(constant), best-effort and Poisson.The code may be downloaded on its official website.
-
-\textbf{BRUTE}\cite{web-brute}: Is a traffic generator that operates on the top of  Linux 2.4-6 and 2.6.x, not currently being supported on newer versions.
-It also support some stochastic functions(constant, poisson, trimodal) for departure time brust, and is able to simulate VoIP traffic.
-The source code(old release) may me fond on official website and on google code repository (\href{https://code.google.com/archive/p/brute/}{https://code.google.com/archive/p/brute/}).
-
-\textbf{PackETH} \cite{web-packeth}: PackETH is GUI and CLI stateless packet generator tool for ethernet.It support many adjustments of parameters, and many protocols as well, ans can set MAC addresses.
-The download link may be found on it official website.
-
-\textbf{Iperf}\cite{web-iperf}: Ipef is network traffic generator tools, designed for the measure of the maximum achievable bandwidth on IP networks, for both TCP and UDP traffic, bu can evaluate delay, windows size, and packet loss.
-Although it is, originally, a command line tool, some developers have created a GUI interface, called Jperf\cite{web-jperf}.
-There is also a Java API, for automating tests\cite{jperf-git}.
-Support IPv4 and IPv6.
-The source code can be found on their offical website.
-
-\textbf{NetPerf}\cite{web-netperf}: Netperf is a benchmark tools that can be used to measure performance of many types of networks, providing tests for both unidirectional throughput, and end-to-end latency.
-It uses a command line interface, and has support to TCP, UDP and SCTP, both over IPv4 and IPv6.
-The source code can be downloaded at website homepage.
-
-\textbf{sourcesOnOff}\cite{sourcesonoff-paper} \cite{web-sourcesonoff}: sourcesOnOff is a recent traffic generator released on 2014, that aims to generate realistic synthetic traffic using probabilistic models to controll on and off time of traffic flows.
-As shown on the paper, it is able to guarantee self-similatiry, an has support to many probabilistic distributions for the on/off times: Weibull, Pareto, Exponential  and Gaussian.
-Supports TCP and UDP over IPv4.
-The source code can be found on the author personal page.
-
-\textbf{TG}\cite{web-tg}: TG is a traffic generator that is able to generate and receive one-way packet streams transmitted from the UNIX user level process between source and traffic sink nodes.
-It is controlled by a simple specification language, that enables the craft of different lengths and interarrival times distributions, such as Constant, uniform, exponential and on/off(markov2).
-
-\footnote{not open-source}\textbf{MGEN}\cite{web-mgen}: MGEN (Multi-Generator) is a traffic generator developed by the Naval Research Laboratory (NRL) PROTocol Engineering Advanced Networking (PROTEAN) Research Group.
-It uses as input can be used to emulate the traffic patterns of unicast and/or multicast UDP and TCP IP applications.
-It support many different types of stochastic functions, nominated periodic, Poisson, burst jitter and clone which are able to control inter departure times and packet size.
-
-\textbf{KUTE}\cite{web-kute}: KUTE is a kernel level packet generator, designed to have a maximum performance traffic generator, and receiver mainly for use with Gigabit Ethernet.
-It works in the kernel level, sending packets as fast as possible, direct to the hardware driver, bypassing the stack.
-But KUTE works only on Linux 2.6, and has only be tested on Ethernet Hardware.
-Also, it only supports constant UDP traffic.
-The source code of the tools is available on its homepage.
-
-\textbf{RUDE \& CRUDE}\cite{web-rude-crude}: RUDE(Real-time UDP Data Emitter) and CRUDE(Collector for RUDE), are small and flexible programs which runs on user-level.
-It has a GUI called GRUDE.
-It works in a similar way MGEN does, but has a higher time resolution.
-But it works only with UDP.
-The source code can be found on its homepage.
-
-\footnote{not open-source}\textbf{NetSpec}\cite{web-netspec}: NetSpec is tool designed to do network tests, as opposed to doing point to point testing.
-NetSpec provides a framework that allows a user to control multiple processes across multiple hosts from a central point of control, using daemons that implement traffic sources and sinks, along with measurement tools.
-Also, it is able to model many different traffic patterns and applications, such as host maximum rate; Constant Bit Rate (CBR) at user level; WWW, World Wide Web; FTP, File Transfer Protocol; telnet; MPEG video; voice and video teleconference.
-This source and application wasn't available anymore on its webpage.
-
-\textbf{Nping}\cite{web-nping}: active hosts, as a traffic generator for network stack stress testing, ARP poisoning, Denial of Service attacks, route tracing, etc.
-Nping CLI permits the users control over protocols headers.
-To source code can be downloaded on its website.
-
-\textbf{TCPreplay}\cite{web-tcpreplay}: TCPreplay is a user-level replay engine, that can use pcap files as input, and then forward, packets in a network interface.
-It can modify some header parameters as well.
-The source code of TCPreplay can be found on github \href{https://github.com/synfinatic/tcpreplay}{https://github.com/synfinatic/tcpreplay}.
-
-\textbf{TCPivo}\cite{tcpivo-paper}\cite{web-tcpivo}: TCPivo is a high-speed traffic replay engine that is able to read traffic traces, and replay packets in a network interface, working at kernel level.
-Until the present data, it is not currently supported kernel versions greater than 2.6.
-The source code can be fond on its official website.
-
-\textbf{NetFPGA PacketGenerator}\cite{web-netfpgapacketgenerator}: NetFPGA PacketGenerator is a hardware-based traffic generator and capture tool, build over the NetFPGA 1G, and open FPGA platform with 4 ethernet interfaces of 1 Gigabit of bandwidth each.
-It is a replay engine tool which uses as input \textit{pcap} files.
-It is able to accurately control the delay between the frames, with the default delay being the same in the pcap file.
-It is also able to capture packets, and report statistics of the traffic.
-The code can be downloaded on github.
-
-\textbf{NetFPGA Caliper}\cite{web-caliper}:  is a hardware-based traffic generator, build on NetFPGA 1G, built over NetThreads platform, a FPGA microprocessor which support threads programing.
-Different form NetFPGA PacketGenerator, Caliper is able to produce live packets.
-It is written in C.
-The code can be downloaded on github.
-
-\textbf{NetFPGA OSNT}\cite{web-osnt}: OSNT(Open Source Network Tester) is hardware based network traffic generator built over the NetFPGA 10G.
-As NetFPGA 1G, NetFPGA 10G is a FPGA platform with 4 ethernet interfaces, but with 10 Gigabits of bandwidth.
-OSNT is a replay engine, and is loaded with pcap traces.
-OSNT Source Network Test code can be found on github.
-
-\textbf{Dpdk Pktgen}\cite{web-dpdk-pktgen}: Pktgen is a traffic generator measurer built over DPDK.
-DPDK is a development kit, a set of libraries and drivers for fast packet processing.
-DPDK was designed to run on any processor, but has some limitation on terms of supported NICs, that can be found on its website.
-
-\textbf{MoonGen}\cite{moongen-paper}\cite{web-moongen} : MoonGen is a scriptable high-speed packet generator built over DPDK and LuaJIT.
-It is able to send packets at 10 Gbit/s, even with 64 bytes packets on a single CPU core.
-MoonGen can achieve this rate even if each packet is modified by a Lua script.
-Also, it provides accurate timestamping and rate control.
-It is able to generate traffic using several protocols ( IPv4, IPv6, IPsec, ARP, ICMP, UDP, and  TCP), and can generate different inter-departure times, like a Poisson process and burst traffic.
-This project can be found on github.
-
-\textbf{gen\_send/gen\_recv}\cite{web-gensend-genrecv}: gen\_send and gen\_recv are simple UDP traffic generator applications.
-It uses UDP sockets, and  gen\_send is able to control features like desired data rate, packet size and inter packet time.
-You can find their source at \href{http://www.citi.umich.edu/projects/qbone/generator.html}{http://www.citi.umich.edu/projects/qbone/generator.html}.
-
-\textbf{mxtraf}\cite{web-mxtraf}: mxtraf enables that a small number of hosts to saturate a network, with a tunable mixture of TCP and UDP traffic.
-You can found the source code at \href{http://mxtraf.sourceforge.net/}{http://mxtraf.sourceforge.net/}.
-
-\textbf{Jigs Traffic Generator (JTG)}\cite{web-jtg}: is a simple, accurate traffic generator.
-JTG process only sends one stream of traffic, and steam characteristics are defined only by command line arguments.
-It also supports IPv6.
-You can find the code at \href{http://www.netlab.tkk.fi/~jmanner/jtg/}{http://www.netlab.tkk.fi/~jmanner/jtg/}.
-
-\textbf{*Poisson Traffic Generator}:
 
@@
 \end{table} 
+\clearpage
 
@@
 \end{table} 
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Application-level/Special-scenarios traffic generators}
-
-\footnote{not open-source}\textbf{ParaSynTG}\cite{parasyntg-paper}: application-level traffic generator configurable by input parameters, which considers most of the observes www traffic workload properties.
-
-\footnote{not open-source}\textbf{EAR}\cite{validate-trafficgen}: traffic generator that uses a technique called “Event Reproduction Ratio”  to mimic wireless IEEE 802.11 protocol behavior.
-
-\footnote{not open-source}\textbf{GenSyn}\cite{web-gensyn}: network traffic generator implemented in Java, that mimic TCP and UDP connections, based on user behavior.
-
-\textbf{Surge}\cite{surge-paper}: Surge is an application level workload generator which emulates a set of real users accessing a web server.
-It matches many empirical measurements of real traffic, like server file distribution, request size distribution, relative file popularity, idle periods of users and other characteristics.
-Its source code can be  found at \href{http://cs-www.bu.edu/faculty/crovella/surge_1.00a.tar.gz}{http://cs-www.bu.edu/faculty/crovella/surge\_1.00a.tar.gz}.
-
-\textbf{Httperf}\cite{web-httperf}: Is an application lever traffic generator to measure web server performance.
-It uses the protocol HTTP (HTTP/1.0 and HTTP/1.1), and offer many types of workloads while keeping track of statistics related to the generated traffic.
-Its most basic operation is to generate a set of HTTP GET requests and measure the number of replies and response rate.
-You can found its source code on GitHub \href{https://github.com/httperf/httperf}{https://github.com/httperf/httperf}.
-
-\textbf{VoIP Traffic Generator}: it is a traffic generator written in Perl, and creates multiple streams of traffic,  aiming to simulate VoIP traffic. You can found its code at \href{
-https://sourceforge.net/projects/voiptg/}{
-https://sourceforge.net/projects/voiptg/}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Flow-level and Closed-loop and multi-level traffic generators}
-
-\textbf{Harpoon}\cite{harpoon-paper}: Harpoon is a flow based traffic generator, that is able to 
-automatically extract form Netflow traces parameters, in order to generate flows that exhibit the same statistical characteristics measured before, including temporal and spatial characteristics.
-The source code of Harpoon can be found on github (\href{https://github.com/jsommers/harpoon}{https://github.com/jsommers/harpoon}).
-
-\textbf{Swing}\cite{swing-paper} \cite{web-swing}: Swing is a closed-loop multi-layer, and network responsive generator.
-It is able to read capture traces, and captures the packet interactions of many applications, being able to models distributions for user, application, and network behavior, stochastic and responsively.
-As mentioned in the previous section, Swing is able to model user behavior, REEs, connection, packets, and network.
-The code may be downloaded on its official website.
-
-\footnote{not open-source}\textbf{LiTGen}(Lightweight Traffic Generator)\cite{litgen-paper} is a open-loop, multilevel traffic generator.
-It is able to model wireless network traffic in a peer user and application basis.
-This tool models the traffic in three different levels: packet level, object level (smaller parts of an application session), and session level.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Others traffic generation tools}
-
-\textbf{NFPA}\cite{nfpa-paper}: NFPA is a benchmark tools based on DPDK Pkgen, specialized on executing and automatize performance measurements over network functions.
-It works being directly connected to an specific device under tests.
-It uses built-in and user defined traffic traces, and Lua scripts control and collect information of DPDK Pktgen.
-It has an command line and Web interface, and automatically plot the results.
-
-\textbf{LegoTG}\cite{legotg-paper}: LegoTG is a modular framework for composing custom traffic generation.
-It aims to simplify the combination on the use of different traffic generators and modulators on different testbeds, automatizing the process of installation, execution, resource allocation and synchronization via a centralized orchestrator, which uses a software repository.
-It already has support to many tools, and to add support to new tools is necessary to add and edit two files, called TGblock, and ExFile.
+\clearpage
 

### 2017-06-20 Docs/Thesis/docs/appendix/appendixB.tex
modifications

@@
 It already has support to many tools, and to add support to new tools is necessary to add and edit two files, called TGblock, and ExFile.
+
+\begin{table}[ht!]
+\centering
+\caption{My caption}
+\label{my-label}
+\begin{tabular}{@{}ll@{}}
+\toprule
+Traffic Generator       & Repository                                                                                                                                                                                                                \\ \midrule
+D-ITG                   & \href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}                                                                                                                         \\
+Ostinato                & \href{http://ostinato.org/}{http://ostinato.org/}                                                                                                                                                                         \\
+Seagull                 & \href{http://gull.sourceforge.net/}{http://gull.sourceforge.net/}                                                                                                                                                         \\
+BRUTE                   & \href{http://wwwtlc.iet.unipi.it/software/brute/ }{http://wwwtlc.iet.unipi.it/software/brute/ }                                                                                                                           \\
+PackETH                 & \href{http://packeth.sourceforge.net/packeth/Home.html}{http://packeth.sourceforge.net/packeth/Home.html}                                                                                                                 \\
+Iperf                   & \href{https://iperf.fr/}{https://iperf.fr/}                                                                                                                                                                               \\
+NetPerf                 & \href{http://www.netperf.org/netperf/}{http://www.netperf.org/netperf/}                                                                                                                                                   \\
+sourcesOnOff            & \href{http://www.recherche.enac.fr/~avaret/sourcesonoff}{http://www.recherche.enac.fr/~avaret/sourcesonoff}                                                                                                               \\
+TG                      & \href{http://www.postel.org/tg/}{http://www.postel.org/tg/}                                                                                                                                                               \\
+MGEN*                   & \href{http://www.nrl.navy.mil/itd/ncs/products/mgen }{http://www.nrl.navy.mil/itd/ncs/products/mgen }                                                                                                                     \\
+KUTE                    & \href{http://caia.swin.edu.au/genius/tools/kute/}{http://caia.swin.edu.au/genius/tools/kute/}                                                                                                                             \\
+RUDE \& CRUDE            & \href{http://rude.sourceforge.net/}{ http://rude.sourceforge.net/}                                                                                                                                                        \\
+Pktgen                  & \href{http://www.linuxfoundation.org/collaborate/workgroups/networking/pktgen}{http://www.linuxfoundation.org/collaborate/workgroups/networking/pktgen}                                                                   \\
+NetSpec                 & \href{http://www.ittc.ku.edu/netspec/}{http://www.ittc.ku.edu/netspec/}                                                                                                                                                   \\
+Nping                   & \href{https://nmap.org/nping/ }{https://nmap.org/nping/}                                                                                                                                                                  \\
+TCPreplay               & \href{http://tcpreplay.appneta.com/}{http://tcpreplay.appneta.com/}                                                                                                                                                       \\
+TCPivo                  & \href{http://www.thefengs.com/wuchang/work/tcpivo/}{http://www.thefengs.com/wuchang/work/tcpivo/}                                                                                                                         \\
+NetFPGA PacketGenerator & \href{https://github.com/NetFPGA/netfpga/wiki/PacketGenerator}{https://github.com/NetFPGA/netfpga/wiki/PacketGenerator}                                                                                                   \\
+NetFPGA Caliper         & \href{https://github.com/NetFPGA/netfpga/wiki/PreciseTrafGen}{https://github.com/NetFPGA/netfpga/wiki/PreciseTrafGen}                                                                                                     \\
+NetFPGA OSNT            & \href{https://github.com/NetFPGA/OSNT-Public/wiki/OSNT-Traffic-Generator}{https://github.com/NetFPGA/OSNT-Public/wiki/OSNT-Traffic-Generator}                                                                             \\
+DPDK Pktgen             & \href{http://pktgen.readthedocs.io/en/latest/getting_started.html}{http://pktgen.readthedocs.io/en/latest/getting\_started.html}                                                                                          \\
+MoonGen                 & \href{https://github.com/emmericp/MoonGen}{https://github.com/emmericp/MoonGen}                                                                                                                                           \\
+gen\_send/gen\_recv       & \href{http://www.citi.umich.edu/projects/qbone/generator.html}{http://www.citi.umich.edu/projects/qbone/generator.html}                                                                                                   \\
+mxtraf                  & \href{http://mxtraf.sourceforge.net/}{http://mxtraf.sourceforge.net/}                                                                                                                                                     \\
+JTG                     & \begin{tabular}[c]{@{}l@{}}\href{https://sourceforge.net/projects/iperf/files/}{https://sourceforge.net/projects/iperf/files/}\\ \href{https://github.com/AgilData/jperf}{https://github.com/AgilData/jperf}\end{tabular} \\
+GenSyn                  & \href{http://www.item.ntnu.no/people/personalpages/fac/poulh/gensyn}{http://www.item.ntnu.no/people/personalpages/fac/poulh/gensyn}                                                                                       \\
+SURGE                   & \href{http://cs-www.bu.edu/faculty/crovella/surge_1.00a.tar.gz}{http://cs-www.bu.edu/faculty/crovella/surge\_1.00a.tar.gz}                                                                                                \\
+Httperf                 & \href{https://linux.die.net/man/1/httperf}{https://linux.die.net/man/1/httperf}                                                                                                                                           \\
+VoIP Traffic Generator  &                                                                                                                                                                                                                           \\
+Harpoon                 & \href{http://cs.colgate.edu/~jsommers/harpoon/}{http://cs.colgate.edu/~jsommers/harpoon/}                                                                                                                                 \\
+Swing                   & \href{http://cseweb.ucsd.edu/~kvishwanath/Swing/}{http://cseweb.ucsd.edu/~kvishwanath/Swing/}                                                                                                                             \\
+NFPA                    &                                                                                                                                                                                                                           \\
+LegoTG                  &                                                                                                                                                                                                                           \\ \bottomrule
+\end{tabular}
+\end{table}

### 2017-06-20 Docs/Thesis/docs/chapter4.tex
modifications

@@
 
+\begin{table}[!ht]
+\begin{tabular}{@{}|l|l|@{}}
+\toprule
+Link                                & \multirow{3}{*}{\textit{headers data}} \\ \cmidrule(r){1-1}
+Network                             &                                        \\ \cmidrule(r){1-1}
+Transport                           &                                        \\ \midrule
+Application                         & appClassification                      \\ \midrule
+\multirow{2}{*}{Inter Packet Times} & calcOnOff                              \\ \cmidrule(l){2-2} 
+                                    & stochasticFitting                      \\ \midrule
+Packet Size                         & stochasticFitting                      \\ \bottomrule
+\end{tabular}
+\end{table}
+
 %\section{Implementation Details}

### 2017-06-21 Docs/Thesis/docs/appendix/appendixC.tex
some modifications on the thesis

\chapter{Chapter ~\ref{ch:modeling-evaluation} Aditional Plots}
\label{ap:aditional-plots}

\section{CDFs distributions}

The trace \textit{bigflows-pcap} has a much higher inter packet rate, and a smaller dispersion. Weibull is the model chosen by AIC/BIC, and it is the second best on correlation and self-similarity (Exponential(Me) and Cauchy are the best respectively). Exponential(Me) chooses as the second preferable, has the closest to the original mean and standard deviation. Comparing the plots of the CDF function, the Weibull seams to express well both small and larger values of inter packet times, while Exponential(Me) is preciser on the mean values, as we can see at figure ~\ref{fig:aproximation-originalbigflows-cdf}.

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-bigFlows}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apC/cdf/bigFlows_Logscale_-_Cauchy_aproximation_vs_Original_set}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apC/cdf/bigFlows_Logscale_-_Exponential_aproximation_(linear_regression)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apC/cdf/bigFlows_Logscale_-_Exponential_aproximation_(mean)_vs_Original_set}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apC/cdf/bigFlows_Logscale_-_Normal_aproximation_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apC/cdf/bigFlows_Logscale_-_Pareto_aproximation_(linear_regression)_vs_Original_set}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apC/cdf/bigFlows_Logscale_-_Pareto_aproximation_(maximum_likehood)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apC/cdf/bigFlows_Logscale_-_Weibull_aproximation_vs_Original_set}
	}
	\caption{CDF functions for the approximations of \textit{bigFlows-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-wan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apC/cdf/wan_Logscale_-_Cauchy_aproximation_vs_Original_set}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apC/cdf/wan_Logscale_-_Exponential_aproximation_(linear_regression)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apC/cdf/wan_Logscale_-_Exponential_aproximation_(mean)_vs_Original_set}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apC/cdf/wan_Logscale_-_Normal_aproximation_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apC/cdf/wan_Logscale_-_Pareto_aproximation_(linear_regression)_vs_Original_set}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apC/cdf/wan_Logscale_-_Pareto_aproximation_(maximum_likehood)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apC/cdf/wan_Logscale_-_Weibull_aproximation_vs_Original_set}
	}
	\caption{CDF functions for the approximations of \textit{wan-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:aproximation-original-cdf-lan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apC/cdf/lan_Logscale_-_Cauchy_aproximation_vs_Original_set}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apC/cdf/lan_Logscale_-_Exponential_aproximation_(linear_regression)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apC/cdf/lan_Logscale_-_Exponential_aproximation_(mean)_vs_Original_set}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apC/cdf/lan_Logscale_-_Normal_aproximation_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apC/cdf/lan_Logscale_-_Pareto_aproximation_(linear_regression)_vs_Original_set}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apC/cdf/lan_Logscale_-_Pareto_aproximation_(maximum_likehood)_vs_Original_set}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apC/cdf/lan_Logscale_-_Weibull_aproximation_vs_Original_set}
	}
	\caption{CDF functions for the approximations of \textit{lan-diurnal-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\section{QQplots}

%\begin{figure}[ht!]
%	\centering
%	\label{fig:aproximation-original-cdf-skype}
%	\subfloat[Chauchy]{
%		\includegraphics[width=78mm]{figures/apC/qq/skype_QQplot_-_Cauchy}
%	}
%	\subfloat[Exponential(LR)]{
%		\includegraphics[width=78mm]{figures/apC/qq/skype_QQplot_-_Exponential(LR)}
%	}
%	\hspace{0mm}
%	\subfloat[Exponential(Me)]{
%		\includegraphics[width=78mm]{figures/apC/qq/skype_QQplot_-_Exponential(Me)}
%	}
%	\subfloat[Normal]{
%		\includegraphics[width=78mm]{figures/apC/qq/skype_QQplot_-_Normal}
%	}
%	\hspace{0mm}
%	\subfloat[Pareto(LR)]{
%		\includegraphics[width=78mm]{figures/apC/qq/skype_QQplot_-_Pareto(LR)}
%	}
%	\subfloat[Pareto(MLH)]{
%		\includegraphics[width=78mm]{figures/apC/qq/skype_QQplot_-_Pareto(MLH)}
%	}
%	\hspace{0mm}
%	\subfloat[Weibull]{
%		\includegraphics[width=78mm]{figures/apC/qq/skype_QQplot_-_Weibull}
%	}
%	\caption{CDF functions for the approximations of \textit{skype-pcap} inter  packet times, of many stochastic functions.}
%\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:qq-bigFlows}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apC/qq/bigFlows_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apC/qq/bigFlows_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apC/qq/bigFlows_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apC/qq/bigFlows_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apC/qq/bigFlows_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apC/qq/bigFlows_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apC/qq/bigFlows_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{bigFlows-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:qq-lan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apC/qq/lan_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apC/qq/lan_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apC/qq/lan_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apC/qq/lan_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apC/qq/lan_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apC/qq/lan_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apC/qq/lan_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{lan-diurnal-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:qq-wan}
	\subfloat[Chauchy]{
		\includegraphics[width=78mm]{figures/apC/qq/wan_QQplot_-_Cauchy}
	}
	\subfloat[Exponential(LR)]{
		\includegraphics[width=78mm]{figures/apC/qq/wan_QQplot_-_Exponential(LR)}
	}
	\hspace{0mm}
	\subfloat[Exponential(Me)]{
		\includegraphics[width=78mm]{figures/apC/qq/wan_QQplot_-_Exponential(Me)}
	}
	\subfloat[Normal]{
		\includegraphics[width=78mm]{figures/apC/qq/wan_QQplot_-_Normal}
	}
	\hspace{0mm}
	\subfloat[Pareto(LR)]{
		\includegraphics[width=78mm]{figures/apC/qq/wan_QQplot_-_Pareto(LR)}
	}
	\subfloat[Pareto(MLH)]{
		\includegraphics[width=78mm]{figures/apC/qq/wan_QQplot_-_Pareto(MLH)}
	}
	\hspace{0mm}
	\subfloat[Weibull]{
		\includegraphics[width=78mm]{figures/apC/qq/wan_QQplot_-_Weibull}
	}
	\caption{CDF functions for the approximations of \textit{wan-pcap} inter  packet times, of many stochastic functions.}
\end{figure}

\section{Validation}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-bigflows}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/bigFlows_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/bigFlows_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/bigFlows_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/bigFlows_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{bigflows-pcap} and its approximations}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-lan}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/lan_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/lan_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/lan_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/lan_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{lan-diurnal-pcap} and its approximations}
\end{figure}

\begin{figure}[ht!]
	\centering
	\label{fig:correlation-hurst-wan}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/wan_Correlation}
		\label{correlation-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/wan_Hurst_Exponent}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/wan_Mean}
	}
	\hspace{0mm}
	\subfloat[]{
		\includegraphics[width=75mm]{figures/apC/val/wan_Standard_Deviation}
		\label{hurst-skype-pcap}
	}
	\caption{Statistical parameters of \textit{wan-pcap} and its approximations}
\end{figure}

### 2017-08-09 Docs/Thesis/docs/chapter1.tex
modification on the thesis text
thesis writing

@@
 
+%3nd-review
 \section{State of Affairs and Motivation}\label{sec:state-of-the-art}
 
-%2nd-review
 Emerging technologies such as SDN and NFV are great promises.
@@
 But, especially on NFV, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}.
-Closed hardware solutions are easier to pass on Service Layer Agreement since it has a much more predictable behavior.
-Once it is expected virtualization to impact negatively, these VNFs have to keep performance degradation and as small as possible, along with a high stability.
-Thus, guarantee the Service Layer Agreements on emerging scenarios is now a harder question.
+Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior.
+Since it is expected virtualization to impact negatively on performance, these VNFs have to keep its degradation as small as possible.
+Guarantee the Service Layer Agreements on emerging scenarios is now a harder question.
 There is a demand for more reliable methods to ensure the SLAs, over different types of loads.
 
-%2nd-review
 It is already a well-known fact that the type of traffic used on performing tests matters.
@@
 
-%2nd-review
-A burstier traffic can cause packet drops buffer overflows on network\cite{burstiness-queue-lenght}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}, what degrades the network performance.
-So, characteristics on packet-trains and inter-packet times, that cause traffic burstiness.
-Also, a burstier and realistic traffic will not just impact on performance, but on measurement as well.
-Realistic and burstiness traffic impacts on bandwidth measurement accuracy\cite{legotg-paper}\cite{background-traffic-matter}.
+A burstier traffic can cause packet more buffer overflows on network\cite{burstiness-queue-lenght}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}.
+Also, a burstier and realistic traffic will not just impact on performance, but on measurement as well, since a realistic and burstier traffic impacts on bandwidth measurement accuracy\cite{legotg-paper}\cite{background-traffic-matter}.
 Another key question is how applications will deal with packets.
 It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}.
-A realistic traffic will have not a single packet-size as used by constant rate traffic generator tools, but a distribution\cite{packet-distribution-model}.
+A synthetic realistic traffic must not have a single packet-size, but must use a distribution\cite{packet-distribution-model}.
 
-%2nd-review
-Also, we have that realistic workload generators are essential security research\cite{ditg-paper}.
-Generation of realistic workloads is important on evaluation firewall middleboxes.
+Also, realistic workload generators are essential security research\cite{ditg-paper}.
+Generation of realistic workloads is important in the evaluation of firewall middleboxes.
 It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.
-Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible, we can expect that its impact over virtualized middle-boxes should be even larger.
-That's because we will have an extra overhead introduced by the virtualization layer.
-Also, on SDN networks, each new flow arriving o a switch introduces an extra communication load between it and the controller, which can generate a performance degradation.
+Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible, we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.
+Also, on SDN networks, each new flow arriving on a switch demands an extra communication load between it and the controller, unpacting necativelly as well.
 We also have a flow-oriented operation on SDN switches. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual ISP scenario.
 
-%2nd-review
 Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment.
 How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a relevant subject.
-Also, how its underlying hardware will behave with this type of a load is an important case of study\cite{instrumentation-framework-nfv}.
 
-%2nd-review
+%3nd-review
 \section{Open-source Solutions}
 
-%2nd-review
 The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}.
@@
 
-%2nd-review
 Some traffic generator tools offer support emulation of single application workloads.
@@
 
-%2nd-review
 Other tools work as packet replay engines, such as TCPreplay and TCPivo.
@@
 
-%2nd-review
-Many tools support a larger set of protocols and high-performance such Seagull and Ostinato.
+Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato.
 Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen.
 They can give a good control of the traffic and high rates.
-The most relevant examples of features are:
+The most relevant examples of features are controlled by these tools are:
 
@@
 
-%2nd-review
 \item Throughput, the number of bytes, number of packets.
 
-%2nd-review
-\item Protocol: most of the tools give support to network and transport protocols. Many also offer support to Link and Application protocols;
+\item Protocols. Most of the tools give support to network and transport protocols. Many also offer support to Link and Application protocols;
 
-%2nd-review
-\item Header and payload configuration: support to header customization includes source and destination port/addresses, QoS parameters, flags, etc.
+\item Header and payload configuration.
+Support for header customization includes source and destination port/addresses, QoS parameters, flags, etc.
 Some traffic generators also allow customizing payload bytes.
 
-%2nd-review
-\item Inter-packet time: custom inter-packet times.
-Some tools offer a set of stochastic distributions to control inter-packet times.
-The user can use these stochastic functions to emulate realistic inter-arrival times.
+\item Inter-packet times. Some tools offer a set of stochastic distributions to control inter-packet times. The user can use these stochastic functions to emulate realistic inter-arrival times.
 
-%2nd-review
-\item On/off periods: support of packet trains periods. Many offer stochastic models to control these bursts.
+\item On/off periods: support of packet trains periods. Many offer stochastic models to control it.
 
-%2nd-review
 \item Sending time and start-time: the user can use these features to control flows timings.
 
-%2nd-review
 \item Packet-size: support for different packet sizes. Some tools offer constant values or stochastic distributions to control packet sizes.
 
-%2nd-review
-\item Many configurable flows.
+\item Paralell flows configuration.
 
-%2nd-review
 \item Emulation of specific applications: common examples are Web server/client communication, VoIP, HTTP, FTP, p2p applications, and so on.
@@
 
-%2nd-review
-But, in this case, selecting a good configuration is by itself a research project.
+Since there is so many features and tools, selecting a good configuration is by itself a research project.
 How to use each parameter to simulate a specific scenario is a hard question \cite{legotg-paper}\cite{selfsimilar-ethernet}.
@@
 
-%2nd-review
-Some tools like Swing and Harpoon, try to use the best of both worlds.
-Both use capture traces to set intern parameters, enabling an easier configuration.
-Also, Swing uses complex multi-levels which are able to provide a high degree of realism\cite{swing-paper}.
+Some tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration.
+Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}.
 But they have their issues as well.
-Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem on setup and configuration.
+Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration.
 Swing\cite{swing-paper} aims to generate realistic background traffic, but do not reach high throughputs \cite{swing-paper} \cite{legotg-paper}.
-As is possible to see, this a result of the fact that its traffic generation engine is coupled to its modeling framework.
-You can't opt to use a newer/faster packet generator.
+Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library.
 The only way of replacing the traffic engine is changing and recompiling the original code.
@@
 
-%2nd-review
 Since synthetic traffic traces generation is mature in academia, the creation of custom network workloads through the configuration of high-throughput open-source is an affordable task.
@@
 
-%2nd-review
-Also, by itself, choosing which workload generator tool may fit better for the user needs is not a simple question.
-Tools like D-ITG\footnote{\href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}} provide support to many different stochastic functions, Ostinato\footnote{\href{http://ostinato.org/}{http://ostinato.org/}} provide a larger support for protocols, and a higher throughput for each thread\cite{comparative-trafficgen-tools}, and other like Seagull\footnote{\href{http://gull.sourceforge.net/doc/WP_Seagull_Open_Source_tool_for_IMS_testing.pdf}{http://gull.sourceforge.net/doc/WP\_Seagull\_Open\_Source\_tool\_for\_IMS\_testing.pdf}} are responsive.
+Also, just choosing which workload generator tool may fit better for the user needs is not a simple question.
+Tools like D-ITG\footnote{\href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}} provide support to many different stochastic functions, Ostinato\footnote{\href{http://ostinato.org/}{http://ostinato.org/}} provides a larger support for protocols, and a higher throughput for each thread\cite{comparative-trafficgen-tools}, and others like Seagull\footnote{\href{http://gull.sourceforge.net/doc/WP_Seagull_Open_Source_tool_for_IMS_testing.pdf}{http://gull.sourceforge.net/doc/WP\_Seagull\_Open\_Source\_tool\_for\_IMS\_testing.pdf}} are responsive.
 
@@
         \includegraphics[height=2.4in]{figures/ch1/layer-diagram}
-        \caption{ Conceptual idea: a <configuration><modelling><intelligence><emulation><acceleration><visualization><distributed><open-source>}
+        \caption{ Architecture conceptual idea: a toll to automatize many tasks on traffic modelling and generation.}
     \label{fig:layer-diagram}
@@
 
-%2nd-review
 Now, we are going to formalize these exposed concepts in a proposal of research and development. Or main targets here are:
@@
 
-%2nd-review
 \item Survey the available open-source Ethernet workload tools available, addressing different features available;
 
-%2nd-review
-\item Define what is a realistic Ethernet traffic, and the man approaches found in literature;
+\item Define what is a realistic Ethernet traffic, and the main approaches found in literature for crafting it;
 
-%2nd-review
 \item Create a general method for modeling and parameterization of Ethernet traffic, aiming to mimic any traffic provided as input;
 
-%2nd-review
 \item Create a software \textit{tool} able of \textit{learning} patterns and characteristics of real network traffic traces, and based on the acquired knowledge, allowing to reproduce network traffic with similar (but not equal) characteristics, \textit{avoiding} the storage of \textit{pcap} files.
@@
 
-%2nd-review
 We call our  tool \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}.
@@
 
-%2nd-review
 \item Traffic Flow Programmability: the tool records this parameterization on a light-weight and human-readable version of a \textit{pcap} file.
@@
 
-%2nd-review
 \item Easy expansion: The sniffing, modeling, and traffic generation processes must work separately, so updates will be easy to manage.
@@
 
-%2nd-review
-Our main goal is to offer an easier configuration, realism than the available platforms today, at a reasonable speed.
-We are introducing programmability and abstraction to the traffic generation, since the user may create a custom traffic in a platform agnostic way.
+Our goal is to offer an easier configuration, realism than the available platforms today, at a reasonable speed.
+To do this, we are introducing the concept of programmability for  traffic generation.
+With SIMITAR, user may program its own synthetic traffic in a platform agnostic way.
 The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.
 
-%2nd-review
 Instead of storing a file huge \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace.
@@
 
-%2nd-review
 Using a component methodology, we decouple the traffic generation, from the data collection and parameterization process.
@@
 
-%2nd-review
-\item Survey the available open-source Ethernet workload tools available, addressing different features available;
+\item Survey the available open-source Ethernet workload tools available, addressing its different features;
 
-%2nd-review
 \item Define what is a realistic Ethernet traffic, and the man approaches found in literature;
 
-%2nd-review
-\item Create a general method for modeling and parameterization of Ethernet traffic, aiming to mimic any traffic provided as input;
+\item Create a general method for modeling and parameterization of Ethernet traffic, aiming to mimic a provided input;
 
-%2nd-review
 \item Create a software \textit{tool} able of \textit{learning} patterns and characteristics of real network traffic traces, and auto-configure the network traffic workloads, allowing to reproduce network traffic with similar (but not equal) characteristics, avoiding storage of \textit{pcap} files.
 
-%2nd-review
 \item It must have a flow-oriented operation, and be able to choose the best features to represent each flow traffic.
@@
 \end{itemize}
-
-%2nd-review
-We call our  tool \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}.
-These targets summarize a target of research, based on what we have exposed.
-Now, we will define some extra features, we want our tool to have:
-
-\begin{itemize}
-
-%2nd-review
-\item Traffic Flow Programmability: the tool records this parameterization on a light-weight and human-readable version of a \textit{pcap} file.
-So the user can create his own models of traffic flow based traffic, in a platform-independent manner.
-He will not have to learn how to configure and script each tool.
-
-%2nd-review
-\item Easy expansion: The sniffing, modeling, and traffic generation processes must work separately, so updates will be easy to manage.
-Also, the traffic generation is flow-oriented (it generates each flow individually).
-Thus the scheduling of each flow is platform-independent.
-In this way, is much easier to expand the support for new traffic generation engines.
-
-\end{itemize}
-
-%2nd-review
-Our main goal is to offer an easier configuration, realism than the available platforms today, at a reasonable speed.
-We are introducing programmability and abstraction to the traffic generation, since the user may create a custom traffic in a platform agnostic way.
-The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.
-
-%2nd-review
-Instead of storing a file huge \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace.
-This tool will store the generalized set of parameters in a human and machine readable XML file we call \textit{Compact Trace Descriptor} (\textit{CTD}).
-Then, we use this data as input for a traffic generator engine.
-We do so using APIs or creating new processes in a controlled manner.
-So will be possible to control packet parameters and flow's behavior in a automatized and self-configuring way.
-
-%2nd-review
-Using a component methodology, we decouple the traffic generation, from the data collection and parameterization process.
-Building it in this non-monolithic way,  enable a simple port for different traffic generators engines, what make our tools easy for updating with newer technologies.
-A project guideline is to reuse as much code and components as possible from the open-source community.
 
@@
 
+%3nd-review
 \section{Document Overview}
 
-%2nd-review
 In this introductory chapter, we presented an abstract of the state of the art, a problem statement, and proposed an approach for research and requirements for development.
@@
 After, we present a brief survey of important topics on realistic traffic generation.
-There, we are defining some important concepts we are going to use in this work, such as self-similarity, and heavy-tailed functions.
+We are defining some important concepts we are going to use in this work, such as self-similarity, and heavy-tailed functions.
 Then, we discuss some techniques of validation of traffic generator tools and some practical examples.
-We will define our tests using this set.
-Finally, we will discuss some main topics on emerging network scenarios: SDN and NFV.
+We also will make an analizis of some related works.
 
@@
 We describe \textit{SIMITAR} low-level requirements and define an architecture and algorithms.
-We also present its classes design and explain how \textit{SIMITAR} we can expand to any traffic generator engine with an API, CLI or script interface.
+We also present its classes design and explain how \textit{SIMITAR} we can expand to any traffic generator engine with an API, CLI interface.
 We use the D-ITG API as an example.
@@
 %2nd-review
-The following chapter~\ref{ch:modeling-evaluation} is a direct sequence of the last.
+In the chapter~\ref{ch:modeling-evaluation} we go deep in some subjects pointed in the previous chapter.
 We present how the modeling process actually works, using a defined data set (which we are going to use in the rest of the work).
@@
 We also describe our used and developed algorithms.
-Finally, we give some implementation.
 
 %2nd-review
-In the chapter Proof of concepts and Validation~\ref{ch:validation}, we define a set of metrics based on previous tests on validation of traffic generators found in the literature.
+In the chapter ~\ref{ch:validation}, we define a set of metrics based on previous tests on validation of traffic generators found in the literature.
 Here, we focus on packet, flow, and scaling metrics.

### 2017-08-09 Docs/Thesis/docs/appendix/appendixB.tex
some modifications on the thesis
ch2 apB

@@
 The goal in this section is to present both the most mentioned tools in the literature, and the most recent and advanced ones.
-On table~\ref{tab:trafficgen-list1} is presented a short review of some of the main features of such tools, such as support for Operational systems, protocols, stochastic functions available for traffic generation, available interfaces, and traffic generator class.
+On table~\ref{tab:trafficgen-list1} is presented a short review of some of the main features of such tools, such as support for Operational systems, protocols, stochastic functions available for traffic generation, and traffic generator class.
 Some free, but not open-source traffic generators are listed as well.
@@
 Some others mentioned tools\cite{web-ditg} we weren't able to find any reference of available features are: \textbf{UDPgen}, \textbf{Network Traffic Generator}, \textbf{Packet Shell}, \textbf{Real-Time Voice Traffic Generator}, \textbf{PIM-SM Protocol Independent Multicast Packet Generator}, \textbf{TTCP}, \textbf{SPAK, Packet Generator}, \textbf{TfGen}, \textbf{TrafGen} and \textbf{Mtools}.
+In the table ~\ref{tab:traffic-gen-links} we present an updated list of links for download.
 
@@
 D-ITG may be used through a CLI, scripts, or a C API, that can be use to create applications and remotely control another hosts through a daemon.
-The code may be downloaded on its official website.
 
@@
 It is also possible to add any unimplemented protocols, through scripts defined by the user.
-The code may be downloaded on its official website (http://ostinato.org/downloads).
 
@@
 It support high speeds, and is reliable, being tested through hundreds of hours.
-It can also generate traffic using three statistical models: uniform(constant), best-effort and Poisson.The code may be downloaded on its official website.
+It can also generate traffic using three statistical models: uniform(constant), best-effort and Poisson.
 
@@
 It also support some stochastic functions(constant, poisson, trimodal) for departure time brust, and is able to simulate VoIP traffic.
-The source code(old release) may me fond on official website and on google code repository (\href{https://code.google.com/archive/p/brute/}{https://code.google.com/archive/p/brute/}).
 
 \textbf{PackETH} \cite{web-packeth}: PackETH is GUI and CLI stateless packet generator tool for ethernet.It support many adjustments of parameters, and many protocols as well, ans can set MAC addresses.
-The download link may be found on it official website.
 
 \textbf{Iperf}\cite{web-iperf}: Ipef is network traffic generator tools, designed for the measure of the maximum achievable bandwidth on IP networks, for both TCP and UDP traffic, bu can evaluate delay, windows size, and packet loss.
-Although it is, originally, a command line tool, some developers have created a GUI interface, called Jperf\cite{web-jperf}.
+It has a GUI interface, called Jperf\cite{web-jperf}.
 There is also a Java API, for automating tests\cite{jperf-git}.
 Support IPv4 and IPv6.
-The source code can be found on their offical website.
 
 \textbf{NetPerf}\cite{web-netperf}: Netperf is a benchmark tools that can be used to measure performance of many types of networks, providing tests for both unidirectional throughput, and end-to-end latency.
-It uses a command line interface, and has support to TCP, UDP and SCTP, both over IPv4 and IPv6.
-The source code can be downloaded at website homepage.
+It has support for TCP, UDP and SCTP, both over IPv4 and IPv6.
 
@@
 Supports TCP and UDP over IPv4.
-The source code can be found on the author personal page.
 
@@
 Also, it only supports constant UDP traffic.
-The source code of the tools is available on its homepage.
 
@@
 It has a GUI called GRUDE.
-It works in a similar way MGEN does, but has a higher time resolution.
-But it works only with UDP.
-The source code can be found on its homepage.
+Ut works only with UDP protocol.
 
@@
 NetSpec provides a framework that allows a user to control multiple processes across multiple hosts from a central point of control, using daemons that implement traffic sources and sinks, along with measurement tools.
-Also, it is able to model many different traffic patterns and applications, such as host maximum rate; Constant Bit Rate (CBR) at user level; WWW, World Wide Web; FTP, File Transfer Protocol; telnet; MPEG video; voice and video teleconference.
-This source and application wasn't available anymore on its webpage.
+Also, it is able to model many different traffic patterns and applications, such as host maximum rate, Constant Bit Rate (CBR), WWW, World Wide Web, FTP, File Transfer Protocol, telnet, MPEG video, voice and video teleconference.
 
@@
 Nping CLI permits the users control over protocols headers.
-To source code can be downloaded on its website.
 
@@
 It can modify some header parameters as well.
-The source code of TCPreplay can be found on github \href{https://github.com/synfinatic/tcpreplay}{https://github.com/synfinatic/tcpreplay}.
 
 \textbf{TCPivo}\cite{tcpivo-paper}\cite{web-tcpivo}: TCPivo is a high-speed traffic replay engine that is able to read traffic traces, and replay packets in a network interface, working at kernel level.
-Until the present data, it is not currently supported kernel versions greater than 2.6.
-The source code can be fond on its official website.
+It is not currently supported kernel versions greater than 2.6.
 
@@
 It is also able to capture packets, and report statistics of the traffic.
-The code can be downloaded on github.
 
@@
 It is written in C.
-The code can be downloaded on github.
 
@@
 OSNT is a replay engine, and is loaded with pcap traces.
-OSNT Source Network Test code can be found on github.
 
@@
 It is able to generate traffic using several protocols ( IPv4, IPv6, IPsec, ARP, ICMP, UDP, and  TCP), and can generate different inter-departure times, like a Poisson process and burst traffic.
-This project can be found on github.
 
@@
 It uses UDP sockets, and  gen\_send is able to control features like desired data rate, packet size and inter packet time.
-You can find their source at \href{http://www.citi.umich.edu/projects/qbone/generator.html}{http://www.citi.umich.edu/projects/qbone/generator.html}.
 
 \textbf{mxtraf}\cite{web-mxtraf}: mxtraf enables that a small number of hosts to saturate a network, with a tunable mixture of TCP and UDP traffic.
-You can found the source code at \href{http://mxtraf.sourceforge.net/}{http://mxtraf.sourceforge.net/}.
 
@@
 It also supports IPv6.
-You can find the code at \href{http://www.netlab.tkk.fi/~jmanner/jtg/}{http://www.netlab.tkk.fi/~jmanner/jtg/}.
 
-\textbf{*Poisson Traffic Generator}:
+%\textbf{*Poisson Traffic Generator}:
 
@@
 It matches many empirical measurements of real traffic, like server file distribution, request size distribution, relative file popularity, idle periods of users and other characteristics.
-Its source code can be  found at \href{http://cs-www.bu.edu/faculty/crovella/surge_1.00a.tar.gz}{http://cs-www.bu.edu/faculty/crovella/surge\_1.00a.tar.gz}.
 
@@
 Its most basic operation is to generate a set of HTTP GET requests and measure the number of replies and response rate.
-You can found its source code on GitHub \href{https://github.com/httperf/httperf}{https://github.com/httperf/httperf}.
 
-\textbf{VoIP Traffic Generator}: it is a traffic generator written in Perl, and creates multiple streams of traffic,  aiming to simulate VoIP traffic. You can found its code at \href{
-	https://sourceforge.net/projects/voiptg/}{
-	https://sourceforge.net/projects/voiptg/}.
+\textbf{VoIP Traffic Generator}: it is a traffic generator written in Perl, and creates multiple streams of traffic,  aiming to simulate VoIP traffic.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Flow-level and Closed-loop and multi-level traffic generators}
+\subsection{Flow-level and multi-level traffic generators}
 
@@
 automatically extract form Netflow traces parameters, in order to generate flows that exhibit the same statistical characteristics measured before, including temporal and spatial characteristics.
-The source code of Harpoon can be found on github (\href{https://github.com/jsommers/harpoon}{https://github.com/jsommers/harpoon}).
 
@@
 As mentioned in the previous section, Swing is able to model user behavior, REEs, connection, packets, and network.
-The code may be downloaded on its official website.
 
@@
 
+\sloppy
 \begin{table}[ht!]
 \centering
-\caption{My caption}
-\label{my-label}
-\begin{tabular}{@{}ll@{}}
+\sloppy
+\caption{Links for the traffic generators repositories}
+\label{tab:traffic-gen-links}
+%\begin{tabular}{@{}ll@{}}
+\begin{tabularx}{\textwidth}{@{}ll@{} p{10.0cm}}
 \toprule
+\sloppy
 Traffic Generator       & Repository                                                                                                                                                                                                                \\ \midrule
@@
 LegoTG                  &                                                                                                                                                                                                                           \\ \bottomrule
-\end{tabular}
+\end{tabularx}
+%\end{tabular}
 \end{table}

### 2017-08-09 Docs/Thesis/docs/chapter2.tex
ch2 apB

@@
 
-%2nd-review
 In this chapter, we will review some topics from the literature that serve as a base for this whole work.
-First of all, we will define what is a traffic generator tool, and introduce a taxonomy that distinguishes them.
-After this, we will present a survey of many available open-source and free traffic generators.
-We introduce each tool and present a feature comparison between each of them.
+We will define what is a traffic generator tool, and introduce a taxonomy that distinguishes them.
+After, we will present a survey of many available open-source and free traffic generators.
+We introduce each tool and then present a feature comparison between each of them.
 As far as we know, this is the extensible features comparison of traffic generators available so far in the literature.
-The first two sections are devoted for this topic.
+The first two sections are devoted to this topic.
 
-%2nd-review
-We also will overview network traffic modeling and realistic traffic generation.
+In the third section we will overview network traffic modeling and realistic traffic generation.
 We will discuss stochastic models that used to describe the Internet traffic.
-Based on that we will discuss what features a realistic traffic should have and highlight important features needed to control to achieve it.
+Based on that we will discuss features a realistic traffic should have.
 We can count self-similarity and burstiness,  header fields, packet size and flow features.
 
-%2nd-review
-In the following section, we will make a brief discussion on validation of traffic generator tools.
+In the following section, we will make a discussion on validation of traffic generator tools.
 First, presenting the main approaches of validation made on literature.
@@
 A traffic generator tool is a system capable of creating and injecting packets into a computer network in a controlled way to generate a synthetic traffic \cite{validate-trafficgen}.
-there is a huge variety of traffic generation tools described on the literature \cite{validate-trafficgen} \cite{ditg-paper} and available i the open-source community\footnote{\href{http://www.icir.org/models/trafficgenerators.html}{http://www.icir.org/models/trafficgenerators.html}}.
-In fact, as exposed in the chapter~\ref{ch:introduction} it is a hard task to find what is the best tool for your needs.
+there is a huge variety of traffic generation tools described on the literature \cite{validate-trafficgen} \cite{ditg-paper} and available in the open-source community\footnote{\href{http://www.icir.org/models/trafficgenerators.html}{http://www.icir.org/models/trafficgenerators.html}}.
 This is a cause of many  different approaches and methodologies available to network traffic generator's developers \cite{validate-trafficgen}.
@@
 Or even a traffic generator that reflect a special scenario such as a specific application; for example a client and server exchanging data\cite{surge-paper}.
-In this case, the target would be to stress a server, not an equipment.
+In this case, the target would be to stress a server.
 Another possibility a huge variety of protocols available, or even support of new protocols.
@@
 Alongside with the traffic generators, there are many APIs available.
-There are low-level APIs which enables direct packet injection and capture, such as \textit{libpcap}\cite{web-tcpdump}, \textit{libtins}\cite{web-libtins}, DPDK\cite{web-dpdk} and the GNU C socket library\cite{web-socket}.
+There are low-level APIs which enables direct packet injection, such as \textit{libpcap}\cite{web-tcpdump}, \textit{libtins}\cite{web-libtins}, DPDK\cite{web-dpdk} and the GNU C socket library\cite{web-socket}.
 And there are high-level APIs, provided by traffic generator tools, such as D-ITG\cite{ditg-paper}, Ostinato\cite{web-ostinato} and MoonGen\cite{moongen-paper}.
@@
 
-The most common traffic generator taxonomy found is  according to its abstraction level\cite{do-you-trust}.
-They are: Application-level/Special-scenarios, flow-level, packet-level and Closed-loop and multi-level traffic generators.
+The most common traffic generator taxonomy in the literature is about its abstraction level\cite{do-you-trust}.
+There are four groups: Application-level, flow-level, packet-level and multi-level traffic generators.
 We present a diagram  ilustrating its concept at figure ~\ref{fig:layers-workload-tools}.
@@
 
-\textbf{Application-level/Special-scenarios traffic generators}: they try to emulate the behavior of network applications, simulating real workloads stochastically, responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool.
-That means, the behavior of the output may change according to what packets have arrived in the network interface} or both.
+\textbf{Application-level traffic generators}: they try to emulate the behavior of network applications, simulating real workloads stochastically and/or responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool.
+That means, the behavior of the output may change according to what packets have arrived in the network interface}.
 As examples we have Surge\cite{surge-paper} able to emulate the behavior of web clients and services.
@@
 
-\textbf{Flow-level traffic generators}: they are able to configure and reproduce precisely features at the flow level\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}.
+\textbf{Flow-level traffic generators}: they are able to configure and reproduce features of flows\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}.
 Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from live routers.
@@
 \textbf{Packet-level traffic generators}: most traffic generators available fall in this class.
-They are able to craft packets and inject them into the network based on Inter departure times (IDT) and packet size(PS).
+They are able to craft packets and inject into the network, and controll features like inter departure times (IDT), packet size(PS), throughput and packets per second\cite{validate-trafficgen}.
 \cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model based generators.
@@
 Maximum throughput engines like Ostinato and Seagull are tools that the main goal is to perform end-to-end stress testing.
-Are included in this category generators that are able to craft packets from the link layer, like Brute\cite{web-brute}, KUTE\cite{web-brute}, and pktgen\cite{web-pktgen}.
+Are included in this category generators that are able to craft packets from the link layer, like Brute, KUTE, and pktgen.
 
-\textbf{Closed-loop and multi-level traffic generators}: this is a more recent class of network traffic generator, and its proposal is to take into account existing interaction among each layer of the network stack, to create background network traffic as close as possible from reality.
+\textbf{Multi-level traffic generators}: this is a more recent class of network traffic generator, and its proposal is to take into account existing interaction among each layer of the network stack, to create background network traffic as close as possible from reality.
 One of the most relevant tools we can found is Swing \cite{swing-paper}.
@@
 Swing is able to model things like\cite{swing-paper}:
+
 \begin{itemize}
@@
 \cite{swing-paper} cite that they have generated traces of about of 200 Mbps, about the same result found by \cite{legotg-paper}.
-In the other hand, D-ITG reached 9808 Mbps\cite{comparative-trafficgen-tools} in a link of 10 Gbps, but operating as a maximum throughput generator.g1
+In the other hand, D-ITG reached 9808 Mbps\cite{comparative-trafficgen-tools} in a link of 10 Gbps, but operating as a maximum throughput generator.
 
@@
 \\
-Regularized Incomplete beta function & $ I_{x}(a, b) = \frac{B(x; a, b)}{B(a, b)} $           \\
+Regularized Incomplete beta function & $ I_{x}(a, b) = \frac{B(x| a, b)}{B(a, b)} $           \\
 \\
-Incomplete beta function             & $ B(x; a, b) = \int_{0}^{x} t^{a - 1} (1 - t)^{(b - 1)} \text{d}t $           \\
+Incomplete beta function             & $ B(x| a, b) = \int_{0}^{x} t^{a - 1} (1 - t)^{(b - 1)} \text{d}t $           \\
 \\
-Beta function                        & $ B(x; a, b) = \int_{0}^{1} t^{a - 1} (1 - t)^{(b - 1)} \text{d}t $           \\
+Beta function                        & $ B(x| a, b) = \int_{0}^{1} t^{a - 1} (1 - t)^{(b - 1)} \text{d}t $           \\
 \\

### 2017-08-10 Docs/Thesis/docs/chapter3.tex
ch3

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \chapter{System architecture and Methods}\label{ch:architecture}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%2nd-review
-In this chapter, we will present developed tool, called SIMITAR: SnIffing, ModellIng and TrAffic geneRation, and how it works.
-First, we will discuss its architecture and components.
-Then we will present a brief tutorial of how to expand its support for a traffic generator engine.
+%3nd-review
+In this chapter, we will present our tool which aims to solve the issues addressed in the chapter ~\ref{ch:introduction}, called SIMITAR (SnIffing, ModellIng and TrAffic geneRation), and how it works.
+It aims to generate a platform-agnostic traffic, which can be extended to any traffic engine, including traffic generators tools and APIs.
+SIMITAR creates a  model in XML, configured using actual traces (from \textit{pcaps} or real-time sniffing), we call Compact Trace Descritor (CTD).
 
-%2nd-review
 We abstract its whole operation cycle in the figure ~\ref{fig:cycle-of-operation}.
@@
 
-%2nd-review
 The first version of this component was implemented in Shell Script (Bash).
@@
 This version was too slow to operate in real time on Ethernet interfaces.
-On the other hand, was fast to implement, and enable the implementation of the other components, before this final version was released.
+On the other hand, was fast to implement, and enable the implementation of the other components, before this last version was released.
 
-%2nd-review
 The second version was implemented using Python.
@@
 The flow classification is made by a class called FlowId.
-It contains class we developed called OrderedSet.
-A set is a list of elements with no repetition, but do not keep track of the insertion order.
-But our OrderedSet does.
-Also, it make use of a  32 bits hash function of the family FNV.
+It has class we developed called OrderedSet.
+A set is a list of elements with no repetition but do not keep track of the insertion order.
+Our OrderedSet does.
+Also, it make use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}.
 The listed header fields are inputs for a hash function, its value is set on the ordered set, and its order is returned.
@@
 As future improvements for this component, we propose a more efficient implementation in C++ and data visualization for the collected data.
-We discuss this in deeper details in the chapter~\ref{ch:conclusion}
+We discuss this in deeper details in the chapter~\ref{ch:conclusion}.
 
@@
 
-%2nd-review
-The database will store the collected raw data for further analysis.
-It is responsible for storing data from different traces in different tables.
-The \textit{Sniffer} and the \textit{TraceAnalyzer}  can access the database.
+The database stores the collected raw data  from the traces for further analysis. The \textit{Sniffer} and the \textit{TraceAnalyzer} can access the database.
 
-%2nd-review
 We choose an SQLite database, because according to the SQLite specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it is the best option for our database.
@@
 
-%2nd-review
-In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from the packets, along with the FlowID calculated by the sniffer component.
+In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from packets, along with the FlowID calculated by the sniffer component.
 
+%3nd-review
 \subsection{Trace Analyzer}
 
-%2nd-review
 This module is the core of our project.
-It creates a compact trace descriptor via the analysis of the collected data.
+It creates a trace model via the analysis of the collected data.
 We define here a Compact Trace Descriptor (CTD) as a human and machine readable file, which describes an original traffic trace trough a set of flows, each of them described by a set of parameters, like header information and analytical models.
 
-%2nd-review
 Therefore, the Trace Analyze learns the features from raw data of traces (stored in the SQLite database) and write them in an XML file.
@@
 \item Flow-level properties like duration of flow, start delay, number of packets per flow, number of KBytes per flow; 
-\item Packet-level QoS metrics like bit rate and packet rate; 
-\item Header fields, like protocols (IPv4, IPv6, TCP, UDP, ICMP, DCCP, SCTP, etc), QoS fields, ports, and addresses.
+\item Header fields, like protocols, QoS fields, ports, and addresses.
 \end{itemize}
@@
 To represent these characteristics, we will use sets of stochastic-based models.
+
+%%%%%%%
+%%%%% parei aqui
+%%%%%
 

### 2017-08-11 Docs/Thesis/docs/chapter3.tex
ch3

@@
 
-%2nd-review
 \begin{figure}
@@
 
+%3nd-review
 \subsubsection{Flow features}
 
-%2nd-review
 Some features are unique per flow and can be directly measured from the data. They are:
 
-%2nd-review
 \begin{itemize}
@@
 
-%2nd-review
 Each one of these parameters is unique per flow.
@@
 
-%%%%%%%
-%%%%% parei aqui
-%%%%%
-
+%3nd-review
 \subsubsection{Inter Packet Times}
@@
 
-%2nd-review
-To represent IPT, we adopt a simplified version of the Harpoon traffic model.
+To represent inter packet times, we adopt a simplified version of the Harpoon traffic model.
 A deep explanation of the original model can be found at \cite{harpoon-paper} and \cite{harpoon-validation}.
@@
 
-%2nd-review
 Harpoon uses a more conventional definition of each level, based on the measurement of SYN and ACK TCP flags.
-Harpoons use TCP flags (SYN) to classify packets in different levels (named there: file, session and user level).
-Since we are just modeling inter-packet times, we choose to estimate these values, based on inter-packet times.
-Since we want to generalize this approach for any protocol, the distinction will be made based on the time delay between packets.
+It use TCP flags (SYN) to classify packets in different levels, named there file, session, and user level.
+We choose to estimate these values, based on inter-packet times only.
+The distinction is made based on the time delay between packets.
 
-%2nd-review
-In our version of the algorithm, we define (as Harpoon does) three different layers of data transference to model and control: file, session, and flow.
+In our algorithm simplified version, we define (as Harpoon does) three different layers of data transference to model and control: file, session, and flow.
 
-%2nd-review
 For SIMITAR, a file is just a sequence of consecutive packets transmitted continuously, without large interruption of traffic.
@@
 
-%2nd-review
 \textbf{Flow-layer}: The Trace Analyzer loads the flow arrival times from the database, and calculates the inter-packet times within the flow context.
 
-%2nd-review
-\textbf{Session-layer}: At the session layer, we use a deterministic approach for evaluating times between transferred files (OFF times) and the actual file transference (ON times).
-It is basically a deterministic ON/OFF model.
+\textbf{Session-layer}: At the session layer, we use a deterministic approach for evaluating times between files and the actual file transference, the OFF and ON times of a packet train model, respectivaly.
 We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.
@@
     \centering
-    \includegraphics[height=1.6in]{figures/ch3/ipt-modeling}
+    \includegraphics[height=0.9in]{figures/ch3/simitar-parametrization}
     \caption{Diagram of parameterization and model selection for inter-packet times and inter-file times.}
@@
 %2nd-review
-We first know how much packets each mode has, and then we fit a model for it.
+We know how much packets each mode has, and then we fit a model for it.
 We use three stochastic models: constant, exponential and normal.
-Since self-similarity is not a requirement, we prefer to use just simple models.
-But, when there is no packet we set a flag NO\_MODEL, and when there is just a single packet we just use the constant model.
-We then calculate the BIC and AIC for each of them and sort according to the AIC value by default, but we decide to set the constant model as the first.
+Since self-similarity do not make sense for packet-sizes, we prefer to use just the simpler models.
+When there is no packet for a model, we set a flag NO\_MODEL, and when there is just a single packet we just use the constant model.
+Then calculate the BIC and AIC for each, but we decide to set the constant model as the first.
 
-%2nd-review
-As is possible to see on many studies \cite{packet-distribution-model}\cite{udp-flows-model}, since the standard deviation of each mode is small, constant fittings use to give good approximations.
-Also, it is computationally cheaper than the others models, since no calculation is a need for each packet sent.
-Since both AIC and BIC criteria always will select the constant model as the worst, we decide to ignore this indicator for the constant model.
+As is possible to see in many works \cite{packet-distribution-model} \cite{udp-flows-model}, since the standard deviation of each mode tends to be small, constant fittings use to give good approximations.
+Also, it is computationally cheaper for the traffic generated than the other models, since no calculation is a need for each packet sent.
+Since both AIC and BIC criteria always will select the constant model as the worst, we decide to ignore this
 
@@
 %2nd-review
-The current version of our tool, do not intrinsically supports responsiveness.
+%The current version of our tool, do not intrinsically supports responsiveness.
 The underlying traffic generator API can support it (such as Seagull\cite{web-seagull}), but we do not generate any mathematical model for this purpose, and this may also stand as a future work we discuss on chapter ~\ref{ch:conclusion}.
@@
 \end{figure*}
-
-%2nd-review
-The Flow Generator handles the data on the CTD file, and use it as parameters for the traffic generation. It crafts and controls each flow in a separated thread.
+0
+The Flow Generator handles the data on the CTD file, and use to retrieve parameters for traffic generation. It crafts and controls each flow in a separated thread.
 

### 2017-08-12 Docs/Thesis/docs/appendix/appendixA.tex
new advancements on the thesis text
3rd revision of the thesis text complete, apA and apB completed. Still have to finish apC and apD

@@
-%\newpage
-%\renewcommand{\appendixname}{Appendix}
+\chapter{Revision of Probability and Math}
+\label{ap:revision-probability}
 
-%\appendix
+\section{Random variable}
+We call random variable X a measurable real-valued  function of possible outcomes ($\Omega$ ) defined on a sample space($E$).
 
-\chapter{Revision of Probability}
-\label{ap:revision-probability}
+\begin{equation}
+	X: \Omega \rightarrow E
+\end{equation}
+
+\section{Probability Density Function (PDF)}
+
+Let X be a continuous random variable.
+We say that X is a continuous random variable if there is a function $f (x) $, that satisfies for a set $B = \{b \in \mathbb{R} | b_ {1} \leq b \leq b_ {2}\} $, defined for all $x = \{x \in \mathbb{R}| - \infty \leq x \leq + \infty\} $, having the property:
+
+\begin{equation}
+	P(X \in B) = \int_{b_{1}}^{b_{2}}f(x) dx 
+\end{equation}
+
+Where $P$ is the probability function of the random variable $x$. $f(x)$ is called probability density function of the random variable $X$\cite{ross-probability}.
+
+\section{Cumulative Distribution Function (CDF)}
+
+The Cumulative Distribution Function of a random variable $X$, we represent by $F (x) $ is defined at a given point $\ \in X$ as\cite{ross-probability}:
+
+\begin{equation}
+F(a) = P(X \leq a) = \int_{- \infty}^{a}f(x) dx 
+\end{equation}
+
+\section{Expected value, Mean, Variance and Standard Deviation}
+
+Let $X$ be a constinuous random variable, and $f(x)$ be its  density function f (x). Then the expected value of $X$ is defined by:
+
+\begin{equation}
+E[X] =  \int_{- \infty}^{+ \infty}xf(x) dx 
+\end{equation}
+
+For a random variable normally distributed $X_{normal}$ the result of this definition is equals to the mean $\mu$ of the distribution($E[X_{normal}] = \mu$).
+For an exponential distribution is equals to the inverse of its rate($E[X_{exponential}] = 1/\lambda$).
+
+The variance of a random variable $X$, denoted by $Var(X)$, is defined by:
+
+\begin{equation}
+Var(X) =  E[( X - E[x])^{2}] 
+\end{equation}
+
+For a random variable $X$ normally distributed, the variance is equal to its standard deviation ($Var(X) = \sigma^{2}$)\cite{ross-probability}.
+
+% For a normal distribution the result of this definition is  its mean ($E[X_{normal}] = \mu$), and for an exponential distribution is equals to the inverse of its rate:  ($E[X_{exponential}] = \frac{1}{\lambda}$).
 
@@
 
-\section{Random variable}
-
-\section{Probability Distribution Function (PDF)}
-
-\section{Cumulative Distribution Function (CDF)}
-
-\section{Expected value, Variance, Mean and Standard Deviation}
+A stochastic process of a random variable represented by $\{X(t)| t \in T\}$ is a collection of random variables.
+Since $t$ is often interpreted as time, $X (t) $ is usually referred as the state of the process at a given time $t$\cite{ross-probability}.
 
@@
 
+A self similar object has the property of looking "roughly" the same at any scale. Self-similar objects are described by the power law:
+
+\begin{equation}
+	N = s^{d}
+\end{equation}
+
+where 
+\begin{equation}
+	d = \frac{\ln{N}}{\ln{s}}
+\end{equation}
+
+is the dimension of the scaling law, called  Hausdorff dimension\cite{web-self-similar}.
+
+\begin{figure*}[ht!]
+	\centering
+	\includegraphics[height=2.0in]{figures/apA/tritrans}
+	\caption{This is a classical example of a self-similar figure, caled Sierpinski triangle.}
+	\label{fig:self-similar-figure-example}
+\end{figure*}
+
 \section{Heavy-tailed distributions}
 
-\section{Hurst Exponent}
+Heavy tailed distributions are probability distributions whose tails are not exponentially bounded.
+A distribution of of a random variable $X$, with cumulative distribution F(x), is said to be heavy tailed, if it satisfies this condition for all $\lambda \in \mathbb{R}$:
 
-\section{Maximum likelihood function}
+\begin{equation}
+	\lim_{x\to\infty} e^{\lambda x} (1 - F(x)) = \infty
+\end{equation}
 
-\section{Akaike information criterion}
+%\section{Hurst Exponent}
+% se der tempo eu faço isso... é mt nadaver
 
-\section{Bayesian information criterion}
+\section{Akaike information criterion (AIC) and Bayesian information criterion (BIC)}
 
-\section{Estimation of parameters of stochastic distributions}
+Suppose that we have an statistical model $M$ of some dataset ${\boldsymbol{x} = \{x_1, ..., x_n}\}$, with $n$ independent and identically distributed observations of a random variable $X$.
+This model can be expressed by a PDF $f(x| \boldsymbol{\theta})$, where $\boldsymbol{\theta}$ a vector of parameter of the PDF, $\boldsymbol{\theta} \in \mathbb{R}^{k}$ ($k$ is the number of parameters).
+The  likelihood function  of this model $M$ is given by:
 
-\subsection{Linear Regression and Gradient Descendant Algorithm}
+\begin{equation}
+L(\boldsymbol{\theta}|\boldsymbol{x} ) =  f(x_1|\boldsymbol{\theta})\cdot...\cdot f(x_n|\boldsymbol{\theta}) = \prod_{i = 1}^{n}f(x_i|\boldsymbol{\theta})
+\end{equation}
 
-\subsection{Maximum likelihood estimation}
+Now, suppose we are trying to estimate the best statistical model, from a set ${M_1, ..., M_n}$, each one whit an estimated vector of parameters  ${\boldsymbol{\hat{\theta_1}}}, ..., {\boldsymbol{\hat{\theta_n}}}$.
+$AIC$ and $BIC$ are defined by:
 
-\subsection{Others methods}
+\begin{equation}
+AIC = 2k - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
+\end{equation}
+
+\begin{equation}
+BIC = k\ln(n) - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
+\end{equation}
+
+In both cases, the preferred model $M_i$, is the one with the smaller value of $AIC_i$ or $BIC_i$.
+
+\section{Gradient Descendent Algorithm}
+
+Given a linear hypothesis for a dataset:
+
+\begin{equation}
+	\boldsymbol{h_{\theta}} = \boldsymbol{\theta}^{T}\boldsymbol{x} 
+\end{equation}
+
+were $\boldsymbol{h_{\theta}}, \boldsymbol{\theta}, \boldsymbol{x} \in \mathbb{R}^{m}$. If $m = 2$ we will just have a simple linear equation $h_{\theta}(x) = \theta_{0} + \theta_{1}x$.
+
+The goal of the gradient descendent is to minimize the cost function, defined by:
+
+\begin{equation}
+	J(\boldsymbol{\theta}) = \frac{1}{2m} \sum_{i = 1}^{m}  ( \boldsymbol{h_{\theta}}(x^{(i)} - y^{(i)} )^{2}
+\end{equation}
+
+To do this, we initialize a $\boldsymbol{\theta_{j}}$ vector (usually with zeros), and repeat this procedure, until $\boldsymbol{\theta_{j}}$ converges:
+
+\begin{equation}
+	\boldsymbol{\theta_{j + 1}} := \boldsymbol{\theta_{j}} - \alpha \frac{1}{m} \sum_{i = 1}^{m}  ( \boldsymbol{h_{\theta}}(x^{(i)} - y^{(i)} )x_{j}^{i}
+\end{equation}
+
+where $\alpha$ is the step value, typically a small positive number. All values of $\boldsymbol{\theta_{j}}$ must be updated simultaneously.

### 2017-08-12 Docs/Thesis/docs/chapter3.tex
3rd revision of the thesis text complete, apA and apB completed. Still have to finish apC and apD

@@
         \centering
-        \includegraphics[height=2.5in]{figures/ch3/database-relational-model}
+        \includegraphics[height=3.0in]{figures/ch3/database-relational-model}
         \caption{SIMITAR's SQLite database relational model}
@@
     \centering
-    \includegraphics[height=4.0in]{figures/ch3/alg-simplified-harpoon}
+    \includegraphics[height=4.5in]{figures/ch3/alg-simplified-harpoon}
     \caption{Simplified-harpoon emission algorithm}
@@
 In that case, these APIs would permit control precisely each packet sent through the interface, but a mutex would be necessary.
-An scriptable application, such as Iperf can be used as well, using \texttt{fork()} or \texttt{popen()}.
+An scriptable tool, such as Iperf can be used as well, using \texttt{fork()} or \texttt{popen()}.
 
@@
 SIMITAR works in four different states: as a sniffer, packet injector, client or server. 
-When it working as a sniffer, is produces as output a Compact Trace Descriptor file. It may operate over a \textit{pcap} file or an Ethernet interface.
+When it working as a sniffer, is produces as output a Compact Trace Descriptor file. It may work over a \textit{pcap} file or an Ethernet interface.
 
@@
 It needs to establish a connection with the destination host (the server), before start sending packets.
+Operating as a client, it must take as an input a list of IP or MAC destination addresses, since they will not match with the ones in the original trace.
 It takes as an input a single destination in the command line, or list of many, in a text file passes as a parameter.
@@
 
-Operating as a client, it must take as an input a list of IP or MAC destination addresses, since they will not match with the ones in the original trace.
  As a packet injector can generate packets on the output interface, without establishing a connection.
@@
 
-The operation of packet injector is still under implementation, and we are using Libtins library.
+The operation of packet injector is still under implementation, and we are using Libtins API.
 Currently, SIMITAR supports client mode with D-ITG, implemented using its C++ API.
@@
 
-When operating as a server, it just start-up the traffic generator server, and waits for server connections. Down bellow, we present simple examples of commands used to activate each operation mode.
+When operating as a server, it just start-up the traffic generator server, and waits forclient requests for connections.
+Down bellow, we present simple examples of commands used to activate each operation mode.
 
@@
 
+\item Flow Generation Progamability: creation of custom synthetic traffic with a certain number of flows, in a traffic-generator independent way.
+
 \item Generate Background traffic with D-ITG: SIMITAR can work to generate background traffic over a network when it receives many addresses as input.

### 2017-08-12 Docs/Thesis/docs/chapter4.tex
some modifications on the thesis
3rd revision of the thesis text complete, apA and apB completed. Still have to finish apC and apD

--- 2017-06-13 Docs/Thesis/docs/chapter4.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Modeling and Algorithms}\label{ch:modeling-evaluation}
+\chapter{Traffic Modeling and Algorithms}\label{ch:modeling-evaluation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %2nd-review
-In this chapter, we propose a method that may be implemented by  software.
+In this chapter, we propose a method automatizable by  software.
 We estimate many stochastic functions through many methodologies and select the best model through the AIC computation\cite{bic-aic-comparision}.
-Since generating random can be cost and have a bias, depending on the seed generator, we cut these problems since our method is analytical.
+Since generating random can be cost and have a bias, depending on the seed generator, we avoid these problems since our method is analytical.
 
 %2nd-review
-We made a brief bibliographic review of some works related works on this topic.
+We made a brief bibliographic review of some related works on this topic.
 Then, we will present the traffic traces we are going to use in this chapter, and in the rest of our work.
@@
 The third we capture in our laboratory LAN, through a period of 24 hours.
-It was captured in the firewall gateway between our local and external network.
+It was captured irewall gateway between our local and external network.
 Along with other tests, We intend to verify diurnal behavior on it.
@@
 %2nd-review
-The fourth is a capture of a busy private network access point to the Internet, available on-line on TCPreplay\cite{web-tcpreplay} website \footnote{ http://tcpreplay.appneta.com/wiki/captures.html}, and is called \texttt{bigFlows.pcap}.
+The fourth is a capture of a busy private network access point to the Internet, available on-line on TCPreplay website \footnote{ \href{http://tcpreplay.appneta.com/wiki/captures.html}{http://tcpreplay.appneta.com/wiki/captures.html}}, and is called \texttt{bigFlows.pcap}.
 We will refer to it \textit{bigflows-pcap}.
@@
 We also calculate another measure of quality called BIC(Bayesian information criterion), for comparison of results.
-In this chapter, we present our results obtained on our prototype implemented in Octave.
+In this chapter, we present our results obtained on our prototype implemented in Octave\footnote{ \href{https://www.gnu.org/software/octave/}{https://www.gnu.org/software/octave/}}.
 
@@
 Now we will give a brief explanation our three procedures: Linear Regression (with the  Gradient descendant algorithm), direct estimation, and maximum likelihood.
-We go deep into details explaining the methods on the appendix ~\ref{ap:revision-probability}, and present the mathematical demonstrations on appendix~\ref{ap:revision-probability}.
-
-%2nd-review
 Some observations must be made.
@@
 To avoid divergence on tangent operation on the linearization the Cauchy function, the inter-packets CDF function values were floor-limited and upper-limited to  $10^{-6}$ and $0.999999$ respectively.
+We implemented this prototype using Octave.
+We upload the code on GitHub, for reproduction purposes\footnote{\textcolor{red}{github-link-aqui}}
 
-%2nd-review
-We implemented this prototype using Octave. We upload the code on GitHub, for reproduction purposes\footnote{github-link-aqui}
+%We go deep into details explaining the methods on the appendix ~\ref{ap:revision-probability}, and present the mathematical demonstrations on appendix~\ref{ap:revision-probability}.
 
@@
 \begin{equation}
-\alpha\ln{(t)} - \alpha\ln{(\beta)} = \ln{-\ln{1 - F(t)}}
+\alpha\ln{(t)} - \alpha\ln{(\beta)} = \ln{(-\ln{(1 - F(t))})}
 \end{equation}
@@
 Having in hands a estimation of the empirical CDF of our data samples, we apply the $x$ and $y$ definitions to linearize the data.
-Using the gradient descendant, we are able to find a estimation of the linear coefficients $\hat{a}$ and $\hat{b}$.
-Using the inverse function of the definition of linear coefficients, we are able to find the estimated parameters $\hat{\alpha}$ and $\hat{\beta}$.
+
+Using the gradient descendant, we find a estimation of the linear coefficients $\hat{a}$ and $\hat{b}$.
+Using the inverse function of linear coefficients, we find the weibull estimated parameters $\hat{\alpha}$ and $\hat{\beta}$.
 
@@
 
-%2nd-review
-We present examples of linearized data, and the linear approximation achieved, as well the cost convergence of the gradient descendant algorithm in the appendix ~\ref{ap:revision-probability}.
+The gradient descendent consists in minimizing a cost function $J(\theta)$.
+We explain this procedure in the appendix ~\ref{ap:revision-probability}.
+In the figure~\ref{fig:linearization} we present as examples, the linearized data for the inter arrivals from the \textit{skype-pcap}, and in the figure ~\ref{fig:linearization-cost} the cost convergence.
+In the appendix ~\ref{ap:aditional-plots}, a complete set of these figures is presented.
 
-%2nd-review
-Applying the inverse equations of the linear coefficients ($\hat{\alpha} = \hat{a}$ and $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$) (the symbol stands for the estimated parameters).
-So we are able to estimate the Weibull distribution parameters.
-
-%2nd-review
+Applying the inverse equations of the linear coefficients ($\hat{\alpha} = \hat{a}$ and $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$) \footnote{The hat symbol ( $ \widehat{} $ ) for the estimated parameters}, we are able to estimate the Weibull distribution parameters.
 We can summarize this procedure, in these steps:
@@
 %2nd-review
-In the parameters estimation, there is an exception, since the Pareto scale ($t_{m}$) is defined by the minimum time.
-
-%2nd-review
+In the parameters estimation (step 4), there is an exception, since the Pareto scale ($t_{m}$) is defined by the minimum time.
 In the table~\ref{tab:linearization-sumary} we present a summary of the used equations in the procedure.
@@
 The hat( $\widehat{}$ ) indicates an estimated value for a parameter.
-
-%2nd-review
-In the figure~\ref{fig:linearization} we presente the linearized
 
@@
 		Exponential & $x_i = t_i$        & $y_i = \ln{(1 - F(t_i))})$        & \multicolumn{2}{l}{$\hat{\lambda} = -\hat{a}$}                                              &  \\
-		Pareto      & $x_i = \ln{(t_i)}$ & $y_i = \ln{(1 = F(t_i))}$         & $\hat{\alpha} = -\hat{a} $         & $\hat{x_{m}} = \min_{i = 0, ..., m}\{x_{i}\}$ &  \\
+		Pareto      & $x_i = \ln{(t_i)}$ & $y_i = \ln{(1 - F(t_i))}$         & $\hat{\alpha} = -\hat{a} $         & $\hat{x_{m}} = \min_{i = 0, ..., m}\{x_{i}\}$ &  \\
 		Weibull     & $x = \ln{(t)}$     & $y = \ln{(-\ln{(1 - F(t))})}$     & $\hat{\alpha} = \hat{a}$                 & $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$                                   & \\
@@
 \centering
-\subfloat[c]{
+\subfloat[Linearized interarrival data]{
   \includegraphics[height=50mm]{figures/ch4/Skype_Weibull_-_Linearized_data_and_linear_fitting}
@@
 %\hspace{0mm}
-\subfloat[c]{
+\subfloat[Cost function of the linear regression]{
   \includegraphics[height=50mm]{figures/ch4/Skype_Weibull_-_Cost_J_iterations__convergence}
@@
 \label{fig:linearization-cost}
+\caption{Linearized data and cost function of weibull linear regression}
 \end{figure}
@@
 %2nd-review
-For the exponential distribution $E(X) = \frac{1}{\lambda}$, therefore:
+For the exponential distribution $E(X) = \frac{1}{\lambda}$, therefore we have:
 \begin{equation}
@@
 
-\subsubsection{AIC and BIC}
-
-%2nd-review
- Suppose that we have an statistical model $M$ of soma dataset ${\boldsymbol{x} = (x_1, ..., x_n)}$, with $n$ independent and identically distributed observations of a random variable $X$.
-This model can be expressed by a PDF $f(x, \boldsymbol{\theta})$, where $\boldsymbol{\theta}$ a vector of parameter of the PDF, $\boldsymbol{\theta} \in \mathbb{R}^{k}$ ($k$ is the number of parameters).
-The  likelihood function  of this model $M$ is given by:
-
-\begin{equation}
-L(\boldsymbol{\theta}|\boldsymbol{x} ) =  f(x_1|\boldsymbol{\theta})...f(x_n|\boldsymbol{\theta}) = \prod_{i = 1}^{n}f(x_i|\boldsymbol{\theta})
-\end{equation}
-
-Now, suppose we are trying to estimate the best statistical model, from a set ${M_1, ..., M_n}$, each one whit an estimated vector of parameters  ${\boldsymbol{\hat{\theta_1}}}, ..., {\boldsymbol{\hat{\theta_n}}}$.
-$AIC$ and $BIC$ are defined by:
-
-\begin{equation}
-AIC = 2k - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
-\end{equation}
-
-\begin{equation}
-BIC = k\ln(n) - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
-\end{equation}
-
-In both cases, the preferred model $M_i$, is the one with the smaller value of $AIC_i$ or $BIC_i$.
+%\subsubsection{AIC and BIC}
 
@@
 \begin{itemize}
-\item Correlation between the sample data and the estimated model;
+\item Correlation between the sample data and the estimated model (Pearson's product-moment coefficient);
 \item Hurst exponent;
@@
 \textit{bigflows-pcap} is much larger, and has a much much smaller mean inter-packet time}
-	\label{tab:prototype-results}
+
 	\scalebox{0.75}{ 
@@
 		\end{tabular}
+	\label{tab:prototype-results}
 	}
@@
 
-The results for the AIC, BIC and parameters of all four traces are at the table~\ref{tab:prototype-results1}.
+The results for the AIC, BIC and parameters of all four traces are at the table~\ref{tab:prototype-results}.
 The results for \textit{wan-pcap} and \textit{lan-diurnal-pcap} are on the table ~\ref{tab:prototype-results}.
 The difference between BIC and AIC values in all simulations are very small.
-Much smaller then the difference between its values between the distributions.
+Much smaller then the difference of these values between the distributions.
 This is an indication that for inter packet times, using AIC or BIC should will not influence significantly the results.
@@
 This was expected, since both are heavy-tailed functions.
-But, Cauchy, on most of the tests, even being a heavy-tailed distribution seems to no present a good fitting.
+But Cauchy on most of the tests, even being a heavy-tailed distribution, seems to no present a good fitting.
 This is effect of the fast divergence of tangent function, when we linearize our data.
@@
 All these results are abstracted by the cost function $J$.
-As we can see, on all pcaps, the best function selected by BI and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.
+As we can see, on all pcaps, the best function selected by BIC and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.
 
@@
 % Skype correlation, Hurst, Mean Standard Deviation
-\begin{figure}[h!]
+\begin{figure}[t!]
 	\centering
@@
 %validation Cost function
-\begin{figure}[ht!]
+\begin{figure}[t!]
 	\centering
@@
 
+\begin{algorithm}[ht!]
+	\caption{stochasticModelFitting}
+	\label{alg:stochasticModelFitting}
+	\begin{algorithmic}[1]
+		\small		\Function{stochasticModelFitting}{$interArrivalData, criterion$}
+		\State $m = interArrivalData.size$
+		\State $interArrivalData = interArrivalData + MIN\_TIME$
+		\If{$m < MINIMUM\_AMOUNT\_OF\_PACKETS$}
+		\State $model\_list = \{constant\}$
+		\Else
+		\State $model\_list = \{weibull, pareto\_lr, pareto\_mlh, exponential\_me, exponential\_lr, normal,$
+		\State $cauchy, constant\}$
+		\EndIf
+
+		\For{$model$ \textbf{in} $model\_list$}
+		\State $model.fitting\_model(interArrivalData)$
+		\EndFor
+		\State $model\_list.sort(criterion)$
+		\State \textbf{return} $model\_list$
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
 \subsection{Conclusion}
@@
 
-Also, except by the Pareto function modeled using the Maximum likelyhood method, have comparative results between the simulations and the AIC/BIC gess.
-The best fittings according to the AIC/BIC usually  returned very acurate models, with close mean and fractal level, and correlation close to one.
+Also, except by the Pareto function modeled using the Maximum likelihood method, have comparative results between the simulations and the AIC/BIC goes.
+The best fittings according to the AIC/BIC usually returned very accurate models, with a small error between the mean and fractal level, and correlation close to one.
 The models selected as the worsts usually returned poor results.
 
-Also, it is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurante fitting, what justify the application of the criteria in all new experiment.
+Also, it is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurate fitting, what justify the application of the criteria in all new experiments.
+For example, Weibull usually performs pretty well, but in some cases, perform poorly, and in others may even diverge.
 
-We do not rely on only one type of parametrization.
+We do not rely on only one type of parameterization.
 This turns our methodology more robust, since a linear regression may diverge.
-But aways there will be an packable model, since our estimations for Normal, Exponential(Me) and Pareto(MLH) cannot.
-Models wich the linear regression diverge, will not have god BIC/AIC estimations, and will not be pickedas primary options.
-
-\section{Others Algorithms and Methods}
-
-In this section we breef present another methods used by the \textit{TraceAnalyzer} component.
-The first to calculate the session ON and OFF times.
-The second classify applications based on its tranport protocol and ports.
-
-\subsection{On/Off Times estimation}
+But always there will be a peaceable model, since our estimations for Normal, Exponential (Me) and Pareto (MLH) cannot.
+Models which the linear regression diverges, will have very high and positive BIC/AIC estimations, and will not stand as primary options.
 
@@
 		\State $fileSize.push(fileSizeSum)$
+		\State \textbf{return} $onTimes, offTimes, pktCounter, fileSize$
 		\EndFunction
@@
 \end{algorithm}
+
+\begin{table}[ht!]
+	\centering
+	\caption{Application matach table}
+	\label{tab:application-protocols}
+	\begin{tabular}{lll}
+		\hline
+		Application Protocol & Transport Protocols & Transport Ports \\ \hline
+		HTTPS               & TCP                & 443             \\
+		FTP                 & TCP                & 20, 21          \\
+		HTTP                & TCP                & 80              \\
+		BGP                 & TCP                & 179             \\
+		DHCP                & UDP                & 67, 68          \\
+		SNMP                & UDP, TCP           & 161             \\
+		DNS                 & UDP, TCP           & 53              \\
+		SSH                 & UDP, TCP           & 22              \\
+		Telnet              & UDP, TCP           & 23              \\
+		TACACS              & UDP, TCP           & 49              \\ \hline
+	\end{tabular}
+\end{table}
+
+\section{Others Algorithms and Methods}
+
+In this section we breef present another methods used by the \textit{TraceAnalyzer} component.
+The first to calculate the session ON and OFF times.
+The second classify applications based on its tranport protocol and ports.
+In the table ~\ref{tab:mehtods} we summarize the stack of models used to create the Compact Trace Descriptor (CTD file).
+
+\subsection{On/Off Times estimation}
 
@@
 
-\begin{table}[h!]
+\begin{table}[ht!]
 	\centering
-\caption{Application classification table}
-\label{tab:application-protocols}
-\begin{tabular}{lll}
+	\caption{Stack of models used to create the CTD file}
+	\label{tab:mehtods}
+	\begin{tabular}{|l|l|}
 		\hline
-Application Protocol & Transport Protocols & Transport Ports \\ \hline
-HTTPS               & TCP                & 443             \\
-FTP                 & TCP                & 20, 21          \\
-HTTP                & TCP                & 80              \\
-BGP                 & TCP                & 179             \\
-DHCP                & UDP                & 67, 68          \\
-SNMP                & UDP, TCP           & 161             \\
-DNS                 & UDP, TCP           & 53              \\
-SSH                 & UDP, TCP           & 22              \\
-Telnet              & UDP, TCP           & 23              \\
-TACACS              & UDP, TCP           & 49              \\ \hline
+		Link Layer                          & \multirow{3}{*}{Packets header's data} \\ \cline{1-1}
+		Network Layer                       &                                       \\ \cline{1-1}
+		Transport Layer                     &                                       \\ \hline
+		Application Layer                   & Application Match Table                    \\ \hline
+		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$                             \\ \cline{2-2} 
+		& 
+		Algorithm: $stochasticModelFitting$                    \\ \hline
+		Packet Sizes                        & Algorithm: $stochasticModelFitting$                    \\ \hline
 	\end{tabular}

### 2017-08-19 Docs/Thesis/docs/chapter6.tex
thesis writing
3rd revision of the thesis text complete, apA and apB completed. Still have to finish apC and apD
**WARNING** THIS IS THE LAST COMMIT BEFORE CHANGING SOME TEST FILES. ALL USELESS SCRIPTS WILL BE PUT INT FOLDERS CALLED delete_this

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Conclusion and Future Work}
-\label{ch:conclusion}
+\chapter{Conclusion and Future Work}\label{ch:conclusion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+TODO Limitations, future work
+
+TODO considerações, contrubuições, lições, boas idéias, mas idéias
+
+\section{Final Conclusions}
+
+\textcolor{red}{some text here}
 
@@
 \end{itemize}
+
+\subsection{Changing the Model, reusing the Architecture}
+
+Since the proposed architecture is model-independent, another future work is to use the same general concepts of compact trace descriptor and API agnostic modeling on different models and compare the results.
+
+Our proposed future work is to implement this idea using the Swing\cite{swing-paper} and the Harpoon Model\cite{harpoon-paper}.
+We can create not just Simitar trace descriptors, but Swing and Harpoon trace descriptors as well.
+So, as here, we would have the same components: the Sniffer, the SQLite database, the DataProcessor, the flow generator, and the same interface based on an XML Compact Trace Descriptor.
+The FlowGenerator would abstract the traffic generation in based on the Swing and Harpoon model, in an API independent way as well.
+
+These implementations can lead to a definitive and standardized model of realistic traffic generation.
+In this way, progresses on high-speed traffic generation would no more make old traffic generators and models obsolete.
+Also, would enable the comparison (ain a fair way) which model is actually the best since the same engine and technic for generating packets will be used.
+
+Also, the idea of a Compact Trace Descriptor, by itself separates the idea of traffic generation and the modeling.
+De development of new methodologies for modeling is  separated from the traffic generation.
+So a data-developer, using any compact trace descriptor interface may just "plug" his method of data modeling in the FlowGenerator.
+He has not to care about how the packets were going to be generated anymore nor in what programming language is being used to craft packets.

### 2017-08-19 Tests/scripts/prototype-flowGenerator/test_sessionOnOffTimes.m

@@ -1,3 +1,4 @@
+%#!/usr/bin/octave-cli -qf
 % constants 
 n_samples = 10000;
 SESSION_CUT_TIME = 2.90;

### 2017-08-23 Tests/prototype-calcOnOff.sh
update

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+sh -c 'cd scripts/prototype-flowGenerator/ && ./test_sessionOnOffTimes.m'

### 2017-08-23 Tests/scripts/prototype-dataProcessor/delete_this/timerelative2timedelta.m

@@ -3,12 +3,14 @@
 arg_list = argv ();
 
 EXPERIMENT_NAME = arg_list{1};
-DATAFILE_NAME_PREFIX = './data/matlab_data_';
+DATAFILE_NAME_PREFIX = 'data/matlab_data_';
 DATAFILE_NAME_EXT = '.txt';
 DATAFILE_NAME = strcat(DATAFILE_NAME_PREFIX,EXPERIMENT_NAME, DATAFILE_NAME_EXT);
 
-%a = sort([1 2 3 4 5 6 7 7 8 9 10 11 1 2 3 5 3 4 2 ])';
-a = sort(load(DATAFILE_NAME))';
+%a = sort(load(DATAFILE_NAME));
+a = sort([1 2 3 4 5 6 7 7 8 9 10 11 1 2 3 5 3 4 2 ]);
+
+printf('%s', DATAFILE_NAME);
 
 adelta = zeros(length(a) - 1, 1);
 
@@ -16,6 +18,6 @@ for i = 1:(length(a) - 1)
 	adelta(i) = a(i + 1) - a(i);
 end
 
-dlmwrite(DATAFILE_NAME, adelta);
+%dlmwrite(DATAFILE_NAME, adelta);
 
 

### 2017-08-23 Tests/scripts/prototype-dataProcessor/pcap-sniffer.sh

@@ -1,0 +1,97 @@
+#!/bin/bash
+
+#files
+MATLAB_DATA="../data/matlab_data_";
+OPT_TIME_CAP="--time-delta";
+OPT_TIME_FLOW="--flow-time-delta"
+
+
+#EX_NUMBER=$1
+arg1=$1
+arg2=$2;
+arg3=$3;
+arg4=$4
+
+main()
+{
+	local pcap_file=${arg2};
+	local exName=${arg3};
+
+
+	if [[ $arg1 == ${OPT_TIME_CAP} ]]
+		then
+		tshark_frameTimeDelta $pcap_file $exName
+
+	elif [[ $arg1 == ${OPT_TIME_FLOW} ]]
+		then
+
+		local flow_filter=$arg4
+		#flow_filter="'(ip.src==69.12.209.118)&&(ip.dst==153.193.117.110)&&(tcp.srcport==80)&&(tcp.dstport==58902)'";
+		tshark_flowTimeDelta $pcap_file $exName ${flow_filter}
+		./timerelative2timedelta.m $exName
+
+	else
+		help_menu;
+	fi
+
+	return 0;
+}
+
+###############################################################################
+#
+###############################################################################
+help_menu()
+{
+
+	echo "./pcap-sniffer.sh --time-delta/--flow-time-delta  <pcap_file> <exName>";
+}
+
+###############################################################################
+#
+###############################################################################
+tshark_frameTimeDelta()
+{
+	# path and filename to of pcap
+	local pcap_path_fileName=$1;
+	local experiment_name=$2
+
+	touch ${MATLAB_DATA}${experiment_name}".txt";
+	tshark -r ${pcap_path_fileName} -T fields -e frame.time_delta >> ${MATLAB_DATA}${experiment_name}".txt";
+
+	echo "time delta stored at " ${MATLAB_DATA}${experiment_name}".txt";
+
+}
+
+###############################################################################
+#
+###############################################################################
+tshark_flowTimeDelta()
+{
+	# path and filename to of pcap
+	local pcap_path_fileName=$1;
+	local experiment_name=$2
+	local flow_filter=$3 #'(ip.src==43.252.226.5)&&(ip.dst==125.6.107.157)&&(tcp.srcport==80)&&(tcp.dstport==64834)'
[…]

### 2017-08-23 Tests/scripts/prototype-dataProcessor/plotCostFunction.sh

@@ -7,7 +7,7 @@ if [[ ${simName} == "" ]];
 	then
 	simName=$RANDOM;
 fi
-SIM_DIR="/FINAL_prototype-"${simName}"/";
+SIM_DIR="/prototype-"${simName}"/";
 
 ./calcCostFunction.py ${PLOT_DIR}${SIM_DIR}
 gnuplot -e "datafile='${PLOT_DIR}${SIM_DIR}/costFunction.dat'" -e "filename='${PLOT_DIR}${SIM_DIR}/costFunction'" -e "ylabel='cost function'"   -e ${font_config} ../gnuplot/tickbar.gnu

### 2017-08-23 Tests/scripts/prototype-dataProcessor/run.sh

@@ -1,0 +1,36 @@
+#!/bin/bash
+
+arg1=$1
+
+main()
+{
+	if [[ $arg1 == ""  ]]
+		then
+		help_menu;
+	elif [[ $arg1 == "--help" ]]
+		then
+		help_menu;
+	else
+		./pcap-sniffer.sh --time-delta  $arg2 $arg1
+		./dataProcessor.m  $arg1;
+		./modelFittingEvaluation-plots.sh  $arg1;
+		./plotCostFunction.sh  $arg1;
+
+	fi
+
+	return 0;
+
+}
+
+help_menu()
+{
+	echo "To run:";
+	echo "./run <experiment-name> <pcap-file-name>"
+
+}
+
+
+if [ "${1}" != "--source-only" ];                                               
+then                                                                            
+    main "${@}";                                                                
+fi 

### 2017-08-23 Tests/scripts/prototype-flowGenerator/calcOnOffSimplified.m

@@ -22,6 +22,7 @@
 ## Author: anderson <anderson@duvel-ThinkCentre-M93p>
 ## Created: 2017-05-31
 
+%% calcOnOff algotithem simplified. Just calc on and off times
 function [onOff onTimes offTimes] = calcOnOffTimes (arrival_time, delta_time, cut_time, min_on_time)
 	m = length(delta_time); % in: number of inter packet times
 	last_off = 0; i = 0; j = 0;

### 2017-08-23 Tests/scripts/prototype-flowGenerator/calcOnOffTimes.m

@@ -22,7 +22,8 @@
 ## Author: anderson <anderson@duvel-ThinkCentre-M93p>
 ## Created: 2017-05-03
 
-%function [onOff onTimes offTimes psCounter fileSize] = calcOnOffTimes (arrival_time, delta_time, psSize_list, cut_time, min_on_time)
+
+%% calcOnOff times complete
 function [onOff onTimes offTimes pktCounter fileSize] = calcOnOffTimes (arrival_time, delta_time, psSize_list, cut_time, min_on_time)
 	% in: number of inter packet times
 	m = length(delta_time);

### 2017-08-23 Tests/scripts/prototype-flowGenerator/delete_this/emissionAlgorithmTest.m

@@ -1,4 +1,7 @@
 %#!/usr/bin/octave-cli -qf
+
+% this script intend to simulate the emission, but was not finished
+
 % constants 
 %n_samples = 10000;
 %FILE_CUT_TIME = 0.5;

### 2017-08-23 Tests/scripts/prototype-flowGenerator/emissionSimulation.m

@@ -22,6 +22,7 @@
 ## Author: anderson <anderson@duvel-ThinkCentre-M93p>
 ## Created: 2017-05-03
 
+% This functions show represent emission times of the traffic generator, but was not finished
 function [list_generated] = emissionSimulation (onTimes, offTimes, lambdaOnOffInterfile, lambdaFile)
 	list_generated = [0];
 	lambdaOn = lambdaOnOffInterfile(1);

### 2017-08-23 Tests/scripts/prototype-flowGenerator/test_sessionOnOffTimes.m

@@ -1,4 +1,4 @@
-%#!/usr/bin/octave-cli -qf
+#!/usr/bin/octave-cli -qf
 % constants 
 n_samples = 10000;
 SESSION_CUT_TIME = 2.90;

### 2017-09-19 Docs/Thesis/docs/appendix/appendixE.tex
**IMPORTANTE MODIFICATIONS**: now the Prototypes/ dir is removed, and all simulations and validation tests are unther Tests/ and are in a Python project format

\chapter{Publications}

\section{IX DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA)}
\includepdf[pages=-]{figures/apE/eadca-article2016.pdf}

\section{X DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA)}
\includepdf[pages=-]{figures/apE/eadca-article2017.pdf}

\section{Generic Paper}
\includepdf[pages=-]{figures/apE/paper.pdf}

### 2017-09-19 Docs/Thesis/docs/chapter4.tex
**IMPORTANTE MODIFICATIONS**: now the Prototypes/ dir is removed, and all simulations and validation tests are unther Tests/ and are in a Python project format

@@
 	\label{tab:mehtods}
-	\begin{tabular}{|l|l|}
+	\begin{tabular}{|l|l|l|}
 		\hline
-		Link Layer                          & \multirow{3}{*}{Packets header's data} \\ \cline{1-1}
-		Network Layer                       &                                       \\ \cline{1-1}
-		Transport Layer                     &                                       \\ \hline
-		Application Layer                   & Application Match Table                    \\ \hline
-		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$                             \\ \cline{2-2} 
-		& 
-		Algorithm: $stochasticModelFitting$                    \\ \hline
-		Packet Sizes                        & Algorithm: $stochasticModelFitting$                    \\ \hline
+		Layer & Method & Variables \\
+		\hline
+		Link Layer  & \multirow{3}{*}{Packets header's data} & \texttt{link\_layer}, \texttt{link\_layer.mac\_src}, \texttt{link\_layer.mac\_dst} \\ \cline{1-1}\cline{3-3}
+
+		Network Layer & & \texttt{network\_layer}, \texttt{network\_layer.src\_ip}, \texttt{network\_layer.dst\_ip}, \texttt{network\_layer.ttl},\texttt{}\\ \cline{1-1}\cline{3-3}
+
+		Transport Layer & & \texttt{transport\_layer}, \texttt{transport\_layer.dst\_port}, \texttt{transport\_layer.src\_port}\\ \hline
+
+		Application Layer  & Application Match Table  & \texttt{application\_layer} \\ \hline
+
+		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$  & \texttt{inter\_packet\_times}\\ 
+		\cline{2-2}\cline{3-3}  & Algorithm: $stochasticModelFitting$                    &\\  \hline
+		Packet Sizes  & Algorithm: $stochasticModelFitting$ &\\ \hline
 	\end{tabular}

### 2017-09-19 SIMITAR/apps/dummy-flow/src/dummy-flow.cpp

@@ -1,0 +1,133 @@
+#include <iostream>
+#include <string>
+#include <algorithm>
+#include <tclap/CmdLine.h>
+#include <NetworkTrace.h>
+#include <DummyFlow.h>
+#include <Defines.h>
+#include <Protocol.h>
+#include <SimitarWorkspace.h>
+
+/**
+ * Print an error message if the input argument is an invalid balue
+ * @param arg input CLI argument
+ * @param arg_name argument name
+ * @param expected_values message with expected values
+ */
+void cli_error_messege(std::string arg, std::string arg_name,
+		std::string expected_values_msg);
+
+/**
+ * Check if the CLI input argument is a valid value
+ * @param val input CLI argument.
+ * @param expectedVals vector with valid CLI arguments.
+ * @return
+ */
+bool cli_check_val(std::string val, std::vector<std::string> expectedVals);
+
+int main(int argc, char** argv)
+{
+	try
+	{
+		///
+		/// CLI parser
+		///
+
+		// program description
+		char progDescription[] = "SIMITAR dummy-flow component.";
+		// version information
+		char version[CHAR_BUFFER];
+		SimitarWorkspace workspace = SimitarWorkspace();
+		std::string str_version = workspace.version_tag() + ":"
+				+ workspace.version_name();
+		strcpy(version, str_version.c_str());
+
+		// comamnd line parsing
+		TCLAP::CmdLine cmd(progDescription, ' ', version);
+		TCLAP::ValueArg<std::string> mode_arg("m", "mode", "Operation mode, as a client or a server",
+				true, "", "string");
+		TCLAP::ValueArg<std::string> in_arg("x", "xml", "xml", true, "Compact Trace Descriptor XML. They are salved at data/xml/ directory.",
+				"string");
+		TCLAP::ValueArg<std::string> dst_list_arg("d", "dst-list-ip", "Text file in CSV format containing a list of desired destinations of IP and MAC adresses, used as servers, in the client mode. These destinations are addressed to the flows in a ring-oriented way.",
+				false, "", "string");
+		TCLAP::ValueArg<std::string> dst_server_arg("p", "dst-ip", "Instead of a textfile, defines a single server destination IP address in the command line.", false,
+				"", "string");
[…]

### 2017-09-19 SIMITAR/apps/iperf-flow/src/Main.cpp

@@ -1,0 +1,137 @@
+// Deps
+#include <iostream>
+#include <string>
+#include <string.h>
+#include <sys/types.h>
+#include <sys/wait.h>
+#include <unistd.h>
+#include <thread>         // std::thread
+#include <mutex>          // std::mutex
+#include <algorithm>
+#include <tclap/CmdLine.h>
+// Simitar
+#include <NetworkTrace.h>
+#include <DummyFlow.h>
+#include <SimitarWorkspace.h>
+// Local
+//#include "IperfFlowt.h"
+
+void cli_error_messege(std::string arg, std::string arg_name,
+		std::string expected_values_msg);
+
+bool cli_check_val(std::string val, std::vector<std::string> expectedVals);
+
+int main(int argc, char** argv)
+{
+	try
+	{
+		///
+		/// CLI parser
+		///
+
+		// program description
+		char progDescription[] = "SIMITAR dummy-flow component.";
+		// version information
+		char version[CHAR_BUFFER];
+		SimitarWorkspace workspace = SimitarWorkspace();
+		std::string str_version = workspace.version_tag() + ":"
+				+ workspace.version_name();
+		strcpy(version, str_version.c_str());
+
+		// comamnd line parsing
+		TCLAP::CmdLine cmd(progDescription, ' ', version);
+		TCLAP::ValueArg<std::string> mode_arg("m", "mode",
+				"Operation mode, as a client or a server", true, "", "string");
+		TCLAP::ValueArg<std::string> in_arg("x", "xml", "xml", true,
+				"Compact Trace Descriptor XML. They are saved at data/xml/ directory.",
+				"string");
+		TCLAP::ValueArg<std::string> dst_list_arg("d", "dst-list-ip",
+				"Text file in CSV format containing a list of desired destinations of IP and MAC adresses, used as servers, in the client mode. These destinations are addressed to the flows in a ring-oriented way.",
+				false, "", "string");
+		TCLAP::ValueArg<std::string> dst_server_arg("p", "dst-ip",
+				"Instead of a text file, defines a single server destination IP address in the command line.",
+				false, "", "string");
+		TCLAP::ValueArg<std::string> eth_arg("e", "ether",
+				"Ethernet interface to send the traffic, as provided by the command `ifconfig`.",
+				false, "", "string");
+
+		cmd.add(mode_arg);
+		cmd.add(in_arg);
[…]

### 2017-09-19 SIMITAR/build.py

@@ -4,36 +4,31 @@ import argcomplete
 import os
 
 def directory_tree():
+	os.system('rm -rf apps/RemoteSystemsTempFiles')
+	os.system('rm -rf RemoteSystemsTempFiles')
+	os.system('mkdir -p libsimitar/obj')
+	os.system('mkdir -p tests/xml')
+	os.system('mkdir -p pcaps')
+	os.system('mkdir -p trace-analyzer/obj')
 	os.system('mkdir -p data/config')
 	os.system('mkdir -p data/db')
 	os.system('mkdir -p data/log')
 	os.system('mkdir -p data/test')
 	os.system('mkdir -p data/xml')
-	os.system('mkdir -p libsimitar/obj')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
-	os.system('mkdir -p ')
 
 
 def clean():
-	os.system('rm -rf RemoteSystemsTempFiles')
-	os.system('rm -rf apps/RemoteSystemsTempFiles')
+	print_header("Directory tree");
+	directory_tree()
 	os.system('make -C libsimitar/ clean')
 	os.system('make -C  trace-analyzer/ clean')
 	os.system('make -C  tests/ clean')
 	# os.system('make -C clean apps/')
 
+
 def build():
-	os.system('rm -rf RemoteSystemsTempFiles')
-	os.system('rm -rf apps/RemoteSystemsTempFiles')
+	print_header("Directory tree");
+	directory_tree()
 	print_header("Libsimitar");
 	os.system('make -C libsimitar/')
 	print_header("Trace Analyzer");
@@ -42,25 +37,29 @@ def build():
 	os.system('make -C tests/')
 	#print_header("FlowGen Apps");
 	# os.system('make -C apps/')
-	
+
 
 def print_header(component_name):
 	print("");
 	print("################################################################################")
-	print(component_name)
+	print("# " + component_name)
 	print("################################################################################")	
+
 
 def print_tutorial():
 	print_header("Tutorial")
 	print('(1) Now run, at the workspace dir (SIMITAR/), run:\n source data/config/simitar-workspace.config.sh\nIt will set the enviroment variables needed.')
[…]

### 2017-09-19 SIMITAR/libsimitar/DataProcessor.h

@@ -34,6 +34,7 @@
 #include "NetworkTrace.h"
 #include "StochasticModelFit.h"
 #include "RegressionTests.h"
+#include "NetworkFlowFactory.h"
 //#include "MesserLog.h"
 
 //namespaces

### 2017-09-19 SIMITAR/libsimitar/DatabaseInterface.h

@@ -12,18 +12,16 @@
 
 //include libraries
 #include <iostream>
-#include <stdio.h>
-#include <stdlib.h>
-#include <sqlite3.h>
 #include <string>
 #include <array>
 #include <cstring>
-#include <string.h>
 #include <list>
 #include <errno.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <sqlite3.h>
 
 //local includes
-//#include "MesserLog.h"
 #include "Protocol.h"
 #include "cfunctions.h"
 #include "SimitarWorkspace.h"

### 2017-09-19 SIMITAR/libsimitar/Defines.h

@@ -7,13 +7,12 @@
 
 #ifndef DEFINES_H_
 #define DEFINES_H_
-//#include <string>
-using namespace std;
+//using namespace std;
 
-#include <plog/Init.h>
-#include <plog/Log.h>
-#include <plog/Appenders/ColorConsoleAppender.h>
-#include <plog/Appenders/RollingFileAppender.h>
+//#include <plog/Init.h>
+//#include <plog/Log.h>
+//#include <plog/Appenders/ColorConsoleAppender.h>
+//#include <plog/Appenders/RollingFileAppender.h>
 
 /**
 Alguns tutoriais importantes:
@@ -318,9 +317,10 @@ typedef enum information_criterion_enum
 
  */
 
+/*
 
 // Log macros
-#define PLOG_INIT() plog::RollingFileAppender<plog::CsvFormatter> fileAppender("MultiAppender.csv", 8000, 3); \
+#define SIMITAR_PLOG_INIT() plog::RollingFileAppender<plog::CsvFormatter> fileAppender("MultiAppender.csv", 8000, 3); \
 		plog::ColorConsoleAppender<plog::TxtFormatter> colorConsoleAppender; \
 		plog::init(plog::debug, &colorConsoleAppender).addAppender(&fileAppender);
 
@@ -336,6 +336,6 @@ typedef enum information_criterion_enum
 #define PLOG_DEBUG LOG_DEBUG  << "[" << __FILE__ << "] "
 #define PLOG_VERBOSE LOG_VERBOSE  << "[" << __FILE__ << "] "
 
-
+*/
 
 #endif /* DEFINES_H_ */

### 2017-09-19 SIMITAR/libsimitar/DitgFlow.cpp

@@ -1,0 +1,256 @@
+/*
+ * DitgFlow.cpp
+ *
+ *  Created on: 15 de set de 2017
+ *      Author: anderson
+ */
+
+#include "DitgFlow.h"
+
+DitgFlow::DitgFlow()
+{
+	// TODO Auto-generated constructor stub
+
+}
+
+DitgFlow::~DitgFlow()
+{
+	// TODO Auto-generated destructor stub
+}
+
+int DitgFlow::server()
+{
+	// popen args
+	FILE *in;
+	char buff[512];
+	//iperf args
+
+	char command[2048] = "ITGRecv ";
+	printf("NOTE: Use Compact Trace Descriptors parameterized in milliseconds (sufix .ms) in the client side.\n");
+
+	if (!(in = popen(command, "r")))
+	{
+		std::cerr << "DitgFlow error: cannot execute command `" << command
+				<< "`" << std::endl;
+		return -1;
+	}
+
+	while (fgets(buff, sizeof(buff), in) != NULL)
+	{
+		simitar_iostream_mutex.lock();
+		std::cout << buff;
+		simitar_iostream_mutex.unlock();
+	}
+
+	pclose(in);
+	return(0);
+}
+
+void DitgFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
+		const uint& npackets, const uint& nbytes, const string& netInterface)
+{
+	simitar_iostream_mutex.lock();
+	printf("command:%s\n",
+			ditg_command(onTime, npackets, nbytes, netInterface).c_str());
+	simitar_iostream_mutex.unlock();
+
+	/*
+	 // popen args
+	 FILE *in;
+	 char buff[512];
+	 //iperf args
+
+	 char command[2048];
+	 strcpy(command,
+	 ditg_command(onTime, npackets, nbytes, netInterface).c_str());
+
+	 if (!(in = popen(command, "r")))
+	 {
+	 std::cerr << "IperfFlow error: cannot execute command `" << command
+	 << "`" << std::endl;
+	 return;
+	 }
+
+	 while (fgets(buff, sizeof(buff), in) != NULL)
+	 {
+	 simitar_iostream_mutex.lock();
+	 std::cout << buff;
+	 simitar_iostream_mutex.unlock();
+	 }
+
+	 pclose(in);
+	 */
+}
+
+std::string DitgFlow::ditg_command(const time_sec& onTime, const uint& npackets,
[…]

### 2017-09-19 SIMITAR/libsimitar/DitgFlow.h

@@ -1,0 +1,50 @@
+/*
+ * DitgFlow.h
+ *
+ *  Created on: 15 de set de 2017
+ *      Author: anderson
+ */
+
+#ifndef DITGFLOW_H_
+#define DITGFLOW_H_
+
+#include "DummyFlow.h"
+
+/**
+ *
+ */
+class DitgFlow: public DummyFlow
+{
+public:
+	/**
+	 *
+	 */
+	DitgFlow();
+	/**
+	 *
+	 */
+	virtual ~DitgFlow();
+	/**
+	 *
+	 * @return
+	 */
+	int server();
+
+	/**
+	 *
+	 * @param flowId
+	 * @param onTime
+	 * @param npackets
+	 * @param nbytes
+	 * @param netInterface
+	 */
+	void flowGenerate(const counter& flowId, const time_sec& onTime,
+			const uint& npackets, const uint& nbytes,
+			const string& netInterface);
+
+private:
+	std::string ditg_command(const time_sec& onTime, const uint& npackets,
+			const uint& nbytes, const string& netInterface);
+};
+
+#endif /* DITGFLOW_H_ */

### 2017-09-19 SIMITAR/libsimitar/DummyFlow.cpp

@@ -20,6 +20,12 @@ void DummyFlow::print()
 {
 }
 
+int DummyFlow::server()
+{
+	printf("[Server-mode operation]\n");
+	return (0);
+}
+
 void DummyFlow::flowStart()
 {
 	//MESSER_LOG_INIT(DEBUG);
@@ -67,9 +73,6 @@ void DummyFlow::flowStart()
 
 }
 
-//void DummyFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
-//		const unsigned int& npackets, uint nbytes, const uint& nbytes,
-//		const string& netInterface)
 void DummyFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
 		const uint& npackets, const uint& nbytes, const string& netInterface)
 {
@@ -97,89 +100,18 @@ void DummyFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
 	////////////////////////////////////////////////////////////////////////////
 	flow_str_print += " Link[" + Protocol(this->getLinkProtocol()).str() + "]";
 
-	/*
-	 flow_str_print += " Link[";
-	 prt = this->getLinkProtocol();
-	 if (prt == PROTOCOL__ETHERNET)
-	 {
-	 flow_str_print += "Ethernet";
-	 }
-	 else
-	 {
-	 flow_str_print += "Ethernet";
-	 }
-	 flow_str_print += "]";
-	 */
 	////////////////////////////////////////////////////////////////////////////
 	/// Network-layer protocol
 	////////////////////////////////////////////////////////////////////////////
 	flow_str_print += " Network[" + Protocol(this->getNetworkProtocol()).str()
 			+ "]";
 
-	/*
-	 flow_str_print += " Network[";
-	 prt = this->getNetworkProtocol();
-	 if (prt == PROTOCOL__IPV4)
-	 {
-	 flow_str_print += "IPv4: ";
-	 }
-	 else if (prt == PROTOCOL__IPV6)
-	 {
-	 flow_str_print += "IPv6: ";
-	 }
-	 else
-	 {
-	 flow_str_print += std::to_string(prt) + ": ";
-	 }
-	 flow_str_print += this->getNetworkSrcAddr() + " > "
-	 + this->getNetworkDstAddr() + "]";
-	 */
 	////////////////////////////////////////////////////////////////////////////
[…]

### 2017-09-19 SIMITAR/libsimitar/DummyFlow.h

@@ -25,6 +25,11 @@
  } l2_addr;
  */
 
+typedef enum
+{
+	method_usleep, method_pooling, method_select
+} sleep_method;
+
 class DummyFlow: public NetworkFlow
 {
 public:
@@ -45,15 +50,21 @@ public:
 
 	/**
 	 *
+	 * @return
+	 */
+	int server();
+
+	/**
+	 *
 	 * @param flowId
 	 * @param onTime
 	 * @param npackets
 	 * @param nbytes
 	 * @param netInterface
 	 */
-	void flowGenerate(const counter& flowId,
-				const time_sec& onTime, const uint& npackets, const uint& nbytes,
-				const string& netInterface);
+	void flowGenerate(const counter& flowId, const time_sec& onTime,
+			const uint& npackets, const uint& nbytes,
+			const string& netInterface);
 //	void flowGenerate(const counter& flowId, const time_sec& onTime,
 //			const unsigned int& npackets, const uint& nbytes,
 //			const string& netInterface);
@@ -69,6 +80,13 @@ public:
 		{	flowStart();});
 	}
 
+private:
+
+	/**
+	 *
+	 * @param sleep_time
+	 */
+	void fsleep(time_sec sleep_time);
 };
 
 #endif /* DUMMYFLOW_H_ */

### 2017-09-19 SIMITAR/libsimitar/IperfFlow.cpp

@@ -1,0 +1,197 @@
+/*
+ * IperfFlow.cpp
+ *
+ *  Created on: 13 de set de 2017
+ *      Author: anderson
+ */
+
+#include "IperfFlow.h"
+
+IperfFlow::IperfFlow()
+{
+}
+
+IperfFlow::~IperfFlow()
+{
+}
+
+int IperfFlow::server()
+{
+	// popen args
+	FILE *in;
+	char buff[512];
+	//iperf args
+
+	char command[2048] = "iperf -s";
+	printf("NOTE: Use Compact Trace Descriptors parameterized in seconds (sufix .sec) in the client side.\n");
+	if (!(in = popen(command, "r")))
+	{
+		std::cerr << "IperfFlow error: cannot execute command `" << command
+				<< "`" << std::endl;
+		return -1;
+	}
+
+	while (fgets(buff, sizeof(buff), in) != NULL)
+	{
+		simitar_iostream_mutex.lock();
+		std::cout << buff;
+		simitar_iostream_mutex.unlock();
+	}
+
+	pclose(in);
+	return(0);
+}
+
+void IperfFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
+		const uint& npackets, const uint& nbytes, const string& netInterface)
+{
+	// popen args
+	FILE *in;
+	char buff[512];
+	//iperf args
+
+	char command[2048];
+	strcpy(command,
+			iperf_command(onTime, npackets, nbytes, netInterface).c_str());
+
+	if (!(in = popen(command, "r")))
+	{
+		std::cerr << "IperfFlow error: cannot execute command `" << command
+				<< "`" << std::endl;
+		return;
+	}
+
+	while (fgets(buff, sizeof(buff), in) != NULL)
+	{
+		simitar_iostream_mutex.lock();
+		std::cout << buff;
+		simitar_iostream_mutex.unlock();
+	}
+
+	pclose(in);
+}
+
+/**
+ Usage: iperf [-s|-c host] [options]
+ iperf [-h|--help] [-v|--version]
+
+ Client/Server:
+ u		-b, --bandwidth #[KMG | pps]  bandwidth to send at in bits/sec or packets per second
+ x		-e, --enhancedreports    use enhanced reporting giving more tcp/udp and traffic information
+ u 		-f, --format    [kmKM]   format to report: Kbits, Mbits, KBytes, MBytes
+ x		-i, --interval  #        seconds between periodic bandwidth reports
[…]

### 2017-09-19 SIMITAR/libsimitar/NetworkFlow.cpp

@@ -14,25 +14,23 @@
 //#include "NemesisFlow.h"
 //#include "LibtinsFlow.h"
 
+/*
 NetworkFlow* NetworkFlow::make_flow(const string& choise)
 {
-/*
 
-	if ((choise == "ditg") || (choise == "DITG") || (choise == "D-ITG"))
+	if ((choise == "ditg"))
 	{
 		return new DitgFlow;
 	}
-	else if ((choise == "iperf") || (choise == "Iperf") || (choise == "IPERF"))
+	else if ((choise == "iperf"))
 	{
 		return new IperfFlow;
 	}
-	else if ((choise == "ostinato") || (choise == "Ostinato")
-			|| (choise == "OSTINATO"))
+	else if ((choise == "ostinato"))
 	{
 		return new OstinatoFlow;
 	}
-	else if ((choise == "Libtins") || (choise == "libtins")
-			|| (choise == "LIBTINS"))
+	else if ((choise == "libtins") || (choise == "tins"))
 	{
 		return new LibtinsFlow;
 	}
@@ -40,11 +38,10 @@ NetworkFlow* NetworkFlow::make_flow(const string& choise)
 	{
 		return new DummyFlow;
 	}
-*/
 
 	return new DummyFlow;
-
 }
+*/
 
 NetworkFlow::NetworkFlow()
 {
@@ -134,7 +131,7 @@ NetworkFlow::~NetworkFlow()
 void NetworkFlow::print()
 {
 	//TODO
-	cout << "flow created" << endl;
+	std::cout << "flow created" << endl;
 }
 
 int NetworkFlow::randTranportPort()

### 2017-09-19 SIMITAR/libsimitar/NetworkFlowFactory.cpp

@@ -1,0 +1,63 @@
+/*
+ * NetworkFlowFactory.cpp
+ *
+ *  Created on: 14 de set de 2017
+ *      Author: anderson
+ */
+
+#include "NetworkFlowFactory.h"
+
+NetworkFlowFactory::NetworkFlowFactory()
+{
+
+}
+
+NetworkFlowFactory::~NetworkFlowFactory()
+{
+}
+
+
+NetworkFlow* NetworkFlowFactory::make_flow(const string& choise)
+{
+	PLOG_INIT(debug);
+	std::string choise_lc;
+
+	// Allocate the destination space
+	choise_lc.resize(choise.size());
+	// Convert the source string to lower case storing the result in destination string
+	std::transform(choise.begin(), choise.end(), choise_lc.begin(), ::tolower);
+
+	if (choise_lc == "dummy")
+	{
+		PLOG_DEBUG << "Creating DummyFlow";
+		return new DummyFlow;
+	}
+	else if(choise_lc == "ditg")
+	{
+		PLOG_DEBUG << "Creating DitgFlow";
+		return new DitgFlow;
+	}
+	else if(choise_lc == "iperf")
+	{
+		PLOG_DEBUG << "Creating IperfFlow";
+		return new IperfFlow;
+	}
+	else if((choise_lc == "tins") || (choise_lc == "libtins"))
+	{
+		PLOG_DEBUG << "Creating TinsFLow";
+		printf("TODO\n");
+	}
+	else if (choise_lc == "ostinato"){
+		PLOG_DEBUG << "Creating OstinatoFLow";
+		printf("TODO\n");
+	}
+
+	PLOG_WARN << ERRORMSG_BAD_VALUE << choise ;
+	PLOG_INFO << "Instantiating DummyFlow as default";
+	return new DummyFlow;
+}
+
+std::string NetworkFlowFactory::support_tools()
+{
+	return("dummy, ditg, iperf, tins");
+}

### 2017-09-19 SIMITAR/libsimitar/NetworkTrace.cpp

@@ -7,12 +7,6 @@
 
 #include "NetworkTrace.h"
 
-//NetworkTrace::NetworkTrace(long int nFlows)
-//{
-//	netFlow = new NetworkFlow[nFlows + 1];
-//	numberOfFlows = nFlows + 1;
-//}
-
 NetworkTrace::NetworkTrace()
 {
 	//MESSER_LOG_INIT(NOTICE);
@@ -25,7 +19,7 @@ NetworkTrace::NetworkTrace(const string& fileName,
 	//MESSER_LOG_INIT(LOG_LEVEL_TRACE);
 
 	long int nflows = 0;
-	long int fcounter = 0;
+	//long int fcounter = 0;
 	string strBuffer;
 	unsigned int uintBuffer;
 	unsigned long int lintBuffer;
@@ -39,9 +33,9 @@ NetworkTrace::NetworkTrace(const string& fileName,
 
 	// Read the xml file into a vector
 	//ifstream theFile(fileName);
-	ifstream theFile(fileName); //TODO
-	vector<char> buffer((istreambuf_iterator<char>(theFile)),
-			istreambuf_iterator<char>());
+	std::ifstream theFile(fileName); //TODO
+	std::vector<char> buffer((std::istreambuf_iterator<char>(theFile)),
+			std::istreambuf_iterator<char>());
 	buffer.push_back('\0');
 
 	// Parse the buffer using the xml file parsing library into doc
@@ -68,13 +62,14 @@ NetworkTrace::NetworkTrace(const string& fileName,
 	charvet2type(root_node->first_attribute("n_flows")->value(), nflows);
 	//for (fcounter = 0; fcounter < nflows; fcounter++)
 	//{
-	fcounter = 0;
+	//fcounter = 0;
 	for (xml_node<> * flow_node = root_node->first_node("flow"); flow_node;
 			flow_node = flow_node->next_sibling())
 	{
 
 		/// Create flow
-		NetworkFlow* netFlow = NetworkFlow::make_flow(trafficGenEngine);
+		//NetworkFlow* netFlow = NetworkFlow::make_flow(trafficGenEngine);
+		NetworkFlow* netFlow = NetworkFlowFactory::make_flow(trafficGenEngine);
 		//NetworkFlow* netFlow = NetworkFlow::make_flow("dummy");
 		//MESSER_DEBUG("netFlow[%d]  @<%s, %s>", fcounter);
 
[…]

### 2017-09-19 SIMITAR/libsimitar/NetworkTrace.h

@@ -11,22 +11,17 @@
 //external libs
 //#include <cstring>
 #include <string.h>
-#include <stdio.h>
+#include <cstdio>
+#include <cstdlib>
 #include <iostream>
-#include <stdio.h>
-#include <stdlib.h>
-#include <pthread.h>
-#include <errno.h>
-//#include <cstdlib>
 #include <thread>
-#include <unistd.h>
 #include <vector>
+#include <errno.h>
+#include <unistd.h>
 #include <rapidxml/rapidxml.hpp>
 #include <rapidxml/rapidxml_print.hpp>
 #include <rapidxml/rapidxml_iterators.hpp>
 #include <rapidxml/rapidxml_utils.hpp>
-
-//#include "rapidxml-1.13/rapidxml.hpp"
 
 using namespace rapidxml;
 using std::string;
@@ -38,17 +33,15 @@ using std::endl;
 using std::vector;
 
 //local libs
+#include "SimitarWorkspace.h"
+#include "CsvFile.h"
+#include "NetworkFlow.h"
+#include "NetworkFlowFactory.h"
+#include "Protocol.h"
 #include "Defines.h"
 #include "cfunctions.h"
-#include "NetworkFlow.h"
-#include "Protocol.h"
 #include "RegressionTests.h"
-#include "CsvFile.h"
-#include "SimitarWorkspace.h"
-//#include "MesserLog.h"
 
-//#define LOG_LEVEL INFO
-#define LOG_LEVEL_TRACE DEBUG
 
 //namespaces
 typedef struct flow_data_struct flowData;
@@ -164,7 +157,12 @@ public:
 	 * @param verbose
 	 * @return
 	 */
-	int exec(bool verbose);
+	int exec();
+
+	/**
+	 *
+	 */
+	void server();
 
 	/**
 	 *
@@ -191,11 +189,23 @@ public:
 	 * interface provided as argument. If the interface is not specified,
 	 * it uses the first Ethernet interface active.
 	 * @param filename
-	 * @param etherInterface
-	 * @param mac
+	 * @param etherInterface local interfaces names, as provided by `ifconfig` command
+	 * @param set_mac true sets the MAC destination addrs, false do not
 	 */
 	void clientServerIps(const char* filename, const char* etherInterface = "",
 			bool set_mac = false);
+
+	/**
+	 * Sets a list of IP and MAC addresses provided as string as
+	 * destinations of all flows in the NetworkTrace, and the local IP
[…]

### 2017-09-19 SIMITAR/libsimitar/SimitarWorkspace.h

@@ -10,12 +10,17 @@
 
 #include <iostream>
 #include <cstdlib>
-#include <stdlib.h>
-#include <string.h>
 #include <string>
+#include <thread>         // std::thread
+#include <mutex>          // std::mutex
 
 #include "Defines.h"
 #include "PlogMacros.h"
+
+// generic iostream mutex
+extern std::mutex simitar_iostream_mutex;
+// ethernet interface mutex
+extern std::mutex simitar_eth_mutex;
 
 class SimitarWorkspace
 {
@@ -48,7 +53,6 @@ public:
 	 * @return
 	 */
 	std::string dir_xml();
-
 
 	std::string database_version();
 
@@ -123,7 +127,6 @@ public:
 	 * @return
 	 */
 	std::string version_name();
-
 
 	/**
 	 *

### 2017-09-19 SIMITAR/libsimitar/cfunctions.h

@@ -8,10 +8,11 @@
 #ifndef CFUNCTIONS_H_
 #define CFUNCTIONS_H_
 
-#include <stdio.h>
-#include <stdlib.h>
+#include <cstdio>
+#include <cstdlib>
+#include <cstring>
+#include <cassert>
 #include <assert.h>
-#include <string.h>
 #include <iostream>
 #include <iomanip>
 #include <string>
@@ -19,15 +20,9 @@
 #include <armadillo>
 #include <vector>
 
-
 #include "Defines.h"
 #include "RegressionTests.h"
 
-//using std::list;
-//using std::vector;
-//using std::string;
-//using std::cout;
-//using std::endl;
 using namespace arma;
 
 #define _TESTS_FLAG 1

### 2017-09-19 SIMITAR/tests/integration/integration-tests.cpp

@@ -72,9 +72,9 @@ int main() {
 		////dp.calculate(experimentName, &dbif, trace);
 		//trace->setTrafficGenEngine("D-ITG");
 		//trace->exec(true);
-		NetworkTrace traceCdt =  NetworkTrace("kkk.xml", "D-ITG");
+		NetworkTrace traceCdt =  NetworkTrace("kkk.xml", "dummy");
 		//NetworkTrace traceCdt =  NetworkTrace("changed-ips-macs-trace.xml", "Dummy");
-		traceCdt.exec(true);
+		traceCdt.exec();
 
 	}
 

### 2017-09-19 SIMITAR/trace-analyzer/src/Main.cpp

@@ -7,7 +7,6 @@
 //============================================================================
 
 // Deps
-#include <iostream>
 #include <string>
 #include <iostream>
 #include <algorithm>
@@ -47,16 +46,16 @@ stored inside the SIMITAR workspace in the directory `data/xml/`, and may be edi
 		strcpy(version, str_version.c_str());
 
 		//vars
-		time_scale dpTimeScale;
+		//time_scale dpTimeScale;
 
 		TCLAP::CmdLine cmd(progDescription, ' ', version);
 
 		TCLAP::ValueArg<std::string> trace_arg("t", "trace",
 				"Trace used to generate the Compact Trace Descriptor", true, "",
 				"string");
-		TCLAP::ValueArg<std::string> timescale_arg("s", "time-scale",
-				"Time scale of the Compact Trace Descriptor. `seconds` or `milliseconds`. Default: `milliseconds``",
-				false, "milliseconds", "string");
+		//TCLAP::ValueArg<std::string> timescale_arg("s", "time-scale",
+		//		"Time scale of the Compact Trace Descriptor. `seconds` or `milliseconds`. Default: `milliseconds``",
+		//		false, "milliseconds", "string");
 		TCLAP::ValueArg<double> minon_arg("n", "min-on",
 				"min_on_time constant used by the algorithm calcOnOff. Defines the minimum time of a packet train. Default: 0.1s",
 				false, 0.1, "double");
@@ -71,7 +70,7 @@ stored inside the SIMITAR workspace in the directory `data/xml/`, and may be edi
 				false, 30, "int");
 
 		cmd.add(trace_arg);
-		cmd.add(timescale_arg);
+		//cmd.add(timescale_arg);
 		cmd.add(minon_arg);
 		cmd.add(minoff_arg);
 		cmd.add(criterion_arg);
@@ -80,19 +79,20 @@ stored inside the SIMITAR workspace in the directory `data/xml/`, and may be edi
 		cmd.parse(argc, argv);
 
 		std::string trace_name = trace_arg.getValue();
-		std::string timescale_val = timescale_arg.getValue();
+		//std::string timescale_val = timescale_arg.getValue();
 		double on_val = minon_arg.getValue();
 		double off_val = minoff_arg.getValue();
 		std::string crit_val = criterion_arg.getValue();
[…]

### 2017-09-19 SIMITAR/trace-analyzer/test.sh

@@ -1,2 +1,5 @@
 #!/bin/bash
+cd ..
+source data/config/simitar-workspace-config.sh
+cd trace-analyzer/; 
 ./trace-analyzer --trace "live_background-traffic-1"

### 2017-09-19 Tests/PrototypeDataProcessor/exec.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+./run.py ../pcaps/skype.pcap skype 
+./run.py ../pcaps/wireshark-wiki_http.pcap wireshark-wiki_http 
+./run.py ../pcaps/wireshark-wiki_ospf.pcap wireshark-wiki_ospf
+./run.py ../pcaps/bigFlows.pcap bigFlows
+./run.py ../pcaps/lanDiurnal.pcap lanDiurnal
+
+
+        

### 2017-09-19 Tests/SimulationMininet/run.py

@@ -1,0 +1,8 @@
+# variaveis para definir: capture_name, duration(exec_time) interface ethernet(eth_if) e binario(bin_file)
+# 1. executar tcpdump na interface eth_if capturando pcap capture_name, e salvando no diretorio ./pcaps/
+# 2. executar binario do simitar bin_file
+# 3. depois de exec_time + 1s, matar o tcpdump
+
+
+
+

### 2017-09-26 Docs/EADCA-2016/abstract.tex
new papers on Docs EADCA-2016 and EADCA-2017, also a temp script called Tests/PrototypeDataProcessor/dataProcessor/calcCostFunction2.py to plot cost functions for trace, but still not automated :\

New emerging technologies have a larger unpredictability, compared to legacy equipment. They require a larger set of meaningful tests on many different scenarios. But, in the open source world is hard to find a single tool able to provide realism, speed, easy usage and flexibility at the same time.  Most of the tools are monolithic and devoted to specific purposes. This work presents a flexible and extensible framework which aims to decouple synthetic traffic modelling from its traffic generator engine. Through a new abstraction layer, it would become possible to use modern and throughput optimized tools to create realistic traffic, in an automated way. This enables a platform agnostic configuration and reproduction of complex scenarios via analytical models. Also we use \textit{pcap} files and live-capture to create "Compact Trace Descriptors".

### 2017-09-26 Docs/EADCA-2016/body.tex
new papers on Docs EADCA-2016 and EADCA-2017, also a temp script called Tests/PrototypeDataProcessor/dataProcessor/calcCostFunction2.py to plot cost functions for trace, but still not automated :\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Emerging technologies such as SDN and NFV are great promises. If succeeding at large-scale, they should change the development and operation of computer networks. But, enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Since virtualization brings some degradation on latency and throughput it must be kept as small as possible.  On stability and resilience, dedicated hardware has a more foreseeable behaviour than VNFs. Along with this, newer extra layers (hypervisor, orchestrator) may generate newer security weaknesses.  Thus, guarantee  the Service Layer Agreements on emerging scenarios is now a harder question. Applications may have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. As conclude by many investigations, realistic and burstiness traffic impacts on bandwidth measurement accuracy\cite{background-traffic-matter}\cite{legotg-paper}. Also, realistic workload generators are essential security research. It can provide training and validation of many tasks, such as  anomaly and thread detection, intrusion and malicious workload.  Moreover, all these aspects have to be validated at actual traffic rates. Thus, there is a demand for tests able to address realism at high throughput rates.

Emerging technologies such as SDN and NFV are great promises. If succeeding at large-scale, they should change the development and operation of computer networks. But, enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}.  Thus, guarantee  the Service Layer Agreements on emerging scenarios is now a harder question. Applications may have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. As conclude by many investigations, realistic and burstiness traffic impacts on bandwidth measurement accuracy\cite{legotg-paper}. Also, realistic workload generators are essential security research\cite{ditg-paper}. Thus, there is a demand for tests able to address realism at high throughput rates.

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}. Each tool uses different methods on traffic generation, focusing on a certain aspects. Some traffic generator tools provide support emulation of single  application workloads. But this is not enough to describe an actual Service Provider(ISP) load or even a LAN scenario. Other tools work as packet replay engines, such as TCPreplay and TCPivo. Although in that way is possible to produce a realistic workload at high rates, it comes with some issues. First, the storage space required becomes huge for long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources. Many tools aim the support of a larger set of protocols and high-performance such Seagull and Ostinato. Many are also able to control inter-departure time and packet size using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen. They can provide a good control of the traffic, and high rates. But, in this case, selecting a good configuration is by itself a research project, since how to use each parameter to simulate a specific scenario is a hard question \cite{selfsimilar-ethernet}. It is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic patterns and  experimental evaluation. Some tools like Swing and Harpoon, try to use the best of both worlds. Both use capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels which are able to provide a high degree of realism\cite{swing-paper}. But they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels. Swing\cite{swing-paper} aims to generate realistic background traffic, not offering high throughput \cite{swing-paper} \cite{legotg-paper}. As is possible to see, this a result of the fact that its traffic generation engine is coupled to its modeling framework. You can't opt to use a newer/faster packet generator. The only way of replacing the traffic engine is changing and recompiling the original code. And this is a hard task.

This project aims to create a framework able solve many of presented issues.  It must be able to "learning" patterns and characteristics of real network traffic traces. Then, using packet generators and accelerators it should reproduce a network traffic with similar  characteristics. Based on observation of live captures or PCAP files, the software must choose the bests parametrized stochastic functions (from a list) to fit the data. These parametrized stochastic functions along with collected header features (such as protocols and addresses) will be record in a machine-readable file (such as XML or JSON) we baptise as a Compact Trace Descriptor (CTD). This data must serve as input for an API of a traffic generator. So it will be possible to control packet parameters, and flow's behaviours, through different APIs. Also, and speed-up may be achieved, though the use of DPDk's KNI interfaces\footnote{ \url{http://dpdk.org/doc/guides/sample_app_ug/kernel_nic_interface.html} }. So, the main goal is to offer an easier configuration, realism, at a higher speed than the available platforms today. Also, it will add programmability and abstraction to the traffic generation, since the user may edit or create a custom traffic descriptor in a platform agnostic way. The the intermediate layer of the figure ~\ref{fig:arquitetura-layer} summarize, goal of the project in an illustrative way.

\begin{figure}[H]
        {\centering
        \includegraphics[height=35mm]{figures/arquitetura-layer.png}
        \caption{Proposal representation in a layer diagram. It automates features such as configuration, modelling, and parametrization, intelligence, emulation, and abstraction through an additional layer.}
        \label{fig:arquitetura-layer}\par}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Literature review and related work}
\label{sec:literature-review}

%\subsection{Classes of traffic generators}
%\label{subsec:classes-traffic-generators}

A common taxonomy used on traffic generator tools based on the layer of operation. It divides them into four categories\cite{do-you-trust}:

\textit{Application-level/Special-scenarios traffic generators}: they emulate applications behaviours, through stochastic and responsive models. Eg.: Surge, GenSym.

\textit{Flow-level traffic generators}: they emulate features of the flow level, such as file transference and bursts. But do not model applications or packet behaviour.Eg.: Harpoon.

\textit{Packet-level traffic generators}: they model inter-departure time and packet size  through stochastic distributions. They focus on performance testing. Eg: D-ITG\cite{ditg-paper}, Ostinato, Seagull, TG.

\textit{Multi-level traffic generators}: These traffic generators models each mentioned layer, describing user and network behaviour. They generate an accurate background traffic, but usually, have bottlenecks on bandwidth. Eg.: Swing\cite{swing-paper}.

%Another important key point is that not every stochastic is able  to represent Ethernet traffic. As showed in many researchers, the Ethernet is self-similar and has a high variability. Self-similarity means it has a fractal-like shape. Characteristics seen in a small-scale of time, are expected to be seen on a long scale of time, as well. Other models, such as like Markov and Poisson-batch cannot capture "burstiness" in a long-term time scale. They do not capture, for example, traffic "spikes" on long-range "ripples". This is referred as Long-range dependence or degree of long-range dependence (LRD). One way to identify if a process is self-similar is checking its Hurst parameter, or Hurt exponent H, as a measure of the "burstiness" and LRD. A random process is self-similar and LRD if 0.5 < H < 1. High variability means, in mathematical terms, an infinite variance. Processes with such characteristic are heavy-tailed [19]. In practical terms, that means a sudden discontinuous change can always occur.  Heavy tail means that a stochastic distribution is not exponentially bounded [19]. This means that a value far from the mean does not have a negligible probability of occurrence. Some examples of heavy-tailed probabilistic functions are Weibull, Cauchy, log-normal, and t-distributions. Thus, self-similarity and high variability must be considered in the modelling.

%\subsection{Related Work}
%\label{subsec:related-work}

Varet et al. \cite{sourcesOnOff-paper} creates an application in C, called SourcesOnOff. It models the activity interval of packet trains using probabilistic distributions. To choose the best stochastic models, the authors captured many traffic traces using TCPdump. Then, they figure out what distribution (Weibull, Pareto, Exponential, Gaussian, etc.) fits better the original traffic traces, using the Bayesian Information Criterion. For this task, they choose the function with the smaller BIC. The smaller this value is, the better the function fits the data.

Bartlett et al. \cite{legotg-paper} implements a modular framework for composing custom traffic generation. Its goal is making easy the combine of different traffic generators and modulators in different test-beds. It automatizes the process of installation, execution, resource allocation and synchronization using a centralized orchestrator and a software repository. It already has support to many tools, and to add support to new tools is necessary to add and edit two files, called TGblock, and ExFile.

%\begin{figure}[H]
%        {\centering
%        \includegraphics[height=45mm]{figures/types-workload-tools}
%        \caption{}
%        \label{fig:wwwwwwww}\par}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Architecture}
\label{sec:system-architecture-and-requirements}

We developed and architecture that solves the listed issues. It has five components: a Sniffer, an SQLite database, a Trace Analyzer, a Flow Generator, and a Network Traffic Generator as a subsystem.

The Sniffer is responsible collecting data from the network traffic. It extracts data from the packets and stores them in the database. This information can be protocols, packet size, inter-arrival time, flows, and so on. Also, after finishing a capture, this component is the responsible for providing data visualization. It may  work over a PCAP file, or over an Ethernet interface. The prototype version of this component uses tsahrk to capture packets and Shell/Octave scripts. To improve performance and avoid bottlenecks, next implementation will use libtins librarie for packet processing. The criteria to classify the traffic into flows is the same of SDN switches: internet protocol, source/destination addresses, transport protocol, and source/destination transport ports. The framework uses an SQLite database.

The Trace Analyzer is the core of the project. It is the tool responsible for characterizing the trace. Using the stored information, breaks the trace into flows, and parametrize each of them.  The parameters are  header fields and stochastic functions/coefficients for each flow. The component models the behaviour of the trace on flow level and packet level. At the packet level, is possible to model the packet-size and the inter-departure time, during packet bursts (ON times). At the flow level, is possible to control bursts periods, session length,  and the number of bytes delivered. We will use likelihood criterions to choose the best probabilistic function and parameters. Options are the smaller error, Akaike information criterion, and Bayesian information criterion\cite{sourcesOnOff-paper}. It will sort the parametrized functions in a priority list. After the parametrization, the Trace Analyzer records these features in a machine-readable file (XML, JSON) called "Compact trace descriptor".  %This file describes each original traces' flow.

\begin{figure}[H]
        {\centering
        \includegraphics[height=50mm]{figures/qualification-HustExponent.png}
        \caption{Hurst exponent value of original and synthetic traces}
        \label{fig:hurst-exponent}\par}
\end{figure}

The Flow Generator pick these abstract parameters and feed an Ethernet workload generator tool. It crafts each flow in an independent way, in a different thread. The presented prototype just uses the D-ITG API as workload tool.  But it can use any packet-level traffic generator with API or CLI. This component handles the flow level models and parametrizes the packet-level tool underneath. Since each packet-level tool supports a different set of stochastic functions, the Flow Generator should pick the first compatible model from the priority list. But prototype presented here still uses simple models on packet and flow crafting, supporting just constant distributions. But the next release should support at packet-level heavy-tailed\cite{sourcesOnOff-paper} and Poison functions for the inter-departure times, and  bimodal distributions\cite{packet-distribution-model}\cite{udp-flows-model} for the packet size. At the flow level, two different alternatives can be used. Model file transference and session,  such as in Harpoon\cite{harpoon-paper}; or use an envelope process, as suggested by Melo et al\cite{envelope-process-equivalent-bandwidth}.

%\begin{figure}[ht!]
%        {\centering
%        \includegraphics[height=45mm]{figures/Component_Diagram_Alternative.pdf}
%        \caption{}
%        \label{fig:arquitetura-layer}\par}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Partial results}
\label{sec:partial-results}

To as proof of concept, we propose a set of tests. We choose them, based on tests used to ensure realism, on related many works \cite{sourcesOnOff-paper} \cite{swing-paper} \cite{legotg-paper}. They aim to ensure realism and similarity. Realism tests measure if a synthetic traffic has expected features of an Ethernet capture. Similarity tests measures if the generated traffic represents specific characteristics of the original one. Here, due the limited space, we will present just two results. The first, which test realism, is the Hurst exponent evaluation. It is able to test the self-similarity of the generated traffic. To be self-similar, a process must have a Hurst exponent between 0.5 and 1 \cite{selfsimilar-ethernet}. Also, usual values of Ethernet traffic lay between 0.8 and 0.9 \cite{selfsimilar-ethernet}.

Thus a realistic Ethernet traffic must have a Hurst exponent close to the last interval. The second test is Wavelet Multiresolution Energy Analysis. It is able to capture characteristics of the traffic at different time-scales. For example, it enables  visualization of a periodic tendency(decrease) or a self-similar tendency(increase) at a certain time scale. Also, at each point, it represents the mean energy of that signal at that time scale. So, similar Ethernet traffics must have slopes at close time-scales. Also, they must have close energy scales. More close are the curves, more similar are the traces.

The evaluated prototype support just constant functions. It selects the inter-departure time equal to the mean. The packet size is set as the most frequent value. The flow's start time and duration are the same from the observed traffic. We capture the original traffic trace on the laboratory LAN. The results are at figures ~\ref{fig:hurst-exponent} and ~\ref{fig:wavelet-mrea}. On both analysis, the generation of the synthetic trace was repeated 30 times. The keys which serves as input to D-ITG were randomly selected. At  is possible to see that the on both cases the Hurst exponent converge to the same value, close to 0.9. But, on the wavelet multiresolution analysis, both curves still different behaviours.

% validation figure sample
%\begin{figure}[H]
%    \centering
%    \subfigure[Original]{\label{fig:a}\includegraphics[height=45mm]{figures/Mbps-base}}
%	\subfigure[Synthetic]{\label{fig:b}\includegraphics[height=45mm]{figures/Mbps-qualification}}
%    \caption{Bandwidth comparison between original and synthetic traces. Granularity of the plot: 10ms }
%    \label{fig:mbps-comparison}
%\end{figure}

%\begin{figure}[H]
%    \centering
%    \subfigure[Original]{\label{fig:a}\includegraphics[height=55mm]{figures/Flow-base}}
%	\subfigure[Synthetic]{\label{fig:b}\includegraphics[height=55mm]{figures/Flow-qualification}}
%    \caption{Number of flows per second comparison between original and synthetic traces. Granularity of the plot: 1s}
%    \label{fig:mbps-comparison}
%\end{figure}

%\begin{figure}[H]
%        {\centering
%        \includegraphics[height=55mm]{figures/qualification-bw.png}
%        \caption{}
%        \label{fig:sss}\par}
%\end{figure}

\begin{figure}[H]
        {\centering
        \includegraphics[height=50mm]{figures/qualification-WaveletMREA}
        \caption{Wavelet Multiresolution Energy Analysis of the original and synthetic traces}
        \label{fig:wavelet-mrea}\par}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and future work}
\label{sec:conclusion-and-future-work}

The framework prototype was already able to generate a realistic (self-similar) Ethernet traffic. But, as expected, is still unable to represent well the particular features of the original traffic trace. This is a result of the, still, poor stochastic modelling. The next job will be implementing a significative modelling of the original traffic trace, through the specified methodology. We expect more significant results, them. Also, we will expand the framework to others workload platforms and compare the results. Packet acceleration could speed-up the performance, which may enable the reproduction of high-throughput traces. This can be implemented using DPDK. Finally, the results should be compared to Swing, on realism, similarity, and performance. This will give a measurement of how good is the framework, compared with others alternatives, and its strong and weak points.

### 2017-09-26 Docs/EADCA-2017/main.tex
new papers on Docs EADCA-2016 and EADCA-2017, also a temp script called Tests/PrototypeDataProcessor/dataProcessor/calcCostFunction2.py to plot cost functions for trace, but still not automated :\

\documentclass[11pt]{article}
\usepackage{eadca-template}
\usepackage[plain]{algorithm}

\usepackage[brazil,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{graphicx,url}
\usepackage[hang]{subfigure}
\usepackage{psfrag}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{hyperref}

% new packages
\usepackage{enumitem}
\usepackage{balance}
%\usepackage[showframe]{geometry}
%\usepackage{lipsum}
%\usepackage{subfig}
%\usepackage{float}
%\usepackage{subfigure}
%\usepackage{graphicx}
%\usepackage[showframe=true]{geometry}

\sloppy

\title{Using BIC and AIC for Ethernet traffic model selection. Is it worth?}

\author{Anderson dos Santos Paschoalon \and Christian Esteve Rothenberg}

\address{Departamento de Engenharia de Computa\c{c}\~{a}o e Automa\c{c}\~{a}o Industrial (DCA) \\
  Faculdade de Engenharia El\'{e}trica e de Computa\c{c}\~{a}o (FEEC) \\
  Universidade Estadual de Campinas (Unicamp)\\
  Caixa Postal 6101, 13083-970 -- Campinas, SP, Brasil
  \email{\{apaschoalon,chesteve\}@dca.fee.unicamp.br}}

\hyphenation{}
\pagestyle{fancy}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\twocolumn[
\maketitle
\thispagestyle{fancy}
\selectlanguage{english}

   \begin{abstract}
 In this work, we aim to evaluate how good are the information criterion AIC and BIC inferring which is the best stochastic process to describe Ethernet inter-packet times. Also, we check if there is a practical difference between using AIC or BIC. To do so, we use a set of stochastic distributions to represent inter-packet of a traffic trace and calculate AIC and BIC. To test the quality of  BIC and AIC guesses,  we define a cost function, based on the comparison of significant stochastic properties for internet traffic modeling, such as correlation, fractal-level and mean. Then, we compare both results.  In this short paper, we present just the results of a public free Skype-application packet capture, but we source as reference further analyzes on different traces. We conclude that for most of the cases AIC and BIC can guess right the best fitting, according to the standards of Ethernet traffic modeling.

   \end{abstract}

  \keywords{BIC, AIC, stochastic function, inter-packet times, correlation, Hurst exponent, heavy-tailed distribution, fractal-level, burstiness, linear-regression, weibull, pareto, exponential, normal, poison, maximum likelihood, Ethernet traffic, traffic modeling, fractal-level, pcap file, Skype traffic}
]

\selectlanguage{English}

\balance
\input{body}

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

\bibliographystyle{unsrt}

\bibliography{bibliography}

\end{document}

### 2017-09-26 Tests/PrototypeDataProcessor/dataProcessor/calcCostFunction2.py

@@ -1,0 +1,86 @@
+#!/usr/bin/python3
+_author_ = 'apaschoalon'
+
+import matplotlib.pyplot as plt
+import numpy as np
+import plotly.plotly as py
+import sys
+import numpy as np
+import csv
+import re
+import tkinter
+
+# command line argument: to de dir data
+#PATH_DIR = str(sys.argv[1])
+PATH_DIR =  '/home/anderson/ProjetoMestrado/Tests/PrototypeDataProcessor/plots/skype/'
+
+class CsvList:
+    def load(self, fileName):
+        result = []
+        reader = csv.reader(open(fileName))
+        comment = re.compile('^#.*')  # ignore commentaties
+        for row in reader:
+            key = row[0].strip()
+            res = comment.match(key)
+            if res != None:
+                continue
+            else:
+                value = row[1]
+                error = row[2]
+                listTuple = (key, value, error)
+                result.append(listTuple)
+        return (result)
+
+def list_truple_index(tuple_list, key, position):
+    retVal = [x for x, y in enumerate(tuple_list) if y[position] == key]
+    # return first match found
+    return(retVal[0])
+
+
+CsvL = CsvList()
+corr = CsvL.load(PATH_DIR + 'Correlation.dat')
+hurst = CsvL.load(PATH_DIR + 'Hurst Exponent.dat')
+mean = CsvL.load(PATH_DIR + 'Mean.dat')
+hurst_diff = []
+mean_diff = []
+corr_float = []
+costFunction  = []
+hurst_original = 0
+mean_original = 0
+
+i = 0
+for i in range(0, len(hurst)):
+    if hurst[i][0] == 'Original':
+        hurst_original =  float(hurst[i][1])
+    if mean[i][0] == 'Original':
+        mean_original = float(mean[i][1])
+
+for i in range(0, len(hurst)):
+    diffval = 0
+    if hurst[i][0] != 'Original':
+        hurst_diff.append((hurst[i][0], abs(float(hurst[i][1]) - hurst_original)))
+    if mean[i][0] != 'Original':
+        mean_diff.append((mean[i][0], abs(float(mean[i][1]) - mean_original)))
+
+for i in range(0, len(corr)):
+    corr_float.append((corr[i][0], float(corr[i][1])))
+
+corr_float.sort(key=lambda tup: tup[1], reverse=True)
+mean_diff.sort(key=lambda tup: tup[1])
[…]

### 2017-10-03 Docs/EADCA-2017/body.tex
updates. tomorrow i'll try IperfFlow and DitgFlow

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:introduction}

There are many works devoted to studying the nature of the Ethernet traffic\cite{selfsimilar-ethernet}. Classic Ethernet models use Poisson related processes. Initially, it makes sense since a Poisson-related process represents the probability of events occur in many independent sources with a known average rate, and independently of the last occurrence \cite{selfsimilar-ethernet} \cite{book-poisson}. However studies made by Leland et al.\cite{selfsimilar-ethernet} showed that the Ethernet traffic has a self-similar and fractal nature. Even if they can represent the randomness of an Ethernet traffic, simple Poisson processes can't express traffic "burstiness" in a long-term time scale, such as traffic "spikes" on long-range ripples. These characteristics are an indication of the fractal and self-similar nature of the traffic that usually we express by distributions with infinite variance, called heavy-tailed. Heavy-tail means its distribution is not exponentially bounded\cite{sourcesonoff-paper}, such as Weibull, Pareto and Cauchy distribution.  Heavy-tailed processes may guarantee self-similarity, but not necessarily will ensure other important features like high correlation between data and same mean packet rate.

Many investigations were made on the literature about the nature of the internet traffic\cite{selfsimilar-ethernet}\cite{analysis-self-similar}\cite{stochartic-selfsimilar}\cite{selfsimilar-highvariability}\cite{multi-player-online-game-self-similarity}, and many others on the modeling of stochastic functions for specific scenarios\cite{estimation-renewal-function-ethernet-traffic}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}\cite{modeling-concurrent-heavy-tailed}\cite{optimal-scheduling-of-heavy-tailed-traffic}\cite{modelling-of-self-similar}. However there are some limitations on this idea of finding a single model. Usually, not the same stochastic distribution will present a proper fitting for all possible kinds of traces\cite{sourcesonoff-paper}. Depending on some variables, such as the capture time, the number of packets or type of traffic, different functions may fit better the available data. On most works the best model representation for an Ethernet traffic is not chosen analytically but based on the researcher own data analyses and purposes\cite{hierarchical-dynamics-interarrival-times}\cite{modeling-concurrent-heavy-tailed}\cite{optimal-scheduling-of-heavy-tailed-traffic}. Also, some methods like linear regression may diverge sometimes. Furthermore, it has already been proven that a single model cannot represent arbitrary traffic traces\cite{sourcesonoff-paper}.

In this work we test the use of information criteria BIC(Bayesian information criterion) and AIC(Akaike information criterion) as tool for choosing the best fitting for inter-packet times of a traffic trace. It is an analytical method which spares and avoid human analyzes, is easy to be implemented by software, and don't relies on simulations and generation of random data. We fit a set of stochastic models through different methods and applying BIC and AIC to choose the best.  On this article, we analyze the results of inter-packet time fitting for one public available trace we call as \textit{skype-pcap}\footnote{It is a lightweight Skype capture, available at \href{https://wiki.wireshark.org/SampleCaptures}{https://wiki.wireshark.org/SampleCaptures}, named \textit{SkypeIRC.cap} }.

First, we explain the mathematical meaning of BIC and AIC and state the methods we are going to use to create a set of candidate models for our dataset. Then we define our cross-validation method based on a cost function $J$, attributing weights from the best to the worst representation for each properties using randomly generated data with our stochastic fittings, we can choose the best possible traffic model among these fittings. Thus we compare the results achieved by AIC/BIC and our cost function. Showing that BIC and AIC are good at guessing the model with smaller $J$ values. Also, we found that for traffic inter-packet times, that the difference between BIC and AIC values is minimal. So choosing one over the other do not seem to be a key question.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{AIC and BIC}\label{sec:aic-bic}

Suppose that we have an statistical model $M$ of some dataset ${\boldsymbol{x} = \{x_1, ..., x_n}\}$, with $n$ independent and identically distributed observations of a random variable $X$. This model can be expressed by a probability density function (PDF) $f(x| \boldsymbol{\theta})$, where $\boldsymbol{\theta}$ is a vector of parameter of the PDF, $\boldsymbol{\theta} \in \mathbb{R}^{k}$ ($k$ is the number of parameters). The  likelihood function  of this model $M$ is given by:
\begin{equation}
L(\boldsymbol{\theta}|\boldsymbol{x} ) =  f(x_1|\boldsymbol{\theta})\cdot...\cdot f(x_n|\boldsymbol{\theta}) = \prod_{i = 1}^{n}f(x_i|\boldsymbol{\theta})
\end{equation}
Now, suppose we are trying to estimate the best statistical model, from a set ${M_1, ..., M_n}$, each one with an estimated vector of parameters  ${\boldsymbol{\hat{\theta_1}}}, ..., {\boldsymbol{\hat{\theta_n}}}$. $AIC$ and $BIC$ are defined by:
\begin{equation}
AIC = 2k - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
\end{equation}
\begin{equation}
BIC = k\ln(n) - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
\end{equation}
In both cases, the preferred model $M_i$, is the one with the smaller value of $AIC_i$ or $BIC_i$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}

We collect inter-packet times from the traffic capture we call \textit{skype-pcap}. Then, we estimate a set of parameters for stochastic processes, using a set of different methodologies, including linear-regression, maximum likelihood, and direct estimation. We are modeling:

\begin{itemize}
 \item Weibull, exponential, Pareto and Cauchy distributions, using linear regression, through the Gradient descendent algorithm. We refer to these exponential and Pareto approximations as Exponential(LR) and Pareto(LR);
    \item Normal and exponential distribution, using direct estimation the mean and the standard deviation of the dataset for the normal, and the mean for the exponential. We refer for to this exponential approximation as Exponential(Me) ;
    \item Pareto distribution, using the maximum likelihood method. We refer to this distribution as Pareto(MLH);
\end{itemize}

\begin{table*}[t]
\centering
\caption{Results of our modeling and simulation methodology for the traffic trace \textit{skype-pcap}. The stochastic processes are ordered form the worst to the best fitting, according to AIC and BIC.}
\label{tab:skype-results}
\begin{tabular}{lcccc}
\hline
Function        & AIC         & BIC        & \multicolumn{2}{c}{Parameters}      \\ \hline
Weibull         & $-2293.8$   & $-2283.8$ & $\alpha:0.522$ & $\beta:0.097$  \\
Exponential(Me) & $-426.13$   & $-421.1$  & \multicolumn{2}{c}{$\lambda:3.319$}  \\
Exponential(LR) & $96.9$   & $101.8$  & \multicolumn{2}{c}{$\lambda:1.505$}         \\
Pareto(MLH)     & $361.9$   & $371.8$  & $\alpha:0.0747$ & $x_m:5e-8$       \\
Normal          & $2423.8$    & $2433.8$   & $\mu:0.301 $   & $\sigma:0.749$ \\
Pareto(LR)      & $6411.0$   & $6421.08$  & $\alpha:0.413$ & $x_m:5e-8$       \\
Cauchy          & $13464.6$    & $13474.5$   & $\gamma:0.000275$ & $x_0:0.219$    \\ \hline
\end{tabular}
\end{table*}

Then, from these parametrized models, we estimate which one best represent our dataset, using AIC  and BIC criteria. These results were obtained using Octave language\footnote{ \href{https://www.gnu.org/software/octave/}{https://www.gnu.org/software/octave/}}, and the scripts are available at \cite{projeto-github} for reproduction purposes. Thus, to see if our criterion of parameter selection can find which is the best model according to traffic modeling standards on realism and benchmarking\cite{validate-trafficgen}, we define a validation methodology. We randomly generated a dataset using our parameterized stochastic processes.  Then we compare it with the original and synthetic sample, trough three different metrics, all with a confidence interval of 95\%:

\begin{itemize}
\item Correlation between the sample data and the estimated model (Pearson's product-moment coefficient);
\item Difference between the original and the synthetic Hurst exponent;
\item Difference between the original and the synthetic mean inter-packet time;
\end{itemize}

The Pearson's product-moment coefficient, or simply correlation coefficient,  is an expression of the linear dependence or association between two datasets. To estimate it, we use the Octave's function \texttt{corr()}. The Hurst exponent is meter self-similarity and indicates the fractal level of the inter-packet times.  To estimate this value we use the function \texttt{hurst()} from Octave, which uses rescaled range method. Finally, the mean is also relevant, since it will meters if the packet rate of the approximation and the original trace are close to each other.

To measure if AIC and BIC are suitable criteria for model selection for inter-packet times, we define a cost function based on the correlation, Hurst exponent and mean. We define $Cr$ as the vector of correlations of the models ordered from the greater to the smaller. Also, let the vectors $Me$ and $Hr$ be the absolute difference (modulus of the difference) between the estimated models and the original datasets of the mean and the Hust exponent respectively. We order both from the smaller to the greatest values. Letting $\phi(V, M)$ be an operator who gives the position of a model $M$ in a vector $V$, we define the cost function $J$ as:
%The Pearson's product-moment coefficient, or simply correlation coefficient,  is an expression of the dependence or association between two datasets. Its value goes from -1 to +1. +1 means a perfect direct linear correlation. -1 indicates perfect inverse linear correlation. 0 means no linear correlation. So, as close the result reach 1, more similar are the inter-packet times to the original values. To estimate it, we use the Octave's function \texttt{corr()}.
%The Hurst exponent is meter self-similarity and indicates the fractal level of the inter-packet times. As close the result is from the original, more similar is the fractal level of the estimated samples from the original. To estimate this value we use the function \texttt{hurst()} from Octave, which uses rescaled range method. Finally, the mean is also relevant, since it will meters if the packet per second rate of the trace and its approximation model are close related. 
%To quantitatively check   if AIC and BIC are good criteria for model selection for inter-packet times, we define a cost function based on the correlation, Hurst exponent and mean. We defined a cost function $J$, based on the randomly generated data values with our estimated stochastic process. Being $Cr$ the vector of correlations ordered from the greater to the smaller. Let $Me$ and $Hr$ defined by the absolute difference between mean and hurt exponent of the estimated values and the original dataset. Both are ordered from the smaller to the greatest values. Letting $\phi(V, M)$ be an operator who gives the position of a model $M$ in a vector $V$, we define the cost function $J$ as:
\begin{equation}
J(M) = \phi(Cr, M) + \phi(Me, M) + \phi(Hr, M)
\end{equation}
The smaller is the cost $J$, the best is the model. Then we compare the results achieved by AIC and BIC, and $J$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\begin{figure}[t]
{\centering
\includegraphics[width=\columnwidth]{figures/Weibull}
\caption{Cumulative distribution function(CDF) for Weibull fitting and empirical data for inter-packet times of \textit{skype-pcap}}
\label{fig:skype-weibull}\par}
\end{figure}
\begin{figure}[b]
{\centering
\includegraphics[width=\columnwidth]{figures/costFunction2}
\caption{Cost function $J$ of each stochastic process for \textit{skype-pcap}.}
\label{fig:cost-function}\par}
\end{figure}
In table~\ref{tab:skype-results} we summarize our estimations for AIC, BIC, and the stochastic process estimated parameters. Then we organize the values in crescent order of quality, according to the selection criteria (the smaller, the better). In figure ~\ref{fig:skype-weibull} we present the best fitting chosen both by BIC and AIC criteria. It is on log-scale, which provides a better visualization for small time values. Visually we can see that linear regression with Weibull distribution was able to provide a good approximation for this dataset.

The difference between BIC and AIC values in all simulations are much smaller than the difference between the distributions. This result indicates that for inter-packet times, using AIC or BIC to pick a model, do not influence the results significantly. According to BIC and AIC previsions, Weibull and Exponential (Me and LR) are the best options, and the cost functions gave exact this same order~\ref{fig:cost-function}. In fact, Weibull pointed as the best stochastic function by BIC and AIC, has half of the penalty imposed by the cost function $J$. The following models however are not in the same order since some results are flipped. But still, no opposite correspondence can be found. No result found by AIC and BIC were far from the one pointed by $J$.

%\begin{figure}[h]
%{\centering
%\includegraphics[width=\columnwidth]{figures/Correlation}
%\caption{Comparison between correlation of the used set of fittings, with a confidence of 95\%}
%\label{fig:skype-correlation}\par}
%\end{figure}

%\begin{figure}[t]
%{\centering
%\includegraphics[width=\columnwidth]{figures/HurstExponent}
%\caption{Comparison between the Hurst exponent of our approximated processes and the original data  with a confidence of 95\%}
%\label{fig:skype-hurst}\par}
%\end{figure}

%\begin{figure}[t]
%{\centering
%\includegraphics[width=\columnwidth]{figures/Mean}
%\caption{cap}
%\label{fig:skype-mean}\par}
%\end{figure}

%The difference between BIC and AIC values in all simulations are very small. Much smaller then the difference of these values between the distributions. This is an indication that for inter packet times, using AIC or BIC to pick a model, will not influence significantly the results.

%According to BIC and AIC previsions, Weibull and Pareto(MLH and LR) are the best options. This was expected, since both are heavy-tailed functions. But Cauchy on most of the tests, even being a heavy-tailed distribution, seems to do no present a good fitting. This is effect of the fast divergence of tangent function, when we linearize our data.

%From the figures ~\ref{fig:skype-correlation} and ~\ref{fig:fig:skype-hurst} we see that in therms of Correlation and Self-similarity it picket clearly the most related model: Weibull. Also in therms of mean packet rate it is still a good choice (along with Exponential(Me), Pareto(LR) and Cauchy). The third and the fourth choices (Pareto(LR)) and Exponential(Me) also are good options in most of these metrics. But, Pareto(MLH) is presented as the second best choice, and it had poor results in comparison to the others, especially on mean and correlation. This is the only model presented as good

%All these results are abstracted by the cost function $J$. As we can see, on all pcaps, the best function selected by BIC and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.

%Another important observation is the fact that exponential function was able to provide the best fitting for the \textit{wan-pcap}. The reasons for this behavior are both result of a much intense traffic with no long-range gaps, and the precision of the measurement.

\section{Conclusion}

In this work, we analyze how BIC and AIC perform being used as analytical selection criteria form stochastic models for Ethernet inter-packet times. Using a cross-validation methodology based on the generation of random data using these models, and pointing a cost function. We saw that both AIC or BIC and the cost function were able to pick the first models in the same order. Therefore, analytically with BIC and AIC, we were able to achieve the same results as pointed by our simulations. Even if AIC and BIC mathematical definitions are unaware of the specific requirements of Ethernet traffic modeling, such as same fractal-level and close packet per second rate, they still can point the best choices according to these constraints.

In this work, we analyze just inter-packet times of a single trace. However at \cite{projeto-github} we perform the same methodology on different types of traffic captures, finding similar results. Therefore, we can conclude that BIC and AIC are healthy alternatives for model selection of Ethernet inter-packet times models and we can safely use them. Finally, we must point some advantages of BIC and AIC instead of simulations. Since it is an analytical model, no generation of random data is necessary,  being computationally cheaper and easy to code. Also, since we do not use a single stochastic function and parameterization strategy, it is resilient to the fact that some methods like linear-regression over Weibull may diverge sometimes. If it happens, BIC or AIC will discard this guesses, and choose another oneautomatically.

Last but not least, to the best of our knowledge, this is the most comprehensive investigation of the actual quality of BIC and AIC as model selection criteria of for inter-packet times.
%Also, except by the Pareto function modeled using the Maximum likelihood method, have comparative results between the simulations and the AIC/BIC goes. The best fittings according to the AIC/BIC usually returned very accurate models, with a small error between the mean and fractal level, and correlation close to one. The models selected as the worsts usually returned poor results.

%Also, it is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurate fitting, what justify the application of the criteria in all new experiments. For example, Weibull usually performs pretty well, but in some cases, perform poorly, and in others may even diverge.

%We do not rely on only one type of parameterization. This turns our methodology more robust, since a linear regression may diverge. But always there will be a peaceable model, since our estimations for Normal, Exponential (Me) and Pareto (MLH) cannot. Models which the linear regression diverges, will have very high and positive BIC/AIC estimations, and will not stand as primary options.

### 2017-10-03 SIMITAR/apps/dummy-flow/src/dummy-flow.cpp

@@ -25,9 +25,14 @@ void cli_error_messege(std::string arg, std::string arg_name,
  */
 bool cli_check_val(std::string val, std::vector<std::string> expectedVals);
 
+/**
+ * Erros list:
+ *  #-1: invalid mode (client/server)
+ *  #-2: exception parsing commandline
+ */
 int main(int argc, char** argv)
 {
-	PLOG_INIT(debug);
+	PLOG_INIT(verbose);
 	try
 	{
 		///
@@ -45,16 +50,20 @@ int main(int argc, char** argv)
 
 		// comamnd line parsing
 		TCLAP::CmdLine cmd(progDescription, ' ', version);
-		TCLAP::ValueArg<std::string> mode_arg("m", "mode", "Operation mode, as a client or a server",
-				true, "", "string");
-		TCLAP::ValueArg<std::string> in_arg("x", "xml", "xml", true, "Compact Trace Descriptor XML. They are salved at data/xml/ directory.",
+		TCLAP::ValueArg<std::string> mode_arg("m", "mode",
+				"Operation mode, as a client or a server", true, "", "string");
+		TCLAP::ValueArg<std::string> in_arg("x", "xml", "xml", true,
+				"Compact Trace Descriptor XML. They are salved at data/xml/ directory.",
 				"string");
-		TCLAP::ValueArg<std::string> dst_list_arg("d", "dst-list-ip", "Text file in CSV format containing a list of desired destinations of IP and MAC adresses, used as servers, in the client mode. These destinations are addressed to the flows in a ring-oriented way.",
+		TCLAP::ValueArg<std::string> dst_list_arg("d", "dst-list-ip",
+				"Text file in CSV format containing a list of desired destinations of IP and MAC adresses, used as servers, in the client mode. These destinations are addressed to the flows in a ring-oriented way.",
 				false, "", "string");
-		TCLAP::ValueArg<std::string> dst_server_arg("p", "dst-ip", "Instead of a textfile, defines a single server destination IP address in the command line.", false,
-				"", "string");
-		TCLAP::ValueArg<std::string> eth_arg("e", "ether", "Ethernet interface to send the traffic, as provided by the command `ifconfig`.", false, "",
-				"string");
+		TCLAP::ValueArg<std::string> dst_server_arg("p", "dst-ip",
[…]

### 2017-10-03 SIMITAR/apps/iperf-flow/test1-client.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+./iperf-flow -x ../../data/xml/skype.sec.xml -m client -p "10.0.0.2"
+

### 2017-10-03 SIMITAR/libsimitar/DitgFlow.cpp

@@ -57,32 +57,31 @@ void DitgFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
 			ditg_command(onTime, npackets, nbytes, netInterface).c_str());
 	simitar_iostream_mutex.unlock();
 
-	/*
-	 // popen args
-	 FILE *in;
-	 char buff[512];
-	 //iperf args
+	// popen args
+	FILE *in;
+	char buff[512];
+	//iperf args
 
-	 char command[2048];
-	 strcpy(command,
-	 ditg_command(onTime, npackets, nbytes, netInterface).c_str());
+	char command[2048];
+	strcpy(command,
+			ditg_command(onTime, npackets, nbytes, netInterface).c_str());
 
-	 if (!(in = popen(command, "r")))
-	 {
-	 std::cerr << "IperfFlow error: cannot execute command `" << command
-	 << "`" << std::endl;
-	 return;
-	 }
+	if (!(in = popen(command, "r")))
+	{
+		std::cerr << "IperfFlow error: cannot execute command `" << command
+				<< "`" << std::endl;
+		return;
+	}
 
-	 while (fgets(buff, sizeof(buff), in) != NULL)
-	 {
-	 simitar_iostream_mutex.lock();
-	 std::cout << buff;
-	 simitar_iostream_mutex.unlock();
-	 }
+	while (fgets(buff, sizeof(buff), in) != NULL)
+	{
+		simitar_iostream_mutex.lock();
+		std::cout << buff;
+		simitar_iostream_mutex.unlock();
+	}
 
-	 pclose(in);
-	 */
+	pclose(in);
+
 }
 
 std::string DitgFlow::ditg_command(const time_sec& onTime, const uint& npackets,

### 2017-10-03 SIMITAR/libsimitar/DummyFlow.cpp

@@ -17,9 +17,6 @@ DummyFlow::~DummyFlow()
 {
 }
 
-void DummyFlow::print()
-{
-}
 
 int DummyFlow::server()
 {
@@ -32,25 +29,12 @@ void DummyFlow::flowStart()
 	/// flow-related vars
 	std::string netInterface = "";
 	time_sec sec_startDelay = getFlowStartDelay(); // times in seconds
-	//time_t usec_startDelay = time_t(sec_startDelay * 1.0e6); // time in useconds
 	uint fid = int(getFlowId());
 	/// loop vars
-	time_t usec_offTime = 0; // time in useconds
 	time_sec sec_onTime = 0;
 	time_sec sec_offTime = 0;
 	uint nbytes = 0;
 	uint npackets = 0;
-
-
-	PLOG_DEBUG << "getFlowStartDelay:" << this->getFlowStartDelay();
-	PLOG_DEBUG << "getTransportProtocol:" << this->getTransportProtocol();
-	PLOG_DEBUG << "getTransportDstPort:" << this->getTransportDstPort();
-	PLOG_DEBUG << "getNetworkDstAddr:" << this->getNetworkDstAddr();
-	PLOG_DEBUG << "getNetworkTtl:" << this->getNetworkTtl();
-	PLOG_INFO << "Time scale factor is " << timeScaleFactor();
-	PLOG_DEBUG << "flowID:" << this->getFlowId();
-
-
 
 	fsleep(sec_startDelay/timeScaleFactor());
 	//usleep(usec_startDelay);
@@ -67,24 +51,14 @@ void DummyFlow::flowStart()
 		{
 			break;
 		}
-		//usec_offTime = time_t(sec_offTime * 1.0e6);
-		//usleep(usec_offTime);
 		fsleep(sec_offTime/timeScaleFactor());
-
 	}
-
 }
 
 void DummyFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
 		const uint& npackets, const uint& nbytes, const string& netInterface)
 {
-	int rc = 0;
-
-	std::cout << "flowGenerate()\n";
-
-	//unsigned int usecs = (unsigned int) (this->getFlowStartDelay() * MEGA_POWER);
 	string flow_str_print = "";
-	protocol prt;
 	StochasticModelFit themodel;
 
 	/***************************************************************************

### 2017-10-03 SIMITAR/libsimitar/DummyFlow.h

@@ -25,10 +25,7 @@
  } l2_addr;
  */
 
-//typedef enum
-//{
-//	method_usleep, method_pooling, method_select
-//} sleep_method;
+
 
 class DummyFlow: public NetworkFlow
 {
@@ -42,11 +39,6 @@ public:
 	 *
 	 */
 	virtual ~DummyFlow();
-
-	/**
-	 *
-	 */
-	void print();
 
 	/**
 	 *

### 2017-10-03 SIMITAR/libsimitar/IperfFlow.cpp

@@ -29,8 +29,8 @@ int IperfFlow::server()
 			"NOTE: Use Compact Trace Descriptors parameterized in seconds (sufix .sec) in the client side.\n");
 	if (!(in = popen(command, "r")))
 	{
-		std::cerr << "IperfFlow error: cannot execute command `" << command
-				<< "`" << std::endl;
+		PLOG_ERROR << "IperfFlow error: cannot execute command `" << command
+				<< "`";
 		return -1;
 	}
 
@@ -52,14 +52,16 @@ void IperfFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
 	FILE *in;
 	char buff[512];
 	//iperf args
-
 	char command[2048];
 	strcpy(command,
 			iperf_command(onTime, npackets, nbytes, netInterface).c_str());
 
+	PLOG_DEBUG << "iperf command: " << command;
+
+
 	if (!(in = popen(command, "r")))
 	{
-		std::cerr << "IperfFlow error: cannot execute command `" << command
+		PLOG_ERROR << "IperfFlow error: cannot execute command `" << command
 				<< "`" << std::endl;
 		return;
 	}
@@ -72,6 +74,7 @@ void IperfFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
 	}
 
 	pclose(in);
+
 }
 
 /**

### 2017-10-03 SIMITAR/libsimitar/NetworkFlow.cpp

@@ -30,7 +30,6 @@ NetworkFlow::NetworkFlow()
 	number_of_packets = 0;
 
 	///protocols parameters  initialization
-
 	link_protocol = PROTOCOL__ETHERNET; //default
 	mac_src = "";
 	mac_dst = "";
@@ -64,8 +63,6 @@ NetworkFlow::NetworkFlow()
 	nkbytes_mode2 = 0;
 	npacket_mode1 = 0;
 	npackets_mode2 = 0;
-	//packetSizeModel1_counter = 0;
-	//packetSizeModel2_counter = 0;
 
 }
 
@@ -120,10 +117,63 @@ NetworkFlow::~NetworkFlow()
 	delete ptr_psMode2;
 }
 
-void NetworkFlow::print()
+std::string NetworkFlow::print()
 {
-	//TODO
-	std::cout << "flow created" << endl;
+	string flow_str_print = "";
+	StochasticModelFit themodel;
+
+	/***************************************************************************
+	 * Dummy-parser
+	 **************************************************************************/
+
+	/**
+	 * Flow-level
+	 */
+	flow_str_print += "Flow" + std::to_string(flowId) + "> Duration:"
+			+ std::to_string(getFlowDuration()) + ", Start-delay:"
+			+ std::to_string(getFlowStartDelay()) + "s" + ", N.packets: "
+			+ std::to_string(getNumberOfPackets());
+
+	////////////////////////////////////////////////////////////////////////////
+	/// Link-layer protocol
+	////////////////////////////////////////////////////////////////////////////
+	flow_str_print += " Link[" + Protocol(this->getLinkProtocol()).str() + "]";
+
+	////////////////////////////////////////////////////////////////////////////
+	/// Network-layer protocol
+	////////////////////////////////////////////////////////////////////////////
+	flow_str_print += " Network[" + Protocol(this->getNetworkProtocol()).str()
+			+ "]";
+
+	////////////////////////////////////////////////////////////////////////////
+	/// Transport-layer protocol
+	////////////////////////////////////////////////////////////////////////////
+	flow_str_print += " Transport["
+			+ Protocol(this->getTransportProtocol()).str() + "]";
+
+	// Application protocol
+	flow_str_print += " Application["
[…]

### 2017-10-03 SIMITAR/libsimitar/NetworkTrace.cpp

@@ -15,7 +15,7 @@ NetworkTrace::NetworkTrace()
 NetworkTrace::NetworkTrace(const string& fileName,
 		const string& trafficGenEngine)
 {
-	PLOG_DEBUG << "NetworkTrace() constructor => args fileName:" << fileName
+	PLOG_DEBUG << "NetworkTrace() file constructor;  args fileName:" << fileName
 						<< ", trafficGenEngine:" << trafficGenEngine;
 
 	long int nflows = 0;
@@ -59,7 +59,7 @@ NetworkTrace::NetworkTrace(const string& fileName,
 
 	charvet2type(root_node->first_attribute("n_flows")->value(), nflows);
 
-	int fcounter = 0;
+	uint fcounter = 0;
 	for (xml_node<> * flow_node = root_node->first_node("flow"); flow_node;
 			flow_node = flow_node->next_sibling())
 	{
@@ -68,9 +68,10 @@ NetworkTrace::NetworkTrace(const string& fileName,
 		NetworkFlow* netFlow = NetworkFlowFactory::make_flow(trafficGenEngine);
 
 		// PLOG debug
-		PLOG_DEBUG << "Factoring flow[" << fcounter
+		PLOG_VERBOSE << "Factoring flow[" << fcounter
 							<< "]: NetworkFlowFactory::make_flow("
 							<< trafficGenEngine << ")";
+		netFlow->setFlowId(fcounter);
 		fcounter++;
 
 		/// Flow Settings
@@ -281,7 +282,7 @@ NetworkTrace::~NetworkTrace()
 
 	for (unsigned int i = 0; i < networkFlow.size(); i++)
 	{
-		//MESSER_DEBUG("delete networkFlow[%d] @ <%s, %s>", i);
+		PLOG_VERBOSE << "delete networkFlow[" << i << "]";
 		delete networkFlow[i];
 	}
 	networkFlow.clear();
@@ -774,7 +775,7 @@ int NetworkTrace::writeToFile(const string& fileName) const
 	file_stored.close();
 	doc.clear();
 
-	//MESSER_DEBUG("Free memory @<%s, %s>");
+	PLOG_DEBUG << "Free memory";
 
 	//Free memory allocated
 	for (i = 0; i < nFlows; i++)
@@ -824,20 +825,19 @@ int NetworkTrace::exec()
 
 	PLOG_DEBUG << "NetworkTrace::exec() >> this->getNumberOfFlows():"
 						<< this->getNumberOfFlows();
[…]

### 2017-10-03 SIMITAR/libsimitar/PlogMacros.h

@@ -17,7 +17,7 @@
 #include <plog/Appenders/ColorConsoleAppender.h>
 #include <plog/Appenders/RollingFileAppender.h>
 
-#define PLOG_INIT(logLevel)\
+//#define PLOG_INIT(logLevel)\
 		char* _plog_logfile_env = std::getenv("SIMITAR_LOGFILE");\
 		char _fileName[500];\
 		if(_plog_logfile_env)\
@@ -32,6 +32,38 @@
 		{\
 			static plog::ColorConsoleAppender<plog::TxtFormatter> consoleAppender;\
 			plog::init(plog::debug, &consoleAppender);\
+			LOG_ERROR  << "[" << __FILE__ << "] " << "Can't find env variable SIMITAR_LOGFILE";\
+		}
+
+
+/**
+ *  Loglevel list for PLOG_INIT
+enum Severity
+{
+    none = 0,   //!< none
+    fatal = 1,  //!< fatal
+    error = 2,  //!< error
+    warning = 3,//!< warning
+    info = 4,   //!< info
+    debug = 5,  //!< debug
+    verbose = 6 //!< verbose
+};
+ */
+#define PLOG_INIT(logLevel)\
+		char* _plog_logfile_env = std::getenv("SIMITAR_LOGFILE");\
+		char _fileName[500];\
+		if(_plog_logfile_env)\
+		{ \
+			strcpy(_fileName, _plog_logfile_env);\
+			static plog::RollingFileAppender<plog::CsvFormatter> fileAppender(_fileName,\
+					800000, 2);\
+			static plog::ColorConsoleAppender<plog::TxtFormatter> consoleAppender;\
+			plog::init(plog::logLevel, &fileAppender).addAppender(&consoleAppender); \
+		}\
+		else\
+		{\
+			static plog::ColorConsoleAppender<plog::TxtFormatter> consoleAppender;\
+			plog::init(plog::logLevel, &consoleAppender);\
 			LOG_ERROR  << "[" << __FILE__ << "] " << "Can't find env variable SIMITAR_LOGFILE";\
 		}
 

### 2017-10-03 SIMITAR/libsimitar/TinsFlow.cpp

@@ -1,0 +1,20 @@
+/*
+ * TinsFlow.cpp
+ *
+ *  Created on: 3 de out de 2017
+ *      Author: anderson
+ */
+
+#include "TinsFlow.h"
+
+TinsFlow::TinsFlow()
+{
+	// TODO Auto-generated constructor stub
+
+}
+
+TinsFlow::~TinsFlow()
+{
+	// TODO Auto-generated destructor stub
+}
+

### 2017-10-17 Docs/EADCA-2017/body.tex
a xls file that plots bic and aic comparision

@@
 There are many works devoted to studying the nature of the Ethernet traffic\cite{selfsimilar-ethernet}.
-Classic Ethernet models use Poisson related processes.
+Classic Ethernet models used Poisson related processes.
 Initially, it makes sense since a Poisson-related process represents the probability of events occur in many independent sources with a known average rate, and independently of the last occurrence \cite{selfsimilar-ethernet} \cite{book-poisson}.
-However studies made by Leland et al.\cite{selfsimilar-ethernet} showed that the Ethernet traffic has a self-similar and fractal nature.
+But studies made by Leland et al.\cite{selfsimilar-ethernet} showed that the Ethernet traffic has a self-similar and fractal nature.
 Even if they can represent the randomness of an Ethernet traffic, simple Poisson processes can't express traffic "burstiness" in a long-term time scale, such as traffic "spikes" on long-range ripples.
-These characteristics are an indication of the fractal and self-similar nature of the traffic that usually we express by distributions with infinite variance, called heavy-tailed.
-Heavy-tail means its distribution is not exponentially bounded\cite{sourcesonoff-paper}, such as Weibull, Pareto and Cauchy distribution.
-Heavy-tailed processes may guarantee self-similarity, but not necessarily will ensure other important features like high correlation between data and same mean packet rate.
+These characteristics are an indication of the fractal and self-similar nature of the traffic, that usually we express by distributions with infinite variance, called heavy-tailed.
+Heavy-tail means its distribution is not exponentially bounded\cite{sourcesonoff-paper}.
+Examples of heavy-tailed functions are Weibull, Pareto, Cauchy.
+But heavy-tailed processes may guarantee self-similarity, but not necessarily they will ensure other important features like a high correlation between data and same mean packet rate.
 
 Many investigations were made on the literature about the nature of the internet traffic\cite{selfsimilar-ethernet}\cite{analysis-self-similar}\cite{stochartic-selfsimilar}\cite{selfsimilar-highvariability}\cite{multi-player-online-game-self-similarity}, and many others on the modeling of stochastic functions for specific scenarios\cite{estimation-renewal-function-ethernet-traffic}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}\cite{modeling-concurrent-heavy-tailed}\cite{optimal-scheduling-of-heavy-tailed-traffic}\cite{modelling-of-self-similar}.
-However there are some limitations on this idea of finding a single model.
+But there are some limitations on this idea of finding a single model.
 Usually, not the same stochastic distribution will present a proper fitting for all possible kinds of traces\cite{sourcesonoff-paper}.
 Depending on some variables, such as the capture time, the number of packets or type of traffic, different functions may fit better the available data.
-On most works the best model representation for an Ethernet traffic is not chosen analytically but based on the researcher own data analyses and purposes\cite{hierarchical-dynamics-interarrival-times}\cite{modeling-concurrent-heavy-tailed}\cite{optimal-scheduling-of-heavy-tailed-traffic}.
+On most of the works the best model representation for an Ethernet traffic is not chosen analytically but based on the researcher own data analyses and specific purposes\cite{hierarchical-dynamics-interarrival-times}\cite{modeling-concurrent-heavy-tailed}\cite{optimal-scheduling-of-heavy-tailed-traffic}.
 Also, some methods like linear regression may diverge sometimes.
-Furthermore, it has already been proven that a single model cannot represent arbitrary traffic traces\cite{sourcesonoff-paper}.
+And it has already been demonstrated that a single model cannot represent arbitrary traffic traces\cite{sourcesonoff-paper}.
 
-In this work we test the use of information criteria BIC(Bayesian information criterion) and AIC(Akaike information criterion) as tool for choosing the best fitting for inter-packet times of a traffic trace.
+In this work test the use of information criteria BIC(Bayesian information criterion) and AIC(Akaike information criterion) as tool for choosing the best fitting for inter-packet times of a traffic trace.
 It is an analytical method which spares and avoid human analyzes, is easy to be implemented by software, and don't relies on simulations and generation of random data.
@@
 First, we explain the mathematical meaning of BIC and AIC and state the methods we are going to use to create a set of candidate models for our dataset.
-Then we define our cross-validation method based on a cost function $J$, attributing weights from the best to the worst representation for each properties using randomly generated data with our stochastic fittings, we can choose the best possible traffic model among these fittings.
-Thus we compare the results achieved by AIC/BIC and our cost function.
-Showing that BIC and AIC are good at guessing the model with smaller $J$ values.
+Then we define our cross-validation method based on a cost function $J$.
+Attributing weights from the best to the worst representation for each properties using randomly generated data with our stochastic fittings, we can choose the best possible traffic model among these fittings.
+We compare the results achieved by AIC/BIC and our cost function.
+We show that BIC and AIC are good at guessing the model with the lesser $J$ values.
 Also, we found that for traffic inter-packet times, that the difference between BIC and AIC values is minimal.
@@
 Suppose that we have an statistical model $M$ of some dataset ${\boldsymbol{x} = \{x_1, ..., x_n}\}$, with $n$ independent and identically distributed observations of a random variable $X$.
-This model can be expressed by a probability density function (PDF) $f(x| \boldsymbol{\theta})$, where $\boldsymbol{\theta}$ is a vector of parameter of the PDF, $\boldsymbol{\theta} \in \mathbb{R}^{k}$ ($k$ is the number of parameters).
+This model can be expressed by a probability density function (PDF) $f(x| \boldsymbol{\theta})$, where $\boldsymbol{\theta}$ a vector of parameter of the PDF, $\boldsymbol{\theta} \in \mathbb{R}^{k}$ ($k$ is the number of parameters).
 The  likelihood function  of this model $M$ is given by:
@@
 \end{equation}
-Now, suppose we are trying to estimate the best statistical model, from a set ${M_1, ..., M_n}$, each one with an estimated vector of parameters  ${\boldsymbol{\hat{\theta_1}}}, ..., {\boldsymbol{\hat{\theta_n}}}$.
+Now, suppose we are trying to estimate the best statistical model, from a set ${M_1, ..., M_n}$, each one whit an estimated vector of parameters  ${\boldsymbol{\hat{\theta_1}}}, ..., {\boldsymbol{\hat{\theta_n}}}$.
 $AIC$ and $BIC$ are defined by:
@@
 
-Then, from these parametrized models, we estimate which one best represent our dataset, using AIC  and BIC criteria.
+Then, from these parametrized models, we estimate which best represent our dataset, using AIC  and BIC criterion.
 These results were obtained using Octave language\footnote{ \href{https://www.gnu.org/software/octave/}{https://www.gnu.org/software/octave/}}, and the scripts are available at \cite{projeto-github} for reproduction purposes.
-Thus, to see if our criterion of parameter selection can find which is the best model according to traffic modeling standards on realism and benchmarking\cite{validate-trafficgen}, we define a validation methodology.
-We randomly generated a dataset using our parameterized stochastic processes.
+To see if our criterion of parameter selection can find which is the best model according to traffic modeling standards on realism and benchmarking\cite{validate-trafficgen}, we define a validation methodology.
+We generate randomly generated a same sized dataset compared to the original, using our stochastic processes fittings.
 Then we compare it with the original and synthetic sample, trough three different metrics, all with a confidence interval of 95\%:
@@
 
-To measure if AIC and BIC are suitable criteria for model selection for inter-packet times, we define a cost function based on the correlation, Hurst exponent and mean.
-We define $Cr$ as the vector of correlations of the models ordered from the greater to the smaller.
-Also, let the vectors $Me$ and $Hr$ be the absolute difference (modulus of the difference) between the estimated models and the original datasets of the mean and the Hust exponent respectively.
+To quantitatively check if AIC and BIC are suitable criteria for model selection for inter-packet times, we define a cost function based on the correlation, Hurst exponent and mean.
+Being $Cr$ the vector of correlations of the models ordered from the greater to the smaller.
+Let's define the vectors $Me$ and $Hr$ as the absolute difference (modulus of the difference) between mean and hurt exponent of the estimated models and the original dataset.
 We order both from the smaller to the greatest values.
@@
 \end{figure}
-In table~\ref{tab:skype-results} we summarize our estimations for AIC, BIC, and the stochastic process estimated parameters.
-Then we organize the values in crescent order of quality, according to the selection criteria (the smaller, the better).
-In figure ~\ref{fig:skype-weibull} we present the best fitting chosen both by BIC and AIC criteria.
+In the table~\ref{tab:skype-results} we summarize our estimations for AIC, BIC, and the stochastic process estimated parameters.
+We organize the values in crescent order of quality, according to the selection criteria (the smaller, the better).
+In the figure ~\ref{fig:skype-weibull} we present the best fitting chosen both by BIC and AIC criteria.
 It is on log-scale, which provides a better visualization for small time values.
@@
 This result indicates that for inter-packet times, using AIC or BIC to pick a model, do not influence the results significantly.
-According to BIC and AIC previsions, Weibull and Exponential (Me and LR) are the best options, and the cost functions gave exact this same order~\ref{fig:cost-function}.
+According to BIC and AIC previsions, Weibull and Exponential (Me and LR) are the best options.
+Our cost functions points exact this order~\ref{fig:cost-function}.
 In fact, Weibull pointed as the best stochastic function by BIC and AIC, has half of the penalty imposed by the cost function $J$.
-The following models however are not in the same order since some results are flipped.
-But still, no opposite correspondence can be found.
+The following model is not in the same order since some results are flipped.
+But still, no opposite correspondence is found.
 No result found by AIC and BIC were far from the one pointed by $J$.
@@
 In this work, we analyze how BIC and AIC perform being used as analytical selection criteria form stochastic models for Ethernet inter-packet times.
-Using a cross-validation methodology based on the generation of random data using these models, and pointing a cost function.
+Using a cross-validation methodology based on the generation of random data with these models, and pointing a cost function.
 We saw that both AIC or BIC and the cost function were able to pick the first models in the same order.
@@
 
-In this work, we analyze just inter-packet times of a single trace.
-However at \cite{projeto-github} we perform the same methodology on different types of traffic captures, finding similar results.
-Therefore, we can conclude that BIC and AIC are healthy alternatives for model selection of Ethernet inter-packet times models and we can safely use them.
+Here in this work, we analyze just inter-packet times of a single trace.
+But at \cite{projeto-github} we perform the same methodology on different types of traffic captures, finding similar results.
+Therefore we can conclude that BIC and AIC are healthy alternatives for model selection of Ethernet inter-packet times models, and we can be safely them.
 Finally, we must point some advantages of BIC and AIC instead of simulations.
 Since it is an analytical model, no generation of random data is necessary,  being computationally cheaper and easy to code.
-Also, since we do not use a single stochastic function and parameterization strategy, it is resilient to the fact that some methods like linear-regression over Weibull may diverge sometimes.
-If it happens, BIC or AIC will discard this guesses, and choose another oneautomatically.
+Also, since we do not use a single stochastic function and parameterization strategy, it is resilient to the fact that some methods like liner-regression over Weibull may diverge sometimes.
+If it happens, BIC or AIC will discard this guesses, and choose another automatically.
 

### 2017-10-17 Docs/EADCA-2017/body2.tex
a xls file that plots bic and aic comparision

--- 2017-10-17 Docs/EADCA-2017/body.tex
@@
 \begin{itemize}
- \item Weibull, exponential, Pareto and Cauchy distributions, using linear regression, through the Gradient descendent algorithm.
-We refer to these exponential and Pareto approximations as Exponential(LR) and Pareto(LR);
-    \item Normal and exponential distribution, using direct estimation the mean and the standard deviation of the dataset for the normal, and the mean for the exponential.
-We refer for to this exponential approximation as Exponential(Me) ;
+    \item Weibull distribution, using linear regression, through the Gradient descendent algorithm;
+    \item Normal distribution, using direct estimation the mean and the standard deviation of the dataset;
+    \item Exponential distribution, using linear regression, through the Gradient descendent algorithm. We refer to this distribution as Exponential(LR);
+    \item Exponential distribution, using a direct estimation of the dataset mean. We refer to this distribution as Exponential(Me);
+    \item Pareto distribution, using linear regression, through the Gradient descendent algorithm. We refer to this distribution as Pareto(LR);
     \item Pareto distribution, using the maximum likelihood method. We refer to this distribution as Pareto(MLH);
+    \item Cauchy distribution, using linear regression, through the Gradient descendent algorithm;
 \end{itemize}
@@
 
-Last but not least, to the best of our knowledge, this is the most comprehensive investigation of the actual quality of BIC and AIC as model selection criteria of for inter-packet times.
 %Also, except by the Pareto function modeled using the Maximum likelihood method, have comparative results between the simulations and the AIC/BIC goes.

### 2017-10-19 SIMITAR/apps/simitar/src/simitar-app.cpp
IMPORTANT: vou fazer algumas alterações, e tudo pode parar de funfar kkk -> preciso passar a interface ethernet como argumento para cada thread

@@ -127,12 +127,12 @@ int main(int argc, char** argv)
 		if (mode == "server")
 		{
 			PLOG_VERBOSE << " execution of traceCdt.server()";
-			traceCdt.server();
+			traceCdt.server(eth_interface);
 		}
 		else
 		{
 			PLOG_VERBOSE << " execution of traceCdt.exec()";
-			traceCdt.exec();
+			traceCdt.exec(eth_interface);
 		}
 
 	} catch (TCLAP::ArgException &e)  // catch any exceptions

### 2017-10-19 SIMITAR/libsimitar/DitgFlow.h

@@ -16,14 +16,17 @@
 class DitgFlow: public DummyFlow
 {
 public:
+
 	/**
 	 *
 	 */
 	DitgFlow();
+
 	/**
 	 *
 	 */
 	virtual ~DitgFlow();
+
 	/**
 	 *
 	 * @return

### 2017-10-19 SIMITAR/libsimitar/NetworkFlow.cpp

@@ -7,17 +7,10 @@
 
 #include "NetworkFlow.h"
 #include "DummyFlow.h"
-//#include "DitgFlow.h"
-//#include "PrintCharFlow.h"
-//#include "IperfFlow.h"
-//#include "OstinatoFlow.h"
-//#include "NemesisFlow.h"
-//#include "LibtinsFlow.h"
 
 NetworkFlow::NetworkFlow()
 {
 	/// flow settings
-	ether_interface = "lo";
 	flow_time_scale = seconds;
 	flow_sleep_method = method_usleep;
 
@@ -173,7 +166,7 @@ std::string NetworkFlow::print()
 	printf("%s\n", flow_str_print.c_str());
 	simitar_iostream_mutex.unlock();
 
-	return(flow_str_print);
+	return (flow_str_print);
 }
 
 int NetworkFlow::randTranportPort()
@@ -181,32 +174,6 @@ int NetworkFlow::randTranportPort()
 	return (rand() % (MAX_TRANSPORT_PORT_NUMBER + 1));
 }
 
-//TODO implementar a lista de hosts -> catch these values from a list
-// useless
-/*
-string NetworkFlow::getHostIP()
-{
-	string dstIP;
-	pthread_mutex_t lock;
-
-	pthread_mutex_init(&lock, NULL);
-	pthread_mutex_lock(&lock);
-	if (network_hostList_conter == 0)
-	{
-		dstIP = "172.16.0.1";
-		network_hostList_conter++;
-	}
-	else
-	{
-		dstIP = "172.16.0.2";
-		network_hostList_conter = 0;
-	}
-	pthread_mutex_unlock(&lock);
-	pthread_mutex_destroy(&lock);
-
-	return (dstIP);
-}
-*/
 unsigned int NetworkFlow::getFlowDsByte() const
 {
 	return flow_ds_byte;
@@ -395,7 +362,6 @@ void NetworkFlow::setTransportProtocol(protocol transportProtocol)
 	transport_protocol = transportProtocol;
 }
 
-
 StochasticModelFit NetworkFlow::getInterDepertureTimeModel(
 		unsigned int position)
 {
@@ -408,9 +374,9 @@ StochasticModelFit NetworkFlow::getInterDepertureTimeModel(
 		themodel.set(NO_MODEL, 0, 0, datum::inf, datum::inf);
 		//ptr_interArrivalModelList->push_back(themodel);
 
[…]

### 2017-10-19 SIMITAR/libsimitar/NetworkFlow.h

@@ -261,7 +261,6 @@ private:
 	/// Flow-level settings
 	////////////////////////////////////////////////////////////////////////////
 
-	std::string ether_interface;
 	time_scale flow_time_scale;
 	sleep_method flow_sleep_method;
 

### 2017-10-19 SIMITAR/libsimitar/NetworkFlowFactory.cpp

@@ -44,7 +44,7 @@ NetworkFlow* NetworkFlowFactory::make_flow(const string& choise)
 	else if((choise_lc == "tins") || (choise_lc == "libtins"))
 	{
 		PLOG_VERBOSE << "Creating TinsFLow";
-		printf("TODO\n");
+		return new TinsFlow;
 	}
 	else if (choise_lc == "ostinato"){
 		PLOG_VERBOSE << "Creating OstinatoFLow";

### 2017-10-19 SIMITAR/libsimitar/NetworkFlowFactory.h

@@ -19,6 +19,7 @@
 #include "DummyFlow.h"
 #include "IperfFlow.h"
 #include "DitgFlow.h"
+#include "TinsFlow.h"
 
 /**
  *

### 2017-10-19 SIMITAR/libsimitar/NetworkTrace.cpp

@@ -46,8 +46,10 @@ NetworkTrace::NetworkTrace(const string& fileName,
 	info_tracename = root_node->first_attribute(LABEL_TRACE_NAME)->value();
 	info_commentaries = root_node->first_attribute(LABEL_COMMENTARIES)->value();
 	info_captureDate = root_node->first_attribute(LABEL_CAPTURE_DATE)->value();
-	m_trafficGenEngine =
-			root_node->first_attribute(LABEL_TRAFFIC_ENGINE)->value();
+
+	// DEBUG - check it it works
+	//m_trafficGenEngine =
+	//		root_node->first_attribute(LABEL_TRAFFIC_ENGINE)->value();
 
 	//MESSER_INFO(
 	//		"Creating Trace: info_tracename=%s, trafficGenEngine=%s,info_captureDate=%s, info_commentaries=%s, n_flows=%s  @<%s, %s>",
@@ -299,16 +301,16 @@ void NetworkTrace::setInfoCaptureDate(const std::string& infoCaptureDate)
 	info_captureDate = infoCaptureDate;
 }
 
-const std::string& NetworkTrace::getInfoCaptureInterface() const
-{
-	return info_captureInterface;
-}
+//const std::string& NetworkTrace::getInfoCaptureInterface() const
+//{
+//	return info_captureInterface;
+//}
 
-void NetworkTrace::setInfoCaptureInterface(
-		const std::string& infoCaptureInterface)
-{
-	info_captureInterface = infoCaptureInterface;
-}
+//void NetworkTrace::setInfoCaptureInterface(
+//		const std::string& infoCaptureInterface)
+//{
+//	info_captureInterface = infoCaptureInterface;
+//}
 
 const std::string& NetworkTrace::getInfoCommentaries() const
 {
@@ -374,9 +376,9 @@ int NetworkTrace::writeToFile(const std::string& fileName) const
 	trace->append_attribute(
 			doc.allocate_attribute(LABEL_TRACE_NAME, tracename));
 
-	string2charvet(m_trafficGenEngine, tgengine);
-	trace->append_attribute(
-			doc.allocate_attribute(LABEL_TRAFFIC_ENGINE, tgengine));
+	//string2charvet(m_trafficGenEngine, tgengine);
+	//trace->append_attribute(
+	//		doc.allocate_attribute(LABEL_TRAFFIC_ENGINE, tgengine));
 
 	string2charvet(info_captureDate, capdate);
[…]

### 2017-10-19 SIMITAR/libsimitar/TinsFlow.cpp

@@ -9,12 +9,277 @@
 
 TinsFlow::TinsFlow()
 {
-	// TODO Auto-generated constructor stub
-
 }
 
 TinsFlow::~TinsFlow()
 {
-	// TODO Auto-generated destructor stub
 }
 
+int TinsFlow::server()
+{
+	printf("TODO: libtins server\n");
+	return (0);
+}
+
+void TinsFlow::flowGenerate(const counter& flowId, const time_sec& onTime,
+		const uint& npackets, const uint& nbytes, const string& netInterface)
+{
+
+	uint npackets_mode1 = (uint) this->getNpacketsMode1();
+	uint npackets_mode2 = (uint) this->getNpacketsMode2();
+	uint packetSize_mode1 = (uint) this->getPacketSizeModelMode1(0).param1();
+	uint packetSize_mode2 = (uint) this->getPacketSizeModelMode2(0).param1();
+
+	PLOG_DEBUG << "[flowId:" << flowId << "] -> " << "onTime:" << onTime
+						<< " npackets:" << npackets << " netInterface:"
+						<< netInterface;
+	PLOG_DEBUG << "[flowId:" << flowId << "] -> " << "npackets_mode1"
+						<< npackets_mode1 << " npackets_mode2:"
+						<< npackets_mode2;
+
+	this->sendPackets(flowId, getLinkProtocol(), getNetworkProtocol(),
+			getTransportProtocol(), getApplicationProtocol(), getMacSrcAddr(),
+			getMacDstAddr(), getNetworkSrcAddr(), getNetworkDstAddr(),
+			getNetworkTtl(), getTransportSrcPort(), getTransportDstPort(),
+			npackets_mode1, packetSize_mode1, "h1-eth0");
+	this->sendPackets(flowId, getLinkProtocol(), getNetworkProtocol(),
+			getTransportProtocol(), getApplicationProtocol(), getMacSrcAddr(),
+			getMacDstAddr(), getNetworkSrcAddr(), getNetworkDstAddr(),
+			getNetworkTtl(), getTransportSrcPort(), getTransportDstPort(),
+			npackets_mode2, packetSize_mode2, "h1-eth0");
+}
+
+void TinsFlow::sendPackets(uint flowID, protocol etherProtocol,
+		protocol netProtocol, protocol transportProtocol, protocol application,
[…]

### 2017-10-19 SIMITAR/libsimitar/TinsFlow.h

@@ -9,12 +9,40 @@
 #define TINSFLOW_H_
 
 #include "DummyFlow.h"
+#include <tins/tins.h>
+
+using namespace Tins;
 
 class TinsFlow: public DummyFlow
 {
 public:
 	TinsFlow();
 	virtual ~TinsFlow();
+
+	/**
+	 *
+	 * @return
+	 */
+	int server();
+
+	/**
+	 *
+	 * @param flowId
+	 * @param onTime
+	 * @param npackets
+	 * @param nbytes
+	 * @param netInterface
+	 */
+	void flowGenerate(const counter& flowId, const time_sec& onTime,
+			const uint& npackets, const uint& nbytes,
+			const string& netInterface);
+
+private:
+	void sendPackets(uint flowID, protocol etherProtocol, protocol netProtocol,
+			protocol transportProtocol, protocol application, std::string etherDst,
+			std::string etherSrc, std::string netSrc, std::string netDst,
+			uint ttlNumber, uint portStc, uint portDst, uint npackets, uint pktSize,
+			std::string networkInterface);
 };
 
 #endif /* TINSFLOW_H_ */

### 2017-10-19 Tests/SimulationMininet/run.py

@@ -3,10 +3,12 @@ import time
 import os
 
 # execution options
+operation_mode = "client" # client, server
 capture_name = "capture-name"
 ether_interface = "enp3s0"
-binary_command = "iperf-flow"  # from local directory, not blocking (using &)
-exec_time = 120
+binary_command_client = "iperf -c 10.0.0.2" 
+binary_command_server = "iperf -s " 
+exec_time = 10
 
 # constants
 CAPTURE_DIR = './pcaps/'
@@ -27,8 +29,12 @@ def main():
     print_header(' Tcpdump interface:' + ether_interface + ', pcap:' + capture_name)
     proc_tcpdump = subprocess.Popen(tcpdump_command, shell=True)
     # execute simitar app
-    print_header('Simitar-app command:' + binary_command)
-    os.system(binary_command + ' &')
+	if(operation_mode == "client"):
+    	print_header('Simitar-app command:' + binary_command_client)
+    	os.system(binary_command_client + ' &')	
+	else:
+		print_header('Simitar-app command:' + binary_command_server)
+		os.system(binary_command_server + ' &')
     # sleep until finishes
     time.sleep(exec_time + 1)  # <-- There's no time.wait, but time.sleep.
     # kill tcpdump

### 2017-10-30 SIMITAR/apps/ditg-flow/src/ditg-flow.cpp
README update

@@ -1,137 +1,0 @@
-// Deps
-#include <iostream>
-#include <string>
-#include <string.h>
-#include <sys/types.h>
-#include <sys/wait.h>
-#include <unistd.h>
-#include <thread>         // std::thread
-#include <mutex>          // std::mutex
-#include <algorithm>
-#include <tclap/CmdLine.h>
-// Simitar
-#include <NetworkTrace.h>
-#include <DummyFlow.h>
-#include <SimitarWorkspace.h>
-// Local
-//#include "IperfFlowt.h"
-
-void cli_error_messege(std::string arg, std::string arg_name,
-		std::string expected_values_msg);
-
-bool cli_check_val(std::string val, std::vector<std::string> expectedVals);
-
-int main(int argc, char** argv)
-{
-	try
-	{
-		///
-		/// CLI parser
-		///
-
-		// program description
-		char progDescription[] = "SIMITAR dummy-flow component.";
-		// version information
-		char version[CHAR_BUFFER];
-		SimitarWorkspace workspace = SimitarWorkspace();
-		std::string str_version = workspace.version_tag() + ":"
-				+ workspace.version_name();
-		strcpy(version, str_version.c_str());
-
-		// comamnd line parsing
-		TCLAP::CmdLine cmd(progDescription, ' ', version);
-		TCLAP::ValueArg<std::string> mode_arg("m", "mode",
-				"Operation mode, as a client or a server", true, "", "string");
-		TCLAP::ValueArg<std::string> in_arg("x", "xml", "xml", true,
-				"Compact Trace Descriptor XML. They are saved at data/xml/ directory.",
-				"string");
-		TCLAP::ValueArg<std::string> dst_list_arg("d", "dst-list-ip",
-				"Text file in CSV format containing a list of desired destinations of IP and MAC adresses, used as servers, in the client mode. These destinations are addressed to the flows in a ring-oriented way.",
-				false, "", "string");
-		TCLAP::ValueArg<std::string> dst_server_arg("p", "dst-ip",
-				"Instead of a text file, defines a single server destination IP address in the command line.",
-				false, "", "string");
-		TCLAP::ValueArg<std::string> eth_arg("e", "ether",
-				"Ethernet interface to send the traffic, as provided by the command `ifconfig`.",
-				false, "", "string");
-
-		cmd.add(mode_arg);
-		cmd.add(in_arg);
-		cmd.add(dst_list_arg);
[…]

### 2017-10-30 SIMITAR/apps/dummy-flow/src/dummy-flow.cpp

@@ -1,157 +1,0 @@
-#include <iostream>
-#include <string>
-#include <algorithm>
-#include <tclap/CmdLine.h>
-#include <NetworkTrace.h>
-#include <DummyFlow.h>
-#include <Defines.h>
-#include <Protocol.h>
-#include <SimitarWorkspace.h>
-
-/**
- * Print an error message if the input argument is an invalid balue
- * @param arg input CLI argument
- * @param arg_name argument name
- * @param expected_values message with expected values
- */
-void cli_error_messege(std::string arg, std::string arg_name,
-		std::string expected_values_msg);
-
-/**
- * Check if the CLI input argument is a valid value
- * @param val input CLI argument.
- * @param expectedVals vector with valid CLI arguments.
- * @return
- */
-bool cli_check_val(std::string val, std::vector<std::string> expectedVals);
-
-/**
- * Erros list:
- *  #-1: invalid mode (client/server)
- *  #-2: exception parsing commandline
- */
-int main(int argc, char** argv)
-{
-	PLOG_INIT(verbose);
-	try
-	{
-		///
-		/// CLI parser
-		///
-
-		// program description
-		char progDescription[] = "SIMITAR dummy-flow component.";
-		// version information
-		char version[CHAR_BUFFER];
-		SimitarWorkspace workspace = SimitarWorkspace();
-		std::string str_version = workspace.version_tag() + ":"
-				+ workspace.version_name();
-		strcpy(version, str_version.c_str());
-
-		// comamnd line parsing
-		TCLAP::CmdLine cmd(progDescription, ' ', version);
-		TCLAP::ValueArg<std::string> mode_arg("m", "mode",
-				"Operation mode, as a client or a server", true, "", "string");
-		TCLAP::ValueArg<std::string> in_arg("x", "xml", "xml", true,
-				"Compact Trace Descriptor XML. They are salved at data/xml/ directory.",
-				"string");
-		TCLAP::ValueArg<std::string> dst_list_arg("d", "dst-list-ip",
-				"Text file in CSV format containing a list of desired destinations of IP and MAC adresses, used as servers, in the client mode. These destinations are addressed to the flows in a ring-oriented way.",
-				false, "", "string");
[…]

### 2017-10-30 SIMITAR/apps/hello-world/src/hello-world.cpp

@@ -1,7 +1,0 @@
-#include <iostream>
-
-int main()
-{
-	std::cout << "hello world" << std::endl;
-	return(0);
-}

### 2017-10-30 SIMITAR/apps/iperf-flow/src/iperf-flow.cpp

@@ -1,157 +1,0 @@
-// Deps
-#include <iostream>
-#include <string>
-#include <string.h>
-#include <sys/types.h>
-#include <sys/wait.h>
-#include <unistd.h>
-#include <thread>         // std::thread
-#include <mutex>          // std::mutex
-#include <algorithm>
-#include <tclap/CmdLine.h>
-// Simitar
-#include <NetworkTrace.h>
-#include <DummyFlow.h>
-#include <SimitarWorkspace.h>
-// Local
-//#include "IperfFlowt.h"
-
-void cli_error_messege(std::string arg, std::string arg_name,
-		std::string expected_values_msg);
-
-bool cli_check_val(std::string val, std::vector<std::string> expectedVals);
-
-int main(int argc, char** argv)
-{
-	PLOG_INIT(verbose);
-	try
-	{
-		///
-		/// CLI parser
-		///
-
-		// program description
-		char progDescription[] = "SIMITAR dummy-flow component.";
-		// version information
-		char version[CHAR_BUFFER];
-		SimitarWorkspace workspace = SimitarWorkspace();
-		std::string str_version = workspace.version_tag() + ":"
-				+ workspace.version_name();
-		strcpy(version, str_version.c_str());
-
-		// comamnd line parsing
-		TCLAP::CmdLine cmd(progDescription, ' ', version);
-		TCLAP::ValueArg<std::string> mode_arg("m", "mode",
-				"Operation mode, as a client or a server", true, "", "string");
-		TCLAP::ValueArg<std::string> in_arg("x", "xml", "xml", true,
-				"Compact Trace Descriptor XML. They are saved at data/xml/ directory.",
-				"string");
-		TCLAP::ValueArg<std::string> dst_list_arg("d", "dst-list-ip",
-				"Text file in CSV format containing a list of desired destinations of IP and MAC adresses, used as servers, in the client mode. These destinations are addressed to the flows in a ring-oriented way.",
-				false, "", "string");
-		TCLAP::ValueArg<std::string> dst_server_arg("p", "dst-ip",
-				"Instead of a text file, defines a single server destination IP address in the command line.",
-				false, "", "string");
-		TCLAP::ValueArg<std::string> eth_arg("e", "ether",
-				"Ethernet interface to send the traffic, as provided by the command `ifconfig`.",
[…]

### 2017-10-30 SIMITAR/apps/iperf-flow/test1-client.sh

@@ -1,4 +1,0 @@
-#!/bin/bash
-
-./iperf-flow -x ../../data/xml/skype.sec.xml -m client -p "10.0.0.6"
-

### 2017-10-30 SIMITAR/apps/iperf-flow/test1-server.sh

@@ -1,4 +1,0 @@
-#!/bin/bash
-
-./iperf-flow -x ../../data/xml/skype.sec.xml -m server -p "10.0.0.2"
-

### 2017-10-30 SIMITAR/apps/simitar/src/simitar-app.cpp

@@ -1,169 +1,0 @@
-#include <iostream>
-#include <string>
-#include <algorithm>
-#include <tclap/CmdLine.h>
-#include <NetworkTrace.h>
-#include <DummyFlow.h>
-#include <Defines.h>
-#include <Protocol.h>
-#include <SimitarWorkspace.h>
-
-/**
- * Print an error message if the input argument is an invalid balue
- * @param arg input CLI argument
- * @param arg_name argument name
- * @param expected_values message with expected values
- */
-void cli_error_messege(std::string arg, std::string arg_name,
-		std::string expected_values_msg);
-
-/**
- * Check if the CLI input argument is a valid value
- * @param val input CLI argument.
- * @param expectedVals vector with valid CLI arguments.
- * @return
- */
-bool cli_check_val(std::string val, std::vector<std::string> expectedVals);
-
-/**
- * Erros list:
- *  #-1: invalid mode (client/server)
- *  #-2: exception parsing commandline
- */
-int main(int argc, char** argv)
-{
-	PLOG_INIT(verbose);
-	try
-	{
-		///
-		/// CLI parser
-		///
-
-		// program description
-		char progDescription[] = "SIMITAR dummy-flow component.";
-		// version information
-		char version[CHAR_BUFFER];
-		SimitarWorkspace workspace = SimitarWorkspace();
-		std::string str_version = workspace.version_tag() + ":"
-				+ workspace.version_name();
-		strcpy(version, str_version.c_str());
-
-		// comamnd line parsing
-		TCLAP::CmdLine cmd(progDescription, ' ', version);
-		TCLAP::ValueArg<std::string> mode_arg("m", "mode",
-				"Operation mode, as a client or a server", false, "client",
-				"string");
-		TCLAP::ValueArg<std::string> tool_arg("t", "tool",
-				"Tool used to generate the traffic", true, "", "string");
-		TCLAP::ValueArg<std::string> in_arg("x", "xml",
-				"Compact Trace Descriptor XML. They are salved at data/xml/ directory.",
-				true, "", "string");
-		TCLAP::ValueArg<std::string> dst_list_arg("d", "dst-list-ip",
[…]

### 2017-10-30 SIMITAR/build.py

@@ -23,8 +23,7 @@ def clean():
 	os.system('make -C libsimitar/ clean')
 	os.system('make -C  trace-analyzer/ clean')
 	os.system('make -C  tests/ clean')
-	# os.system('rm -rf data/log/*.log')
-	# os.system('make -C clean apps/')
+	os.system('rm -rf data/log/*.log')
 
 
 def build():
@@ -47,10 +46,10 @@ def print_header(component_name):
 	print("################################################################################")	
 
 
-def print_tutorial():
-	print_header("Tutorial")
-	print('(1) Now run, at the workspace dir (SIMITAR/), run:\n source data/config/simitar-workspace.config.sh\nIt will set the enviroment variables needed.')
-	print("(2) To install in the operational system runs:\n ./build --install \nIt will compile, save the enviroment variables in the .bashrc file, and create links to the binaries in the /usr/bin/ directory. So, there will be no need for running the simitar-workspace.config.sh script.")
+#def print_tutorial():
+#	print_header("Tutorial")
+#	print('(1) Now run, at the workspace dir (SIMITAR/), run:\n source data/config/simitar-workspace.config.sh\nIt will set the enviroment variables needed.')
+#	print("(2) To install in the operational system runs:\n ./build --install \nIt will compile, save the enviroment variables in the .bashrc file, and create links to the binaries in the /usr/bin/ directory. So, there will be no need for running the simitar-workspace.config.sh script.")
 
 
 def install():
@@ -103,12 +102,13 @@ if __name__ == '__main__':
 	parser.add_argument("--clean", help="Clean", action="store_true")
 	parser.add_argument("--install", help="TODO", action="store_true")
 	parser.add_argument("--unninstall", help="TODO", action="store_true")
+	parser.add_argument("--deps", help="TODO", action="store_true")
 	argcomplete.autocomplete(parser)
 	args = parser.parse_args()
 	if args.remake:
 		clean()
 		build()
-		print_tutorial()
+		#print_tutorial()
 	elif args.clean:
 		clean()
 	elif args.install:
@@ -118,8 +118,10 @@ if __name__ == '__main__':
 		unninstall()
 	elif args.build:
 		build()
+	elif args.deps:
+		deps()
 	else:
 		build()
-		print_tutorial()
+		#print_tutorial()
 
 

### 2017-10-30 Tests/SimulationMininet/config.py

@@ -6,7 +6,7 @@ class config:
 	############################################################################
 	# execution controll
 	############################################################################
-	tool_name = "iperf" # tins, iperf, ditg
+	tool_name = "tins" # tins, iperf, ditg
 	toplology_type = "simple" # simple, tree
 	capture_name = "wombat01_skype"
 	ctd_xml_file = "../data/xml/skype.sec.xml"
@@ -18,23 +18,18 @@ class config:
 	# application controll
 	############################################################################
 	simitargen_app_dir = "../../SIMITAR/simitar-gen/"
-	
 	############################################################################
 	# experiment configuration
 	############################################################################
 	exec_time = 323
 	#exec_time = 10
 	capture_dir = './pcaps/'
+	############################################################################
+	# do not change
+	############################################################################
 	pcap_name = capture_name + "_" + toplology_type + "_" + tool_name
 
-################################################################################
-# simitar coomands
-################################################################################
-#cd_dir = " cd " + simitargen_app_dir = "; "
-#binary_command_client = cd_dir + " sudo -E ./simitar-gen --tool " + tool_name + " --mode client --ether " + ether_interface_client + " --xml " + ctd_xml_file + " --dst-ip " + dst_ip_addr
-#binary_command_server = cd_dir + " sudo -E ./simitar-gen --tool " + tool_name + " --mode server --ether " + ether_interface_server + " --xml " + ctd_xml_file
-#binary_command_client = cd_dir + " sudo -E ./simitar-gen --tool tins --mode  "  + operation_mode + " --ether " + ether_interface +" --xml " + ctd_xml_file 
-#binary_command_server = cd_dir + " sudo -E ./simitar-gen --tool tins --mode  "  + operation_mode + " --ether " + ether_interface +" --xml " + ctd_xml_file
+
 
 
 

### 2017-10-30 Tests/SimulationMininet/run-client.py

@@ -15,7 +15,7 @@ def print_header(title):
 def main():
 
 	# capture pcap
-	tcpdump_command = "tcpdump -i " + config.ether_interface_client + " -s 65535 -w " + config.capture_dir + config.pcap_name + ".client.pcap"
+	tcpdump_command = "tcpdump -i " + config.ether_interface_client + " -s 65535 -w " + config.capture_dir + config.pcap_name + "_" + config.ether_interface_client  + ".client.pcap"
 	os.system('mkdir -p ' + config.capture_dir)
 	print_header("Tcpdump")
 	print("> interface: " + config.ether_interface_client)

### 2017-10-30 Tests/SimulationMininet/run-server.py

@@ -3,7 +3,7 @@
 import subprocess
 import time
 import os
-from config import *
+from config import config
 
 operation_mode = "server"
 
@@ -16,7 +16,7 @@ def print_header(title):
 
 def main():
 	# capture pcap
-	tcpdump_command = 'tcpdump -i ' + config.ether_interface_server  + ' -s 65535 -w ' + config.capture_dir + config.pcap_name + '.server.pcap'
+	tcpdump_command = 'tcpdump -i ' + config.ether_interface_server  + ' -s 65535 -w ' + config.capture_dir + config.pcap_name + "_" + config.ether_interface_server  +'.server.pcap'
 	os.system('mkdir -p ' + config.capture_dir)
 	print_header("Tcpdump")
 	print("> interface: " + config.ether_interface_server)
@@ -38,7 +38,7 @@ def main():
 		exit()
 	print("\nPress ctrl-C to finish")
 	os.system(script_server + ' &')
-	
+
 
 if __name__ == "__main__":
 	main()

### 2017-10-30 Tests/SimulationMininet/simple-topo-test.py

@@ -24,9 +24,9 @@ def createTopo():
 	return topo
 
 class MultiSwitch( OVSSwitch ):
-    "Custom Switch() subclass that connects to different controllers"
-    def start( self, controllers ):
-        return OVSSwitch.start( self, [ cmap[ self.name ] ] )
+	"Custom Switch() subclass that connects to different controllers"
+	def start( self, controllers ):
+		return OVSSwitch.start( self, [ cmap[ self.name ] ] )
 
 setLogLevel( 'info' )
 cOdl = RemoteController( 'OpenDayLight', ip='127.0.0.1', port=6633 )
@@ -38,7 +38,7 @@ net.build()
 net.start()
 h1, h2  = net.hosts[0], net.hosts[1]
 #Running a command on host h1
-print h1.cmd('ifconfig')
+print(h1.cmd('ifconfig'))
 CLI( net )
 net.stop()
 os.system('mn -c')

### 2017-10-30 Tests/Validation/analysis/analysis-flow.m

@@ -65,15 +65,36 @@ vetFlow1 = TraceData1(:, 2);
 vetDepertureTimes2 = TraceData2(:, 5);
 vetFlow2 = TraceData2(:, 2);
 sample_size = GRANULARITY;
+
+
+
 [timeVector1 nFlows1 flowCdf1] = calc_flow(vetDepertureTimes1, vetFlow1, sample_size);
 [timeVector2 nFlows2 flowCdf2] = calc_flow(vetDepertureTimes2, vetFlow2, sample_size);
+
+%input ("DEBUG: Press any key to continue vetFlow")
+%[vetFlow1(1:30) vetFlow2(1:30)]
+%input ("DEBUG: Press any key to continue timeVector")
+%[ timeVector1(1:30) timeVector2(1:30) ]
+%input ("DEBUG: Press any key to continue nFlows")
+%[ nFlows1(1:30) nFlows2(1:30) ]
+%input ("DEBUG: Press any key to continue flowCdf")
+%[ flowCdf1(1:30) flowCdf2(1:30) ]
+%input ("DEBUG: Press any key to continue")
 
 m1 = min(timeVector1(end), timeVector2(end));
 m2 = max(timeVector1(end), timeVector2(end));
 
+%input ("DEBUG: Press any key to continue m1 m2")
+%m1
+%m2
+
 timeVector1 = regularizeVet(timeVector1, m1);
 vetFlow1 = regularizeVet(vetFlow1, m1);
 vetFlow2 = regularizeVet(vetFlow2, m1);
+%input ("DEBUG: Press any key to continue vetFlow")
+%size(vetFlow1)
+%size(vetFlow2)
+%[vetFlow1(1:30), vetFlow2(1:30)]
 
 flowCdf1 = regularizeVet(flowCdf1, m2);
 flowCdf2 = regularizeVet(flowCdf2, m2);
@@ -88,7 +109,7 @@ labels = 'time(x)(seconds) n.flows(y)1 n.flows(y)1';
 filename = strcat(DATA_DIR, title, PLOT_DATA_EXT);
 matrix2File(Flow_Ps, filename, title, labels);
 
-Flow_CDF = [timeVector2 flowCdf2 flowCdf2];
+Flow_CDF = [timeVector2 flowCdf1 flowCdf2];
 title = 'FlowCdf';
 labels = 'time(x)(seconds) flowsCDF1 flowsCDF2';
 filename = strcat(DATA_DIR, title, PLOT_DATA_EXT);

### 2017-10-30 Tests/Validation/analysis/calc_flow.m

@@ -19,12 +19,12 @@ function [timeVector nFlowsVector flowCdfVector flowCumulativeVector] = calc_flo
 % Parameters:
 %
 %       Input vetDepertureTimes: deperture times of each packet
-%	Input vetPacketSizes: list of packet sizes
-%	Input sample_size: distance between each time intervall
+%	Input vetDepertureTimes: list of inter packet times for each packet
+%	Input vetFlows: list of flows ID of each packet
+%   Input sample_size: number of packets
 %	Output timeVector: vector of time intervalls
 %	Output nFlowsVector: vector of flow per sample_size
 %	Output flowCdfVector: flow cumulative distribution
-%	Output flowCumulativeVector: flow cumulative values
 %
 vetDepertureTimes = vetDepertureTimes(:);
 vetFlows = vetFlows(:);

### 2017-10-30 Tests/Validation/analysis/regularizeVet.m

@@ -1,8 +1,8 @@
 function [ v1 ] = regularizeVet(vet1, m)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Make a vector have a specified size. If the vector is larger, the larger 
-% index values will be discarted. If the vector is smaller, they will be filled 
-% with zeros. 
+% index values will be discarted. If the vector is smaller, the lest value will
+% be repeated with zeros.
 %
 % Licensing:
 %

### 2017-10-30 Tests/Validation/run.py

@@ -2,32 +2,38 @@
 import os
 import sys
 import time
+from config import config
 sys.path.append(os.path.dirname(os.path.abspath(__file__)) + '/..')
 
 import GnuplotScripts.GnuplotScripts as gps
 import Cd.Cd as dir
 
-PCAP_FILE1 = "../../Pcap/wireshark-wiki_http.pcap"
-PCAP_FILE2 = "../../Pcap/wireshark-wiki_ospf.pcap"
-TEST_NAME = "lemur"
+# PCAP_FILE1 = "../../Pcap/wireshark-wiki_http.pcap"
+# PCAP_FILE2 = "../../Pcap/wireshark-wiki_ospf.pcap"
+# TEST_NAME = "lemur"
 
 
-def main(args):
-    pcap1 = args[0]
-    pcap2 = args[1]
-    analyzis_name = args[2]
+#def main(args):
+def main():
+    pcap1 = config.pcap1
+    pcap2 = config.pcap2
+    pcap_name1 = config.pcap1_type
+    pcap_name2 = config.pcap2_type
+    analyzis_name = config.analysis_name
     # input arguments
-    pcap_file1 = localDir = os.path.dirname(os.path.abspath(__file__)) + '/' + pcap1
-    pcap_file2 = localDir = os.path.dirname(os.path.abspath(__file__)) + '/' + pcap2
+    pcap_file1 = os.path.dirname(os.path.abspath(__file__)) + '/' + pcap1
+    pcap_file2 = os.path.dirname(os.path.abspath(__file__)) + '/' + pcap2
     plots_dir = 'plots/' + analyzis_name
     # making sure the program is being executed in the source location, so it can be executed from anyware
     cd = dir.Cd(os.path.dirname(os.path.abspath(__file__)))
-    run_analyzis(pcap_file1=pcap_file1, pcap_file2=pcap_file2, analyzis_name=analyzis_name, plots_dir=plots_dir, cd=cd)
-    plot_data('http', 'ospf', analyzis_name, plots_dir)
+    run_analyzis(pcap_file1=pcap_file1, pcap_name1=pcap_name1, pcap_file2=pcap_file2, pcap_name2=pcap_name2,
+                 pktfilter_prefix=config.pktfilter_prefix, analyzis_name=analyzis_name, plots_dir=plots_dir, cd=cd)
+    plot_data(config.pcap1_type, config.pcap2_type, analyzis_name, plots_dir)
 
 def validation_help():
[…]

### 2017-10-30 test-iperf.sh

@@ -1,4 +1,0 @@
-#!/bin/bash
-#iperf -c 10.0.0.2 --bandwidth 0k --time 0.100000 --format k  --udp  --bind 10.0.0.1:35990 --realtime  --nodelay  --ttl 64 --nodelay
-iperf -c 10.0.0.2 --bandwidth 0k --time 0.100000 --format k  --udp  --bind 10.0.0.1:35990 --realtime  --nodelay  --ttl 64 --nodelay
-

### 2017-10-31 Docs/Thesis/docs/chapter5.tex
thesis writing
README update
some updates on the thesis text

@@
-\chapter{Proof of Concepts and Validation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Proof of Concepts and Validation}\label{ch:validation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-As first proof of concepts for our tool, we are going to use Mininet's emulated testbeds.
-These tests are easily implemented and reproduced, and are able to test the performance of our tool, without kernel and hardware overheads.
-Tests in a physical testbeds, and real network functions stays for future work.
+As proof of concepts for our tool, we are going to use Mininet's emulated testbeds.
+These tests are easily implemented and reproduced, and are able to test the performance on traffic generation realism.
+Tests in a physical testbeds of, and network functions stays for future work.
 
@@
 
-All Python scripts used to create the scenarios, the Shell Scripts used to automate the tests and capture the traffic, and the Octave scripts to perform all the calculations are available on Github\footnote{\textcolor{red}{github-link}}.
-To start running the tests, following the tutorial on Github, you should not take more than 10 minutes.
+All scripts used to create the scenarios, automate the tests, and cae the traffic, and the Octave scripts to perfom all thelable at the poject github repository\footnote{\href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}}.
+They are organized as a set of python packages to enable easy reproductionon Github\footnote{\textcolor{red}{github-link}}.
+To start rub and with all depencies installed, you should not take more than 10 minutes.
 
 We will perform this testes using SIMITAR \textit{alpha} version, operation as a client on host \textit{h1}, and as a server on all other hosts.
-As traffic generator engine, we will use D-ITG and Iperf.
-The operation as a packet injector using Libtins is still unther implementation.
+As traffic generator engine, we will use Iperf, D-ITG, and Libtins C++ API.
 
-\section{Scalling Evaluation}
+\section{Simitar using Iperf and with skype-pcap}
+
+\subsection{Single hop SDN topology}
+
+We perform
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[scale=0.75]{figures/ch5/iperfFlowsPs.pdf}
+	\caption{the caption}
+	\label{fig:iperfFlowsPs}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[scale=0.75]{figures/ch5/iperfFlowCdf.pdf}
+	\caption{the caption}
+	\label{fig:iperfFlowCdf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[scale=0.75]{figures/ch5/iperfBandwidth.pdf}
+	\caption{the caption}
+	\label{fig:iperfBandwidth}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[scale=0.75]{figures/ch5/iperfWaveletMREA.pdf}
+	\caption{the caption}
+	\label{fig:iperfWaveletMREA}
+\end{figure}
+
+\subsection{Tree SDN topology}
+
+\section{Simitar using D-ITG with skype-pcap}
+
+\section{Simitar using Libtins with skype-pcap}
+
+\section{Simitar lanDiurnal-pcap/bigFlows-pcap}
+
+\subsection{Iperf as packetgen tool}
+
+\subsection{Libtins as packetgen tool}
 
 To evaluate the Scalling profile of the traccic generator, we are usig the same validation used for Swing\cite{swing-paper}: multiresolution energy analysis.
-
-\section{Packet and Flow Metrics Evaluation}

### 2017-10-31 Docs/Thesis/docs/chapter5.tex
more collectted data, update on some files

@@
 
-We perform
-
-\begin{figure}[!ht]
+\begin{figure}[t!]
 	\centering
-	\includegraphics[scale=0.75]{figures/ch5/iperfFlowsPs.pdf}
-	\caption{the caption}
-	\label{fig:iperfFlowsPs}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[scale=0.75]{figures/ch5/iperfFlowCdf.pdf}
-	\caption{the caption}
-	\label{fig:iperfFlowCdf}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[scale=0.75]{figures/ch5/iperfBandwidth.pdf}
-	\caption{the caption}
-	\label{fig:iperfBandwidth}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[scale=0.75]{figures/ch5/iperfWaveletMREA.pdf}
-	\caption{the caption}
-	\label{fig:iperfWaveletMREA}
+	\subfloat[\textit{skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperfFlowsPs.pdf}
+		\label{fig:iperf-single-flowps}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{bigFlows-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperfBandwidth.pdf}
+		\label{fig:iperf-single-bw}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{lan-diurnal-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperfFlowCdf.pdf}
+		\label{fig:iperf-single-flowcdf}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{wan-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperfWaveletMREA.pdf}
+		\label{fig:iperf-single-wavelet}
+	}
+	\caption{caption}
+	\label{fig:iperf-single}
 \end{figure}
@@
 
+\begin{figure}[t!]
+	\centering
+	\subfloat[\textit{skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowsPs.pdf}
+		\label{fig:iperf-flowps}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{bigFlows-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperftreeBandwidth.pdf}
+		\label{fig:iperf-bw}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{lan-diurnal-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowCdf.pdf}
+		\label{fig:iperf-flowcdf}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{wan-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperftreeWaveletMREA.pdf}
+		\label{fig:iperf-tree-wavelet}
+	}
+	\caption{caption}
+	\label{fig:iperf-tree}
+\end{figure}
+
 \section{Simitar using D-ITG with skype-pcap}
@@
 \section{Simitar using Libtins with skype-pcap}
+
+\begin{figure}[t!]
+	\centering
+	\subfloat[\textit{skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/tinsFlowsPs.pdf}
+		\label{fig:tins-single-flowps}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{bigFlows-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/tinsBandwidth.pdf}
+		\label{fig:tins-single-bw}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{lan-diurnal-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/tinsFlowCdf.pdf}
+		\label{fig:tins-single-flowcdf}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{wan-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/tinsWaveletMREA.pdf}
+		\label{fig:tins-single-wavelet}
+	}
+	\caption{caption}
+	\label{fig:tins-single}
+\end{figure}
 

### 2017-10-31 Tests/SimulationMininet/config.py

@@ -8,12 +8,13 @@ class config:
 	############################################################################
 	tool_name = "tins" # tins, iperf, ditg
 	toplology_type = "simple" # simple, tree
-	capture_name = "wombat01_skype"
+	capture_name = "pangolin03_skype"
 	ctd_xml_file = "../data/xml/skype.sec.xml"
 	ether_interface_client = "h1-eth0"
 	ether_interface_server = "h2-eth0"
-	dst_ip_addr = "10.0.0.2"
-	dst_ip_file = "../data/csv/ip-addrs-list1.csv"
+	host_name = "h2"
+	dst_ip_addr = "10.0.0.2" # used for a single hop (simple) topology
+	dst_ip_file = "../data/csv/ip-addrs-list1.csv" # used for a tree topology
 	############################################################################
 	# application controll
 	############################################################################
@@ -27,7 +28,7 @@ class config:
 	############################################################################
 	# do not change
 	############################################################################
-	pcap_name = capture_name + "_" + toplology_type + "_" + tool_name
+	pcap_name = capture_name + "_" + toplology_type + "_" + tool_name + '_host-' + host_name
 
 
 

### 2017-10-31 Tests/Validation/analysis/delete_this/plotBandwidth.m

@@ -1,101 +1,0 @@
-#!/usr/bin/octave-cli -qf
-% plotTraceWaveketMra.m
-%
-% Licensing:
-%
-%       This code is distributed under the GNU LGPL license.
-%
-% Modified:
-%
-%       26 March 2017
-%
-% Author:
-%
-%       Anderson Paschoalon
-%
-% Command line args:
-%
-%	arg1: experiment name
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Initialization and load data
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%inicialization
-arg_list = argv ();
-close all; clc; clf;
-graphics_toolkit ('gnuplot');
-set(0, 'DefaultLineLineWidth', 4);
-set(0,'defaulttextfontsize', 14);
-set(0,'DefaultAxesFontSize',12)
-set(0,'DefaultAxesFontName', 'Times New Roman')
-EXPERIMENT_NAME = arg_list{1};
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Constants
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% plot directory whre the gnuplot data files will be saved
-PLOT_DIR = '../../plots/';
-
-% gnuplot data extension
-PLOT_DATA_EXT = '.dat';
-
-% path and datafile prefix. file generated by pcap-sniffer.py
-DATAFILE_NAME_PREFIX = '../data/packetsinfo_';
-
-%  file extension
-DATAFILE_NAME_EXT = '.txt';
-
-% path+file with packet data to be loaded
-SIMULATION_DATA = strcat(DATAFILE_NAME_PREFIX, EXPERIMENT_NAME, DATAFILE_NAME_EXT);
-
-% load basic data 
[…]

### 2017-10-31 Tests/Validation/analysis/delete_this/plotTraceFlowData.m

@@ -1,128 +1,0 @@
-#!/usr/bin/octave-cli -qf
-% plotTraceFlowData.m
-%
-% Licensing:
-%
-%       This code is distributed under the GNU LGPL license.
-%
-% Modified:
-%
-%       26 March 2017
-%
-% Author:
-%
-%       Anderson Paschoalon
-%
-% Command line args:
-%
-%	arg1: experiment name
-%	arg2: granularity
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Initialization and load data
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%inicialization
-arg_list = argv ();
-close all; clc; clf;
-graphics_toolkit ('gnuplot');
-pkg load statistics;
-set(0, 'DefaultLineLineWidth', 4);
-set(0,'defaulttextfontsize', 14);
-set(0,'DefaultAxesFontSize',12)
-set(0,'DefaultAxesFontName', 'Times New Roman')
-DATA_FILE1 = arg_list{1};
-DATA_FILE2 = arg_list{2};
-GRANULARITY = str2num(arg_list{3});
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Constants
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% gnuplot data extension
-PLOT_DATA_EXT = '.dat';
-
-% path and datafile prefix. file generated by pcap-sniffer.py
-DATA_DIR = './data/';
-
-%  file extension
-DATAFILE_NAME_EXT = '.txt';
-
-% path+file with packet data to be loaded
-SIMULATION_DATA1 = strcat(DATA_DIR, DATA_FILE1);
-SIMULATION_DATA2 = strcat(DATA_DIR, DATA_FILE2);
-
-% load basic data 
[…]

### 2017-10-31 Tests/Validation/analysis/delete_this/plotTraceWaveletMra.m

@@ -1,108 +1,0 @@
-#!/usr/bin/octave-cli -qf
-% plotTraceWaveketMra.m
-%
-% Licensing:
-%
-%       This code is distributed under the GNU LGPL license.
-%
-% Modified:
-%
-%       26 March 2017
-%
-% Author:
-%
-%       Anderson Paschoalon
-%
-% Command line args:
-%
-%	arg1: experiment name
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Initialization and load data
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%inicialization
-arg_list = argv ();
-close all; clc; clf;
-graphics_toolkit ("gnuplot");
-set(0, 'DefaultLineLineWidth', 4);
-set(0,'defaulttextfontsize', 14);
-set(0,'DefaultAxesFontSize',12)
-set(0,'DefaultAxesFontName', 'Times New Roman')
-EXPERIMENT_NAME = arg_list{1};
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Constants
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% plot directory whre the gnuplot data files will be saved
-PLOT_DIR = '../../plots/';
-
-% gnuplot data extension
-PLOT_DATA_EXT = ".dat";
-
-% path and datafile prefix. file generated by pcap-sniffer.py
-DATAFILE_NAME_PREFIX = "../data/packetsinfo_";
-
-%  file extension
-DATAFILE_NAME_EXT = ".txt";
-
-% path+file with packet data to be loaded
-SIMULATION_DATA = strcat(DATAFILE_NAME_PREFIX, EXPERIMENT_NAME, DATAFILE_NAME_EXT);
-
-% load basic data 
[…]

### 2017-10-31 Tests/Validation/analysis/delete_this/traceBandwidth.m

@@ -1,50 +1,0 @@
-function [timeVector bandwidthVector mean_bandwidth] = bandwidth(vetDepertureTimes, vetPacketSizes, sample_size)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Returns the bandwisth over a sequnce of time intervals defined by sample_size.
-% It also returns the time sequence of times for this bandwidth values,
-% and the mean bandwidth.
-% 
-% Licensing:
-%
-%       This code is distributed under the GNU LGPL license.
-%
-% Modified:
-%
-%       29 March 2016
-%
-% Author:
-%
-%       Anderson Paschoalon
-%
-% Parameters:
-%
-%       Input vetDepertureTimes: deperture times of each packet
-%	Input vetPacketSizes: list of packet sizes
-%	Input sample_size: distance between each time intervall
-%	Output timeVector: vector of time intervalls
-%	Output bandwidthVector: vector of bandwidth values
-%	Output mean_bandwidth: mean bandwidth value 
-%
-vetDepertureTimes = vetDepertureTimes(:);
-vetPacketSizesBits = vetPacketSizes(:)*8;
-maxTime = vetDepertureTimes(end);
-out_size = floor(maxTime/sample_size);
-timeVector = zeros(out_size, 1);
-bandwidthVector = zeros(out_size, 1);
-
-
-actualTime = 0;
-j = 1;
-for i = 1:out_size
-	actualTime = actualTime + sample_size;
-	timeVector(i) = actualTime;
-	while (actualTime > vetDepertureTimes(j))
-		bandwidthVector(i) = bandwidthVector(i) + vetPacketSizes(j);
-		j = j + 1;
-	endwhile
-
-endfor
-
-bandwidthVector = bandwidthVector/sample_size;
-mean_bandwidth = sum(vetPacketSizes)/maxTime;
-%est2 = sum(bandwidthVector)/length(bandwidthVector)

### 2017-10-31 Tests/Validation/analysis/delete_this/traceFlow.m

@@ -1,73 +1,0 @@
-function [timeVector nFlowsVector flowCdfVector flowCumulativeVector] = traceFlow(vetDepertureTimes, vetFlows, sample_size)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Returns the number of flows over a sequnce of time intervals defined by 
-% sample_size, and the Empirical CDF of flows. It also returns the time 
-% sequence of times for the number of flows values.
-% 
-% Licensing:
-%
-%       This code is distributed under the GNU LGPL license.
-%
-% Modified:
-%
-%       29 March 2016
-%
-% Author:
-%
-%       Anderson Paschoalon
-%
-% Parameters:
-%
-%       Input vetDepertureTimes: deperture times of each packet
-%	Input vetPacketSizes: list of packet sizes
-%	Input sample_size: distance between each time intervall
-%	Output timeVector: vector of time intervalls
-%	Output nFlowsVector: vector of flow per sample_size
-%	Output flowCdfVector: flow cumulative distribution
-%	Output flowCumulativeVector: flow cumulative values
-%
-vetDepertureTimes = vetDepertureTimes(:);
-vetFlows = vetFlows(:);
-maxTime = vetDepertureTimes(end);
-out_size = floor(maxTime/sample_size);
-in_size = length(vetDepertureTimes);
-
-%numberOfFlows = max(vetFlows);
-%oldValsList = zeros(numberOfFlows, 1);
-nFlowsVector = zeros(out_size, 1);
-timeVector = zeros(out_size, 1);
-flowCdfVector = zeros(out_size, 1);
-flowCumulativeVector = zeros(out_size, 1);
-newFlowsVector = zeros(in_size, 1);
-actualTime = 0;
-firstIndex = 0;
-lastIndex = 0;
-
-% eval newsFlows vector
-larger_flow = 0;
-for i = 1:in_size
-	flowNumber = vetFlows(i);
-	if(flowNumber > larger_flow)
-		larger_flow = flowNumber;
-	endif
-	newFlowsVector(i) = larger_flow;
-endfor
-
-% Flows per seconds
-j = 1; %input index
-i = 1; %output index
-for i = 1:out_size
-	actualTime = actualTime + sample_size;
-	timeVector(i) = actualTime;
[…]

### 2017-10-31 Tests/Validation/config.py

@@ -3,14 +3,35 @@
 ################################################################################
 
 class config:
+    # pcap directory (all pcaps must be in the same directory)
     pcaps_dir = "pcaps/"
+
+    # pcap1 file name
     pcapfile_1 = "skype.pcap"
+
+    # pcap2 file name
+    pcapfile_2 = "pangolin03_skype_simple_tins_host-h2_h1-eth0.client.pcap"
+    #pcapfile_2 = "wombat03_skype_simple_iperf_host-h1_h1-eth0.client.pcap"
+    #pcapfile_2 = ""
     #pcapfile_2 = "wombat01_skype_simple_tins_h1-eth0.client.pcap"
-    pcapfile_2 = "wombat01_skype_simple_iperf_h1-eth0.client.pcap"
+    #pcapfile_2 = "wombat01_skype_simple_iperf_h1-eth0.client.pcap"
+    #pcapfile_2 = "wombat01_skype_tree_iperf_h1-eth0.client.pcap"
     #pcapfile_2 = "ospf.pcap"
-    analysis_name = "uva_iperf"
+
+    # analyzis name. this name will name the directory where the plots will be saved
+    analysis_name = "framboesa_tins"
+
+    # pcap1 name that will be used as legend on the plot
     pcap1_type = "skype-pcap"
-    pcap2_type = "simitar-iperf"
+
+    # pcap2 name that will be used as legend on the plot
+    pcap2_type = "simitar-tins"
+
+    # just some information that will be recorded on the file about.log
+    #comments = "Neste esperimento executei o simitar utilizando como ferramenta o iperf, em uma topologia arvore SDN. O cliente (gerador de pacotes) era o host h1, e os clientes os hosts h2-h8."
+    comments = "Neste esperimento executei o simitar utilizando como ferramenta tins, em uma topologia one-hop SDN. O cliente (gerador de pacotes) era o host h1, e o servidor é o host h2"
+
+
     ############################################################################
     # do not change
     ############################################################################

### 2017-10-31 Tests/Validation/run.py

@@ -27,7 +27,7 @@ def main():
     # making sure the program is being executed in the source location, so it can be executed from anyware
     cd = dir.Cd(os.path.dirname(os.path.abspath(__file__)))
     run_analyzis(pcap_file1=pcap_file1, pcap_name1=pcap_name1, pcap_file2=pcap_file2, pcap_name2=pcap_name2,
-                 pktfilter_prefix=config.pktfilter_prefix, analyzis_name=analyzis_name, plots_dir=plots_dir, cd=cd)
+                 pktfilter_prefix=config.pktfilter_prefix, analyzis_name=analyzis_name, plots_dir=plots_dir, cd=cd, comments=config.comments)
     plot_data(config.pcap1_type, config.pcap2_type, analyzis_name, plots_dir)
 
 def validation_help():
@@ -42,7 +42,7 @@ def print_header(title):
     print('###############################################################################')
 
 
-def run_analyzis(pcap_file1, pcap_name1, pcap_file2, pcap_name2, pktfilter_prefix, analyzis_name, plots_dir, cd):
+def run_analyzis(pcap_file1, pcap_name1, pcap_file2, pcap_name2, pktfilter_prefix, analyzis_name, plots_dir, cd, comments):
     # print info
     print_header("Analysis " + analyzis_name + " using pcaps: " + pcap_file1 + ' and ' + pcap_file2)
     print('> pcap_file1: ' + pcap_file1 )
@@ -79,6 +79,7 @@ def run_analyzis(pcap_file1, pcap_name1, pcap_file2, pcap_name2, pktfilter_prefi
         time.localtime().tm_min) + ':' + str(time.localtime().tm_sec)
     os.system('echo \"' + str_about + '\" >>' + plots_dir + '/about.log')
     os.system('echo \"' + str_date + '\" >>' + plots_dir + '/about.log')
+    os.system('echo \"' + 'comments: ' + comments + '\" >>' + plots_dir + '/about.log')
 
 
 def plot_data(trace_name1, trace_name2, analyzis_name, plots_dir):

### 2017-11-07 Docs/Thesis/docs/chapter5.tex
updates on thesis text

@@
 As proof of concepts for our tool, we are going to use Mininet's emulated testbeds.
-These tests are easily implemented and reproduced, and are able to test the performance on traffic generation realism.
-Tests in a physical testbeds of, and network functions stays for future work.
+We automate these tests using scripts, so they are reproducible.
+They are responsible for building the topology, run the SIMITAR traffic generator, collect \textit{pcaps} and perform the proposed proof of concept analysis.
+We make four plots for each trace, where we compare the original and the synthetic trace.
+The first two we used just for visual comparison:  flows per second and bandwidth.
+To compare the quality of the realism of the generated traffic, we plot the Flows cumulative distribution function\cite{harpoon-paper}, and the Wavelet multiresolution analysis\cite{swing-paper}.
+Tests on physical testbeds and network functions stay for future work.
 
-This first testbed is a tree topology, and represents tests performed by Swing\cite{swing-paper} found on the literature \cite{background-traffic-matter}\cite{legotg-paper}.
-The second is much simples, and is just a one hop connection of two hosts.
-Both topologies are SDN neworks, and have OpenDayLight Beryllium as controller.
+\begin{table}[ht!]
+	\centering
+	\caption{Experiments specification table}
+	\label{tab:specifications}
+	\begin{tabular}{ll}
+		\hline
+		Processor            & Intel(R) Core(TM) i7-4770, 8 cores, CPU @ 3.40GHz \\
+		RAM                  & 15.5 GB                                           \\
+		HD                   & 1000 GB                                            \\
+		Linux         & 4.8.0-59-generic                                  \\
+		Ubuntu        & Ubuntu 16.10 (yakkety)                            \\
+		SIMITAR       & v0.4.2 (Eulemur rubriventer)                      \\
+		Mininet       & 2.3.0d1                                           \\
+		Iperf         & iperf version 2.0.9 (1 June 2016) pthreads        \\
+		Libtins       & 3.4-2                                             \\
+		OpenDayLight v & 0.4.0-Beryllium                                   \\
+		Octave        & 4.0.3                                             \\
+		Pyshark              & 0.3.6.2                                           \\
+		Wireshark            & 2.2.6+g32dac6a-2ubuntu0.16.10                     \\ \hline
+	\end{tabular}
+\end{table}
 
-All the traffic is generated by the host \textit{h1} with IPv4 address 10.0.0.1.
-The traffic will to be captured form the host interface with TCPdump in a pcap format, and just the outgoing traffic will be considered.
-Any response packet form the hosts will be ignorated, since we want to evaluate just the traffic generated by the host, as it were a replay engine, such as TCPreplay or TCPivo\cite{tcpivo-paper}
+We use two different testbeds: a tree topology (figure~\ref{fig:topo-tree}), similar to tests performed by Swing\cite{swing-paper}\cite{background-traffic-matter}\cite{legotg-paper}, and a single hop connection of two hosts.
+Both topologies are SDN networks and have OpenDayLight Beryllium as the controller.
+We present the complete specification of these experiments at the table ~\ref{tab:specifications}.
+
+We generate the traffic on the host \textit{h1} with IPv4 address 10.0.0.1.
+The traffic is captured from the host interface with TCPdump in a \textit{pcap} format.
+We organized the project directory tree as follows\footnote{ \href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests} }: we placed the software at \texttt{SIMITAR}.
+We paced the validation tests, with short tutorials at \texttt{Tests} directory.
+The software documentation is at \texttt{Docs} directory.
+We organized the tests as python packages, configurable by a \texttt{config.py} file.
 
@@
 \end{figure}
-
-All scripts used to create the scenarios, automate the tests, and cae the traffic, and the Octave scripts to perfom all thelable at the poject github repository\footnote{\href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}}.
-They are organized as a set of python packages to enable easy reproductionon Github\footnote{\textcolor{red}{github-link}}.
-To start rub and with all depencies installed, you should not take more than 10 minutes.
-
-We will perform this testes using SIMITAR \textit{alpha} version, operation as a client on host \textit{h1}, and as a server on all other hosts.
-As traffic generator engine, we will use Iperf, D-ITG, and Libtins C++ API.
 
@@
 
-\section{Simitar using D-ITG with skype-pcap}
-
 \section{Simitar using Libtins with skype-pcap}
@@
 
-\section{Simitar lanDiurnal-pcap/bigFlows-pcap}
-
-\subsection{Iperf as packetgen tool}
-
-\subsection{Libtins as packetgen tool}
+\section{Current Limitations}
 

### 2017-11-07 Docs/Thesis/docs/chapter5.tex
docs

@@
 They are responsible for building the topology, run the SIMITAR traffic generator, collect \textit{pcaps} and perform the proposed proof of concept analysis.
-We make four plots for each trace, where we compare the original and the synthetic trace.
-The first two we used just for visual comparison:  flows per second and bandwidth.
-To compare the quality of the realism of the generated traffic, we plot the Flows cumulative distribution function\cite{harpoon-paper}, and the Wavelet multiresolution analysis\cite{swing-paper}.
-Tests on physical testbeds and network functions stay for future work.
+
+We make four plots for each trace, were we compare the original and the synthetic trace.
+Two of them we use for mere visual comparison:  flows per second and bandwidth.
+To compare the quality of the realism of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.
+In both case, the more similar the plots are, more similar the traffics are.
+The flow's cumulative distribution measures each new flow in the trace.
+The wavelet multiresolution analysis is capable of capture traffic scaling characteristics.
+If the value decreases, a periodicity on that time scale exists.
+With white-noise features, the traffic will remain constant.
+If the traffic has self-similar characteristics on a particular time scale, its value will increase linearly.
 
@@
 Both topologies are SDN networks and have OpenDayLight Beryllium as the controller.
-We present the complete specification of these experiments at the table ~\ref{tab:specifications}.
+We present the complete specification of these experiments at the table~\ref{tab:specifications}.
 
@@
 The traffic is captured from the host interface with TCPdump in a \textit{pcap} format.
-We organized the project directory tree as follows\footnote{ \href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests} }: we placed the software at \texttt{SIMITAR}.
-We paced the validation tests, with short tutorials at \texttt{Tests} directory.
-The software documentation is at \texttt{Docs} directory.
-We organized the tests as python packages, configurable by a \texttt{config.py} file.
+We organized the project directory tree as follows\footnote{ \href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests} }: we placed the software at \textit{SIMITAR}.
+We paced the validation tests, with short tutorials at \textit{Tests} directory.
+The software documentation is at \textit{Docs} directory.
+We organized the tests as python packages, configurable by a \textit{config.py} file.
 
@@
 \end{figure}
+
+\section{About SIMITAR v0.4.2 (Eulemur rubriventer) \protect\footnote{We label the tags of SIMITAR control version on GitHub as lemurs species names \href{https://en.wikipedia.org/wiki/List\_of\_lemur\_species}{https://en.wikipedia.org/wiki/List\_of\_lemur\_species}} }
+
+% \project\footnote{}
 

### 2017-11-11 Docs/Thesis/docs/chapter4.tex
new papers on Docs EADCA-2016 and EADCA-2017, also a temp script called Tests/PrototypeDataProcessor/dataProcessor/calcCostFunction2.py to plot cost functions for trace, but still not automated :\
up

@@
 
-\subsection{Introduction}
+\subsection{About Inter packet time and packet trains modelling}
 
@@
 There many consolidate works that investigate the nature of the internet traffic\cite{selfsimilar-ethernet}\cite{analysis-self-similar}\cite{stochartic-selfsimilar}\cite{selfsimilar-highvariability}\cite{multi-player-online-game-self-similarity}, and many others on the modelling of stochastic functions for specific scenarios\cite{estimation-renewal-function-ethernet-traffic}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}\cite{modeling-concurrent-heavy-tailed}\cite{optimal-scheduling-of-heavy-tailed-traffic}\cite{modelling-of-self-similar}.
-But not as many on model choice automatization\cite{sourcesonoff-paper}.
+But not as many on model choice automation\cite{sourcesonoff-paper}.
 
@@
 %2nd-review
-We will start defining the datasets we are going to use in the rest of this work. Then, we define our criteria of parameterization and model choice and a methodology for measure the quality of method.
-
-%In this chapter we will evaluate our proposed method for data modeling of inter-packet times.
-We will present curves obtained by our prototype (implemented in Gnu Octave\footnote{\href{https://www.gnu.org/software/octave/}{https://www.gnu.org/software/octave/}}) that shows in detail how each step works.
-After explaining this process, we will present an evaluation method of our results, analyzing to analyze its quality.
-After this, we give some details of how we convert code from Octave to C++ and its benefits on time execution.
-All code used in this section is available on our GitHub page.%, on the directory \texttt{Prototypes}.
-
-\subsection{Datasets}
-
-%2nd-review
 We start defining also define the \textit{pcaps} datasets we are going to use in the rest of this text. We will use for datasets, and for reproduction purposes, three are public available. 
@@
 
+%In this chapter we will evaluate our proposed method for data modeling of inter-packet times.
+We will present curves obtained by our prototype (implemented in Gnu Octave\footnote{\href{https://www.gnu.org/software/octave/}{https://www.gnu.org/software/octave/}}) that shows in detail how each step works.
+After explaining this process, we will present an evaluation method of our results, analyzing to analyze its quality.
+After this, we give some details of how we convert code from Octave to C++ and its benefits on time execution.
+All code used in this section is available on our GitHub page.%, on the directory \texttt{Prototypes}.
+
 %Along with these datasets, we will use two subpcaps from the originals.
@@
 The second, \textit{caida1s-pcap} is a trace with the first second from \texttt{wan-pcap}.
-
-\subsection{Methodology}
 

### 2017-11-11 Docs/Thesis/docs/chapter5.tex
up

@@
 
-\section{Emulated Testbeds}
+\section{Validation Tests}
 
@@
 We automate these tests using scripts, so they are reproducible.
-They are responsible for building the topology, run the SIMITAR traffic generator, collect \textit{pcaps} and perform the proposed proof of concept analysis.
+They are responsible for running all the proposed tests in this chapter and perform the calculations.
+It includes:
 
-We make four plots for each trace, were we compare the original and the synthetic trace.
-Two of them we use for mere visual comparison:  flows per second and bandwidth.
-To compare the quality of the realism of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.
-In both case, the more similar the plots are, more similar the traffics are.
-The flow's cumulative distribution measures each new flow in the trace.
-The wavelet multiresolution analysis is capable of capture traffic scaling characteristics.
-If the value decreases, a periodicity on that time scale exists.
-With white-noise features, the traffic will remain constant.
-If the traffic has self-similar characteristics on a particular time scale, its value will increase linearly.
+\begin{itemize}
+	\item Build the topology;
+	\item Run the SIMITAR traffic generator;
+	\item Collect \textit{pcaps};
+	\item Perform the proposed proof of concept analysis. 
+\end{itemize}
 
@@
 		Libtins       & 3.4-2                                             \\
-		OpenDayLight v & 0.4.0-Beryllium                                   \\
+		OpenDayLight  & 0.4.0-Beryllium                                   \\
 		Octave        & 4.0.3                                             \\
 		Pyshark       & 0.3.6.2                                     \\
-		Wireshark            & 2.2.6+g32dac6a-2ubuntu0.16.10                     \\ \hline
+		Wireshark     & 2.2.6+g32dac6a-2ubuntu0.16.10               \\
+		Tcudump       & 4.9.0 \\
+		libpcap       & 1.7.4\\
+		\hline
 	\end{tabular}
 \end{table}
+
+For each test, we generate a set of plots to compare the original and synthetic trace.
+Two of them we use for mere visual comparison:  flows per second and bandwidth.
+To compare the realism quality of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.
+In both cases, the more similar the plots are, the more similar the traffics are according to each perspective.
+
+The flow's cumulative distribution measures each new flow identified the trace.
+It is a measure similarity of the traffic at the flow-level.
+The wavelet multiresolution analysis is capable of capture traffic scaling characteristics and is a measure of similarity at the packet-level.
+If the value decreases, a periodicity on that time scale exists.
+With white-noise features, the traffic will remain constant.
+If the traffic has self-similar characteristics on a particular time scale, its value will increase linearly.
 
@@
 
-\section{About SIMITAR v0.4.2 (Eulemur rubriventer) \protect\footnote{We label the tags of SIMITAR control version on GitHub as lemurs species names \href{https://en.wikipedia.org/wiki/List\_of\_lemur\_species}{https://en.wikipedia.org/wiki/List\_of\_lemur\_species}} }
+We use as testbeds: a tree topology (figure~\ref{fig:topo-tree}), similar to tests performed by Swing\cite{swing-paper}\cite{background-traffic-matter}\cite{legotg-paper}, and a single hop connection of two hosts.
+Both topologies are SDN networks and have OpenDayLight Beryllium as the controller.
+We present the complete specification of these experiments at the table~\ref{tab:specifications}.
 
-% \project\footnote{}
+For generating the traffic on the host \textit{h1} with IPv4 address 10.0.0.1.
+The traffic is captured from the host interface with TCPdump in a \textit{pcap} format.
+We organized the project directory tree as follows\footnote{ \href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests} }: we placed the software at \textit{SIMITAR}.
+We paced the validation tests, with short tutorials at \textit{Tests} directory.
+They are organized as python packages, and configurable by a \textit{config.py} file.
+The software documentation is at \textit{Docs} directory.
 
-\section{Simitar using Iperf and with skype-pcap}
+We use SIMITAR v0.4.2 (Eulemur rubriventer)\foornote{ We label the tags of SIMITAR control version on GitHub as lemurs species names (\href{https://en.wikipedia.org/wiki/List_of_lemur_species}{https://en.wikipedia.org/wiki/List_of_lemur_species})}, as tagged at the GitHub repository.
+SIMITAR already have two functional traffic generator engines: Iperf and libtins C++ API.
 
-\subsection{Single hop SDN topology}
+For schedule of the timing of traffic generated by each flow, we implemented three methodologies: \texttt{usleep()} C function,\texttt{select()} C function and \textit{pooling}.
+Here we use \texttt{usleep()} .
+We implemented the class \texttt{IperfFlow,} responsible for generate the traffic of each flow, using \texttt{popen()} and \texttt{pclose()} to instantiate Iperf processes, responsible for generating the traffic.
+Traffic customization on Iperf has many limitations.
+It cannot assign arbitrary IP addresses as source and destination since it must establish a connection between the source and destination.
+For the transport layer, it just supports TCP and UDP protocol, and constant bandwidth traffic.
+On the other hand, it enables customization of transmission time, number of packets, windows size, TTL, packet sizes, payload and many other features.
+Since Iperf has to establish a communication, SIMITAR must operate in the client mode on the source, and server mode on the destinations.
 
-\begin{figure}[t!]
+Libtins enable the creation and emission of arbitrary packets and do not require the establishment of a connection.
+Thus SIMITAR does not need to operate in server mode on the destination.
+The packet customization capability is vast, and enable a full usage of our model parameters.
+Control inter-packet times stays for future work.
+
+\section{Results}
+
+\begin{table}[ht!]
 	\centering
-	\subfloat[\textit{skype-pcap}]{
+	\caption{My caption}
+	\label{my-label}
+	\begin{tabular}{lllll}
+		\hline
+		& skype-pcap & simitar iperf one-hop & simitar iperf tree & simitar libtins \\ \hline
+		Hurst Exponent                  &            &                       &                    &                 \\
+		Data bit rate (kbps)            &            &                       &                    &                 \\
+		Average packet rate (packets/s) &            &                       &                    &                 \\
+		Average packet size (bytes)     &            &                       &                    &                 \\
+		Number of packets               &            &                       &                    &                 \\ \hline
+	\end{tabular}
+\end{table}
+
+% Flows per second
+\begin{figure}[ht!]
+	\centering
+	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
 		\includegraphics[width=77mm]{figures/ch5/iperfFlowsPs.pdf}
-		\label{fig:iperf-single-flowps}
+		\label{fig:iperfCdf}
 	}
 	\hspace{0mm}
-	\subfloat[\textit{bigFlows-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperfBandwidth.pdf}
-		\label{fig:iperf-single-bw}
+	\subfloat[\textit{Iperf, tree, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowsPs.pdf}
+		\label{fig:iperftreeCdf}
 	}
 	\hspace{0mm}
-	\subfloat[\textit{lan-diurnal-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperfFlowCdf.pdf}
-		\label{fig:iperf-single-flowcdf}
+	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/tinsFlowsPs.pdf}
+		\label{fig:tinsCdf}
 	}
 	\hspace{0mm}
-	\subfloat[\textit{wan-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperfWaveletMREA.pdf}
-		\label{fig:iperf-single-wavelet}
-	}
-	\caption{caption}
-	\label{fig:iperf-single}
-\end{figure}
-
-\subsection{Tree SDN topology}
-
-\begin{figure}[t!]
-	\centering
-	\subfloat[\textit{skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowsPs.pdf}
-		\label{fig:iperf-flowps}
+	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/tinsFlowsPs.pdf}
+		\label{fig:tinsLgwCdf}
 	}
 	\hspace{0mm}
-	\subfloat[\textit{bigFlows-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperftreeBandwidth.pdf}
-		\label{fig:iperf-bw}
+	\caption{Flow per seconds}
+	\label{fig:flows-ps}
+\end{figure}
+% Bandwidth
+\begin{figure}[h!]
+	\centering
+	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperfBandwidth.pdf}
+		\label{fig:iperfCdf}
 	}
 	\hspace{0mm}
-	\subfloat[\textit{lan-diurnal-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowCdf.pdf}
-		\label{fig:iperf-flowcdf}
+	\subfloat[\textit{Iperf, tree, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperftreeBandwidth.pdf}
+		\label{fig:iperftreeCdf}
 	}
 	\hspace{0mm}
-	\subfloat[\textit{wan-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperftreeWaveletMREA.pdf}
-		\label{fig:iperf-tree-wavelet}
-	}
-	\caption{caption}
-	\label{fig:iperf-tree}
-\end{figure}
-
-\section{Simitar using Libtins with skype-pcap}
-
-\begin{figure}[t!]
-	\centering
-	\subfloat[\textit{skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/tinsFlowsPs.pdf}
-		\label{fig:tins-single-flowps}
+	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/tinsBandwidth.pdf}
+		\label{fig:tinsCdf}
 	}
 	\hspace{0mm}
-	\subfloat[\textit{bigFlows-pcap}]{
+	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
 		\includegraphics[width=77mm]{figures/ch5/tinsBandwidth.pdf}
-		\label{fig:tins-single-bw}
+		\label{fig:tinsLgwCdf}
 	}
 	\hspace{0mm}
-	\subfloat[\textit{lan-diurnal-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/tinsFlowCdf.pdf}
-		\label{fig:tins-single-flowcdf}
+	\caption{Traces bandwidth.}
+	\label{fig:flows-bandwidth}
+\end{figure}
+% Flow CDF
+\begin{figure}[ht!]
+	\centering
+	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperfFlowCdf.pdf}
+		\label{fig:iperfCdf}
 	}
 	\hspace{0mm}
-	\subfloat[\textit{wan-pcap}]{
+	\subfloat[\textit{Iperf, tree, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowCdf.pdf}
+		\label{fig:iperftreeCdf}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/tinsFlowCdf.pdf}
+		\label{fig:tinsCdf}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/tinsFlowCdf.pdf}
+		\label{fig:tinsLgwCdf}
+	}
+	\hspace{0mm}
+	\caption{Flows cumulative distributions.}
+	\label{fig:flows-cdf}
+\end{figure}
+% Wabelet
+\begin{figure}[h!]
+	\centering
+	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperfWaveletMREA.pdf}
+		\label{fig:iperfWaveletMREA}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{Iperf, tree, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/iperftreeWaveletMREA.pdf}
+		\label{fig:iperftreeWaveletMREA}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
 		\includegraphics[width=77mm]{figures/ch5/tinsWaveletMREA.pdf}
-		\label{fig:tins-single-wavelet}
+		\label{fig:tinsWaveletMREA}
 	}
-	\caption{caption}
-	\label{fig:tins-single}
+	\hspace{0mm}
+		\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
+			\includegraphics[width=77mm]{figures/ch5/tinsWaveletMREA.pdf}
+			\label{fig:tinsLgwWaveletMREA}
+		}
+		\hspace{0mm}
+	\caption{Wavelet multiresolution energy analysis.}
+	\label{fig:wavelet}
 \end{figure}

### 2017-11-11 SIMITAR/libsimitar/TinsFlow.cpp

@@ -287,13 +287,13 @@ void TinsFlow::sendPackets(uint flowID, protocol etherProtocol,
 		sender.open_l2_socket(networkInterface);
 		sender.open_l3_socket(socket_type);
 
-		std::cout << std::endl << "[FlowId:" << flowID << "]: <";
+		//std::cout << std::endl << "[FlowId:" << flowID << "]: <";
 		for (uint i = 0; i < npackets; i++)
 		{
 			sender.send(*flowPkt, iface);
-			std::cout << i << ", ";
+			//std::cout << i << ", ";
 		}
-		std::cout << ">" << endl;
+		//std::cout << ">" << endl;
 		sender.close_socket(socket_type, networkInterface);
 
 	} catch (Tins::invalid_address &e)

### 2017-11-11 Tests/SimulationMininet/config.py

@@ -6,15 +6,15 @@ class config:
 	############################################################################
 	# execution controll
 	############################################################################
-	tool_name = "iperf" # tins, iperf, ditg
-	toplology_type = "simple" # simple, tree
-	capture_name = "coala_skype"
+	tool_name = "tins" # tins, iperf, ditg
+	toplology_type = "simple" # simple or tree
+	capture_name = "guaxinim_lgw10s" # prefix name that will be given to the pcap. Sugestion use animal names :P 
 	#ctd_xml_file = "../data/xml/skype.sec.xml"
 	#ctd_xml_file = "../data/xml/skype.ms.xml"
-	ctd_xml_file = "../data/xml/lgw10s.sec.xml"
+	ctd_xml_file = "../data/xml/lgw10s.sec.xml" # Compact trace descriptor
 	ether_interface_client = "h1-eth0"
 	ether_interface_server = "h2-eth0"
-	host_name = "h2"
+	host_name = "h1"
 	dst_ip_addr = "10.0.0.2" # used for a single hop (simple) topology
 	dst_ip_file = "../data/csv/ip-addrs-list1.csv" # used for a tree topology
 	############################################################################
@@ -24,7 +24,7 @@ class config:
 	############################################################################
 	# experiment configuration
 	############################################################################
-	exec_time = 11
+	exec_time = 15 
 	#exec_time = 10
 	capture_dir = './pcaps/'
 	############################################################################

### 2017-11-11 Tests/Validation/config.py

@@ -11,17 +11,18 @@ class config:
     pcapfile_1 = "lan-gateway-10s.pcap"
 
     # pcap2 file name
-    pcapfile_2 = "pangolin03_skype_simple_tins_host-h2_h1-eth0.client.pcap"
-    pcapfile_2 = "coala_skype_simple_iperf_host-h2_h1-eth0.client.pcap"
+    #pcapfile_2 = "pangolin03_skype_simple_tins_host-h2_h1-eth0.client.pcap"
+    #pcapfile_2 = "coala_skype_simple_iperf_host-h2_h1-eth0.client.pcap"
     #pcapfile_2 = "wombat03_skype_simple_iperf_host-h1_h1-eth0.client.pcap"
-    #pcapfile_2 = ""
+    #pcapfile_2 = "wombat03_skype_simple_iperf_host-h1_h1-eth0.client.pcap"
     #pcapfile_2 = "wombat01_skype_simple_tins_h1-eth0.client.pcap"
     #pcapfile_2 = "wombat01_skype_simple_iperf_h1-eth0.client.pcap"
     #pcapfile_2 = "wombat01_skype_tree_iperf_h1-eth0.client.pcap"
     #pcapfile_2 = "ospf.pcap"
+    pcapfile_2 = "guaxinim_lgw10s_simple_tins_host-h1_h1-eth0.client.pcap"
 
-    # analyzis name. this name will name the directory where the plots will be saved
-    analysis_name = "abacate_tins"
+    # analyzis name. this name will name the directory where the plots will be saved. Sugestion: fruit name :P
+    analysis_name = "jaca_tins2"
 
     # pcap1 name that will be used as legend on the plot
     pcap1_type = "lgw10s-pcap"
@@ -31,7 +32,7 @@ class config:
 
     # just some information that will be recorded on the file about.log
     #comments = "Neste esperimento executei o simitar utilizando como ferramenta o iperf, em uma topologia arvore SDN. O cliente (gerador de pacotes) era o host h1, e os clientes os hosts h2-h8."
-    comments = "Neste esperimento executei o simitar utilizando como ferramenta iperf, em uma topologia one-hop SDN. O cliente (gerador de pacotes) era o host h1, e o servidor é o host h2"
+    comments = "Neste esperimento executei o simitar utilizando como ferramenta tins, em uma topologia one-hop SDN. O cliente (gerador de pacotes) era o host h1, e o servidor o host h2. Estou tentando reproduzir o trafego pesado do lan-gateway"
 
 
     ############################################################################

### 2017-11-11 Tests/Validation/run.py

@@ -1,4 +1,5 @@
 #!/usr/bin/python3.5
+import argparse
 import os
 import sys
 import time
@@ -14,7 +15,7 @@ import Cd.Cd as dir
 
 
 #def main(args):
-def main():
+def main(replot):
     pcap1 = config.pcap1
     pcap2 = config.pcap2
     pcap_name1 = config.pcap1_type
@@ -26,13 +27,15 @@ def main():
     plots_dir = 'plots/' + analyzis_name
     # making sure the program is being executed in the source location, so it can be executed from anyware
     cd = dir.Cd(os.path.dirname(os.path.abspath(__file__)))
-    run_analyzis(pcap_file1=pcap_file1, pcap_name1=pcap_name1, pcap_file2=pcap_file2, pcap_name2=pcap_name2,
-                 pktfilter_prefix=config.pktfilter_prefix, analyzis_name=analyzis_name, plots_dir=plots_dir, cd=cd, comments=config.comments)
+    if replot == False:
+        run_analyzis(pcap_file1=pcap_file1, pcap_name1=pcap_name1, pcap_file2=pcap_file2, pcap_name2=pcap_name2,
+            pktfilter_prefix=config.pktfilter_prefix, analyzis_name=analyzis_name, plots_dir=plots_dir, cd=cd, comments=config.comments)
     plot_data(config.pcap1_type, config.pcap2_type, analyzis_name, plots_dir)
 
 def validation_help():
     print('To execute run:')
-    print('    ./run.py')
+    print('    ./run.py          : run the calculations and plot the data')
+    print('    ./run.py --replot : replot the data')
     print('To configure edite the file config.py')
 
 def print_header(title):
@@ -67,12 +70,13 @@ def run_analyzis(pcap_file1, pcap_name1, pcap_file2, pcap_name2, pktfilter_prefi
     os.system('./analysis-hustExponent.m  ' + datafile1 + ' ' + datafile2)
     os.system('./analysis-bandwidth.m ' + datafile1 + ' ' + datafile2 + ' "1" "10^6"')
     os.system('./analysis-flow.m ' + datafile1 + ' ' + datafile2 + ' "1"')
+    os.system('./analysis-pcapinfo.sh ' + pcap_file1 + ' ' + pcap_file2)
     # back to root dir
     cd.back()
     # creating plots dir
     os.system('rm -rf ' + plots_dir)
     os.system('mkdir -p ' + plots_dir)
[…]

### 2017-11-11 Tests/Validation/scripts/analysis-hustExponent.m

@@ -67,8 +67,8 @@ h2 = hurst(interArrival2);
 % Save data 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 h = [h1 h2];
-title = 'hust exponent : inter-packet times';
-labels = strcat('Hurst:',DATA_FILE1 ,', Hurst:',DATA_FILE2);
-filename = strcat(DATA_DIR, title, PLOT_DATA_EXT);
+title = ' hust exponent : inter-packet times';
+labels = strcat(' Hurst:',DATA_FILE1 ,', Hurst:',DATA_FILE2);
+filename = strcat(DATA_DIR, 'hurst_exponent', PLOT_DATA_EXT);
 matrix2File(h, filename, title, labels);
 

### 2017-11-11 Tests/Validation/scripts/analysis-pcapinfo.sh

@@ -1,1 +1,15 @@
-capinfos ../pcaps/skype.pcap  | sed "s/\(.*\):\(\s\)*//g"
+#!/bin/bash
+
+pcapfile1=$1
+pcapfile2=$2
+data_dir='./data/'
+info_file=${data_dir}'pcapsinfo.txt'
+hline='-------------------------------------------------------------'
+
+# capinfos ../pcaps/skype.pcap  
+echo ${hline} >> ${info_file}
+capinfos ${pcapfile1} >> ${info_file}
+echo ${hline} >> ${info_file}
+capinfos ${pcapfile2} >> ${info_file}
+cat ${info_file}
+

### 2017-11-14 Docs/Thesis/docs/chapter5.tex
>>>>>update in some scripts...BUGS.... actually I'm using this version on the thesis....<<<<<<

@@
 
-We use SIMITAR v0.4.2 (Eulemur rubriventer)\foornote{ We label the tags of SIMITAR control version on GitHub as lemurs species names (\href{https://en.wikipedia.org/wiki/List_of_lemur_species}{https://en.wikipedia.org/wiki/List_of_lemur_species})}, as tagged at the GitHub repository.
+We use SIMITAR v0.4.2 (Eulemur rubriventer)\footnote{ We label the tags of SIMITAR control version on GitHub as lemurs species names (\href{https://en.wikipedia.org/wiki/List_of_lemur_species}{https://en.wikipedia.org/wiki/List\_of\_lemur\_species})}, as tagged at the GitHub repository.
 SIMITAR already have two functional traffic generator engines: Iperf and libtins C++ API.
@@
 	\centering
-	\caption{My caption}
+	\caption{Sumary of results comparing the original traces (italic) and te traffic generated by SIMITAR, with the description of the scenario.}
 	\label{my-label}
-	\begin{tabular}{lllll}
+	\scalebox{0.87}{
+\begin{tabular}{lcccccc}
 	\hline
-		& skype-pcap & simitar iperf one-hop & simitar iperf tree & simitar libtins \\ \hline
-		Hurst Exponent                  &            &                       &                    &                 \\
-		Data bit rate (kbps)            &            &                       &                    &                 \\
-		Average packet rate (packets/s) &            &                       &                    &                 \\
-		Average packet size (bytes)     &            &                       &                    &                 \\
-		Number of packets               &            &                       &                    &                 \\ \hline
+	\multicolumn{1}{c}{\multirow{3}{*}{}} & \multirow{3}{*}{\textit{skype-pcap}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}skype, \\ one-hop, \\ iperf\end{tabular}}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}skype, \\ tree, \\ iperf\end{tabular}}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}skype, \\ one-hop, \\ libtins\end{tabular}}} & \multirow{3}{*}{\textit{lgw10s-pcap}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}lgw10s, \\ one-hop, \\ libtins\end{tabular}}} \\
+	\multicolumn{1}{c}{}                  &                             & \multicolumn{1}{c}{}                                                                                     & \multicolumn{1}{c}{}                                                                                  & \multicolumn{1}{c}{}                                                                                       &                              & \multicolumn{1}{c}{}                                                                                        \\
+	\multicolumn{1}{c}{}                  &                             & \multicolumn{1}{c}{}                                                                                     & \multicolumn{1}{c}{}                                                                                  & \multicolumn{1}{c}{}                                                                                       &                              & \multicolumn{1}{c}{}                                                                                        \\ \hline
+	Hurst Exponent                        & 0.601                       & 0.618                                                                                                    & 0.598                                                                                                 & 0.691                                                                                                      & 0.723                        & 0.738                                                                                                       \\
+	Data bit rate (kbps)                  & 7                           & 19                                                                                                       & 19                                                                                                    & 12                                                                                                         & 7252                         & 6790                                                                                                        \\
+	Average packet rate (packets/s)       & 3                           & 4                                                                                                        & 5                                                                                                     & 6                                                                                                          & 2483                         & 2440                                                                                                        \\
+	Average packet size (bytes)           & 260,89                      & 549,05                                                                                                   & 481,14                                                                                                & 224,68                                                                                                     & 365,00                       & 347,85                                                                                                      \\
+	Number of packets                     & 1071                        & 1428                                                                                                     & 1604                                                                                                  & 2127                                                                                                       & 24 k                         & 24 k                                                                                                        \\
+	Number of flows                       & 167                         & 350                                                                                                      & 325                                                                                                   & 162                                                                                                        & 3350                         & 3264                                                                                                        \\ \hline
 \end{tabular}
+	}
 \end{table}
@@
 	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperfFlowsPs.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-iperf-FlowsPs.pdf}
 		\label{fig:iperfCdf}
@@
 	\subfloat[\textit{Iperf, tree, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowsPs.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-FlowsPs.pdf}
 		\label{fig:iperftreeCdf}
@@
 	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/tinsFlowsPs.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-tins-FlowsPs.pdf}
 		\label{fig:tinsCdf}
@@
 	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/tinsFlowsPs.pdf}
+		\includegraphics[width=77mm]{figures/ch5/lgw-tins-FlowsPs.pdf}
 		\label{fig:tinsLgwCdf}
@@
 	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperfBandwidth.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-iperf-Bandwidth.pdf}
 		\label{fig:iperfCdf}
@@
 	\subfloat[\textit{Iperf, tree, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperftreeBandwidth.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-Bandwidth.pdf}
 		\label{fig:iperftreeCdf}
@@
 	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/tinsBandwidth.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-tins-Bandwidth.pdf}
 		\label{fig:tinsCdf}
@@
 	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/tinsBandwidth.pdf}
+		\includegraphics[width=77mm]{figures/ch5/lgw-tins-Bandwidth.pdf}
 		\label{fig:tinsLgwCdf}
@@
 	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperfFlowCdf.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-iperf-FlowCdf.pdf}
 		\label{fig:iperfCdf}
@@
 	\subfloat[\textit{Iperf, tree, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowCdf.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-FlowCdf.pdf}
 		\label{fig:iperftreeCdf}
@@
 	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/tinsFlowCdf.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-tins-FlowCdf.pdf}
 		\label{fig:tinsCdf}
@@
 	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/tinsFlowCdf.pdf}
+		\includegraphics[width=77mm]{figures/ch5/lgw-tins-FlowCdf.pdf}
 		\label{fig:tinsLgwCdf}
@@
 	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperfWaveletMREA.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-iperf-WaveletMREA.pdf}
 		\label{fig:iperfWaveletMREA}
@@
 	\subfloat[\textit{Iperf, tree, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/iperftreeWaveletMREA.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-WaveletMREA.pdf}
 		\label{fig:iperftreeWaveletMREA}
@@
 	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/tinsWaveletMREA.pdf}
+		\includegraphics[width=77mm]{figures/ch5/skype-tins-WaveletMREA.pdf}
 		\label{fig:tinsWaveletMREA}
@@
 		\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
-			\includegraphics[width=77mm]{figures/ch5/tinsWaveletMREA.pdf}
+			\includegraphics[width=77mm]{figures/ch5/lgw-tins-WaveletMREA.pdf}
 			\label{fig:tinsLgwWaveletMREA}

### 2017-11-14 Tests/Validation/config.py

@@ -14,7 +14,6 @@ class config:
     #pcapfile_2 = "pangolin03_skype_simple_tins_host-h2_h1-eth0.client.pcap"
     #pcapfile_2 = "coala_skype_simple_iperf_host-h2_h1-eth0.client.pcap"
     #pcapfile_2 = "wombat03_skype_simple_iperf_host-h1_h1-eth0.client.pcap"
-    #pcapfile_2 = "wombat03_skype_simple_iperf_host-h1_h1-eth0.client.pcap"
     #pcapfile_2 = "wombat01_skype_simple_tins_h1-eth0.client.pcap"
     #pcapfile_2 = "wombat01_skype_simple_iperf_h1-eth0.client.pcap"
     #pcapfile_2 = "wombat01_skype_tree_iperf_h1-eth0.client.pcap"
@@ -22,7 +21,7 @@ class config:
     pcapfile_2 = "guaxinim_lgw10s_simple_tins_host-h1_h1-eth0.client.pcap"
 
     # analyzis name. this name will name the directory where the plots will be saved. Sugestion: fruit name :P
-    analysis_name = "jaca_tins2"
+    analysis_name = "Jaca_tins"
 
     # pcap1 name that will be used as legend on the plot
     pcap1_type = "lgw10s-pcap"
@@ -32,8 +31,7 @@ class config:
 
     # just some information that will be recorded on the file about.log
     #comments = "Neste esperimento executei o simitar utilizando como ferramenta o iperf, em uma topologia arvore SDN. O cliente (gerador de pacotes) era o host h1, e os clientes os hosts h2-h8."
-    comments = "Neste esperimento executei o simitar utilizando como ferramenta tins, em uma topologia one-hop SDN. O cliente (gerador de pacotes) era o host h1, e o servidor o host h2. Estou tentando reproduzir o trafego pesado do lan-gateway"
-
+    comments = "Neste esperimento executei o simitar utilizando como ferramenta Libtins(C++), em uma topologia single hop SDN. O cliente (gerador de pacotes) era o host h1, e o servidor os hosts h2-h8. Estou tentando reproduzir um pesado trafego de um lan gateway por 10 segundos."
 
     ############################################################################
     # do not change

### 2017-11-14 Tests/Validation/scripts/analysis-flow.m

@@ -68,44 +68,29 @@ sample_size = GRANULARITY;
 
 
 
-[timeVector1 nFlows1 flowCdf1] = calc_flow(vetDepertureTimes1, vetFlow1, sample_size);
-[timeVector2 nFlows2 flowCdf2] = calc_flow(vetDepertureTimes2, vetFlow2, sample_size);
+[timeVector1 nFlows1 flowCdf1 cumulative1 maxflows1] = calc_flow(vetDepertureTimes1, vetFlow1, sample_size);
+[timeVector2 nFlows2 flowCdf2 cumulative2 maxflows2] = calc_flow(vetDepertureTimes2, vetFlow2, sample_size);
 
-%input ("DEBUG: Press any key to continue vetFlow")
-%[vetFlow1(1:30) vetFlow2(1:30)]
-%input ("DEBUG: Press any key to continue timeVector")
-%[ timeVector1(1:30) timeVector2(1:30) ]
-%input ("DEBUG: Press any key to continue nFlows")
-%[ nFlows1(1:30) nFlows2(1:30) ]
-%input ("DEBUG: Press any key to continue flowCdf")
-%[ flowCdf1(1:30) flowCdf2(1:30) ]
-%input ("DEBUG: Press any key to continue")
 
 m1 = min(timeVector1(end), timeVector2(end));
 m2 = max(timeVector1(end), timeVector2(end));
 
-%input ("DEBUG: Press any key to continue m1 m2")
-%m1
-%m2
-
 timeVector1 = regularizeVet(timeVector1, m1);
-vetFlow1 = regularizeVet(vetFlow1, m1);
-vetFlow2 = regularizeVet(vetFlow2, m1);
-%input ("DEBUG: Press any key to continue vetFlow")
-%size(vetFlow1)
-%size(vetFlow2)
-%[vetFlow1(1:30), vetFlow2(1:30)]
+nFlows1 = regularizeVet(nFlows1, m1);
+nFlows2 = regularizeVet(nFlows2, m1);
 
 flowCdf1 = regularizeVet(flowCdf1, m2);
 flowCdf2 = regularizeVet(flowCdf2, m2);
+cumulative1 = regularizeVet(cumulative1, m2);
+cumulative2 = regularizeVet(cumulative2, m2);
[…]

### 2017-11-14 Tests/Validation/scripts/calc_flow.m

@@ -1,4 +1,4 @@
-function [timeVector nFlowsVector flowCdfVector flowCumulativeVector] = calc_flow(vetDepertureTimes, vetFlows, sample_size)
+function [timeVector nFlowsVector flowCdfVector flowCumulativeVector nflows] = calc_flow(vetDepertureTimes, vetFlows, sample_size)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Returns the number of flows over a sequnce of time intervals defined by 
 % sample_size, and the Empirical CDF of flows. It also returns the time 
@@ -25,12 +25,14 @@ function [timeVector nFlowsVector flowCdfVector flowCumulativeVector] = calc_flo
 %	Output timeVector: vector of time intervalls
 %	Output nFlowsVector: vector of flow per sample_size
 %	Output flowCdfVector: flow cumulative distribution
+%	Output nflows: number ov flows
 %
 vetDepertureTimes = vetDepertureTimes(:);
 vetFlows = vetFlows(:);
 maxTime = vetDepertureTimes(end);
 out_size = floor(maxTime/sample_size);
 in_size = length(vetDepertureTimes);
+nflows = max(vetFlows);
 
 %numberOfFlows = max(vetFlows);
 %oldValsList = zeros(numberOfFlows, 1);
@@ -68,6 +70,15 @@ for i = 1:out_size
 	nFlowsVector(i) = uniqueFlows;
 	flowCumulativeVector(i) = newFlowsVector(j);
 	
+	%i
+	%firstIndex
+	%lastIndex
+	%vetFlows(firstIndex:lastIndex)
+	%unique(vetFlows(firstIndex:lastIndex))
+	%uniqueFlows
+	%pause;
+	
 endfor
 flowCdfVector = flowCumulativeVector/max(flowCumulativeVector);
+
 

### 2017-11-14 Docs/Thesis/docs/chapter5.tex
thesis text update

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%'
 \section{Validation Tests}
@@
 As proof of concepts for our tool, we are going to use Mininet's emulated testbeds.
-We automate these tests using scripts, so they are reproducible.
+We automate all these tests using scripts, so they are reproducible.
 They are responsible for running all the proposed tests in this chapter and perform the calculations.
@@
 	\item Run the SIMITAR traffic generator;
-	\item Collect \textit{pcaps};
-	\item Perform the proposed proof of concept analysis. 
+	\item Collect the packeckets as \textit{pcap} files, and stract data from it;
+	\item Perform the proposed proof of concept analysis;
+	\item Plot the data.
 \end{itemize}
+
+Each test is organized as a Python packege, responsible for tigger all the applications and other scripts.
+The parameters for each simulation can be configured by a \textit{config.py} file.
+Also the file \textit{README} provide a tutorial to run correctely each test.
+With all tools instaled, less then fifteen minutes is enought to stat runnin each test again.A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specificatins and the software versions.
 
@@
 
-For each test, we generate a set of plots to compare the original and synthetic trace.
-Two of them we use for mere visual comparison:  flows per second and bandwidth.
-To compare the realism quality of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.
-In both cases, the more similar the plots are, the more similar the traffics are according to each perspective.
-
-The flow's cumulative distribution measures each new flow identified the trace.
-It is a measure similarity of the traffic at the flow-level.
-The wavelet multiresolution analysis is capable of capture traffic scaling characteristics and is a measure of similarity at the packet-level.
-If the value decreases, a periodicity on that time scale exists.
-With white-noise features, the traffic will remain constant.
-If the traffic has self-similar characteristics on a particular time scale, its value will increase linearly.
-
-We use two different testbeds: a tree topology (figure~\ref{fig:topo-tree}), similar to tests performed by Swing\cite{swing-paper}\cite{background-traffic-matter}\cite{legotg-paper}, and a single hop connection of two hosts.
-Both topologies are SDN networks and have OpenDayLight Beryllium as the controller.
-We present the complete specification of these experiments at the table~\ref{tab:specifications}.
-
-We generate the traffic on the host \textit{h1} with IPv4 address 10.0.0.1.
-The traffic is captured from the host interface with TCPdump in a \textit{pcap} format.
-We organized the project directory tree as follows\footnote{ \href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests} }: we placed the software at \textit{SIMITAR}.
-We paced the validation tests, with short tutorials at \textit{Tests} directory.
-The software documentation is at \textit{Docs} directory.
-We organized the tests as python packages, configurable by a \textit{config.py} file.
-
 \begin{figure}[!ht]
@@
 
-We use as testbeds: a tree topology (figure~\ref{fig:topo-tree}), similar to tests performed by Swing\cite{swing-paper}\cite{background-traffic-matter}\cite{legotg-paper}, and a single hop connection of two hosts.
+For each test, we generate a set of plots to compare the original and synthetic trace.
+Two of them we use for mere visual comparison:  flows per second and bandwidth.
+To compare the realism quality of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.
+On every case, the more closer the plots are, the more similar the traffics are according to each perspective.
+Also, we wrote in the table ~\ref{tab:results-summary} a complation of each traffic statistics.
+
+The flow's cumulative distribution measures each new flow identified the trace.
+It is a measure similarity of the traffic at the flow-level.
+The wavelet multiresolution analysis is capable of capture traffic scaling characteristics and is a measure of similarity at the packet-level.
+If the value decreases, a periodicity on that time scale exists.
+With white-noise features, the traffic will remain constant.
+If the traffic has self-similar characteristics on a particular time scale, its value will increase linearly.
+
+We use as testbeds: a tree topology (figure~\ref{fig:topo-tree}), similar to tests performed by Swing\cite{swing-paper}\cite{background-traffic-matter}\cite{legotg-paper}, and a one-hop connection of two hosts.
 Both topologies are SDN networks and have OpenDayLight Beryllium as the controller.
-We present the complete specification of these experiments at the table~\ref{tab:specifications}.
 
@@
 The traffic is captured from the host interface with TCPdump in a \textit{pcap} format.
-We organized the project directory tree as follows\footnote{ \href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests} }: we placed the software at \textit{SIMITAR}.
-We paced the validation tests, with short tutorials at \textit{Tests} directory.
-They are organized as python packages, and configurable by a \textit{config.py} file.
+We organized the project directory tree as follows\footnote{ \href{https://github.com/AndersonPaschoalon/ProjetoMestrado}{https://github.com/AndersonPaschoalon/ProjetoMestrado} }: the software is at \textit{SIMITAR}.
+All validation tests and project prototypes we aved at \textit{Tests} directory.
 The software documentation is at \textit{Docs} directory.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
@@
 	\caption{Sumary of results comparing the original traces (italic) and te traffic generated by SIMITAR, with the description of the scenario.}
-	\label{my-label}
+	\label{tab:results-summary}
 	\scalebox{0.87}{
@@
 		\includegraphics[width=77mm]{figures/ch5/skype-iperf-FlowsPs.pdf}
-		\label{fig:iperfCdf}
+		\label{fig:iperfFps}
 	}
@@
 		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-FlowsPs.pdf}
-		\label{fig:iperftreeCdf}
+		\label{fig:iperftreeFps}
 	}
@@
 		\includegraphics[width=77mm]{figures/ch5/lgw-tins-FlowsPs.pdf}
-		\label{fig:tinsLgwCdf}
+		\label{fig:tinsLgwFps}
 	}
@@
 		\includegraphics[width=77mm]{figures/ch5/skype-iperf-Bandwidth.pdf}
-		\label{fig:iperfCdf}
+		\label{fig:iperfBw}
 	}
@@
 		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-Bandwidth.pdf}
-		\label{fig:iperftreeCdf}
+		\label{fig:iperftreeBw}
 	}
@@
 		\includegraphics[width=77mm]{figures/ch5/skype-tins-Bandwidth.pdf}
-		\label{fig:tinsCdf}
+		\label{fig:tinsBw}
 	}
@@
 		\includegraphics[width=77mm]{figures/ch5/lgw-tins-Bandwidth.pdf}
-		\label{fig:tinsLgwCdf}
+		\label{fig:tinsLgwBw}
 	}
@@
 
-\section{Current Limitations}
+We display our results in the figures ~\ref{fig:flows-ps} to ~\ref{fig:wavelet}, and in the table ~\ref{tab:results-summary}.
+As we can see in the figure ~\ref{fig:flows-bandwidth}, the generated traffics are not identical regarding bandwidth.
+But the synthetic and original both presents a fractal-like shape.
+In fact, the values of each  Hurst exponent of inter-packet times had an error smaller than 10\% compared to the original in every case.
+The plot of flows per second seems much more accurate visually, since most of the peaks match.
+We can analyze it precisely observing the cumulative flow distribution\ref{fig:flows-cdf}, where the results were almost identical on every plot.
+However, when SIMITAR is replicating the traffic of \textit{lgw10s-pcap} the number of flows per second decreases.
+It happens because of the methodology of traffic generation of the class \textit{TinsFlow} since it sends the packets of each flow as fast as possible.
+This behavior can be observed in the bandwidth plot as well since it is much larger in the first seconds.
 
-To evaluate the Scalling profile of the traccic generator, we are usig the same validation used for Swing\cite{swing-paper}: multiresolution energy analysis.
+%<<<<<<<<<<<<<<<<<<<<>>>>>>>>>>>>>>>>>>>>>>>>>
+
+The best results achieved by SIMITAR were on the flow distribution characterization.
+On every experiment made, the cumulative distribution of flows was almost identical.
+The small imprecisions on the plots are expected and should result from threads and process concurrence of resources and imprecision on the sleep/wake signaling on the traffic generation side.
+Imprecisions on packet capture buffer may count as well since the operating system did the packet timing.
+This was our greatest achievement in our research.
+This result means that our method of flow scheduling and independent traffic generation were effective and efficient on replicating the original traffic.
+The actual number of flows was much larger when SIMITAR used Iperf and about the same amount but small when used libtins.
+This happens because Iperf establishes the connection to control the signaling and the traffic statistics in addition to the connection of the actual traffic.
+With libtins, the number is small because if an error happens when it is creating a flow, its execution is aborted.
+
+On Wavelet multiresolution analysis of inter-packet times, the results have changed more in each case.
+The time resolution chosen was ten milliseconds, and it is represented in $\log_2$ scale.
+The actual time scale of each $j$ value is given by the equation:
+
+\begin{equation}
+t = \frac{2^{j}}{100} [s]
+\end{equation}
+
+In the first case(figure ~\ref{fig:iperfWaveletMREA}), SIMITAR using Iperf in a single-hop scenario, on small time scales the energy level of the synthetic traffic remained almost constant, which indicates white-noise characteristics.
+The original skype traffic increased linearly, an indication of fractal shape.
+The synthetic trace started to increase at the time scale 5-6 (300-600 milliseconds).
+After this scale, the error between the curves become very small.
+One possible reason for this behavior is the fact that the constant which regulate the minimum burst time (\texttt{DataProcessor::m\_min\_on\_time}) is set to 100 milliseconds.
+For small time scales the traffic become similar to white noise since Iperf just emits traffic with constant bandwidth.
+For larger scales, it captures the same fractals patterns of the original trace.
+It also captures a periodicity pattern at the time-scale of 9 seconds.
+The authors of \cite{swing-paper} measured the same periodicity pattern.
+But on this trace, we observe some periodicity at 11 and 13 time-scales (20 and 80 seconds).
+
+In the second case, on a tree topology on small time scales, the same white-noise behavior is identified.
+We identify a similar behavior on the energy behavior on larger time-scales, but with a larger gap between the curves.
+Packet collision on switches requiring retransmission packets explains this behavior.
+In fact, as we can see in the table ~\ref{tab:results-summary}, two hundred more packets are leaving the client on the tree topology compared to the one-hop.
+
+On the last two plots, where we use libtins as packet crafter, the energy level is much higher, and the curves are much less correlated.
+SIMITAR are not modeling inter-packet with libtins, and are sending packets as fast as possible.
+We may observe on the figures ~\ref{fig:tinsBw} and ~\ref{fig:tinsLgwBw} that than have much  higher peaks compared to the original \textit{skype-pcap}.
+As we see in the figure ~\ref{fig:tinsBw}, it just captured some periodicity characteristics at the time larger than 11-12 (20-40 seconds).
+SIMITAR determines larger periods between packets with session OFF times, and the session cut time (\texttt{DataProcessor::m\_session\_cut\_time}) is 30 seconds, that explain this behavior.
+
+The current implementation still has problems on accurately reproduce \textit{pcaps} with high bandwidth values and a larger number of flows.
+The major limitation is the time required to generate the compact trace descriptor.
+The procedure is still mono-thread, and the linear regression procedure is not optimized.
+So, the time for processing a large pcap file with thousands of flows is still prohibitively high, spending dozens of hours on processing.
+
+Using the first 10 seconds of the trace \textit{bigFlows-pcap}, on 10 seconds of operation, Iperf generated much fewer packets than the expected.
+It is an expected behavior since the operating system couldn't handle so much newer processes (one per flow) in such short time.
+On the other hand, the same drawback wasn't observed using libtins as traffic generator tool, since being a low-level API makes it much computationally cheaper.
+In the figure ~\ref{fig:} we visualize the results of SIMITAR using \textit{libtins}.
+The flow's cumulative distribution was achieved a good result.
+But, the wavelet analysis curves still didn't match.
+
+%\section{Current Limitations}
+%
+%To evaluate the Scalling profile of the traccic generator, we are usig the same validation used for Swing\cite{swing-paper}: multiresolution energy analysis.

### 2017-11-14 SIMITAR/simitar.py

@@ -1,82 +1,0 @@
-#!/bin/bash
-
-import sys
-import os
-import re
-
-def title(title_str):
-    print("")
-    print("###############################################################################")
-    print(title_str)
-    print("###############################################################################")
-
-def check_dependencies_libs(lib_list):
-    for lib_name in lib_list:
-        dependency_check_out = os.popen('ldconfig -p | grep ' +  lib_name).read()
-        dependency_check_out = ''.join(dependency_check_out.split()).replace("\n", "")
-
-        if dependency_check_out == '':
-            print('Missing lybrary ' + lib_name)
-            exit()
-        else:
-            print(lib_name + ' ok')
-
-def check_dependencies_tools(tools_list):
-    for tool_name in tools_list:
-        dependency_check_out = os.popen('command -v ' + tool_name + ' -v').read()
-        dependency_check_out = ''.join(dependency_check_out.split()).replace("\n", "")
-
-        if dependency_check_out == '':
-            print('Missing tool ' + tool_name)
-            exit()
-        else:
-            print(tool_name + ' ok')
-
-def check_dependencies_python(pkg_list):
-    for pkg in pkg_list:
-        try:
-            import pkg
-            print()
-        except ImportError:
-            print('Missing Python package ' + pkg)
-            exit()
-
-def trick_eclipse(projec_dir):
-    """
-    Trick eclipse, letting the binaries be built in a bin directory
-    :return:
-    """
-    os.system('cd ' + projec_dir)
-    os.system('rm -rf Debug')
-    os.system('rm -rf Release')
-    os.system('mkdir bin')
-    os.system('ln -s bin Debug')
-    os.system('ln -s bin Release')
-
-
-if __name__ == '__main__':
-    title('Checking dependencies')
-    lib_list = ('armadillo', 'ITG', 'sqlite3', 'libboost', 'libblas', 'liblapack', 'openblas', 'sctp', 'log4cpp')
-    tool_list = ('tshark', 'wireshark', 'octave', 'sqlite3', 'cmake', 'iperf', 'ostinato')
-    python_dps = ('sqlite3', 'pyshark', 'rstr', 'numpy', 'fnvhash', 'termcolor')
-    check_dependencies_libs(lib_list)
-    check_dependencies_tools(tool_list)
-    #check_dependencies_python(python_dps)
-
-    title('Building libsimicar')
-    #os.system('make -C common/')
-
[…]

### 2017-11-16 Docs/Thesis/docs/appendix/appendixC.tex
3rd revision of the thesis text complete, apA and apB completed. Still have to finish apC and apD
updates on the thesis text

@@
 
-\section{CDFs distributions}
+In this appendix, we include some plots made during the process of model validation from the chapter ~\ref{ch:modeling-evaluation}, not included in the final version of the text. They include:
 
-The trace \textit{bigflows-pcap} has a much higher inter packet rate, and a smaller dispersion.
-Weibull is the model chosen by AIC/BIC, and it is the second best on correlation and self-similarity (Exponential(Me) and Cauchy are the best respectively).
-Exponential(Me) chooses as the second preferable, has the closest to the original mean and standard deviation.
-Comparing the plots of the CDF function, the Weibull seams to express well both small and larger values of inter packet times, while Exponential(Me) is preciser on the mean values, as we can see at figure ~\ref{fig:aproximation-originalbigflows-cdf}.
+\begin{itemize}
+
+	\item CDF's distributions;
+
+	\item QQPlots;
+
+	\item Correlation;
+
+	\item Hurst exponent;
+
+	\item Mean inter-packet times;
+
+	\item Standard deviation of inter-packet times;
+
+\end{itemize}
 

### 2017-11-16 Docs/Thesis/docs/chapter3.tex
updates on the thesis text

@@
 
-SIMITAR works in four different states: as a sniffer, packet injector, client or server. 
-When it working as a sniffer, is produces as output a Compact Trace Descriptor file. It may work over a \textit{pcap} file or an Ethernet interface.
+Each SIMITAR component works as a different application:
+
+\begin{itemize}
+	\item \texttt{sniffer-cli.py};
+	\item \texttt{trace.db} (sqlite3 database);
+	\item \texttt{trace-analyzer}.
+	\item \texttt{simitar-gen} (traffic generator).
+\end{itemize}
+
+When it working as a sniffer, it strores data from the capture traffic in the sqlite3 database.
+It may work over a \textit{pcap} file or an Ethernet interface.
+Working as a trace a trace-analyzer, it receive the name of the trace as stored in the database, and creates a XML compact trace descriptor.
+The constants used in the modelling may be changed and provided as command line argument.
+If not, the default values will be used.
+
+As a traffic generator it may work as a client or a server.
+Working as a server is necessary for tools that require establishing a connection before generate the traffic, such as Iperf and D-ITG.
+It will just work passivaly.
+Working as a client, is acts as a traffic emissor.
+Tools such as \textit{libtins} dos not require server operation the send the traffic.
 

### 2017-11-16 Docs/Thesis/docs/chapter5.tex
updates on the thesis text

@@
 As proof of concepts for our tool, we are going to use Mininet's emulated testbeds.
-We automate all these tests using scripts, so they are reproducible.
+We automate all tests using scripts, so our experiments are are fully  reproducible.
 They are responsible for running all the proposed tests in this chapter and perform the calculations.
@@
 
-Each test is organized as a Python packege, responsible for tigger all the applications and other scripts.
+Each test is organized as a Python packege, responsible for tigger all the applications and procedures.
 The parameters for each simulation can be configured by a \textit{config.py} file.
-Also the file \textit{README} provide a tutorial to run correctely each test.
-With all tools instaled, less then fifteen minutes is enought to stat runnin each test again.A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specificatins and the software versions.
+The files \textit{README} on each packege, provide a tutorial to run correctely each test.
+With all tools instaled, less then fifteen minutes is enought for run each test again.
+A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specificatins and the software versions.
 
@@
 
+% Bandwidth
+\begin{figure}[h!]
+	\centering
+	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/skype-iperf-Bandwidth.pdf}
+		\label{fig:iperfBw}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{Iperf, tree, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-Bandwidth.pdf}
+		\label{fig:iperftreeBw}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/skype-tins-Bandwidth.pdf}
+		\label{fig:tinsBw}
+	}
+	\hspace{0mm}
+	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
+		\includegraphics[width=77mm]{figures/ch5/lgw-tins-Bandwidth.pdf}
+		\label{fig:tinsLgwBw}
+	}
+	\hspace{0mm}
+	\caption{Traces bandwidth.}
+	\label{fig:flows-bandwidth}
+\end{figure}
 % Flows per second
@@
 	\label{fig:flows-ps}
-\end{figure}
-% Bandwidth
-\begin{figure}[h!]
-	\centering
-	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/skype-iperf-Bandwidth.pdf}
-		\label{fig:iperfBw}
-	}
-	\hspace{0mm}
-	\subfloat[\textit{Iperf, tree, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-Bandwidth.pdf}
-		\label{fig:iperftreeBw}
-	}
-	\hspace{0mm}
-	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/skype-tins-Bandwidth.pdf}
-		\label{fig:tinsBw}
-	}
-	\hspace{0mm}
-	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
-		\includegraphics[width=77mm]{figures/ch5/lgw-tins-Bandwidth.pdf}
-		\label{fig:tinsLgwBw}
-	}
-	\hspace{0mm}
-	\caption{Traces bandwidth.}
-	\label{fig:flows-bandwidth}
 \end{figure}
@@
 
-We display our results in the figures ~\ref{fig:flows-ps} to ~\ref{fig:wavelet}, and in the table ~\ref{tab:results-summary}.
-As we can see in the figure ~\ref{fig:flows-bandwidth}, the generated traffics are not identical regarding bandwidth.
-But the synthetic and original both presents a fractal-like shape.
-In fact, the values of each  Hurst exponent of inter-packet times had an error smaller than 10\% compared to the original in every case.
-The plot of flows per second seems much more accurate visually, since most of the peaks match.
+We display our results in the figures ~\ref{fig:flows-ps} to ~\ref{fig:wavelet}, and in the table ~\ref{tab:results-summary}, where the original and the synthetic traffics are compared.
+As we can see in the figure ~\ref{fig:flows-bandwidth}, the generated traffics are not identical regarding bandwidth, however both presents fractal-like shape.
+The Hurst exponent of inter-packet times in every case has an error smaller than 10\% compared to the original in every case.
+This result indicates that in fact, the fractal-level of each synthetic traffic is indeed similar to the original.
+
+The plot of flows per second seems much more accurate visually since most of the peaks match.
+Indeed, no visual lag between the plots.
 We can analyze it precisely observing the cumulative flow distribution\ref{fig:flows-cdf}, where the results were almost identical on every plot.
 However, when SIMITAR is replicating the traffic of \textit{lgw10s-pcap} the number of flows per second decreases.
-It happens because of the methodology of traffic generation of the class \textit{TinsFlow} since it sends the packets of each flow as fast as possible.
-This behavior can be observed in the bandwidth plot as well since it is much larger in the first seconds.
-
-%<<<<<<<<<<<<<<<<<<<<>>>>>>>>>>>>>>>>>>>>>>>>>
+It happens because of the methodology of traffic generation of the class \textit{TinsFlow} since it sends the packets of each stream as fast as possible.
+So each flow occurrence is restricted to smaller intervals.
+This behavior can be observed as well in the bandwidth plot.
+It is much larger in the first seconds and small at the end.
 
@@
 Imprecisions on packet capture buffer may count as well since the operating system did the packet timing.
-This was our greatest achievement in our research.
-This result means that our method of flow scheduling and independent traffic generation were effective and efficient on replicating the original traffic.
-The actual number of flows was much larger when SIMITAR used Iperf and about the same amount but small when used libtins.
-This happens because Iperf establishes the connection to control the signaling and the traffic statistics in addition to the connection of the actual traffic.
-With libtins, the number is small because if an error happens when it is creating a flow, its execution is aborted.
+This was our most significant achievement in our research.
+This result means that our method of flow scheduling and independent traffic generation were effective and efficient on replicating the original traffic at the flow-level.
+The actual number of flows was much more significant when SIMITAR used Iperf and about the same amount but little small when used libtins.
+This discrepancy happens with Iperf because it establishes additional connections to control the signaling and traffic statistics.
+So, this more substantial number of flows comes from accounting, not just the traffic connections, but also with the signaling as well.
+With libtins, the number of flows is small, because, if it fails to create a new traffic flow, this flows generation execution is aborted.
 
@@
 The time resolution chosen was ten milliseconds, and it is represented in $\log_2$ scale.
-The actual time scale of each $j$ value is given by the equation:
+The actual time pf each time-scale $j$ value is given by the equation:
 
@@
 
-In the first case(figure ~\ref{fig:iperfWaveletMREA}), SIMITAR using Iperf in a single-hop scenario, on small time scales the energy level of the synthetic traffic remained almost constant, which indicates white-noise characteristics.
+In the first case (figure ~\ref{fig:iperfWaveletMREA}), SIMITAR using Iperf in a single-hop scenario, on small time scales the energy level of the synthetic traffic remained almost constant, which indicates white-noise characteristics.
 The original skype traffic increased linearly, an indication of fractal shape.
@@
 
-The current implementation still has problems on accurately reproduce \textit{pcaps} with high bandwidth values and a larger number of flows.
-The major limitation is the time required to generate the compact trace descriptor.
+The current implementation still has problems on accurately reproduce \textit{pcaps} with high bandwidth values and a more substantial number of flows.
+The primary limitation is the time required to generate the trace descriptor.
 The procedure is still mono-thread, and the linear regression procedure is not optimized.
-So, the time for processing a large pcap file with thousands of flows is still prohibitively high, spending dozens of hours on processing.
+Although creating a trace descriptor of a small pcap file is fast, the time for processing large pcap file with thousands of flows is still prohibitively high, spending dozens of hours.
 
@@
 On the other hand, the same drawback wasn't observed using libtins as traffic generator tool, since being a low-level API makes it much computationally cheaper.
-In the figure ~\ref{fig:} we visualize the results of SIMITAR using \textit{libtins}.
-The flow's cumulative distribution was achieved a good result.
-But, the wavelet analysis curves still didn't match.
+Some others unexpected behavior must have a more in-depth investigation, such as libtins generating more packets than expected for \textit{skype-pcap}, but not for \textit{lgw10s-pcap}, and why the creation of some flows fail, and how to fix it if possible.
 
-%\section{Current Limitations}
-%
-%To evaluate the Scalling profile of the traccic generator, we are usig the same validation used for Swing\cite{swing-paper}: multiresolution energy analysis.
+Another promising possible investigation is what traffic each tool can better represent.
+In terms of number of flows and packets, bandwidth and for larger \textit{pcaps}, \textit{libtins} is a best option.
+But Iperf has presented a better performance replicating scaling characteristics of applications.

### 2017-11-16 Docs/Thesis/docs/chapter6.tex
updates on thesis text
updates on the thesis text

@@
 
-TODO Limitations, future work
-
-TODO considerações, contrubuições, lições, boas idéias, mas idéias
-
-\section{Final Conclusions}
-
-\textcolor{red}{some text here}
-
 \section{Future Work}
 
-In this section we present some ideas for future works and implementation for SIMITAR.
-On the first section "Improoving results", we suggest approaches for improving the current results.
+In this section we discuss some ideas for future works and implementation for SIMITAR.
+On the first section "Improoving results", we suggest approaches to get better results.
 They include calibration of some constants, finer controll of packet injection, and performance improovments.
 
-\subsection{Improoving results}
+\subsection{Improoving performance}
+
+The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor.
+In the current implementation, the linear regression is mono-thread, and the stop criteria are just the number of iterations.
+Parallel processing, and creating stop criteria based on convergence should increase the processing performance.
+
+On the traffic generation, currently, the threads for all flows are being instantiated once the traffic generations start.
+A smarter traffic generation, where each thread is instantiated when the traffic is active and dies when it is inactive should reduce the overhead for \textit{pcap} files with a large number of flows.
+For traffic with a massive amount of flows, a methodology for merging them should reduce overheads and enable replication of traffic with a larger bandwidth.
+
+Finally, the current implementation using \textit{libtins} to generate the packets does not model inter-packet times.
+To avoid processing overheads on calculating random numbers, these values may be calculated before the actual traffic generation, and then be used.
+By this approach, the scaling characteristics of the traffic generated by libtins should improve, and be closer to the original traffic.
 
@@
 We can do this first adjusting some constants used by our algorithms.
-Some of these values will change the performance not for all but on tools that support stochastic functions for inter packet times.
+Some of these values will change the performance on tools that supports stochastic functions for inter packet times.
 They are:
@@
 Second, because we avoid the parameterization process, which can be costly in the case of linear regression.
-Its value today is set to 30.increasing this value, we may achieve a more reasonable performance for individual flows.
+Its value today is set to 30.
+Increasing this value, we may achieve a more reasonable performance for individual flows.
 	\item \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times.
@@
 
-The modification of others  constants or approaches may change the performance for any type of underlying tool or API. They are:
+The modification of others  constants or approaches may change the performance for any tool or API. They are:
 
@@
 \end{itemize}
-
-% Para extensão do trafego gerado, é necessário um estudo da melhor calibração para cada ferramente, como o D-ITG, Iperf, Libtins, o que pode melhorar os resultados
-
-\subsubsection{SIMITAR as a Packet Injector}
-
-This proposed functionality is still under implementation, and we are using Libtins API \footnote{\href{http://libtins.github.io/}{http://libtins.github.io/}}.
-It enables packet crafting and injection at a reasonable performance, and provide support for many protocols.
-It is not threaded safe, so will require some cars, such as the use of mutexes.
-But will enable a finer control of packet header contents, packet sizes, inter-packet times and a number of packets sent.
-In that way, we expect to achieve better results in terms of realism.
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[height=2.0in]{figures/ch6/libtins-flow}
-	\caption{Expansion of SIMITAR using Libtins for traffic generation}
-	\label{fig:libtins-flow}
-\end{figure}
 
@@
 
-\subsubsection{Thread Menager}
-
-Instead of each flow's thread control individually sleep and wake times, a better approach would be a separated thread control and manage all the other threads' life-cycle operation.
-This approach can increase the timing accuracy for flows and \textit{files}.
-
-% \subsubsection{Improving DataProcessor Performance}
-
-% Melhorar os algoritimos adicionando técnicas adicionais de modelagem, como condição de parada para o algoritimo gradient descendent, stochastic gradient descendent, entre outros
-
 \subsection{Further Implementations}
@@
 
-	\item \textbf{Use OpenDayLight REST API for data collection}: Another different approach for data collection could be the use the OpenDayLight REST API to collect data from an SDN OpenFlow switches, instead of a using a Sniffer.
+	%\item \textbf{Use OpenDayLight REST API for data collection}: Another different approach for data collection could be the use the OpenDayLight REST API to collect data from an SDN OpenFlow switches, instead of a using a Sniffer.
 Through REST API is possible to extract many statistics from nodes, hosts, and ports, such active flows, the number of packets matched per flows, packet drops, and so on.
@@
 He has not to care about how the packets were going to be generated anymore nor in what programming language is being used to craft packets.
+
+\section{Final Conclusions}
+
+TODO Limitations, future work
+
+TODO considerações, contrubuições, lições, boas idéias, mas idéias
+
+\textcolor{red}{some text here}

### 2017-11-17 Docs/Thesis/docs/chapter6.tex
updates on the thesis text

@@
 In this section we discuss some ideas for future works and implementation for SIMITAR.
-On the first section "Improoving results", we suggest approaches to get better results.
-They include calibration of some constants, finer controll of packet injection, and performance improovments.
+We suggest approaches to get better results.
+They include perfromance improovments, calibration of some constants and finer controll of packet injection.
+We list them as a task list in the talbe
 
-\subsection{Improoving performance}
+\begin{table}[ht!]
+	\centering
+	\caption{Future Work: task list}
+	\label{tab:task-list}
+	\begin{tabular}{cccc}
+		\hline
+		\multicolumn{3}{c}{{\color[HTML]{000000} Future Work}}                                                                               & Priority                \\ \hline
+		1                      & Optimizing linear regression                              &                                                 & \textit{high}                    \\
+		2                      & Flow-merging option                                       &                                                 & medium                  \\
+		3                      & Smart flow-scheduler                                      &                                                 & \textit{high}                    \\
+		4                      & \texttt{DataProcessor::minimumAmountOfPackets}                         &                                                 & low                     \\
+		5                      & DPDK KNI interfaces                                       &                                                 & low                     \\
+		6                      & Multi-thread C++ sniffer                                  & \multirow{-6}{*}{Performance}                   & \textit{high}                    \\ \hline
+		7                      & Model inter-packet times on \texttt{TinsFlow}           &                                                 & \textit{high}                    \\
+		8                      & D-ITG flow generator (\texttt{DitgFlow})                &                                                 & low                     \\
+		9                      & DPDK flow generator (\texttt{DpdkFlow})                 &                                                 & medium                     \\
+		10                     & Ostinato flow generator (\texttt{OstinatoFlow})         & \multirow{-4}{*}{Tool support}                  & low                     \\ \hline
+		11                     & \texttt{DataProcessor::min\_time}                       &                                                 & low                     \\
+		12                     & \texttt{DataProcessor::m\_min\_on\_time}                &                                                 & low                     \\
+		13                     & \texttt{DataProcessor::m\_session\_cut\_time}           &                                                 & low                     \\
+		14                     & Minimum number of packets per flow option                 & \multirow{-4}{*}{Calibration}  & low                     \\ \hline
+		15 & Python API/Lua for traffic generation & & low \\
+		16 & Crafter of  pcap files & & low \\
+		%17 & Json compact trace descriptor  & \multirow{-3}{*}{New features} & low 
+		\hline
+	\end{tabular}
+\end{table}
 
-The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor.
+(1) The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor.
+The performance becomes an issue when processing large \textit{pcap} files with more dozens of thousands of flows.
+The processing in this case may take some hours.
 In the current implementation, the linear regression is mono-thread, and the stop criteria are just the number of iterations.
-Parallel processing, and creating stop criteria based on convergence should increase the processing performance.
+Parallel processing, and creating stop criteria based on convergence, alongside with the number of iterations, should increase the processing performance.
 
-On the traffic generation, currently, the threads for all flows are being instantiated once the traffic generations start.
+(2) Crating an option for merging flows is a possibility to imprrove performance of traffic with several thousands of flows and Gigabits of bandwidth, such as from WAN captures.
+A merge criterion for example is considere just network headers to classify the flows.
+
+(3) On the traffic generation, currently, the threads for all flows are being instantiated once the traffic generations start.
 A smarter traffic generation, where each thread is instantiated when the traffic is active and dies when it is inactive should reduce the overhead for \textit{pcap} files with a large number of flows.
-For traffic with a massive amount of flows, a methodology for merging them should reduce overheads and enable replication of traffic with a larger bandwidth.
+For traffic with a massive amount of flows, a methodology for merging them should reduce overheads and enable replication of traffic with a much larger bandwidth.
 
-Finally, the current implementation using \textit{libtins} to generate the packets does not model inter-packet times.
-To avoid processing overheads on calculating random numbers, these values may be calculated before the actual traffic generation, and then be used.
-By this approach, the scaling characteristics of the traffic generated by libtins should improve, and be closer to the original traffic.
-
-\subsubsection{Tool calibration}
-
-To improve our results, the first approach is performing a deeper study on calibrating each tool, to achieve the best results possible.
-We can do this first adjusting some constants used by our algorithms.
-Some of these values will change the performance on tools that supports stochastic functions for inter packet times.
-They are:
-
-\begin{itemize}
-	\item \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of flow packets is larger than this value.
+(4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of flow packets is larger than this value.
 If it is smaller, we use only the constant model, for two reasons.
 First, because with a small sample, the accuracy estimate stochastic model is poor.
-Second, because we avoid the parameterization process, which can be costly in the case of linear regression.
+Second, because we avoid the parameterization process, which is cost in the case of linear regression.
 Its value today is set to 30.
-Increasing this value, we may achieve a more reasonable performance for individual flows.
-	\item \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times.
-We use this value to avoid inter-packet times equals to zero due to the sniffer resolution.
-In that case, some of our procedures would diverge.
-It can change the fitting accuracy.
-Today, this value is $5e-8$.
-\end{itemize}
+Increasing this value, we may achieve a more reasonable performance for individual flows, and reduce the processing time.
 
-The modification of others  constants or approaches may change the performance for any tool or API. They are:
-
-\begin{itemize}
-
-	\item \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have.
-This value  can change the precision of the generated traffic.
-Currently this value is $0.1$s.
-
-	\item \texttt{DataProcessor::m\_session\_cut\_time}: this member defines whatever a file transference still active or has ended.
-It defines the smallest OFF time acceptable.
-This value will change how many files SIMITAR will transfer per flow, and how many times it will call the underlying traffic generator.
-This constant may affect both computational performance and traffic realism.
-
-	\item \textit{Control a minimum number of packets required for SIMITAR create a new flow}: This would reduce the number of flows created, improving its computational performance.
-Since SIMITAR manages each flow in a  different thread, it will create fewer threads, reducing overheads.
-This action should not impact  on throughput and scaling characteristics because few packets would be ignored.
-But it can increase the precision of the most significant flows since all the threads are competing each other on the Operational System.
-But, the number of flows created would be smaller.
-
-\end{itemize}
-
-\subsubsection{Traffic generation performance}
+(5) One possibility to improove the traffic generation performance isuse DPDK KNI interfaces \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}.
+The The DPDK Kernel NIC Interface (KNI) allow applications from the user's space interact with DPDK ports.
+In this way, we may achieve a faster packet processing.
+This can be integrated as an instatiatable feature of SIMITAR (figure ~\ref{fig:dpdk-if}).
 
@@
 
-Some approaches may be taken to improve the traffic generation performance.
-One possibility is to use DPDK KNI interfaces \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}.
-The The DPDK Kernel NIC Interface (KNI) allow applications from the user's space interact with DPDK ports.
-In this way, we may achieve a faster packet processing.
+(6) Another issue is the sniffer component is taking to much time to extract data form large \textit{pcap} files.
+Implementing an C/C++ multi-thread sniffer, includding the packet processing and the SQL queries, will improove its performance.
 
-Another possibility is to use DPDK API craft packets.
-Using a low-level library such for packet generation, we will be able to custom generate packets and bypass the Linux network stack (packet acceleration).
-We present in the figure ~\ref{fig:DpdkFlow} how we could expand our tool to implement a packet generator based on DPDK.
+(7) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times.
+To avoid processing overheads on calculating random numbers, these values may be calculated before the actual traffic generation, and then be used.
+By this approach, the scaling characteristics of the traffic generated by libtins should improve, and be closer to the original traffic.
 
-\subsection{Further Implementations}
+(8-10) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}.
+D-ITG offers many stochastic functions for cusmtumization of inter-packet times, Ostinato offers a rich header and protocol custumization, and DPDK a high performance on packet generation.
+Each tools is able to affer a different result on traffic generation, each with benefits and drawbacks, such as cumputation cost, and complexity of development.
+DPDK offers the possibility to bypass the Linux network stack, called packet acceleration.
+So, this implementation could enable for SIMITAR high-bandwidht along wiht traffic realism.
 
-\begin{itemize}
+(11) Constant \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times.
+We use this value to avoid inter-packet times equals to zero due to the sniffer resolution.
+In that case, some of our procedures would diverge.
+It can change the fitting accuracy.
+Today, this value is $5e-8$.
 
-	\item \textbf{C++ Sniffer}: Implementing the Sniffer and its SQL queries in C++ should increase its performance.
+(12) \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have.
+This value  can change the precision of the generated traffic.
+Currently this value is $0.1$s.
 
-	%\item \textbf{Use OpenDayLight REST API for data collection}: Another different approach for data collection could be the use the OpenDayLight REST API to collect data from an SDN OpenFlow switches, instead of a using a Sniffer.
-Through REST API is possible to extract many statistics from nodes, hosts, and ports, such active flows, the number of packets matched per flows, packet drops, and so on.
-But, different features would be measured,  and a new model for traffic generation would be needed.
-On the other hand, we could reuse many procedures implemented.
+(13) Constant \texttt{DataProcessor::m\_session\_cut\_time}: this member defines whatever a file transference still active or has ended.
+It defines the smallest OFF time acceptable.
+This value will change how many files SIMITAR will transfer per flow, and how many times it will call the underlying traffic generator.
+This constant may affect both computational performance and traffic realism.
 
-	\item \textbf{SIMITAR Python API}: Currently, SIMITAR only enables the programming of flow traffic generation in C++.
-Adding Python support for reading NetwrokTrace and NetworkFlow objects, we can enable expansion for Python traffic generation APIs, without creating C++ "wrappers".
+(14) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: This would reduce the number of flows created, improving its computational performance.
+Since SIMITAR manages each flow in a  different thread, it will create fewer threads, reducing overheads.
+This action should not impact  on throughput and scaling characteristics because few packets would be ignored.
+But it can increase the precision of the most significant flows since all the threads are competing each other on the Operational System.
+But, the number of flows created would be smaller.
 
-	\item \textbf{Expand SIMITAR}: Expand the SIMITAR support for more traffic generator tools and APIs, such as MoonGen LUA API, Ostinato Python API, Seagull traffic generator, and many others.
+(15) Currently, SIMITAR only enables the programming of flow traffic generation in C++.
+Adding Python and Lua support for reading NetwrokTrace and NetworkFlow objects, we can enable expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ "wrappers".
+
+(16) \textbf{PcapGen: a compact \textit{pcap} lybrary}: Create a component capable of generate synthetic \textit{pcap} files, using Compact Trace Descriptors(CTDs) files.
+We can implement this using SIMITAR as a packet injector, but in an emulated host interface, for example, using Mininet.
+Then, the traffic can be collected, using a tool such as TCPDump or Tshark.
+We present a diagram of this idea in the figure ~\ref{fig:pcap-gen}.
+This expansion would enable SIMITAR  to work as trace library for pcap-based benchmark tools.
 
@@
 
-	\item \textbf{PcapGen: a compact \textit{pcap} lybrary}: Create a component capable of generate synthetic \textit{pcap} files, using Compact Trace Descriptors(CTDs) files.
-We can implement this using SIMITAR as a packet injector, but in an emulated host interface, for example, using Mininet.
-Then, the traffic can be collected, using a tool such as TCPDump or Tshark.
-We present a diagram of this idea in the figure ~\ref{fig:pcap-gen}.
-This expansion would enable SIMITAR  to work as trace library for pcap-based benchmark tools.
+%\item \textbf{Use OpenDayLight REST API for data collection}: Another different approach for data collection could be the use the OpenDayLight REST API to collect data from an SDN OpenFlow switches, instead of a using a Sniffer.
+Through REST API is possible to extract many statistics from nodes, hosts, and ports, such active flows, the number of packets matched per flows, packet drops, and so on.
+But, different features would be measured,  and a new model for traffic generation would be needed.
+On the other hand, we could reuse many procedures implemented.
 
-	% Oferecer a possibilidade de automatização de medições e testes extendendo a ferramenta
+%\subsection{Changing the Model, reusing the Architecture}
 
-	% usar redes neurais para classificação de aplicações
+%Since the proposed architecture is model-independent, another future work is to use the same general concepts of compact trace descriptor and API agnostic modeling on different models and compare the results.
 
-\end{itemize}
-
-\subsection{Changing the Model, reusing the Architecture}
-
-Since the proposed architecture is model-independent, another future work is to use the same general concepts of compact trace descriptor and API agnostic modeling on different models and compare the results.
-
-Our proposed future work is to implement this idea using the Swing\cite{swing-paper} and the Harpoon Model\cite{harpoon-paper}.
+%Our proposed future work is to implement this idea using the Swing\cite{swing-paper} and the Harpoon Model\cite{harpoon-paper}.
 We can create not just Simitar trace descriptors, but Swing and Harpoon trace descriptors as well.
@@
 
-These implementations can lead to a definitive and standardized model of realistic traffic generation.
+%These implementations can lead to a definitive and standardized model of realistic traffic generation.
 In this way, progresses on high-speed traffic generation would no more make old traffic generators and models obsolete.
@@
 
-Also, the idea of a Compact Trace Descriptor, by itself separates the idea of traffic generation and the modeling.
+%Also, the idea of a Compact Trace Descriptor, by itself separates the idea of traffic generation and the modeling.
 De development of new methodologies for modeling is  separated from the traffic generation.
@@
 
-TODO Limitations, future work
-
 TODO considerações, contrubuições, lições, boas idéias, mas idéias

### 2017-11-19 Docs/Thesis/docs/chapter4.tex
thesis update, ch5 and ch6

@@
 
-\begin{table}[ht!]
-	\centering
-	\caption{Stack of models used to create the CTD file}
-	\label{tab:mehtods}
-	\begin{tabular}{|l|l|l|}
-		\hline
-		Layer & Method & Variables \\
-		\hline
-		Link Layer  & \multirow{3}{*}{Packets header's data} & \texttt{link\_layer}, \texttt{link\_layer.mac\_src}, \texttt{link\_layer.mac\_dst} \\ \cline{1-1}\cline{3-3}
-
-		Network Layer & & \texttt{network\_layer}, \texttt{network\_layer.src\_ip}, \texttt{network\_layer.dst\_ip}, \texttt{network\_layer.ttl},\texttt{}\\ \cline{1-1}\cline{3-3}
-
-		Transport Layer & & \texttt{transport\_layer}, \texttt{transport\_layer.dst\_port}, \texttt{transport\_layer.src\_port}\\ \hline
-
-		Application Layer  & Application Match Table  & \texttt{application\_layer} \\ \hline
-
-		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$  & \texttt{inter\_packet\_times}\\ 
-		\cline{2-2}\cline{3-3}  & Algorithm: $stochasticModelFitting$                    &\\  \hline
-		Packet Sizes  & Algorithm: $stochasticModelFitting$ &\\ \hline
-	\end{tabular}
-\end{table}
+%\begin{table}[ht!]
+%	\centering
+%	\caption{Stack of models used to create the CTD file}
+%	\label{tab:mehtods}
+%	\begin{tabular}{|l|l|}
+%		\hline
+%		Layer & Method \\
+%		\hline
+%		Link Layer  & \multirow{3}{*}{Packets header's data} \\ \cline{1-1}\cline{3-3}
+%		
+%		Network Layer & \\ \cline{1-1}\cline{3-3}
+%		
+%		Transport Layer & \\ \hline
+%		
+%		Application Layer  & Application Match Table  \\ \hline
+%		
+%		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$  \\ 
+%
+%		%\cline{2-2}\cline{3-3}  
+%		& Algorithm: $stochasticModelFitting$ \\  \hline
+%
+%		Packet Sizes  & Algorithm: $stochasticModelFitting$ \\ \hline
+%
+%	\end{tabular}
+%\end{table}
 

### 2017-11-19 Docs/Thesis/docs/chapter5.tex
thesis update, ch5 and ch6

@@
 But Iperf has presented a better performance replicating scaling characteristics of applications.
+
+\section{Conclusions}
+
+SIMITAR was designed to work at flow-level and packet level.
+At the flow-level, our methodology can achieve great results.
+In fact,  The cumulative distribution of flows is almost identical on each case.
+From the perspective of benchmark of a middle-box such as an SND switch, this is a great result, since its performance depends on the number of registered flows.
+However, because of packets exchanged by signaling connection, the traffic generated by Iperf, even following the same cumulative flow distribution, had created more streams then expected.
+
+At packet level, the current results with Iperf replicate with high accuracy the scaling characteristics of the original traffic, and the number of generated packets are not far than the expected.
+However, the packet size replication and therefore the bandwidth is not accurate.
+Also, \textit{libtins} as traffic generator tool still is limited in this aspect.
+
+Once the current implementation of the Flow Generator still does not uses the whole set of parameters from the Compact Trace Descriptor, and many optimizations yet to be made, this is a satisfactory result that validates and proves the potential of our proposed methodology.
+Even we designing  SIMITAR  to prioritizing modularity over finner control, when we compare these current results with the more consolidated realistic traffic generator available, they are closer.
+At the flow-lever our results are at least as good as the achieved by Harpoon\cite{harpoon-paper} and Swing\cite{swing-paper}.
+At the scaling characteristics, on lightweight traces, they are already comparable in quality.

### 2017-11-19 Docs/Thesis/docs/chapter6.tex
thesis update, ch5 and ch6

@@
 
-In this section we discuss some ideas for future works and implementation for SIMITAR.
+In this section, we discuss some ideas for future works and implementation for SIMITAR.
 We suggest approaches to get better results.
-They include perfromance improovments, calibration of some constants and finer controll of packet injection.
-We list them as a task list in the talbe
+They include performance improvements, calibration of constants\footnote{Calibration here means to test many values, and see which one can improve our outcomes for a large variety of traces of traces.} and a finer control of packet injection.
+We list them as a task list on the table ~\ref{tab:task-list}.
 
@@
 		\hline
-		\multicolumn{3}{c}{{\color[HTML]{000000} Future Work}}                                                                               & Priority                \\ \hline
+		\multicolumn{3}{c}{Future Work}	& Priority \\ \hline
 		1                      & Optimizing linear regression                              &                                                 & \textit{high}                    \\
@@
 		15 & Python API/Lua for traffic generation & & low \\
-		16 & Crafter of  pcap files & & low \\
+		16 & Crafter of  pcap files & \multirow{-2}{*}{New features} & low \\
 		%17 & Json compact trace descriptor  & \multirow{-3}{*}{New features} & low 
@@
 The performance becomes an issue when processing large \textit{pcap} files with more dozens of thousands of flows.
-The processing in this case may take some hours.
-In the current implementation, the linear regression is mono-thread, and the stop criteria are just the number of iterations.
-Parallel processing, and creating stop criteria based on convergence, alongside with the number of iterations, should increase the processing performance.
+The time expended for processing traces, in this case, is exceeding tens of hours.
+In the current implementation, the linear regression execution is mono-thread, and the stop criterion is just the number of iterations.
+Parallel processing, and creating stop criteria based on convergence in addition to the number of iterations will improve the performance.
 
-(2) Crating an option for merging flows is a possibility to imprrove performance of traffic with several thousands of flows and Gigabits of bandwidth, such as from WAN captures.
-A merge criterion for example is considere just network headers to classify the flows.
+(2) Crating an option for merging flows is a possibility to improve the performance of traffic with several thousands of flows and Gigabits of bandwidth, such as from WAN captures.
+A merge criterion, for example, is to consider just network headers on flow's classification.
 
-(3) On the traffic generation, currently, the threads for all flows are being instantiated once the traffic generations start.
-A smarter traffic generation, where each thread is instantiated when the traffic is active and dies when it is inactive should reduce the overhead for \textit{pcap} files with a large number of flows.
-For traffic with a massive amount of flows, a methodology for merging them should reduce overheads and enable replication of traffic with a much larger bandwidth.
+(3) Currently, all the flow threads are instantiated once the traffic generations start.
+A smarter traffic generation where SIMITAR instantiates each thread when the traffic, and join when it is inactive should reduce the overhead for traces with a large number of flows.
+For traffics with a massive amount of streams, a methodology for merging them should reduce computational costs and enable replication of traffic with a much more significant bandwidth.
 
-(4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of flow packets is larger than this value.
-If it is smaller, we use only the constant model, for two reasons.
-First, because with a small sample, the accuracy estimate stochastic model is poor.
-Second, because we avoid the parameterization process, which is cost in the case of linear regression.
-Its value today is set to 30.
-Increasing this value, we may achieve a more reasonable performance for individual flows, and reduce the processing time.
+(4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount.
+If it is smaller, SIMITAR just uses the constant model.
+We decide to do it for two reasons.
+First, because with a small sample, the modeling accuracy is poor .
+Second, we avoid the cost of the parameterization process.
+Now, its value is set to Its value today is set to 30.
+Increasing this amount, we may achieve a more reasonable performance for individual flows, and reduce the processing time.
 
-(5) One possibility to improove the traffic generation performance isuse DPDK KNI interfaces \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}.
-The The DPDK Kernel NIC Interface (KNI) allow applications from the user's space interact with DPDK ports.
+(5) One possibility to improve the traffic generation performance issue DPDK Kernel NIC Interface  (KNI interfaces) \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}.
+DPDK KNI interfaces allow applications from the user's space interact with DPDK ports.
 In this way, we may achieve a faster packet processing.
-This can be integrated as an instatiatable feature of SIMITAR (figure ~\ref{fig:dpdk-if}).
+This can be integrated as an insatiable feature of SIMITAR (figure ~\ref{fig:dpdk-if}).
 
@@
 
-(6) Another issue is the sniffer component is taking to much time to extract data form large \textit{pcap} files.
-Implementing an C/C++ multi-thread sniffer, includding the packet processing and the SQL queries, will improove its performance.
+(6) Another issue is the sniffer component is taking to much time to extract data from large \textit{pcap} files.
+Implementing a C/C++ multi-thread sniffer, including the packet processing and the SQL queries, will improve its performance.
 
 (7) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times.
-To avoid processing overheads on calculating random numbers, these values may be calculated before the actual traffic generation, and then be used.
-By this approach, the scaling characteristics of the traffic generated by libtins should improve, and be closer to the original traffic.
+To avoid overheads on random numbers calculation,  these values must be calculated before the actual traffic generation.
+Modelling inter-packet times the scaling characteristics of libtins traffic should improve.
 
 (8-10) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}.
-D-ITG offers many stochastic functions for cusmtumization of inter-packet times, Ostinato offers a rich header and protocol custumization, and DPDK a high performance on packet generation.
-Each tools is able to affer a different result on traffic generation, each with benefits and drawbacks, such as cumputation cost, and complexity of development.
-DPDK offers the possibility to bypass the Linux network stack, called packet acceleration.
-So, this implementation could enable for SIMITAR high-bandwidht along wiht traffic realism.
+D-ITG offers many stochastic functions for customization of inter-packet times, Ostinato provides a rich set of headers and protocols, and DPDK a high performance on packet generation.
+Each tool can offer a different result on traffic generation, each with benefits and drawbacks, such as computational cost, and development complexity.
+Also, DPDK provides the possibility to bypass the Linux network stack, called packet acceleration.
+So, this implementation can enable for SIMITAR high-bandwidth along with traffic realism.
 
-(11) Constant \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times.
+(11) Calibrate  the constant  \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times.
 We use this value to avoid inter-packet times equals to zero due to the sniffer resolution.
-In that case, some of our procedures would diverge.
-It can change the fitting accuracy.
+A zero-inter-packet time would make the procedure fail.
+This value can change the fitting accuracy.
 Today, this value is $5e-8$.
 
-(12) \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have.
-This value  can change the precision of the generated traffic.
+(12) Calibrate  the constant \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have.
+It can change the generated traffic precision.
 Currently this value is $0.1$s.
 
-(13) Constant \texttt{DataProcessor::m\_session\_cut\_time}: this member defines whatever a file transference still active or has ended.
+(13) Calibrate  the constant \texttt{DataProcessor::m\_session\_cut\_time}: this value defines whatever a file transference still active or has ended.
 It defines the smallest OFF time acceptable.
 This value will change how many files SIMITAR will transfer per flow, and how many times it will call the underlying traffic generator.
-This constant may affect both computational performance and traffic realism.
+This constant affects the computational performance and traffic realism.
 
-(14) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: This would reduce the number of flows created, improving its computational performance.
-Since SIMITAR manages each flow in a  different thread, it will create fewer threads, reducing overheads.
+(14) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: this would reduce the number of flows created, improving its computational performance.
+Since SIMITAR manages each flow in a different thread, it will create fewer threads simultaneously, reducing overheads.
 This action should not impact on throughput and scaling characteristics because few packets would be ignored.
-But it can increase the precision of the most significant flows since all the threads are competing each other on the Operational System.
+But it can increase the precision of the most significant flows since all the threads are competing for each other on the Operational System.
 But, the number of flows created would be smaller.
@@
 (15) Currently, SIMITAR only enables the programming of flow traffic generation in C++.
-Adding Python and Lua support for reading NetwrokTrace and NetworkFlow objects, we can enable expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ "wrappers".
+Adding Python and Lua support for the Flow Generator component, we can enable expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ wrappers.
 
@@
 
-TODO considerações, contrubuições, lições, boas idéias, mas idéias
+In this dissertation we discuss our process of conceiving, researching, definition and development and validation of an realistic traffic generator able to at the same time fulfill gaps others proposals haven't, and achieve results comparable to the available proposals.
+This was not a linear procedure.
+Was indeed anespiral procedure, as proposed by Sommervile on Software Engineering\cite{sommerville}.
+At the figure~\ref{fig:spiral} we show how it was done.
 
-\textcolor{red}{some text here}
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[scale=0.4]{figures/ch6/spiral}
+	\caption{Spiral research and development procedure}
+	\label{fig:spiral}
+\end{figure}
+
+Starting with some concepts, we search in the literatue the state of things, related works and some gaps for inovation.
+We proposed a traffic generator, and validated a simplistic prototype \footnote{In the appendix ~\ref{ap:publications}, the  article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios" where this prototype is validated is presented.} \footnote{This initial step was crucial, since on later stages, changes on the architecture design are much more dificult.
+In fact, some ponctual changes such as directory structure and new classes are inevitable.
+But structural changes are impracticable.}.
+After this we serch for more sollutions and methodologies that could be applied to solve or problem.
+In this procedure we researched many topics that at end didnt fit to our intentions, such as Machine Learning and Neural Networks.
+But others such as Linear regression, maximum likelihood, and BIC and AIC were indeed sactisfatory.
+Again, we planned a methodology, a procedure, and validate these ideais, as prototypes.
+Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection.
+Is it worth?"(at appendix ~\ref{ap:publications}.
+Than we reseach for more related works to  gain insights and find platforms and lybraries able to fulfill our requirements.
+In this step we designed our algorithms presented on chapter ~\ref{ch:modeling-evaluation}, and choosed the APIs, packages and lybraries.
+This procedure continued by incremental upgrades, until we arrived on the version presented on the chapter ~\ref{ch:validation}.
+
+- revisitar as contribuições e os resultados alcançados, e comparar com a literatura
+
+- paragrafo de encerramento

### 2017-11-21 Docs/Thesis/docs/chapter6.tex
update on ch6

@@
 
-In this section, we discuss some ideas for future works and implementation for SIMITAR.
-We suggest approaches to get better results.
-They include performance improvements, calibration of constants\footnote{Calibration here means to test many values, and see which one can improve our outcomes for a large variety of traces of traces.} and a finer control of packet injection.
-We list them as a task list on the table ~\ref{tab:task-list}.
+With the work done so far and the results achieved, we may identify the current limitation of our project, and plan improvements to solve these issues. 
+We can list as  main weak points right now:
+
+\begin{itemize}
+	\item Poor performance of the Trace Analyzer and Sniffer components;
+	\item Weak scaling results of the traffic generator using \textit{libtins}.
+\end{itemize}
+
+And as further implementations, but with low priority, we may have:
+
+\begin{itemize}
+	\item Support for new traffic generator tools;
+	\item APIs for the Flow Generator on  Python and Lua, wich have cosolidate traffic generator APIs;
+	\item A \textit{pcap-crafter} component. Instead of creating traffic, creates a \textit{pcap} file.
+\end{itemize}
+
+Identified these issues and possible future works, we conceived approaches and methods to achieve these results.
+They include improvements on the implementation,  calibration of constants\footnote{Calibration here means to test many values, and see which one can improve our outcomes for a large variety of traces of traces.}, a finner control of packet injection, use of new technologies and newer implementations.
+As we always did in the project, we create a task list of activities and organize them by priority and goal.
+They are listed in the table ~\ref{tab:task-list}.
 
@@
 		4                      & \texttt{DataProcessor::minimumAmountOfPackets}                         &                                                 & low                     \\
-		5                      & DPDK KNI interfaces                                       &                                                 & low                     \\
+		5                      & DPDK KNI interfaces                                       &                                                 & medium                     \\
 		6                      & Multi-thread C++ sniffer                                  & \multirow{-6}{*}{Performance}                   & \textit{high}                    \\ \hline
@@
 This was not a linear procedure.
-Was indeed anespiral procedure, as proposed by Sommervile on Software Engineering\cite{sommerville}.
-At the figure~\ref{fig:spiral} we show how it was done.
+Was indeed an espiral procedure, as proposed by Sommervile on Software Engineering\cite{sommerville}.
+Clealy its not identical, because we adapt it for research purposes.
+At the figure~\ref{fig:spiral} we show a diagram of who  it was done.
 
@@
 
-Starting with some concepts, we search in the literatue the state of things, related works and some gaps for inovation.
-We proposed a traffic generator, and validated a simplistic prototype \footnote{In the appendix ~\ref{ap:publications}, the  article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios" where this prototype is validated is presented.} \footnote{This initial step was crucial, since on later stages, changes on the architecture design are much more dificult.
+Starting with some concepts and ideias, we started definin our goals, and to do so, a task list.
+The concepts and the task lists were organized on "Working Plan" documents.
+These tasks lists covered the whole process, and included reserch, study of new subjects, implementation and testing.
+Next, search in the literatue the state of things, related works and some gaps for inovation.
+At this point we defined the concepts of our traffic generator according to gaps the state of things we find in the literature.
+Then we create an architecture model using UML, defining the software components, classes and sequence diagrams.
+This initial step was crucial, since on later stages, changes on the architecture design are much more dificult.
 In fact, some ponctual changes such as directory structure and new classes are inevitable.
-But structural changes are impracticable.}.
-After this we serch for more sollutions and methodologies that could be applied to solve or problem.
-In this procedure we researched many topics that at end didnt fit to our intentions, such as Machine Learning and Neural Networks.
-But others such as Linear regression, maximum likelihood, and BIC and AIC were indeed sactisfatory.
+But structural changes are impracticable.
+At this point we implemented a simplistic prototype, and validate it\footnote{In the appendix ~\ref{ap:publications}, this prototype is validated in the article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios"}.
+
+After this we serch for more sollutions and methodologies that could be applied to solve or problems and improove the performance of ou prototype.
+In this procedure we researched many topics that at end didn't fit to our intentions, such as Machine Learning and Neural Networks.
+But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed sactisfatory.
 Again, we planned a methodology, a procedure, and validate these ideais, as prototypes.
@@
 Than we reseach for more related works to  gain insights and find platforms and lybraries able to fulfill our requirements.
-In this step we designed our algorithms presented on chapter ~\ref{ch:modeling-evaluation}, and choosed the APIs, packages and lybraries.
+In this step we designed our algorithms presented on chapter ~\ref{ch:modeling-evaluation}, and choosed the APIs, packages and lybraries, such as Armadillo\cite{armadillo}, a C++ linear algebra lybrary.
+Many ideas we used to conceive our ideas were inspired on previous works and sollutions, such as Harpoon\cite{harpoon-validation}, sourcesOnoff \cite{sourcesonoff-paper} and LegoTG\cite{legotg-paper}.
 This procedure continued by incremental upgrades, until we arrived on the version presented on the chapter ~\ref{ch:validation}.
 
-- revisitar as contribuições e os resultados alcançados, e comparar com a literatura
+In the chapter ~\ref{ch:modeling-evaluation} we achieve a major contribution of our work, that is show that the information criterias AIC and BIC are efficient analyctial methodos for select models for inter-packet times.
+Both are able infer a good model, even evaluated according different types of metrics, without any type of simulation.
+Also we show evidence that for Ethernet traffic of data, choosing AIC and BIC make almost no difference.
+As far as is our knowleadge, this is the most complete study on the use of AIC and BIC on inter-packet times modelling of Ethernet traffic.
 
-- paragrafo de encerramento
+At the end, we were able to implement a functional implementation of solution proposed in the chapter ~\ref{ch:introduction}.
+Our main contrubution here is the development of a traffc generator tool that at the same time is able to provide realistic synthetic traffic, and its modelling framework is extensible for most of the traffic generation lybraries and tools.
+In fact, our current implementations use tow very distinct packet-crafters: \textit{libtins}, a C++ library designed for the implementation of sniffers and traffic generators, and Iperf, a traffic generator commonly used to measure bandwidth.
+
+Out tests performed on the chapter ~\ref{ch:validation} intend to focous on packet-level, flow-level and scalling metrics, as we state on chapter ~\ref{ch:ch:literature-review}.
+The results were notably good at the flow level.
+SIMITAR were able to replicate the flow-cumulative distribution with high acurracy, and with \textit{libtins}, the number of flows as well.
+The number of flows were larger, because it establishes aditional connections for signaling and statistics control.
+On scalling and packet matrics, the results still have to be improved.
+Iperf as the traffic generator tool, still being limited, has prooved to be efficient on replication the scalling characteristics for the Skype traffic.
+Since it estrablishes socket connections to generate the traffic, we believe that this fact make it and acurate on replication traffic from applications.
+
+Finally, we created a list of improovments and future works, aiming the improovment of perfomance on processing time, and packet generaration; and the methods to improove the realism of the traffic generated.
+In the is we believe to overcome the current limitations.

### 2017-11-21 Docs/Thesis/docs/chapter6.tex
update on ch6

@@
 
-Starting with some concepts and ideias, we started definin our goals, and to do so, a task list.
-The concepts and the task lists were organized on "Working Plan" documents.
-These tasks lists covered the whole process, and included reserch, study of new subjects, implementation and testing.
-Next, search in the literatue the state of things, related works and some gaps for inovation.
-At this point we defined the concepts of our traffic generator according to gaps the state of things we find in the literature.
-Then we create an architecture model using UML, defining the software components, classes and sequence diagrams.
-This initial step was crucial, since on later stages, changes on the architecture design are much more dificult.
-In fact, some ponctual changes such as directory structure and new classes are inevitable.
+We started defining our goals creating a task list, formalizing it on "Working Plan" documents.
+These tasks lists covered the whole process and included research, the study of new subjects, implementation, and testing.
+Next, search on the literature the state of things, related works and points for innovation.
+At this point, we defined the concepts of our traffic generator.
+We create an architecture model using UML, defining the software components, classes and sequence diagrams.
+This initial step was crucial since, in later stages, changes in the architecture design are much more difficult.
+In fact, some small changes such as directory structure and new classes are inevitable.
 But structural changes are impracticable.
@@
 
-After this we serch for more sollutions and methodologies that could be applied to solve or problems and improove the performance of ou prototype.
-In this procedure we researched many topics that at end didn't fit to our intentions, such as Machine Learning and Neural Networks.
-But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed sactisfatory.
-Again, we planned a methodology, a procedure, and validate these ideais, as prototypes.
+After this, we search for more solutions and methodologies that could be applied to solve our problems and improve the performance of our prototype.
+In this procedure, we researched many topics that at the end didn't fit our intentions, such as Machine Learning and Neural Networks.
+But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed satisfactory.
+Again, we planned a methodology, procedure, and validate these ideas, as prototypes.
 Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection.
-Is it worth?"(at appendix ~\ref{ap:publications}.
-Than we reseach for more related works to  gain insights and find platforms and lybraries able to fulfill our requirements.
-In this step we designed our algorithms presented on chapter ~\ref{ch:modeling-evaluation}, and choosed the APIs, packages and lybraries, such as Armadillo\cite{armadillo}, a C++ linear algebra lybrary.
-Many ideas we used to conceive our ideas were inspired on previous works and sollutions, such as Harpoon\cite{harpoon-validation}, sourcesOnoff \cite{sourcesonoff-paper} and LegoTG\cite{legotg-paper}.
-This procedure continued by incremental upgrades, until we arrived on the version presented on the chapter ~\ref{ch:validation}.
+Is it worth?" (in the appendix ~\ref{ap:publications}).
+Then we research for more related works to gain insights and find platforms and libraries able to fulfill our requirements.
+In this step, we designed our algorithms presented in chapter ~\ref{ch:modeling-evaluation}, and chose the APIs, packages, and libraries, such as Armadillo\cite{armadillo}, a C++ linear algebra library.
+Many ideas we used to conceive our ideas were inspired by previous works and solutions, such as Harpoon\cite{harpoon-validation}, sourcesOnoff \cite{sourcesonoff-paper} and LegoTG\cite{legotg-paper}.
+This procedure continued with incremental upgrades until we arrived on the version presented on the chapter ~\ref{ch:validation}.
 
-In the chapter ~\ref{ch:modeling-evaluation} we achieve a major contribution of our work, that is show that the information criterias AIC and BIC are efficient analyctial methodos for select models for inter-packet times.
-Both are able infer a good model, even evaluated according different types of metrics, without any type of simulation.
-Also we show evidence that for Ethernet traffic of data, choosing AIC and BIC make almost no difference.
-As far as is our knowleadge, this is the most complete study on the use of AIC and BIC on inter-packet times modelling of Ethernet traffic.
+In the chapter ~\ref{ch:modeling-evaluation} we achieve a significant contribution of our work, which shows that the information criteria AIC and BIC are efficient analytical methods for select models for inter-packet times.
+Both can infer a good model, even evaluated according to different types of metrics, without any simulation.
+Also, we show evidence that for Ethernet traffic of data, choosing AIC and BIC make almost no difference.
+As far as is our knowledge, this is a complete study on the use of AIC and BIC on inter-packet times modeling of Ethernet traffic.
 
-At the end, we were able to implement a functional implementation of solution proposed in the chapter ~\ref{ch:introduction}.
-Our main contrubution here is the development of a traffc generator tool that at the same time is able to provide realistic synthetic traffic, and its modelling framework is extensible for most of the traffic generation lybraries and tools.
+In the end, we were able to implement a functional implementation of the solution proposed in the chapter ~\ref{ch:introduction}.
+Our main contribution here is the development of a traffic generator tool that at the same time can provide realistic synthetic traffic, and its modeling framework is extensible for most of the traffic generation libraries and tools.
 In fact, our current implementations use tow very distinct packet-crafters: \textit{libtins}, a C++ library designed for the implementation of sniffers and traffic generators, and Iperf, a traffic generator commonly used to measure bandwidth.
 
-Out tests performed on the chapter ~\ref{ch:validation} intend to focous on packet-level, flow-level and scalling metrics, as we state on chapter ~\ref{ch:ch:literature-review}.
-The results were notably good at the flow level.
-SIMITAR were able to replicate the flow-cumulative distribution with high acurracy, and with \textit{libtins}, the number of flows as well.
-The number of flows were larger, because it establishes aditional connections for signaling and statistics control.
-On scalling and packet matrics, the results still have to be improved.
-Iperf as the traffic generator tool, still being limited, has prooved to be efficient on replication the scalling characteristics for the Skype traffic.
-Since it estrablishes socket connections to generate the traffic, we believe that this fact make it and acurate on replication traffic from applications.
+Out tests performed on the chapter ~\ref{ch:validation} intend to focus on packet-level, flow-level and scaling metrics, as we state on chapter ~\ref{ch:literature-review}.
+The results were notably good at the flow-level.
+SIMITAR were able to replicate the flow-cumulative distribution with high accuracy, and with \textit{libtins}, the number of flows as well.
+The number of flows was larger because it establishes additional connections for signaling and statistics control.
+On scaling and packet matrics, the results still have to be improved.
+Iperf as the traffic generator tool, still being limited, has proved to be efficient on replication the scaling characteristics for the Skype traffic.
+Since it establishes socket connections to generate the traffic, we believe that this fact makes it accurate on replication traffic from applications.
 
-Finally, we created a list of improovments and future works, aiming the improovment of perfomance on processing time, and packet generaration; and the methods to improove the realism of the traffic generated.
+Finally, we created a list of improvements and future works, aiming the improvement of performance on processing time, and packet generation; and the methods to improve the realism of the traffic generated.
 In the is we believe to overcome the current limitations.

### 2017-11-22 Docs/PaperAicBic/body.tex
new directories for the papers, new updates on the thesis

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:introduction}

It is already a well-known fact that the type of traffic used on performing tests matters. Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption. It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of a new technology. There are many reasons for this behavior, which includes burstiness and packet sizes. A burstier traffic can cause packet more buffer overflows on network\cite{burstiness-queue-lenght}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}. Also, a burstier and realistic traffic will not just impact on performance, but on measurement as well, since a realistic and burstier traffic impacts on bandwidth measurement accuracy\cite{legotg-paper}\cite{background-traffic-matter}. Knowing that, many traffic generator tools\cite{ditg-paper} provide a set of pre-defined stochastic models to control the emission packets, controlling packet-trains and inter-pacekt times.

There are many works devoted on studing the nature of the Ethernet traffic~\cite{selfsimilar-ethernet}\cite{analysis-self-similar}\cite{stochartic-selfsimilar}\cite{selfsimilar-highvariability}\cite{multi-player-online-game-self-similarity}. Classic Ethernet models use Poisson related processes, wich represents the probability of events occur in many independent sources with a known average rate, and independently of the last occurrence~\cite{selfsimilar-ethernet}~\cite{book-poisson}. However studies made by Leland et al.~\cite{selfsimilar-ethernet} showed that the Ethernet traffic has a self-similar and fractal nature. Even if they can represent the randomness of an Ethernet traffic, simple Poisson processes can't express traffic "burstiness" in a long-term time scale, such as traffic "spikes" on long-range ripples. These characteristics are an indication of the fractal and self-similar nature of the traffic that usually we express by distributions with infinite variance, called heavy-tailed. Heavy-tail means its distribution is not exponentially bounded\cite{sourcesonoff-paper}, such as Weibull, Pareto and Cauchy distribution.  Heavy-tailed processes may guarantee self-similarity, but not necessarily will ensure other important features like high correlation between data and same mean packet rate\cite{validate-trafficgen}.

Therefore, there are many investigations on how to model stochastic functions for different scenarios~\cite{estimation-renewal-function-ethernet-traffic}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}\cite{modeling-concurrent-heavy-tailed}\cite{optimal-scheduling-of-heavy-tailed-traffic}\cite{modelling-of-self-similar}. However, there are some limitations on this idea of finding a single ideal model. Usually, not the same stochastic distribution will present a proper fitting for all possible kinds of traces~\cite{sourcesonoff-paper}. Depending on some variables, such as the capture time, the number of packets or type of traffic, different functions may fit better the available data. On most works the best model representation for an Ethernet traffic is not chosen analytically but based on the researcher own data analyses and purposes~\cite{hierarchical-dynamics-interarrival-times}\cite{modeling-concurrent-heavy-tailed}\cite{optimal-scheduling-of-heavy-tailed-traffic}. Also, some methods like linear regression may diverge sometimes. Furthermore, it has already been proven that a single model cannot represent arbitrary traffic traces~\cite{sourcesonoff-paper}.

In this work we propose and evaluate the use of information criteria BIC (Bayesian information criterion) and AIC (Akaike information criterion) as tool for an automatic selection best fitting for inter-packet times of a traffic trace. It is an analytical and deterministic method which spares and avoid human analyzes, is easy to be implemented by software, and don't relies on simulations and generation of random data. We fit a set of stochastic models through different methods and applying BIC and AIC to choose the best.

First, we explain the mathematical meaning of BIC and AIC and state the methods we are going to use to create a set of candidate models for our dataset. Then we define our cross-validation method based on a cost function $J$, attributing weights from the best to the worst representation for each properties using randomly generated data with our stochastic fittings, we can choose the best possible traffic model among these fittings. This cost function depends on important stochastic properties for traffic modelling. Thus we compare the results achieved by AIC/BIC and our cost function. In that way we show that thay are a worth method for inteligent selection of inter-packet times stochastic models, being able to gess models with smaller $J$ values. We also found that for traffic inter-packet times, that the difference between BIC and AIC values is minimal. Thus, selecting  one over the other does not seem a key question.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Literature Review}\label{sec:review}

\subsection{Modelling Ethernet Traffic}

There are plenty of works on the literature which proposes new processes and methodologies for modeling times between packets and packet trains. Fiorini \cite{modeling-concurrent-heavy-tailed} presents a heavy-tailed ON/OFF model, which tries to represent a traffic generated by many sources. The model emulates a multiple source power-tail Markov-Modulated (PT-MMPP) ON/OFF process, where the ON times are power-tail distributed. They achieve analytical performance measurements using Linear Algebra Queueing Theory.

Kreban and Clearwater\cite{hierarchical-dynamics-interarrival-times} presents a model for times between job submissions of multiple users over a super computer. They show that the Weibull probability functions are able to express well small and high values of inter-job submission times. They also tested exponential, lognormal and Pareto distributions. Exponential distribution couldn't  represent long-range values because it fell off too fast and Pareto was too slow. Lognormal fit well small values, but was poor on larger ones. Kronewitter\cite{optimal-scheduling-of-heavy-tailed-traffic} presents a model of scheduling traffic of many heavy-tail sources. On his work, he uses many Pareto sources to represent the traffic. To estimate the shape parameter $\alpha$ they use linear regression.

\subsection{AIC and BIC}

Suppose that we have an statistical model $M$ of some dataset ${\boldsymbol{x} = \{x_1, ..., x_n}\}$, with $n$ independent and identically distributed observations of a random variable $X$. This model can be expressed by a probability density function (PDF) $f(x| \boldsymbol{\theta})$, where $\boldsymbol{\theta}$ is a vector of parameter of the PDF, $\boldsymbol{\theta} \in \mathbb{R}^{k}$ ($k$ is the number of parameters). The  likelihood function  of this model $M$ is given by:
\begin{equation}
L(\boldsymbol{\theta}|\boldsymbol{x} ) =  f(x_1|\boldsymbol{\theta})\cdot...\cdot f(x_n|\boldsymbol{\theta}) = \prod_{i = 1}^{n}f(x_i|\boldsymbol{\theta})
\end{equation}
Now, suppose we are trying to estimate the best statistical model, from a set ${M_1, ..., M_n}$, each one with an estimated vector of parameters  ${\boldsymbol{\hat{\theta_1}}}, ..., {\boldsymbol{\hat{\theta_n}}}$. $AIC$ and $BIC$ are defined by:
\begin{equation}
AIC = 2k - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
\end{equation}
\begin{equation}
BIC = k\ln(n) - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
\end{equation}
In both cases, the preferred model $M_i$, is the one with the smaller value of $AIC_i$ or $BIC_i$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}

We start defining the \textit{pcaps} datasets we are going to use in the rest of this text. We will use for datasets, and for reproduction purposes, three are public available. 
The first is a lightweight Skype packet capture, found in  Wireshark wiki\footnote{ Available at \url{https://wiki.wireshark.org/SampleCaptures}, named  \textit{SkypeIRC.cap}}, we call it \textit{skype-pcap}. The second is a CAIDA\footnote{ \url{http://www.caida.org/home/} } capture, wich we analyze its first second capture\footnote{Available at \url{https://data.caida.org/datasets/passive-2016/equinix-chicago/20160121-130000.UTC}, named as \textit{equinix-chicago.dirB.20160121-135641.UTC.anon.pcap.gz}  }, and we refer to it as \textit{wan-pcap}. The third we capture in our laboratory LAN, through a period of 24 hours. It was captured firewall gateway between our local and external network. Along with other tests, We intend to verify diurnal behavior on it. That means a high demand of packets during the day and a small in the night. We call it \textit{lan-diurnal-pcap}. Finally, the last is a capture of a busy private network access point to the Internet, available on-line on TCPreplay website \footnote{Available at \url{http://tcpreplay.appneta.com/wiki/captures.html}, named \texttt{bigFlows.pcap}}, we will refer to it \textit{bigflows-pcap}.

Further we collect inter-packet times from the traffic traces. Then, we estimate a set of parameters for stochastic processes, using a set of different methodologies such as linear-regression, maximum likelihood, and direct estimation of parameters. We are modelling:

\begin{itemize}
\item Weibull, exponential, Pareto and Cauchy distributions, using linear regression, through the Gradient descendent algorithm. We refer to these exponential and Pareto approximations as Exponential(LR) and Pareto(LR);
\item Normal and exponential distribution, using direct estimation the mean and the standard deviation of the dataset for the normal, and the mean for the exponential. We refer for to this exponential approximation as Exponential(Me);
\item Pareto distribution, using the maximum likelihood method. We refer to this distribution as Pareto(MLH);
\end{itemize}

Then, from these parametrized models, we estimate which one best represent our dataset, using AIC  and BIC criteria. These results were obtained using Octave language\footnote{ \url{https://www.gnu.org/software/octave/}}, and the scripts are available at \cite{projeto-github} for reproduction purposes. Thus, to see if our criterion of parameter selection can find which is the best model according to traffic modeling standards on realism and benchmarking\cite{validate-trafficgen}, we define a validation methodology. We randomly generated a dataset using our parameterized stochastic processes.  Moreover, we compare it with the original and synthetic sample, trough three different metrics, all with a confidence interval of 95\%:

\begin{itemize}
\item Correlation between the sample data and the estimated model (Pearson's product-moment coefficient);
\item Difference between the original and the synthetic Hurst exponent;
\item Difference between the original and the synthetic mean inter-packet time;
\end{itemize}

The Pearson's product-moment coefficient, or simply correlation coefficient,  is an expression of the dependence or association between two datasets. Its value goes from -1 to +1. +1 means a perfect direct linear correlation. -1 indicates perfect inverse linear correlation. 0 means no linear correlation. So, as close the result reach 1, more similar are the inter-packet times to the original values. To estimate it, we use the Octave's function \texttt{corr()}.

The Hurst exponent is meter self-similarity and indicates the fractal level of the inter-packet times. As close the result is from the original, more similar is the fractal level of the estimated samples from the original. To estimate this value we use the function \texttt{hurst()} from Octave, which uses rescaled range method. Finally, the mean is also relevant, since it will meters if the packet per second rate of the trace and its approximation model are close related.

To quantitatively check   if AIC and BIC are good criteria for model selection for inter-packet times, we define a cost function based on the correlation, Hurst exponent and mean. We defined a cost function $J$, based on the randomly generated data values with our estimated stochastic process. Being $Cr$ the vector of correlations ordered from the greater to the smaller. Let $Me$ and $Hr$ defined by the absolute difference between mean and hurt exponent of the estimated values and the original dataset. Both are ordered from the smaller to the greatest values. Letting $\phi(V, M)$ be an operator who gives the position of a model $M$ in a vector $V$, we define the cost function $J$ as:

\begin{equation}
J(M) = \phi(Cr, M) + \phi(Me, M) + \phi(Hr, M)
\end{equation}

The smaller is the cost $J$, the best is the model. Then we compare the results achieved by AIC and BIC, and $J$.

%\begin{table*}[t]
%\centering
%\caption{Results of our modeling and simulation methodology for the traffic trace \textit{skype-pcap}. The stochastic processes are ordered form the worst to the best fitting, according to AIC and BIC.}
%\label{tab:skype-results}
%\begin{tabular}{lcccc}
%\hline
%Function        & AIC         & BIC        & \multicolumn{2}{c}{Parameters}      \\ \hline
%Weibull         & $-2293.8$   & $-2283.8$ & $\alpha:0.522$ & $\beta:0.097$  \\
%Exponential (Me) & $-426.13$   & $-421.1$  & \multicolumn{2}{c}{$\lambda:3.319$}  \\
%Exponential (LR) & $96.9$   & $101.8$  & \multicolumn{2}{c}{$\lambda:1.505$}         \\
%Pareto (MLH)     & $361.9$   & $371.8$  & $\alpha:0.0747$ & $x_m:5e-8$       \\
%Normal          & $2423.8$    & $2433.8$   & $\mu:0.301 $   & $\sigma:0.749$ \\
%Pareto (LR)      & $6411.0$   & $6421.1$  & $\alpha:0.413$ & $x_m:5e-8$       \\
%Cauchy          & $13464.6$    & $13474.5$   & $\gamma:0.000275$ & $x_0:0.219$    \\ \hline
%\end{tabular}
%\end{table*}

\begin{figure}[ht!]
{\centering
\includegraphics[width=\columnwidth]{figures/Weibull}
\caption{Cumulative distribution function(CDF) for Weibull fitting and empirical data for inter-packet times of \textit{skype-pcap}}
\label{fig:skype-weibull}\par}
\end{figure}

\begin{table*}[ht!]
	\centering
	\caption{Results of the octave prototype, include BIC and AIC values, para estimated parameters for two of our pcap traces: \textit{skype-pcap }and \textit{bigflows-pcap}. \textit{bigflows-pcap} is much larger, and has a much much smaller mean inter-packet time}
    \scalebox{0.95}{ 
		\begin{tabular}{lcccccccccc}
			\hline
			& \multicolumn{10}{c}{Trace} \\ \cline{2-11} 
			Function		& Order & AIC  & BIC  & \multicolumn{2}{c}{Parameters}  
			& Order & AIC & BIC  & \multicolumn{2}{c}{Parameters} \\ \hline

			& \multicolumn{5}{c}{skype-pcap}  & \multicolumn{5}{c}{lan-diurnal-pcap}   \\ \hline 
			Cauchy          &	7 & $1.35e4$    & $2.19e4$    & $\gamma:2.59e-4$ & $x_0:1.05e-1$    
			&	5 & $-2.85e7$   & $-2.85e7$   & $\gamma:9.63e-3$ & $x_0:-3.61e-3$    \\
			Exponential(LR) &	3 & $9.69e1$   & $1.02e2$   & \multicolumn{2}{c}{$\lambda:1.86$}   
			&	6 & $1.79e6$    & $1.79e6$    & \multicolumn{2}{c}{$\lambda:8.51e-1$}    \\
			Exponential(Me) &	2 & $-4.26e2$   & $-4.28e3$   & \multicolumn{2}{c}{$\lambda:7.01$}   
			&	4 & $-3.12e7$   & $-3.12e7$   & \multicolumn{2}{c}{$ \lambda:58.78$} \\
			Normal          &	5 & $2.42e3$    & $3.31e3$    & $\mu:1.43e-1 $    & $\sigma:5.01e-1$ 
			&	7 & $Inf$       & $Inf$       & $\mu:1.70e-2$     & $\sigma:8.56e-2$ \\
			Pareto(LR)      &	6 & $6.4e3$   & $-8.27e3$   & $\alpha:2.52e-1$ & $x_m:5e-8$    
			&	3 & $-4.60e7$   & $-4.60e7$   & $\alpha:2.55e-1$ & $ x_m:5e-8$    \\
			Pareto(MLH)     &	4 & $3.62e2$   & $3.72e2$   & $\alpha:9.21e-2$ & $x_m:5e-8$    
			&	2 & $-5.03e7$   & $-5.03e7$   & $\alpha:1.15e-1$ & $ x_m:5e-8$    \\
			Weibull         &	1 & $-2.29e3$   & $-2.28e3$  & $\alpha:3.20e-1$ & $\beta:1.52e-2$  
			&	1 & $-5.60e7$   & $-5.60e7$   & $\alpha:3.34e-1$ & $\beta:1.83e-3$  \\ \hline	
			& \multicolumn{5}{c}{bigFlows-pcap} & \multicolumn{5}{c}{wan-pcap}  \\ \hline
			Cauchy          &	6 & $7.14e6$    & $7.14e6$   & $\gamma:1.94e0$ &$x_0:-7.25$    
			&	7 & $5.99e7$    & $5.99e7$   & $ \gamma:8.28e2$ &$x_0:-4.52e3$    \\
			Exponential(LR) &	7 & $7.33e6$    & $7.33e6$   & \multicolumn{2}{c}{$\lambda:1.489e-1$}   
			&	6 & $5.68e7$    & $ 5.68e7$  & \multicolumn{2}{c}{$\lambda:2.2e-5$}   \\
			Exponential(Me) &	2 & $-1.09e7$   & $-1.09e7$  & \multicolumn{2}{c}{$\lambda:2.64e3$}   
			&	1 & $-6.58e7$   & $-6.58e7$  & \multicolumn{2}{c}{$\lambda:6.58e5$} \\
			Normal          &	5 & $-9.35e6$   & $-9.35e6$  & $\mu:3.79e-4$   &$\sigma:6.60e-4$ 
			&	2 & $-6.39e7$   & $-6.39e7$  & $\mu:2e-6$     & $\sigma:1e-6$ \\
			Pareto(LR)      &	4 & $-1.02e7$   & $-1.02e7$  & $\alpha:1.489e-1 $ & $x_m:5e-8 $    
			&	4 & $-5.31e7$   & $-5.31e7$  & $\alpha:NaN$ & $x_m:5e-8 $    \\
			Pareto(MLH)     &	3 & $-1.03e7$   & $-1.03e7$  & $\alpha:1.362e-1$ & $x_m:5e-8 $    
			&	5 & $-6.25e7$   & $-6.25e7$  & $\alpha:3.39e-1$ & $x_m:5e-8 $    \\
			Weibull         &	1 & $-1.10e7$   & $-1.10e7$  & $\alpha:2.81e-1$ & $\beta:5.54e-4$  
			&	3 & $-5.46e7$   & $-5.46e7$  & $\alpha:7.64e-2$ & $\beta:1e-6$  \\ \hline
		\end{tabular}
        }
	\label{tab:prototype-results}
\end{table*}

\begin{figure}[ht!]
{\centering
\includegraphics[width=\columnwidth]{figures/Skype_Hurst_Exponent}
\caption{Hurst exponent calculation of inter-packet times for \textit{skype-pcap} and its approximations}
\label{fig:skype-hurst}\par}
\end{figure}

\begin{figure}[ht!]
{\centering
\includegraphics[width=\columnwidth]{figures/Skype_Correlation}
\caption{Correlation between \textit{skype-pcap} inter-packet times and its approximations.}
\label{fig:skype-correlation}\par}
\end{figure}

\begin{figure}[ht!]
{\centering
\includegraphics[width=\columnwidth]{figures/Skype_Mean}
\caption{Mean inter-packet times for \textit{skype-pcap} and its approximations.}
\label{fig:skype-mean}\par}
\end{figure}

\begin{figure*}[ht!]
	\centering
	\subfloat[\textit{skype-pcap}]{
		\includegraphics[width=75mm]{figures/Skype_costFunction}
		\label{cost-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[\textit{bigFlows-pcap}]{
		\includegraphics[width=75mm]{figures/bigFlows_costFunction}
		\label{cost-bigFlows-pcap}
	}
	\hspace{0mm}
	\subfloat[\textit{lan-diurnal-pcap}]{
		\includegraphics[width=75mm]{figures/Lan_costFunction}
		\label{cost-lan-pcap}
	}
	\hspace{0mm}
	\subfloat[\textit{wan-pcap}]{
		\includegraphics[width=75mm]{figures/Wan_costFunction}
		\label{cost-wan-pcap}
	}
	\caption{Cost function for each one of the datasets used in this validation process}
	\label{fig:cost-function}
\end{figure*}

\begin{figure}[ht!]
{\centering
\includegraphics[width=\columnwidth]{figures/pcap-comparision}
\caption{Comparision of the model selection order for BIC/AIC and the cost function for each pcap.}
\label{fig:model-order}\par}
\end{figure}

%Analyzing the plots, and what they would mean, our Cauchy fitting would impose an almost contant traffic , with the inter packet time close to the mean. On the trace \textit{skype-pcap} the exponential plots seems to not represent well the small values of inter packet times. This is due fact that an exponential process is good at representing values close to the mean. But, it fails to represent values too small and higher. On the other hand, a self-similar process like Weibull and Pareto are better representing inter packet times with higher dispersion. Pareto(MLH) has a slow convergence, wich means this distribution may genarate values of inter-packet times too large.

%Analyzing the QQplots, we may observe that in most of the distribution, the samples (original data) has a much havier-tail effect than in the estimated data. This is verified by the almost blue horizontal lines formed by the "exes". But, the Weibull distribution follow much closer the original data. Also is possible to see that the sample has a right skew compared to the estimation on Exponential(LR), Exponential(Me), Normal, and Pareto(MLH). This means that this estimation would not represent so well small values of time in this case. On the other hand, Pareto(LR) and Weibull would not suffer from this problem.

%The results for the AIC, BIC and parameters of all four traces are at the table~\ref{tab:prototype-results}.  The results for \textit{wan-pcap} and \textit{lan-diurnal-pcap} are on the table ~\ref{tab:prototype-results}. The difference between BIC and AIC values in all simulations are very small. Much smaller then the difference of these values between the distributions. This is an indication that for inter packet times, using AIC or BIC should will not influence significantly the results.

%On our previsions, Weibull and Pareto(MLH and LR) are the best options. This was expected, since both are heavy-tailed functions. But Cauchy on most of the tests, even being a heavy-tailed distribution, seems to no present a good fitting. This is effect of the fast divergence of tangent function, when we linearize our data.

%Analyzing the quality of AIC and BIC as criterion of choose on \textit{skype-pcap},based on the results form figure ~\ref{fig:correlation-hurst-skype-pcap} we see that in therms of Correlation and Self-similarity it picket the right model: Weibull. Also in therms of mean packet rate and dispersion it is still one of the best choises (along with Exponential(Me), Pareto(LR) and Cauchy). The third and the fourth choices (Pareto(LR)) and Exponential(LR) also are good options in most of these metrics. But, Pareto(MLH) is presented as the second best choice, and it had poor results in comparison to the others, especially on mean, correlation and dispersion.

%All these results are abstracted by the cost function $J$. As we can see, on all pcaps, the best function selected by BIC and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.

%Another important observation is the fact that exponential function was able to provide the best fitting for the \textit{wan-pcap}. The reasons for this behavior are both result of a much intense traffic with no long-range gaps, and the precision of the measurement.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

%Here in this chapter we only discuss the plots achived obtained by the pcap \textit{skype-pcap} for simplicity. The other plots are provided and commented on the appendix ~\ref{ap:aditional-plots}. In the figure ~\ref{fig:aproximation-original-cdf} we present all estimated CDF functions along with the empirical CDF, for the trace \textit{skype-pcap}. They are on logscale, wich provide a better visualization for small time scales. In the case of the normal function, all values smaller than zero, were set to zero on the plot. Is possible to see different accuracies and types of fittings on each plot. Visually, the best fit seems to be the Weibull trough linear regression.

In table~\ref{tab:prototype-results} we summarize our estimations for AIC, BIC, and the stochastic process estimated parameters for all \textit{pcap} traces. We iserted and aditional column to facilitate the observation of the quality of fitting according BIC and AIC. For visualization, in the figure ~\ref{fig:skype-weibull} we present the best fitting chosen by BIC and AIC criteria for the \textit{skype-pcap}. It is on log-scale, which provides a better visualization for small time values. Visually we can see that linear regression with Weibull distribution was able to provide a good approximation for this dataset.

First, let's take a look on table ~\ref{tab:prototype-results}. On \textit{skype-pcap} and \textit{bigFlows-pcap}, \textit{lan-diurnal-pcap}, the fitting pointed as the best was Weibull, except on the \textit{wan-pcap}, where Exponential(Me) was selected. This can be explained by the fact that this one had the largest bandwidth from all three pcaps, having smaller inter-packet times with a smaller range, and closer to the mean. The difference between BIC and AIC values in all simulations is much smaller than the difference between each distribution (for most of the cases are not larger than 1\%). This result indicates that for inter-packet times, using AIC or BIC to pick a model, do not influence the results significantly.

For \textit{skype-pcap}, according to BIC and AIC previsions, Weibull and Exponential (Me and LR) are the best options, and the cost functions gave exact this same order~\ref{fig:cost-function}. In fact, Weibull pointed as the best stochastic function by BIC and AIC, has half of the penalty imposed by the cost function $J$. The following models however are not in the same order since some results are flipped. But still, no opposite correspondence can be found. No result found by AIC and BIC were far from the one pointed by $J$.

Furthermore, for \textit{wan-pcap} and \textit{lan-diurnal-pcap}, the function pointed by AIC/BIC was the same as pointed by $J$: Exponential(Me) and Weibull respectivally. On \textit{big-Flows-pcap} the first two gesses values are flipped, however we can notice that the difference between the AIC/BIC values were of just 7\%, wich indicate a closer level of quality. A more complete chart of the selection order between both metricas are on the figure ~\ref{fig:model-order}, relative to the $J$ selection order. The linear patern represent the ideal results. In some cases, like the 2nd and 6th

%\begin{figure}[h]
%{\centering
%\includegraphics[width=\columnwidth]{figures/Correlation}
%\caption{Comparison between correlation of the used set of fittings, with a confidence of 95\%}
%\label{fig:skype-correlation}\par}
%\end{figure}

%\begin{figure}[t]
%{\centering
%\includegraphics[width=\columnwidth]{figures/HurstExponent}
%\caption{Comparison between the Hurst exponent of our approximated processes and the original data  with a confidence of 95\%}
%\label{fig:skype-hurst}\par}
%\end{figure}

%\begin{figure}[t]
%{\centering
%\includegraphics[width=\columnwidth]{figures/Mean}
%\caption{cap}
%\label{fig:skype-mean}\par}
%\end{figure}

%The difference between BIC and AIC values in all simulations are very small. Much smaller then the difference of these values between the distributions. This is an indication that for inter packet times, using AIC or BIC to pick a model, will not influence significantly the results.

%According to BIC and AIC previsions, Weibull and Pareto(MLH and LR) are the best options. This was expected, since both are heavy-tailed functions. But Cauchy on most of the tests, even being a heavy-tailed distribution, seems to do no present a good fitting. This is effect of the fast divergence of tangent function, when we linearize our data.

%From the figures ~\ref{fig:skype-correlation} and ~\ref{fig:fig:skype-hurst} we see that in therms of Correlation and Self-similarity it picket clearly the most related model: Weibull. Also in therms of mean packet rate it is still a good choice (along with Exponential(Me), Pareto(LR) and Cauchy). The third and the fourth choices (Pareto(LR)) and Exponential(Me) also are good options in most of these metrics. But, Pareto(MLH) is presented as the second best choice, and it had poor results in comparison to the others, especially on mean and correlation. This is the only model presented as good

%All these results are abstracted by the cost function $J$. As we can see, on all pcaps, the best function selected by BIC and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.

%Another important observation is the fact that exponential function was able to provide the best fitting for the \textit{wan-pcap}. The reasons for this behavior are both result of a much intense traffic with no long-range gaps, and the precision of the measurement.

\section{Conclusion}

In this work, we analyze how BIC and AIC perform being used as analytical selection criteria form stochastic models for Ethernet inter-packet times. Using a cross-validation methodology based on the generation of random data using these models, and pointing a cost function. We saw that both AIC or BIC and the cost function were able to pick the first models in the same order. Therefore, analytically with BIC and AIC, we were able to achieve the same results as pointed by our simulations. Even if AIC and BIC mathematical definitions are unaware of the specific requirements of Ethernet traffic modeling, such as same fractal-level and close packet per second rate, they still can point the best choices according to these constraints.

In this work, we analyze just inter-packet times of a single trace. However at \cite{projeto-github} we perform the same methodology on different types of traffic captures, finding similar results. Therefore, we can conclude that BIC and AIC are healthy alternatives for model selection of Ethernet inter-packet times models and we can safely use them. Finally, we must point some advantages of BIC and AIC instead of simulations. Since it is an analytical model, no generation of random data is necessary,  being computationally cheaper and easy to code. Also, since we do not use a single stochastic function and parameterization strategy, it is resilient to the fact that some methods like linear-regression over Weibull may diverge sometimes. If it happens, BIC or AIC will discard this guesses, and choose another oneautomatically.

Last but not least, to the best of our knowledge, this is the most comprehensive investigation of the actual quality of BIC and AIC as model selection criteria of for inter-packet times.
%Also, except by the Pareto function modeled using the Maximum likelihood method, have comparative results between the simulations and the AIC/BIC goes. The best fittings according to the AIC/BIC usually returned very accurate models, with a small error between the mean and fractal level, and correlation close to one. The models selected as the worsts usually returned poor results.

%Also, it is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurate fitting, what justify the application of the criteria in all new experiments. For example, Weibull usually performs pretty well, but in some cases, perform poorly, and in others may even diverge.

%We do not rely on only one type of parameterization. This turns our methodology more robust, since a linear regression may diverge. But always there will be a peaceable model, since our estimations for Normal, Exponential (Me) and Pareto (MLH) cannot. Models which the linear regression diverges, will have very high and positive BIC/AIC estimations, and will not stand as primary options.

### 2017-11-22 Docs/PaperAicBic/instructions.tex
new directories for the papers, new updates on the thesis

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig1}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\cite{nfv-challenges}                                                                
\cite{sdn-survey}                                                  
\cite{instrumentation-framework-nfv}                                                   
\cite{nfv-benchmarking-fault}

### 2017-11-22 Docs/PaperSimitar/header.tex
new directories for the papers, new updates on the thesis

%\title{Paper Title*\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
%}
\title{Using BIC and AIC for Ethernet traffic model selection. Is it worth?}

\author{\IEEEauthorblockN{1\textsuperscript{st} Anderson dos Santos Paschoalon}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{State University of Campinas}\\
Campinas, Brazil \\
anderson.paschoalon@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Christian Esteve Rothenberg }
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{State University of Campinas}\\
Campinas, Brazil  \\
chesteve@dca.fee.unicamp.br}
}

\maketitle

\begin{abstract}
In this work, we aim to evaluate how good are the information criteria AIC and BIC inferring which is the best stochastic process to describe Ethernet inter-packet times. Also, we check if there is a practical difference between using AIC or BIC. We use a set of stochastic distributions to represent inter-packet of a traffic trace and calculate AIC and BIC. To test the quality of  BIC and AIC guesses,  we define a cost function based on the comparison of significant stochastic properties for internet traffic modeling, such as correlation, fractal-level and mean. Then, we compare both results.  In this short paper, we present just the results of a public free Skype-application packet capture, but we provide as reference further analyzes on different traffic traces. We conclude that for most cases AIC and BIC can guess right the best fitting according to the standards of Ethernet traffic modeling.
\end{abstract}

\begin{IEEEkeywords}
BIC, AIC, stochastic function, inter-packet times, correlation, Hurst exponent, heavy-tailed distribution, fractal-level, burstiness, linear-regression, weibull, pareto, exponential, normal, poison, maximum likelihood, Ethernet traffic, traffic modeling, fractal-level, pcap file, Skype traffic.
\end{IEEEkeywords}

### 2017-11-22 Docs/Thesis/docs/chapter1.tex
new directories for the papers, new updates on the thesis

@@
 
-A burstier traffic can cause packet more buffer overflows on network\cite{burstiness-queue-lenght}\cite{modelling-of-self-similar}\cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}.
-Also, a burstier and realistic traffic will not just impact on performance, but on measurement as well, since a realistic and burstier traffic impacts on bandwidth measurement accuracy\cite{legotg-paper}\cite{background-traffic-matter}.
+A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}.
+Also, a burstier and realistic traffic will not just impact on performance, but on measurement accuracy as well \cite{legotg-paper} \cite{background-traffic-matter}.
 Another key question is how applications will deal with packets.
 It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}.
-A synthetic realistic traffic must not have a single packet-size, but must use a distribution\cite{packet-distribution-model}.
+A synthetic realistic traffic must not have a single packet-size, but must use a distribution \cite{packet-distribution-model}.
 
-Also, realistic workload generators are essential security research\cite{ditg-paper}.
+Realistic workload generators are also essential security research\cite{ditg-paper}.
 Generation of realistic workloads is important in the evaluation of firewall middleboxes.
 It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.
+
 Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible, we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.
-Also, on SDN networks, each new flow arriving on a switch demands an extra communication load between it and the controller, unpacting necativelly as well.
-We also have a flow-oriented operation on SDN switches. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual ISP scenario.
+
+Another important point is the flow-oriented operation of SDN networks.
+Each new flow arriving on a SDN switch demands an extra communication load between it and the controller.
+This may create a bootleneck between the switch and the controller.
+We also have a flow-oriented operation on SDN switches.
+Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual ISP scenario.
 
@@
 
-%3nd-review
 \section{Open-source Solutions}
@@
 
-Now, we are going to formalize these exposed concepts in a proposal of research and development. Or main targets here are:
+Now, we are going to formalize these exposed conceptual gaps in the literature, in a proposal of research and development. Or main targets here are:
 

### 2017-11-22 Docs/Thesis/docs/macros.tex
new directories for the papers, new updates on the thesis

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Author}{
Anderson dos Santos Paschoalon
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Year}{
	Anderson dos Santos Paschoalon
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ThesisTitle}{
SIMITAR: A Tool for Generation of Synthetic and Realistic Network Workload for Benchmarking and Testing
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\TituloDaTese}{
SIMITAR: Uma Ferramente para Geração de Trafego de Rede Sintético e Realistico para Benchmarking e Testes
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\AtaDeDefesa}{
\textbf{COMISSÃO JULGADORA - DISSERTAÇÃO DE MESTRADO}
\vspace{1cm}
\begin{flushleft}
\textbf{Candidato}: Anderson dos Santos Paschoalon \hspace{1cm}     RA: 083233 \\
\textbf{Data da Defesa}: \\
\textbf{Título da Tese}: \\
``SIMITAR: A Tool for Generation of Synthetic and Realistic Network Workload for Benchmarking and Testing''\\%english\\
``SIMITAR: Uma Ferramente para Geração de Trafego de Rede Sintético e Realistico para Benchmarking e Testes''%portuguese
\end{flushleft}
\vspace{0.2cm}
\begin{flushleft}Prof. Dr. Christian Rodolfo Esteve Rothenberg (Presidente, FEEC/UNICAMP)\\
Prof. Dr. Edmundo Roberto Mauro Madeira (IC/UNICAMP) - Membro Titular\\
Prof. Dr. Marcos Antonio de Siqueira (PADTEC) - Membro Titular
\end{flushleft}
\vspace{0.2cm} 
\begin{flushleft}Ata de defesa, com as respectivas assinaturas dos membros da Comissão Julgadora, encontra-se no processo de vida acadêmica do aluno. \end{flushleft}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Abstract}{

Application-Layer Traffic Optimization (ALTO) is a recently standardized protocol that provides abstract network topology and cost maps in addition to endpoint information services that can be consumed by applications in order to become network-aware and to take optimized decisions regarding traffic flows. 
In this work, we propose a public service based on the ALTO specification using public routing information available at the Brazilian Internet eXchange Points (IXPs).
Our ALTO server prototype takes the acronym AaaS (ALTO-as-a-Service) and is based on over 2.5GB of real BGP data from the 25 Brazilian IX.br public IXPs.
We evaluate our proposal in terms of functional behaviour and performance via proof-of-concept experiments, which point to the potential benefits of applications being able to take smart endpoint selection decisions when consuming the developer-friendly ALTO APIs.

\vspace{\onelineskip}

\noindent\textbf{Keywords}: Routing (Computer network management); IXPs (Internet exchange points); Computer networks; SDN (software defined networking).
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Resumo}{
Otimização de Tráfego na Camada de Aplicação (ALTO - \textit{Application-Layer Traffic Optimization}) é um protocolo recentemente padronizado que fornece uma topologia da rede e mapa de custos abstratos, além de serviços de informação de endpoints que podem ser consumidos pelos aplicativos, a fim de tornar-se conscientes da rede e tomar decisões otimizadas sobre os  
Neste trabalho, propomos um serviço público baseado nas especificações ALTO usando informação de roteamento pública disponível nos Pontos de Troca de Tráfego (PTTs) brasileiros.
Nosso protótipo de servidor ALTO, representado pela sigla AaaS (ALTO-as-a-Service), é baseado em mais de 2,5 GB de dados BGP reais dos 25 PTTs públicos brasileiros (IX.br).
Nossa proposta é avaliada em termos de comportamento funcional e desempenho através de experimentos de prova de conceito que apontam como potencial benefício das aplicações, a capacidade de tomar decisões inteligentes na seleção de endpoint ao consumir as APIs ALTO.
\vspace{\onelineskip}
\noindent\textbf{Palavras-chaves}: Roteamento (Administração de redes de computadores); Engenharia de tráfego; Redes de computadores; Bancos de dados.

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Acknowledgements}{
First of all, I would like to thank my advisor Prof. Dr. Christian Rothenberg for the trust and for letting me be part of his selected group of students. I would not be able to imagine the undertaking of this research without his innovative ideas, consistent support and continuous encouragement. I would therefore like to express my gratitude for being a great instructor and an even greater friend.

At the State University of Campinas (Unicamp) I have had the opportunity to learn from the best professors. I would like to acknowledge Prof. Dr. Mauricio Magalhães, Prof. Dr. Edson Borin, Prof. Dr. Edmundo Madeira and Prof. Dr. Léo Pini for sharing their knowledge and experience, which served as a constant motivation throughout this work.

I would like to thank the committee members Marcos Antonio de Siqueira, Edmundo Roberto Mauro Madeira and Christian Rothenberg for the recommendations and insightful criticism they offered me in order to improve the final version of my thesis.

I had the good fortune to meet very talented people within the INTRIG and LCA groups. My special thanks go to Mateus, Samuel, Samira, Gyanesh, Alex, Luis, Raphael, Anderson, Hirley, Ramon, Alaelson, Claudio, Talita, Javier, Elias, Rodrigo, Roberto, Mariana, Ranyeri, Aldo, Wallace, Vitor, Raphael V. and Amadeu, Mariana and Lino for their friendship and their support throughout these two years.

I would like to express special gratitude for the financial and technical support received from the Ericsson Innovation Center (Brazil), which allowed me to carry out this research.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Agradecimentos}{
	exemplo	
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Epigrafe}{
\textit{``Discipline, sooner or later, will defeat intelligence.''\\
``A disciplina cedo ou tarde vencerá a inteligência.''\\
``La disciplina tarde o temprano vencerá a la inteligencia.''}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\EpigrafeAuthor}{
Japanese proverb
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Dedicatoria}{

Nesssa dedicatoria, gostaria de agradescer a todos que me ajudarem por essa etapa, direta ou indiretamente. Des daqueles que me inspiraram e me motivaram a seguir por esse caminho, aqueles que me ensinaram e me ajudaram durante o processo, e a aqueles cuja simples companhia me deram energia e me motivaram para estar aqui onde estou hoje. A todos, seja os que estão listado abaixo, como aqueles cuja minha memória não me ajudou na escrita desse texto.

Gostaria de agradecer ao meu professor e orientador Christian Esteves Rothemberg, sem o qual, seja pelo ensino, seja pela orientação e apoio durante o projeto, este trabalho não teria saído do papel.

Agradeço também a todos os Intrigers, colegas de grupo e de bancada, Alex, Javier, Nathan, Daniel, Danny, Gyanesh, Rafael, Fabricio e todos os demais. Agradeço a todos os demais colegas de laboratorio do LCA, em especial a Mijail, Suelen, Amadeu, Paul, ....

Agradeço a todos os companheiros e amigos que fiz em todos esses anos de Unicamp

Agradeço a todos os grandes amigos e companheiros da Opus Dei, em especial Padre Fabiano. E também todos meus caros amigos da Igreja Batista Fonte.

Agradeço aos meus companheiros passados e atuais da casa P7: Lucas Zorzetti(Xildo),

Agradeço a minha família, a meu Pai Tirso José Paschoalon por todo sua preocupação e ensino.  A minha Mãe Rosangela dos Santos Mota, por todo o seu carinho e amor. E a minha irmã Ariela Paschoalon, pela companhia e afeto.

E por ultimo agradeço a Deus por todos seu dons, proteção aamor

}

### 2017-11-22 Docs/Thesis/docs/chapter1.tex
updates

@@
 Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption.
-It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of a new technology.
+It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of new technologies.
 There are many reasons for this behavior, which includes burstiness and packet sizes.
@@
 It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}.
-A synthetic realistic traffic must not have a single packet-size, but must use a distribution \cite{packet-distribution-model}.
+A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.
 
@@
 
-Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible, we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.
+Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.
 
-Another important point is the flow-oriented operation of SDN networks.
-Each new flow arriving on a SDN switch demands an extra communication load between it and the controller.
-This may create a bootleneck between the switch and the controller.
+Another critical point is the flow-oriented operation of SDN networks.
+Each new flow arriving on an SDN switch demands an extra communication load between it and the controller.
+This may create a bottleneck between the switch and the controller.
 We also have a flow-oriented operation on SDN switches.

### 2017-11-22 Docs/Thesis/docs/appendix/appendixE.tex
IMPORTANT: vou fazer algumas alterações, e tudo pode parar de funfar kkk -> preciso passar a interface ethernet como argumento para cada thread
thesis update, ch5 and ch6
update on the thesis text

@@
 \chapter{Publications}
+\label{ap:publications}
 
-\section{IX DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA)}
+\begin{itemize}
+	\item IX DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA
+	\item X DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA)
+	\item Using BIC and AIC for Ethernet traffic model selection. Is it worth?
+	\item SIMITAR: realistic and autoconfigurable traffic generation
+\end{itemize}
+
 \includepdf[pages=-]{figures/apE/eadca-article2016.pdf}
 
-\section{X DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA)}
 \includepdf[pages=-]{figures/apE/eadca-article2017.pdf}
 
-\section{Generic Paper}
-\includepdf[pages=-]{figures/apE/paper.pdf}
+\includepdf[pages=-]{figures/apE/paperAicBic.pdf}
+
+\includepdf[pages=-]{figures/apE/paperSimitar.pdf}
+
+%\section{Generic Paper 3}
+%\includepdf[pages=-]{figures/apE/paper3.pdf}

### 2017-11-22 Docs/Thesis/docs/appendix/todo.tex
update on the thesis text

@@
 Liks úteis: 
-
->> http://www.backtrack-linux.org/forums/showthread.php?t=8740
-
->> https://sudks.wordpress.com/2016/04/27/tools-traffic-networking/
-
->> http://www.linuxlinks.com/article/2012042806090428/BenchmarkTools.html
-
->> http://uperf.org/
+http://www.backtrack-linux.org/forums/showthread.php?t=8740
+https://sudks.wordpress.com/2016/04/27/tools-traffic-networking/
+http://www.linuxlinks.com/article/2012042806090428/BenchmarkTools.html
+http://uperf.org/
 
@@
 \end{enumerate}
-
-\section{Chapter 3 - Architecture}
-
-\section{Chapter 4 - Modeling}
-
-\section{Chapter 5 - Prof of concepts}
-
-\section{Chapter 6 - Usage cases}
-
-\section{Chapter 7 - Conclusion}

### 2017-11-22 Docs/Thesis/docs/chapter3.tex
update on the thesis text

@@
 If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time.
-In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds) \textcolor{red}{<<<<pode mudar, calibrar>>>>}.
+In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds).
 The control of ON/OFF periods is made by the \texttt{NetworkFlow} class.

### 2017-11-24 Docs/Thesis/docs/chapter1.tex
up

@@
 
-A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}.
-Also, a burstier and realistic traffic will not just impact on performance, but on measurement accuracy as well \cite{legotg-paper} \cite{background-traffic-matter}.
+A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}, and  measurement accuracy\cite{legotg-paper} \cite{background-traffic-matter}.
 Another key question is how applications will deal with packets.
@@
 This may create a bottleneck between the switch and the controller.
-We also have a flow-oriented operation on SDN switches.
-Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual ISP scenario.
+Also the SDN switches have a flow-oriented operation.
+Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider.
 
@@
 The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}.
-Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation.
+Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.
 
 Some traffic generator tools offer support emulation of single application workloads.
-But this does not correspond to real complex scenarios, with a large number of distributed hosts in an Internet Service Provider (ISP) or even a Local Area Network (LAN).
-
+But this does not correspond to real complex scenarios.
 Other tools work as packet replay engines, such as TCPreplay and TCPivo.
@@
 Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources.
-
 Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato.
 Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen.
-They can give a good control of the traffic and high rates.
-The most relevant examples of features are controlled by these tools are:
 
-\begin{itemize}
+We have available have a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others.
+These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators.
+For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK.
+Also, many traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.
 
-\item Throughput, the number of bytes, number of packets.
-
-\item Protocols. Most of the tools give support to network and transport protocols. Many also offer support to Link and Application protocols;
-
-\item Header and payload configuration.
+%They can give a good control of the traffic and high rates. Es example of controllable features we can list:
+%\begin{itemize}
+%\item Throughput, the number of bytes, number of packets.
+%\item Protocols. Most of the tools give support to network and transport protocols. Many also offer support to Link and Application protocols;
+%\item Header and payload configuration.
 Support for header customization includes source and destination port/addresses, QoS parameters, flags, etc.
 Some traffic generators also allow customizing payload bytes.
+%\item Inter-packet times. Some tools offer a set of stochastic distributions to control inter-packet times. The user can use these stochastic functions to emulate realistic inter-arrival times.
+%\item On/off periods: support of packet trains periods. Many offer stochastic models to control it. 
+%\item Sending time and start-time: the user can use these features to control flows timings.  
+%\item Packet-size: support for different packet sizes. Some tools offer constant values or stochastic distributions to control packet sizes.
+%\item Paralell flows configuration.
+%\item Emulation of specific applications: common examples are 
+%\end{itemize}
 
-\item Inter-packet times. Some tools offer a set of stochastic distributions to control inter-packet times. The user can use these stochastic functions to emulate realistic inter-arrival times.
-
-\item On/off periods: support of packet trains periods. Many offer stochastic models to control it.
-
-\item Sending time and start-time: the user can use these features to control flows timings.
-
-\item Packet-size: support for different packet sizes. Some tools offer constant values or stochastic distributions to control packet sizes.
-
-\item Paralell flows configuration.
-
-\item Emulation of specific applications: common examples are Web server/client communication, VoIP, HTTP, FTP, p2p applications, and so on.
-
-\end{itemize}
-
-Since there is so many features and tools, selecting a good configuration is by itself a research project.
+If the user whats to reproduce an realistic traffic scenatio, since there is so many features and tools, selecting a good configuration is by itself a complex research project.
 How to use each parameter to simulate a specific scenario is a hard question \cite{legotg-paper}\cite{selfsimilar-ethernet}.
 It is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic patterns and experimental evaluation.
+Also, having a good compromisse between quality of realism, progamming time and scalability another challange.
+Since this is a complex process, a simplistic and less time-expensive sollution is choosen over a a realistic and acuratter but comple and time-costly sollution.
 
+Some sollutions exists on the open-source comunity.
 Some tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration.
@@
 Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration.
-Swing\cite{swing-paper} aims to generate realistic background traffic, but do not reach high throughputs \cite{swing-paper} \cite{legotg-paper}.
+Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}.
 Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library.
 The only way of replacing the traffic engine is changing and recompiling the original code.
-And this is a hard task.
+And this is a hard task\cite{legotg-paper}.
 
-Since synthetic traffic traces generation is mature in academia, the creation of custom network workloads through the configuration of high-throughput open-source is an affordable task.
+%Since synthetic traffic traces generation is mature in academia, the creation of custom network workloads through the configuration of  open-source tools is an affordable task.
 But it is not often available in an automatic way, and most of the times is a challenging question\cite{legotg-paper}, and still, requires expert knowledge.
@@
 
-Also, just choosing which workload generator tool may fit better for the user needs is not a simple question.
+% Also, just choosing which workload generator tool may fit better for the user needs is not a simple question.
 Tools like D-ITG\footnote{\href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}} provide support to many different stochastic functions, Ostinato\footnote{\href{http://ostinato.org/}{http://ostinato.org/}} provides a larger support for protocols, and a higher throughput for each thread\cite{comparative-trafficgen-tools}, and others like Seagull\footnote{\href{http://gull.sourceforge.net/doc/WP_Seagull_Open_Source_tool_for_IMS_testing.pdf}{http://gull.sourceforge.net/doc/WP\_Seagull\_Open\_Source\_tool\_for\_IMS\_testing.pdf}} are responsive.
@@
 
-Our goal is to offer an easier configuration, realism than the available platforms today, at a reasonable speed.
+Our goal is to offer an easier configuration, with a reasoble degree of realism than the available platforms today, at a reasonable speed.
 To do this, we are introducing the concept of programmability for  traffic generation.

### 2017-11-25 Docs/Thesis/docs/chapter1.tex
thesis update

@@
 Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources.
+
 Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato.
 Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen.
+But all of them just offer a complet framework to be congfigured, but the customization of the traffic is all up to user to do.
+So, there is no simple way for the user to create an synthetic realistic traffic scenario.
 
-We have available have a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others.
+We also have available a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others.
 These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators.
 For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK.
-Also, many traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.
+Also, many of the listed traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.
 
@@
 
-If the user whats to reproduce an realistic traffic scenatio, since there is so many features and tools, selecting a good configuration is by itself a complex research project.
-How to use each parameter to simulate a specific scenario is a hard question \cite{legotg-paper}\cite{selfsimilar-ethernet}.
-It is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic patterns and experimental evaluation.
-Also, having a good compromisse between quality of realism, progamming time and scalability another challange.
-Since this is a complex process, a simplistic and less time-expensive sollution is choosen over a a realistic and acuratter but comple and time-costly sollution.
+Therefore we have a large variety open-source tools available for custom traffic generation.
+But reproducing a realistic traffic scenario is a hard question.
+Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}.
+But usually this is not the goal of the project, so the researcher or the them have scarce time available to work over it.
+Since it is usually is not the main goal of the project, but just a mean many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.
+Reproducig a realistic traffic usung these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation.
+Since it usually is not the goal of the research, but a mean.
 
-Some sollutions exists on the open-source comunity.
-Some tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration.
+For this gap, there are some sollutions on the open source community.
+Tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration.
 Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}.
@@
 The only way of replacing the traffic engine is changing and recompiling the original code.
-And this is a hard task\cite{legotg-paper}.
+This is clearly a hard task\cite{legotg-paper}, and an error prone activity.
+Again, we fall in the same problem a complex task that usually is not the goal of the project.
+
+Another issue is the large variety of tools, and different methods of configuration and limitations.
+To create a custom traffic, a user must read large manuals, and custom-design scripts.
+One of our bigger proposals is create a tool able to automatically do this processes.
+So The user may design his custom traffic by creating his own Compact Trace Descriptor, and create a traffic using many different tools, like Ostinato, D-ITG, Iperf, but not caring about how to proper configure each of them.
 
@@
 
-Now, we are going to formalize these exposed conceptual gaps in the literature, in a proposal of research and development. Or main targets here are:
+In this section, we are going to present our solution discussed in this text.
+SIMITAR is a traffic generator able to learn features of a real traffic automatically, and reproduce a synthetic traffic similar to the original.
+It records a model for the traffic in an XML file we call Compact Trace Descriptor.
+
+But first we will formalize our research targets, and then define a requirement list for SIMITAR, that means, what we want it to do. The main research targets are:
 
@@
 
-\item Survey the available open-source Ethernet workload tools available, addressing different features available;
+	\item Survey open-source Ethernet workload tools, addressing different features of each one.
+In this step, we want to evaluate the existing solution ready to use for network researchers and developers, and what can be used and integrated into our project as part of our solution;
 
-\item Define what is a realistic Ethernet traffic, and the main approaches found in literature for crafting it;
+	\item Define what a realistic Ethernet traffic is, and a set of metrics to measure the realism and the similarity between an original and a synthetic traffic.
+
+	\item Research the main apporoaches and methods found of the literature to create model Ethernet traffic, and for realistic traffic generation.
 
@@
 
-\item Create a software \textit{tool} able of \textit{learning} patterns and characteristics of real network traffic traces, and based on the acquired knowledge, allowing to reproduce network traffic with similar (but not equal) characteristics, \textit{avoiding} the storage of \textit{pcap} files.
-It must have a flow-oriented operation, and be able to choose the best features to represent each flow traffic.
-It will generate realistic Ethernet traffic based on these features learned, using available open source tools and APIs;
+	\item Create a software able of \textit{learning} metrics from real network traffic, and based on the that reproduce it workload with similar (but not equal) characteristics, \textit{avoiding} the storage of \textit{pcap} files.
 
@@
 We call our  tool \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}.
-These targets summarize a target of research, based on what we have exposed until now.
-We also will define some extra features, we want to have on our tool:
+This acronym summarizes its operation.
+Now, we are going to define a requirement list for our proposed software.
 
@@
 
-\item Traffic Flow Programmability: the tool records this parameterization on a light-weight and human-readable version of a \textit{pcap} file.
+	\item It must be able to extract data from a real traffic and store in a database. It must be able to obtain data from real-time traffics and from \textit{pcap} files;
+
+	\item It must have a flow-based abstract model for traffic generation, not attached to any specific technology. Then, its model should be parameterized using this stored data;
+
+	\item Human readable: it must produce a human-readable file as output that describes our traffic using our abstract model. We call this file a Compact Trace Descriptor;
+
+	\item Easy expansion: the traffic modeling and generation must be decoupled. Ideally, it must able to use as traffic generator engine any library or traffic generator tool;
+
+	\item Easy to use: It must be simple to use. It has to take as input a Compact Trace Descriptor, just as a traffic replay engine (such as TCPreplay) would take a \textit{pcap} file;
+
+	\item Traffic programmability: It must have what we call \textit{traffic generation progamability}.
+The compact trace descriptor must be simple and easy to read.
+In that way, the user may want to create his custom traffic, in a platform agnostic way.
+The traffic programmability must be flow-oriented;
+
+	\item The traffic modeling and generation must be flow-oriented. Each flow must be modeled and generated separately.
+
+\end{itemize}
+
+%These targets summarize a target of research, based on what we have exposed until now. We also will define some extra features, we want to have on our tool:
+%\begin{itemize}
+%\item Traffic Flow Programmability: the tool records this parameterization on a light-weight and human-readable version of a \textit{pcap} file.
 So the user can create his own models of traffic based on flows, in a platform-independent manner.
 He will not have to learn how to configure and script each tool.
-
-\item Easy expansion: The sniffing, modeling, and traffic generation processes must work separately, so updates will be easy to manage.
+%\item Easy expansion: The sniffing, modeling, and traffic generation processes must work separately, so updates will be easy to manage.
 Also, the traffic generation is flow-oriented (it generates each flow individually).
@@
 In this way, is much easier to expand the support for new traffic generation engines.
+%\end{itemize}
 
-\end{itemize}
+On the figure ~\ref{fig:layer-diagram} we abstract our concepts we stated in a layer diagram model.
+Or tool must work as an interface for the user automatizing traffic modeling, configuration, and emulation.
+Also should provide a service intelligence, programmability, and acceleration\footnote{Packet acceleration is a concept introduced by DPDK\cite{web-dpdk}, which means kernel by-pass.
+Packet acceleration optimizes the packet processing, and therefore traffic generation, enabling higher throughput rates.
+But, in the current version, this feature is not implemented, but its methodology is discussed in the section of future works in the chapter ~\ref{ch:conclusion}.}.
 
-Our goal is to offer an easier configuration, with a reasoble degree of realism than the available platforms today, at a reasonable speed.
+Our primary goal is to offer simple configuration, with realism, at a reasonable speed.
 To do this, we are introducing the concept of programmability for traffic generation.
-With SIMITAR, user may program its own synthetic traffic in a platform agnostic way.
+With SIMITAR, the user may program its synthetic traffic in a platform agnostic way.
 The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.
 
-Instead of storing a file huge \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace.
-This tool will store the generalized set of parameters in a human and machine readable XML file we call \textit{Compact Trace Descriptor} (\textit{CTD}).
+Instead of storing a huge file \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace.
+This tool will store the generalized set of parameters in a human and machine-readable XML file we call \textit{Compact Trace Descriptor} (\textit{CTD}).
 Then, we use this data as input for a traffic generator engine.
 We do so using APIs or creating new processes in a controlled manner.
-So will be possible to control packet parameters and flow's behavior in a automatized and self-configuring way.
+So will be possible to control packet parameters and flow's behavior in an automatized and self-configuring way.
 
@@
 
-Now, we are going to formalize these exposed concepts in a proposal of research and development. Or main targets here are:
-
-\begin{itemize}
-
-\item Survey the available open-source Ethernet workload tools available, addressing its different features;
-
-\item Define what is a realistic Ethernet traffic, and the man approaches found in literature;
-
-\item Create a general method for modeling and parameterization of Ethernet traffic, aiming to mimic a provided input;
-
-\item Create a software \textit{tool} able of \textit{learning} patterns and characteristics of real network traffic traces, and auto-configure the network traffic workloads, allowing to reproduce network traffic with similar (but not equal) characteristics, avoiding storage of \textit{pcap} files.
-
-\item It must have a flow-oriented operation, and be able to choose the best features to represent each flow traffic.
+%Now, we are going to formalize these exposed concepts in a proposal of research and development. Or main targets here are:
+%\begin{itemize}
+%\item Survey the available open-source Ethernet workload tools available, addressing its different features;
+%\item Define what is a realistic Ethernet traffic, and the man approaches found in literature;
+%\item Create a general method for modeling and parameterization of Ethernet traffic, aiming to mimic a provided input;
+%\item Create a software \textit{tool} able of \textit{learning} patterns and characteristics of real network traffic traces, and auto-configure the network traffic workloads, allowing to reproduce network traffic with similar (but not equal) characteristics, avoiding storage of \textit{pcap} files.
+%\item It must have a flow-oriented operation, and be able to choose the best features to represent each flow traffic.
 It will generate realistic Ethernet traffic based on these features learned, using available open source tools and APIs;
-
-\end{itemize}
+%\end{itemize}
 
@@
 
-%3nd-review
 \section{Document Overview}
 
-In this introductory chapter, we presented an abstract of the state of the art, a problem statement, and proposed an approach for research and requirements for development.
+In this introductory chapter, we presented an abstract of state of the art, a problem statement, and proposed an approach for research and requirements for development.
 
 %2nd-review
-In the chapter section~\ref{ch:literature-review}, we go deeper on some subjects mentioned here.
+In the chapter section~\ref{ch:literature-review}, we go more in-depth on some subjects mentioned here.
 First, we present an extensive survey on open-source traffic generator tools.
 We summarize the benefits, and features supported by each one.
-After, we present a brief survey of important topics on realistic traffic generation.
-We are defining some important concepts we are going to use in this work, such as self-similarity, and heavy-tailed functions.
+After, we offer a brief review of essential topics on realistic traffic generation.
+We are defining some central concepts we are going to use in this work, such as self-similarity, and heavy-tailed functions.
 Then, we discuss some techniques of validation of traffic generator tools and some practical examples.
-We also will make an analizis of some related works.
+We also will analyze some related works.
 
@@
 Chapter ~\ref{ch:architecture} introduces the methodology used in our project.
-We describe \textit{SIMITAR} low-level requirements and define an architecture and algorithms.
-We also present its classes design and explain how \textit{SIMITAR} we can expand to any traffic generator engine with an API, CLI interface.
-We use the D-ITG API as an example.
+We describe \textit{SIMITAR} low-level requirements and define an architecture and their algorithms.
+We also present its classes design and explain how \textit{SIMITAR} we can expand to any traffic generator engine or library, with an API, CLI interface.
+We use the Iperf as an example.
 We explain its operation and suggest some use cases.
@@
 In the chapter~\ref{ch:modeling-evaluation} we go deep in some subjects pointed in the previous chapter.
-We present how the modeling process actually works, using a defined data set (which we are going to use in the rest of the work).
-We also present some evaluation methods to check the modeling quality.
+We present how the modeling process works, using a defined data set (which we are going to use in the rest of the work).
+We also show some evaluation methods to check the modeling quality.
 We also describe our used and developed algorithms.
@@
 
-%On chapter Use Cases~\ref{ch:use-cases}, we present two use cases of our tool.
-One using an NFV testbed, and other using an SDN p4 switch.
+% On chapter Use Cases~\ref{ch:use-cases}, we present two use cases of our tool.
+One using an NFV testbed, and other handling an SDN p4 switch.
 Here we focus on QoS metrics, such as mean RTT.
-%use tools such as tcptrace and NFPA  on the use cases
+%use tools such as Tcptrace and NFPA  on the use cases
 
-%2nd-review
-Finally, on chapter Conclusion and Future Work~\ref{ch:conclusion}, we summarized our work and highlights future works to improve \textit{SIMITAR} on realism and performance.
+% 2nd-review
+Finally, on chapter Conclusion and Future Work~\ref{ch:conclusion}, we summarized our work and highlighted future actions to improve \textit{SIMITAR} on realism and performance.

### 2017-11-25 Docs/Thesis/docs/chapter3.tex
thesis update

@@
 %3nd-review
-In this chapter, we will present our tool which aims to solve the issues addressed in the chapter ~\ref{ch:introduction}, called SIMITAR (SnIffing, ModellIng and TrAffic geneRation), and how it works.
-It aims to generate a platform-agnostic traffic, which can be extended to any traffic engine, including traffic generators tools and APIs.
+In this chapter, we will present our tool which aims to fill the gaps addressed in the chapter ~\ref{ch:introduction}.
+It is called SIMITAR (SnIffing, ModellIng and TrAffic geneRation) and aims to generate a platform-agnostic traffic: it can be extended to almost any traffic engine, including traffic generators tools and APIs.
 SIMITAR creates a  model in XML, configured using actual traces (from \textit{pcaps} or real-time sniffing), we call Compact Trace Descritor (CTD).
@@
 Our tool, from live captures or \textit{pcap} file collects raw data from Ethernet traffic.
-It then breaks these data into different flows.
-It uses this data to generate a set of parameters for our traffic models, using a set of algorithms.
-Finally, it provides these parameters to a traffic generator engine and controls its packets injection.
+It then breaks these data into different flows and uses this data to generate a set of parameters for our traffic model, using a set of algorithms.
+Finally, SIMITAR provides these parameters to a traffic generator engine and controls its packets injection.
 
@@
 
-%2nd-review
 To meet the requirements presented in the section ~\ref{ch:introduction}, we will present a solution, and define how each part works, as in a low-level requirement list\cite{sommerville}.
-
-%2nd-review
-SIMITAR architecture is presented in the figure~\ref{fig:architecture}, and it is composed of five components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator} and the \textit{Network Traffic Generator}, as subsystem.
+SIMITAR architecture is presented in the figure~\ref{fig:architecture}, and it is composed of for components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator};  and a \textit{Network Traffic Generator}, as subsystem.
 We describe each part below.
@@
 On the other hand, was fast to implement, and enable the implementation of the other components, before this last version was released.
+The second and cuerrent version is implemented using Python.
+This version used Pyshark \footnote{\href{https://pypi.python.org/pypi/pyshark}{https://pypi.python.org/pypi/pyshark}} as sniffer library.
 
-The second version was implemented using Python.
-This version used Pyshark\footnote{\href{https://pypi.python.org/pypi/pyshark}{https://pypi.python.org/pypi/pyshark}} as sniffer library.
-The flow classification is made by a class called FlowId.
-It has class we developed called OrderedSet.
+It has a data structure we developed called \textit{OrderedSet}.
 A set is a list of elements with no repetition but do not keep track of the insertion order.
@@
 Also, it make use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}.
-The listed header fields are inputs for a hash function, its value is set on the ordered set, and its order is returned.
-This value is set as a packet flowID.
+The listed header fields are inputs for a hash function, its value is set on the ordered set, and its order(index on the \textit{OrderedSet}) is returned.
+The index value is set as a packet flowID.
 
@@
 
-The database stores the collected raw data  from the traces for further analysis. The \textit{Sniffer} and the \textit{TraceAnalyzer} can access the database.
+The database stores the collected raw data  from the traces for further analysis.
+The \textit{Sniffer} and the \textit{TraceAnalyzer} components uses the database.
+We choose an SQLite database, because according to its specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it fits well our porposes.
+It is simple and well-suitable for an amount of data smaller than terabytes.
+In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from packets, along with the flowID calculated by the sniffer component.
 
-We choose an SQLite database, because according to the SQLite specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it is the best option for our database.
-It is simple and well-suitable for an amount of data smaller than terabytes.
-
-In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from packets, along with the FlowID calculated by the sniffer component.
-
-%3nd-review
 \subsection{Trace Analyzer}
@@
 
-Harpoon uses a more conventional definition of each level, based on the measurement of SYN and ACK TCP flags.
+Harpoon uses a definition of each level, based on the measurement of SYN and ACK TCP flags.
 It use TCP flags (SYN) to classify packets in different levels, named there file, session, and user level.
@@
 In our algorithm simplified version, we define (as Harpoon does) three different layers of data transference to model and control: file, session, and flow.
-
 For SIMITAR, a file is just a sequence of consecutive packets transmitted continuously, without large interruption of traffic.
@@
 The session-layer refers to a sequence of multiple files transmitted between a source and a destination, belonging to the same flow.
-And the flow level refers to the conjunct of flow classified by the Sniffer.
+And the flow level refers to the conjunct of flows, as classified by the Sniffer.
+Now, we explain SIMITAR operation on each layer.
+All contants and defaults mode of operation can be changed by command line options.
 
-\textbf{Flow-layer}: The Trace Analyzer loads the flow arrival times from the database, and calculates the inter-packet times within the flow context.
+In the \textbf{flow layer} the \textit{TraceAnalyzer} loads the flow arrival times from the database, and calculates the inter-packet times within the flow context.
 
-\textbf{Session-layer}: At the session layer, we use a deterministic approach for evaluating times between files and the actual file transference, the OFF and ON times of a packet train model, respectivaly.
+At the \textbf{session layer}, we use a deterministic approach for evaluating file tranference time and times between files: ON/OFF times sequence of packet trains.
 We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.
@@
 It also determines the number of packets and bytes transferred by each file.
-Since the on times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms.
-We did this, first because ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators.
-Second, because in the case of just one packet, the ON time would be zero.
-OFF times, on the other hand, are defined by the constant \texttt{m\_session\_cut\_time}.
+Since the ON times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms.
+ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators and in the case of just one packet, the ON time would be zero.
+So setting aminimum acceptable time solve these issues.
+The OFF times, on the other hand, are defined by the constant \texttt{session\_cut\_time} \footnote{In the code it is called \texttt{DataProcessor::m\_session\_cut\_time} }.
 If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time.
-In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds).
-The control of ON/OFF periods is made by the \texttt{NetworkFlow} class.
+In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} for the \texttt{session\_cut\_time}: 30 seconds.
+The control of ON/OFF periods in the traffic generation is made by the \textit{FlowGenerator} component \footnote{This control is made by the class \texttt{NetworkFlow}}.
 
 %2nd-review
-\textbf{File-layer}: Here we model the inter-packet times at the file level.
-To estimate inter-packet times within files, we select all inter-packet times smaller than \texttt{m\_session\_cut\_time}.
+In the \textbf{file layer}, we model the inter-packet times at the file level.
+To estimate inter-packet times within files, we select all inter-packet times smaller than \texttt{session\_cut\_time}\footnote{In the code it is called\texttt{DataProcessor::m\_session\_cut\_time} }.
 All files within the same flow are considered to follow the same model.
@@
 From those, Weibull, Pareto, and Cauchy are heavy-tailed functions, and therefore self-similar processes.
-\textcolor{red}{<<<<pode mudar, calibrar>>>>} But if the flow has less than 30 packets, just the constant model is evaluated.
+But if the flow has less than 30 packets, just the constant model is evaluated.
 It is because numerical methods gave poor results if the data sample used is small.
-We sort these models according to the Akaike Information Criterion (AIC)\cite{sourcesonoff-paper}\cite{bic-aic-comparision}.
+We sort these models according to the Akaike Information Criterion (AIC) as default\cite{sourcesonoff-paper}\cite{bic-aic-comparision}.
 We will enter in deeper details on this methodology on the chapter ~\ref{ch:modeling-evaluation}.
@@
 %2nd-review
-An example of the final result of all the methods is presented in the XML code down below. It illustrates a flow of a \textit{Compact Trace Descriptor}(CDT) file.
+An example of the final result of all the methods is presented in the XML code down below.
+It illustrates a flow of a \textit{Compact Trace Descriptor}(CDT) file.
+The traffic models for inter-packet times are grouped by the tag \texttt{inter\_packet\_times}, and the packet trains by the tag \texttt{session\_times}.
+All the times are in seconds, and \texttt{inf} represents infinity.
+The protocol of each layer is stored as data by each tag.
 
@@
                breaklines=true]{xml}
-<flow start_delay="31.621941" duration="91.584654" ds_byte="0" n_kbytes="1" n_packets="13">
-	<link_layer mac_src="no-mac-src" mac_dst="no-mac-dst">ETHERNET</link_layer>
-	<network_layer src_ip="10.1.1.48" dst_ip="216.58.199.35" ttl="64">IPV4</network_layer>
-	<transport_layer dst_port="34683" src_port="443">TCP</transport_layer>
-	<application_layer>HTTPS</application_layer>
+
+	<flow start_delay="0.144400" duration="317.744333" ds_byte="0" n_kbytes="40" n_packets="344">
+		<link_layer mac_src="64:1c:67:69:51:bb" mac_dst="70:62:b8:9b:3e:d1">ETHERNET</link_layer>
+		<network_layer src_ip="192.168.1.1" dst_ip="192.168.1.2" ttl="64">IPV4</network_layer>
+		<transport_layer dst_port="2128" src_port="53">UDP</transport_layer>
+		<application_layer>DNS</application_layer>
 		<inter_packet_times>
-		<stochastic_model name="pareto-ml" aic="-24.738412" bic="-23.768599" param1="0.152500524612205" param2="0.000024050000003"/>
-		<stochastic_model name="weibull" aic="-16.155977" bic="-15.186164" param1="0.130469107098031" param2="0.063433369086366"/>
-		<stochastic_model name="pareto-lr" aic="49.322192" bic="50.292005" param1="0.892551148108768" param2="0.000024050000003"/>
-		<stochastic_model name="exponential-me" aic="76.776570" bic="77.746383" param1="0.131026317153354" param2="0.000000000000000"/>
-        <stochastic_model name="normal" aic="105.882623" bic="106.852436" param1="7.632054549999999" param2="17.598918053235813"/>
-        <stochastic_model name="exponential-lr" aic="116.913056" bic="117.882870" param1="0.009752000000000" param2="0.000000000000000"/>
-        <stochastic_model name="cauchy" aic="128.406532" bic="129.376345" param1="1.935832000000000" param2="-7.245692000000000"/>
-        <stochastic_model name="constant" aic="inf" bic="inf" param1="7.632054549999999" param2="0.000000000000000"/>
+			<stochastic_model name="pareto-ml" aic="-1165.310696" bic="-1157.646931" param1="0.405085202535192" param2="0.002272655895996"/>
+			<stochastic_model name="pareto-lr" aic="-454.049749" bic="-446.385984" param1="0.061065000000000" param2="0.002272655895996"/>
+			<stochastic_model name="weibull" aic="-246.882037" bic="-239.218273" param1="0.120355000000000" param2="0.001629000000000"/>
+			<stochastic_model name="exponential-me" aic="486.370061" bic="494.033826" param1="1.340057495455104" param2="0.000000000000000"/>
+			<stochastic_model name="normal" aic="1629.370900" bic="1637.034665" param1="0.746236637899171" param2="2.626808289821357"/>
+			<stochastic_model name="exponential-lr" aic="3166.816047" bic="3174.479812" param1="0.009752000000000" param2="0.000000000000000"/>
+			<stochastic_model name="cauchy" aic="31737.418442" bic="31745.082207" param1="0.000000000000194" param2="-3152.827055696396656"/>
+			<stochastic_model name="constant" aic="inf" bic="inf" param1="0.746236637899171" param2="0.000000000000000"/>
 		</inter_packet_times>
-	<session_times on_times="0.96856400,0.10000000,0.10000000" off_times="45.30807900,45.30801100" n_packets="11,1,1" n_bytes="1650,66,66"/>
-	<packet_sizes n_packets="13" n_kbytes="1">
-		<ps_mode1 n_packets="12" n_kbytes="1">
-			<stochastic_model name="constant" aic="inf" bic="inf" param1="99.916667" param2="0.000000"/>
-			<stochastic_model name="normal" aic="137.020397" bic="137.990210" param1="99.916667" param2="64.408439"/>
-			<stochastic_model name="exponential-me" aic="138.504076" bic="139.473889" param1="0.010008" param2="0.000000"/>
+		<session_times on_times="29.22199798,73.40390396,151.84077454" off_times="30.85738373,32.42027283" n_packets="19,103,222" n_bytes="2272,12399,26689"/>
+		<packet_sizes n_packets="344" n_kbytes="40">
+			<ps_mode1 n_packets="344" n_kbytes="40">
+				<stochastic_model name="constant" aic="inf" bic="inf" param1="120.232558" param2="0.000000"/>
+				<stochastic_model name="normal" aic="2926.106952" bic="2933.788235" param1="120.232558" param2="16.941453"/>
+				<stochastic_model name="exponential-me" aic="3987.126362" bic="3994.807645" param1="0.008317" param2="0.000000"/>
 			</ps_mode1>
-		<ps_mode2 n_packets="1" n_kbytes="0">
-		<stochastic_model name="constant" aic="inf" bic="inf" param1="583.000000" param2="0.000000"/>
+			<ps_mode2 n_packets="0" n_kbytes="0">
+				<stochastic_model name="no-model-selected" aic="inf" bic="inf" param1="0.000000" param2="0.000000"/>
 			</ps_mode2>
@@
 	</flow>
+
 \end{minted}
@@
 \end{figure*}
-0
+
 The Flow Generator handles the data on the CTD file, and use to retrieve parameters for traffic generation. It crafts and controls each flow in a separated thread.
@@
                breaklines=true]{bash}
-# Operation as a sniffer over a Ethernet interface named <ether-interface> 
-./simitar --sniffer --if <ether-interface> --out <cdt-name>
-# Operation as a client using the traffic generator D-ITG, using a list of destination hosts of a text file
-./simitar --client ditg --in <cdt-xml-name> --dst-list-ip <ip-list-file> 
-# Operation as a packet injector with uses the Libtins library to craft packets
-./simitar --pkt-injection libtins --in <cdt-xml-name> 
-# Operation as a server. just runs D-ITG in the server mode.
-./simitar --server ditg
+
+# @ SIMITAR/, load enviroment variables
+source data/config/simitar-workspace-config.sh
+
+# @ SIMITAR/sniffer/, execute to sniffer the eth0 interface, and create a trace entry called "intrig" in the database
+./sniffer-cli.py new intrig live eth0
+
+# @ SIMITAR/sniffer/, execute this command to list all traces recorded in the database
+./sniffer-cli.py list
+
+# @ SIMITAR/trace-analyzer/, execute this command to create two Compact Trace Descriptors, called intrig.ms.xml and intrig.sec.xml.
+The first is parameterized using milisecons, and de second, uses seconds as time unity.
+./trace-analyzer --trace intrig
+
+# @ SIMITAR/simitar-gen/, execute these commands to generate traffic using the intrig.sec.xml compact trace descriptor. It is stored at the directory "../data/xml/". 
+# Libtins
+./simitar-gen --tool tins --mode client --ether eth0 --xml ../data/xml/intrig.sec.xml 
+# Iperf
+./simitar-gen --tool iperf --mode client --ether eth0 --xml ../data/xml/intrig.sec.xml --dst-ip 10.0.0.2
+./simitar-gen --tool iperf --mode server --ether eth0 --xml ../data/xml/intrig.sec.xml
 

### 2017-11-27 Docs/Thesis/docs/chapter3.tex
thesis update

@@
 
-%3nd-review
+% ok1
+
 In this chapter, we will present our tool which aims to fill the gaps addressed in the chapter ~\ref{ch:introduction}.
-It is called SIMITAR (SnIffing, ModellIng and TrAffic geneRation) and aims to generate a platform-agnostic traffic: it can be extended to almost any traffic engine, including traffic generators tools and APIs.
-SIMITAR creates a  model in XML, configured using actual traces (from \textit{pcaps} or real-time sniffing), we call Compact Trace Descritor (CTD).
+It is called SIMITAR (SnIffing, ModellIng and TrAffic geneRation) and aims to generate a platform-agnostic traffic: it can use as traffic generator engine almost any traffic generator tools and programming API.
+It just requires a programming or command line interface.
+SIMITAR creates a  model in XML based on actual traces (\textit{pcaps} or real-time captures), we call Compact Trace Descriptor (CTD).
 
@@
 % cycle of operation
-%2nd-review
 \begin{figure*}[ht!]
@@
 
-To meet the requirements presented in the section ~\ref{ch:introduction}, we will present a solution, and define how each part works, as in a low-level requirement list\cite{sommerville}.
-SIMITAR architecture is presented in the figure~\ref{fig:architecture}, and it is composed of for components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator};  and a \textit{Network Traffic Generator}, as subsystem.
+% ok1
+
+To meet the requirements presented in the chapter ~\ref{ch:introduction}, we will define our solution, and how it works.
+SIMITAR architecture is presented in the figure~\ref{fig:architecture}.
+It is composed of four components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator};  and a \textit{Network Traffic Generator}, as subsystem.
 We describe each part below.
@@
 
-%2nd-review
+% ok1
+
 This component collects network traffic data and classifies it into flows, storing stores in an SQLite database.
-It defines each flow by the same criteria used by SDN switches\cite{sdn-survey}, through header fields matches (Link Protocol, Network Protocol, Network Source Address, Network Destination Address, Transport Protocol, Transport Source Port, Transport Destination Port).
-It can work over a \textit{pcap} file or over an Ethernet interface.
+It defines each flow by the same criteria used by SDN switches\cite{sdn-survey},  through header fields matches.
+It uses:
+
+\begin{itemize}
+\item Link Protocol
+\item Network Protocol
+\item Network Source and Destination Address
+\item Transport Protocol
+\item Transport Source and Destination Port
+\end{itemize}
 
@@
 
-The first version of this component was implemented in Shell Script (Bash).
-Tsahrk\footnote{\href{https://www.wireshark.org/docs/man-pages/tshark.html}{https://www.wireshark.org/docs/man-pages/tshark.html}} was used to extract header fields, and Awk to match the flows, and Sed/Awk to create the Sqlite queries.
+We implemented the first version of this component in Shell Script (Bash).
+Tsahrk\footnote{\href{https://www.wireshark.org/docs/man-pages/tshark.html}{https://www.wireshark.org/docs/man-pages/tshark.html}} was used to extract header fields, and Awk to match the flows, and Sed/Awk to create the SQLite queries.
 This version was too slow to operate in real time on Ethernet interfaces.
-On the other hand, was fast to implement, and enable the implementation of the other components, before this last version was released.
-The second and cuerrent version is implemented using Python.
+On the other hand, this approach was fast to implement and enable the implementation of the other components.
+The second and current version was made using Python.
 This version used Pyshark \footnote{\href{https://pypi.python.org/pypi/pyshark}{https://pypi.python.org/pypi/pyshark}} as sniffer library.
@@
 It has a data structure we developed called \textit{OrderedSet}.
-A set is a list of elements with no repetition but do not keep track of the insertion order.
+A set is a list of elements with no repetition but does not keep track of the insertion order.
 Our OrderedSet does.
-Also, it make use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}.
-The listed header fields are inputs for a hash function, its value is set on the ordered set, and its order(index on the \textit{OrderedSet}) is returned.
-The index value is set as a packet flowID.
+Also, it makes use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}.
+The listed header fields are inputs for a hash function, and its value is set on the ordered set which returns its order (index on the \textit{OrderedSet}).
+The index value is chosen as a packet flowID.
 
 %c++ http://ideone.com/F0V42m
-%2nd-review
 As future improvements for this component, we propose a more efficient implementation in C++ and data visualization for the collected data.
+In that way, we may optimize the packet processing.
 We discuss this in deeper details in the chapter~\ref{ch:conclusion}.
@@
 
+% ok1
+
 The database stores the collected raw data from the traces for further analysis.
 The \textit{Sniffer} and the \textit{TraceAnalyzer} components uses the database.
-We choose an SQLite database, because according to its specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it fits well our porposes.
+We choose an SQLite database, because according to its specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it fits well our purposes.
 It is simple and well-suitable for an amount of data smaller than terabytes.
@@
 
+% ok1
+
 This module is the core of our project.
 It creates a trace model via the analysis of the collected data.
-We define here a Compact Trace Descriptor (CTD) as a human and machine readable file, which describes an original traffic trace trough a set of flows, each of them described by a set of parameters, like header information and analytical models.
-
-Therefore, the Trace Analyze learns the features from raw data of traces (stored in the SQLite database) and write them in an XML file.
+We define here a Compact Trace Descriptor (CTD) as a human and machine-readable file, which describes a traffic trace through a set of flows, each of them represented by a set of parameters, such as header information and analytical models.
+The Trace Analyze has the task to learn these features from raw traces data (stored in the SQLite database) and generate an XML file.
 In the figure~\ref{fig:CTD-diagram} we show a directory diagram of a CDT file.
 It has many of many flow fields, and each one contains each parameter estimated.
-
-%\begin{figure*}[!ht]
-%    \centering
-%    \begin{subfigure}[t]{0.45\textwidth}
-%        \centering
-%        \includegraphics[height=2.5in]{figures/03_compact_trace_descriptor_tree_structure}
-%        \caption{caption}
-%    \end{subfigure}%
-%    ~ 
-%    \begin{subfigure}[t]{0.45\textwidth}
-%        \centering
-%        \includegraphics[height=2.5in]{figures/03_compact_trace_descriptor_tree_structure_2}
-%        \caption{caption}
-%    \end{subfigure}
-%    \caption{caption}
-%    \label{fig:CTD-diagram}
-%\end{figure*}
-%height=2.5in
-%
+Now we will describe how we construct it.
 
@@
 
-%3nd-review
 \subsubsection{Flow features}
 
-Some features are unique per flow and can be directly measured from the data. They are:
+% ok1
+
+Some unique per-flow features are directly measured from the data. They are:
 
@@
 
-%3nd-review
 \subsubsection{Inter Packet Times}
@@
 
-To represent inter packet times, we adopt a simplified version of the Harpoon traffic model.
+To represent inter-packet times, we adopt a simplified version of the Harpoon's traffic model.
 A deep explanation of the original model can be found at \cite{harpoon-paper} and \cite{harpoon-validation}.
@@
 Harpoon uses a definition of each level, based on the measurement of SYN and ACK TCP flags.
-It use TCP flags (SYN) to classify packets in different levels, named there file, session, and user level.
+It uses TCP flags (SYN) to classify packets in different levels, named their file, session, and user level.
 We choose to estimate these values, based on inter-packet times only.
@@
 
-In our algorithm simplified version, we define (as Harpoon does) three different layers of data transference to model and control: file, session, and flow.
+In our algorithm simplified version, we define three different layers of data transference to model and control: file, session, and flow.
 For SIMITAR, a file is just a sequence of consecutive packets transmitted continuously, without large interruption of traffic.
-It can be, for example, packets transmitted downloading a file, of UDP packets of a connection or a single ICMP echo packet.
+It can be, for example, packets sent downloading a file, packets from a  UDP  connection or a single ICMP echo packet.
 The session-layer refers to a sequence of multiple files transmitted between a source and a destination, belonging to the same flow.
-And the flow level refers to the conjunct of flows, as classified by the Sniffer.
+The flow level refers to the conjunct of flows, as classified by the Sniffer.
 Now, we explain SIMITAR operation on each layer.
-All contants and defaults mode of operation can be changed by command line options.
 
-In the \textbf{flow layer} the \textit{TraceAnalyzer} loads the flow arrival times from the database, and calculates the inter-packet times within the flow context.
+In the \textbf{flow layer} the \textit{TraceAnalyzer} loads the flow arrival times from the database and calculates the inter-packet times within the flow context.
 
-At the \textbf{session layer}, we use a deterministic approach for evaluating file tranference time and times between files: ON/OFF times sequence of packet trains.
+At the \textbf{session layer}, we use a deterministic approach for evaluating file transference time and times between files: ON/OFF times sequence of packet trains.
 We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.
@@
 Since the ON times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms.
-ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators and in the case of just one packet, the ON time would be zero.
-So setting aminimum acceptable time solve these issues.
+ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators.
+Also in the case of just one packet, the ON time would be zero.
+So setting a minimum acceptable time to solve these issues.
 The OFF times, on the other hand, are defined by the constant \texttt{session\_cut\_time} \footnote{In the code it is called \texttt{DataProcessor::m\_session\_cut\_time} }.
-If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time.
+If the time between two packets of the same flow is larger than \texttt{session\_cut\_time}, we consider them belonging to a different file, so this time is a session OFF time.
 In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} for the \texttt{session\_cut\_time}: 30 seconds.
-The control of ON/OFF periods in the traffic generation is made by the \textit{FlowGenerator} component \footnote{This control is made by the class \texttt{NetworkFlow}}.
+The control of ON/OFF periods in the traffic generation is made by the \textit{Flow Generator} component \footnote{This control is made by the class \texttt{NetworkFlow}}.
 
-%2nd-review
 In the \textbf{file layer}, we model the inter-packet times at the file level.
@@
 We sort these models according to the Akaike Information Criterion (AIC) as default\cite{sourcesonoff-paper}\cite{bic-aic-comparision}.
-We will enter in deeper details on this methodology on the chapter ~\ref{ch:modeling-evaluation}.
-The methodology of selection is presented in the figure~\ref{fig:model-parameterization}
+We will enter into deeper details on this methodology on the chapter ~\ref{ch:modeling-evaluation}.
+The methodology of selection is presented in the figure~\ref{fig:model-parameterization}, and all constants and modes of operation can be changed by command line options.
 
-%2nd-review
 \begin{figure*}[ht!]
@@
 
-%\begin{figure*}[ht!]
-%    \centering
-%    \includegraphics[height=4.0in]{figures/ch3/alg-paremeterization}
-%    \caption{caption.}
-%    \label{fig:harpoon-alg-times-estimator}
-%\end{figure*}
-
 \subsubsection{Packet Sizes}
 
-%2nd-review
 Our approach for the packet size is much simpler.
@@
 
-%2nd-review
 We know how much packets each mode has, and then we fit a model for it.
 We use three stochastic models: constant, exponential and normal.
-Since self-similarity do not make sense for packet-sizes, we prefer to use just the simpler models.
+Since self-similarity does not make sense for packet-sizes, we prefer to use just the simpler models.
 When there is no packet for a model, we set a flag NO\_MODEL, and when there is just a single packet we just use the constant model.
@@
 Also, it is computationally cheaper for the traffic generated than the other models, since no calculation is a need for each packet sent.
-Since both AIC and BIC criteria always will select the constant model as the worst, we decide to ignore this
+Since both AIC and BIC criteria always will select the constant model as the worst, we decide to ignore this.
 
@@
 
-%2nd-review
 We first implemented it using the D-ITG API.
@@
 
-%2nd-review
 This component works in two different layers according to the traffic generators classification introduced in the chapter ~\ref{ch:literature-review}: at the Flow level, and packet level, as presented in the figure ~\ref{fig:layers-workload-tools}.
@@
 
-%2nd-review
-At the flow level, it controls each flow using the algorithm at figure~\ref{alg-simplified-harpoon}.
-This algorithm basically handles the our model defined at the figure~\ref{fig:modified-harpoon-model}.
+At the flow-level, it controls each flow using the algorithm at figure~\ref{alg-simplified-harpoon}. This algorithm handles our model defined at the figure~\ref{fig:modified-harpoon-model}.
 
@@
 It is the time when the first flow packet was captured in the original capture.
-it then calls the underlying traffic generation method, passing to it the file ON time, number of packets and number of bytes to be sent (file size).
-Then it sleeps the next Session-OFF time from the stack until it ends.
+It then calls the underlying traffic generation method, passing to it the file ON time, number of packets and number of bytes to be sent (file size).
+Then it sleeps the next session OFF time from the stack until it ends.
 When the list of ON/OFF times is over, the thread ends.
-The thread scheduling/joining is implemented by the class \texttt{NetworkTrace} and its sleep/wake process by the class \texttt{DummyFlow}.
 
@@
 At the packet level, it must use the expanded class of the \texttt{DummyFlow}.
-In this level, the job of our tool is to configure the underlying engine, to send a file.
+In this level, the job of our tool is to configure the underlying engine, to send a file, as defined before.
 Therefore it uses the \textit{getters} available, and the passed parameters, defined by the operation described in the previous session.

### 2017-11-28 Docs/Thesis/docs/chapter3.tex
up

@@
 \subsubsection{Compact Trace Descriptor}
+%<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<
 
@@
 The traffic models for inter-packet times are grouped by the tag \texttt{inter\_packet\_times}, and the packet trains by the tag \texttt{session\_times}.
-All the times are in seconds, and \texttt{inf} represents infinity.
+All the times are in seconds, and "\texttt{inf}" represents infinity.
 The protocol of each layer is stored as data by each tag.
@@
 
-The Flow Generator handles the data on the CTD file, and use to retrieve parameters for traffic generation. It crafts and controls each flow in a separated thread.
-
-We first implemented it using the D-ITG API.
-But our Flow Generator can use any traffic generator with API, CLI or script interface as well.
-To easily expand this component, we use the design pattern factory.
-If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow} and add the support on the method \texttt{make\_flow()} of the class \texttt{NetworkFlow}.
-We will discuss this deeper in the next section.
+The Flow Generator handles the data on the \textit{Compact Trace Descriptor} file, and use to retrieve parameters for traffic generation.
+It crafts and controls each flow in a separated thread.
+To valitate its operation we implemented using Iperf traffic generation\cite{web-iperf} and Libtins C++ API.
+To simplify the expansion of this component, we use the design pattern factory.
+If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow}.
+The new class must not have any new attribute.
+Support for this class must be given in the \texttt{NetworkFlowFactory} class.
 
@@
 
-\subsubsection{Flow-level Traffic Generation Operation}
+At the flow-level, SIMITAR controls each flow using the algorithm at figure~\ref{alg-simplified-harpoon}.
+This algorithm handles our model defined at the figure~\ref{fig:modified-harpoon-model}.
+This procedure is independet of the traffic generator being used.
 
-At the flow-level, it controls each flow using the algorithm at figure~\ref{alg-simplified-harpoon}. This algorithm handles our model defined at the figure~\ref{fig:modified-harpoon-model}.
+It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps for \texttt{start\_delay} seconds.
+This is the arrival time of the first flow packet.
+Passed this time, it then calls the underlying traffic generation tool(defined as command line argument), and pass to it the flowID, file ON time, number of packets and number of bytes to be sent (file size), and network interface.
+Then it sleeps the next session OFF time.
+When the list of ON/OFF times from the flow is over, the thread ends.
 
-%2nd-review
-It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps its \texttt{start\_delay}.
-It is the time when the first flow packet was captured in the original capture.
-It then calls the underlying traffic generation method, passing to it the file ON time, number of packets and number of bytes to be sent (file size).
-Then it sleeps the next session OFF time from the stack until it ends.
-When the list of ON/OFF times is over, the thread ends.
-
-\subsubsection{Flow Generation Programming}
-
-%2nd-review
-At the packet level, it must use the expanded class of the \texttt{DummyFlow}.
-In this level, the job of our tool is to configure the underlying engine, to send a file, as defined before.
-Therefore it uses the \textit{getters} available, and the passed parameters, defined by the operation described in the previous session.
+At the packet level, the  \texttt{DummyFlow} derived class must implement  a new \texttt{flowGenerate()} method.
+Here, the job of our tool is to configure the underlying engine, to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}.
+This method must use the available parameters, atributes and \textit{getters} to configure and generate a thread-safe traffic.
 The implementation of this level should follow the flowchart presented in the figure ~\ref{fig:alg-traffic-engine-config}.
@@
                breaklines=true]{c++}
-void flowGenerate(const counter& flowId, const time_sec& onTime, const uint& npackets, const uint& nbytes,  const string& netInterface)
+
+// This implementation is just a simplified version to illustrate the procedure.
+void DitgFlow::flowGenerate(const counter& flowId, const time_sec& onTime, const uint& npackets, const uint& nbytes,  const string& netInterface)
 {
-	char localhost[CHAR_BUFFER];
-	string strCommand;
-	char command[CHAR_BUFFER];
-	uint i = 0;
-	int rc = 0;
-	getLocalIp("eth0", localhost);
+	// create command to generate the traffic
+	std::string strCommand;
+	std::string localhost = getNetworkSrcAddr(); 
 	strCommand += " -t " + std::to_string(onTime); 
 	strCommand += " -k " + std::to_string(nbytes / 1024);
-	strCommand += " -a " + getHostIP();
+	strCommand += " -a " + getNetworkDstAddr();
+
+	// configure protocol
 	if (this->getTransportProtocol() == PROTOCOL__TCP)
@@
 		strCommand += " -T ICMP ";
-	for(;;i++)
+
+	//configure inter-packet time model, just Weibull or Constant
+	for(uint i = 0;;i++)
 	{	
-		StochasticModelFit idtModel = this->getInterDepertureTimeModel(i);
+		StochasticModelFit idtModel = getInterDepertureTimeModel(i);
 		if(idtModel.modelName() == WEIBULL)
@@
 	}
-	strcpy(command, strCommand.c_str());
-	rc = DITGsend(localhost, command); // it is not blocking
-    usleep(onTime*10e6);
+
+	// it uses C strings as arguments
+	// it is not blocking, so it must block until finishes
+	int rc = DITGsend(localhost.c_str(), command.c_str()); 
+    usleep(onTime*10e6); // D-ITG uses miliseconds as time unity
 	if (rc != 0)
 	{
-		printf("\nDITGsend() return value was %d\n", rc);
+		PLOG_ERROR << "DITGsend() return value was" << rc ; // our log macro for erros
 		exit(EXIT_FAILURE);

### 2017-11-29 Docs/Thesis/docs/chapter3.tex
update

@@
 \centering
-\subfloat[first]{
+\subfloat[]{
   \includegraphics[height=4.in]{figures/ch3/cdt1}
 }
-\subfloat[second]{
+\subfloat[]{
   \includegraphics[height=4.in]{figures/ch3/cdt2}
@@
 	\centering
+	\includegraphics[height=3.0in]{figures/ch3/trace-flow}
+	\caption{Class hierarchy of NetworkTrace and NetworkFlow, which enables the abstraction of the traffic generation model of the traffic generation engine.}
+	\label{fig:network-trace-flow-class-diagram}
+\end{figure*}
+
+\begin{figure*}[ht!]
+    \centering
     \includegraphics[height=4.5in]{figures/ch3/alg-simplified-harpoon}
@@
 \end{figure*}
-
-The Flow Generator handles the data on the \textit{Compact Trace Descriptor} file, and use to retrieve parameters for traffic generation.
-It crafts and controls each flow in a separated thread.
-To valitate its operation we implemented using Iperf traffic generation\cite{web-iperf} and Libtins C++ API.
-To simplify the expansion of this component, we use the design pattern factory.
-If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow}.
-The new class must not have any new attribute.
-Support for this class must be given in the \texttt{NetworkFlowFactory} class.
-
-This component works in two different layers according to the traffic generators classification introduced in the chapter ~\ref{ch:literature-review}: at the Flow level, and packet level, as presented in the figure ~\ref{fig:layers-workload-tools}.
 
@@
 
-At the flow-level, SIMITAR controls each flow using the algorithm at figure~\ref{alg-simplified-harpoon}.
-This algorithm handles our model defined at the figure~\ref{fig:modified-harpoon-model}.
-This procedure is independet of the traffic generator being used.
+The Flow Generator handles the data on the \textit{Compact Trace Descriptor} file, and use to retrieve parameters for traffic generation.
+It crafts and controls each flow in a separated thread.
+We already implemented this component using Iperf traffic generator and Libtins C++ API, and it must follow the calss hierarcy as presented in the figure ~\ref{fig:network-trace-flow-class-diagram}.
+This component was designed using the design pattern Factory, to simplify its expansion and support\footnote{If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow}, creating a new derived class (figure ~\ref{fig:network-trace-flow-class-diagram} ).
+On our current implementation we already have implemented \texttt{IperfFlow} and \texttt{TinsFlow}, and \texttt{DitgFlow} is under validation process.
+This new class has the requirement of not have any new attribute.
+The support for this new class must be given on the factory class \texttt{NetworkFlowFactory}.
+For closed loop packet-crafters (that means, tools which must establish a connection between the source and the destination), two methods must be implemented: \texttt{flowGenerate()} and \texttt{server()}.
+\texttt{flowGenerate()} is responsible for sending a \textit{file}, as defined on de figure~\ref{fig:modified-harpoon-model}, and \texttt{server()} to receive $n$ files.
+Open loop packet-crafters, such as we implemented using Libtins (just sent the packets, do not establishes a connection), the server do not need to be implemented.}.
 
+This component and therefore our traffic generator is a multi-layer workload generator according to the typing introduced on chapter ~\ref{ch:literature-review} \footnote{Since it works both at packet and flow level, but do not work at application level.}.
+At the flow-level, SIMITAR controls each flow using the algorithm at figure~\ref{fig:alg-simplified-harpoon}.
+This algorithm handles our model defined at the figure ~\ref{fig:modified-harpoon-model}.
+This procedure is independent of the underlying packet crafting tool used.
 It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps for \texttt{start\_delay} seconds.
@@
 
-At the packet level, the  \texttt{DummyFlow} derived class must implement  a new \texttt{flowGenerate()} method.
-Here, the job of our tool is to configure the underlying engine, to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}.
-This method must use the available parameters, atributes and \textit{getters} to configure and generate a thread-safe traffic.
-The implementation of this level should follow the flowchart presented in the figure ~\ref{fig:alg-traffic-engine-config}.
-Down below we present a simplistic code of how the D-ITG API can be used to generate packet-level traffic.
-We call this concept \textit{Flow Generation Programming} A more complex configuration is possible, but it serves to illustrate the procedure.
-Its API documentation is available at on D-ITG web-site \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}.
+At the packet level, the job of our tool is to configure the underlying engine, to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}.
+This method must use the available parameters, attributes and \textit{getters} to configure and generate a thread-safe traffic using the method \texttt{flowGenerate()}.
+The \textit{file} configuration must follow the in the figure ~\ref{fig:alg-traffic-engine-config}.
+Down below we present a simple code of how the D-ITG API can be used to generate packet-level traffic.
+A more complex configuration is possible, but it serves to illustrate the procedure.
+We call this concept \textit{Flow Generation Programming}.
+Its API documentation is available at on D-ITG website \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}.
+
 \begin{minted}[frame=single,
@@
 	//configure inter-packet time model, just Weibull or Constant
+	StochasticModelFit idtModel;
 	for(uint i = 0;;i++)
 	{	
-		StochasticModelFit idtModel = getInterDepertureTimeModel(i);
+		idtModel = this->getInterDepertureTimeModel(i);
 		if(idtModel.modelName() == WEIBULL)
@@
 	// it is not blocking, so it must block until finishes
-	int rc = DITGsend(localhost.c_str(), command.c_str()); 
+	int rc = DITGsend(localhost.c_str(), command.c_str()); // D-ITG API
     usleep(onTime*10e6); // D-ITG uses miliseconds as time unity
@@
 A network traffic generator software that should provide its API or script interface for the \textit{FlowGenerator} component.
-
-Since \texttt{DITGsend()} is thread safe, no mutex is need.
-It would be needed if a lower level API, such Libtins or Libpcap was used.
-In that case, these APIs would permit control precisely each packet sent through the interface, but a mutex would be necessary.
-An scriptable tool, such as Iperf can be used as well, using \texttt{fork()} or \texttt{popen()}.
-
-As we claimed before, this tools is simple of being expanded for almost any traffic generation API, since its modeling framework is not coupled to the traffic generation.
-The figure \ref{fig:network-trace-flow-class-diagram} illustrates it well.
-It presents three possibilities of different traffic generation engines, all being configured and scheduled in a platform-agnostic way.
-
-\begin{figure*}[ht!]
-    \centering
-    \includegraphics[height=3.0in]{figures/ch3/trace-flow}
-    \caption{Class hierarchy of NetworkTrace and NetworkFlow, which enables the abstraction of the traffic generation model of the traffic generation engine.}
-    \label{fig:network-trace-flow-class-diagram}
-\end{figure*}
+With this tool, the user must be eble to send packets/traffic and controll atributes, such as sending time, bandwidht, number of packets, protocols, and so on.
+That means, any available parameter form the compact trace descriptor.
+If it does not have an API but an CLI, the user may have to use functions such as \texttt{fork()} or \texttt{popen()}.
 
@@
 
-When it working as a sniffer, it strores data from the capture traffic in the sqlite3 database.
+When it working as a sniffer, it stores data from the captured traffic in the sqlite3 database.
 It may work over a \textit{pcap} file or an Ethernet interface.
-Working as a trace a trace-analyzer, it receive the name of the trace as stored in the database, and creates a XML compact trace descriptor.
-The constants used in the modelling may be changed and provided as command line argument.
+Working as a trace a trace-analyzer, it receives the name of the trace as stored in the database, and creates an XML compact trace descriptor.
+The constants used in the modeling may be changed and provided as command line argument.
 If not, the default values will be used.
-
-As a traffic generator it may work as a client or a server.
-Working as a server is necessary for tools that require establishing a connection before generate the traffic, such as Iperf and D-ITG.
-It will just work passivaly.
-Working as a client, is acts as a traffic emissor.
-Tools such as \textit{libtins} dos not require server operation the send the traffic.
-
-When it operates as a client or as packet injector, it is operating as a traffic generator.
-The difference is that as a client, the used traffic generator is connection-oriented.
-It needs to establish a connection with the destination host (the server), before start sending packets.
-Operating as a client, it must take as an input a list of IP or MAC destination addresses, since they will not match with the ones in the original trace.
-It takes as an input a single destination in the command line, or list of many, in a text file passes as a parameter.
-Also, it uses the machine IP address as packet's source IP.
-
- As a packet injector can generate packets on the output interface, without establishing a connection.
-It uses the original IP and MAC destination and source addresses.
-As a client, the reproduction of the trace is expected to be poor in the flow level metrics exposed in the chapter ~\ref{ch:literature-review}, since it will use new addresses values.
-
-The operation of packet injector is still under implementation, and we are using Libtins API.
-Currently, SIMITAR supports client mode with D-ITG, implemented using its C++ API.
-We intend to provide support for many others traffic generators, such Iperf and Ostinato.
-
-When operating as a server, it just start-up the traffic generator server, and waits forclient requests for connections.
-Down bellow, we present simple examples of commands used to activate each operation mode.
+As a traffic generator, it may work as a client or a server.
+Working as a server is necessary for closed-loop engines; tools that require establishing a connection before generating the traffic, such as Iperf and D-ITG.
+It will just work passively.
+Working as a client is acting as a traffic emitter.
+Open loop packet-crafter tools such as \textit{libtins} does not require server operation the send the traffic.
+In the case of closed-loop tools, the destination IP addresses must be explicitly given in the command line by the options \texttt{--dst-list-ip} or \texttt{--dst-ip}.
+Down below, we present simple examples of commands used to activate each operation mode.
 
@@
 \end{minted}
-
-As use cases, we can cite:
-
-\begin{itemize}
-
-\item Flow Generation Progamability: creation of custom synthetic traffic with a certain number of flows, in a traffic-generator independent way.
-
-\item Generate Background traffic with D-ITG: SIMITAR can work to generate background traffic over a network when it receives many addresses as input.
-If each destination is reachable, D-ITG will establish a connection with each destination, and recreate flows as described in the CDT file.
-
-\item Stress a Device Under Test (DUT): It can be used to stress a single device with a more self-similar realistic traffic.
-The CDT file can be manually modified to change some aspects of the traffic, such as the number os packets or throughput applied by the traffic generator of each flow.
-Some undesirable features such as Stochastic models or lesser flow may be taken out, SIMITAR does not have constraints on a number of flows and Stochastic models adopted (but must have at least one).
-
-\item Generate synthetic \textit{pcap} files: Using virtual interfaces, we can reproduce a traffic, and capture it with a sniffer tool, such as Tcpdump, Wireshark or Tshark.
-We plan to automatize this process as a future work, with an operation mode of \textit{pcap} generator.
-To do this we are going to use Mininet to create the virtual interfaces and Libtins to inject packets.
-
-\end{itemize}

### 2017-11-29 Docs/Thesis/docs/chapter6.tex
update

@@
 		\multicolumn{3}{c}{Future Work}	& Priority \\ \hline
-		1                      & Optimizing linear regression                              &                                                 & \textit{high}                    \\
+		1   & Optimizing linear regression                      &                                & \textcolor{red}{high} \\
 		2   & Flow-merging option                               &                                & medium \\
@@
 		5   & DPDK KNI interfaces                               &                                & medium \\
-		6                      & Multi-thread C++ sniffer                                  & \multirow{-6}{*}{Performance}                   & \textit{high}                    \\ \hline
-		7                      & Model inter-packet times on \texttt{TinsFlow}           &                                                 & \textit{high}                    \\
-		8                      & D-ITG flow generator (\texttt{DitgFlow})                &                                                 & low                     \\
-		9                      & DPDK flow generator (\texttt{DpdkFlow})                 &                                                 & medium                     \\
-		10                     & Ostinato flow generator (\texttt{OstinatoFlow})         & \multirow{-4}{*}{Tool support}                  & low                     \\ \hline
-		11                     & \texttt{DataProcessor::min\_time}                       &                                                 & low                     \\
-		12                     & \texttt{DataProcessor::m\_min\_on\_time}                &                                                 & low                     \\
-		13                     & \texttt{DataProcessor::m\_session\_cut\_time}           &                                                 & low                     \\
-		14                     & Minimum number of packets per flow option                 & \multirow{-4}{*}{Calibration}  & low                     \\ \hline
-		15 & Python API/Lua for traffic generation & & low \\
-		16 & Crafter of  pcap files & \multirow{-2}{*}{New features} & low \\
-		%17 & Json compact trace descriptor  & \multirow{-3}{*}{New features} & low 
+		6   & Multi-thread C++ sniffer                          &                                & \textit{high} \\ \hline
+		7   & Cluster operation (high speed traffic-gen) & \multirow{-7}{*}{Performance}  & \textit{high} \\
+		8   & Model inter-packet times on \texttt{TinsFlow}     &                                & \textit{high} \\
+		9   & D-ITG flow generator (\texttt{DitgFlow})          &                                & low \\
+		10  & DPDK flow generator (\texttt{DpdkFlow})           &                                & medium \\
+		11  & Ostinato flow generator (\texttt{OstinatoFlow})   & \multirow{-4}{*}{Tool support} & low \\ \hline
+		12  & \texttt{DataProcessor::min\_time}                 &                                & low \\
+		13  & \texttt{DataProcessor::m\_min\_on\_time}          &                                & low \\
+		14  & \texttt{DataProcessor::m\_session\_cut\_time}     &                                & low \\
+		15  & Minimum number of packets per flow option         & \multirow{-4}{*}{Calibration}  & low \\ \hline
+		16  & Python API/Lua for traffic generation             &                                & low \\
+		17  & Crafter of  pcap files                            & \multirow{-2}{*}{New features} & low \\
+
 		\hline
@@
 
-(7) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times.
+(7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be splitted on $m$ different files, each describing $n/m$ flows, and still describe the same traffic.
+With $m$ synchronized machines woking in parallel, each using one of these $m$ parts of the original \textit{compact trace descriptor}, with use of link-agregattion techinique\footnote{http://www.comutadores.com.br/configurando-link-aggregationetherchannel-entre-cisco-e-hpn/} we can achieve high speeds on bare-metal.
+
+(8) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times.
 To avoid overheads on random numbers calculation,  these values must be calculated before the actual traffic generation.
@@
 
-(8-10) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}.
+(9-11) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}.
 D-ITG offers many stochastic functions for customization of inter-packet times, Ostinato provides a rich set of headers and protocols, and DPDK a high performance on packet generation.
@@
 
-(11) Calibrate  the constant  \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times.
+(12) Calibrate  the constant  \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times.
 We use this value to avoid inter-packet times equals to zero due to the sniffer resolution.
@@
 
-(12) Calibrate  the constant \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have.
+(13) Calibrate  the constant \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have.
 It can change the generated traffic precision.
@@
 
-(13) Calibrate  the constant \texttt{DataProcessor::m\_session\_cut\_time}: this value defines whatever a file transference still active or has ended.
+(14) Calibrate  the constant \texttt{DataProcessor::m\_session\_cut\_time}: this value defines whatever a file transference still active or has ended.
 It defines the smallest OFF time acceptable.
@@
 
-(14) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: this would reduce the number of flows created, improving its computational performance.
+(15) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: this would reduce the number of flows created, improving its computational performance.
 Since SIMITAR manages each flow in a different thread, it will create fewer threads simultaneously, reducing overheads.
@@
 
-(15) Currently, SIMITAR only enables the programming of flow traffic generation in C++.
+(16) Currently, SIMITAR only enables the programming of flow traffic generation in C++.
 Adding Python and Lua support for the Flow Generator component, we can enable expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ wrappers.
 
-(16) \textbf{PcapGen: a compact \textit{pcap} lybrary}: Create a component capable of generate synthetic \textit{pcap} files, using Compact Trace Descriptors(CTDs) files.
+(17) \textbf{PcapGen: a compact \textit{pcap} lybrary}: Create a component capable of generate synthetic \textit{pcap} files, using Compact Trace Descriptors(CTDs) files.
 We can implement this using SIMITAR as a packet injector, but in an emulated host interface, for example, using Mininet.

### 2017-11-30 Docs/Thesis/docs/chapter4.tex
update thesis text

@@
 We implemented this prototype using Octave.
-We upload the code on GitHub, for reproduction purposes\footnote{\textcolor{red}{github-link-aqui}}
+We upload the code on GitHub, for reproduction purposes\footnote{\href{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests/PrototypeDataProcessor}{https://github.com/AndersonPaschoalon/ProjetoMestrado/tree/master/Tests/PrototypeDataProcessor}}
 

### 2017-11-30 Docs/Thesis/docs/chapter6.tex
update thesis text

@@
 		\multicolumn{3}{c}{Future Work}	& Priority \\ \hline
-		1   & Optimizing linear regression                      &                                & \textcolor{red}{high} \\
-		2   & Flow-merging option                               &                                & medium \\
-		3   & Smart flow-scheduler                              &                                & \textit{high} \\
+		1   & Optimizing linear regression                       &                                & \textbf{\textit{high}} \\
+		2   & Flow-merging option                                &                                & \textit{medium} \\
+		3   & Smart flow-scheduler and thread/process management &                                & \textbf{\textit{high}} \\
 		4   & \texttt{DataProcessor::minimumAmountOfPackets}     &                                & low \\
-		5   & DPDK KNI interfaces                               &                                & medium \\
-		6   & Multi-thread C++ sniffer                          &                                & \textit{high} \\ \hline
-		7   & Cluster operation (high speed traffic-gen) & \multirow{-7}{*}{Performance}  & \textit{high} \\
-		8   & Model inter-packet times on \texttt{TinsFlow}     &                                & \textit{high} \\
+		5   & DPDK KNI interfaces                                &                                & \textit{medium} \\
+		6   & Multi-thread C++ sniffer                           &                                & \textbf{\textit{high}} \\ 
+		7   & Cluster operation (high speed traffic-gen)         & \multirow{-7}{*}{Performance}  & \textbf{\textit{high}} \\ \hline
+		8   & Model inter-packet times on \texttt{TinsFlow}      &                                & \textbf{\textit{high}} \\
 		9   & D-ITG flow generator (\texttt{DitgFlow})           &                                & low \\
-		10  & DPDK flow generator (\texttt{DpdkFlow})           &                                & medium \\
+		10  & DPDK flow generator (\texttt{DpdkFlow})            &                                & \textit{medium} \\
 		11  & Ostinato flow generator (\texttt{OstinatoFlow})    & \multirow{-4}{*}{Tool support} & low \\ \hline
@@
 In the current implementation, the linear regression execution is mono-thread, and the stop criterion is just the number of iterations.
-Parallel processing, and creating stop criteria based on convergence in addition to the number of iterations will improve the performance.
+Parallel processing, and creating stop criteria based on convergence in addition to the number of iterations will improve the performance, along with some code optimizations.
 
@@
 For traffics with a massive amount of streams, a methodology for merging them should reduce computational costs and enable replication of traffic with a much more significant bandwidth.
+Another improvement in traffic generations is reduced memory consumption per thread and process, and optimize the code.
 
@@
 We decide to do it for two reasons.
-First, because with a small sample, the modeling accuracy is poor .
+First, because with a small sample, the modeling accuracy is poor.
 Second, we avoid the cost of the parameterization process.
@@
 In this step, we designed our algorithms presented in chapter ~\ref{ch:modeling-evaluation}, and chose the APIs, packages, and libraries, such as Armadillo\cite{armadillo}, a C++ linear algebra library.
-Many ideas we used to conceive our ideas were inspired by previous works and solutions, such as Harpoon\cite{harpoon-validation}, sourcesOnoff \cite{sourcesonoff-paper} and LegoTG\cite{legotg-paper}.
+Many ideas we used to conceive our ideas were inspired by previous works and solutions, such as D-ITG\cite{ditg-paper}, Harpoon\cite{harpoon-validation}, Swing\cite{swing-paper} sourcesOnoff\cite{sourcesonoff-paper}, and LegoTG\cite{legotg-paper}.
 This procedure continued with incremental upgrades until we arrived on the version presented on the chapter ~\ref{ch:validation}.
@@
 
-Finally, we created a list of improvements and future works, aiming the improvement of performance on processing time, and packet generation; and the methods to improve the realism of the traffic generated.
-In the is we believe to overcome the current limitations.
+Finally, we created a list of improvements and future works, aiming the improvement of the software, inclusing, performance better processing time and packet generation, and the realismo on the traffic generated.
+In fact, the greater bootleneck of the project resides on processing performance.
+The results on realism, even with a lot of room for improovments, already have a good quality.
+With the proposed future works we believe to be possible overcome the current limitations.

### 2017-11-30 SIMITAR/libsimitar/NetworkTrace.cpp

@@ -32,7 +32,7 @@ NetworkTrace::NetworkTrace(const string& fileName,
 	xml_node<> * root_node;
 
 	// Read the xml file into a vector
-	std::ifstream theFile(fileName); //TODO
+	std::ifstream theFile(fileName);
 	std::vector<char> buffer((std::istreambuf_iterator<char>(theFile)),
 			std::istreambuf_iterator<char>());
 	buffer.push_back('\0');

### 2017-11-30 Docs/PaperSimitar/body.tex
new files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:introduction}

Emerging technologies such as SDN and NFV are great promises. If succeeding at large-scale, they would change drastically the development and operation of computer networks. But, especially on NFV, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. Since it is expected virtualization to impact negatively on performance, these VNFs have to keep its degradation as small as possible. Guarantee the Service Layer Agreements on emerging scenarios is now a harder question. There is a demand for more reliable methods to ensure the SLAs, over different types of loads.

It is already a well-known fact that the type of traffic used on performing tests matters. Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption. It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of new technologies. There are many reasons for this behavior, which includes burstiness and packet sizes.

A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}, and  measurement accuracy\cite{legotg-paper} \cite{background-traffic-matter}. Another key question is how applications will deal with packets. It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.

Realistic workload generators are also essential security research\cite{ditg-paper}.  Generation of realistic workloads is important in the evaluation of firewall middleboxes. It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.

Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.

Another critical point is the flow-oriented operation of SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller.  Also the SDN switches have a flow-oriented operation. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider.

Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a relevant subject.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open-source Solutions}\label{sec:review}

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.

Some traffic generator tools offer support emulation of single application workloads. But this does not correspond to real complex scenarios. Other tools work as packet replay engines, such as TCPreplay and TCPivo. Although in that way is possible to produce a realistic workload at high rates, it comes with some issues. First, the storage space required becomes huge for long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources.

Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen. But all of them just offer a complet framework to be congfigured, but the customization of the traffic is all up to user to do. So, there is no simple way for the user to create an synthetic realistic traffic scenario.

We also have available a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others. These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators. For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK. Also, many of the listed traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.

%They can give a good control of the traffic and high rates. Es example of controllable features we can list:
%\begin{itemize}
%\item Throughput, the number of bytes, number of packets.
%\item Protocols. Most of the tools give support to network and transport protocols. Many also offer support to Link and Application protocols;
%\item Header and payload configuration. Support for header customization includes source and destination port/addresses, QoS parameters, flags, etc. Some traffic generators also allow customizing payload bytes.
%\item Inter-packet times. Some tools offer a set of stochastic distributions to control inter-packet times. The user can use these stochastic functions to emulate realistic inter-arrival times.
%\item On/off periods: support of packet trains periods. Many offer stochastic models to control it. 
%\item Sending time and start-time: the user can use these features to control flows timings.  
%\item Packet-size: support for different packet sizes. Some tools offer constant values or stochastic distributions to control packet sizes.
%\item Paralell flows configuration.
%\item Emulation of specific applications: common examples are 
%\end{itemize}

Therefore we have a large variety open-source tools available for custom traffic generation. But reproducing a realistic traffic scenario is a hard question. Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}. But usually this is not the goal of the project, so the researcher or the them have scarce time available to work over it. Since it is usually is not the main goal of the project, but just a mean many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.   Reproducig a realistic traffic usung these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation. Since it usually is not the goal of the research, but a mean.

For this gap, there are some sollutions on the open source community. Tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}. But they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}. Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code. This is clearly a hard task\cite{legotg-paper}, and an error prone activity. Again, we fall in the same problem a complex task that usually is not the goal of the project.

Another issue is the large variety of tools, and different methods of configuration and limitations. To create a custom traffic, a user must read large manuals, and custom-design scripts. One of our bigger proposals is create a tool able to automatically do this processes. So The user may design his custom traffic by creating his own Compact Trace Descriptor, and create a traffic using many different tools, like Ostinato, D-ITG, Iperf, but not caring about how to proper configure each of them.

%Since synthetic traffic traces generation is mature in academia, the creation of custom network workloads through the configuration of  open-source tools is an affordable task. But it is not often available in an automatic way, and most of the times is a challenging question\cite{legotg-paper}, and still, requires expert knowledge. It requires time, study, and is vulnerable to human mistakes and lack of validation. Such work may require weeks to complete a realistic reproduction of a single scenario, so most of the time it is just not done. We argue that widely (i.e. affordable) existing approaches can be regarded as simplistic often point solutions to more general cases.

% Also, just choosing which workload generator tool may fit better for the user needs is not a simple question. Tools like D-ITG\footnote{\href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}} provide support to many different stochastic functions, Ostinato\footnote{\href{http://ostinato.org/}{http://ostinato.org/}} provides a larger support for protocols, and a higher throughput for each thread\cite{comparative-trafficgen-tools}, and others like Seagull\footnote{\href{http://gull.sourceforge.net/doc/WP_Seagull_Open_Source_tool_for_IMS_testing.pdf}{http://gull.sourceforge.net/doc/WP\_Seagull\_Open\_Source\_tool\_for\_IMS\_testing.pdf}} are responsive.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Architecture and Modelling}\label{sec:architecture}

To meet the requirements presented in the section ~\ref{sec:introduction}, we will define our solution, and how it works. SIMITAR architecture is presented in the figure~\ref{fig:architecture}. It is composed of four components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator};  and a \textit{Network Traffic Generator}, as subsystem. We describe each part below.

\begin{figure}[ht!]
        \centering
        \includegraphics[height=2.7in]{figures/architecture-diagram}
        \caption{Architecture of SIMITAR}
    \label{fig:architecture}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sniffer}

This component collects network traffic data and classifies it into flows, storing stores in an SQLite database. It defines each flow by the same criteria used by SDN switches\cite{sdn-survey},  through header fields matches. It uses:

\begin{itemize}
\item Link Protocol
\item Network Protocol
\item Network Source and Destination Address
\item Transport Protocol
\item Transport Source and Destination Port
\end{itemize}

\begin{figure}[ht!]
        \centering
        \includegraphics[width=\linewidth]{figures/sniffer-classifier}
        \caption{SIMITAR's sniffer hash-based flow classification}
    \label{fig:sniffer}
\end{figure}

It has a data structure we developed called \textit{OrderedSet}. A set is a list of elements with no repetition but does not keep track of the insertion order. Our OrderedSet does. Also, it makes use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}. The listed header fields are inputs for a hash function, and its value is set on the ordered set which returns its order (index on the \textit{OrderedSet}). The index value is chosen as a packet flowID.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SQLite database}

\begin{figure}[ht!]
        \centering
        \includegraphics[width=\linewidth]{figures/database-relational-model}
        \caption{SIMITAR's SQLite database relational model}
    \label{fig:simitar-database}
\end{figure}

The database stores the collected raw data from the traces for further analysis. The \textit{Sniffer} and the \textit{TraceAnalyzer} components uses the database.  We choose an SQLite database, because according to its specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it fits well our purposes. It is simple and well-suitable for an amount of data smaller than terabytes. In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from packets, along with the flowID calculated by the sniffer component.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Trace Analyzer}

This module is the core of our project. It creates a trace model via the analysis of the collected data. We define here a Compact Trace Descriptor (CTD) as a human and machine-readable file, which describes a traffic trace through a set of flows, each of them represented by a set of parameters, such as header information and analytical models.  The Trace Analyze has the task to learn these features from raw traces data (stored in the SQLite database) and generate an XML file.  In the figure~\ref{fig:CTD-diagram} we show a directory diagram of a CDT file. It has many of many flow fields, and each one contains each parameter estimated. Now we will describe how we construct it.

\begin{figure}[ht!]
        \centering
        \includegraphics[width=\linewidth]{figures/cdt1}
        \caption{Directory diagram of the schema of a Compact Trace Descriptor (CDT) file.}
    \label{fig:CTD-diagram}
\end{figure}

\subsubsection{Flow features}

Some unique per-flow features are directly measured from the data. They are:

\begin{itemize}
\item Flow-level properties like duration of flow, start delay, number of packets per flow, number of KBytes per flow; 
\item Header fields, like protocols, QoS fields, ports, and addresses.
\end{itemize}

Each one of these parameters is unique per flow. Other features like PSD (packet size distribution) e IPT (Inter-packet time), have a more complex behavior.  To represent these characteristics, we will use sets of stochastic-based models.

\subsubsection{Inter Packet Times}

To represent inter-packet times, we adopt a simplified version of the Harpoon's traffic model. A deep explanation of the original model can be found at \cite{harpoon-paper} and \cite{harpoon-validation}. Here, we will explain our simplified version, which is illustrated at figure~\ref{fig:modified-harpoon-model}.

Harpoon uses a definition of each level, based on the measurement of SYN and ACK TCP flags. It uses TCP flags (SYN) to classify packets in different levels, named their file, session, and user level. We choose to estimate these values, based on inter-packet times only. The distinction is made based on the time delay between packets.

In our algorithm simplified version, we define three different layers of data transference to model and control: file, session, and flow. For SIMITAR, a file is just a sequence of consecutive packets transmitted continuously, without large interruption of traffic. It can be, for example, packets sent downloading a file, packets from a  UDP  connection or a single ICMP echo packet. The session-layer refers to a sequence of multiple files transmitted between a source and a destination, belonging to the same flow.  The flow level refers to the conjunct of flows, as classified by the Sniffer.  Now, we explain SIMITAR operation on each layer.

In the \textbf{flow layer} the \textit{TraceAnalyzer} loads the flow arrival times from the database and calculates the inter-packet times within the flow context.

At the \textbf{session layer}, we use a deterministic approach for evaluating file transference time and times between files: ON/OFF times sequence of packet trains. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.  We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the ON times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators. Also in the case of just one packet, the ON time would be zero. So setting a minimum acceptable time to solve these issues. The OFF times, on the other hand, are defined by the constant \texttt{session\_cut\_time} \footnote{In the code it is called \texttt{DataProcessor::m\_session\_cut\_time} }. If the time between two packets of the same flow is larger than \texttt{session\_cut\_time}, we consider them belonging to a different file, so this time is a session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} for the \texttt{session\_cut\_time}: 30 seconds. The control of ON/OFF periods in the traffic generation is made by the \textit{Flow Generator} component \footnote{This control is made by the class \texttt{NetworkFlow}}.

In the \textbf{file layer}, we model the inter-packet times at the file level. To estimate inter-packet times within files, we select all inter-packet times smaller than \texttt{session\_cut\_time}\footnote{In the code it is called\texttt{DataProcessor::m\_session\_cut\_time} }. All files within the same flow are considered to follow the same model. We delegate the control of the inter-packet times to the underlying workload engine tool. We ordered them, from the best to the worst. Currently, we are using eight different stochastic functions parameterizations. They are Weibull(linear regression), Normal(mean/standard deviation calculation), Exponential(mean and linear regression estimation), Pareto(linear regression and maximum likelihood), Cauchy(linear regression) and Constant(mean calculation). From those, Weibull, Pareto, and Cauchy are heavy-tailed functions, and therefore self-similar processes. But if the flow has less than 30 packets, just the constant model is evaluated. It is because numerical methods gave poor results if the data sample used is small. We sort these models according to the Akaike Information Criterion (AIC) as default\cite{sourcesonoff-paper}\cite{bic-aic-comparision}. We will enter into deeper details on this methodology on the chapter ~\ref{ch:modeling-evaluation}. The methodology of selection is presented in the figure~\ref{fig:model-parameterization}, and all constants and modes of operation can be changed by command line options.

\subsubsection{Packet Sizes}

Our approach for the packet size is much simpler. Since the majority of packet size distribution found on real measurements are bi-modal \cite{packet-distribution-model}\cite{sourcesonoff-paper}\cite{udp-flows-model}, we first sort all packet sizes of flow in two modes. We define a packet size mode cut value of 750 bytes, same value adopted by \cite{udp-flows-model}.

We know how much packets each mode has, and then we fit a model for it. We use three stochastic models: constant, exponential and normal. Since self-similarity does not make sense for packet-sizes, we prefer to use just the simpler models. When there is no packet for a model, we set a flag NO\_MODEL, and when there is just a single packet we just use the constant model. Then calculate the BIC and AIC for each, but we decide to set the constant model as the first.

As is possible to see in many works \cite{packet-distribution-model} \cite{udp-flows-model}, since the standard deviation of each mode tends to be small, constant fittings use to give good approximations. Also, it is computationally cheaper for the traffic generated than the other models, since no calculation is a need for each packet sent. Since both AIC and BIC criteria always will select the constant model as the worst, we decide to ignore this.

\subsubsection{Packet Sizes}

Our approach for the packet size is much simpler. Since the majority of packet size distribution found on real measurements are bi-modal \cite{packet-distribution-model}\cite{sourcesonoff-paper}\cite{udp-flows-model}, we first sort all packet sizes of flow in two modes. We define a packet size mode cut value of 750 bytes, same value adopted by \cite{udp-flows-model}.

We know how much packets each mode has, and then we fit a model for it. We use three stochastic models: constant, exponential and normal. Since self-similarity does not make sense for packet-sizes, we prefer to use just the simpler models. When there is no packet for a model, we set a flag NO\_MODEL, and when there is just a single packet we just use the constant model. Then calculate the BIC and AIC for each, but we decide to set the constant model as the first.

As is possible to see in many works \cite{packet-distribution-model} \cite{udp-flows-model}, since the standard deviation of each mode tends to be small, constant fittings use to give good approximations. Also, it is computationally cheaper for the traffic generated than the other models, since no calculation is a need for each packet sent. Since both AIC and BIC criteria always will select the constant model as the worst, we decide to ignore this.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Validation}\label{sec:validation}

\subsection{Methodology}

As proof of concepts for our tool, we are going to use Mininet's emulated testbeds. We automate all tests using scripts, so our experiments are are fully  reproducible. They are responsible for running all the proposed tests in this chapter and perform the calculations. It includes:

\begin{itemize}
	\item Build the topology;
	\item Run the SIMITAR traffic generator;
	\item Collect the packeckets as \textit{pcap} files, and stract data from it;
	\item Perform the proposed proof of concept analysis;
	\item Plot the data.
\end{itemize}

Each test is organized as a Python packege, responsible for tigger all the applications and procedures. The parameters for each simulation can be configured by a \textit{config.py} file. The files \textit{README} on each packege, provide a tutorial to run correctely each test. With all tools instaled, less then fifteen minutes is enought for run each test again. A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specificatins and the software versions.

\begin{table}[ht!]
	\centering
	\caption{Experiments specification table}
	\label{tab:specifications}
	\begin{tabular}{ll}
		\hline
		Processor            & Intel(R) Core(TM) i7-4770, 8 cores, CPU @ 3.40GHz \\
		RAM                  & 15.5 GB                                           \\
		HD                   & 1000 GB                                           \\
		Linux         & 4.8.0-59-generic                                  \\
		Ubuntu        & Ubuntu 16.10 (yakkety)                            \\
		SIMITAR       & v0.4.2 (Eulemur rubriventer)                      \\
		Mininet       & 2.3.0d1                                           \\
		Iperf         & iperf version 2.0.9 (1 June 2016) pthreads        \\
		Libtins       & 3.4-2                                             \\
		OpenDayLight  & 0.4.0-Beryllium                                   \\
		Octave        & 4.0.3                                             \\
		Pyshark       & 0.3.6.2                                     \\
		Wireshark     & 2.2.6+g32dac6a-2ubuntu0.16.10               \\
		Tcudump       & 4.9.0 \\
		libpcap       & 1.7.4\\
		\hline
	\end{tabular}
\end{table}

\begin{figure}[h!]
	\centering
	\subfloat[Single hop SDN topology]{
		\includegraphics[width=\linewidth]{figures/topo-simple}
		\label{fig:topo-simple}
	}
	\hspace{0mm}
	\subfloat[Tree SDN topology]{
		\includegraphics[width=\linewidth]{figures/topo-tree}
		\label{fig:topo-tree}
	}
	\hspace{0mm}
	\caption{Mininet SDN topologies. Controller OpenDayLight Beryllium.)}
	\label{fig:topo}
\end{figure}

For each test, we generate a set of plots to compare the original and synthetic trace. Two of them we use for mere visual comparison: flows per second and bandwidth. To compare the realism quality of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.  On every case, the more closer the plots are, the more similar the traffics are according to each perspective. Also, we wrote in the table ~\ref{tab:results-summary} a complation of each traffic statistics.

The flow's cumulative distribution measures each new flow identified the trace. It is a measure similarity of the traffic at the flow-level.  The wavelet multiresolution analysis is capable of capture traffic scaling characteristics and is a measure of similarity at the packet-level. If the value decreases, a periodicity on that time scale exists. With white-noise features, the traffic will remain constant. If the traffic has self-similar characteristics on a particular time scale, its value will increase linearly.

We use as testbeds: a tree topology (figure~\ref{fig:topo-tree}), similar to tests performed by Swing\cite{swing-paper}\cite{background-traffic-matter}\cite{legotg-paper}, and a one-hop connection of two hosts. Both topologies are SDN networks and have OpenDayLight Beryllium as the controller.

For generating the traffic on the host \textit{h1} with IPv4 address 10.0.0.1. The traffic is captured from the host interface with TCPdump in a \textit{pcap} format.  We organized the project directory tree as follows\footnote{ \href{https://github.com/AndersonPaschoalon/ProjetoMestrado}{https://github.com/AndersonPaschoalon/ProjetoMestrado} }: the software is at \textit{SIMITAR}. All validation tests and project prototypes we aved at \textit{Tests} directory. The software documentation is at \textit{Docs} directory.

We use SIMITAR v0.4.2 (Eulemur rubriventer)\footnote{ We label the tags of SIMITAR control version on GitHub as lemurs species names (\href{https://en.wikipedia.org/wiki/List_of_lemur_species}{https://en.wikipedia.org/wiki/List\_of\_lemur\_species})}, as tagged at the GitHub repository.  SIMITAR already have two functional traffic generator engines: Iperf and libtins C++ API.

\begin{table*}[h]
	\centering
	\caption{Sumary of results comparing the original traces (italic) and te traffic generated by SIMITAR, with the description of the scenario.}
	\label{tab:results-summary}
	%\scalebox{0.87}{
\begin{tabular}{lcccccc}
	\hline
	\multicolumn{1}{c}{\multirow{3}{*}{}} & \multirow{3}{*}{\textit{skype-pcap}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}skype, \\ one-hop, \\ iperf\end{tabular}}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}skype, \\ tree, \\ iperf\end{tabular}}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}skype, \\ one-hop, \\ libtins\end{tabular}}} & \multirow{3}{*}{\textit{lgw10s-pcap}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}lgw10s, \\ one-hop, \\ libtins\end{tabular}}} \\
	\multicolumn{1}{c}{}                  &                             & \multicolumn{1}{c}{}                                                                                     & \multicolumn{1}{c}{}                                                                                  & \multicolumn{1}{c}{}                                                                                       &                              & \multicolumn{1}{c}{}                                                                                        \\
	\multicolumn{1}{c}{}                  &                             & \multicolumn{1}{c}{}                                                                                     & \multicolumn{1}{c}{}                                                                                  & \multicolumn{1}{c}{}                                                                                       &                              & \multicolumn{1}{c}{}                                                                                        \\ \hline
	Hurst Exponent                        & 0.601                       & 0.618                                                                                                    & 0.598                                                                                                 & 0.691                                                                                                      & 0.723                        & 0.738                                                                                                       \\
	Data bit rate (kbps)                  & 7                           & 19                                                                                                       & 19                                                                                                    & 12                                                                                                         & 7252                         & 6790                                                                                                        \\
	Average packet rate (packets/s)       & 3                           & 4                                                                                                        & 5                                                                                                     & 6                                                                                                          & 2483                         & 2440                                                                                                        \\
	Average packet size (bytes)           & 260,89                      & 549,05                                                                                                   & 481,14                                                                                                & 224,68                                                                                                     & 365,00                       & 347,85                                                                                                      \\
	Number of packets                     & 1071                        & 1428                                                                                                     & 1604                                                                                                  & 2127                                                                                                       & 24 k                         & 24 k                                                                                                        \\
	Number of flows                       & 167                         & 350                                                                                                      & 325                                                                                                   & 162                                                                                                        & 3350                         & 3264                                                                                                        \\ \hline
\end{tabular}
	%}
\end{table*}

For schedule of the timing of traffic generated by each flow, we implemented three methodologies: \texttt{usleep()} C function,\texttt{select()} C function and \textit{pooling}. Here we use \texttt{usleep()} . We implemented the class \texttt{IperfFlow,} responsible for generate the traffic of each flow, using \texttt{popen()} and \texttt{pclose()} to instantiate Iperf processes, responsible for generating the traffic. Traffic customization on Iperf has many limitations. It cannot assign arbitrary IP addresses as source and destination since it must establish a connection between the source and destination. For the transport layer, it just supports TCP and UDP protocol, and constant bandwidth traffic. On the other hand, it enables customization of transmission time, number of packets, windows size, TTL, packet sizes, payload and many other features. Since Iperf has to establish a communication, SIMITAR must operate in the client mode on the source, and server mode on the destinations.

Libtins enable the creation and emission of arbitrary packets and do not require the establishment of a connection.  Thus SIMITAR does not need to operate in server mode on the destination. The packet customization capability is vast, and enable a full usage of our model parameters. Control inter-packet times stays for future work.

\subsection{Results}

% Bandwidth
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-iperf-Bandwidth.pdf}
		\label{fig:iperfBw}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-tree-iperf-Bandwidth.pdf}
		\label{fig:iperftreeBw}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-tins-Bandwidth.pdf}
		\label{fig:tinsBw}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/lgw-tins-Bandwidth.pdf}
		\label{fig:tinsLgwBw}
	}
	\hspace{0mm}
	\caption{Traces bandwidth.}
	\label{fig:flows-bandwidth}
\end{figure}
% Flows per second
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-iperf-FlowsPs.pdf}
		\label{fig:iperfFps}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-tree-iperf-FlowsPs.pdf}
		\label{fig:iperftreeFps}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-tins-FlowsPs.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/lgw-tins-FlowsPs.pdf}
		\label{fig:tinsLgwFps}
	}
	\hspace{0mm}
	\caption{Flow per seconds}
	\label{fig:flows-ps}
\end{figure}
% Flow CDF
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-iperf-FlowCdf.pdf}
		\label{fig:iperfCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-tree-iperf-FlowCdf.pdf}
		\label{fig:iperftreeCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-tins-FlowCdf.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/lgw-tins-FlowCdf.pdf}
		\label{fig:tinsLgwCdf}
	}
	\hspace{0mm}
	\caption{Flows cumulative distributions.}
	\label{fig:flows-cdf}
\end{figure}
% Wabelet
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-iperf-WaveletMREA.pdf}
		\label{fig:iperfWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-tree-iperf-WaveletMREA.pdf}
		\label{fig:iperftreeWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/skype-tins-WaveletMREA.pdf}
		\label{fig:tinsWaveletMREA}
	}
	\hspace{0mm}
		\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
			\includegraphics[width=77mm]{figures/lgw-tins-WaveletMREA.pdf}
			\label{fig:tinsLgwWaveletMREA}
		}
		\hspace{0mm}
	\caption{Wavelet multiresolution energy analysis.}
	\label{fig:wavelet}
\end{figure}

We display our results in the figures ~\ref{fig:flows-ps} to ~\ref{fig:wavelet}, and in the table ~\ref{tab:results-summary}, where the original and the synthetic traffics are compared. As we can see in the figure ~\ref{fig:flows-bandwidth}, the generated traffics are not identical regarding bandwidth, however both presents fractal-like shape. The Hurst exponent of inter-packet times in every case has an error smaller than 10\% compared to the original in every case. This result indicates that in fact, the fractal-level of each synthetic traffic is indeed similar to the original.

The plot of flows per second seems much more accurate visually since most of the peaks match.  Indeed, no visual lag between the plots. We can analyze it precisely observing the cumulative flow distribution\ref{fig:flows-cdf}, where the results were almost identical on every plot. However, when SIMITAR is replicating the traffic of \textit{lgw10s-pcap} the number of flows per second decreases. It happens because of the methodology of traffic generation of the class \textit{TinsFlow} since it sends the packets of each stream as fast as possible. So each flow occurrence is restricted to smaller intervals. This behavior can be observed as well in the bandwidth plot. It is much larger in the first seconds and small at the end.

The best results achieved by SIMITAR were on the flow distribution characterization. On every experiment made, the cumulative distribution of flows was almost identical. The small imprecisions on the plots are expected and should result from threads and process concurrence of resources and imprecision on the sleep/wake signaling on the traffic generation side. Imprecisions on packet capture buffer may count as well since the operating system did the packet timing. This was our most significant achievement in our research. This result means that our method of flow scheduling and independent traffic generation were effective and efficient on replicating the original traffic at the flow-level. The actual number of flows was much more significant when SIMITAR used Iperf and about the same amount but little small when used libtins. This discrepancy happens with Iperf because it establishes additional connections to control the signaling and traffic statistics.  So, this more substantial number of flows comes from accounting, not just the traffic connections, but also with the signaling as well.  With libtins, the number of flows is small, because, if it fails to create a new traffic flow, this flows generation execution is aborted.

On Wavelet multiresolution analysis of inter-packet times, the results have changed more in each case. The time resolution chosen was ten milliseconds, and it is represented in $\log_2$ scale. The actual time pf each time-scale $j$ value is given by the equation:

\begin{equation}
t = \frac{2^{j}}{100} [s]
\end{equation}

In the first case (figure ~\ref{fig:iperfWaveletMREA}), SIMITAR using Iperf in a single-hop scenario, on small time scales the energy level of the synthetic traffic remained almost constant, which indicates white-noise characteristics. The original skype traffic increased linearly, an indication of fractal shape. The synthetic trace started to increase at the time scale 5-6 (300-600 milliseconds). After this scale, the error between the curves become very small. One possible reason for this behavior is the fact that the constant which regulate the minimum burst time (\texttt{DataProcessor::m\_min\_on\_time}) is set to 100 milliseconds. For small time scales the traffic become similar to white noise since Iperf just emits traffic with constant bandwidth. For larger scales, it captures the same fractals patterns of the original trace. It also captures a periodicity pattern at the time-scale of 9 seconds. The authors of \cite{swing-paper} measured the same periodicity pattern. But on this trace, we observe some periodicity at 11 and 13 time-scales (20 and 80 seconds).

In the second case, on a tree topology on small time scales, the same white-noise behavior is identified. We identify a similar behavior on the energy behavior on larger time-scales, but with a larger gap between the curves. Packet collision on switches requiring retransmission packets explains this behavior. In fact, as we can see in the table ~\ref{tab:results-summary}, two hundred more packets are leaving the client on the tree topology compared to the one-hop.

On the last two plots, where we use libtins as packet crafter, the energy level is much higher, and the curves are much less correlated. SIMITAR are not modeling inter-packet with libtins, and are sending packets as fast as possible. We may observe on the figures ~\ref{fig:tinsBw} and ~\ref{fig:tinsLgwBw} that than have much  higher peaks compared to the original \textit{skype-pcap}.  As we see in the figure ~\ref{fig:tinsBw}, it just captured some periodicity characteristics at the time larger than 11-12 (20-40 seconds). SIMITAR determines larger periods between packets with session OFF times, and the session cut time (\texttt{DataProcessor::m\_session\_cut\_time}) is 30 seconds, that explain this behavior.

The current implementation still has problems on accurately reproduce \textit{pcaps} with high bandwidth values and a more substantial number of flows. The primary limitation is the time required to generate the trace descriptor.  The procedure is still mono-thread, and the linear regression procedure is not optimized. Although creating a trace descriptor of a small pcap file is fast, the time for processing large pcap file with thousands of flows is still prohibitively high, spending dozens of hours.

Using the first 10 seconds of the trace \textit{bigFlows-pcap}, on 10 seconds of operation, Iperf generated much fewer packets than the expected. It is an expected behavior since the operating system couldn't handle so much newer processes (one per flow) in such short time. On the other hand, the same drawback wasn't observed using libtins as traffic generator tool, since being a low-level API makes it much computationally cheaper.  Some others unexpected behavior must have a more in-depth investigation, such as libtins generating more packets than expected for \textit{skype-pcap}, but not for \textit{lgw10s-pcap}, and why the creation of some flows fail, and how to fix it if possible.

Another promising possible investigation is what traffic each tool can better represent. In terms of number of flows and packets, bandwidth and for larger \textit{pcaps}, \textit{libtins} is a best option. But Iperf has presented a better performance replicating scaling characteristics of applications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}\label{sec:conclusion}

SIMITAR was designed to work at flow-level and packet level. At the flow-level, our methodology can achieve great results. In fact,  The cumulative distribution of flows is almost identical on each case. From the perspective of benchmark of a middle-box such as an SND switch, this is a great result, since its performance depends on the number of registered flows. However, because of packets exchanged by signaling connection, the traffic generated by Iperf, even following the same cumulative flow distribution, had created more streams then expected.

At packet level, the current results with Iperf replicate with high accuracy the scaling characteristics of the original traffic, and the number of generated packets are not far than the expected. However, the packet size replication and therefore the bandwidth is not accurate. Also, \textit{libtins} as traffic generator tool still is limited in this aspect.

Once the current implementation of the Flow Generator still does not uses the whole set of parameters from the Compact Trace Descriptor, and many optimizations yet to be made, this is a satisfactory result that validates and proves the potential of our proposed methodology. Even we designing  SIMITAR  to prioritizing modularity over finner control, when we compare these current results with the more consolidated realistic traffic generator available, they are closer. At the flow-lever our results are at least as good as the achieved by Harpoon\cite{harpoon-paper} and Swing\cite{swing-paper}. At the scaling characteristics, on lightweight traces, they are already comparable in quality.

+++++++++++++++++++++++++++++++++

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{>>>>> Temp Introduction <<<<<< }\label{sec:introduction-temp}

On network benchmarking and testing, it is known that the traffic properties interfere on the network component performance\cite{burstiness-queue-lenght}\cite{harpoon-validation} and measurament acuracy\cite{swing-paper}. Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption. A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Features such as packet-trains periods and inter-packet times affect traffic burstiness}. Also, a burstier and realistic traffic  impacts not just on performance, but on measurement accuracy as well \cite{legotg-paper} \cite{background-traffic-matter}. Along with that, buffers quees and software applications have performance degradation processing small-sized packets. All this indicates that tests with constant bit rate traffic generator tools such as Iperf and Ostinato are important but not enough to guarantee the SLAs for new technologies.

Realistic workload generators are also essential security research\cite{ditg-paper}, and are crucial on the evaluation of firewall middleboxes. It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}. Another critical point is the flow-oriented operation of SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller. We also have a flow-oriented operation on SDN switches. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual ISP scenario.

Alongside with that the introduction of virtualization via techinologies such as NFV  still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. We can expect that its impact mentioned before over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a important subject on testing and benchmarking.

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation. Some traffic generator tools offer support emulation of single application workloads. But this does not correspond to real complex scenarios, with a large number of distributed hosts in an Internet Service Provider (ISP) or even a Local Area Network (LAN). Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen. Since there is so many features and tools, selecting a good configuration is by itself a research project. How to use each parameter to simulate a specific scenario is a hard question \cite{legotg-paper}\cite{selfsimilar-ethernet}. It is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic patterns and experimental evaluation.

Some tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}. But they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic background traffic, but do not reach high throughputs \cite{swing-paper} \cite{legotg-paper}. Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code. And this is a hard task.

Since synthetic traffic traces generation is mature in academia, the creation of custom network workloads through the configuration of high-throughput open-source is an affordable task. But it is not often available in an automatic way, and most of the times is a challenging question\cite{legotg-paper}, and still, requires expert knowledge. It requires time, study, and is vulnerable to human mistakes and lack of validation. Such work may require weeks to complete a realistic reproduction of a single scenario, so most of the time it is just not done. We argue that widely (i.e. affordable) existing approaches can be regarded as simplistic often point solutions to more general cases.

Also, just choosing which workload generator tool may fit better for the user needs is not a simple question. Tools like D-ITG\footnote{\href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}} provide support to many different stochastic functions, Ostinato\footnote{\href{http://ostinato.org/}{http://ostinato.org/}} provides a larger support for protocols, and a higher throughput for each thread\cite{comparative-trafficgen-tools}, and others like Seagull\footnote{\href{http://gull.sourceforge.net/doc/WP_Seagull_Open_Source_tool_for_IMS_testing.pdf}{http://gull.sourceforge.net/doc/WP\_Seagull\_Open\_Source\_tool\_for\_IMS\_testing.pdf}} are responsive.

### 2017-11-30 Docs/PaperSimitar/header.tex
new files

@@
 %}
-\title{Using BIC and AIC for Ethernet traffic model selection. Is it worth?}
+\title{SIMITAR: realistic and autoconfigurable traffic generation}
 
@@
 \begin{abstract}
-In this work, we aim to evaluate how good are the information criteria AIC and BIC inferring which is the best stochastic process to describe Ethernet inter-packet times.
-Also, we check if there is a practical difference between using AIC or BIC.
-We use a set of stochastic distributions to represent inter-packet of a traffic trace and calculate AIC and BIC.
-To test the quality of  BIC and AIC guesses,  we define a cost function based on the comparison of significant stochastic properties for internet traffic modeling, such as correlation, fractal-level and mean.
-Then, we compare both results.
-In this short paper, we present just the results of a public free Skype-application packet capture, but we provide as reference further analyzes on different traffic traces.
-We conclude that for most cases AIC and BIC can guess right the best fitting according to the standards of Ethernet traffic modeling.
+It is a well known fact that the type of traffic on network measurements matters.
+A realistic Ethernet have a different impact compared to constant traffic tools like Iperf, even with the same bandwidth.
+A burstier traffic may cause buffers overflows when a constant traffic does not, decrease on the measurement acuracy.
+The number of flows of a traffic may have an impact of flow-oriented nodes, such as SDN switches and controllers.
+Today in an scenario where software defined networks are going to play an essential role in the future of the networks, a depper validation of new technologies in order to guarantee the SLAs is crucial.
+In this scenario we come with an anternative for realist traffic generation.
+Most of open-source realistic traffic generator tools have the modelling layer coupled to the traffic generator API, wich make it difficult to be update to newer lybraries, or require user programming and manual configuration.
+We propose a sollution called SIMITAR: SnIffing, ModellIng and TrAffic geneRation, that have a separated moddelling framework from the traffic generator, which is flow-oriented, and is autoconfigurable.
+It creates and use as imputs compact traces descriptos, XML files that describes all features of the traffics.
+Currently we are able to replicate with acuracy 
 \end{abstract}
@@
 \begin{IEEEkeywords}
-BIC, AIC, stochastic function, inter-packet times, correlation, Hurst exponent, heavy-tailed distribution, fractal-level, burstiness, linear-regression, weibull, pareto, exponential, normal, poison, maximum likelihood, Ethernet traffic, traffic modeling, fractal-level, pcap file, Skype traffic.
+Sniffing, traffic modelling, BIC, AIC, inter-packet times, Wavelet scalling, traffic generator, Burstiness, pcap file, linear regression, Iperf
 \end{IEEEkeywords}

### 2017-12-01 Docs/PaperSimitar/body.tex
up

@@
 
-Emerging technologies such as SDN and NFV are great promises.
-If succeeding at large-scale, they would change drastically the development and operation of computer networks.
-But, especially on NFV, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}.
-Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior.
-Since it is expected virtualization to impact negatively on performance, these VNFs have to keep its degradation as small as possible.
-Guarantee the Service Layer Agreements on emerging scenarios is now a harder question.
-There is a demand for more reliable methods to ensure the SLAs, over different types of loads.
+%> Burstiness de um trafego interfere nas medidas
+It is already a well-known fact that the type of traffic used on tests impacts in many results, even with the same avarage bandwidth.
+Tests with constant bit rate traffic generator tools are not enough for a complete validation of new technologies.
+Realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same avarage bandwidth.
+As reason we can for this behavior we have traffic burstiness and many different packet sizes\footnote{Traffic burstness is the intermitent increase and decreace on data transference.
+Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}.
+A realistic burstier traffic can cause more buffer overflows, increase packet losses, cause a network performance degeneration \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, and interfere on the measurement acuracy \cite{legotg-paper} \cite{background-traffic-matter} compared to a constrant traffic.
+Also the traffic burstiness interferes on the  measurement accuracy.
 
-It is already a well-known fact that the type of traffic used on performing tests matters.
-Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption.
-It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of new technologies.
-There are many reasons for this behavior, which includes burstiness and packet sizes.
-
-A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}, and  measurement accuracy\cite{legotg-paper} \cite{background-traffic-matter}.
+%> Aplicações e middleboxes
 Another key question is how applications will deal with packets.
@@
 A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.
+Realistic workload generators are also essential security research\cite{ditg-paper}.
+It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}, over firewall middleboxes and softwares.
+In this case, not just the traffic burstiness is relevant, but the connection behavior and header contents, such as protocols and port numbers.
 
-Realistic workload generators are also essential security research\cite{ditg-paper}.
-Generation of realistic workloads is important in the evaluation of firewall middleboxes.
-It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.
-
-Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.
-
-Another critical point is the flow-oriented operation of SDN networks.
+%Emerging technologies such as SDN and NFV are  drastically changing  computer networks.
+But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}.
+Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior.
+Guarantee the Service Layer Agreements on emerging scenarios is now a harder question.
+There is a demand for more reliable methods to ensure the SLAs, over different types of loads.
+Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect an even larger impact over over virtualized middle-boxes should be even larger, due the virtualization layer extra overhead.
+Also, we have the flow-based ofperation of  SDN networks.
 Each new flow arriving on an SDN switch demands an extra communication load between it and the controller.
 This may create a bottleneck between the switch and the controller.
-Also the SDN switches have a flow-oriented operation.
-Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider.
-
+The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table.
+Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider.
 Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment.
-How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a relevant subject.
+How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject.
+Emerging technologies such as SDN and NFV are  drastically changing  computer networks.
+But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}, since hardware solutions  have a much more predictable behavior.
+There is a demand for more reliable methods to ensure the Service Layer Agreements, over different types of loads.
+We can expect an even larger impact over over virtualized middle-boxes should be even larger compared to dedicated hardware devices, due the virtualization-layer extra overhead.
+Along with that, on Software Defined Networks we have the flow-based operation.
+Each new flow arriving on an SDN switch demands an extra communication between it and the controller, wich may create a boobleneck.
+The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table.
+Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider.
+Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment.
+How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Open-source Solutions}\label{sec:review}
+\section{Open-source Traffic Generators}\label{sec:review}
 
@@
 Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.
+Traffic generators are commonly classified into four different groups\cite{do-you-trust}: application-level, flow-level, packet-level and multi-level traffic generators.
 
-Some traffic generator tools offer support emulation of single application workloads.
-But this does not correspond to real complex scenarios.
-Other tools work as packet replay engines, such as TCPreplay and TCPivo.
-Although in that way is possible to produce a realistic workload at high rates, it comes with some issues.
-First, the storage space required becomes huge for long-term and high-speed traffic capture traces.
-Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources.
+\textbf{Application-level traffic generators}: they try to emulate the behavior of network applications, simulating real workloads stochastically and/or responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool.
+That means, the behavior of the output may change according to what packets have arrived in the network interface}.
+As examples we have Surge\cite{surge-paper} able to emulate the behavior of web clients and services.
+The behavior of such applications is, in general, based on request-response exchanges models.
 
+\textbf{Flow-level traffic generators}: they are able to configure and reproduce features of flows\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}.
+Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from live routers.
+
+\textbf{Packet-level traffic generators}: most traffic generators available fall in this class.
+They are able to craft packets and inject into the network, and controll features like inter departure times (IDT), packet size(PS), throughput and packets per second\cite{validate-trafficgen}.
+\cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model based generators.
+Traffic Replay engines, such TCPreplay\cite{web-tcpreplay}, are  able to read packet capture files (\textit{pcap} files), and inject copies on a network interface.
+Model-based generators, such D-ITG \cite{ditg-paper}, TG\cite{web-tg}, may have PS and IDT configured by the user.
+They can configure IDT  either by constant values (defining the packet rate or bandwidth) or by stochastic models.
+Maximum throughput engines like Ostinato and Seagull are tools that the main goal is to perform end-to-end stress testing.
+Are included in this category generators that are able to craft packets from the link layer, like Brute, KUTE, and pktgen.
+
+\textbf{Multi-level traffic generators}: its proposal is to take into account existing interaction among each layer of the network stack, to create background network traffic as close as possible from reality.
+The most relevant tool of this class is Swing \cite{swing-paper}.
+Swing take into account many points of each layer, using an approach based on randomness and responsiveness \cite{swing-paper}.
+That means, it uses packet-sizes and inter packet times stochastic models, but also take into account flow and application layer behavior.
+Swing is able to model things like\cite{swing-paper}:
+
+\begin{itemize}
+
+	\item User behavior: Number of request and responses, time between requests and responses;
+
+	\item Request and Responses: number of connections, time between start of connections;
+
+	\item Connection: Number of request and responses per connection, applications modeling (HTTP, P2P, SMTP), transport protocols TCP/UDP based on the application, response sizes, request sizes, user think between exchanges on a connection;
+
+	\item Packet: packet size (Maximum transmission unit), IP addresses, (MTU), bit rate and packet arrival distribution,
+
+	\item Link: link Latency Delay, loss rates.
+
+\end{itemize}
+
+Swing take as input collected \textit{pcap} files.
+Botta at al.
+\cite{do-you-trust} argues that due its complexity, they are rarely used to conduct experimental researchers.
+Also, we can  justify due its overheads, since the performance of such complex traffic generator is limited\cite{legotg-paper}.
+The authors Vishwanat et al.
+\cite{swing-paper} cite that they have generated traces of about of 200 Mbps, about the same result found by \cite{legotg-paper}.
+In the other hand, D-ITG reached 9808 Mbps\cite{comparative-trafficgen-tools} in a link of 10 Gbps, but operating as a maximum throughput generator.
+
+Application level traffic generators may be realistic from a server operation system perspective, but are not able to represent real complex scenarios.
+Replay engines such as  TCPreplay and TCPivo have some limitation.
+First, they usually do not replicate the same inter-packet times form the original trace, just creates a constant bandwidth traffic.
+They also requere storage of \textit{pcap} files, wich may become huge for  long-term and high-speed traffic capture traces.
+Also, obtaining good traffic traces sometimes is hard, due privacy issues and limited sources.
 Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato.
@@
 For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK.
-Also, many of the listed traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.
+Many of the listed traffic generators provides their own high-level API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.
 

### 2017-12-01 Docs/PaperSimitar/header.tex
up

@@
 It is a well known fact that the type of traffic on network measurements matters.
-A realistic Ethernet have a different impact compared to constant traffic tools like Iperf, even with the same bandwidth.
-A burstier traffic may cause buffers overflows when a constant traffic does not, decrease on the measurement acuracy.
+A realistic Ethernet traffic have a different impact over a device compared to constant traffic (such as generated by Iperf), even with the same avarage bandwidth.
+A burstier traffic can cause more buffers overflows, increace losses and decrease on the measurement acuracy.
 The number of flows of a traffic may have an impact of flow-oriented nodes, such as SDN switches and controllers.
-Today in an scenario where software defined networks are going to play an essential role in the future of the networks, a depper validation of new technologies in order to guarantee the SLAs is crucial.
+Therefore, in an scenario where software defined networks are going to play an essential role in the future of the networks, a depper validation of new technologies in order to guarantee the SLAs is crucial.
 In this scenario we come with an anternative for realist traffic generation.
 Most of open-source realistic traffic generator tools have the modelling layer coupled to the traffic generator API, wich make it difficult to be update to newer lybraries, or require user programming and manual configuration.
-We propose a sollution called SIMITAR: SnIffing, ModellIng and TrAffic geneRation, that have a separated moddelling framework from the traffic generator, which is flow-oriented, and is autoconfigurable.
-It creates and use as imputs compact traces descriptos, XML files that describes all features of the traffics.
-Currently we are able to replicate with acuracy 
+We propose a sollution called SIMITAR: SnIffing, ModellIng and TrAffic geneRation, wich separetes the processes of data collection, modelling and traffic generation, is flow-oriented, and is autoconfigurable.
+It creates and use as imputs compact traces descriptos, XML files that model a network trace.
+Currently we are able to replicate with acuracy some applications traffics and the flow-level properties from the traffic.
 \end{abstract}

### 2017-12-02 Docs/PaperSimitar/body.tex
paper

@@
 
+%> SDN e NFV
+Emerging technologies such as SDN and NFV are  drastically changing  computer networks.
+But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}, since hardware solutions  have a much more predictable behavior.
+There is a demand for more reliable methods to ensure the Service Layer Agreements, over different types of loads.
+We can expect an even larger impact over over virtualized middle-boxes should be even larger compared to dedicated hardware devices, due the virtualization-layer extra overhead.
+Along with that, on Software Defined Networks we have the flow-based operation\cite{sdn-survey}.
+Each new flow arriving on an SDN switch demands an extra communication between it and the controller, wich may create a boobleneck.
+The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table.
+Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider.
+Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment.
+How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject.
 %Emerging technologies such as SDN and NFV are  drastically changing  computer networks.
@@
 How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject.
-Emerging technologies such as SDN and NFV are  drastically changing  computer networks.
-But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}, since hardware solutions  have a much more predictable behavior.
-There is a demand for more reliable methods to ensure the Service Layer Agreements, over different types of loads.
-We can expect an even larger impact over over virtualized middle-boxes should be even larger compared to dedicated hardware devices, due the virtualization-layer extra overhead.
-Along with that, on Software Defined Networks we have the flow-based operation.
-Each new flow arriving on an SDN switch demands an extra communication between it and the controller, wich may create a boobleneck.
-The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table.
-Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider.
-Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment.
-How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject.
 
@@
 
+%> sobre open-source traf gen
 The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}.
-Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.
-Traffic generators are commonly classified into four different groups\cite{do-you-trust}: application-level, flow-level, packet-level and multi-level traffic generators.
+Most of these tools were built for specific purposes and goals, each of them wiht diferent methods of traffic generation and enabling the controll of  different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, packet train periods, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.
+Traffic generators are commonly classified into four different groups, according to its layer of operation\cite{do-you-trust}: application-level, flow-level, packet-level and multi-level traffic generators.
 
-\textbf{Application-level traffic generators}: they try to emulate the behavior of network applications, simulating real workloads stochastically and/or responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool.
+%> Applucation-level
+\textbf{Application-level traffic generators} try to emulate the behavior of network applications, simulating real workloads stochastically and/or responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool.
 That means, the behavior of the output may change according to what packets have arrived in the network interface}.
 As examples we have Surge\cite{surge-paper} able to emulate the behavior of web clients and services.
-The behavior of such applications is, in general, based on request-response exchanges models.
 
-\textbf{Flow-level traffic generators}: they are able to configure and reproduce features of flows\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}.
+%> Flow-level
+\textbf{Flow-level traffic generators} are able to configure and reproduce features of flows\cite{do-you-trust}\cite{sourcesonoff-paper}, such as number of flows and flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}.
 Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from live routers.
 
-\textbf{Packet-level traffic generators}: most traffic generators available fall in this class.
+%> Packet-level
+\textbf{Packet-level traffic generators} is the most common  traffic generators class available.
 They are able to craft packets and inject into the network, and controll features like inter departure times (IDT), packet size(PS), throughput and packets per second\cite{validate-trafficgen}.
 \cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model based generators.
+On the other hand, offer the control for just a single flow each time, and if available will require scripting.
 Traffic Replay engines, such TCPreplay\cite{web-tcpreplay}, are  able to read packet capture files (\textit{pcap} files), and inject copies on a network interface.
@@
 
-\textbf{Multi-level traffic generators}: its proposal is to take into account existing interaction among each layer of the network stack, to create background network traffic as close as possible from reality.
-The most relevant tool of this class is Swing \cite{swing-paper}.
+%> multi-level
+\textbf{Multi-level traffic generators} have the porpose of  take into account existing interaction among each layer of the network stack, to create network traffic as close as possible from reality.
+The most relevant open-source  tool of this class is Swing \cite{swing-paper}.
 Swing take into account many points of each layer, using an approach based on randomness and responsiveness \cite{swing-paper}.
@@
 Swing is able to model things like\cite{swing-paper}:
-
 \begin{itemize}
-
 	\item User behavior: Number of request and responses, time between requests and responses;
-
 	\item Request and Responses: number of connections, time between start of connections;
-
 	\item Connection: Number of request and responses per connection, applications modeling (HTTP, P2P, SMTP), transport protocols TCP/UDP based on the application, response sizes, request sizes, user think between exchanges on a connection;
-
 	\item Packet: packet size (Maximum transmission unit), IP addresses, (MTU), bit rate and packet arrival distribution, 
-
 	\item Link: link Latency Delay, loss rates.
-
 \end{itemize}
-
-Swing take as input collected \textit{pcap} files.
-Botta at al.
-\cite{do-you-trust} argues that due its complexity, they are rarely used to conduct experimental researchers.
-Also, we can  justify due its overheads, since the performance of such complex traffic generator is limited\cite{legotg-paper}.
+Swing take as input collected \textit{pcap} files. Botta at al. \cite{do-you-trust} argues that due its complexity, they are rarely used to conduct experimental researchers. 
+% Also, we can  justify due its overheads, since the performance of such complex traffic generator is limited\cite{legotg-paper}.
 The authors Vishwanat et al.
@@
 
-Application level traffic generators may be realistic from a server operation system perspective, but are not able to represent real complex scenarios.
+%> limitações dos traffic gen
+Application level traffic generators may be realistic from a operation system perspective, but are not able to represent real complex scenarios.
 Replay engines such as  TCPreplay and TCPivo have some limitation.
@@
 Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato.
-Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen.
+Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen\cite{moongen-paper}.
 But all of them just offer a complet framework to be congfigured, but the customization of the traffic is all up to user to do.
@@
 
+%> low/high level APIs
 We also have available a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others.
@@
 
-Therefore we have a large variety open-source tools available for custom traffic generation.
+%> muitas ferramestas, mas dificil de gerar trafego realistico
+Indeed, we have a large variety open-source tools available for custom traffic generation.
 But reproducing a realistic traffic scenario is a hard question.
@@
 
-For this gap, there are some sollutions on the open source community.
-Tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration.
+%> Open source alternatives
+For this gap tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration and provide a realistc traffic generaion.
 Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}.
 But they have their issues as well.
-Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration.
+Harpoon does not configure parameters at packet level\cite{harpoon-validation} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration.
 Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}.
@@
 
+%> not automatic configuration
 Another issue is the large variety of tools, and different methods of configuration and limitations.
@@
 
-To meet the requirements presented in the section ~\ref{sec:introduction}, we will define our solution, and how it works.
-SIMITAR architecture is presented in the figure~\ref{fig:architecture}.
-It is composed of four components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator};  and a \textit{Network Traffic Generator}, as subsystem.
-We describe each part below.
+In this section we are going to present the SIMITAR architecture and operation.
+SIMITAR is composed of four components, as presented in the figure ~\ref{fig:architecture}:  the \textit{Sniffer}, a \textit{SQLite database}, the \textit{TraceAnalyzer}, and the \textit{FlowGenerator}.
+We explain each part down below.
 
@@
         \centering
-        \includegraphics[height=2.7in]{figures/architecture-diagram}
+        \includegraphics[width=\linewidth]{figures/architecture-diagram}
         \caption{Architecture of SIMITAR}
@@
 The listed header fields are inputs for a hash function, and its value is set on the ordered set which returns its order (index on the \textit{OrderedSet}).
-The index value is chosen as a packet flowID.
+The index value is chosen as a packet \textit{flowID}.
 
@@
 The \textit{Sniffer} and the \textit{TraceAnalyzer} components uses the database.
-We choose an SQLite database, because according to its specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it fits well our purposes.
-It is simple and well-suitable for an amount of data smaller than terabytes.
-In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from packets, along with the flowID calculated by the sniffer component.
+We choose an SQLite database, because according to its specifications it is simple and well-suitable for an amount of data smaller than terabytes \footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}.
+In the figure ~\ref{fig:simitar-database} we show the relational model of our database, which stores a set of features extracted from packets, along with the \textit{flowID} calculated by the sniffer component.
 
@@
 At the \textbf{session layer}, we use a deterministic approach for evaluating file transference time and times between files: ON/OFF times sequence of packet trains.
-We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.
+We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-validation}.
 We develop an algorithm called \textit{calcOnOff} responsible for estimating these times.
@@
 
+\subsection{Flow Generator}
+
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=\linewidth]{figures/trace-flow}
+	\caption{Class hierarchy of NetworkTrace and NetworkFlow, which enables the abstraction of the traffic generation model of the traffic generation engine.}
+	\label{fig:network-trace-flow-class-diagram}
+\end{figure}
+
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=\linewidth]{figures/alg-simplified-harpoon}
+	\caption{Simplified-harpoon emission algorithm}
+	\label{fig:alg-simplified-harpoon}
+\end{figure}
+
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=\linewidth]{figures/alg-traffic-engine-config}
+	\caption{Traffic engine configuration model}
+	\label{fig:alg-traffic-engine-config}
+\end{figure}
+
+The Flow Generator handles the data on the \textit{Compact Trace Descriptor} file, and use to retrieve parameters for traffic generation.
+It crafts and controls each flow in a separated thread.
+We already implemented this component using Iperf traffic generator and Libtins C++ API, and it must follow the calss hierarcy as presented in the figure ~\ref{fig:network-trace-flow-class-diagram}.
+This component was designed using the design pattern Factory, to simplify its expansion and support\footnote{If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow}, creating a new derived class (figure ~\ref{fig:network-trace-flow-class-diagram} ).
+On our current implementation we already have implemented \texttt{IperfFlow} and \texttt{TinsFlow}, and \texttt{DitgFlow} is under validation process.
+This new class has the requirement of not have any new attribute.
+The support for this new class must be given on the factory class \texttt{NetworkFlowFactory}.
+For closed loop packet-crafters (that means, tools which must establish a connection between the source and the destination), two methods must be implemented: \texttt{flowGenerate()} and \texttt{server()}.
+\texttt{flowGenerate()} is responsible for sending a \textit{file}, as defined on de figure~\ref{fig:modified-harpoon-model}, and \texttt{server()} to receive $n$ files.
+Open loop packet-crafters, such as we implemented using Libtins (just sent the packets, do not establishes a connection), the server do not need to be implemented.}.
+
+This component and therefore our traffic generator is a multi-layer workload generator according to the typing introduced on chapter ~\ref{ch:literature-review} \footnote{Since it works both at packet and flow level, but do not work at application level.}.
+At the flow-level, SIMITAR controls each flow using the algorithm at figure~\ref{fig:alg-simplified-harpoon}.
+This algorithm handles our model defined at the figure ~\ref{fig:modified-harpoon-model}.
+This procedure is independent of the underlying packet crafting tool used.
+It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps for \texttt{start\_delay} seconds.
+This is the arrival time of the first flow packet.
+Passed this time, it then calls the underlying traffic generation tool(defined as command line argument), and pass to it the flowID, file ON time, number of packets and number of bytes to be sent (file size), and network interface.
+Then it sleeps the next session OFF time.
+When the list of ON/OFF times from the flow is over, the thread ends.
+
+At the packet level, the job of our tool is to configure the underlying engine, to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}.
+This method must use the available parameters, attributes and \textit{getters} to configure and generate a thread-safe traffic using the method \texttt{flowGenerate()}.
+The \textit{file} configuration must follow the in the figure ~\ref{fig:alg-traffic-engine-config}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-12-04 Docs/Thesis/docs/chapter1.tex
up

@@
 %3nd-review
-\section{State of Affairs and Motivation}\label{sec:state-of-the-art}
+\section{Motivation}
 
@@
 If succeeding at large-scale, they would change drastically the development and operation of computer networks.
-But, especially on NFV, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}.
+However, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}.
 Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior.
@@
 
-\section{Open-source Solutions}
+\section{Related Work}
 
@@
 Some traffic generator tools offer support emulation of single application workloads.
-But this does not correspond to real complex scenarios.
+However, this does not correspond to real complex scenarios.
 Other tools work as packet replay engines, such as TCPreplay and TCPivo.
@@
 Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen.
-But all of them just offer a complet framework to be congfigured, but the customization of the traffic is all up to user to do.
+All of them offer a complex configuration framework, but its custumization is all up to the user.
 So, there is no simple way for the user to create an synthetic realistic traffic scenario.

### 2017-12-05 Docs/Thesis/docs/chapter3.tex
up

@@
 
-% ok1
+In this chapter, we will present our tool which aims to fill the gaps addressed in the chapter ~\ref{ch:introduction}.
+We call it \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}.
+This acronym summarizes its operation.
+SIMITAR is a traffic generator able to learn features of a real traffic automatically, and reproduce a synthetic traffic similar to the original.
+It records a model for the traffic in an XML file we call \textit{compact trace descriptor} (CTD file).
+As input-data SIMITAR can use \textit{pcap} files or real-time captures.
 
-In this chapter, we will present our tool which aims to fill the gaps addressed in the chapter ~\ref{ch:introduction}.
-It is called SIMITAR (SnIffing, ModellIng and TrAffic geneRation) and aims to generate a platform-agnostic traffic: it can use as traffic generator engine almost any traffic generator tools and programming API.
-It just requires a programming or command line interface.
-SIMITAR creates a  model in XML based on actual traces (\textit{pcaps} or real-time captures), we call Compact Trace Descriptor (CTD).
+\begin{figure*}[ht!]
+	\centering
+	\includegraphics[height=2.4in]{figures/ch1/layer-diagram}
+	\caption{ Architecture conceptual idea: a toll to automatize many tasks on traffic modelling and generation.}
+	\label{fig:layer-diagram}
+\end{figure*}
 
+On the figure ~\ref{fig:layer-diagram} we abstract our concepts we stated in a layer diagram model.
+Or tool must work as an interface for the user automatizing traffic modeling, configuration, and emulation and offering services of intelligence and traffic generatrion programmability.
+In the figure we also include packet-acceleration\footnote{Packet acceleration is a concept introduced by DPDK\cite{web-dpdk}, which means kernel by-pass.
+Packet acceleration optimizes the packet processing, and therefore traffic generation, enabling higher throughput rates.}, however, in the current version, this feature is not implemented, but how to do it is discussed in the section of future works in the chapter ~\ref{ch:conclusion}.
+
+Our primary goal is to offer simple configuration, with realism, at a reasonable speed.
+We are introducing the concept of programmability for traffic generation.
+Since the \textit{compact trace descriptor} is a XML file, the user may create his custom traffic in a platform agnostic way creating his own CTD file.
+The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.
+Instead of storing a huge file \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace.
+
+Then, we use this data as input for a traffic generator engine.
+We do so using APIs or creating new processes in a controlled manner.
+So will be possible to control packet parameters and flow's behavior in an automatized and self-configuring way.
+Using a component methodology, we decouple the traffic generation, from the data collection and parameterization process.
+Building it in this non-monolithic way,  enable a simple port for different traffic generators engines, what make our tools easy for updating with newer technologies.
+A project guideline is to reuse as much code and components as possible from the open-source community.
 We abstract its whole operation cycle in the figure ~\ref{fig:cycle-of-operation}.

### 2017-12-06 Docs/Thesis/docs/chapter1.tex
merge brench

@@
 
-Emerging technologies such as SDN and NFV are great promises.
-If succeeding at large-scale, they would change drastically the development and operation of computer networks.
+Emerging technologies such as SDN and NFV are great promises and would change drastically the development and operation of computer networks.
 However, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}.
@@
 It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.
-
 Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.
@@
 Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider.
-
 Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment.
@@
 
-Therefore we have a large variety open-source tools available for custom traffic generation.
-But reproducing a realistic traffic scenario is a hard question.
+We have a large variety open-source tools available for custom traffic generation, but reproducing a realistic traffic scenario is a hard question.
 Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}.
-But usually this is not the goal of the project, so the researcher or the them have scarce time available to work over it.
-Since it is usually is not the main goal of the project, but just a mean many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.
+Since it is usually is not the main goal of the project, but just a mean, many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.
 Reproducig a realistic traffic usung these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation.
-Since it usually is not the goal of the research, but a mean.
 
-For this gap, there are some sollutions on the open source community.
+There are fewer sollutions on the open source community available that aim to fill this gap.
 Tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration.
 Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}.
-But they have their issues as well.
+However they have their issues as well.
 Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration.
@@
 
-\section{\textit{SIMITAR}: SnIffing, ModellIng and TrAffic geneRation}
+\section{Problem Statement}
 
-\begin{figure*}[ht!]
-        \centering
-        \includegraphics[height=2.4in]{figures/ch1/layer-diagram}
-        \caption{ Architecture conceptual idea: a toll to automatize many tasks on traffic modelling and generation.}
-    \label{fig:layer-diagram}
-\end{figure*}
-
-In this section, we are going to present our solution discussed in this text.
-SIMITAR is a traffic generator able to learn features of a real traffic automatically, and reproduce a synthetic traffic similar to the original.
-It records a model for the traffic in an XML file we call Compact Trace Descriptor.
-
-But first we will formalize our research targets, and then define a requirement list for SIMITAR, that means, what we want it to do. The main research targets are:
+Based on what we stated,  we are going to formalize our research targets, and define que requet list to fulfill these gaps. Our main research targets in this work are:
 
@@
 
-We call our  tool \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}.
-This acronym summarizes its operation.
-Now, we are going to define a requirement list for our proposed software.
+Hence, we will define a requeriment list for the tool we are going to develop and present in this research:
 
@@
 
-	\item It must be able to extract data from a real traffic and store in a database. It must be able to obtain data from real-time traffics and from \textit{pcap} files;
+	\item Autoconfigurable: It must be able to extract data from a real traffic and store in a database, and use it to parametrize its traffic model.
+It must be able to obtain data from real-time traffics and from \textit{pcap} files;
 
-	\item It must have a flow-based abstract model for traffic generation, not attached to any specific technology. Then, its model should be parameterized using this stored data;
+	\item Technology independent: It must have a flow-based abstract model for traffic generation, not attached to any specific technology.
 
@@
 
-	\item Easy expansion: the traffic modeling and generation must be decoupled. Ideally, it must able to use as traffic generator engine any library or traffic generator tool;
+	\item Extensibility: the traffic modeling and generation must be decoupled. Ideally, it must able to use as traffic generator engine any library or traffic generator tool;
 
-	\item Easy to use: It must be simple to use. It has to take as input a Compact Trace Descriptor, just as a traffic replay engine (such as TCPreplay) would take a \textit{pcap} file;
+	\item Simple usage: It must be easy to use. It has to take as input a Compact Trace Descriptor, just as a traffic replay engine (such as TCPreplay) would take a \textit{pcap} file;
 
-	\item Traffic programmability: It must have what we call \textit{traffic generation progamability}.
+	\item Traffic generation programmability: It must have what we call \textit{traffic generation progamability}.
 The compact trace descriptor must be simple and easy to read.
@@
 
-	\item The traffic modeling and generation must be flow-oriented. Each flow must be modeled and generated separately.
+	\item Flow-oriented: The traffic modeling and generation must be flow-oriented. Each flow must be modeled and generated separately.
 
@@
 %\end{itemize}
-
-On the figure ~\ref{fig:layer-diagram} we abstract our concepts we stated in a layer diagram model.
-Or tool must work as an interface for the user automatizing traffic modeling, configuration, and emulation.
-Also should provide a service intelligence, programmability, and acceleration\footnote{Packet acceleration is a concept introduced by DPDK\cite{web-dpdk}, which means kernel by-pass.
-Packet acceleration optimizes the packet processing, and therefore traffic generation, enabling higher throughput rates.
-But, in the current version, this feature is not implemented, but its methodology is discussed in the section of future works in the chapter ~\ref{ch:conclusion}.}.
-
-Our primary goal is to offer simple configuration, with realism, at a reasonable speed.
-To do this, we are introducing the concept of programmability for traffic generation.
-With SIMITAR, the user may program its synthetic traffic in a platform agnostic way.
-The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.
-
-Instead of storing a huge file \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace.
-This tool will store the generalized set of parameters in a human and machine-readable XML file we call \textit{Compact Trace Descriptor} (\textit{CTD}).
-Then, we use this data as input for a traffic generator engine.
-We do so using APIs or creating new processes in a controlled manner.
-So will be possible to control packet parameters and flow's behavior in an automatized and self-configuring way.
-
-Using a component methodology, we decouple the traffic generation, from the data collection and parameterization process.
-Building it in this non-monolithic way,  enable a simple port for different traffic generators engines, what make our tools easy for updating with newer technologies.
-A project guideline is to reuse as much code and components as possible from the open-source community.
 

### 2017-12-07 Docs/Thesis/docs/chapter1.tex
update

@@
 Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato.
-Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen.
+Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper}, sourcesOnOff\cite{sourcesonoff-paper}, and MoonGen.
 All of them offer a complex configuration framework, but its custumization is all up to the user.
@@
 So The user may design his custom traffic by creating his own Compact Trace Descriptor, and create a traffic using many different tools, like Ostinato, D-ITG, Iperf, but not caring about how to proper configure each of them.
+In the table ~\ref{tab:related-work} we summarize our current scenario.
+
+\begin{table}[ht!]
+	\centering
+	\caption{Current scenario of traffic generation}
+	\scalebox{0.87}{
+	\begin{tabular}{cccccc}
+		\hline
+		\rowcolor[HTML]{9B9B9B} 
+		Sollution    & User Space  & Autoconfigurable & Realistic Traffic & Traffic Custumization & Extensibility \\ \hline
+		Harpoon      & \textbf{no} & yes              & yes               & yes                   & \textbf{no}   \\
+		\rowcolor[HTML]{C0C0C0} 
+		D-ITG        & yes         & \textbf{no}      & yes               & yes                   & \textbf{no}   \\
+		Swing        & yes         & yes              & yes               & \textbf{no}           & \textbf{no}   \\
+		\rowcolor[HTML]{C0C0C0} 
+		Ostinato     & yes         & \textbf{no}      & \textbf{no}       & yes                   & yes           \\
+		LegoTG       & yes         & \textbf{no}      & \textbf{no}       & yes                   & yes           \\
+		\rowcolor[HTML]{C0C0C0} 
+		sourcesOnOff & yes         & \textbf{no}      & yes               & yes                   & \textbf{no}   \\
+		Iperf        & yes         & \textbf{no}      & \textbf{no}       & yes                   & \textbf{no}   \\ \hline
+	\end{tabular}
+	}
+	\label{tab:related-work}
+\end{table}
 

### 2017-12-07 Docs/Thesis/docs/chapter2.tex
update

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Classes of traffic generator tools}
-
-The most common traffic generator taxonomy in the literature is about its abstraction level\cite{do-you-trust}.
+The most common traffic generator classification in the literature is about its abstraction level\cite{do-you-trust}.
 There are four groups: Application-level, flow-level, packet-level and multi-level traffic generators.
@@
 
-\subsubsection{According to its abstraction level}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{According to its abstraction level}
 
@@
 
-\subsubsection{According to its implementation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{According to its implementation}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overview of Network Traffic Modeling and Realistic Traffic Generation}
+\section{Network Traffic Modeling and Realistic Traffic Generation}
 
@@
 \section{Validation of Traffic Generator Tools}
+% techniques
 
-There are many possible validation technics for traffic generator tools found in the literature.
+There are many possible validation techniques for traffic generator tools found in the literature.
 Any of them have their own importance and application.

### 2017-12-07 Docs/Thesis/docs/chapter3.tex
update

@@
 On the figure ~\ref{fig:layer-diagram} we abstract our concepts we stated in a layer diagram model.
-Or tool must work as an interface for the user automatizing traffic modeling, configuration, and emulation and offering services of intelligence and traffic generatrion programmability.
-In the figure we also include packet-acceleration\footnote{Packet acceleration is a concept introduced by DPDK\cite{web-dpdk}, which means kernel by-pass.
+Or tool must work as an interface for the user automatizing traffic modeling, configuration, and emulation and offer services of intelligence and traffic generation programmability.
+In the figure, we also include packet-acceleration\footnote{Packet acceleration is a concept introduced by DPDK\cite{web-dpdk}, which means kernel by-pass.
 Packet acceleration optimizes the packet processing, and therefore traffic generation, enabling higher throughput rates.}, however, in the current version, this feature is not implemented, but how to do it is discussed in the section of future works in the chapter ~\ref{ch:conclusion}.
+To avoid confusions, we will refer to the underlying workload tool as packet generator engine/tool, and for SIMITAR as a traffic generator.
+Even if this packet generator may be a traffic generator itself (such as Iperf), on SIMITAR, its operates just on the packet-level, as we explain in the chapter ~\ref{ch:literature-review}, and our tool is a multi-layer traffic generator tool.
 
-Our primary goal is to offer simple configuration, with realism, at a reasonable speed.
-We are introducing the concept of programmability for traffic generation.
-Since the \textit{compact trace descriptor} is a XML file, the user may create his custom traffic in a platform agnostic way creating his own CTD file.
+Our primary goal is to offer simple configuration, with \textbf{realism}, at a reasonable speed.
 The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.
 Instead of storing a huge file \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace.
+We are also introducing the concept of \textbf{programmability}.
+Since the \textit{compact trace descriptor},  is an XML file, the user may create his custom traffic in a platform agnostic way creating his own CTD file.
+So the will be able to create multi-flow Ethernet workload not having to create many scripts for each tool or reading its documentation.
+A single description of the traffic will fit any supported packet generator.
+Using a component methodology, we decouple the packet generation, from the data collection and parameterization process.
+We developt it using the design pattern factory to make the extension easy for any packet generator engine.
 
-Then, we use this data as input for a traffic generator engine.
-We do so using APIs or creating new processes in a controlled manner.
-So will be possible to control packet parameters and flow's behavior in an automatized and self-configuring way.
-Using a component methodology, we decouple the traffic generation, from the data collection and parameterization process.
-Building it in this non-monolithic way,  enable a simple port for different traffic generators engines, what make our tools easy for updating with newer technologies.
-A project guideline is to reuse as much code and components as possible from the open-source community.
 We abstract its whole operation cycle in the figure ~\ref{fig:cycle-of-operation}.
@@
 It then breaks these data into different flows and uses this data to generate a set of parameters for our traffic model, using a set of algorithms.
-Finally, SIMITAR provides these parameters to a traffic generator engine and controls its packets injection.
+Finally, SIMITAR provides these parameters to a packet generator engine and controls its packets injection.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{SIMITAR Architecture}
-
-% ok1
 
@@
 \subsection{Sniffer}
-
-% ok1
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Trace Analyzer}
-
-% ok1
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Flow features}
-
-% ok1
 
@@
 Here, we will explain our simplified version, which is illustrated at figure~\ref{fig:modified-harpoon-model}.
-
 Harpoon uses a definition of each level, based on the measurement of SYN and ACK TCP flags.
@@
 In the \textbf{flow layer} the \textit{TraceAnalyzer} loads the flow arrival times from the database and calculates the inter-packet times within the flow context.
-
 At the \textbf{session layer}, we use a deterministic approach for evaluating file transference time and times between files: ON/OFF times sequence of packet trains.
@@
 All files within the same flow are considered to follow the same model.
-We delegate the control of the inter-packet times to the underlying workload engine tool.
+We delegate the control of the inter-packet times to the underlying packet generator engine.
 We ordered them, from the best to the worst.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Flow Generator}
@@
 	\includegraphics[height=3.0in]{figures/ch3/trace-flow}
-	\caption{Class hierarchy of NetworkTrace and NetworkFlow, which enables the abstraction of the traffic generation model of the traffic generation engine.}
+	\caption{Class hierarchy of NetworkTrace and NetworkFlow, which enables the abstraction of the traffic generation model of the packet generation engine.}
 	\label{fig:network-trace-flow-class-diagram}
@@
 	\includegraphics[height=4.0in]{figures/ch3/alg-traffic-engine-config}
-	\caption{Traffic engine configuration model}
+	\caption{Packet engine configuration method}
 	\label{fig:alg-traffic-engine-config}
@@
 It crafts and controls each flow in a separated thread.
-We already implemented this component using Iperf traffic generator and Libtins C++ API, and it must follow the calss hierarcy as presented in the figure ~\ref{fig:network-trace-flow-class-diagram}.
-This component was designed using the design pattern Factory, to simplify its expansion and support\footnote{If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow}, creating a new derived class (figure ~\ref{fig:network-trace-flow-class-diagram} ).
+We already implemented this component using Iperf and Libtins(C++ API) as packet generators.
+It must follow the class hierarcy as presented in the figure ~\ref{fig:network-trace-flow-class-diagram}.
+This component was designed using the design pattern Factory, to simplify its expansion and support\footnote{If the user wants to introduce support for a new packet generator engine, he just has to expand the class \texttt{DummyFlow}, creating a new derived class (figure ~\ref{fig:network-trace-flow-class-diagram} ).
 On our current implementation we already have implemented \texttt{IperfFlow} and \texttt{TinsFlow}, and \texttt{DitgFlow} is under validation process.
@@
 
-This component and therefore our traffic generator is a multi-layer workload generator according to the typing introduced on chapter ~\ref{ch:literature-review} \footnote{Since it works both at packet and flow level, but do not work at application level.}.
+This component itself is a multi-layer workload generator according to the typing introduced on chapter ~\ref{ch:literature-review} \footnote{Since it works both at packet and flow level, but do not work at application level.}.
 At the flow-level, SIMITAR controls each flow using the algorithm at figure~\ref{fig:alg-simplified-harpoon}.
@@
 This is the arrival time of the first flow packet.
-Passed this time, it then calls the underlying traffic generation tool(defined as command line argument), and pass to it the flowID, file ON time, number of packets and number of bytes to be sent (file size), and network interface.
+Passed this time, it then calls the underlying packet generator tool(defined as command line argument), and pass to it the flowID, file ON time, number of packets and number of bytes to be sent (file size), and network interface.
 Then it sleeps the next session OFF time.
@@
 
-At the packet level, the job of our tool is to configure the underlying engine, to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}.
+At the packet level, SIMITAR configures the packet-generator tool to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}.
 This method must use the available parameters, attributes and \textit{getters} to configure and generate a thread-safe traffic using the method \texttt{flowGenerate()}.
@@
 
-\subsection{Network Traffic Generator}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Network Packet Generator}
 
-A network traffic generator software that should provide its API or script interface for the \textit{FlowGenerator} component.
-With this tool, the user must be eble to send packets/traffic and controll atributes, such as sending time, bandwidht, number of packets, protocols, and so on.
+A network packet generator is a tool or lybrary that should provide its API or script interface\footnote{In the case of a tool with a available CLI, to use it as packet generator we must use functions such as \texttt{fork()} or \texttt{popen()}.
+For Iperf, we used \texttt{popen()}.} for the \textit{FlowGenerator} component.
+With this engine, the user must be eble to send packets and controll atributes such as sending time, bandwidth, number of packets, protocols, and so on.
 That means, any available parameter form the compact trace descriptor.
-If it does not have an API but an CLI, the user may have to use functions such as \texttt{fork()} or \texttt{popen()}.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Usage and Use Cases}
@@
 \begin{itemize}
-	\item \texttt{sniffer-cli.py};
-	\item \texttt{trace.db} (sqlite3 database);
-	\item \texttt{trace-analyzer}.
-	\item \texttt{simitar-gen} (traffic generator).
+	\item \textit{Sniffer}: \texttt{sniffer-cli.py};
+	\item \textit{Database}: \texttt{trace.db};
+	\item \textit{Trace Analyzer}: \texttt{trace-analyzer}.
+	\item \textit{Flow Generator}: \texttt{simitar-gen} (the actual traffic generator).
 \end{itemize}
 
-When it working as a sniffer, it stores data from the captured traffic in the sqlite3 database.
-It may work over a \textit{pcap} file or an Ethernet interface.
-Working as a trace a trace-analyzer, it receives the name of the trace as stored in the database, and creates an XML compact trace descriptor.
-The constants used in the modeling may be changed and provided as command line argument.
-If not, the default values will be used.
-As a traffic generator, it may work as a client or a server.
-Working as a server is necessary for closed-loop engines; tools that require establishing a connection before generating the traffic, such as Iperf and D-ITG.
+Down below we show some usage commands of SIMITAR's components.
+The \texttt{sniffer-cli.py} application creates a new trace entry on the database using the command option \texttt{new}.
+Then the \texttt{Trace Analyzer} is able to create a \textit{compact trace descriptor} using the same trace entry.
+We can change the constants used by the \textit{Trace Analyzer} by command line option.
+As a traffic generator (\texttt{simitar-gen}), SIMITAR may work as a client or a server.
+Working as a server is necessary for closed-loop packet-generator engines; tools that require establishing a connection before generating the traffic, such as Iperf and D-ITG.
 It will just work passively.
 Working as a client is acting as a traffic emitter.
-Open loop packet-crafter tools such as \textit{libtins} does not require server operation the send the traffic.
-In the case of closed-loop tools, the destination IP addresses must be explicitly given in the command line by the options \texttt{--dst-list-ip} or \texttt{--dst-ip}.
-Down below, we present simple examples of commands used to activate each operation mode.
+Open loop packet-crafter tools such as \textit{libtins} does not require server operation to send the traffic.
+In case of closed-loop tools, the destination IP addresses must be explicitly given in the command line by the options \texttt{--dst-list-ip} or \texttt{--dst-ip}.
 
@@
 
-# @ SIMITAR/sniffer/, execute to sniffer the eth0 interface, and create a trace entry called "intrig" in the database
+# @ SIMITAR/sniffer/, execute to sniff the eth0 interface, and create a trace entry called "intrig" in the database
 ./sniffer-cli.py new intrig live eth0
@@
 \end{minted}
+
+\begin{figure*}[ht!]
+	\centering
+	\includegraphics[height=2.4in]{figures/ch3/use-case}
+	\caption{Use case example of SIMITAR}
+	\label{fig:use-case}
+\end{figure*}
+
+An example of use case is presented in the figure ~\ref{fig:use-case}.
+A Device under test can be stressed using a combination of traffic generated by many clients and server pairs.
+In the case of an open-loop packet generator tool (such as in the Libtins implementation), the servers pairs are not necessary.
+Using passive network measures, such as Pathload and pathChirp \cite{swing-paper}, it is possible to measure statistics form the device under tests.

### 2017-12-07 Docs/Thesis/docs/chapter4.tex
update

@@
 In this chapter we are going to go in deep details on some implementations and modelling approaches mentioned in the last chapter.
-
-In the frist section, we are going to discuss our methodology for modelling inter pacekt times, and validade it as a good choise. The problem we want to adress are these one:
+In the frist section, we are going to discuss our methodology for modelling inter pacekt times, and validade it as a good choise.
+The problem we want to adress are these one:
 
@@
 
-	\item We have a set of empirical inter-packet times, and some aproximate stochastic models that describe it. We want to know what is the best, in a analyctical way.
+	\item We have a set of empirical inter-packet times, and some aproximate stochastic models that describe it. We want to know what is the best, in a analyctical way, avoiding human analyzis;
 
@@
 
-Many works have been made in second point on the literature, but not so many on the second. So we are proposing a model, and validating it.
-
-In the second section, we will describe breifely two others we used to calc flow's session ON and OFF times, and
+In the second section, we will describe and discuss the methods we used to estimate the packet-trains sizes (ON/OFF times), and to do the application classification.
+The calculation of the packet trains periods in our model is deterministic.
+The \textit{compact trace descriptor} stores the same ON and OFF times from each flow from the original traffic trace.
+The application classification is made by a match table of transport protocols and ports.
 
@@
 
-%2nd-review
-In this chapter, we propose a method automatizable by  software.
-We estimate many stochastic functions through many methodologies and select the best model through the AIC computation\cite{bic-aic-comparision}.
-Since generating random can be cost and have a bias, depending on the seed generator, we avoid these problems since our method is analytical.
-
-%2nd-review
-We made a brief bibliographic review of some related works on this topic.
-Then, we will present the traffic traces we are going to use in this chapter, and in the rest of our work.
-After we present or selected method for parameterization and fitting choice.
-To test our criteria quality, we define a validation method, based on cross-validations made by simulations.
-
-\subsection{Related Works}
-
-%2nd-review
 There are plenty of works on the literature which proposes new processes and methodologies for modeling times between packets and packet trains.
-
-%2nd-review
 Fiorini \cite{modeling-concurrent-heavy-tailed} presents a heavy-tailed ON/OFF model, which tries to represent a traffic generated by many sources.
@@
 They achieve analytical performance measurements using Linear Algebra Queueing Theory.
-
-%2nd-review
 Kreban and Clearwater\cite{hierarchical-dynamics-interarrival-times} presents a model for times between job submissions of multiple users over a super computer.
@@
 Lognormal fit well small values, but was poor on larger ones.
-
-%2nd-review
 Kronewitter\cite{optimal-scheduling-of-heavy-tailed-traffic} presents a model of scheduling traffic of many heavy-tail sources.
@@
 To estimate the shape parameter $\alpha$ they use linear regression.
+
+%2nd-review
+In this chapter, we propose a method automatizable by  software.
+We estimate many stochastic functions through many methodologies and select the best model through the AIC computation\cite{bic-aic-comparision}.
+Since generating random can be cost and have a bias, depending on the seed generator, we avoid these problems since our method is analytical.
+We show the traffic traces we are going to use in this chapter, and in the rest of our work.
+After we present or selected method for parameterization and fitting choice.
+To test our criteria quality, we define a validation method, based on cross-validations made by simulations.
 
@@
 
-\subsection{Methodology}
+\subsection{Modelling Methodology}
 
@@
 
-\subsubsection{Validation}
+\subsection{Modelling Method Validation}
 
@@
 
-\subsection{Results}
+\subsection{Modelling Results}
 
@@
 
-Also the order of the stochastic function tend to not differ much. We are able to conclude that using AIC or BIC as criteria for choosing models for inter-packet times is a good choise.
+We are able to conclude that using AIC or BIC as criteria for choosing models for inter-packet times is a good choise.
 
-Also, except by the Pareto function modeled using the Maximum likelihood method, have comparative results between the simulations and the AIC/BIC goes.
+Except by the Pareto function modeled using the Maximum likelihood method, have comparative results between the simulations and the AIC/BIC goes.
 The best fittings according to the AIC/BIC usually returned very accurate models, with a small error between the mean and fractal level, and correlation close to one.
@@
 
-Also, it is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurate fitting, what justify the application of the criteria in all new experiments.
+It is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurate fitting, what justify the application of the criteria in all new experiments.
 For example, Weibull usually performs pretty well, but in some cases, perform poorly, and in others may even diverge.
@@
 Models which the linear regression diverges, will have very high and positive BIC/AIC estimations, and will not stand as primary options.
+
+\section{ON/OFF Periods and Application classification}
 
@@
 
-\section{Others Algorithms and Methods}
-
-In this section we breef present another methods used by the \textit{TraceAnalyzer} component.
+In this section we breef show another methods used by the \textit{TraceAnalyzer} component.
 The first to calculate the session ON and OFF times.
 The second classify applications based on its tranport protocol and ports.
-In the table ~\ref{tab:mehtods} we summarize the stack of models used to create the Compact Trace Descriptor (CTD file).
-
-\subsection{On/Off Times estimation}
+In the table ~\ref{tab:methods} we summarize the stack of models used to create the Compact Trace Descriptor (CTD file).
 
@@
 
-\subsection{Application classification}
-
 We also developed an simple test to guess the application protocol, based on the port numbers and the tranport protocol used by each flow.
@@
 
-%\begin{table}[ht!]
-%	\centering
-%	\caption{Stack of models used to create the CTD file}
-%	\label{tab:mehtods}
-%	\begin{tabular}{|l|l|}
-%		\hline
-%		Layer & Method \\
-%		\hline
-%		Link Layer  & \multirow{3}{*}{Packets header's data} \\ \cline{1-1}\cline{3-3}
-%		
-%		Network Layer & \\ \cline{1-1}\cline{3-3}
-%		
-%		Transport Layer & \\ \hline
-%		
-%		Application Layer  & Application Match Table  \\ \hline
-%		
-%		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$  \\ 
-%
-%		%\cline{2-2}\cline{3-3}  
-%		& Algorithm: $stochasticModelFitting$ \\  \hline
-%
-%		Packet Sizes  & Algorithm: $stochasticModelFitting$ \\ \hline
-%
-%	\end{tabular}
-%\end{table}
+\section{Conclusion}
+
+In this section, we went on details on some methodologies mentioned in the chapter ~\ref{ch:architecture}.
+Here we avoid implementation and architecture concepts, and just discussed the methods.
+In this first section, we focused our research on develope a consistent method for automatic selection of stochastic functions for inter-packet times.
+Since we could not find any other methodology in the literature, we developt our own and tested if it is worth or not.
+The results showed our method satisfactory and had presented a reasonable prediction rate on the best functions.
+We now can ensure that it is a safe method and that AIC and BIC are good criterions for this sort of data.
+We abstracted this method in the algorithm ~\ref{alg:stochasticModelFitting}.
+In the second section, we also present the methods used to estimate packet trains periods (algorithm ~\ref{alg:calcOnOff}) and make the application classification (table ~\ref{tab:application-protocols}).
+In the table ~\ref{tab:methods}, the usage of each method is summarized.
+
+\begin{table}[ht!]
+	\centering
+	\caption{Methods used by each layer.}
+	\label{tab:methods}
+	\begin{tabular}{cc}
+		\hline
+		Layer                               & Method                                 \\ \hline
+		Link Layer                          & \multirow{3}{*}{Packets header's data} \\
+		Network Layer                       &                                        \\
+		Transport Layer                     &                                        \\
+		Application Layer                   & Application Match Table                \\
+		\multirow{2}{*}{Inter Packet Times} & Algorithm: $calcOnOff$                 \\
+		& Algorithm: $stochasticModelFitting$    \\
+		Packet Sizes                        & Algorithm: $stochasticModelFitting$    \\ \hline
+	\end{tabular}
+\end{table}
 

### 2017-12-07 Docs/Thesis/docs/chapter2.tex
update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Traffic generator tools}
+\section{Traffic generator tools}\label{sec:traffic-gen}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Network Traffic Modeling and Realistic Traffic Generation}
+\section{Network Traffic Modeling and Realistic Traffic Generation}\label{sec:modeling-traffic}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Validation of Traffic Generator Tools}
+\section{Validation of Traffic Generator Tools}~\ref{sec:validation-traffic-gen}
 % techniques
@@
 
+\section{Conclusions}
+
+In this chapter, we review and discussed some fundamental concepts of our research: network traffic generators, network traffic modeling, and network traffic generators validation.
+In the section ~\ref{sec:traffic-gen} we surveyed types of traffic generators, and a comparison between its considerable variability of features.
+It helped us to summarize and have a deep understanding of what is available today for use, and define its gaps.
+Also, it helped us to see find what tools and frameworks are possible for us to use.
+In the section ~\ref{sec:modeling-traffic} create a brief overview putting together efforts on network traffic modeling and realistic traffic generation.
+On modeling, we made a short historical summary of some critical points, and on realistic traffic generation, we discussed some reference tools.
+Finally, we revied methodologies for validation of traffic generator tools, presenting some study cases at the end.
+This survey worked as a reference for the definition of our methodology of evaluation.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-04-25 Docs/Thesis/docs/appendix/appendixB.tex
thesis update

@@
-\chapter{Traffic Generators Survay}
+\chapter{Traffic Generators Survey}
 \label{ap:traffic-gen-survey}
@@
 \end{table}
+
+\section{Validation of Ethernet traffic generators: some use cases}
+
+In this section we list some use cases of validation of Ethernet traffic generators.
+Our validation methods used on chapter~\ref{ch:modeling-evaluation} and~\ref{ch:validation} were based on them.
+We are going to present seven different study cases on validation of related traffic generators.
+They are Swing\cite{swing-paper}, Harpoon\cite{harpoon-paper}, D-ITG\cite{ditg-paper}, sourcesOnOff\cite{sourcesonoff-paper}, MoonGen\cite{moongen-paper}, LegoTG\cite{legotg-paper} and NFPA\cite{nfpa-paper}.
+
+\subsubsection{Swing}
+Swing\cite{swing-paper} is at present, one of the main references of realistic traffic generation.
+The authors extracted bidirectional metrics from a network link of synthetic traces.
+Their goals were to get realism, responsiveness, and randomness.
+They define realism as a trace that reflects the following characteristics of the original:
+
+\begin{itemize}
+	\item Packet inter-arrival rate and burstiness across many time scales;
+	\item Packet size distributions;
+	\item Flow characteristics as arrival rate and length distributions;
+	\item Destination IPs and port distributions.
+\end{itemize}
+
+The traffic generator uses a structural model the account interactions between many layers of the network stack.
+Each layer has many control variables, which is randomly generated by a stochastic process.
+They begin the parameterization, classifying tcpdump\cite{web-libpcap} \textit{pcap}  files with the data, they are able to estimate parameters.
+
+They validate the results using publicly available traffic traces, from Mawi\cite{web-mawi} and CAIDA\cite{web-caida}. On the paper, the author focuses on these validation metrics:
+
+\begin{itemize}
+	\item Comparison of estimated parameters of the original and swing  generated traces;
+	\item Comparison of aggregate and per-application bandwidth and packets per seconds ;
+	\item QoS metrics such as two-way delay and loss rates;
+	\item Scaling analysis, via Energy multiresolution energy analysis.
+\end{itemize}
+
+To the vast majority of the results, both original and swing traces results were close to each other.
+Thus,  Swing was able to match aggregate and burstiness metrics, per byte and per packet, across many timescales.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Harpoon}
+
+Harpoon\cite{harpoon-validation}\cite{harpoon-paper} is a traffic generator able to generate representative traffic at IP \textit{flow level}.
+It can generate TCP and IP with the same byte, packet, temporal and spatial characteristics measured at routers.
+Also, Harpoon is a self-configurable tool, since it automatically extracts parameters from network traces.
+It estimates some parameters from original traffic trace: file sizes, inter-connection times, source and destination IP addresses, and the number of active sessions.
+
+As proof of concept \cite{ harpoon-validation}, the authors compared statistics from original, and harpoon's generated traces.
+The two main types of comparisons: diurnal throughput, and for stochastic variable CDF and frequency distributions.
+Diurnal throughput refers to the average bandwidth variation within a day period.
+In a usual network, during the day the bandwidth consumption is larger, and at night smaller.
+Also, they compared:
+
+\begin{itemize}
+	\item CDF of bytes transferred per 10 minutes
+	\item CDF of packets transferred per 10 minutes
+	\item CDF of inter-connection time
+	\item CDF of file size
+	\item CDF of flow arrivals per 1 hour
+	\item Destination IP address frequency
+\end{itemize}
+
+In the end, they showed the differences in throughput evaluation of a Cisco 6509 switch/router using Harpoon and a constant rate traffic generator.  
+Harpoon was proven able to give close CDFs, frequency and diurnal throughput plots compared to the original traces.
+Also, the results demonstrated that Harpoon provides a more variable load on routers, compared to constant rate traffic.
+It indicates the importance of using realistic traffic traces on the evaluation of equipment and technologies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{D-ITG}
+
+D-ITG\cite{ditg-paper} is a network traffic generator, with many configurable features.
+The tool provides a platform that meets many emerging requirements for a realistic traffic generation.
+For example, multi-platform, support of many protocols, distributed operation, sending/receiving flow scalability, generation models, and analytical model based generation high bit/packet rate.
+You can see different analytical and models and protocols supported by D-ITG at table ~\ref{tab:trafficgen-list1}.
+
+We will focus on the evaluation of realism on analytical model parameterization.
+It is a synthetic replication of a LAN party of eight players of Age of Mythology \footnote{\href{https://www.ageofempires.com/games/aom/}{https://www.ageofempires.com/games/aom/}}.
+They have captured traffic flows during the party.
+Then, they modeled its packet size and inter-packet time distributions.
+They show that the synthetic traffic and the analytical model have similar curves of packet size and inter-packet time; thus it can approximate the empirical data.
+Also, the mean and the standard deviation of the bit rate of the empirical and synthetic data are similar.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{sourcesOnOff}
+
+Varet et al.
+\cite{sourcesonoff-paper} create an application implemented in C, called SourcesOnOff.
+It models the activity interval of packet trains using probabilistic distributions.
+To choose the best stochastic models, the authors have captured traffic traces using TCPdump.
+Then the developed tool can figure out what distribution (Weibull, Pareto, Exponential, Gaussian, etc.) fits better the original traffic traces.
+It uses the Bayesian Information Criterion (BIC) for distance assessment.
+It tests the smaller BIC for each distribution and selects it as the best choice.
+It ensured good correlation between the original and generated traces and self-similarity.
+
+The validation methods used on sourcesOnOff are: 
+\begin{itemize}
+	\item Visual comparison between On time and Off time of the original trace and the stochastic fitting;
+	\item QQplots, which aim to evaluate the correlation between inter-trains duration of real and generated traffic;
+	\item Measurement of Autocorrelation\footnote{
+		The autocorrelation functions measures the correlation between data samples $y_{t}$ and $y_{t + k}$, where $k =0, ..., K$, and the data sample $\{y\}$  is generated by a stochastic process.
+
+		According to \cite{book-time-series-analysis}, the autocorrelation for a lag $k$ is:
+
+		\begin{equation}
+		r_{k} = \frac{c_{k}}{c_{0}}
+		\end{equation}
+
+		where
+
+		\begin{equation}
+		c_{k} = \frac{1}{T - 1}\sum_{t = 1}^{T - k} (y_{t} - \bar{y})(y_{t+k} - \bar{y})
+		\end{equation}
+
+		and $c_{0}$ is the sample variance of the time series. 
+	} of the measured throughput of the real and synthetic traffic;
+	\item Hurst exponent computation of the real and the synthetic trace;
+\end{itemize}
+
+The results pointed to an excellent stochastic fitting, but better for On-time values.
+On the other hand, the correlation value of the QQplot was more significant on the Off time values (99.8\% versus 97.9\%).
+In the real and synthetic traces, the autocorrelation of the throughput remained between an upper limit of 5\%.
+Finally, the ratio between the evaluated Hurst exponent always remained smaller than 12\%.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{MoonGen}
+
+MoonGen\cite{moongen-paper} is a high-speed scriptable paper capable of saturating 10 GnE link with 64 bytes packets, using a single CPU core.
+The authors have built it over DPDK and LuaJit, enabling the user to have high flexibility on the crafting of each packet, through Lua scripts.
+It has multi-core support and runs on commodity server hardware.
+It can test latency with sub-microsecond precision and accuracy, using hardware timestamping of modern NICs cards.
+The Lua scripting API enable the implementation and high customization along with high-speed.
+This includes the controlling of packet sizes and control of inter-departure times.
+
+The authors evaluated this traffic generator focused on throughput metrics, rather than others.
+Also, they have small packet sizes (64 bytes to 256), since the per-packet costs dominate.
+In their work, they were able to surpass 15 Gbit/s with an XL710 40 GbE NIC.
+Also, they achieve throughput values close to the line rate with packets of 128 bytes, and 2 CPU cores.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{LegoTG}
+
+Bartlett et al.\cite{legotg-paper} implements a modular framework for composing custom traffic generation, called LegoTG.
+As argued by the authors (and by this present work), automation of many aspects of traffic generation is a desirable feature.
+The process of how to generate proper background traffic may become research by itself.
+Traffic generators available today offer a single model and a restricted set of features into a single code base, makes customization difficult.
+
+The primary purpose of their experiment is to show how LegoTG can generate background traffic, only.
+Also, it shows how realistic background traffic can influence research conclusions.
+The test chosen is one of the use cases proposed for Swing\cite{background-traffic-matter}, and it evaluates the error on bandwidth estimation of different measurement tools.
+It shows that LegoTG can provide secure and custom traffic generation.

### 2018-04-25 Docs/Thesis/docs/chapter1.tex
update
thesis update

@@
 
-Emerging technologies such as SDN and NFV are great promises and would change drastically the development and operation of computer networks.
-However, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}.
+Emerging technologies such as SDN and NFV can be considered great promises that would drastically change the development and operation of computer networks.
+However, its enabling technologies such as virtualization still pose challenges as for performance,  reliability, and security\cite{nfv-challenges}.
 Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior.
-Since it is expected virtualization to impact negatively on performance, these VNFs have to keep its degradation as small as possible.
-Guarantee the Service Layer Agreements on emerging scenarios is now a harder question.
-There is a demand for more reliable methods to ensure the SLAs, over different types of loads.
+Since it is expected that virtualization will affect performance negatively, these VNFs have to keep their degradation as small as possible.
+Therefore, guaranteeing the Service Layer Agreements becomes now a harder question.
+There is a demand for more reliable methods to ensure SLAs, over different types of loads.
 
 It is already a well-known fact that the type of traffic used on performing tests matters.
-Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption.
-It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of new technologies.
-There are many reasons for this behavior, which includes burstiness and packet sizes.
+Studies show that  realistic Ethernet traffic provides different and variable load characteristics on routers\cite{harpoon-validation}, even with the same average bandwidth consumption.
+This fact indicates that tests that employ constant bit rate traffic generator tools are not enough for a complete validation of new technologies.
+There are many reasons for this behavior, which includes a grater traffic burstiness and variable packet sizes.
 
-A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}, and  measurement accuracy\cite{legotg-paper} \cite{background-traffic-matter}.
-Another key question is how applications will deal with packets.
-It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}.
-A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.
+A burstier traffic can cause packet losses and buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}; thus degenerating network performance\footnote{Packet-trains periods and inter-packet times affect traffic burstiness}, and  measurement accuracy\cite{legotg-paper} \cite{background-traffic-matter}.
+Another key question is how applications will deal with packets, since it is a well-known fact that applications have a huge performance degradation in processing small packets\cite{comparative-trafficgen-tools}.
+A realistic synthetic traffic must not have a single one but rater use variable packet sizes \cite{packet-distribution-model}.
 
-Realistic workload generators are also essential security research\cite{ditg-paper}.
-Generation of realistic workloads is important in the evaluation of firewall middleboxes.
+Furthermore realistic workload generators are an essential security research\cite{ditg-paper}, since generation of realistic workloads is important for evaluation of firewall middleboxes.
 It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.
-Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.
+Over a virtualized enviroment a realistic workload is expected to have an even larger inpact.
 
-Another critical point is the flow-oriented operation of SDN networks.
-Each new flow arriving on an SDN switch demands an extra communication load between it and the controller.
-This may create a bottleneck between the switch and the controller.
-Also the SDN switches have a flow-oriented operation.
+Another critical point is the flow-oriented operation of SDN networks, in which each new flow arriving on an SDN switch demands an extra communication with the controller, that may cause a bottleneck.
 Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider.
@@
 The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}.
-Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.
+Most of these tools were built for specific purposes and goals, so that each uses different methods of traffic generation, and enable controll of different features, such as: bits/bytes per second; packets per seconds; packet-sizes; protocols, header or payload customization; inter-packet times and On/Off periods; starting and sending time; and emulation of applications, such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.
 
-Some traffic generator tools offer support emulation of single application workloads.
-However, this does not correspond to real complex scenarios.
+Some traffic generator tools offer support emulation of single application workloads, however, this does not correspond to real complex scenarios.
 Other tools work as packet replay engines, such as TCPreplay and TCPivo.
-Although in that way is possible to produce a realistic workload at high rates, it comes with some issues.
-First, the storage space required becomes huge for long-term and high-speed traffic capture traces.
-Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources.
+While is possible to produce a realistic workload at high rates using this tools, they comes with some drawbacks.
+Firstly, the storage space required becomes huge for long-term and high-speed traffic capture traces, lastly, obtaining good traffic traces is sometimes hard, due privacy issues and fewer good sources.
 
-Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato.
+Many tools support a larger set of protocols and high-throughput for traffic generation, such Seagull and Ostinato.
 Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper}, sourcesOnOff\cite{sourcesonoff-paper}, and MoonGen.
 All of them offer a complex configuration framework, but its custumization is all up to the user.
-So, there is no simple way for the user to create an synthetic realistic traffic scenario.
+So, there is no simple way for the user to create a synthetic and realistic traffic scenario.
 
-We also have available a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others.
-These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators.
+We also have a variety of APIs that enable the creation of traffic and custom packets, which include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others.
+These APIs provide a finer controll and customization over each packet, and are used to implement traffic generators.
 For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK.
-Also, many of the listed traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.
+In addition, many of the listed traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.
 
@@
 
-We have a large variety open-source tools available for custom traffic generation, but reproducing a realistic traffic scenario is a hard question.
+There is a  have a large variety of open-source tools available for custom traffic generation, but reproducing a realistic traffic scenario is a hard matter.
 Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}.
-Since it is usually is not the main goal of the project, but just a mean, many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.
-Reproducig a realistic traffic usung these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation.
+Since it usually is not the main goal of the project, but just a mean of validation, many times a simplistic and unrealistic solution is selected due the limited resources such as time and labor.
+Creating a realistic traffic through these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation.
 
-There are fewer sollutions on the open source community available that aim to fill this gap.
-Tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration.
-Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}.
+There are few solutions on the open source community available that aiming to fill this gap, such as Harpoon\cite{harpoon-paper} and Swing\cite{swing-paper}.They capture traces to set internal parameters, providing an easier configuration.
 However they have their issues as well.
 Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration.
-Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}.
-Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library.
-The only way of replacing the traffic engine is changing and recompiling the original code.
-This is clearly a hard task\cite{legotg-paper}, and an error prone activity.
-Again, we fall in the same problem a complex task that usually is not the goal of the project.
+Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic; so throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}.
+ecause its traffic generation engine is coupled to its modeling framework, you cannot opt to use a newer/faster packet generation library.
+The only way of replacing the traffic engine is changing and recompiling the original code which is a hard and  error prone activity\cite{legotg-paper}.
+Again, we fall in the same issue, a complex task that is usually not the goal of the project.
+In the table ~\ref{tab:related-work} we give a brief summary of what we have available on some open-source traffic-generators tools.
 
-Another issue is the large variety of tools, and different methods of configuration and limitations.
+% Another matter is the large variety of tools, and different methods of configuration and its limitations.
 To create a custom traffic, a user must read large manuals, and custom-design scripts.
@@
 		\rowcolor[HTML]{9B9B9B} 
-		Sollution    & User Space  & Autoconfigurable & Realistic Traffic & Traffic Custumization & Extensibility \\ \hline
+		Solution    & User Space  & Autoconfigurable & Realistic Traffic & Traffic Custumization & Extensibility \\ \hline
 		Harpoon      & \textbf{no} & yes              & yes               & yes                   & \textbf{no}   \\
@@
 
-	\item Research the main apporoaches and methods found of the literature to create model Ethernet traffic, and for realistic traffic generation.
+	\item Research the main apporoaches and methods found of the literature for realistic traffic generation.
 
-	\item Create a general method for modeling and parameterization of Ethernet traffic, aiming to mimic any traffic provided as input;
+	\item Create a general method for modeling and parameterization of Ethernet traffic;
 
-	\item Create a software able of \textit{learning} metrics from real network traffic, and based on the that reproduce it workload with similar (but not equal) characteristics, \textit{avoiding} the storage of \textit{pcap} files.
+	\item Create a self-configurable tool that observes and uses real network traffic, and try to mimic and reproduce its behavior characteristics, \textit{avoiding} the storage of \textit{pcap} files.
 
@@
 The compact trace descriptor must be simple and easy to read.
-In that way, the user may want to create his custom traffic, in a platform agnostic way.
+That way, the user may want to create his custom traffic, in a platform agnostic way.
 The traffic programmability must be flow-oriented;

### 2018-04-25 Docs/Thesis/docs/chapter2.tex
thesis update

@@
 
-In this chapter, we will review some topics from the literature that serve as a base for this whole work.
-We will define what is a traffic generator tool, and introduce a taxonomy that distinguishes them.
-After, we will present a survey of many available open-source and free traffic generators.
-We introduce each tool and then present a feature comparison between each of them.
-As far as we know, this is the extensible features comparison of traffic generators available so far in the literature.
-The first two sections are devoted to this topic.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{A Brief Survey on Traffic Generators}\label{sec:traffic-gen}
 
-In the third section we will overview network traffic modeling and realistic traffic generation.
-We will discuss stochastic models that used to describe the Internet traffic.
-Based on that we will discuss features a realistic traffic should have.
-We can count self-similarity and burstiness,  header fields, packet size and flow features.
+A traffic generator is a tool capable of creating and injecting packets into a computer network in a controlled way to generate a synthetic traffic \cite{validate-trafficgen}.
+There is a vast variety of traffic generators described on the literature \cite{validate-trafficgen} \cite{ditg-paper} and available in the open-source community\footnote{\href{http://www.icir.org/models/trafficgenerators.html}{http://www.icir.org/models/trafficgenerators.html}}.
+This is a consequence of an equally large amount of approaches for crafting synthetic traffic \cite{validate-trafficgen}.
 
-In the following section, we will make a discussion on validation of traffic generator tools.
-First, presenting the main approaches of validation made on literature.
-Then, we will discuss some validation study cases of related works, always introducing new concepts when needed.
+The development of new network generators tightly related with to the current needs of network environment, applications sets, and purpose of use \cite{validate-trafficgen}.
+For example, if we want to evaluate the performance limits of equipment or new technology, you may want to execute stress tests, at specific constant rates.
+In this case, maximum throughput traffic generator is more interesting.
+On the other hand, to test how it performs on an actual network environment, you should search for a tool that produces a stochastically realist profile.
+Or, if you have a more specific usage case, you may search for a traffic generator that emulates an application scenario such as a client and a network server\cite{surge-paper}.
 
-%Finally, we will present a short overview of new arriving network technologies: SDN and NFV.
-We will use them as use cases at the chapter ~\ref{ch:use-cases}.
-Also, we will present our motivations for this choice.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Traffic generator tools}\label{sec:traffic-gen}
-
-%2nd-review
-A traffic generator tool is a system capable of creating and injecting packets into a computer network in a controlled way to generate a synthetic traffic \cite{validate-trafficgen}.
-there is a huge variety of traffic generation tools described on the literature \cite{validate-trafficgen} \cite{ditg-paper} and available in the open-source community\footnote{\href{http://www.icir.org/models/trafficgenerators.html}{http://www.icir.org/models/trafficgenerators.html}}.
-This is a cause of many  different approaches and methodologies available to network traffic generator's developers \cite{validate-trafficgen}.
-
-%2nd-review
-%Also, previous research such as Oliver et al.
-\cite{flow-level-ip} have demonstrated that one unique statistical law cannot express all complexity of an original Internet trace (an Internet trace is an Internet traffic capture made over a network interface).
-So, just selecting a stochastic process for a traffic generator, do not guarantee realism.
-
-%2nd-review
-New network generators development is directly related with to the current needs of network environment, applications sets, and purpose of use \cite{validate-trafficgen}.
-According to the context, you may want to send as many packets as possible through an interface to  equipment stress .
-So, in this case, a maximum throughput traffic generator is more interesting.
-In others situations, you may want a stochastically realist profile.
-Or even a traffic generator that reflect a special scenario such as a specific application; for example a client and server exchanging data\cite{surge-paper}.
-In this case, the target would be to stress a server.
-Another possibility a huge variety of protocols available, or even support of new protocols.
-
-%2nd-review
-Alongside with the traffic generators, there are many APIs available.
-There are low-level APIs which enables direct packet injection, such as \textit{libpcap}\cite{web-tcpdump}, \textit{libtins}\cite{web-libtins}, DPDK\cite{web-dpdk} and the GNU C socket library\cite{web-socket}.
+Alongside with the variety of traffic generators, there are many APIs to create traffic.
+Some are low-level APIs which enables direct packet injection, such as \textit{libpcap}\cite{web-tcpdump}, \textit{libtins}\cite{web-libtins}, DPDK\cite{web-dpdk} and the GNU C socket library\cite{web-socket}.
 And there are high-level APIs, provided by traffic generator tools, such as D-ITG\cite{ditg-paper}, Ostinato\cite{web-ostinato} and MoonGen\cite{moongen-paper}.
-In this case they enable an easy custom traffic generation and statistics.
+In this case, they enable an easy custom traffic generation and statistics.
 Also, there are implementations of hardware-based traffic generators using NetFPGAs\footnote{\href{http://netfpga.org/site/\#/}{http://netfpga.org/site/\#/}}.
 
-%2nd-review
-In the literature there are many classifications of traffic generators\cite{sourcesonoff-paper}\cite{hybrid-traffic-gen}\cite{validate-trafficgen}\cite{do-you-trust}.
-Some tools may have some features compatible with one or more classes.
+There are many classifications of traffic generators\cite{sourcesonoff-paper}\cite{hybrid-traffic-gen}\cite{validate-trafficgen}\cite{do-you-trust}, and many have features that fall into more than one class.
 But classify them it is an efficient way to distinguish the difference between these tools.
-We will give two different taxonomies:
+We will cite here two:
 
-%2nd-review
 \begin{itemize}
@@
 There are four groups: Application-level, flow-level, packet-level and multi-level traffic generators.
-We present a diagram  ilustrating its concept at figure ~\ref{fig:layers-workload-tools}.
+We present a diagram illustrating its concept in figure ~\ref{fig:layers-workload-tools}.
 
@@
 
-\textbf{Application-level traffic generators}: they try to emulate the behavior of network applications, simulating real workloads stochastically and/or responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool.
-That means, the behavior of the output may change according to what packets have arrived in the network interface}.
-As examples we have Surge\cite{surge-paper} able to emulate the behavior of web clients and services.
-The behavior of such applications is, in general, based on request-response exchanges models.
+\textbf{Application-level traffic generators}: they try to emulate the behavior of network applications, simulating real workloads stochastically or responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool.
+That means the behavior of the output may change according to what packets have arrived in the network interface}.
+As examples, we have Surge\cite{surge-paper}, which emulates the communication between clients and web servers.
 
 \textbf{Flow-level traffic generators}: they are able to configure and reproduce features of flows\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}.
-Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from live routers.
+Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from  routers.
 
 \textbf{Packet-level traffic generators}: most traffic generators available fall in this class.
-They are able to craft packets and inject into the network, and controll features like inter departure times (IDT), packet size(PS), throughput and packets per second\cite{validate-trafficgen}.
-\cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model based generators.
-Traffic Replay engines, such TCPreplay\cite{web-tcpreplay}, are  able to read packet capture files (\textit{pcap} files), and inject copies on a network interface.
+They can craft and inject packets into the network, and control features like inter-departure times (IDT), packet size(PS), throughput and packets per second\cite{validate-trafficgen}.
+\cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model-based generators.
+Traffic Replay engines, such TCPreplay\cite{web-tcpreplay}, can read packet capture files (\textit{pcap} files), and inject copies on a network interface.
 Model-based generators, such D-ITG \cite{ditg-paper}, TG\cite{web-tg}, may have PS and IDT configured by the user.
@@
 Maximum throughput engines like Ostinato and Seagull are tools that the main goal is to perform end-to-end stress testing.
-Are included in this category generators that are able to craft packets from the link layer, like Brute, KUTE, and pktgen.
+Are included in this category generators that can craft packets from the link layer, like Brute, KUTE, and pktgen.
 
-\textbf{Multi-level traffic generators}: this is a more recent class of network traffic generator, and its proposal is to take into account existing interaction among each layer of the network stack, to create background network traffic as close as possible from reality.
-One of the most relevant tools we can found is Swing \cite{swing-paper}.
-Swing take into account many points of each layer, using an approach based on randomness and responsiveness \cite{swing-paper}.
-That means, it uses PS and IDT stochastic models, but also take into account flow and application layer behavior.
-Swing is able to model things like\cite{swing-paper}:
-
-\begin{itemize}
-
-\item User behavior: Number of request and responses, time between requests and responses;
-
-\item Request and Responses: number of connections, time between start of connections;
-
-\item Connection: Number of request and responses per connection, applications modeling (HTTP, P2P, SMTP), transport protocols TCP/UDP based on the application, response sizes, request sizes, user think between exchanges on a connection;
-
-\item Packet: packet size (Maximum transmission unit), IP addresses, (MTU), bit rate and packet arrival distribution,
-
-\item Link: link Latency Delay, loss rates.
-
-\end{itemize}
-
+\textbf{Multi-level traffic generators}: this is a more recent class of network traffic generator.
+They take into account existing interaction among each layer of the network stack, to create network traffic as close as possible to reality.
+Today, the most relevant tool is Swing \cite{swing-paper}.
 Swing take as input collected \textit{pcap} files.
@@
 \cite{do-you-trust} argues that due its complexity, they are rarely used to conduct experimental researchers.
-Also, we can  justify due its overheads, since the performance of such complex traffic generator is limited\cite{legotg-paper}.
-The authors Vishwanat et al.
-\cite{swing-paper} cite that they have generated traces of about of 200 Mbps, about the same result found by \cite{legotg-paper}.
-In the other hand, D-ITG reached 9808 Mbps\cite{comparative-trafficgen-tools} in a link of 10 Gbps, but operating as a maximum throughput generator.
+Also, due its complexity, its performance is limited\cite{legotg-paper}.
+
+% On the other hand, D-ITG reached 9808 Mbps\cite{comparative-trafficgen-tools} in a link of 10 Gbps, but operating as a maximum throughput generator.
 
@@
 
-\textbf{Software-only traffic generators}: Implementations of traffic generators completely independent of its running hardware platform. This comprehends most of traffic generator tolls.
+\textbf{Software-only traffic generators}: Implementations of traffic generators utterly independent of its running hardware platform. This implementation comprehends most of traffic generator tolls.
 
-\textbf{Software and hardware-dependent traffic generators}: Traffic generators implemented in software, but dependent of underlying hardware.
+\textbf{Software and hardware-dependent traffic generators}: Traffic generators implemented in software, but dependent on the underlying hardware.
 The most preeminent examples of this class are implemented over DPDK\cite{web-dpdk}.
 DPDK works directly on the NIC interface, avoiding overheads of the Operational System.
-As cited on its official website, this approach permits huge precision and speed in the timing of packets, since it is able to send and receive packets within less than 80 clock cycles.
+As cited on its official website, this approach permits huge precision and speed in the timing of packets, since it can send and receive packets within less than 80 clock cycles.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Validation of Traffic Generator Tools}~\ref{sec:validation-traffic-gen}
-% techniques
+\section{Validation of Traffic Generator Tools}~\label{sec:validation-traffic-gen}
 
-There are many possible validation techniques for traffic generator tools found in the literature.
-Any of them have their own importance and application.
-Magyesi and Szabó\cite{validate-trafficgen} presents an abstract of the main metrics validation metrics.
-The authors classify them in four categories: packet based metrics, flow based metrics, scaling characteristics and QoS/QoE related metrics.
-As suggested by other works\cite{swing-paper}, we state here that an synthetic traffic can be considered realistic, metrics of these four classes are close to measured on a real scenario.
-
+After the implementation of a traffic generator, it has to be validated. Thus, we need a set of proof of concepts to evaluate if it reached its purposes or not. 
+There are many validation techniques researchers have proposed over time, according to the traffic generator intended behavior.
+Magyesi and Szabó\cite{validate-trafficgen} presented on their work a survey of these techniques, grouped by type of metric.
+The authors classify them into four categories: packet based metrics, flow-based metrics, scaling characteristics and QoS/QoE related metrics.
+As suggested by other works\cite{swing-paper}, we state here that synthetic traffic can be considered realistic, metrics of these four classes are close to measured in a real scenario.
 Here we present a short review of each of these validation techniques.
-After that, we will present seven different study cases on validation of related traffic generators.
-They are Swing\cite{swing-paper}, Harpoon\cite{harpoon-paper}, D-ITG\cite{ditg-paper}, sourcesOnOff\cite{sourcesonoff-paper}, MoonGen\cite{moongen-paper}, LegoTG\cite{legotg-paper} and NFPA\cite{nfpa-paper}.
 
@@
 
-Flow based metrics are becoming more important since newer network elements, like SDN devices, are able of execute flow-based operations\cite{validate-trafficgen}\cite{sdn-survey}.
-Magyesi and Szabó\cite{validate-trafficgen} consider the most important flow metrics the flow size distribution and the flow volume.
-The flow volume are proportional to the number of flow instances and flow-based device should run simultaneously.
-And the flow sizes defines how much time each instance will run.
+Flow-based metrics are becoming more critical since newer network elements, like SDN devices, are able of executing flow-based operations\cite{validate-trafficgen}\cite{sdn-survey}.
+Magyesi and Szabó\cite{validate-trafficgen} consider the essential flow metrics the flow size distribution and the flow volume.
+The flow volume stands for the number of flows of traffic.
+The flow size distribution is a measure of the length of time and in size of data of each flow in network traffic.
+The flow volume is proportional to the number of flow instances that a flow-based device should run simultaneously.
+And the flow sizes defines how much time each of these instances will  run.
 
@@
 Due its non-stationary nature, traditional methods fail on extract useful information\cite{validate-trafficgen}.
-The first analysis made in that way were focus on the estimation of the Hurst exponent\cite{selfsimilar-ethernet}.
-They demonstrated the self-similar nature of the ethernet traffic.
-As explained before, a self-similar traffic should an Hust exponent $H$, such as $ 0.5 < H < 1$.
-Over the years, wavalet based analysis have become an efficient way of reveal correlations, bursts and scaling  nature of the ethernet traffic\cite{validate-trafficgen}.
-Many works found on the literature have used wavelet based analysis \cite{swing-paper}\cite{non-intrusive-wavelet}\cite{wavelet-analysis-long-range}.
+The first analysis made in that way focused on the estimation of the Hurst exponent\cite{selfsimilar-ethernet}.
+They demonstrated the self-similar nature of the Ethernet traffic.
+As explained before, self-similar traffic should a Hust exponent $H$, such as $ 0.5 < H < 1$.
+Over the years, wavelet-based analysis has become an efficient way of reveal correlations, bursts and scaling nature of the ethernet traffic\cite{validate-trafficgen}.
+Many works found on the literature have used wavelet-based analysis \cite{swing-paper}\cite{non-intrusive-wavelet}\cite{wavelet-analysis-long-range}.
 
@@
 \cite{non-intrusive-wavelet} and Abry and Veitch \cite{wavelet-analysis-long-range} offers an extensible explanation of wavelet-based scaling analysis (WSA) or wavelet multi-resolution energy analysis (WMA).
-Here, is presented a brief summary of the main information presented by these two works, which you should refer to, for further details.
+Here, is presented a summary of the primary information offered by these two works, which you should refer to, for further details.
 
@@
 
-If we take the differences, instead of the avarages, evaluate the so called \textit{details}.
+If we take the differences, instead of the averages, evaluate the so-called \textit{details}.
 
@@
 
-On energy wavelet multiresolution energy plots, we can capture three main different behavior, according to the scale.
+On energy wavelet multiresolution energy plots, we can capture three different main behavior, according to the scale.
 On \textbf{periodic time series}, the Energy values will be small.
@@
 Perfect \textbf{white noise time series} will maintain the same value of the energy function.
-So an approximately constant values for the energy function $E_{j}$ indicates white noise behavior (wich can be represented by a Poisson process\cite{poisson-white-noise}).
+So an approximately constant values for the energy function $E_{j}$ indicates white noise behavior (which can be represented by a Poisson process\cite{poisson-white-noise}).
 On \textbf{self-similar time series}, the energy function plot $\log(E_{j})$ will grow approximately linearly with the scale $j$.
@@
 Some recent works suggest the use of multi-fractal models, instead of the self-similar models (also called monofractal)\cite{validate-trafficgen}\cite{udp-flows-model}.
-Since there is a lack  on multiscaling analysis on the literature on validation of traffic generators, this approach will not be used in this work.
+Since there is a lack of multiscaling analysis on the literature on validation of traffic generators, this type of analysis will stay for future works.
 
@@
 
-Dependendin on the type of plot, some behavios of the empirical dataset, compared to the theoretical may be observed. In the figure ~\ref{fig:qqplot-tutorial} is presented a sumary.
+Dependent on how the plot behaves, some features of the empirical dataset compared to the theoretical can be observed. In the figure ~\ref{fig:qqplot-tutorial} is presented a summary.
 
@@
 
-For the point of view of a traffic generation, is interesting that the QoS and QoE metrics present similar values to the ones found on real scenarios.
-As stated by Magyesi and Szabó\cite{validate-trafficgen}, important QoS/QoE metrics on validation of workload tools are: Round trip Time values (RTT), avarage queue whaiting time and queue size.
-Still on queue size, self-similar traffic consumes router buffers faster than Poisson traffic\cite{multi-player-online-game-self-similarity}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Study cases}
-
-\subsubsection{Swing}
-Swing\cite{swing-paper} is at the present time, one of the main references of realistic traffic generation.
-The authors extracted bidirectional metrics from a network link of synthetic traces.
-Their goals were to get  realism, responsiveness, and randomness.
-They define realism as a trace that reflects the following characteristics of the original:
-
-\begin{itemize}
-\item Packet inter-arrival rate and burstiness across many time scales;
-\item Packet size distributions;
-\item Flow characteristics as arrival rate and length distributions;
-\item Destination IPs and port distributions.
-\end{itemize}
-
-The traffic generator uses a structural model the account interactions between many layers of the network stack.
-Each layer has many control variables, which is randomly generated by a stochastic process.
-They begin the parameterization, classifying tcpdump\cite{web-libpcap} \textit{pcap}  files with the data, they are able to estimate parameters.
-
-They validate the results using public available traffic traces, from Mawi\cite{web-mawi} and CAIDA\cite{web-caida}. On the paper, the author focuses on these validation metrics:
-
-\begin{itemize}
-\item Comparison of estimated parameters of the original and swing  generated traces;
-\item Comparison of aggregate and per-application bandwidth and packets per seconds ;
-\item QoS metrics such as two-way delay and loss rates;
-\item Scaling analysis, via Energy multiresolution energy analysis.
-\end{itemize}
-
-To the vast majority of the results, both original and swing traces results were close from each other.
-Thus,  Swing was able to match aggregate and burstiness metrics, per byte and per packet, across many time scales.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Harpoon}
-
-Harpoon\cite{harpoon-validation}\cite{harpoon-paper} is a traffic generator able to generate representative traffic at IP \textit{flow level}.
-It is able to generate TCP and IP with the same byte, packet, temporal and spatial characteristics measured at routers.
-Also, Harpoon is a self-configurable tool, since it automatically extracts parameters from network traces.
-It estimates some parameters from original traffic trace: file sizes, inter-connection times, source and destination IP addresses, and the number of active sessions.
-
-As proof of concept \cite{ harpoon-validation}, the authors compared statistics from original and harpoon's generated traces.
-The two main types of comparisons: diurnal throughput, and for stochastic variable CDF and frequency distributions.
-Diurnal throughput refers to the mean bandwidth variation within a day period.
-In a usual network, during the day the bandwidth consumption is larger, and at night smaller.
-Also, they compared:
-
-\begin{itemize}
-\item CDF of bytes transferred per 10 minutes
-\item CDF of packets transferred per 10 minutes
-\item CDF of inter-connection time
-\item CDF of file size
-\item CDF of flow arrivals per 1 hour
-\item Destination IP address frequency
-\end{itemize}
-
-At the end, they showed the differences on throughput evaluation of a Cisco 6509 switch/router using Harpoon and a constant rate traffic generator.  
-Harpoon was proven able to give close CDFs, frequency and diurnal throughput plots compared to the original traces.
-Also, the results demonstrated that Harpoon provide a more variable load on routers, compared to a constant rate traffic.
-It indicates the importance of using realistic traffic traces on the evaluation of equipment and technologies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{D-ITG}
-
-D-ITG\cite{ditg-paper} is a network traffic generator, with many configurable features.
-The tool provides a platform that meets many emerging requirements for a realistic traffic generation.
-For example, multi-platform, support of many protocols, distributed operation, sending/receiving flow scalability, generation models, and analytical model based generation high bit/packet rate.
-You can see different analytical and models and protocols supported by D-ITG at table ~\ref{tab:trafficgen-list1}.
-
-We will focus on the evaluation of realism on analytical model parameterization.
-It is a synthetic replication of a LAN party of eight players of Age of Mythology \footnote{\href{https://www.ageofempires.com/games/aom/}{https://www.ageofempires.com/games/aom/}}.
-They have captured traffic flows during the party.
-Then, they modeled its packet size and inter-packet time distributions.
-They show that the synthetic traffic and the analytical model have similar curves of packet size and inter-packet time, thus it can approximate the empirical data.
-Also, the mean and the standard deviation of the bit rate of the empirical and synthetic data are similar.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{sourcesOnOff}
-
-Varet et al.
-\cite{sourcesonoff-paper} creates an application implemented in C, called SourcesOnOff.
-It models the activity interval of packet trains using probabilistic distributions.
-To choose the best stochastic models, the authors have captured traffic traces using TCPdump.
-Then the developed tool is able to figure out what distribution(Weibull, Pareto, Exponential, Gaussian, etc) fits better the original traffic traces.
-It uses the Bayesian Information Criterion (BIC) for distance assessment.
-It tests the smaller BIC for each distribution, and selects it as the best choice.
-It ensures good correlation between the original and generated traces and self-similarity.
-
-The validation methods used on sourcesOnOff are: 
-\begin{itemize}
-\item Visual comparison between On time and Off time of the original trace and the stochastic fitting;
-\item QQplots, which aim to evaluate the correlation between inter-trains duration of real and generated traffic;
-\item Measurement of Autocorrelation\footnote{
-The autocorrelation functions measures the correlation between data samples $y_{t}$ and $y_{t + k}$, where $k =0, ..., K$, and the data sample $\{y\}$  is generated by an stochastic process.
-
-According to \cite{book-time-series-analysis}, the autocorrelation for a lag $k$ is:
-
-\begin{equation}
-r_{k} = \frac{c_{k}}{c_{0}}
-\end{equation}
-
-where
-
-\begin{equation}
-c_{k} = \frac{1}{T - 1}\sum_{t = 1}^{T - k} (y_{t} - \bar{y})(y_{t+k} - \bar{y})
-\end{equation}
-
-and $c_{0}$ is the sample variance of the time series. 
-} of the measured throughput of the real and synthetic traffic;
-\item Hurst exponent computation of the real and the synthetic trace;
-\end{itemize}
-
-The results pointed to a good stochastic fitting, but better for On time values.
-On the other hand, the correlation value of the QQplot was bigger on the Off time values (99.8\% versus 97.9\%).
-In the real and synthetic traces, the autocorrelation of the throughput remained between an upper limit of 5\%.
-Finally, the ratio between the evaluated Hurst exponent always remained smaller than 12\%.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{MoonGen}
-
-MoonGen\cite{moongen-paper} is a high-speed scriptable paper capable of sature  10 GnE link with 64 bytes packets, using a single CPU core.
-The authors have built it over DPDK and LuaJit, enabling the user to have high flexibility on the crafting of each packet, through Lua scripts.
-It has multi-core support and runs on commodity server hardware.
-It is able to test latency with sub-microsecond precision and accuracy, using hardware timestamping of modern NICs cards.
-The Lua scripting API enable the implementation and high customization along with high-speed.
-This includes the controlling of packet sizes and control of inter-departure times.
-
-The authors evaluated this traffic generator focused on throughput metrics, rather than others.
-Also, they have small packet sizes (64 bytes to 256), since the per-packet costs dominate.
-In their work, they were able to surpass 15 Gbit/s with an XL710 40 GbE NIC.
-Also, they achieve throughput values close to the line rate with packets of 128 bytes, and 2 CPU cores.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{LegoTG}
-
-Bartlett et al.\cite{legotg-paper} implements a modular framework for composing custom traffic generation, called LegoTG.
-As argued by the authors (and by this present work), automation of many aspects of traffic generation is a desirable feature.
-The process of how to generate a proper background traffic may become a research by itself.
-Traffic generators available today offer a single model and a restricted set of features into a single code base, makes customization difficult.
-
-The main purpose of their experiment is to show how LegoTG is able to generate background traffic, in a simple way.
-Also, it shows how a realistic background traffic can influence on research conclusions.
-The experiment chosen is one of the use cases proposed for Swing\cite{background-traffic-matter}, and its evaluate the error on bandwidth estimation of different measurement tools.
-It shows that LegoTG is able eble to provide easy and custrom traffic generation.
+For the point of view of a traffic generation, is interesting that the QoS and QoE metrics present similar values to the ones found in real scenarios.
+As stated by Magyesi and Szabó\cite{validate-trafficgen}, important QoS/QoE metrics on validation of workload tools are Roundtrip Time values (RTT), average queue waiting time and queue size.
+Still, on queue size, self-similar traffic consumes router buffers faster than Poisson traffic\cite{multi-player-online-game-self-similarity}.
 
@@
 In the section ~\ref{sec:modeling-traffic} create a brief overview putting together efforts on network traffic modeling and realistic traffic generation.
-On modeling, we made a short historical summary of some critical points, and on realistic traffic generation, we discussed some reference tools.
-Finally, we revied methodologies for validation of traffic generator tools, presenting some study cases at the end.
-This survey worked as a reference for the definition of our methodology of evaluation.
+On modeling, we made a short historical summary of some critical points, and on practical traffic generation, we discussed some reference tools.
 
@@
 \cite{instrumentation-framework-nfv} create a web-based framework for NFV instrumentation in bare-metal and embedded level, but the source code is not provided.
-\cite{nfv-benchmarking-fault} implement some usage cases of NFVIs (Network Function Virtualization Infrastructures) based on fault injection.
+\cite{nfv-benchmarking-fault} implement some use cases of NFVIs (Network Function Virtualization Infrastructures) based on fault injection.
 \cite{nfpa-paper} implement an open-source tool, called NFPA, focusing on benchmarking of Network Functions.

### 2018-04-25 Docs/Thesis/docs/chapter3.tex
update
thesis update

@@
 This acronym summarizes its operation.
-SIMITAR is a traffic generator able to learn features of a real traffic automatically, and reproduce a synthetic traffic similar to the original.
+SIMITAR is a traffic generator able to learn features of real traffic automatically, and reproduce synthetic traffic similar to the original.
 It records a model for the traffic in an XML file we call \textit{compact trace descriptor} (CTD file).
@@
 Our primary goal is to offer simple configuration, with \textbf{realism}, at a reasonable speed.
-The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.
+The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the purpose of the project in an illustrative way.
 Instead of storing a huge file \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace.
@@
 Since the \textit{compact trace descriptor},  is an XML file, the user may create his custom traffic in a platform agnostic way creating his own CTD file.
-So the will be able to create multi-flow Ethernet workload not having to create many scripts for each tool or reading its documentation.
+So the user will be able to create multi-flow Ethernet traffic not having to build many scripts for each tool or reading its documentation.
 A single description of the traffic will fit any supported packet generator.
@@
 Also, it makes use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}.
-The listed header fields are inputs for a hash function, and its value is set on the ordered set which returns its order (index on the \textit{OrderedSet}).
+The listed header fields are inputs for a hash function.
+The hash value is then added to the ordered set which returns its order (index on the \textit{OrderedSet}).
 The index value is chosen as a packet flowID.
@@
 
-Some unique per-flow features are directly measured from the data. They are:
+We measure some flow-features directly from data. They are:
 
@@
 Each one of these parameters is unique per flow.
-Other features like PSD (packet size distribution) e IPT (Inter-packet time), have a more complex behavior.
+Other features like packet-size distribution and inter-packet times follow probability distributions.
 To represent these characteristics, we will use sets of stochastic-based models.
@@
 
-To represent inter-packet times, we adopt a simplified version of the Harpoon's traffic model.
+To represent inter-packet times, we adopt a modified version of the Harpoon's traffic model.
 A deep explanation of the original model can be found at \cite{harpoon-paper} and \cite{harpoon-validation}.
-Here, we will explain our simplified version, which is illustrated at figure~\ref{fig:modified-harpoon-model}.
 Harpoon uses a definition of each level, based on the measurement of SYN and ACK TCP flags.
@@
 The distinction is made based on the time delay between packets.
+For our purposes, the advantage of this strategy is that the evaluation of the packet-train is not attached to a specific protocol.
+We illustrate this behavior in the figure~\ref{fig:modified-harpoon-model}.
 
-In our algorithm simplified version, we define three different layers of data transference to model and control: file, session, and flow.
-For SIMITAR, a file is just a sequence of consecutive packets transmitted continuously, without large interruption of traffic.
-It can be, for example, packets sent downloading a file, packets from a  UDP  connection or a single ICMP echo packet.
+In our algorithm, we define three different layers of data transference to model and control: \textit{file}, \textit{session}, and \textit{flow}.
+For SIMITAR, a \textit{file} is a sequence of consecutive packets transmitted continuously, without long interruption of traffic.
+A file can be, for example, packets from download, a UDP   connection or a single ICMP echo packet.
 The session-layer refers to a sequence of multiple files transmitted between a source and a destination, belonging to the same flow.
@@
 We will enter into deeper details on this methodology on the chapter ~\ref{ch:modeling-evaluation}.
-The methodology of selection is presented in the figure~\ref{fig:model-parameterization}, and all constants and modes of operation can be changed by command line options.
+We present the methodology of selection in the figure~\ref{fig:model-parameterization}.
+All these constants and modes of operation are modifiable via command-line options.
 
@@
 Since the majority of packet size distribution found on real measurements are bi-modal \cite{packet-distribution-model}\cite{sourcesonoff-paper}\cite{udp-flows-model}, we first sort all packet sizes of flow in two modes.
-We define a packet size mode cut value of 750 bytes, same value adopted by \cite{udp-flows-model}.
+We define a packet-size cut value of 750 bytes, same value adopted by \cite{udp-flows-model}.
 
@@
 Since self-similarity does not make sense for packet-sizes, we prefer to use just the simpler models.
-When there is no packet for a model, we set a flag NO\_MODEL, and when there is just a single packet we just use the constant model.
+When there is no packet for a model, we set a flag NO\_MODEL, and when there is only a single packet, we use the constant model.
 Then calculate the BIC and AIC for each, but we decide to set the constant model as the first.
@@
 \subsubsection{Compact Trace Descriptor}
-%<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<
 
@@
 We already implemented this component using Iperf and Libtins(C++ API) as packet generators.
-It must follow the class hierarcy as presented in the figure ~\ref{fig:network-trace-flow-class-diagram}.
-This component was designed using the design pattern Factory, to simplify its expansion and support\footnote{If the user wants to introduce support for a new packet generator engine, he just has to expand the class \texttt{DummyFlow}, creating a new derived class (figure ~\ref{fig:network-trace-flow-class-diagram} ).
+It must follow the class hierarchy as presented in the figure ~\ref{fig:network-trace-flow-class-diagram}.
+This component was designed using the design pattern Factory, to simplify its expansion and support\footnote{If the user wants to introduce support for a new packet generator engine, he has to expand the class \texttt{DummyFlow}, creating a new derived class (figure ~\ref{fig:network-trace-flow-class-diagram} ).
 On our current implementation we already have implemented \texttt{IperfFlow} and \texttt{TinsFlow}, and \texttt{DitgFlow} is under validation process.
 This new class has the requirement of not have any new attribute.
-The support for this new class must be given on the factory class \texttt{NetworkFlowFactory}.
+The support for this new class must be implemented on the factory class \texttt{NetworkFlowFactory}.
 For closed loop packet-crafters (that means, tools which must establish a connection between the source and the destination), two methods must be implemented: \texttt{flowGenerate()} and \texttt{server()}.
 \texttt{flowGenerate()} is responsible for sending a \textit{file}, as defined on de figure~\ref{fig:modified-harpoon-model}, and \texttt{server()} to receive $n$ files.
-Open loop packet-crafters, such as we implemented using Libtins (just sent the packets, do not establishes a connection), the server do not need to be implemented.}.
+For packet-crafter that support open-loop traffic\footnote{just sent the packets, do not establishes a connection}, such as the one we implemented using Libtins, the server side not needs to be implemented.}.
 
@@
 At the flow-level, SIMITAR controls each flow using the algorithm at figure~\ref{fig:alg-simplified-harpoon}.
-This algorithm handles our model defined at the figure ~\ref{fig:modified-harpoon-model}.
+This algorithm handles our model defined in the figure ~\ref{fig:modified-harpoon-model}.
 This procedure is independent of the underlying packet crafting tool used.
 It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps for \texttt{start\_delay} seconds.
-This is the arrival time of the first flow packet.
+The \texttt{start\_delay} is the arrival time of the first flow packet.
 Passed this time, it then calls the underlying packet generator tool(defined as command line argument), and pass to it the flowID, file ON time, number of packets and number of bytes to be sent (file size), and network interface.
@@
 At the packet level, SIMITAR configures the packet-generator tool to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}.
-This method must use the available parameters, attributes and \textit{getters} to configure and generate a thread-safe traffic using the method \texttt{flowGenerate()}.
+This method must use the available parameters, attributes and \textit{getters} to configure and generate thread-safe traffic using the method \texttt{flowGenerate()}.
 The \textit{file} configuration must follow the in the figure ~\ref{fig:alg-traffic-engine-config}.
@@
 
-A network packet generator is a tool or lybrary that should provide its API or script interface\footnote{In the case of a tool with a available CLI, to use it as packet generator we must use functions such as \texttt{fork()} or \texttt{popen()}.
+A network packet generator is a tool or library that should provide its API or script interface\footnote{In the case of a tool with an available CLI, to use it as packet generator we must use functions such as \texttt{fork()} or \texttt{popen()}.
 For Iperf, we used \texttt{popen()}.} for the \textit{FlowGenerator} component.
-With this engine, the user must be eble to send packets and controll atributes such as sending time, bandwidth, number of packets, protocols, and so on.
+With this engine, the user must be able to send packets and control attributes such as sending time, bandwidth, number of packets, protocols, and so on.
 That means, any available parameter form the compact trace descriptor.
@@
 # @ SIMITAR/trace-analyzer/, execute this command to create two Compact Trace Descriptors, called intrig.ms.xml and intrig.sec.xml.
-The first is parameterized using milisecons, and de second, uses seconds as time unity.
+The first is parameterized using milliseconds, and de second uses seconds as time unity.
 ./trace-analyzer --trace intrig
@@
 A Device under test can be stressed using a combination of traffic generated by many clients and server pairs.
-In the case of an open-loop packet generator tool (such as in the Libtins implementation), the servers pairs are not necessary.
+In the case of an open-loop packet generator tool (such as in the Libtins implementation), the servers and clients pairs are not necessary.
 Using passive network measures, such as Pathload and pathChirp \cite{swing-paper}, it is possible to measure statistics form the device under tests.

### 2018-04-25 Docs/Thesis/docs/chapter4.tex
update
thesis update

@@
 
-In this chapter we are going to go in deep details on some implementations and modelling approaches mentioned in the last chapter.
-In the frist section, we are going to discuss our methodology for modelling inter pacekt times, and validade it as a good choise.
-The problem we want to adress are these one:
+In this chapter, we are going to go into deep details on some implementations and modeling approaches mentioned in the last chapter.
+In the first section, we are going to discuss our methodology for modeling inter packet-times and validate it as a good choice.
+The problem we want to address are these:
 
@@
 
-	\item We have a set of empirical inter-packet times, and some aproximate stochastic models that describe it. We want to know what is the best, in a analyctical way, avoiding human analyzis;
+    \item We have a set of empirical inter-packet times, and some approximate stochastic models that describe it. We want to know what is the best analytically, avoiding human analysis;
 
-	\item We whant to know whatever if our modelling aproaches are good ot not to describe inter pacekt times.
+    \item We want to know whatever if our modeling approaches are suitable or not to describe inter-packet times.
 
@@
 
-\subsection{About Inter packet time and packet trains modelling}
+\subsection{About Inter packet time and packet trains modeling}
 
@@
 But studies made by Leland et al.\cite{selfsimilar-ethernet} showed that the Ethernet traffic has a self-similar and fractal nature.
-Even if they are able to represent the randomness of an Ethernet traffic, simple Poisson processes can't express traffic "burstiness" in a long-term time scale, such as traffic "spikes" on long-range "ripples".
-This is an indicative of the fractal and self-similar nature of the traffic, that usually we express by distributions with infinite variance, called heavy-tailed.
+Even if they can represent the randomness of Ethernet traffic, simple Poisson processes can't express traffic "burstiness" on a long-term time scale, such as traffic "spikes" on long-range "ripples".
+These characteristics are an indication of the fractal and self-similar nature of the traffic, that usually we express by distributions with infinite variance, called heavy-tailed.
 Heavy-tail means that a stochastic distribution is not exponentially bounded\cite{sourcesonoff-paper}.
@@
 
-There are plenty of works on the literature which proposes new processes and methodologies for modeling times between packets and packet trains.
-Fiorini \cite{modeling-concurrent-heavy-tailed} presents a heavy-tailed ON/OFF model, which tries to represent a traffic generated by many sources.
+There are plenty of works in the literature which proposes new processes and methodologies for modeling times between packets and packet trains.
+Fiorini \cite{modeling-concurrent-heavy-tailed} presents a heavy-tailed ON/OFF model, which tries to represent traffic generated by many sources.
 The model emulates a multiple source power-tail Markov-Modulated (PT-MMPP) ON/OFF process, where the ON times are power-tail distributed.
 They achieve analytical performance measurements using Linear Algebra Queueing Theory.
-Kreban and Clearwater\cite{hierarchical-dynamics-interarrival-times} presents a model for times between job submissions of multiple users over a super computer.
-They show that the Weibull probability functions are able to express well small and high values of inter-job submission times.
+Kreban and Clearwater\cite{hierarchical-dynamics-interarrival-times} presents a model for times between job submissions of multiple users over a supercomputer.
+They show that the Weibull probability functions can express well small and high values of inter-job submission times.
 They also tested exponential, lognormal and Pareto distributions.
 Exponential distribution couldn't represent long-range values because it fell off too fast and Pareto was too slow.
-Lognormal fit well small values, but was poor on larger ones.
+Lognormal fit well small values, but was weak on larger ones.
 Kronewitter\cite{optimal-scheduling-of-heavy-tailed-traffic} presents a model of scheduling traffic of many heavy-tail sources.
@@
 %2nd-review
-In this chapter, we propose a method automatizable by  software.
+In this chapter, we propose a method automatically by software.
 We estimate many stochastic functions through many methodologies and select the best model through the AIC computation\cite{bic-aic-comparision}.
-Since generating random can be cost and have a bias, depending on the seed generator, we avoid these problems since our method is analytical.
-We show the traffic traces we are going to use in this chapter, and in the rest of our work.
-After we present or selected method for parameterization and fitting choice.
+Since generating random can be costly and have a bias, depending on the seed generator, we avoid these problems since our method is analytical.
+We show the traffic traces we are going to use in this chapter, and in the rest of our work, and then present or selected method for parameterization and fitting choice.
 To test our criteria quality, we define a validation method, based on cross-validations made by simulations.
@@
 %2nd-review
-We start defining also define the \textit{pcaps} datasets we are going to use in the rest of this text. We will use for datasets, and for reproduction purposes, three are public available. 
+We start defining also define the \textit{pcaps} datasets we are going to use in the rest of this text. We will use for datasets, and for reproduction purposes, three are publicly available. 
 The first is a lightweight Skype capture, found in  Wireshark wiki\footnote{https://wiki.wireshark.org/}, and can be found at \href{https://wiki.wireshark.org/SampleCaptures}{https://wiki.wireshark.org/SampleCaptures}.
@@
 The third we capture in our laboratory LAN, through a period of 24 hours.
-It was captured irewall gateway between our local and external network.
+It was captured firewall gateway between our local and external network.
 Along with other tests, We intend to verify diurnal behavior on it.
@@
 %2nd-review
-The fourth is a capture of a busy private network access point to the Internet, available on-line on TCPreplay website \footnote{ \href{http://tcpreplay.appneta.com/wiki/captures.html}{http://tcpreplay.appneta.com/wiki/captures.html}}, and is called \texttt{bigFlows.pcap}.
+The fourth is a capture of a busy private network access point to the Internet, available online on TCPreplay website \footnote{ \href{http://tcpreplay.appneta.com/wiki/captures.html}{http://tcpreplay.appneta.com/wiki/captures.html}}, and we call it \texttt{bigFlows.pcap}.
 We will refer to it \textit{bigflows-pcap}.
@@
 Then, we estimate a set of parameters for stochastic functions, using different methodologies.
-Then, from these parametrized models, we estimate which best represent our data set, using the measure of quality AIC (Akaike information criterion).
-We also calculate another measure of quality called BIC(Bayesian information criterion), for comparison of results.
+Then, from these parametrized models, we determine which best represent our data set, using the measure of quality AIC (Akaike information criterion).
+We also calculate another ratio of quality called BIC (Bayesian information criterion), for comparison of results.
 In this chapter, we present our results obtained on our prototype implemented in Octave\footnote{ \href{https://www.gnu.org/software/octave/}{https://www.gnu.org/software/octave/}}.
@@
 % In probability theory and statistics, the exponential distribution (a.k.a.
-negative exponential distribution) is the probability distribution that describes the time between events in a Poisson process, i.e.
-a process in which events occur continuously and independently at a constant average rate.
+negative exponential distribution) is the probability distribution that describes the time between events in a Poisson process, i.e., a process in which events occur continuously and independently at a constant average rate.
 It is a particular case of the gamma distribution.
-It is the continuous analogue of the geometric distribution, and it has the key property of being memoryless.
+It is the continuous analog of the geometric distribution, and it has the crucial property of being memoryless.
 In addition to being used for the analysis of Poisson processes, it is found in various other contexts.
@@
 Since the time samples resolution used were of $10^{-6}$s, all values equal to zero were set to  $5\cdot10^{-8}$s, to avoid division by zero.
-To avoid divergence on tangent operation on the linearization the Cauchy function, the inter-packets CDF function values were floor-limited and upper-limited to  $10^{-6}$ and $0.999999$ respectively.
+To avoid divergence in tangent operation used in the linearization of the Cauchy function, we floor-limited and upper-limited the inter-packet CDF  values by  $10^{-6}$ and $0.999999$, respectively.
 We implemented this prototype using Octave.
@@
 
-Using the gradient descendant, we find a estimation of the linear coefficients $\hat{a}$ and $\hat{b}$.
-Using the inverse function of linear coefficients, we find the weibull estimated parameters $\hat{\alpha}$ and $\hat{\beta}$.
+Using the gradient descendant, we find an estimation of the linear coefficients $\hat{a}$ and $\hat{b}$.
+Using the inverse function of linear factors, we see the Weibull estimated parameters $\hat{\alpha}$ and $\hat{\beta}$.
 
@@
 In the table~\ref{tab:linearization-sumary} we present a summary of the used equations in the procedure.
-In this notation, the subscript $i$ means that it must be applied on every empirical value measured.
+In this notation, the subscript $i$ means that it must be applied to every value measured empirically.
 The hat( $\widehat{}$ ) indicates an estimated value for a parameter.
@@
 %2nd-review
-The expected value $E(X)$ and variance $Var(X)$ of a random variable $X$ of some distributions are close related with its parameters.
+The expected value $E(X)$ and variance $Var(X)$ of a random variable $X$ of some distributions are closely related to its parameters.
 Since the mean $\bar{\mu}$ and its standard deviation $\bar{\sigma}$ are in general good approximations for the expected value and variance, we use them to estimate parameters.
@@
 %2nd-review
-To see if our criterion of parameter selection is actually is able to find which is the best model, we define a validation methodology. 
-We generate a vector with the same size form the original, with random generated data through our model estimation.
+To see if our criterion of parameter selection is can find which is the best model, we define a validation methodology. 
+We generate a vector with the same size form the original, with randomly generated data through our model estimation.
 Then we compare it with the original sample, trough four different metrics, all with a confidence interval of 95\%:
@@
 \item Hurst exponent;
-\item Mean inter packet time;
-\item Standard deviation of inter packet times.
+\item Mean inter-packet time;
+\item Standard deviation of inter-packet times.
 \end{itemize}
@@
 0 means no linear correlation.
-So, as close the result reach 1, more similar are the inter-packet times to the original values.
+So, as close the result reaches 1, more similar are the inter-packet times to the original values.
 To estimate it, we use the Octave's function \texttt{corr()}.
@@
 As explained before in the chapter~\ref{ch:literature-review}, the Hurst exponent is meter self-similarity and indicates the fractal level of the inter-packet times.
-As close the result is from the original, more similar is the fractal level of the estimated samples from the original.To estimate this value we use the function \texttt{hurst()} from Octave, which uses rescaled range method.
+As close the result is from the original, more similar is the fractal level of the estimated samples from the original.
+To determine this value, we use the function \texttt{hurst()} from Octave, which uses rescaled range method.
 Finally we measure the mean and the standard deviation (as a measure of the dispersion), using the Octave's functions \texttt{mean()} and \texttt{std()}.
@@
 %2nd-review
-As close the correlation, Hurst exponent, mean and the standard deviation is from the original dataset, the better is model fitting.
-Also, analyzing the mean, we can see if a certain modeling procedure tends to be more penalized for the values close, or far from zero.
-This means that if the mean inter-packet time tends to be smaller or higher compared to the original.
+As close the correlation, Hurst exponent, average and the standard deviation is from the original dataset, the better is model fitting.
+Also, analyzing the average, we can see if a particular modeling procedure tends to be more penalized for the values close, or far from zero.
+This means that if the average inter-packet time tends to be smaller or higher compared to the original.
 
 %2nd-review
-With these results in hands, we can see if AIC and BIC are good criteria for model selection for inter-packet times.
+With these results in hands, we can see if AIC and BIC are reasonable criteria for model selection for inter-packet times.
 To quantitatively check it, we define a cost function based on the correlation, Hurst exponent and mean.
@@
 %2nd-review
-Being $Cr$ the vector of correlations ordered from the greater to the smaller.
-Let $Me$ and $Hr$ defined by the absolute difference between mean and hurt exponent of the estimated values and the original dataset.
+Being $Cr$ the vector of correlations ordered from greater to the smaller, let $Me$ and $Hr$ defined by the absolute difference between average and hurt exponent of the estimated values and the original dataset.
 Both are ordered from the smaller to the greatest values.
-Letting $\phi(V, M)$ be an operator wich gives the position of a model $M$ in a vector $V$, we define the cost function $J$ as:
+Letting $\phi(V, M)$ be an operator which gives the position of a model $M$ in a vector $V$, we define the cost function $J$ as:
 
@@
     \centering
-	\caption{Results of the octave prototype, include BIC and AIC values, para estimated parameters for two of our pcap traces: \textit{skype-pcap }and \textit{bigflows-pcap}.
+    \caption{Results of the octave prototype, include BIC and AIC values, para estimated parameters for two of our \textit{pcap} traces: \textit{skype-pcap }and \textit{bigflows-pcap}.
 \textit{bigflows-pcap} is much larger, and has a much much smaller mean inter-packet time}
@@
 
-Here in this chapter we only discuss the plots achived obtained by the pcap \textit{skype-pcap} for simplicity.
+Here in this chapter we only discuss the plots achieved obtained by the \textit{pcap} \textit{skype-pcap} for simplicity.
 The other plots are provided and commented on the appendix ~\ref{ap:aditional-plots}.
 In the figure ~\ref{fig:aproximation-original-cdf} we present all estimated CDF functions along with the empirical CDF, for the trace \textit{skype-pcap}.
-They are on logscale, wich provide a better visualization for small time scales.
-In the case of the normal function, all values smaller than zero, were set to zero on the plot.
+They are on log-scale, which provide a better visualization for small time scales.
+In the case of the normal function, all values smaller than zero were set to zero on the plot.
 Is possible to see different accuracies and types of fittings on each plot.
@@
 
-Analyzing the plots, and what they would mean, our Cauchy fitting would impose an almost contant traffic , with the inter packet time close to the mean.
-On the trace \textit{skype-pcap} the exponential plots seems to not represent well the small values of inter packet times.
-This is due fact that an exponential process is good at representing values close to the mean.
+Analyzing the plots, and what they would mean, our Cauchy fitting would impose almost constant traffic, with the inter-packet time close to the mean.
+On the trace \textit{skype-pcap} the exponential plots seems not to represent well the small values of inter-packet times.
+This is due fact that an exponential process is good at describing values close to the average.
 But, it fails to represent values too small and higher.
-On the other hand, a self-similar process like Weibull and Pareto are better representing inter packet times with higher dispersion.
-Pareto(MLH) has a slow convergence, wich means this distribution may genarate values of inter-packet times too large.
+On the other hand, a self-similar process like Weibull and Pareto are better serving inter-packet times with higher dispersion.
+Pareto(MLH) has a slow convergence, which means this distribution may generate values of inter-packet times too large.
 
-Analyzing the QQplots, we may observe that in most of the distribution, the samples (original data) has a much havier-tail effect than in the estimated data.
-This is verified by the almost blue horizontal lines formed by the "exes".
-But, the Weibull distribution follow much closer the original data.
+Analyzing the QQplots, we can observe that in most of the distribution, the samples (original data) has a much havier-tail effect than in the estimated data.
+We can verify this by the by the almost blue horizontal lines formed by the x-marks.
+But, the Weibull distribution follows much closer the original data.
 Also is possible to see that the sample has a right skew compared to the estimation on Exponential(LR), Exponential(Me), Normal, and Pareto(MLH).
-This means that this estimation would not represent so well small values of time in this case.
+This "right-skew" means that this estimation would not represent so well small values of time in this case.
 On the other hand, Pareto(LR) and Weibull would not suffer from this problem.
 
-The results for the AIC, BIC and parameters of all four traces are at the table~\ref{tab:prototype-results}.
+The results for the AIC, BIC, and parameters of all four traces are at the table~\ref{tab:prototype-results}.
 The results for \textit{wan-pcap} and \textit{lan-diurnal-pcap} are on the table ~\ref{tab:prototype-results}.
-The difference between BIC and AIC values in all simulations are very small.
-Much smaller then the difference of these values between the distributions.
-This is an indication that for inter packet times, using AIC or BIC should will not influence significantly the results.
+The differences between BIC and AIC values from a same stochastic function all cases are small compared to the difference between their values calculated between different distributions.
+Since we compared many different types of Ethernet traces, this result indicates that for inter-packet times, use AIC or BIC as decision criteria should not influence the results from most of the cases.
 
 On our previsions, Weibull and Pareto(MLH and LR) are the best options.
-This was expected, since both are heavy-tailed functions.
-But Cauchy on most of the tests, even being a heavy-tailed distribution, seems to no present a good fitting.
-This is effect of the fast divergence of tangent function, when we linearize our data.
+We expected that since both are heavy-tailed functions.
+But Cauchy on most of the tests, even being a heavy-tailed distribution, seems to no present a proper fitting.
+The quick divergence of the tangent function is the cause for this lousy fitting.
 
-Analyzing the quality of AIC and BIC as criterion of choose on \textit{skype-pcap},based on the results form figure ~\ref{fig:correlation-hurst-skype-pcap} we see that in therms of Correlation and Self-similarity it picket the right model: Weibull.
-Also in therms of mean packet rate and dispersion it is still one of the best choises (along with Exponential(Me), Pareto(LR) and Cauchy).
+Analyzing the quality of AIC and BIC as criteria of choose on \textit{skype-pcap}, based on the results form figure ~\ref{fig:correlation-hurst-skype-pcap} we see that concerning Correlation and Self-similarity it picked the right model: Weibull.
+Also regarding average packet rate and dispersion, it is still one of the best choices (along with Exponential(Me), Pareto(LR) and Cauchy).
 The third and the fourth choices (Pareto(LR)) and Exponential(LR) also are good options in most of these metrics.
@@
 Another important observation is the fact that exponential function was able to provide the best fitting for the \textit{wan-pcap}.
-The reasons for this behavior are both result of a much intense traffic with no long-range gaps, and the precision of the measurement.
+The reasons for this behavior are both results of a much great traffic with no long-range gaps, and the precision of the measurement.
 
@@
 
-We are able to conclude that using AIC or BIC as criteria for choosing models for inter-packet times is a good choise.
+We can conclude that using AIC or BIC as criteria for choosing models for inter-packet times is a good choice.
 
@@
 The best fittings according to the AIC/BIC usually returned very accurate models, with a small error between the mean and fractal level, and correlation close to one.
-The models selected as the worsts usually returned poor results.
+The models selected as the worsts traditionally yielded poor results.
 
 It is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurate fitting, what justify the application of the criteria in all new experiments.
-For example, Weibull usually performs pretty well, but in some cases, perform poorly, and in others may even diverge.
+For example, Weibull usually plays pretty well, but in some cases, perform poorly, or may even diverge.
 
 We do not rely on only one type of parameterization.
-This turns our methodology more robust, since a linear regression may diverge.
+This approach turns our methodology more robust, since a linear regression may diverge.
 But always there will be a peaceable model, since our estimations for Normal, Exponential (Me) and Pareto (MLH) cannot.
-Models which the linear regression diverges, will have very high and positive BIC/AIC estimations, and will not stand as primary options.
+Models which the linear regression diverges will have very high and positive BIC/AIC estimations, and will not stand as primary options.
 
@@
 
-In this section we breef show another methods used by the \textit{TraceAnalyzer} component.
+In this section, we briefly show another method used by the \textit{TraceAnalyzer} component.
 The first to calculate the session ON and OFF times.
-The second classify applications based on its tranport protocol and ports.
+The second classify applications based on its transport protocol and ports.
 In the table ~\ref{tab:methods} we summarize the stack of models used to create the Compact Trace Descriptor (CTD file).
 
-We developed an algorithms to calculate the times between the ON and OFF times of the \textit{files}, and the number of packets and bytes as well.
-It uses a list of packet arrival times(relative to the first), time between packets and packet sizes.
+We developed an algorithm to calculate the times between the ON and OFF times of the \textit{files}, and the number of packets and bytes as well.
+It uses a list of packet arrival times(relative to the first), the time between packets and packet sizes.
 It defines a minimum time of ON acceptable.
-This times is used for two reasons:
+These times are used for two reasons:
 
 \begin{itemize}
-\item In case of a \textit{file} of just one packet, it will not produce a On time of zero
-\item It avoid a \textit{file} On time too small, wich may be less than acceptable for packet generator tools.
+\item In case of a \textit{file} of just one packet, it will not produce an ON-time of zero
+\item It avoids a \textit{file} On time too small, which may be less than acceptable for packet generator tools.
 \end{itemize}
@@
 As explained in the previous chapter, a \textit{file} is defined by a large OFF time, we call $cutTime$.
-If a inter packet $deltaTime$ time is larger than the $cutTime$ it defines an OFF time, and the ON time is calculated base on the last OFF time recorded.
-If the first $deltaTime$ defines an OFF time, or if it is the first ON time, its calculation is threated separetely.
+If an inter-packet $deltaTime$ time is larger than the $cutTime$ it defines an OFF time, and the ON time is calculated base on the last OFF time recorded.
+If the first $deltaTime$ defines an OFF time, or if it is the first ON time, its calculation is treated separately.
 In the last ON time, it is not defined by an OFF time, so we deal with it after the loop.
-It keep counters to calc the number of bytes and packets within every defined ON time.
+It keeps counters to calc the number of bytes and packets within every defined ON time.
 It returns four vectors: $onTimes$, $offTimes$, $pktCounter$ and $fileSize$.
@@
 
-We also developed an simple test to guess the application protocol, based on the port numbers and the tranport protocol used by each flow.
-We currently are classifing the application protocols presented in the table ~\ref{tab:application-protocols}.
-If a flow matches the port number, and the transport protocol, it is classified as belongig to an application protocol.
+We also developed a simple test to guess the application protocol, based on the port numbers and the transport protocol used by each flow.
+We currently are classifying the application protocols presented in the table ~\ref{tab:application-protocols}.
+If a flow matches the port number, and the transport protocol, it is classified as belonging to an application protocol.
 
-\section{Conclusion}
+\section{Conclusions}
 
@@
 
-%\subsection{Software Engineering process and Lessons Leaned}
+%\subsection{Software Engineering process and Lessons Learned}
 
@@
 
-%We can conclude by this evaluation, that our chosen methodology for selecting stochastic models for inter packet data is appropriated. The first thing to observe is that, for a high
+%We can conclude by this evaluation, that our chosen methodology for selecting stochastic models for inter-packet data is appropriated. The first thing to observe is that, for a high
 
@@
 This turns our methodology more robust, since a linear regression may diverge.
-But aways there will be an packable model, since our estimations for Normal, Exponential(Me) and Pareto(MLH) cannot.
+But always there will be a packable model, since our estimations for Normal, Exponential(Me) and Pareto(MLH) cannot.
 Models wich the linear regression diverge, will not have god BIC/AIC estimations, and will not be picked.
@@
 We will present curves obtained by our Matlab prototype that shows in detail how each step works.
-After explaining this process, we will present an evaluation method of our results, using \textit{QQplots}.
+After explaining this process, we will display an evaluation method of our results, using \textit{QQplots}.
 After this, we give some details of how we convert code from Matlab to C++ and its benefits on time execution.
-All code used in this section is available on our GitHub page, on the directory \texttt{Prototypes}.
+All code used in this section is available on our GitHub page, in the directory \texttt{Prototypes}.
 
 %We also define here the datasets we are going to use in the rest of this text.
-We will use two datasets, and for reproduction purposes, one is public available.
+We will use two datasets, and for reproduction purposes, one is publicly available.
 The first is a CAIDA\footnote{http://www.caida.org/home/}{http://www.caida.org/home/}, and can be found at  \href{https://data.caida.org/datasets/passive-2016/equinix-chicago/20160121-130000.UTC}{https://data.caida.org/datasets/passive-2016/equinix-chicago/20160121-130000.UTC}.
@@
 
-%After we implement this models, we where able to get different approximations for the stochastic functions.
-To evaluate how well the method is able to fit inter packet times, we first test it against a whole set of inter packet times.
+%After we implement this model, we were able to get different approximations for the stochastic functions.
+To evaluate how well the method can fit inter-packet times, we first test it against a whole set of inter-packet times.
 Figures (...) represents the CDF fitting for the function for the \textit{skype-pcap}.
-In the apendix ~\ref{ap:mathematical-modeling}, we also present the fitting achieved for whole set of inter-packet times, and for a single selected flow of \textit{caida-pcap} and\textit{lan-diurnal-pcap} \textit{pcaps} .
-We are able to see that the Weibull approximation fits better then any exponential approximation.
+In the appendix ~\ref{ap:mathematical-modeling}, we also present the fitting achieved for whole set of inter-packet times, and for a single selected flow of \textit{caida-pcap} and\textit{lan-diurnal-pcap} \textit{pcaps} .
+We can see that the Weibull approximation fits better than any exponential approximation.
 But, we define an automatic way to estimate the best fitting.
-We  use the AIC (Akaike information criterion), winch is gave by:
+We  use the AIC (Akaike information criterion), which is given by:
 
@@
 The smaller is the AIC value, the best is the function fitting.
-An alternative for the AIC, is the BIC value, which follow the same rule.
-Big is defined by the equation:
+An alternative for the AIC is the BIC value, which follows the same rule.
+This equation defines BIC:
 
@@
 %As we can see, both BIC and AIC agree on each element, which one is the best and the worst.
-In this case, the best is the Weibull and the worst is the Cauchy.
+In this case, the best is the Weibull, and the worst is the Cauchy.
 The exponential models, which are the continuous version of a classical Poisson process, is worse than Weibull and both Pareto estimation.
 
-%But, to verify if our estimation is good, we need to see what sort of data these stochastic process are able to generate, and how close the stochastic properties of the synthetic dataset is from the original.
-In this way, we will be able to verify its actual quality in  unbiased way.
+%But, to verify if our estimation is reasonable, we need to see what sort of data these stochastic processes can generate, and how close the stochastic properties of the synthetic dataset is from the original.
+In this way, we will be able to verify its actual quality in an unbiased way.
 
-% The Pearson correlation is +1 in the case of a perfect direct (increasing) linear relationship (correlation), −1 in the case of a perfect decreasing (inverse) linear relationshi
+% The Pearson correlation is +1 in the case of a perfect direct (increasing) linear relationship (correlation), −1 in the case of an ideal decreasing (inverse) linear relationship
 

### 2018-04-25 Docs/Thesis/docs/chapter5.tex
thesis update

@@
 As proof of concepts for our tool, we are going to use Mininet's emulated testbeds.
-We automate all tests using scripts, so our experiments are are fully  reproducible.
+We automate all tests using scripts, so our experiments are fully reproducible.
 They are responsible for running all the proposed tests in this chapter and perform the calculations.
@@
 
-Each test is organized as a Python packege, responsible for tigger all the applications and procedures.
-The parameters for each simulation can be configured by a \textit{config.py} file.
-The files \textit{README} on each packege, provide a tutorial to run correctely each test.
-With all tools instaled, less then fifteen minutes is enought for run each test again.
-A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specificatins and the software versions.
+Each test is organized as a Python package, responsible for trigger all the applications and procedures.
+A \textit{config.py} file can configure the parameters for each simulation.
+The files \textit{README} on each package, provide a tutorial to run each test correctly.
+With all tools installed, less then fifteen minutes is enough for rerunning each test.
+A complete specification of our scenario we show at the table ~\ref{tab:specifications}, including the hardware specifications and the software versions.
 
@@
 For each test, we generate a set of plots to compare the original and synthetic trace.
-Two of them we use for mere visual comparison: flows per second and bandwidth.
-To compare the realism quality of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.
-On every case, the more closer the plots are, the more similar the traffics are according to each perspective.
-Also, we wrote in the table ~\ref{tab:results-summary} a complation of each traffic statistics.
+Two of them we use for visual comparison: flows per second and bandwidth.
+To examine the realism quality of the generated traffic, we plot the flows cumulative distribution function (CDF)\cite{harpoon-paper}, and the Wavelet multiresolution analysis.
+In every case, the closer the plots are, the more similar are the traces.
+Also, we wrote on the table ~\ref{tab:results-summary} a compilation of each traffic statistics.
 
@@
 It cannot assign arbitrary IP addresses as source and destination since it must establish a connection between the source and destination.
-For the transport layer, it just supports TCP and UDP protocol, and constant bandwidth traffic.
+For the transport layer, it supports TCP and UDP protocol, and constant bandwidth traffic.
 On the other hand, it enables customization of transmission time, number of packets, windows size, TTL, packet sizes, payload and many other features.
@@
 This behavior can be observed as well in the bandwidth plot.
-It is much larger in the first seconds and small at the end.
+It is much more significant in the first seconds and small in  the end.
 
@@
 The original skype traffic increased linearly, an indication of fractal shape.
-The synthetic trace started to increase at the time scale 5-6 (300-600 milliseconds).
+The synthetic trace started to grow at the time scale 5-6 (300-600 milliseconds).
 After this scale, the error between the curves become very small.
 One possible reason for this behavior is the fact that the constant which regulate the minimum burst time (\texttt{DataProcessor::m\_min\_on\_time}) is set to 100 milliseconds.
-For small time scales the traffic become similar to white noise since Iperf just emits traffic with constant bandwidth.
-For larger scales, it captures the same fractals patterns of the original trace.
+For small time scales the traffic become similar to white noise since Iperf emits traffic with constant bandwidth.
+For larger time-scales, it captures the same fractals patterns of the original trace.
 It also captures a periodicity pattern at the time-scale of 9 seconds.
@@
 In the second case, on a tree topology on small time scales, the same white-noise behavior is identified.
-We identify a similar behavior on the energy behavior on larger time-scales, but with a larger gap between the curves.
+We identify a similar response for energy on larger time-scales, but with a more significant gap between the curves.
 Packet collision on switches requiring retransmission packets explains this behavior.
@@
 Using the first 10 seconds of the trace \textit{bigFlows-pcap}, on 10 seconds of operation, Iperf generated much fewer packets than the expected.
-It is an expected behavior since the operating system couldn't handle so much newer processes (one per flow) in such short time.
+It is supposed behavior since the operating system couldn't handle so much newer processes (one per flow) in such short time.
 On the other hand, the same drawback wasn't observed using libtins as traffic generator tool, since being a low-level API makes it much computationally cheaper.
@@
 SIMITAR was designed to work at flow-level and packet level.
-At the flow-level, our methodology can achieve great results.
+At the flow-level, our methodology can achieve excellent results.
 In fact,  The cumulative distribution of flows is almost identical on each case.

### 2018-04-25 Docs/Thesis/docs/chapter6.tex
update
thesis update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter{Conclusion and Future Work}\label{ch:conclusion}
+\chapter{Future Work and Final Conclusions}\label{ch:conclusion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 (4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount.
-If it is smaller, SIMITAR just uses the constant model.
+Otherwise, SIMITAR uses the constant model.
 We decide to do it for two reasons.
-First, because with a small sample, the modeling accuracy is poor.
+First, because with a small sample, the modeling accuracy is reduced.
 Second, we avoid the cost of the parameterization process.
 Now, its value is set to Its value today is set to 30.
-Increasing this amount, we may achieve a more reasonable performance for individual flows, and reduce the processing time.
+Increasing this amount, we may achieve more reasonable performance for individual flows, and reduce the processing time.
 
@@
 In this way, we may achieve a faster packet processing.
-This can be integrated as an insatiable feature of SIMITAR (figure ~\ref{fig:dpdk-if}).
+This can be integrated as an instantiable feature of SIMITAR (figure ~\ref{fig:dpdk-if}).
 
@@
 
-(7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be splitted on $m$ different files, each describing $n/m$ flows, and still describe the same traffic.
-With $m$ synchronized machines woking in parallel, each using one of these $m$ parts of the original \textit{compact trace descriptor}, with use of link-agregattion techinique\footnote{http://www.comutadores.com.br/configurando-link-aggregationetherchannel-entre-cisco-e-hpn/} we can achieve high speeds on bare-metal.
+(7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be split on $m$ separate files, each representing $n/m$ flows, and still portray the same traffic.
+With $m$ synchronized machines working in parallel, each using one of these $m$ parts of the original \textit{compact trace descriptor}, with use of link-aggregation techinique\footnote{http://www.comutadores.com.br/configurando-link-aggregationetherchannel-entre-cisco-e-hpn/} we can achieve high speeds on bare-metal.
 
 (8) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times.
-To avoid overheads on random numbers calculation,  these values must be calculated before the actual traffic generation.
-Modelling inter-packet times the scaling characteristics of libtins traffic should improve.
+To avoid overheads,  the values of inter-packet times must be calculated before the actual traffic generation.
+Modeling inter-packet times the scaling characteristics of libtins traffic should improve.
 
@@
 (15) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: this would reduce the number of flows created, improving its computational performance.
-Since SIMITAR manages each flow in a different thread, it will create fewer threads simultaneously, reducing overheads.
+Since SIMITAR manages each flow in a different thread, it will generate fewer threads simultaneously, reducing overheads.
 This action should not impact on throughput and scaling characteristics because few packets would be ignored.
@@
 (16) Currently, SIMITAR only enables the programming of flow traffic generation in C++.
-Adding Python and Lua support for the Flow Generator component, we can enable expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ wrappers.
+Adding Python and Lua support for the Flow Generator component, we can allow expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ wrappers.
 
@@
 %Our proposed future work is to implement this idea using the Swing\cite{swing-paper} and the Harpoon Model\cite{harpoon-paper}.
-We can create not just Simitar trace descriptors, but Swing and Harpoon trace descriptors as well.
+We can create not just SIMITAR trace descriptors, but Swing and Harpoon trace descriptors as well.
 So, as here, we would have the same components: the Sniffer, the SQLite database, the DataProcessor, the flow generator, and the same interface based on an XML Compact Trace Descriptor.
-The FlowGenerator would abstract the traffic generation in based on the Swing and Harpoon model, in an API independent way as well.
+The FlowGenerator would abstract the traffic generation based on the Swing and Harpoon model, in an API independent way as well.
 
@@
 In this way, progresses on high-speed traffic generation would no more make old traffic generators and models obsolete.
-Also, would enable the comparison (ain a fair way) which model is actually the best since the same engine and technic for generating packets will be used.
+Also, would enable the comparison (in a fair way) which model is the best since the same engine and technic for generating packets will be used.
 
-%Also, the idea of a Compact Trace Descriptor, by itself separates the idea of traffic generation and the modeling.
-De development of new methodologies for modeling is  separated from the traffic generation.
-So a data-developer, using any compact trace descriptor interface may just "plug" his method of data modeling in the FlowGenerator.
+%Also, the idea of a Compact Trace Descriptor, by itself separates the concept of traffic generation and the modeling.
+The development of new methodologies for modeling is divided from the traffic generation.
+So a data-developer, using any small trace descriptor interface may just "plug" his method of data modeling in the FlowGenerator.
 He has not to care about how the packets were going to be generated anymore nor in what programming language is being used to craft packets.
@@
 
-In this dissertation we discuss our process of conceiving, researching, definition and development and validation of an realistic traffic generator able to at the same time fulfill gaps others proposals haven't, and achieve results comparable to the available proposals.
+In this dissertation, we discuss our process of conceiving, researching, definition and development and validation of a realistic traffic generator able to at the same time fulfill gaps others proposals haven't, and achieve results comparable to the available suggestions.
 This was not a linear procedure.
-Was indeed an espiral procedure, as proposed by Sommervile on Software Engineering\cite{sommerville}.
-Clealy its not identical, because we adapt it for research purposes.
-At the figure~\ref{fig:spiral} we show a diagram of who  it was done.
+Was indeed a spiral procedure, as proposed by Sommerville on Software Engineering\cite{sommerville}.
+It's not identical, because we adapt it for research purposes.
+At the figure~\ref{fig:spiral} we show a diagram of how we do it.
 
@@
 But structural changes are impracticable.
-At this point we implemented a simplistic prototype, and validate it\footnote{In the appendix ~\ref{ap:publications}, this prototype is validated in the article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios"}.
+At this point we implemented a simple prototype, and validate it\footnote{In the appendix ~\ref{ap:publications}, this prototype is validated in the article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios"}.
 
@@
 
-In the chapter ~\ref{ch:modeling-evaluation} we achieve a significant contribution of our work, which shows that the information criteria AIC and BIC are efficient analytical methods for select models for inter-packet times.
+In the chapter ~\ref{ch:modeling-evaluation} we achieve a significant contribution to our work, which shows that the information criteria AIC and BIC are efficient analytical methods for select models for inter-packet times.
 Both can infer a good model, even evaluated according to different types of metrics, without any simulation.
@@
 Our main contribution here is the development of a traffic generator tool that at the same time can provide realistic synthetic traffic, and its modeling framework is extensible for most of the traffic generation libraries and tools.
-In fact, our current implementations use tow very distinct packet-crafters: \textit{libtins}, a C++ library designed for the implementation of sniffers and traffic generators, and Iperf, a traffic generator commonly used to measure bandwidth.
+In fact, our current implementations use tow very distinct packet-crafters: \textit{libtins}, a C++ library designed for the application of sniffers and traffic generators, and Iperf, a traffic generator commonly used to measure bandwidth.
 
@@
 
-Finally, we created a list of improvements and future works, aiming the improvement of the software, inclusing, performance better processing time and packet generation, and the realismo on the traffic generated.
-In fact, the greater bootleneck of the project resides on processing performance.
-The results on realism, even with a lot of room for improovments, already have a good quality.
+Finally, we created a list of improvements and future works, aiming the development of the software, including, performance better processing time and packet generation, and the realism on the traffic generated.
+In fact, the higher bottleneck of the project resides on processing performance.
+The results on realism, even with a lot of room for improvement, already have a good quality.
 With the proposed future works we believe to be possible overcome the current limitations.

### 2018-04-25 Docs/Thesis/docs/macros.tex
updates
up
thesis update

@@
 \newcommand{\Year}{
-	Anderson dos Santos Paschoalon
+	2017
 }
@@
 \newcommand{\TituloDaTese}{
-SIMITAR: Uma Ferramente para Geração de Trafego de Rede Sintético e Realistico para Benchmarking e Testes
+SIMITAR: Uma Ferramenta para Geração de Trafego de Rede Sintético e Realistico para Benchmarking e Testes
 }
@@
 Gostaria de agradecer ao meu professor e orientador Christian Esteves Rothemberg, sem o qual, seja pelo ensino, seja pela orientação e apoio durante o projeto, este trabalho não teria saído do papel.
+Gostaria de agredecer toda sua paciencia e entendimento por esses ultimos anos.Sua liderança será uma fonte de inspiração para mim para o restante de minha carreira, e ela está apenas começando.
+Sem sua idéias  inovadoras, suporte e encorajamento continuo, este projeto não teria saido do papel.
+Especialmente pelo fato de que em pesquisa muitas vezes as coisas não saem como o esperado, e temos que reiniciar do zero o processo.
 
@@
 
-E por ultimo agradeço a Deus por todos seu dons, proteção aamor
+E por ultimo agradeço a Deus por todos seu dons, proteção e amor.
 

### 2018-05-14 Docs/Thesis/docs/chapter1.tex
*1* ECLIPSE: OXYGEN. *2* MODIFICATION ON THE SIMITAR CODE. NOW RAPIDXML IS LOCATED IN DEPS DIR, AND THE CODE CHANGED A LITTE ON NETWORK TRACE CLASS.

@@
 
-Emerging technologies such as SDN and NFV can be considered great promises that would drastically change the development and operation of computer networks.
+Emerging technologies such as SDN and NFV can be considered great promises that are going to  drastically change the development and operation of computer networks if established in large scale.
 However, its enabling technologies such as virtualization still pose challenges as for performance,  reliability, and security\cite{nfv-challenges}.
@@
 
-Furthermore realistic workload generators are an essential security research\cite{ditg-paper}, since generation of realistic workloads is important for evaluation of firewall middleboxes.
+Furthermore realistic traffic generators are an essential security research\cite{ditg-paper}, since generation of realistic workloads is important for evaluation of firewall middleboxes.
 It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.
@@
 Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider.
+
 Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment.
@@
 For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK.
-In addition, many of the listed traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.
+In addition, many of the listed traffic generators provides their own (high-level) APIs, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.
 
@@
 Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration.
-Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic; so throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}.
-ecause its traffic generation engine is coupled to its modeling framework, you cannot opt to use a newer/faster packet generation library.
+Swing\cite{swing-paper} only generates TCP and UDP traffic, and have limitations on throughputs rates\cite{swing-paper} \cite{legotg-paper}.
+Because its traffic generation engine is coupled to its modeling framework, you cannot opt to (easily) use a newer/faster packet generation library.
 The only way of replacing the traffic engine is changing and recompiling the original code which is a hard and  error prone activity\cite{legotg-paper}.
 Again, we fall in the same issue, a complex task that is usually not the goal of the project.
-In the table ~\ref{tab:related-work} we give a brief summary of what we have available on some open-source traffic-generators tools.
+In the table~\ref{tab:related-work} we give a brief summary of what we have available on some open-source traffic-generators tools.
 

### 2018-05-14 Docs/Thesis/docs/chapter2.tex
*1* ECLIPSE: OXYGEN. *2* MODIFICATION ON THE SIMITAR CODE. NOW RAPIDXML IS LOCATED IN DEPS DIR, AND THE CODE CHANGED A LITTE ON NETWORK TRACE CLASS.

@@
 For example, if we want to evaluate the performance limits of equipment or new technology, you may want to execute stress tests, at specific constant rates.
-In this case, maximum throughput traffic generator is more interesting.
+In this case, a maximum throughput traffic generator is more interesting\cite{validate-trafficgen}.
 On the other hand, to test how it performs on an actual network environment, you should search for a tool that produces a stochastically realist profile.
@@
 But classify them it is an efficient way to distinguish the difference between these tools.
-We will cite here two:
+We will cite here two sorts of classification:
 
@@
 
-The most common traffic generator classification in the literature is about its abstraction level\cite{do-you-trust}.
-There are four groups: Application-level, flow-level, packet-level and multi-level traffic generators.
+The most common classification is about its abstraction level\cite{do-you-trust}, and it divides the traffic generators in four groups: Application-level, flow-level, packet-level and multi-level traffic generators.
 We present a diagram illustrating its concept in figure ~\ref{fig:layers-workload-tools}.
@@
 
-\textbf{Flow-level traffic generators}: they are able to configure and reproduce features of flows\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}.
+\textbf{Flow-level traffic generators}: they can configure and reproduce flow characteristics\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}.
 Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from  routers.
 
-\textbf{Packet-level traffic generators}: most traffic generators available fall in this class.
-They can craft and inject packets into the network, and control features like inter-departure times (IDT), packet size(PS), throughput and packets per second\cite{validate-trafficgen}.
+\textbf{Packet-level traffic generators}: most common type of traffic generator.
+They can control packet-features like inter-departure times, packet size, throughput and packets per second\cite{validate-trafficgen}.
 \cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model-based generators.
@@
 
-Another desired characteristic is a high variability, in mathematical terms, an infinite variance.
-Process with such characteristic is said to be heavy-tailed \cite{sourcesonoff-paper}.
+Another stochastic characteristic of the Ethernet traffic is high variability, or infinite variance.
+Processes with such characteristic are said to be heavy-tailed \cite{sourcesonoff-paper}.
 In practical terms, that means a sudden discontinuous change can always occur.
@@
 
-An important desirable feature that should be controlled is the packet size distribution since each flow may have its own packet distribution.
-As we can see in many works, the packet size of a trace may result in a huge impact in a trace throughput \cite{stochartic-selfsimilar}\cite{performance-trafficgen}; small packets cause a huge overhead in the packet throughput.
-In the table ~\ref{tab:packet-size-impact} there are a survey of results found by two different works \cite{comparative-trafficgen-tools} \cite{performance-trafficgen} about the impact of different packet sizes in the throughput rate.Therefore, it is an important factor we must taken into account in the evaluation of new proposals, and in the implementation of network workloads generators.
+Another relevant feature is the packet size distribution.
+As we can see in many works, the packet size of a trace may result in a huge impact in a trace throughput \cite{stochartic-selfsimilar}\cite{performance-trafficgen}, since small packets cause a larger overhead on packet processing.
+To exemplify, in the table~\ref{tab:packet-size-impact} we survey results from two different works \cite{comparative-trafficgen-tools} \cite{performance-trafficgen} about throughput impact of packet sizes.
 On packet size distribution characterization, we can find many works in the literature.
 For example, \cite{packet-distribution-model} analyses many packet sizes distributions of many packet traces, in many environments.
-Some general results are that 90\% of UDP packets are smaller than 500 bytes, and most packets transmitted using TCP have 40 bytes (acknowledgment) and 1500 bytes (Maximum Transmission Unit, MTU) \cite{packet-distribution-model}.
+Some general results are that \textbf{\textit{90\%}} of UDP packets are smaller than 500 bytes, and most packets transmitted using TCP have \textbf{\textit{40 bytes}} (acknowledgment) and \textbf{\textit{1500}} bytes (Maximum Transmission Unit, MTU) \cite{packet-distribution-model}.
 For UDP traffic, we have similar results, since mostly they are bimodal as well \cite{udp-flows-model}.
-Ostrowsky et al.\cite{udp-flows-model} found that, on UDP traces the modes of two regions are 120 and 1350 bytes, with a cut-off value of 750 bytes.
-They also find that roughly UDP packets constitute 20\% of the total number of packets on captures.
+Ostrowsky et al.\cite{udp-flows-model} found that, on UDP traces the modes of two regions are \textbf{\textit{120}} and \textbf{\textit{1350}} bytes, with a \textbf{\textit{cut-off}} value of \textbf{\textit{750 bytes}}.
+They also find that roughly UDP packets constitute \textbf{\textit{20\%}} of the total number of packets on captures.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scaling Characteristics}
+\subsection{Fractal and Scaling Characteristics}
 
@@
 On \textbf{self-similar time series}, the energy function plot $\log(E_{j})$ will grow approximately linearly with the scale $j$.
+This explains why it has become a standard for realistic traffic generation analysis.
+In a single plot, we can easily identifiy periodicities, and self-similar and Poisson process characteristics, just seeing if it decays, grow, or remain constant.
 

### 2018-05-14 Docs/Thesis/docs/chapter3.tex
*1* ECLIPSE: OXYGEN. *2* MODIFICATION ON THE SIMITAR CODE. NOW RAPIDXML IS LOCATED IN DEPS DIR, AND THE CODE CHANGED A LITTE ON NETWORK TRACE CLASS.

@@
 
-In this chapter, we will present our tool which aims to fill the gaps addressed in the chapter ~\ref{ch:introduction}.
-We call it \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}.
+In this chapter, we will present our tool which aims to fill the gaps addressed in the chapter~\ref{ch:introduction}.
+We call it \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}\footnote{And Scimitar is curved sword originated on the Middle East.}.
 This acronym summarizes its operation.
@@
 On the figure ~\ref{fig:layer-diagram} we abstract our concepts we stated in a layer diagram model.
-Or tool must work as an interface for the user automatizing traffic modeling, configuration, and emulation and offer services of intelligence and traffic generation programmability.
+Or tool work as an interface for the user automatizing traffic modeling, configuration, and emulation and offer services of intelligence and traffic generation programmability.
 In the figure, we also include packet-acceleration\footnote{Packet acceleration is a concept introduced by DPDK\cite{web-dpdk}, which means kernel by-pass.
@@
 
-Our primary goal is to offer simple configuration, with \textbf{realism}, at a reasonable speed.
+Our primary goal is to offer all services mentioned in the table~\ref{tab:related-work}, realismo on the synthetic traffic, auto-modelling and traffic configuration, simple usage,  configuration, and plain possibility of traffic customization for the user.
 The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the purpose of the project in an illustrative way.
@@
 We are also introducing the concept of \textbf{programmability}.
-Since the \textit{compact trace descriptor},  is an XML file, the user may create his custom traffic in a platform agnostic way creating his own CTD file.
+Since the \textit{compact trace descriptor}(CDF), is an XML file, the user may create his custom traffic in a platform agnostic way creating his own CTD file.
 So the user will be able to create multi-flow Ethernet traffic not having to build many scripts for each tool or reading its documentation.
@@
 We abstract its whole operation cycle in the figure ~\ref{fig:cycle-of-operation}.
-Our tool, from live captures or \textit{pcap} file collects raw data from Ethernet traffic.
-It then breaks these data into different flows and uses this data to generate a set of parameters for our traffic model, using a set of algorithms.
-Finally, SIMITAR provides these parameters to a packet generator engine and controls its packets injection.
+Our tool collect packet data  from live captures or \textit{pcap} files.
+It then breaks the traffic into flows and uses the data to generate  parameters for our traffic model.
+Finally, SIMITAR provides these parameters to a packet generator engine and controls the packet injection.
 
@@
 SIMITAR architecture is presented in the figure~\ref{fig:architecture}.
-It is composed of four components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator};  and a \textit{Network Traffic Generator}, as subsystem.
+It is composed of four components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator},  and a \textit{Network Traffic Generator}, as subsystem.
 We describe each part below.
@@
 This component collects network traffic data and classifies it into flows, storing stores in an SQLite database.
-It defines each flow by the same criteria used by SDN switches\cite{sdn-survey},  through header fields matches.
-It uses:
+It uses header field matches to classify the flows, such as in SDN switches\cite{sdn-survey}.
+The used fields are:
 
@@
 Our OrderedSet does.
-Also, it makes use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}.
+Also, it uses a  64 bits hash function from the FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.} family.
 The listed header fields are inputs for a hash function.
@@
     \includegraphics[height=2.0in]{figures/ch3/modified-harpoon-model}
-    \caption{The schema of the modified version of the Harpoon algorithm we adopt on SCIMITAR.}
+    \caption{The schema of the modified version of the Harpoon algorithm we adopt on SIMITAR.}
     \label{fig:modified-harpoon-model}
@@
 The distinction is made based on the time delay between packets.
-For our purposes, the advantage of this strategy is that the evaluation of the packet-train is not attached to a specific protocol.
+For our purposes, the advantage of our strategy is that the evaluation of the packet-train is not attached to a specific header field, so we can define packet trains for any sort of flow.
 We illustrate this behavior in the figure~\ref{fig:modified-harpoon-model}.
@@
 We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.
-We develop an algorithm called \textit{calcOnOff} responsible for estimating these times.
+We develop an algorithm called \textit{calcOnOff} that estimate these times.
 It also determines the number of packets and bytes transferred by each file.
@@
 In the \textbf{file layer}, we model the inter-packet times at the file level.
-To estimate inter-packet times within files, we select all inter-packet times smaller than \texttt{session\_cut\_time}\footnote{In the code it is called\texttt{DataProcessor::m\_session\_cut\_time} }.
-All files within the same flow are considered to follow the same model.
+We select all times smaller than \texttt{session\_cut\_time}\footnote{In the code it is called\texttt{DataProcessor::m\_session\_cut\_time} }, and all files within the same flow are considered to follow the same model.
 We delegate the control of the inter-packet times to the underlying packet generator engine.
@@
 Currently, we are using eight different stochastic functions parameterizations.
-They are Weibull(linear regression), Normal(mean/standard deviation calculation), Exponential(mean and linear regression estimation), Pareto(linear regression and maximum likelihood), Cauchy(linear regression) and Constant(mean calculation).
-From those, Weibull, Pareto, and Cauchy are heavy-tailed functions, and therefore self-similar processes.
+We display each of them on the table~\ref{tab:parameterizations-sumary} .
+
+\begin{table}[ht!]
+	\centering
+	\caption{Functions and parameterizations used by SIMITAR}
+		\begin{tabular}{c c c c}
+			\toprule
+			\textbf{Function} & Linear Regression & Maximum Likelihood & Empirical\footnotemark \\
+			\midrule
+			Weibull         & $\checkmark$    &                  &                  \\
+			Normal             &                  &                  &  $\checkmark$    \\
+			Exponential      & $\checkmark$    &                  &  $\checkmark$    \\
+			Pareto          & $\checkmark$    & $\checkmark$    &                  \\
+			Cauchy          & $\checkmark$    &                  &                  \\
+			Constant          &                 &                  & $\checkmark$    \\
+			\bottomrule
+		\end{tabular}
+		\label{tab:parameterizations-sumary}
+\end{table}
+\footnotetext{Empirical estimation, by calculation of the avarge, and standard deviation}
+
+From the functions presented in the first column~\ref{tab:parameterizations-sumary}, Weibull, Pareto, and Cauchy are heavy-tailed (and self-similar processes).
 But if the flow has less than 30 packets, just the constant model is evaluated.

### 2018-05-14 Docs/Thesis/docs/chapter4.tex
*1* ECLIPSE: OXYGEN. *2* MODIFICATION ON THE SIMITAR CODE. NOW RAPIDXML IS LOCATED IN DEPS DIR, AND THE CODE CHANGED A LITTE ON NETWORK TRACE CLASS.

@@
 In this chapter, we are going to go into deep details on some implementations and modeling approaches mentioned in the last chapter.
-In the first section, we are going to discuss our methodology for modeling inter packet-times and validate it as a good choice.
-The problem we want to address are these:
+In the first section, we are going to discuss our methodology for modeling inter packet-times, and proof that it is a good choice.
+But before putting our hands on the problem, we need to precisely define what we want.
+We abstract our ideas in the bullets below:
 
@@
 
-    \item We have a set of empirical inter-packet times, and some approximate stochastic models that describe it. We want to know what is the best analytically, avoiding human analysis;
+    \item Given a set of empiral inter-packet times, we want to parametrize not only one, bua a set of "candidates" stochastic functions to describe it
 
-    \item We want to know whatever if our modeling approaches are suitable or not to describe inter-packet times.
+    \item We want to know, analitically,  which of these candidates is the best, avoiding human analysis;
+
+    \item We need a proof that our choosen analifical analysis is good or not to describe inter-packet times.
 
@@
 We explain this procedure in the appendix ~\ref{ap:revision-probability}.
-In the figure~\ref{fig:linearization} we present as examples, the linearized data for the inter arrivals from the \textit{skype-pcap}, and in the figure ~\ref{fig:linearization-cost} the cost convergence.
+In the figure~\ref{fig:linearization} we present as examples, the linearized data for the inter arrivals from the \textit{skype-pcap}, and in the figure ~\ref{fig:cost} the cost convergence.
 In the appendix ~\ref{ap:aditional-plots}, a complete set of these figures is presented.
@@
 \centering
-\label{fig:aproximation-original-cdf}
 \subfloat[Chauchy]{
@@
 }
+\label{fig:aproximation-original-cdf}
 \caption{CDF functions for the approximations of \textit{skype-pcap} inter  packet times, of many stochastic functions.}
@@
 The other plots are provided and commented on the appendix ~\ref{ap:aditional-plots}.
-In the figure ~\ref{fig:aproximation-original-cdf} we present all estimated CDF functions along with the empirical CDF, for the trace \textit{skype-pcap}.
+In the figure~\ref{fig:aproximation-original-cdf} we present all estimated CDF functions along with the empirical CDF, for the trace \textit{skype-pcap}.
 They are on log-scale, which provide a better visualization for small time scales.
@@
 All these results are abstracted by the cost function $J$.
-As we can see, on all pcaps, the best function selected by BIC and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.
+As we can see, on all pcaps, the best function selected by BIC and AIC(table~\ref{tab:prototype-results}) also had the small cost(figure~\ref{fig:cost-function}).
 
@@
 The reasons for this behavior are both results of a much great traffic with no long-range gaps, and the precision of the measurement.
+
+Since there is a lot of information on table~\ref{tab:prototype-results} and on the figure~\ref{fig:cost-function}, we capture just the order of choise form each \textit{pcap} plotted on the figure~\ref{fig:cost-function_vs_aic-bic}.
+We can see that expecially on the best fittings, the results were closer.
+Just for the \textit{bigFlows-pcap} the results from the best and second best models were flipped.
+On all the other cases, the choises were the same.
+For the worsts models, the results tend to differ more, and loose correlation.
+It is not a bad thing, since they were not good choices after all.
 
@@
 
+%validation Cost function
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width=100mm]{figures/ch4/aic-bic_vs_costFunction_order}
+	\caption{Comparison of model selection order com cost function and AIC/BIC}
+    \label{fig:cost-function_vs_aic-bic}
+\end{figure}
+
 \begin{algorithm}[ht!]
@@
 
-We can conclude that using AIC or BIC as criteria for choosing models for inter-packet times is a good choice.
+We can conclude that using AIC or BIC as criteria for choosing good models for inter-packet times is a good choice.
 
@@
     \centering
-    \caption{Application matach table}
+    \caption{Application match table}
     \label{tab:application-protocols}

### 2018-05-14 Docs/Thesis/docs/chapter5.tex
*1* ECLIPSE: OXYGEN. *2* MODIFICATION ON THE SIMITAR CODE. NOW RAPIDXML IS LOCATED IN DEPS DIR, AND THE CODE CHANGED A LITTE ON NETWORK TRACE CLASS.

@@
 If the traffic has self-similar characteristics on a particular time scale, its value will increase linearly.
+We show a sumary of all performed tests on table~\ref{tab:validation-tests-performed}.
+
+\begin{table}
+	\centering
+	\label{tab:validation-tests-performed}
+	\caption{Performed validations}
+		\begin{tabular}{c c}
+			\toprule
+			\textbf{Metric Type} & \textbf{Validations} \\
+			\midrule
+			\makecell{Packet Based \\Metrics}                & \makecell{Data bit rate (kbps), Average packet\\
+				rate (packets/s), Average packet size\\
+				(bytes), Number of packets, Number of\\
+				packets, Bandwidth over time}\\
+
+			\makecell{Flow Based \\ Metrics}                & \makecell{Number of flows, Flows per second, \\
+				Flows CDF distributions}\\
+
+			\makecell{Fractal and Scaling \\ Characteristics} & \makecell{Hurst Exponent, Wavelet \\
+				Multiresolution Analisis}\\
+			\bottomrule
+		\end{tabular}
+
+\end{table}
 
@@
 The packet customization capability is vast, and enable a full usage of our model parameters.
-Control inter-packet times stays for future work.
+Control inter-packet times stays for future work~\ref{ch:conclusion}.
 

### 2018-05-14 Docs/Thesis/docs/chapter6.tex
*1* ECLIPSE: OXYGEN. *2* MODIFICATION ON THE SIMITAR CODE. NOW RAPIDXML IS LOCATED IN DEPS DIR, AND THE CODE CHANGED A LITTE ON NETWORK TRACE CLASS.

@@
         \multicolumn{3}{c}{Future Work}    & Priority \\ \hline
-        1   & Optimizing linear regression                       &                                & \textbf{\textit{high}} \\
-        2   & Flow-merging option                                &                                & \textit{medium} \\
-        3   & Smart flow-scheduler and thread/process management &                                & \textbf{\textit{high}} \\
-        4   & \texttt{DataProcessor::minimumAmountOfPackets}     &                                & low \\
-        5   & DPDK KNI interfaces                                &                                & \textit{medium} \\
-        6   & Multi-thread C++ sniffer                           &                                & \textbf{\textit{high}} \\ 
-        7   & Cluster operation (high speed traffic-gen)         & \multirow{-7}{*}{Performance}  & \textbf{\textit{high}} \\ \hline
-        8   & Model inter-packet times on \texttt{TinsFlow}      &                                & \textbf{\textit{high}} \\
-        9   & D-ITG flow generator (\texttt{DitgFlow})           &                                & low \\
-        10  & DPDK flow generator (\texttt{DpdkFlow})            &                                & \textit{medium} \\
-        11  & Ostinato flow generator (\texttt{OstinatoFlow})    & \multirow{-4}{*}{Tool support} & low \\ \hline
-        12  & \texttt{DataProcessor::min\_time}                  &                                & low \\
-        13  & \texttt{DataProcessor::m\_min\_on\_time}           &                                & low \\
-        14  & \texttt{DataProcessor::m\_session\_cut\_time}      &                                & low \\
-        15  & Minimum number of packets per flow option          & \multirow{-4}{*}{Calibration}  & low \\ \hline
-        16  & Python API/Lua for traffic generation              &                                & low \\
-        17  & Crafter of  pcap files                             & \multirow{-2}{*}{New features} & low \\
+        A1   & Modelling Optimizations                       &                                & \textbf{\textit{high}} \\
+        A2   & Flow-merging option                                &                                & \textit{medium} \\
+        A3   & Smart flow-scheduler and thread management &                                & \textbf{\textit{high}} \\
+        A4   & \texttt{DataProcessor::minimumAmountOfPackets}     &                                & low \\
+        A5   & DPDK KNI interfaces                                &                                & \textit{medium} \\
+        A6   & Multi-thread C++ sniffer                           &                                & \textbf{\textit{high}} \\ 
+        A7   & Cluster operation (high speed traffic-gen)         & \multirow{-7}{*}{Performance}  & \textbf{\textit{high}} \\ \hline
+        B1   & Model inter-packet times on \texttt{TinsFlow}      &                                & \textbf{\textit{high}} \\
+        B2   & D-ITG flow generator (\texttt{DitgFlow})           &                                & low \\
+        B3  & DPDK flow generator (\texttt{DpdkFlow})            &                                & \textit{medium} \\
+        B4  & Ostinato flow generator ((\texttt{OstinatoFlow}))            & 						&  \textit{medium}
+         \\
+        B5  &  Multi-tool flow generator    & \multirow{-5}{*}{Tool support} & low \\ \hline
+        C1  & \texttt{DataProcessor::min\_time}                  &                                & low \\
+        C2  & \texttt{DataProcessor::m\_min\_on\_time}           &                                & low \\
+        C3  & \texttt{DataProcessor::m\_session\_cut\_time}      &                                & low \\
+        C4  & Minimum number of packets per flow option          & \multirow{-4}{*}{Calibration}  & low \\ \hline
+        D1  & Python and Lua API on the FlowGenerator component             &                                & low \\
+        D2  & Crafter of  pcap files                             & \multirow{-2}{*}{New features} & low \\
 
@@
 
-(1) The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor.
+(A1) The major issue of SIMITAR now is optimizing data processing for creating the compact trace descriptor.
 The performance becomes an issue when processing large \textit{pcap} files with more dozens of thousands of flows.
@@
 Parallel processing, and creating stop criteria based on convergence in addition to the number of iterations will improve the performance, along with some code optimizations.
+Make the XML less verbose should help in this sense as well.
 
-(2) Crating an option for merging flows is a possibility to improve the performance of traffic with several thousands of flows and Gigabits of bandwidth, such as from WAN captures.
+(A2) Crating an option for merging flows is a possibility to improve the performance of traffic with several thousands of flows and Gigabits of bandwidth, such as from WAN captures.
 A merge criterion, for example, is to consider just network headers on flow's classification.
 
-(3) Currently, all the flow threads are instantiated once the traffic generations start.
+(A3) Currently, all the flow threads are instantiated once the traffic generations start.
 A smarter traffic generation where SIMITAR instantiates each thread when the traffic, and join when it is inactive should reduce the overhead for traces with a large number of flows.
@@
 
-(4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount.
+(A4) Constant \texttt{DataProcessor::minimumAmountOfPackets}: SIMITAR only estimates stochastic models for inter-packet times if the number of packets for this flow is larger than this amount.
 Otherwise, SIMITAR uses the constant model.
@@
 
-(5) One possibility to improve the traffic generation performance issue DPDK Kernel NIC Interface  (KNI interfaces) \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}.
+(A5) One possibility to improve the traffic generation performance issue DPDK Kernel NIC Interface  (KNI interfaces) \footnote{\href{http://dpdk.org/doc/guides/prog_guide/kernel_nic_interface.html}{http://dpdk.org/doc/guides/prog\_guide/kernel\_nic\_interface.html}}.
 DPDK KNI interfaces allow applications from the user's space interact with DPDK ports.
@@
 
-(6) Another issue is the sniffer component is taking to much time to extract data from large \textit{pcap} files.
+(A6) Another issue is the sniffer component is taking to much time to extract data from large \textit{pcap} files.
 Implementing a C/C++ multi-thread sniffer, including the packet processing and the SQL queries, will improve its performance.
 
-(7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be split on $m$ separate files, each representing $n/m$ flows, and still portray the same traffic.
+(A7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be split on $m$ separate files, each representing $n/m$ flows, and still portray the same traffic.
 With $m$ synchronized machines working in parallel, each using one of these $m$ parts of the original \textit{compact trace descriptor}, with use of link-aggregation techinique\footnote{http://www.comutadores.com.br/configurando-link-aggregationetherchannel-entre-cisco-e-hpn/} we can achieve high speeds on bare-metal.
 
-(8) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times.
+(B1) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times.
 To avoid overheads,  the values of inter-packet times must be calculated before the actual traffic generation.
@@
 
-(9-11) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}.
+(B2-B5) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}.
 D-ITG offers many stochastic functions for customization of inter-packet times, Ostinato provides a rich set of headers and protocols, and DPDK a high performance on packet generation.
@@
 So, this implementation can enable for SIMITAR high-bandwidth along with traffic realism.
+Finally, a multi-tool FlowGenerator is possible as well, using different sorts of lybraries and tools for producing certains types of flows.
+For example, using SURGE\cite{surge-paper} to create HTTP flows, and Libtins to produce UDP flows.
 
@@
 In this step, we designed our algorithms presented in chapter ~\ref{ch:modeling-evaluation}, and chose the APIs, packages, and libraries, such as Armadillo\cite{armadillo}, a C++ linear algebra library.
-Many ideas we used to conceive our ideas were inspired by previous works and solutions, such as D-ITG\cite{ditg-paper}, Harpoon\cite{harpoon-validation}, Swing\cite{swing-paper} sourcesOnoff\cite{sourcesonoff-paper}, and LegoTG\cite{legotg-paper}.
+Many ideas we used to conceive our problems were inspired by previous works and solutions, such as D-ITG\cite{ditg-paper}, Harpoon\cite{harpoon-validation}, Swing\cite{swing-paper} sourcesOnoff\cite{sourcesonoff-paper}, and LegoTG\cite{legotg-paper}.
 This procedure continued with incremental upgrades until we arrived on the version presented on the chapter ~\ref{ch:validation}.
@@
 In fact, the higher bottleneck of the project resides on processing performance.
+For processing huges \textit{pcap} files, it still takes a prohibitive amount of time.
 The results on realism, even with a lot of room for improvement, already have a good quality.

### 2018-05-14 SIMITAR/build.py

@@ -62,6 +62,7 @@ def unninstall():
 
 
 def deps():
+	# pip install argcomplete 
 	print_header("Tools dependencies")
 	os.system('sudo apt-get install ostinato;')
 	os.system('sudo apt-get install wireshark')

### 2018-05-14 SIMITAR/libsimitar/NetworkTrace.h

@@ -18,10 +18,15 @@
 #include <vector>
 #include <errno.h>
 #include <unistd.h>
-#include <rapidxml/rapidxml.hpp>
-#include <rapidxml/rapidxml_print.hpp>
-#include <rapidxml/rapidxml_iterators.hpp>
-#include <rapidxml/rapidxml_utils.hpp>
+//#include <rapidxml/rapidxml.hpp>
+//#include <rapidxml/rapidxml_print.hpp>
+//#include <rapidxml/rapidxml_iterators.hpp>
+//#include <rapidxml/rapidxml_utils.hpp>
+#include "rapidxml-1.13/rapidxml.hpp"
+#include "rapidxml-1.13/rapidxml_utils.hpp"
+#include "rapidxml-1.13/rapidxml_print.hpp"
+//#include "rapidxml-1.13/rapidxml_iterators.hpp"
+
 
 using namespace rapidxml;
 using std::string;
